### 2019-08-25 TSC/R1/ReviewResponse.tvt.tex
adding TSC revision folder

\documentclass[11pt]{article}

\usepackage[paper=a4paper,dvips,top=4cm,left=2.5cm,right=2.5cm,
foot=2cm,bottom=4cm]{geometry}
%\usepackage{float}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
%\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{amssymb,amsmath}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{comment}
\usepackage{color,soul}
\usepackage{ragged2e} 
\usepackage[usenames,dvipsnames]{xcolor}
%\usepackage{subfigure}
%\usepackage{flushend}

% *** CITATION PACKAGES ***
%
\usepackage{cite}
%\usepackage[pdftex]{graphicx}

\usepackage[caption=false,font=footnotesize]{subfig}
%
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\setlength{\intextsep}{-1ex} % remove extra space above and below in-line float
\newcommand{\SCS}{\textsc{iCS}\xspace}
\newcommand{\SCSP}{\textsc{fCS}\xspace}
\newcommand{\MCSP}{\textsf{MCSP}\xspace}
\newcommand{\dMCSP}{\textsf{dMCSP}\xspace}
\newcommand{\focs}{\textsc{foCS}\xspace}
\newcommand{\iocs}{\textsc{ioCS}\xspace}
\newcommand{\fcs}{\textsc{fCS}\xspace}
\newcommand{\ics}{\textsc{iCS}\xspace}

\ifodd 1
\newcommand{\com}[1]{{\color{ForestGreen} #1}}%revise of the text
\else
\newcommand{\com}[1]{#1}
\fi

\begin{document}

\title{Response Letter for manuscript VT-2016-01986: ``Microgrid Revenue Maximization by Charging Scheduling of EVs in Multiple Parking Stations'' \\
	\vspace{4mm} \large
	by  Bahram~Alinia, Mohammad~H.~Hajiesmaili, and Noel Crespi
}

\maketitle

We are very grateful to the referees for their thorough reviews of our paper and their constructive comments. Based on their suggestions, we have greatly improved the quality of our paper. This document provides a summary of changes made in the revised
manuscript and detailed responses to the comments of the reviewers. The main changes in the revised manuscript are summarized below:

\begin{enumerate}
\item Based on the critical comments of the reviewers regarding the practicality of the system model and randomness in EVs' demand, we added Section VI ``Online Solution'' to the revised manuscript that provides efficient online and practical algorithms for the studied problems.

\item The entire simulation section is revised to add the result of the new online algorithms along with the previous offline solutions.

\item The sections "Related Works" and "Introduction" are revised. Specially, we cited new references to position our work and clarify the contributions.

\end{enumerate}

In what follows, we mention first the comments (as appeared in the decision letter) followed by a description on how we addressed those comments in the paper.

\newpage
\section{Reviewer $\# 1$}
{\color{blue}In this work the authors consider the scheduling of the EV charging in multiple stations which are owned by a single owner. The objective is to minimize the peak value of the aggregated load. This problem is formulated as a mixed integer programming problem. A primal-dual method is developed to approximately solve this problem in polynomial time. Some property of the method is studied theoretically and demonstrated numerically. Overall the paper is clearly written and well organized. Most related references have been appropriately cited. But the current manuscript may be further improved in the following aspects.}

\subsection{Major Comments}
%We sincerely appreciate you for taking the time to review our paper. Following the
%concerns and suggestions, the paper has carefully been revised to address the reviewer's
%comments properly.

\vspace{5mm}
{\color{blue}
\noindent\textbf{Comment 1.1:}\\
It is not clear how to handle the randomness in the load. A critical assumption in both the problem formulation as well as the theoretical analysis is the perfect knowledge of the arrival time (as well as the departure time) of the electric vehicles. This can hardly be true in practice. The authors need to discuss how the uncertainty in this knowledge may affect the performance of the proposed method. This can at least be done numerically.
}

\vspace{5mm}
\noindent\textbf{Response:}\\
We agree with the reviewer that the assumption of having perfect knowledge of EVs' charging profile is not realistic. To address the issue, in the revised version we added a new section (Section VI on Page $8$) that provides ``online'' algorithms for the problems such that the charging profile of an EV (i.e, its arrival time, deadline, valuation, demand, and maximum charging rate) is not revealed to the charging station before the EV arrives to the station and plugged in. We designed two online algorithms in which we have no assumption on the probabilistic modeling of future arrivals. The new algorithms (\iocs for integral revenue model and \focs for fractional revenue model) are simple yet efficient greedy algorithms that at each time slot only plan for available EVs. The time complexity of online algorithms is $O(n^2T)$ (See Table \ref{tbl:tbl1}) where $n$ is the total number of EVs in all charging stations and $T$ is the number of time slots. Based on the proposed algorithms, the whole simulation section is revised accordingly to include the result for the new algorithms along with the results of previous offline algorithms (i.e., \ics and \fcs). According to the results (See Fig. $1$ in the revised manuscript on Page $10$), \iocs (which is the online version of the \ics algorithm) is $83\%$ and $81\%$ of the \ics and optimal solution of integral revenue model on average, respectively. Moreover, \focs is $80\%$ of its offline optimal solution, \fcs, on average.

	\begin{table}[h]
		\centering
		\vspace{3mm}
		\caption{Proposed algorithms}
		\label{tbl:tbl1}
		\begin{tabular}{ | l | c | c | c |}
			\hline
			\textbf{Algorithm} & Revenue model & Online or Offline & \textbf{Time complexity} \\ \hline\hline    
			\fcs& fractional& offline& $O(n^2T+nT^2)$\\\hline  
			\ics& integral& offline& $O(nT\log T+n^2T)$ \\\hline 
			\focs& fractional& online& $O(n^2T)$\\\hline 
			\iocs& integral&  online& $O(n^2T)$\\\hline
		\end{tabular}
	\end{table}
\vspace{5mm}
%\setcounter{table}{0}
\renewcommand{\thetable}{\Alph{table}}
\vspace{4mm}
{\color{blue}
\noindent\textbf{Comment 1.2:}\\
 As a follow-up with the above comment, it would be a good idea to review some literature that considers the uncertainty in the EV charging problem.}

\vspace{7mm}
\noindent\textbf{Response:}\\
We thank the reviewer for this comment. In light of this comment, we added Subsection II-4 on Page $3$ (Scheduling Under Demand Uncertainty). We added new references to the paper and in this subsection, we reviewed online solutions including [17],[26],[29],[30],[33-37] and clearly positioned our contribution. 
%%%%%%%%%%%%%%%%%%%
\newpage
\section{Reviewer $\# 2$}
{\color{blue}The paper is in good written. The approach has demonstrated well, and the result is clear.}

\subsection{Major Comments}

\vspace{5mm}
{\color{blue}
\noindent\textbf{Comment 2.1}\\
To improve the paper further, stochastic factors are recommended to added into the problem formulation. This may result more complicated problem, but it would be more interesting.}

\vspace{7mm}
\noindent\textbf{Response:}\\
We thank the reviewer for pointing this out. We made all necessary changes to add stochastic factors to our problem model, and proposed \focs and \iocs algorithms that work in online scenario such that the information of the EVs reveals only after their arrival. The new algorithm make decisions only based on the information of available EVs. For more details, please see the response for Comment 1.1.

\vspace{5mm}
{\color{blue}
\noindent\textbf{Comment 2.2}\\
The paper cited sufficient papers, but reference [35] is not referred in the content.
}

\vspace{7mm}
\noindent\textbf{Response:}\\
Thanks for the subtle comment. The reference is removed in the revised manuscript, and verified the other references. 
%%%%%%%%%%%%
\newpage
\section{Reviewer $\# 3$}
{\color{blue}This paper addresses an interesting and timely topic. However the reviewer has the following comments and concerns.}

\subsection{Major Comments}

\vspace{5mm}
{\color{blue}
\noindent\textbf{Comment 3.1}\\
There is a great amount of existing work on EV charging scheduling in distribution systems (including Microgrids). More important references must be provided in Section I-B and Section II.}

\vspace{7mm}
\noindent\textbf{Response:}\\
We thank the reviewer for his/her comment. To respond to the reviewer's concern, we added more references to Section I-B on Page $1$ (regarding related studies for microgirds) and Section II (regarding online algorithms for EV scheduling problem on Page $3$).

\vspace{5mm}
{\color{blue}
\noindent\textbf{Comment 3.2}\\
Especially, please clearly distinguish this paper with other publications. Otherwise, it is very difficult to identify any new technical contributions of this paper.}

\vspace{7mm}
\noindent\textbf{Response:}\\
Although the EV scheduling problem received substantial attention by researchers during the last years, we believe that the related studies are different in problem formulation and their solution cannot be applied to the unique setting in our work. Some shortcomings one can observe in the previous studies are as follows:

\begin{itemize}

\item \emph{Unlimited charging speed for EVs}: Many studies such as [12],[21],[23-26],[28], %\cite{Malhotra,Jiang,Wen,YCao,TZhang,Akhavan,Lee,WTang} 
assume that EVs can get charged with unlimited charging speed. Notice that considering the charging rate limitation is crucial to make a solution practical for EV scheduling problem. If the charging rate constraint could be eliminated, many of already existed solutions in job scheduling domain such as the well known YDS algorithm 
(``A scheduling model for reduced CPU energy," \emph{in
Proc. of IEEE FOCS}, 1995) for CPU scheduling problem could be directly applied to EV scheduling problem. The charging speed constraint appears in our problem formulation, and our solutions consider it.

\item \emph{Unlimited resource in charging station:} As explained in Section II-2 of the manuscript on Page $3$, the charger devices installed in the parking stations have limitation
on the maximum electricity that they can transfer at each time unit. However, many studies 
[30],[31],[36],[37]
%\cite{Zhao,WTang,Chen,Karfopoulos} 
do not put a constraint on the peak of charging station which cannot represent a real-world problem. The constraint in (1c) in the manuscript represents the resource limitation at each charging station. Also, constraint in (1b) corresponds to total peak limitation in microgrid.

\item \emph{Revenue model:} We consider two charging models namely integral and fractional revenue models (see Section III-A-3 on Page $4$) and develop solutions under both models which is not covered in the previous studies. Each charging model has its advantages. For example, in some scenarios if users get $90\%$ of their demand, they are still satisfied. But this may not be satisfactory in another scenario that a user needs to receive all its demand to reach to its desired destination. Covering both charging models makes our solutions comprehensive and applicable to a wider range of practical scenarios.

\item \emph{Single station solution:}
As elaborated in Section II-1 on Page $2$,  most of previous solutions [8], [12], [18-23] only work under single charging station scenario while the global optimal solution cannot be obtained by separately solving the single station problems as discussed in Section IV.

\end{itemize}

In our paper, we formulate microgrid revenue maximization problem under local and global peak constraints while addressing the aforementioned limitations in the previous studies. Notice that the problem is not studied yet in its current form. We then develop two offline and two online algorithms for both fractional and integral revenue models summarized in Table \ref{tbl:tbl1}.

Our proposed offline algorithm for fractional revenue model, \fcs, is proved to be optimal.
We also provided  a competitive ratio\footnote{Note that competitive ratio is a well-established metric in theoretical computer science for evaluating the performance of algorithms with no or partial future information. } for the online version of \fcs (i.e., \focs) with the details given in Theorem $5$ on Page $9$. The improvement of the competitive ratio is part of our future studies. Moreover, for \ics algorithm (developed for integral revenue model) and when all EVs have the same arrival time, we proved an approximation ratio of $\alpha = {\Big( 1+\sum_{j=1}^m {\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}\Big)}$, where $p_j$ is local peak constraint in station $j$, $q_j$ is the maximum charging rate of the EVs in station $j$ and $s$ is a slackness parameter.

In the revised manuscript, we modified the Introduction and Related Work Sections to distinguish our contribution with the existing literature clearly.

\vspace{5mm}
{\color{blue}
\noindent\textbf{Comment 3.3}\\
The problem formulation is quite standard. The reviewer is not quite sure whether the proposal methods/algorithms are suitable for a realistic scenario in terms of computational cost, accuracy, complexity, and etc.}

\vspace{7mm}
\noindent\textbf{Response:}\\
We revised the paper carefully to clearly highlight efficiency of our proposed solution regarding the important concerns raised in this comment: 
\begin{itemize}
	\item Regarding how algorithms are suitable for a realistic scenario: we agree that in the previous version of our paper there were concerns related to practicality of the proposed methods. Hence, we solved the issue by proposing two new algorithms that work in online scenario in which the decision making is based on the available information and there is no assumptions on demand profile of future coming EVs. In this way, we resolved one of the most important practicality issues of our method. The detailed explanation of the online algorithms is given in Section~VI of the revised paper on Pages~8-9 and the response to Comment 1.1. 
	\item Regarding computational cost and complexity: the time complexities of all proposed algorithms (two online and two offline) are polynomial and are presented in Table \ref{tbl:tbl1} of the response letter and Table II of the revised manuscript on Page 5. In the revision manuscript we provided the detailed explanation for complexity analysis of our algorithms.

	\item Regarding accuracy: in addition to theoretical bounds that we provided for our algorithms (optimality of \fcs, approximation ratio for \ics when all EVs have same arrival time, and competitive ratio of \focs), in simulation section we compared each algorithm to its optimal solution with a confidence level of $95\%$ to assure the accuracy of results. The results show that our online algorithms (i.e., \iocs and \focs) are, on average, around $80\%$ of their optimal solution while the offline algorithm \ics is always more than $90\%$ of the optimal in different scenarios. For more details, please refer to Section VII of the manuscript on Pages~9-12.
\end{itemize}

\vspace{5mm}
{\color{blue}
\noindent\textbf{Comment 3.4}\\
Overall, the topic is worth investigation. But, to the best of the reviewer's knowledge, this paper presents an artificial concept that couples microgrid revenue maximization with EV charging. It is quite complicated technically, but that cannot hide the fact that fundamental real issues that any real-world microgrid operator faces have not been properly addressed.}

\vspace{7mm}
\noindent\textbf{Response:}\\
Thanks for the comment.
Among several issues that the future microgrids are facing, we believe that their policies in managing huge EV charging demand are critical. The reason is that there is a rapid growth in both EV usage and EV battery size (See Section I-B of the revised manuscript for more details and real-world numbers). Considering this general scenario, the aim of our paper is to solve EV scheduling problem in a small microgrid composing of multiple charging stations owned by a single utility provider such as in a university or building. 
%It is assumed in the paper that the microgrid receives a certain amount of electricity from main grid in a hourly manner and each charging station also has its own constraints on the amount of electricity it can deliver to EVs. We also assume that a central controller is responsible to optimize scheduling of EVs in all charging stations. We did not insert some parameters into our formulation as they have no effect on the final solution such as location of the charging stations. Overall, we agree that the problem formulation is  standard, but we believe that this does not affect the practicality of the solutions.

\vspace{5mm}
{\color{blue}
\noindent\textbf{Comment 3.5}\\
The quality of this paper can be significantly improved. Overall, the reviewer does NOT recommend the acceptance of this paper as is. Another concern is that IEEE TVT may not be a suitable venue for this paper.}

\vspace{7mm}
\noindent\textbf{Response:}\\
To address the reviewer's concern, in addition to the new technical improvements, we carefully improved the organization and presentation of the paper. In summary, we believe that the revised manuscript is significantly improved in terms of technical contribution (by proposing more practical online algorithms, and further complexity analysis of the previous algorithms) and providing more related works and distinguishing our work among the previous work by highlighting unique and important challenges that we are tackling.

%%%%%%%%%%%%%%%%
\newpage
\section{Reviewer $\# 4$}
{\color{blue}This paper proposes fractional and integral revenue models for EV charging scheduling problems in multiple parking stations. The paper is well organized and the technical idea is clearly presented with good integrity. The authors gave the proof of optimum of the proposed algorithm for fractional revenue model, and analyzed the complexity of their algorithms. The reviewer recommends this paper after the revision based on the following suggestions.}

\subsection{Major Comments}

{\color{blue}
\noindent\textbf{Comment 4.1}\\
The authors may elaborate the pricing policy applied by the parking station or utility which governs these parking stations.}

\vspace{2mm}
\noindent\textbf{Response:}\\
Thanks for pointing this precious comment. The variable $v_i$ defined in the paper is valuation of EV $i$ when it receives its demand $D_i$. The valuation $v_i$ in simple and default case is the price imposed by charging station that the owner of EV $i$ should pay to receive its demand, $D_i$ (as it is in the paper). In this case, the charging station is allowed to use any pricing policy as it does not affect our algorithms. With this interpretation, our algorithms solve revenue maximization problem for utility provider. $v_i$ can also represent the valuation of demand from the user's point of view indicating that how much the user will be happy if it receives its submitted demand. With this interpretation, our algorithms try to maximize users' satisfaction or users' social welfare. Therefore, our proposed algorithms are general and work for any valuation setting that is proposed by either EVs or charging stations.

\vspace{5mm}
{\color{blue}
\noindent\textbf{Comment 4.2}\\
This paper only discusses the charging scheduling problem in a static scenario. Existing work such as “QoE-aware Power Management in Vehicle-to-Grid Networks: a Matching-theoretic Approach” in IEEE Transactions on Smart Grid has discussed the EV charging scheduling problem under the mobile scenario. These existing work should be addressed in Section II.}

\vspace{2mm}
\noindent\textbf{Response:}\\
We thank the reviewer for suggesting this related study. In the revised version, we have considered dynamic (online) scenario, as well (for further explanations, please read response to Comment 1.1). In addition, we have added subsection II-4 to review online EV charging algorithms.
The suggested work is related to our studied problem and focuses on assignment of EVs to different charging stations in a network of charging stations (not a real microgrid) assuming that the travel information of EVs is known. We added this work to our references and cited it in Section I and Section II.

%{\color{red}: I think we can mention that in the revised version in addition to static scenario, we have considred dynamic (online) scenario and refer to the comments above for further explanation...}

\vspace{2mm}
{\color{blue}
\noindent\textbf{Comment 4.3}\\
The authors should give the definition of the valuation of EVs in detail in the paper. Does the valuation mean the price that an EV will be charged after the charging is completed?}

\vspace{7mm}
\noindent\textbf{Response:}\\
We believe that the answer to this comment is given in response of Comment 4.1.

%%%%%%%%%%%%
\newpage
\section{Reviewer $\# 5$}
{\color{blue}The paper is focusing on revenue maximization of EV parking stations which are part of a microgrid having an overall capacity limit. The paper is written with a very clear language and a very good organization.

The paper formulated two optimization problems named fractional revenue model and integral revenue model, both of which have a high amount of applicability in a realistic parking station environment. The stated optimization problems are sound and very easy to understand. Next, the paper proposes one algorithm for each of the two stated optimization problems the ISCS and FSCS. Both algorithms are explained in detail. Then, the performance of these two proposed algorithms have been evaluated and  compared withe the optimal result for the integral revenue problem and a greedy algorithm from the literature via simulations. The results show that, the proposed algorithms work quite nice in total revenue, actual peak, and \% of fully charged EVs.

Overall, this is a very good paper focusing on a timely topic.}

\subsection{Major Comments}

\vspace{2mm}
{\color{blue}
\noindent\textbf{Comment 5.1}\\
On page 8, it is stated that the slackness parameter is selected to be as 1.2. Then, in section VI.D, the authors show the results of selecting this slackness and elaborate on its effects. It would be really good, if on page 8 it is stated that the effect of slackness will be investigated in section VI.D. Otherwise, the reader mistakenly thinks that slackness is selected arbitrarily as 1.2 which confuses the reader.}

\vspace{7mm}
\noindent\textbf{Response:}\\
We thank the reviewer for pointing this out. We added the required explanation on Page $10$ of the revised version 
%{\color{red} check the page numbers in the final round, this is not correct.}

\vspace{5mm}
{\color{blue}
\noindent\textbf{Comment 5.2}\\
As explained in section VI.A, the paper uses a probabilistic model for the arrival and departure times, the required recharge amount for each EV. There are some publications in the EV recharging literature which focuses on using realistic traces as an input instead of a probabilistic one. The usage of a realistic vehicular mobility trace has been briefly mentioned in the conclusion paper. It might be worthwhile to elaborate more on this topic and explain what the authors expect if such a realistic trace would be used.}

\vspace{5mm}
\noindent\textbf{Response:}\\
Thanks for highlighting this point. We agree that using realistic vehicular mobility trace can better expose the strengths and weaknesses of the proposed methods. In light of this comment, we developed and added two online algorithms for both integral and fractional revenue models to the revised manuscript where the details can be found in Section VI. Also, we re-run all simulation scenarios in Section VII to include the new algorithms. The results reveal that the performance of the online solutions are around $80\%$ of the optimal offline solution. The Abstract and Conclusion sections are also updated accordingly.

%We agree with the reviewer

%Thanks for this useful comment.

%We thank the reviewer for pointing this out.

%Thanks for suggesting this point.

%We acknowledge the reviewer for suggesting this point. We agree that the

%We sincerely appreciate you for taking the time to review our paper. Following the concerns and suggestions, the paper has carefully been revised to address the reviewer's comments properly. We also tried to briefly reflect all the clarifications in the revised 4-page manuscript.

%Thanks. We agree that .....

%We agree that ....

%We thank the reviewer for pointing this out.

%Thanks for highlighting this point.

%We thank the reviewer for pointing this precious comment.

%Thanks for pointing this issue.

%We thank the reviewer for suggesting this point.

%\begin{itemize}
%\item[[A7]] D. G. Luenberger, Optimization by Vector Space Methods, John Wiley and Sons, Inc., New York, 1969.   
%\end{itemize}

%\vspace{5mm}
%\noindent\textbf{Response:}\\
%Thanks. We believe that the response to this comment is given within our response to Comment 3.11 above. 
\begin{comment}
			\bibliographystyle{IEEEtranS}

			%	\bibliography{IEEEabrv,references}
			\begin{thebibliography}{1}

\bibitem{Malhotra}
A. Malhotra, G. Binetti, A. Davoudi and I. D. Schizas, ``Distributed Power Profile Tracking for Heterogeneous Charging of Electric Vehicles,'' \emph{IEEE Trans. Smart Grid}, no. 99, pp. 1-10, 2016.

\bibitem{Jiang}
				B. Jiang, and Y. Fei, ``Decentralized Scheduling of PEV On-Street
				Parking and Charging for Smart Grid Reactive Power Compensation,'' in \emph{Proc.
					IEEE PES Innov. Smart Grid Technol. (ISGT)}, Washington, DC, USA, Feb. 2013.

\bibitem{Wen}
				C-K. Wen, J-C. Chen, J-H. Teng, and P. Ting, ``Decentralized Plug-in Electric Vehicle Charging Selection Algorithm in Power Systems,'' \emph{IEEE Trans. Smart Grid}, vol. 3, no. 4, pp. 1779-1789, 2012.

\bibitem{YCao}   
				Y. Cao, and N. Wang, ``Towards Efficient Electric Vehicle Charging Using VANET-Based Information Dissemination,'' \emph{IEEE Trans. on Vehicular Technology}, no. 99   pp. 1-1, 2016.
				%In this article, we aim to improve drivers comfort, e.g., to minimize EV’s charging waiting time. Particularly, the CS-selection decision on where to charge is made by individual EV for privacy and scalability benefits.

\bibitem{TZhang}   
				T. Zhang, W. Chen, and Z. Han, ``Charging Scheduling of Electric Vehicles With Local Renewable Energy Under Uncertain Electric Vehicle Arrival and Grid Power Price,'' \emph{IEEE Trans. on Vehicular Technology}, vol. 63, no. 6, pp. 2600-2612, 2014.
				%In this paper, we consider delay-optimal charging scheduling of the electric vehicles (EVs) at a charging station with multiple charge points. The goal is to minimize the mean waiting time (in ueue) for EVs under the long-term constraint on the cost.

\bibitem{Akhavan}
				E. Akhavan-Rezai, M.F. Shaaban, E.F. El-Saadany, and F. Karray ``Online Intelligent Demand Management of Plug-In Electric Vehicles in Future Smart Parking Lots,'' \emph{IEEE Systems Journal}, no. 99, pp. 1-12, 2015.
\bibitem{WTang}
W. Tang, and Y. J. Zhang,  ``A Model Predictive Control Approach for Low-Complexity Electric Vehicle Charging Scheduling: Optimality and Scalability,'' \emph{IEEE Trans. on Power Systems}, 2017.

\bibitem{yds}
F. F. Yao, A. J. Demers, and S. Shenker, ``A scheduling model for reduced CPU energy,'' in \emph{ Proc. of 36th IEEE Symposium on Foundations of Computer Science}, 1995.

\bibitem{Lee}
				W. Lee, L. Xiang, R. Schober, and V. W. S. Wong, ``Electric Vehicle Charging Stations With Renewable Power Generators: A Game Theoretical Analysis,'' \emph{IEEE Trans. Smart Grid}, vol. 6, no. 22, pp. 608-617 , 2015.

\bibitem{Zhao}
				S. Zhao, X. Lin, and M. Chen, ``Peak-Minimizing Online EV Charging: Price-of-Uncertainty and Algorithm Robustification,'' in \emph{Proc. of IEEE INFOCOM} ,2015.

\bibitem{Karfopoulos}
				E. L. Karfopoulos, and N. Hatziargyriou, ``Distributed Coordination of Electric Vehicles Providing V2G Services,'' \emph{IEEE Trans. on Power Systems}, vol. 31, no. 1, pp. 329-338, 2015.

\bibitem{Chen}
				S. Chen and L. Tong, ``iEMS for Large Sscale Charging of Electric Vehicles
				Architecture and Optimal Online Scheduling,'' \emph{in Proc. IEEE Int. Conf.
					Smart Grid Commun. (SmartGridComm)}, 2012.

				%%

\bibitem{Zen}
M. Zen, S. Leng, Y. Zhang, and J. He,``QoE-aware Power Management in Vehicle-to-Grid Networks: a Matching-theoretic Approach,'' \emph{IEEE Trans. of Smart Grids,} vol. PP, no. 99, 2016.

			\end{thebibliography}
\end{comment}

\end{document}

6741 460 573 918

### 2019-08-25 TSC/Response-TSC.tex
adding TSC revision folder

\documentclass[11pt]{article}

\usepackage[paper=a4paper,dvips,top=4cm,left=2.5cm,right=2.5cm,
foot=2cm,bottom=4cm]{geometry}
%\usepackage{float}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
%\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{amssymb,amsmath}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{comment}
\usepackage{color,soul}
\usepackage{ragged2e} 
\usepackage[usenames,dvipsnames]{xcolor}
%\usepackage{subfigure}
%\usepackage{flushend}

% *** CITATION PACKAGES ***
%
\usepackage{cite}
\usepackage[pdftex]{graphicx}
\graphicspath{{figRes/}{../}}

\usepackage[caption=false,font=footnotesize]{subfig}
%
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\setlength{\intextsep}{-1ex} % remove extra space above and below in-line float

\newcommand{\sa}{\textsc{SmartAllocate}}
\newcommand{\rc}{\textsc{ReConsider}}
\newcommand{\bc}{\textsc{BetaCover}}
\newcommand{\ics}{\textsc{iCS}\xspace}
\newcommand{\fcs}{\textsc{fCS}\xspace}
\newcommand{\MCSP}{\textsf{SPAN}\xspace}
\newcommand{\dMCSP}{\textsf{dSPAN}\xspace}
\newcommand{\focs}{\textsc{foCS}\xspace}
\newcommand{\iocs}{\textsc{ioCS}\xspace}
\newcommand{\finalalg}{\textsc{ioCS+}\xspace}
\newcommand{\opt}{\textsc{OPT}\xspace}
\newcommand{\alg}{\textsc{ALG}\xspace}
\newcommand{\rtl}{\textsc{GreedyRTL}\xspace}
\newcommand{\iolp}{\textsc{ioLP}\xspace}
\newcommand{\folp}{\textsc{foLP}\xspace}

\ifodd 1
\newcommand{\rev}[1]{{\color{black}#1}}%revise of the text
\newcommand{\com}[1]{\textbf{\color{red}(Bahram says: #1)}}%comment of the text
\newcommand{\comm}[1]{\textbf{\color{red}(Mohammad says: #1)}}%comment of the text
\else
\newcommand{\rev}[1]{#1}
\newcommand{\com}[1]{}
\fi

\usepackage[colorinlistoftodos, textwidth=4cm, shadow]{todonotes}
\newcommand{\bahram}[1]{\todo[inline,color=orange!40]{{\it Bahram:~}#1}}
\newcommand{\enrique}[1]{\todo[inline,color=blue!15]{#1}}
\begin{document}

\title{Response Letter for manuscript TSG-01885-2017 ``Online EV Scheduling Algorithms for Adaptive Charging Networks with Global Peak Constraints'' \\
	\vspace{4mm} \large
	by  Bahram~Alinia, Mohammad~H.~Hajiesmaili, Zachary J. Lee, Noel Crespi, and Enrique Mallada
}

\maketitle

\textbf{Dear Editor,}

We are very grateful for handling our paper and the time and effort that you and your team put into the process. We have thoroughly revised our manuscript based on your and the referees' constructive comments. This document provides a summary of changes made in the revised manuscript and detailed responses to the comments of the reviewers. The major changes in the revised manuscript are summarized below:

\begin{enumerate}
\item \textit{Better articulation of the paper's positioning, contribution, and significance}. 
\begin{itemize}
\item To highlight the positioning of our work among the extensive literature in EV charging scheduling, we added further explanations in Introduction to determine the exact scenario of interest among others. While several related work consider  EV scheduling in low-load regimes, our work tackle the resource-limited EV scheduling in high-load regimes. More details are given in response to Comment 3.1. 
\item We added a new Related Work Section in the revision (Section II) to highlight the positioning, contribution, and difference of our work as compared to the existing literature. The organization of the related work is based on the constructive Comment 1.0.3 of Reviewer 1. More details are given in response to Comments 1.0.1 and 1.0.3.
\item We re-organized and improved our the motivation statement and unique challenges of tackling ``global peak constraints'' in Introduction by considering Caltech ACN as a real example, \rev{clarifying the technical differences between scheduling problem with and without the global peak constraint}.  More details are given in response to Comment 2.2.
\end{itemize}
\item \textit{Better presentation and making the paper to be self-contained.} We have failed in our previous version of the paper to present our work in a self-contained manner. In the revision we compiled a 10-page manuscript by adding two new sections on Related Work (Section II) and offline algorithm design (Section IV-A), to the main manuscript. As mentioned in the previous item, related work helps to clarify the positioning, contribution, and significance of our work. In addition, with offline algorithm design in the main body, we do not refer to any algorithm in Appendix anymore, and it helps to follow the other online and offline algorithms easier. More details are given in responses to Comments 1.0.2 and 2.1.

\item \textit{More clarification on the valuation model}. Since we tackle EV charging scheduling in resource-limited scenarios with peak-constraints, we formulated a \rev{social welfare maximization problem} in which the goal is to achieve optimal revenue from the heterogeneous EVs with different valuations. We clarified the notion of valuation in system model in Section III-A in Page 3. More details are given in responses to Comments 1.2, 1.4, 2.3, and 3.1.

\item \textit{Re-implementation of all simulations and providing more explanations on simulation scenarios and setup.}  The EV battery properties including charging rates, etc., that we used in the first submission were not up-to-date according to the latest battery \rev{and chargers} technologies. In the revised version, we updated those properties and re-implemented all the simulations. We explained the simulation set-up in more details in Section VI. We combined two figures to save more space and provide more room and to be able to compare our proposed online and approximate algorithms to the optimal solution and existing algorithms in single plots. More details are given in responses to Comments 1.13, 1.14, 1.15, 1.16, 2.6, and 3.2.

\end{enumerate}

In what follows, we mention first the comments (as appeared in the decision letter, highlighted in {\color{blue} blue} in this letter) followed by a description on how we addressed those comments in the paper. Once again, thank you and your team for providing very constructive comments to help in improving this paper.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

%\renewcommand{\thesection}{\arabic{count})}
%\newcounter{count}
%\stepcounter{count}
%\addtocounter{section}{1}
%\setcounter{section}{1}
{\Large\textbf{Editor's Comments:}}
\vspace{3mm}

{\color{blue}All three reviewers have expressed concern regarding the necessity of appendix, which makes the paper over the page limit set by this journal. The authors are advised to reduce the length of their paper. In addition, organization of the paper needs to be improved and contribution needs to be clarified.}

\vspace{5mm}
\noindent\textbf{Response:}
Based on the constructive comments, we revised the paper in 10 pages  by adding important contents such as literature review and an important technical contribution on offline algorithm design for fractional business model. 
By adding these contents and revising the paper carefully, the contribution of our paper is highlighted by demonstrating (1) the importance, uniqueness, and challenges of our specific problem motivated by observations from Caltech adaptive charging network; and (2) differences with the similar existing works in terms of system model, and proposed technical solutions.  More details are given in the aforementioned major comments and also the specific responses to the reviewers.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Reviewer $\# 1$}
{\color{blue}}
%
%\vspace{4mm}
%{\color{blue}\noindent\\
%We sincerely appreciate you for taking the time to review
%our paper. Following the concerns and suggestions, the paper
%has carefully been revised to address the reviewer's comments
%properly.
%}

{\color{blue}The authors in this paper present two online algorithms to schedule EV charging for two different business models.}
\vspace{3mm}

$\vartriangleright$ \noindent\textbf{Response:}

We appreciate the reviewer's effort for his/her in-depth review. Below is our itemized response to this comment.

\vspace{3mm}
{\color{blue}
\textbf{1.0.1.} While the authors try to present extensive proof on the optimality of their algorithms, the problem of EV scheduling is an old problem and the problem authors discuss are no longer the most essential/important issues. 
 }
\vspace{3mm}

	$\vartriangleright$ \noindent\textbf{Response:}

We agree with the reviewer that the general EV scheduling problem has been studied extensively in the recent years, which demonstrates its importance in facilitating the deployment of EVs in energy systems. However, based on a real-world hierarchical architecture in the Adaptive Charging Network (ACN) in California Institute of Technology, in this work, we identified that the global peak constraint of the ACN results in a unique, yet challenging EV scheduling scenario that has not been addressed in the existing work.  Consequently, we formulated the corresponding EV scheduling problem and proposed solutions in two possible business models. Our experimental results also show that our scheduling mechanisms can achieve better performance as the existing scheduling practices in Caltech ACN, and at the same time the solutions can provide sound analytical performance guarantees. We further the positioning and significance of our paper in the highlighted parts of the Introduction.

	\vspace{3mm}
{\color{blue}	
\textbf{1.0.2.} The writing of the paper is quite confusing and hard to follow. It's more like a technical report that lacks good context. The authors simply cite certain algorithm from other paper without explaining it, making it very difficult for the reader to follow.}

\vspace{3mm}
	$\vartriangleright$ \noindent\textbf{Response:}

	This is because of the page limit in the first submission. 
	In the revised manuscript, we complied a 10-pages manuscript by reorganizing the paper and adding several important contents to the main body of the paper to make it self-contained. In particular, we added an optimal offline algorithm from our technical report to the revised manuscript with detailed explanations. Hence, in the revised version there is no more algorithm cited from other references or our technical report. The details of this algorithm is in Section IV-A, Pages 4-5 of the revised manuscript.

%\bibliography{ref-response}{}
%\vspace{-3mm}
%\bibliographystyle{ieeetr}

\end{document}

### 2019-08-25 TSC/R1/res.tex
adding TSC revision folder

\documentclass[11pt]{article}

\usepackage[paper=a4paper,dvips,top=4cm,left=2.5cm,right=2.5cm,
foot=2cm,bottom=4cm]{geometry}
%\usepackage{float}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
%\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{amssymb,amsmath}
\usepackage{caption}
%\usepackage{subcaption}
\usepackage{comment}
\usepackage{color,soul}
%\usepackage{ragged2e} 
%\usepackage[usenames,dvipsnames]{xcolor}
%\usepackage{subfigure}
%\usepackage{flushend}
% *** CITATION PACKAGES ***
%
\usepackage{cite}
\usepackage[pdftex]{graphicx}
\graphicspath{{figRes/}{../}}

\usepackage[caption=false,font=footnotesize]{subfig}
%
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\setlength{\intextsep}{-1ex} % remove extra space above and below in-line float

\newcommand{\sa}{\textsc{SmartAllocate}}
\newcommand{\rc}{\textsc{ReConsider}}
\newcommand{\bc}{\textsc{BetaCover}}
\newcommand{\ics}{\textsc{iCS}\xspace}
\newcommand{\fcs}{\textsc{fCS}\xspace}
\newcommand{\MCSP}{\textsf{SPAN}\xspace}
\newcommand{\dMCSP}{\textsf{dSPAN}\xspace}
\newcommand{\focs}{\textsc{foCS}\xspace}
\newcommand{\iocs}{\textsc{ioCS}\xspace}
\newcommand{\finalalg}{\textsc{ioCS+}\xspace}
\newcommand{\opt}{\textsc{OPT}\xspace}
\newcommand{\alg}{\textsc{ALG}\xspace}
\newcommand{\rtl}{\textsc{GreedyRTL}\xspace}
\newcommand{\iolp}{\textsc{ioLP}\xspace}
\newcommand{\folp}{\textsc{foLP}\xspace}

\ifodd 1
\newcommand{\rev}[1]{{\color{black}#1}}%revise of the text
\newcommand{\com}[1]{\textbf{\color{red}(Bahram says: #1)}}%comment of the text
\newcommand{\comm}[1]{\textbf{\color{red}(Mohammad says: #1)}}%comment of the text
\else
\newcommand{\rev}[1]{#1}
\newcommand{\com}[1]{}
\fi

\usepackage[colorinlistoftodos, textwidth=4cm, shadow]{todonotes}
\newcommand{\bahram}[1]{\todo[inline,color=orange!40]{{\it Bahram:~}#1}}
\newcommand{\enrique}[1]{\todo[inline,color=blue!15]{#1}}
\begin{document}

\title{Response Letter for manuscript TSG-01885-2017 ``Online EV Scheduling Algorithms for Adaptive Charging Networks with Global Peak Constraints'' \\
	\vspace{4mm} \large
	by  Bahram~Alinia, Mohammad~H.~Hajiesmaili, Zachary J. Lee, Noel Crespi, and Enrique Mallada
}

\maketitle

\textbf{Dear Editor,}

We are very grateful for handling our paper and the time and effort that you and your team put into the process. We have thoroughly revised our manuscript based on your and the referees' constructive comments. This document provides a summary of changes made in the revised manuscript and detailed responses to the comments of the reviewers. The major changes in the revised manuscript are summarized below:

\begin{enumerate}
\item \textit{...}.

\end{enumerate}

In what follows, we mention first the comments (as appeared in the decision letter, highlighted in {\color{blue} blue} in this letter) followed by a description on how we addressed those comments in the paper. Once again, thank you and your team for providing very constructive comments to help in improving this paper.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

%\renewcommand{\thesection}{\arabic{count})}
%\newcounter{count}
%\stepcounter{count}
%\addtocounter{section}{1}
%\setcounter{section}{1}
{\Large\textbf{Editor's Comments:}}
\vspace{3mm}

{\color{blue}The reviewers have identified several issues with the paper that lie mainly with a lack of justification for some of the assumptions made which restrict the value of the theoretical results produced. Also the authors need to clearly delineate this work from their previous work. A major revision of this paper is recommended.}

\vspace{5mm}
\noindent\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Reviewer $\# 1$}

{\color{blue} The authors fail to explain the difference of the first part on the fractional model from their earlier work: several 2-competitive scheduling methods are listed by Alinia et al. (2018) and references, including an algorithm with a better competitive ratio and/or runtime. I think this should not have been included in this paper. }
\vspace{3mm}

$\vartriangleright$ \noindent\textbf{Response:} 
Our earlier work presents algorithms for only fractional revenue model. Current manuscript, which can be considered as journal extension of the previous work, studies both fractional and integral models. Although the presented algorithms in the conference version provide a competitive ratio of $2-1/U$ (with $U$ as "scarcity level"), the proof holds when all EVs have the same maximum charging rate. In the current study, we consider hetregenousity in this parameter and prove the online algorithm is 2-competitive.

To clarify this, we added an explanation in Section ...

\vspace{3mm}
{\color{blue} Furthermore, why is there no inclusion of electricity prices and/or value for demand response, which is a particular powerful use case for EV charging scheduling? More generally speaking, please add a proper motivation of the two models: when would we use which model in practice? }
\vspace{3mm}

{\color{red}: @Mohammad: This is not clear for me in most parts}

$\vartriangleright$ \noindent\textbf{Response:} 
The variable $v_i$ defined in the paper is valuation of EV $i$ when it receives its demand $D_i$. In simple and default case $v_i$ can represent the price imposed by charging station that the owner of EV $i$ should pay to receive its demand, $D_i$ (as it is in the paper). In this case, the charging station is allowed to use any pricing policy as it does not affect our algorithms. With this interpretation, our algorithms solve revenue maximization problem for utility provider. $v_i$ can also represent the valuation of demand from the user's point of view indicating that how much the user will be happy if it receives its submitted demand. With this interpretation, our algorithms try to maximize users' satisfaction or users' social welfare. Therefore, our proposed algorithms are general and work for any valuation setting that is proposed by either EVs or charging stations.

\vspace{3mm}
{\color{blue} The approach for the integral model seems novel to me, and it is nice that a theoretical analysis is included. However, the theoretical results are disappointing, which reduces their value a bit: they only hold under severe restrictions: Thm.4 only holds "when EVs have same arrival time" ... which is quite unrealistic. Thm.5 only holds for m=1, which is the single constraint often found in literature. (Of which the authors write: [our] "problem is different from EV charging scheduling with capacity constraint in single station scenarios [2], [4], [7]–[12]".). Moreover, the ratios are pretty weak (for Thm.4: number of charging stations +1 times the optimal, for Thm.5: number of different arrival slots + 1 times the optimal). }
\vspace{3mm}

$\vartriangleright$ \noindent\textbf{Response:} 
...

\vspace{3mm}
{\color{blue} Actual useful proof of the quality of the proposed algorithm can be found in the experiments. I think the paper could be interesting if this section received significantly more attention, for example
 - showing the effect of problem parameters (range in arrival times, departure times, values, demand, number of vehicles, etc.) on the performance of the  algorithms (not only value but also computation time)
 - comparing to other methods from the literature, e.g. Yao et al. (2017) use a charging priority (think of this as your value) and adding the extra CS constraints is pretty straightforward for such MILP models. Moreover, Yao et al. (2017) also include prices as well as demand response, but also these can of course just be ignored.
 }
\vspace{3mm}

$\vartriangleright$ \noindent\textbf{Response:} 
{\color{red}@Mohammad: We should try to distinguish our work from Yao et al. but it seems difficult.}

\vspace{3mm}
{\color{blue} The implementation of the algorithms and the benchmark problems would be helpful if submitted as supplementary files. }
\vspace{3mm}

$\vartriangleright$ \noindent\textbf{Response:} 
We listed pseudo-codes for all proposed algorithms and an interested reader can easily convert them to real implementation code. We believe that detailed implementation of the algorithms has no added value as the goal here is to provide algorithms and analysis and not focusing on programming challenges.

\vspace{3mm}
{\color{blue} On page 2 and page 7 you write that "the underlying problem is NP-hard due to 0/1 selection" and you mention knapsack, but in fact knapsack is one of the easier NP-hard problems. It seems that your integral model models a strongly NP-hard problem, see De Weerdt et al. (2018). }
\vspace{3mm}

$\vartriangleright$ \noindent\textbf{Response:} 
Thanks for the point. We agree that our problem is strongly NP-Hard and we corrected the related phrases in the manuscript.

\vspace{3mm}
{\color{blue} On page 4, l19, the constraint (1d) seems to force equal charging speed from the arrival time to the departure time. I don't think this constraint is met by the greedy algorithms, is it? Then this is not your "Scheduling Problem for Adaptive charging Network (SPAN) under fractional revenue model"? }
\vspace{3mm}

$\vartriangleright$ \noindent\textbf{Response:} 
...

\vspace{3mm}
{\color{blue} p4: The discussion of the offline algorithm could benefit from an example why straightforwardly allocating the most valuable ($v_i/D_i$) is not optimal (because of charging speed limits), and then introduce the greedy re-allocation (based on flexibility). }
\vspace{3mm}

$\vartriangleright$ \noindent\textbf{Response:} 
...

\vspace{3mm}
{\color{blue} In the experimental evaluation the results for both models are put together in the same figure, which gets us into the odd situation that some results are better than optimal.
 }
\vspace{3mm}

$\vartriangleright$ \noindent\textbf{Response:} 
...

\vspace{3mm}
{\color{blue} typos:
p3: "We formulate Scheduling"

p3:l33: "ptotal, which we refer to it as the global peak, hereafter" => I think you mean to say that this is the capacity limit, not the global peak.

p4: "a definitions"

p7: "If there is not enough resources"

p7: "In primal-dual algorithm"

note [page 8]: Other approximations?

p8: "under integral mode"

p8: "for fractional mode"

p8: "We propose the IOCS"

p8: "over set of"

p8: "with optima"

p8: "in accordance to NHTS survey"

p8: "of arriving an EV in the peak hours"

p9: "in integral revenue

p9: "The proposed algorithms compared to"

p9: "IO LP.Recall"
 }
\vspace{3mm}

$\vartriangleright$ \noindent\textbf{Response:} 
...

\begin{itemize}
\item B. Alinia, M. S. Talebi, M. H. Hajiesmaili, A. Yekkehkhany and N. Crespi, Competitive Online Scheduling Algorithms with Applications in Deadline-Constrained EV Charging, IEEE/ACM 26th International Symposium on Quality of Service (IWQoS), 2018
doi: 10.1109/IWQoS.2018.8624184

\item de Weerdt, M. M., Albert, M., Conitzer, V., \& Linden, K. V. D. (2018). Complexity of scheduling charging in the smart grid. In Proceedings of the Twenty-Seventh International Joint Conference on Artificial Intelligence (pp. 4736-4742).

\item Yao, L., Lim, W. H., \& Tsai, T. S. (2017). A real-time charging scheme for demand response in electric vehicle parking station. IEEE Transactions on Smart Grid, 8(1), 52-62.
\end{itemize}

\newpage
\section{Reviewer $\# 2$}

\vspace{3mm}
{\color{blue} 1.      The authors need to examine the literature more thoroughly. Although the proposed methods have a certain degree of novelty, more related works exist. For example, the authors could consider some of the following papers, while others may also exist.

\begin{itemize}
\item a: Huang, S., Wu, Q., Oren, S. S., Li, R., \& Liu, Z. (2015). Distribution locational marginal pricing through quadratic programming for congestion management in distribution networks. IEEE Transactions on Power Systems, 30(4), 2170-2178.

\item b: Hu, J., You, S., Lind, M., \& Østergaard, J. (2014). Coordinated charging of electric vehicles for congestion prevention in the distribution grid. IEEE Transactions on Smart Grid, 5(2), 703-711.

\item c: Rigas, E. S., Ramchurn, S. D., Bassiliades, N., \& Koutitas, G. (2013, October). Congestion management for urban EV charging systems. In 2013 IEEE International Conference on Smart Grid Communications (SmartGridComm) (pp. 121-126). IEEE.

\end{itemize}
}
\vspace{3mm}

$\vartriangleright$ \noindent\textbf{Response:} 
...

\vspace{3mm}
{\color{blue} The authors claim that if prediction or modelling techniques were used, the performance of the proposed algorithms would deteriorate. However, they do not present any results to support their claim.  }
\vspace{3mm}

$\vartriangleright$ \noindent\textbf{Response:} 
...

\vspace{3mm}
{\color{blue} An interesting extension would be to let users define a set of CSs to charge and let the scheduling algorithms take the final decision of the CS to charge. In this way, the flexibility of the algorithms would increase and the load across the CSs could be better managed. However, the downside would be that the complexity of the algorithms would increase. }
\vspace{3mm}

$\vartriangleright$ \noindent\textbf{Response:} 
...

\vspace{3mm}
{\color{blue} Is truth telling regarding the EVs’ valuations guaranteed? Is it possible for the EVs to cooperate and report lower valuations? It is not clear in the paper. If not, this could come in contrast with the revenue maximization objective function. Moreover, this would cause serious implications in the online algorithms which use the valuations to select the EVs to charge.     }
\vspace{3mm}

$\vartriangleright$ \noindent\textbf{Response:} 
...

\vspace{3mm}
{\color{blue} The length of each time point is set to 1 hour. This is too long, and the accuracy of the algorithms is reduced. Moreover, the online algorithm is not really online, as it schedules EVs every hour. }
\vspace{3mm}

$\vartriangleright$ \noindent\textbf{Response:} 
...

\vspace{3mm}
{\color{blue} Some results on execution times and scalability of the proposed algorithms must be added.
 }
\vspace{3mm}

$\vartriangleright$ \noindent\textbf{Response:} 
...

%\bibliography{ref-response}{}
%\vspace{-3mm}
%\bibliographystyle{ieeetr}

\end{document}

### 2019-08-25 TSC/R1/similarResponseLetters/ResponseLetter-tsg-submitMay11.tex
adding more responses

\documentclass[11pt]{article}

\usepackage[paper=a4paper,dvips,top=4cm,left=2.5cm,right=2.5cm,
foot=2cm,bottom=4cm]{geometry}
%\usepackage{float}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
%\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{amssymb,amsmath}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{comment}
\usepackage{color,soul}
\usepackage{ragged2e} 
\usepackage[usenames,dvipsnames]{xcolor}
%\usepackage{subfigure}
%\usepackage{flushend}

% *** CITATION PACKAGES ***
%
\usepackage{cite}
\usepackage[pdftex]{graphicx}
\graphicspath{{figRes/}{../}}

\usepackage[caption=false,font=footnotesize]{subfig}
%
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\setlength{\intextsep}{-1ex} % remove extra space above and below in-line float

\newcommand{\sa}{\textsc{SmartAllocate}}
\newcommand{\rc}{\textsc{ReConsider}}
\newcommand{\bc}{\textsc{BetaCover}}
\newcommand{\ics}{\textsc{iCS}\xspace}
\newcommand{\fcs}{\textsc{fCS}\xspace}
\newcommand{\MCSP}{\textsf{SPAN}\xspace}
\newcommand{\dMCSP}{\textsf{dSPAN}\xspace}
\newcommand{\focs}{\textsc{foCS}\xspace}
\newcommand{\iocs}{\textsc{ioCS}\xspace}
\newcommand{\finalalg}{\textsc{ioCS+}\xspace}
\newcommand{\opt}{\textsc{OPT}\xspace}
\newcommand{\alg}{\textsc{ALG}\xspace}
\newcommand{\rtl}{\textsc{GreedyRTL}\xspace}
\newcommand{\iolp}{\textsc{ioLP}\xspace}
\newcommand{\folp}{\textsc{foLP}\xspace}

\ifodd 1
\newcommand{\rev}[1]{{\color{black}#1}}%revise of the text
\newcommand{\com}[1]{\textbf{\color{red}(Bahram says: #1)}}%comment of the text
\newcommand{\comm}[1]{\textbf{\color{red}(Mohammad says: #1)}}%comment of the text
\else
\newcommand{\rev}[1]{#1}
\newcommand{\com}[1]{}
\fi

\usepackage[colorinlistoftodos, textwidth=4cm, shadow]{todonotes}
\newcommand{\bahram}[1]{\todo[inline,color=orange!40]{{\it Bahram:~}#1}}
\newcommand{\enrique}[1]{\todo[inline,color=blue!15]{#1}}
\begin{document}

\title{Response Letter for manuscript TSG-01885-2017 ``Online EV Scheduling Algorithms for Adaptive Charging Networks with Global Peak Constraints'' \\
	\vspace{4mm} \large
	by  Bahram~Alinia, Mohammad~H.~Hajiesmaili, Zachary J. Lee, Noel Crespi, and Enrique Mallada
}

\maketitle

\textbf{Dear Editor,}

We are very grateful for handling our paper and the time and effort that you and your team put into the process. We have thoroughly revised our manuscript based on your and the referees' constructive comments. This document provides a summary of changes made in the revised manuscript and detailed responses to the comments of the reviewers. The major changes in the revised manuscript are summarized below:

\begin{enumerate}
\item \textit{Better articulation of the paper's positioning, contribution, and significance}. 
\begin{itemize}
\item To highlight the positioning of our work among the extensive literature in EV charging scheduling, we added further explanations in Introduction to determine the exact scenario of interest among others. While several related work consider  EV scheduling in low-load regimes, our work tackle the resource-limited EV scheduling in high-load regimes. More details are given in response to Comment 3.1. 
\item We added a new Related Work Section in the revision (Section II) to highlight the positioning, contribution, and difference of our work as compared to the existing literature. The organization of the related work is based on the constructive Comment 1.0.3 of Reviewer 1. More details are given in response to Comments 1.0.1 and 1.0.3.
\item We re-organized and improved our the motivation statement and unique challenges of tackling ``global peak constraints'' in Introduction by considering Caltech ACN as a real example, \rev{clarifying the technical differences between scheduling problem with and without the global peak constraint}.  More details are given in response to Comment 2.2.
\end{itemize}
\item \textit{Better presentation and making the paper to be self-contained.} We have failed in our previous version of the paper to present our work in a self-contained manner. In the revision we compiled a 10-page manuscript by adding two new sections on Related Work (Section II) and offline algorithm design (Section IV-A), to the main manuscript. As mentioned in the previous item, related work helps to clarify the positioning, contribution, and significance of our work. In addition, with offline algorithm design in the main body, we do not refer to any algorithm in Appendix anymore, and it helps to follow the other online and offline algorithms easier. More details are given in responses to Comments 1.0.2 and 2.1.

\item \textit{More clarification on the valuation model}. Since we tackle EV charging scheduling in resource-limited scenarios with peak-constraints, we formulated a \rev{social welfare maximization problem} in which the goal is to achieve optimal revenue from the heterogeneous EVs with different valuations. We clarified the notion of valuation in system model in Section III-A in Page 3. More details are given in responses to Comments 1.2, 1.4, 2.3, and 3.1.

\item \textit{Re-implementation of all simulations and providing more explanations on simulation scenarios and setup.}  The EV battery properties including charging rates, etc., that we used in the first submission were not up-to-date according to the latest battery \rev{and chargers} technologies. In the revised version, we updated those properties and re-implemented all the simulations. We explained the simulation set-up in more details in Section VI. We combined two figures to save more space and provide more room and to be able to compare our proposed online and approximate algorithms to the optimal solution and existing algorithms in single plots. More details are given in responses to Comments 1.13, 1.14, 1.15, 1.16, 2.6, and 3.2.

\end{enumerate}

In what follows, we mention first the comments (as appeared in the decision letter, highlighted in {\color{blue} blue} in this letter) followed by a description on how we addressed those comments in the paper. Once again, thank you and your team for providing very constructive comments to help in improving this paper.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

%\renewcommand{\thesection}{\arabic{count})}
%\newcounter{count}
%\stepcounter{count}
%\addtocounter{section}{1}
%\setcounter{section}{1}
{\Large\textbf{Editor's Comments:}}
\vspace{3mm}

{\color{blue}All three reviewers have expressed concern regarding the necessity of appendix, which makes the paper over the page limit set by this journal. The authors are advised to reduce the length of their paper. In addition, organization of the paper needs to be improved and contribution needs to be clarified.}

\vspace{5mm}
\noindent\textbf{Response:}
Based on the constructive comments, we revised the paper in 10 pages  by adding important contents such as literature review and an important technical contribution on offline algorithm design for fractional business model. 
By adding these contents and revising the paper carefully, the contribution of our paper is highlighted by demonstrating (1) the importance, uniqueness, and challenges of our specific problem motivated by observations from Caltech adaptive charging network; and (2) differences with the similar existing works in terms of system model, and proposed technical solutions.  More details are given in the aforementioned major comments and also the specific responses to the reviewers.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Reviewer $\# 1$}
{\color{blue}}
%
%\vspace{4mm}
%{\color{blue}\noindent\\
%We sincerely appreciate you for taking the time to review
%our paper. Following the concerns and suggestions, the paper
%has carefully been revised to address the reviewer's comments
%properly.
%}

{\color{blue}The authors in this paper present two online algorithms to schedule EV charging for two different business models.}
\vspace{3mm}

$\vartriangleright$ \noindent\textbf{Response:}

We appreciate the reviewer's effort for his/her in-depth review. Below is our itemized response to this comment.

\vspace{3mm}
{\color{blue}
\textbf{1.0.1.} While the authors try to present extensive proof on the optimality of their algorithms, the problem of EV scheduling is an old problem and the problem authors discuss are no longer the most essential/important issues. 
 }
\vspace{3mm}

	$\vartriangleright$ \noindent\textbf{Response:}

We agree with the reviewer that the general EV scheduling problem has been studied extensively in the recent years, which demonstrates its importance in facilitating the deployment of EVs in energy systems. However, based on a real-world hierarchical architecture in the Adaptive Charging Network (ACN) in California Institute of Technology, in this work, we identified that the global peak constraint of the ACN results in a unique, yet challenging EV scheduling scenario that has not been addressed in the existing work.  Consequently, we formulated the corresponding EV scheduling problem and proposed solutions in two possible business models. Our experimental results also show that our scheduling mechanisms can achieve better performance as the existing scheduling practices in Caltech ACN, and at the same time the solutions can provide sound analytical performance guarantees. We further the positioning and significance of our paper in the highlighted parts of the Introduction.

	\vspace{3mm}
{\color{blue}	
\textbf{1.0.2.} The writing of the paper is quite confusing and hard to follow. It's more like a technical report that lacks good context. The authors simply cite certain algorithm from other paper without explaining it, making it very difficult for the reader to follow.}

\vspace{3mm}
	$\vartriangleright$ \noindent\textbf{Response:}

	This is because of the page limit in the first submission. 
	In the revised manuscript, we complied a 10-pages manuscript by reorganizing the paper and adding several important contents to the main body of the paper to make it self-contained. In particular, we added an optimal offline algorithm from our technical report to the revised manuscript with detailed explanations. Hence, in the revised version there is no more algorithm cited from other references or our technical report. The details of this algorithm is in Section IV-A, Pages 4-5 of the revised manuscript.

\vspace{3mm}
{\color{blue}
\textbf{1.0.3.} The authors state that most of the existing literature only discusses about optimal operation with single CS, which is not true. The field of EV Demand Side Management has long discussed the optimal operations with EV coordinations, renewable energy and battery storage, which is way beyond the simple scope of single CS scheduling. The reviewer recommends the writer to conduct more in-depth literature review. A good starting point may be "Mukherjee, Joy Chandra, and Arobinda Gupta. "A review of charge scheduling of electric vehicles in smart grid." IEEE Systems Journal 9.4 (2015): 1541-1553."
}

\vspace{3mm}
	$\vartriangleright$ \noindent\textbf{Response:}

We agree with the reviewer that there are extensive literature in the general area of EV demand side management and we have expanded our literature review in the revised version by citing the above survey and several other recent references  such as: 
	 \begin{itemize}
	 	\item P. M. de Quevedo, G. Mun ̃oz-Delgado, and J. Contreras, ``Impact of electric vehicles on the expansion planning of distribution systems considering renewable energy, storage and charging stations,'' IEEE Transactions on Smart Grid, 2017.

	 	\item 	 J. C. Mukherjee and A. Gupta, ``Distributed charge scheduling of plug-in electric vehicles using inter-aggregator collaboration'' IEEE Transactions on Smart Grid, vol. 8, no. 1, pp. 331--341, 2017.

	 	\item M. Shafie-Khah, P. Siano, D. Z. Fitiwi, N. Mahmoudi, and J. P. Catala ̃o, ''An innovative two-level model for electric vehicle parking lots in distribution systems with renewable energy,'' IEEE Transactions on Smart Grid, vol. 9, no. 2, pp. 1506--1520, 2018.
	 \end{itemize}
We fully understand that our statement in the beginning of Related Work section, was not accurate in the \textit{general area of EV demand side management}. We revised our related work to \textit{first} highlight that there are extensive work in this general research direction, and \textit{secondly}, we narrow down our review to those that tackle EV charging scheduling in single or multiple charging scheduling. With these modifications proposed by the reviewer the current version of the Related Work is more comprehensive and it highlights the uniqueness and importance of our work in more organized manner.
	 %And we fully understand that 
%	 However, we study the problem under a different system model which is based on Caltech adaptive charging network by considering local and global peak constraints while the local peak constraints can be over-provisioned. With the over-provisioned peaks, sum of the local peaks is more than the global peak. However, a proper centralized scheduling mechanism can intelligently allocate EVs in different charging stations such that a) resource utilization is maximized compared to non over-provisioned case, and b) the global peak constraint is not violated.
%Moreover, we considered two different business models (i.e., fractional and integral) and developed scheduling algorithms for both online and offline case.
%In addition, we provided extensive analysis regarding the competitive/approximation ratio of the algorithms.

\subsection{Comments}
%We sincerely appreciate you for taking the time to review our paper. Following the
%concerns and suggestions, the paper has carefully been revised to address the reviewer's
%comments properly.

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 1.1:}\\
Page1 line 51: "Caltech ACN[4]". The reference is incorrect.
}}

\vspace{5mm}
\noindent\textbf{Response:}

Thanks for in-depth review of our paper. The cited reference includes an academic paper that describes the Caltech Adaptive Charing Network (ACN) and it is the only reference describing Caltech ACN.  
\\

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 1.2:}\\
Page 1 line 27: What does valuation mean? There is no clear definition for this value. It looks like a "bid" by each customer for their desired power. However, in current business model, the fee is mostly linearly correlated with the energy user uses, so this "valuation" should mostly be the energy demand of the user. However, it is true that the "valuation" could be more nuanced, given different user's profile, need and other background. If this is the case, it should be more clearly explained and the function for "valuation" should be more clearly defined.
}}

\vspace{5mm}
\noindent\textbf{Response:}

In this study, we consider the scenario in which the aggregate EV charging demands are beyond the local and global peak constraints of the adaptive charging network.  In this resource-limited scenario, it is rationale to solve a social welfare maximization problem with the goal of maximizing the aggregate \textit{utility} (in simplified case, \textit{valuation}, as we considered in our paper) of the users, i.e., EVs, in the system. In this way, the parameter $v_i$ denotes the willingness to pay (or valuation) of EV $i$ when it receives the entire demand $D_i$. We assume that $v_i$ is submitted by the user as the input to our optimization framework and it could be different for different users.

In the current business model, the aggregate charging demand is usually lower than the local and global peak constraints,  hence, the charging model pointed by the reviewer makes sense. This flat charging model, however, is not sustainable in the scenarios in which the peak constraint in the charging network hinders fulfilling the entire charging demand of the users and calls for new business models. As advocated in our study (and several other studies, for example \cite{robu2011online,gerding2011online,stein2012model}  in this letter and [8], [11], [12], [33] in the revised manuscript, in EV charging scheduling or in broader way in general utility maximization resource allocation problems), a natural way is to let EVs to announce their willingness to pay (valuations) and try to propose scheduling mechanisms that maximizes the aggregate valuation subject to the capacity constraints of the charging network.

%However, $v_i$ can carry different meanings depending on the application where the simplest interpretation is electricity price. In more complicated cases, $v_i$ can be priority or importance of the user, valuation of received power from the user/aggregator's point of view, etc. In such scenarios, $v_i$ is not a function of the demand. We solve the problem in a general case regardless of the meaning of input variable $v_i$.
%We made it clear in the paper that the valuation represents the profit of the charging station

 In the revised paper, we explained the clear definition of ``valuation'' of the EVs and the further justifications regarding this definition, in Section III-A2, in Page 3. In addition, in Introduction, we referred to the corresponding section for detailed definition of EV charging profiles (including valuations) right after the first appearance.

 %In simple and default case is the price imposed by charging station that the owner of EV $i$ should pay to receive its demand, $D_i$ (as it is in the paper). In this case, the charging station is allowed to use any pricing policy as it does not affect our algorithms. With this interpretation, our algorithms solve revenue maximization problem for utility provider. $v_i$ can also represent the valuation of demand from the user's point of view indicating that how much the user will be happy if it receives its submitted demand. With this interpretation, our algorithms try to maximize users' satisfaction or users' social welfare. Therefore, our proposed algorithms are general and work for any valuation setting that is proposed by either EVs or charging stations.

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 1.3:}\\
The integral model is not quite a practical and meaningful one. It is rarely the case that if a service provider fails to provide full service, they will not charge for service at all. Again, as in 2, most of the income of current (and near future) existing service providers are linearly correlated to the energy, so this problem will never come across. However, although it doesn't exist yet, it is also true that there can be a "guaranteed" service to charge "all-or-nothing" to users. This can be an interesting business model but there are many questions that need to be answered, such as: what if the customer proposes a demand that can be never reached (such as ask for 40kWh with a 30kWh to be filled battery) and a high valuation? In this case, the system will charge him with high priority but will never charge him for fee. Also, what happens to the users who get rejected due to request not being feasible? It would appear that they will occupy a charging station without getting charged, which is a waste of physical resources and a bad service to customer.
}}

\vspace{5mm}
\noindent\textbf{Response:}

The ``integral charging model'' is not happening in the current EV charging scenarios. However, as stated by the reviewer this model makes sense as a future EV charging scheduling business model specially in high demand congested scenarios. There are several technical questions and challenges to realize this model, as some highlighted by the reviewer. Given that the underlying optimization problem that captures the integral business model in a combinatorial NP-hard problem, our focus in this model is to design online algorithms that work efficiently in this scenario. This, to our belief, is one of the most critical challenges to realize the integral business model.

We acknowledge the other challenges and questions raised by the reviewer on the feasibility scenarios of this model and we can categorize them generally into preprocessing phase before optimization step, where the inputs to the problem are examined to be feasible (as we have stated in our system model in Section II-A2).

 Along the line of questions raised by the reviewer, another important issue is that users should be informed at their arrival time about the admission decision not at the deadline otherwise they might wait for a long time in the charging station and finally leave the station with empty hands. To solve this issue, charging scheduling scenarios with ``on-arrival commitment'' should be proposed. Our investigation shows that satisfying this property in solution design is quite challenging that requires different set of algorithms. We addressed the charging scheduling with on-arrival commitment in a separate work that is in submission now. To clarify the differences, we have referred to this work in the revised manuscript with explanations of differences in Section II in Page 2.

%In integral model, the charging algorithms need to be designed in a way that they give a user all its demand or nothing as it is done by our algorithms. Therefore, it cannot happen that a user receive partial demand and pay nothing.

%In the paper we assumed that the submitted demands are feasible with respect to arrival time, deadline, battery capacity and maximum charging rate. In practice the state of charge a battery is known and therefore, non feasible demands can be easily detected by the charging system.

%Regarding rejected users, they need to leave the charging station when they are rejected as it can happen in conventional fuel stations.

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 1.4:}\\
It seems that the ranking of both models is largely dependent on different "unit valuation" of different users (page 3 line 46-49, page 4 line 25-27). However, in most of the cases, most users only want to pay for standard rate and very few are fine with high premium (let alone government regulation). It’s also a very impractical assumption that every user will propose their desired valuation every time they charge their car, and everyone proposes a different one so that the ranking is meaningful. Given this, is there any value of the algorithm if everyone's unit bid is the same? In most of scheduling algorithms, the “ranking” is done with requested kWh or remaining time, which the authors did not take into account in their presented ranking.
}}

\vspace{5mm}
\noindent\textbf{Response:}

Given the explanations in response to Comment 1.3, and considering valuations as the willingness of EVs to pay in capacity-constrained scenarios, the algorithm design in our work based on different ``unit valuation'' makes sense. The reviewer's argument on the willingness of users to pay for standard rate is reasonable in the scenarios without capacity constraints, which is not sustainable in future congested scenarios.

We also emphasize that heterogeneity in users' valuation is a common model considered in recent research studies. For example, see \cite{robu2011online,gerding2011online,stein2012model} in this letter, and [8], [11], [12], [33] in the revised manuscript.

%We also would like to take the reviewer's attention to \cite{} in this letter where also distinguish the EVs based on their unit values.

%\comm{@Bahram: please complete this sentence by providing some references from existing work.}
%\bahram{Done.}

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 1.5:}\\
Constraint (1d) is wrong: $y_i^t$ should always be less than $k_i$ no matter how much energy is charged overall, because the max power rate is governed by the physical charging station hardware.

}}

\vspace{5mm}
\noindent\textbf{Response:}

Note that \rev{we always have $\sum_t y_i^{t}\leq D_i$ as it is guaranteed by constraint  (1a). Therefore, constraint (1d) gives us $y_i^{t}\leq k_i$}. As stated in the remarks after problem formulation, the straightforward way to express this constraint is to follow the reviewer's suggestion and simply state that at each time slot $t$, the charging rate of EV $i$ should be less than or equal to its maximum charging rate, i.e., $y_i^t\leq k_i, \forall i,t$. 
However, for the sake of effective algorithm design for integral model and reducing the integrality gap of the relaxed linear problem, this constraint is strengthened in the form of (1d). 
Note that in case that the aggregated charging of EV $i$ during its availability window is equal to its demand, i.e., $\sum_{t^\prime=a_i}^{d_i} y_i^{t^\prime}= D_i$, (1d) reduces to the simple form of $y_i^t\leq k_i$.  
This is a natural and elegant way in approximation algorithm design to improve the performance of the algorithms under linear-relaxation based design.

The corresponding explanation is highlighted in the revised manuscript in Section III-B in Page 4.
\\

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 1.6:}\\
Eq (2) the min function seems unnecessary because (1a) already guaranteed the second term will never be larger than the first term.
}}

\vspace{5mm}
\noindent\textbf{Response:}

Thanks, yes, under a proper algorithm design where over-charging is guaranteed to not happen, as in our algorithm, the min function is unnecessary. Consequently, we removed the min function in the revised version. 
%However, in terms of readability, we think that current form of the equation is more clear.

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 1.7:}\\
Page 2 line 21: the authors claim they use a "valley filling" algorithm. What algorithm is used and how do they affect the scheduling? The effect should be quite significant to the results as many paper solely discusses the optimal operation of those but the author did not mention at all. Also is the entire fCS algorithm copied from [12]?
}}

\vspace{5mm}
\noindent\textbf{Response:}

The valley-filling approach is used in \textsc{SmartAllocate} procedure (listed as Algorithm 4 in Page 7), and it simply tries  to reduce the peak of the system by prioritizing the slots with more available resources. We clarified the explanation of the valley-filling strategy in Section V-A1, in Page 7. Also, its effect is shown by simulation in Section V, subsection ``Comparison Based on Actual Peak'', and Fig. 3, in Page 9.

In the previous submission, the \fcs, as our proposed algorithm, was explained in the technical report in [12] (now [34]). However, in the revised manuscript, we included entire explanation of the algorithm in the main body of the paper.

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 1.8:}\\
In the fractional model, the difference between online and offline is unclear. It seems that if offline algorithm is re-run every time a new car comes, the order is rearranged in real-time and the result should be the same with offline, which is optimal. Given the today's computing power, this should be a very easy job to do.
}}

\vspace{5mm}
\noindent\textbf{Response:}

The proposed approach by the reviewer is a popular, yet straightforward method in the online scheduling. However, it turns out that this approach cannot provide an optimal solution to the problem even in fractional revenue model. In fact, this approach only provides a 2-competitive solution. i.e., the profit obtained by this approach would be $1/2$ of the optimum. We bring an example to clarify.

Fig. \ref{fig:Ex1} shows a simple scenario in a single charging station with $T=2$ and $p_1=p^{\text{total}}=1$. The charging profile of an EV $i$ is shown in the form of $\pi_i=(a_i,d_i,v_i,D_i,k_i)$ where it is assumed that $k_i=1$ for all $i$.
At $t=1$, EVs 1 and 2 arrive and the scheduler has no information about the future coming EVs. If we run an optimal offline algorithm over the available EVs at $t=1$, it will allocate EV 2 at $t=1$ and postpone charging of EV 1 to $t=2$ according to their deadline. Now assume that EV 3 arrives at $t=2$ which has the same demand and unit value as EV 1 (see Fig. \ref{fig:Ex1b}). Then, by re-computing the optimal solution at $t=2$, the solution is to choose either EV 1 or EV 3 to charge due to capacity constraint. Therefore, the final solution obtained by this approach achieves a total revenue of $1+\epsilon$ by charging EVs 2 at $t=1$ and one of the EVs 1 or 3 at $t=2$. However, the optimal solution in this example is charging EV 1 at $t=1$ and EV 3 at $t=2$ and obtaining a gain equal to 2. This example shows that the competitive ratio of the proposed approach by the reviewer cannot be better than $2-\epsilon$ where $\epsilon$ can be arbitrarily small.  
\begin{figure*}[t]
		\center
		\begin{subfigure}[b]{.33\textwidth}%
		\includegraphics[width=\textwidth]{Ex1a.pdf}
		\caption{EVs $1$ and $2$ arrive at $t=1$.}%
		\label{fig:Ex1a}%
		\end{subfigure}
		\hspace{8mm}
		\begin{subfigure}[b]{.33\textwidth}%
		\includegraphics[width=\textwidth]{Ex1b.pdf}
		\caption{EV $3$ arrives at $t=2$.}%
		\label{fig:Ex1b}
		\end{subfigure}		
		\caption{Worst case scenario when the scheduling algorithm is to re-run an optimal algorithm at each time slot considering only available EVs. Dotted line indicates a time slot that is not visited yet and the scheduler has no information about the arriving EVs in that slot. The numbers inside parentheses indicate arrival time, deadline, value, demand and maximum charging rate of the EV, respectively.}
		\label{fig:Ex1}
\end{figure*}

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 1.9:}\\
Page 5 line 21: Please explain the basic algorithm in [18] and how yours is different.
}}

\vspace{5mm}
\noindent\textbf{Response:}

The comment refers to reference [33] in the revised paper which studies the offline problem for integral revenue model in single station scenario. In [33], the authors developed an algorithm which uses the idea of sorting EVs based on their unit value and then select them to charge which is the same general idea we utilized in designing the \ics algorithm. The \ics algorithm extends the proposed algorithm in [33] in three different ways. \textbf{First}, method of [33] works only for single station scenario where there is no global peak constraint. \textbf{Second}, method of [33] works only when arrival times of EVs are the same. \textbf{Third}, we extended theoretical results in [33] and derive performance bounds for the \ics under multiple station scenario. We explained these differences in Section V-A1, Page 7, in the revised manuscript. Last but not the least, we compared the result of our algorithm with the proposed algorithm in [33] as reported in Fig. 3 of the manuscript in Page 9.
\\

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 1.10:}\\
(8a) What is alpha, gamma, beta, pi? How are they related to (1a)-(1d)?
}}

\vspace{5mm}
\noindent\textbf{Response:}

Our solution approach for offline integral revenue model is to develop a primal-dual algorithm which requires formulating the dual problem to analyze the performance using weak duality property. 
Basically, in primal-dual approximation algorithm design, each constraint (resp. variable) in primal (resp. dual) problem is associated with a variable (resp. constraint) in dual (resp. primal) problem. In our case, constraints (1a)-(1d) are respectively associated with dual variables $\alpha, \beta, \gamma$ and $\pi$. For more details, we refer to Chapter 12 of ``Approximation Algorithms'' textbook by Vijay Vazirani, which is cited in our paper as reference [16]. We added a short explanation before formulating the dual problem in Page 6 of the paper. 
\\

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 1.11:}\\
Page 5 line 30: How is the feasibility checked?
}}

\vspace{5mm}
\noindent\textbf{Response:}

The comment refers to feasibility check of allocating an EV in \ics algorithm (Section V-A-1, Page 7, Scheduling of the Selected EV). Since \ics is working under integral revenue model, each EV should receive all or nothing of its demand. Therefore, when \ics is trying to allocate an EV, it should first check that if there is enough remaining resource in availability window of the EV. This check is done in Line 6 of the \ics algorithm in Page 7 of the revised version. \rev{We also cited the corresponding algorithm line  when we used the term ``feasibility check'' in Page 7.} 
\\

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 1.12:}\\
The definition of m and n are very confusing. In the fractional model, the summations are used with n all the time, suggesting that every car will have a charging station. In the integral model (8a), m and n come in together without clear explanation what each term means. 
}}

\vspace{5mm}
\noindent\textbf{Response:}

Parameter $n$ is the total number of EVs (in the entire charging network) and $m$ is the number of charging stations as explained in Table I in Page 3. Each charging station (CS) is equipped with enough number of chargers to charge multiple EVs simultaneously as long as the peak constraint is respected. Moreover, $h(i)$ indicates the charging station of EV $i$ and is given to the problem as an input (i.e., we assume that EVs choose their charging stations). 
We further clarified the explanations in Table I and corresponding explanations in Sections III-A1 and III-A2, in Page 3.

The objective function in (8a) is in the form of $A+B+C$ with $A=\sum_{i=1}^n D_i\alpha _i, B=\sum_{j=1}^m \sum_{t=1}^T p_j\beta (t)$ and $C=\sum_{t=1}^T p^\mathsf{total}\gamma (t)$. 
The term $A$ is constructed according to Constraint (1a) in primal problem which applies the constraint for all $n$ EVs. Therefore, the summation index is $n$. The term $B$ is constructed according to Constraint (1c) which enforces the constraint for all charging stations and all time slots. Therefore, indexes in $B$ are $m$ and $T$ (number of time slots). Similarly, the term $C$ is constructed based on constraint (1b) which applies for all time slots and therefore the summation index in $C$ is $T$.

%Therefore, the studied scheduling problem does not include assignment of EVs to CSs as we assume that there is no communication between users and the scheduler before they arrive to a CS. With these assumptions (which represent a realistic scenario), some CSs might face high amount of power demand while there are few EVs in the other CSs. To handle this situation and achieve a high resource utilization in the charging network, we assumed that local peaks in each CS can be over-provisioned. We note that arriving an EV to a charging stations does not guarantee that it will get charged.

\vspace{3mm}
{\color{blue}In the case study, the CS number is set and the number of the cars is increased. It's unclear what the authors are doing here? Are all cars guaranteed a CS? If so, what's the point of number of CS? }

\vspace{3mm}
\noindent\textbf{Response:}

As explained in response to the previous comment, several EVs can get charged in each charging station. Given a fixed number of CSs, we can increase the number of EVs. In the simulation scenario, $n$ EVs randomly select their CSs in the ACN. Therefore, when $n$ increases, the density of EVs at each CS will be increased as well and the algorithms will face resource shortage. The goal is to evaluate the proposed algorithms when the demand-to-supply ratio increases.
%We added a phrase to the simulation setup to clarify this.

\vspace{3mm}
{\color{blue}If CS defines the bottleneck of maximum vehicle charging at the same time, what are the other cars doing? Waiting? But in Fig. 2 and 3, the revenue with different number of CS (and quite small compared to 100 cars) are almost the same. Nothing is explained clearly.}

\vspace{3mm}
\noindent\textbf{Response:}

We thank the reviewer for pointing this issue. Fig. 2 and Fig. 3 are combined in the revised paper due to space limit.

We highlight two points here. First, in our system model, if the CS cannot charge all EVs in the station simultaneously according to the peak constraints, some EVs should wait. When EV $i$ is waiting, we have $y_{i,t}=0$. However, the scheduler can switch between different subset of EVs for charging. Particularly, preemption is allowed with no cost i.e., the scheduler can pause charging of an EV and resume it later.

Second, since both local and global peak constraints must be respected by the scheduling algorithms, adding more charging stations (with known local peak constraints) may not lead to a revenue improvement if the global peak constraint is not increased accordingly. %Therefore, to increase the revenue of the ACN, increasing the number of CSs is not enough if the global peak constraint is fixed and acts as the bottleneck. 
This is the main reason that the revenue of the algorithms do not greatly improve by increasing number of CSs in Fig. 2 of the previous submission. In the revised paper, we updated our simulation setting and re-run all the scenarios. It can be observed from Fig. 2 of the revised paper that by increasing the number of CSs, the revenue also increases.

%This is the main reason that revenue in Fig. 2 and Fig. 3 is almost the same. To make the scenario meaningful, we re-run the simulation by choosing a higher value of global peak constraint and based on the new result, the total revenue increased as number of CSs increases.

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 1.13:}\\
Table III: The max charging rate for EVs are largely wrong. It's well known that a Tesla can charge up to 120kW with DC and CHAdeMO (Nissan Leaf)/J1772 Combo (BMW) can charge at 30kW/60kW.
}}

\vspace{5mm}
\noindent\textbf{Response:}

The charging rates we used in the first submission were not up-to-date according to the latest battery technologies. 
In light of this comment, we updated the rates by assuming that DC chargers are installed in the charging stations and the charging method is CHAdeMO which can give a charging rate up to 50 kW. We re-run all the simulations accordingly and  reported the new results. 
% kWh is a measure of energy while kW is a measure of power. That is to say, the unit should be kWh when we are talking of ``storage'' (e.g., battery capacity) while it should be kW when talking of charging/discharging ``rate''.

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 1.14:}\\
Page 7 line 39-41: The setup of the case study is very unclear. We don’t know how many cars are coming at what time, how long they stay and what energy they typical ask for. The revenue of the two cases are almost the same (up to ~10\% difference), which means that the resources in the case study are mostly enough for the demand. This might not be an interesting case especially for the integral revenue case. The author should investigate more deeply how the performance would be different when the supply is not enough (with more and more vehicles). 
}}

\vspace{5mm}
\noindent\textbf{Response:}

We thank the reviewer for pointing this issue.
We revised the simulation set up and made it clear how we set EVs' profile including their demand, deadline and valuation. For details, please see \emph{Simulation Setup and Overview} in Section VI, Page 8. Also, we set local and global peak constraints in our main simulation scenario in Fig. 2 of the paper (Section VI, Evaluation Based on Total Revenue) such that the algorithms face resource shortage. To show the level of the resource scarcity in the new setting, in Fig. 2 of this letter fraction of the fully charged EVs in different methods extracted from the simulation data of Fig. 2 in the paper. As it can be seen from Fig. \ref{fig:acc} in this letter,
even in optimal solution and for the case of having $8$ CSs, the percentage of the EVs who received their entire demand is less than $65\%$ which implies a high level of resource shortage. Due to space constraint, we do not report the results in Fig. \ref{fig:acc} in the manuscript.

We re-run all the simulations with the new setting and reported the results in the paper. Based on the new results in Fig. 2 of the paper in Page 9, we observe that when the number of CSs increases (specially from 2 to 4) by keeping the global peak constraint fixed, the revenue of the algorithms increases as well for all methods.

\begin{figure*}[t]	
				\centering
				\begin{subfigure}[b]{0.3\textwidth}
					\begin{center}
						\includegraphics[width=\textwidth]{acc-M2.pdf}
						\caption{$m=2$}
						\label{fig:acc-M2}
					\end{center}
				\end{subfigure}
				\begin{subfigure}[b]{0.3\textwidth}
					\begin{center}
						\includegraphics[width=\textwidth]{acc-M4.pdf}
						\caption{$m=4$}
						\label{fig:acc-M4}
					\end{center}
				\end{subfigure}% 	
				\begin{subfigure}[b]{0.3\textwidth}
					\begin{center}
						\includegraphics[width=\textwidth]{acc-M8.pdf}
						\caption{$m=8$}
						\label{fig:acc-M8}
					\end{center}
				\end{subfigure}% 
				\caption{Fraction of full charged EVs in different methods.} 
				\label{fig:acc}
				\vspace{-3mm}
			\end{figure*}

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 1.15:}\\
Fig 2, 3: With more and more vehicles, both scenarios should show a converged non-linear revenue curve, with the integral revenue converging more pre-maturely. But the shown result is simply linear, again showing that the capacity is not saturated and the case study is ill set-up.
}}

\vspace{5mm}
\noindent\textbf{Response:}

We agree with the reviewer that after some point and when number of EVs is large compared to the available resources, increasing the number of EVs should not change the total revenue obtained by the algorithms mainly because the newly added EVs cannot make a difference in solution of the algorithms. In our new simulations, this can be seen in Fig. 2a in the revised version where the revenue of the different algorithms only slightly change when number of EVs is increasing from 200 to 250. This is not the case in Fig. 2b and Fig. 2c of the paper. However, it is not because the capacity is not saturated as the reported results in Fig. \ref{fig:acc} of this letter shows that there is a great amount of resource shortage. We believe that the reason lies behind the heterogeneity of EVs' unit value. When increasing number of EVs, until some point, the algorithms are able to improve their selected EVs for charge by relying on EVs with higher unit values \emph{while probably leaving a large portion of EVs un-allocated.} Therefore, the fact that the revenue is linearly increasing in Fig. 2b and Fig. 2c of the paper with the number of EVs does not imply that the capacity is not saturated. 
We believe that if we increase number of EVs in a highly dense scenarios, the revenue of the algorithms will only change slightly with different number of EVs. \rev{To investigate this, we re-run the scenario of Fig. 2 of the revised manuscript while the number of EVs is increased from 400 to 500 instead of 100 to 250 and plotted the results in Fig. \ref{fig:V-NN} in this letter. Based on the results, there is no significant improvement in highly dense scenarios which confirms our argument.} However, this result confirms a simple fact and does not address our simulation goal in Fig. 2 of the paper which is observing how the algorithms scale with the number of EVs.

\begin{figure*}[t]	
				\centering
				\begin{subfigure}[b]{0.3\textwidth}
					\begin{center}
						\includegraphics[width=\textwidth]{V-NN2.pdf}
						\caption{$m=2$}
						\label{fig:V-NN2}
					\end{center}
				\end{subfigure}
				\begin{subfigure}[b]{0.3\textwidth}
					\begin{center}
						\includegraphics[width=\textwidth]{V-NN4.pdf}
						\caption{$m=4$}
						\label{fig:V-NN4}
					\end{center}
				\end{subfigure}% 
				\caption{Investigating the impact of increasing number of EVs in highly dense scenarios.} 
				\label{fig:V-NN}	
			\end{figure*}

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 1.16:}\\
How the valuation is generated for each user in the case study is not explained.
}}

\vspace{5mm}
\noindent\textbf{Response:}

We thank the reviewer for pointing this issue. The unit value of each EV in the simulation is randomly and uniformly selected from interval $[\frac{1}{2}z,\frac{3}{2}z]$ where $z$ is average price for 1 kWh of power in the US. We added this explanation to simulation setup in Section VI.

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 1.17:}\\
The author should consider customer’s satisfaction in the optimization. User’s demand is only used to determine whether it’s feasible, rather than giving their priorities. It would seem too brutal to reject/rank users solely by how much they try to pay.
}}

\vspace{5mm}
\noindent\textbf{Response:}

The variable $v_i$ provides us with enough flexibility to handle such scenarios. 
Let's assume that the overall satisfaction of a user is determined using a function $f(.)$ of multiple parameters (e.g., their payment, priority, etc) where the output of $f(.)$ for profile of user $i$ is $v_i$. Then, our formulated optimization problem turns into maximizing the overall satisfaction of the users while there is no modification required in the proposed algorithms.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Reviewer $\# 2$}
{\color{blue}}
%
%\vspace{4mm}
%{\color{blue}\noindent\\
%We sincerely appreciate you for taking the time to review
%our paper. Following the concerns and suggestions, the paper
%has carefully been revised to address the reviewer's comments
%properly.
%}

%We sincerely appreciate you for taking the time to review our paper. Following the
%concerns and suggestions, the paper has carefully been revised to address the reviewer's
%comments properly.

{\color{blue}This paper considers a EV charging problem with both local and global maximum charging rates. Considering both fractional and integer charging control problems, this paper proposed a offline and an online algorithm for each problem.}

\subsection{Comments}

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 2.1:}\\
The paper intends to include four algorithms in one paper under strict 8-page limit. As a result, even important literature reviews on online algorithm design are moved to the appendix, which is not a common practice and in fact a bad way to present the paper to the audience. The offline algorithm for the fractional case is not described at all in the paper, but referring to an online report. As a result, the paper is not self-contained in its current form.
}}

\vspace{5mm}
\noindent\textbf{Response:}

In the revised manuscript, we complied a 10-page manuscript by reorganizing the paper and adding several important contents to the main body of the paper to make it self-contained. In particular, we added the \rev{Related Works section} and optimal offline algorithm from our technical report to the revised manuscript, with detailed explanations, hence in the revised version there is no more algorithms cited from other references. The details of this algorithm is in Section IV-A, Pages 4-5 of the revised manuscript. 
\\

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 2.2:}\\
Compared to the existing solution without the global constraint, that is the new challenge in the design? Does this greatly impact the algorithm design.
}}

\vspace{5mm}
\noindent\textbf{Response:}

Without the global peak constraint, the problem degenerates to multiple single-station sub-problems, each with a local peak constraint. In this scenario, the global optimal solution can be obtained by solving sub-problems separately.

In the presence of a global peak constraint where the aggregate capacity constraint of charging stations is greater than the global peak constraint, the optimal solutions of the sub-problems may not be feasible for the global problem. This is because the aggregate demand obtained by optimal local solutions may go beyond the maximum tolerable capacity of the adaptive charging network. Consequently, the problem must be solved globally, by taking into account both local and global peak constraints. 
It is worth to note that this two-level capacity constraint architecture comes from the practical systems. Our motivation in this paper is from Caltech Adaptive Charging Network, where the ACN operator might limit the total power drawn from EVs (which is essentially the global peak constraint) to control costs, reserve the capacity for other loads, and/or participate in demand-response events.

In terms of algorithm design, the general ideas of sorting and selecting the most valuable sources are still the same as the case without the global peak constraints, however, there are several details in both algorithm design and competitive and approximation analysis where we do required specific design tailored for the case with global peak constraints. In the following, we mention some of the technical challenges by adding global peak constraints:
\begin{itemize}
	\item Additional steps in constructing dual  problem (as appeared in the the third term in the objective function of dual problem in Equation (9a) in Page 6 of the revised manuscript). This leads to additional challenges in weak-duality analysis in primal-dual framework. 
	\item More sophisticated scheduling rules in algorithms design to ensure respecting the global peak constraints (e.g., Line 4 of Algorithm 2, Line 4 of Algorithm 4, etc.). 
\end{itemize}
Last but not the least, we note that our competitive analysis in Section IV-B is entirely novel and to the best of our knowledge is not used in any previous work.

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 2.3:}\\
We can clearly see in the formulation (1) that the EVs have different charging price $v_i/D_i$. From the system operator's perspective, why serving different users at different prices, is this reasonable and practical in commercial system? or it is just an extension from the Knapsack problem.
}}

\vspace{5mm}
\noindent\textbf{Response:}

This is a constructive comment that also raised by the Reviewer 1 in Comment 1.2. For detailed explanation we refer to our response to Comment 1.2. However, in the following we provide a short response as well.

In this study, we consider the scenario in which the aggregate EV charging demands are beyond the local and global peak constraints of the adaptive charging network.  In this resource-limited scenario, it is rationale to solve a social welfare maximization problem with the goal of maximizing the aggregate \textit{utility} (in simplified case, \textit{valuation}, as we considered in our paper) of the users, i.e., EVs, in the system.

In the current scenarios, the aggregate demand is usually lower than the local and global peak constraints,  hence, the charging model pointed by the reviewer makes sense. This flat charging model, however, is not sustainable in the scenarios in which the peak constraints hinders fulfilling the entire demand of the users. As advocated in our study (and several other studies in EV charging scheduling or in broader way in general utility maximization resource allocation problems such as [8], [11], [33] in the revised manuscript), a natural way is to let EVs to announce their willingness to pay and try to propose scheduling mechanisms that maximizes the aggregate valuation subject to the capacity constraints.

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 2.4:}\\
The generalized Knapsack problem must have off-the-shelf efficient approximate methods, the authors should consider comparing the proposed method with them. For the fractional one, what is the advantages of the proposed off-line method compared to general method to solve LP, e.g., interior point method.
}}

\vspace{5mm}
\noindent\textbf{Response:}

First we emphasize that the formulated problem in this study is a time-expanded online version of original knapsack problem, which is more complicated than the basic knapsack problem. Consequently, applying the off-the-shelf approximation methods for knapsack problem may not be possible or may produce unsatisfactory results. Second, in simulations, we compared the results of our proposed online and offline algorithms against optimal solutions where the optimal solution is obtained using Gurobi (reference [38] in the revised paper) as a generic off-the-shelf solver to solve mixed integer linear problems.

The advantages of the proposed offline algorithm against general methods to solve LPs are (i) it comes with lower computational complexity, and more importantly (ii) it provides insights in designing online algorithm for fractional case, and offline and online algorithms for integral case; and finally, (iii) it leverages a valley-filling policy to further reduce the peak by distributing the demand over time smoothly.

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 2.5:}\\
What is the point of Fig. 4 if considering only a single charging station where the global peak constraint is absent (the main contribution of this paper)?
}}

\vspace{5mm}
\noindent\textbf{Response:}

Fig. 4 is now Fig. 3 in the revised version as we combined figures to save space.
The goal here is to compare our method to existing works (in particular, GreedyRTL algorithm in reference [33] in the revised paper), and show that even in the absence of the global peak, our algorithms work better than the existing works. Since the GreedyRTL works only in single station scenario (so local and global peaks are the same), we set the number of charging stations to one and assumed that there is no global peak constraint. The result is that not only our designed \ics algorithm slightly improves the GreedyRTL in terms of the revenue, but also greatly reduces the actual peak of the charging station through its valley-filling technique.

\begin{figure*}[t]
	\center
	\begin{subfigure}[b]{.33\textwidth}%
		\includegraphics[width=\textwidth]{Ex2a.pdf}
		\caption{Jobs $1$ and $2$ arrive at $t=1$.}%
		\label{fig:Ex2a}%
	\end{subfigure}
	\hspace{8mm}
	\begin{subfigure}[b]{.33\textwidth}%
		\includegraphics[width=\textwidth]{Ex2b.pdf}
		\caption{No EV arrives at $t=2$.}%
		\label{fig:Ex2b}
	\end{subfigure}		
	\caption{Worst case scenario for the \focs algorithm. Dotted line indicates a time slot that is not visited yet and the scheduler has no information about the arriving EVs in that slot. The numbers inside parentheses indicate arrival time, deadline, value, demand and maximum charging rate of the EV, respectively.}
	\label{fig:Ex2}
\end{figure*}

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 2.6:}\\
In Fig. 2, the proposed foCS performs worse than benchmark foLP, please explain. Besides, the benchmark methods should be briefly explained.
}}

\vspace{5mm}
\noindent\textbf{Response:}

This comment refers to simulation results in the previous version of the paper where the number of EVs is changed from 50 to 100 and revenue results for the algorithms are gathered.
According to the results, \focs performs worse in highly dense scenarios while performs well in low dense scenarios. In the revised manuscript, the simulation settings are fully changed according to Comment 1.14 of Reviewer \#1 to only consider highly dense scenarios which is where the performance of the \focs is below the \folp. We believe that one major reason for this performance issue is that the \focs is \emph{deadline-oblivious} i.e., it does not use the deadline information of the users in decision making. Therefore, in the revised manuscript we made a small but effective modification into the algorithm to make it \emph{deadline-aware} as follows: when algorithm sorts the EVs based on their unit values, if two EVs have the same unit value, then the one with earliest deadline comes first in the sorted list (See Algorithm 2 Lin 2 and the highlighted text in Section IV-B in Page 5). The new simulation results (Fig. 2 in the revised version) show the effectiveness of this method such that the performance of the \focs is now similar or slightly better than the \folp in all cases.

We also explained the fOLP algorithm in simulation setting in Section VI, Page 9.

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 2.7:}\\
For the competitive analysis, can the authors explain at what condition the worst case (is likely to) happen? Now the 2-competitive result is not surprising and provides little insight.
}}

\vspace{5mm}
\noindent\textbf{Response:}

Fig. \ref{fig:Ex2} in this letter shows the worst case scenario for the \focs algorithm where there is only one charging station with $p_1=p^\text{total}=1$. If we run \focs over the scenario of Fig. \ref{fig:Ex2}, the algorithm will select EV 1 at time slot 1 because its unit value is higher. Then, if no EV arrives at time slot $2$, the total revenue of the algorithm will be $1+\epsilon$ while the optimal solution is to allocate EV 2 at $t=1$ and EV 1 at $t=2$ which makes the total revenue 2. Since we can set the $\epsilon$ to an arbitrarily small value, the competitive ratio is $2$.

We emphasize that this is a theoretical analysis that characterizes the performance of our algorithm in worst-case scenarios. Our simulations results show that in reality the result of our algorithm is much better than worst-case analytical results.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\section{Reviewer $\# 3$}
{\color{blue}}
%
%\vspace{4mm}
%{\color{blue}\noindent\\
%We sincerely appreciate you for taking the time to review
%our paper. Following the concerns and suggestions, the paper
%has carefully been revised to address the reviewer's comments
%properly.
%}

{\color{blue}The authors of the paper, "Online ev scheduling algorithms for adaptive charging networks with global peak constraints", proposed online scheduling approaches of electric vehicles considering the peak constraints in the multi-layer charging networks, and integers constraints of the decision variables. This paper presents interesting research ideas of approximating the MILP problem with bounds. However, the reviewer has the following concerns that need to be addressed:}

\subsection{Comments}
%We sincerely appreciate you for taking the time to review our paper. Following the
%concerns and suggestions, the paper has carefully been revised to address the reviewer's
%comments properly.

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 3.1:}\\
Most of the previous optimization-based EV scheduling algorithms, the demand is treated as a constraint, i.e. the charging system has to deliver the demand before the vehicle leaves. In this paper, this constraint does not have to be satisfied. Please provide justifications. In addition, the scenario with the peak constraints from system operators also needs to be justified. It's better to associate the problem setting with real-world markets. For instance, in California, TOU pricing with energy charge and demand charge (cost applied to monthly global peaks) can be integrated. A sample paper minimizing demand charges instead of modeling it as an imaginative constraint can be found:
J. Jin and Y. Xu, "Optimal Storage Operation Under Demand Charge," in IEEE Transactions on Power Systems, vol. 32, no. 1, pp. 795-808, Jan. 2017.
}}

\vspace{5mm}
\noindent\textbf{Response:}

Thanks for this constructive comment. We justified our particular scenario as compared to the scenarios with demand as a constraint in the second paragraph of the Introduction (see highlighted section in the revised paper). As pointed by the reviewer the scenarios with demand as a constraints accounts for the low-load regimes where there is no limit on the resources (capacity of the charging networks). This scenario mainly captures the current EV charging scheduling models, where the number of EVs are not too large.

In contrast, our study tackles the high-load regimes which is motivated by the rapid proliferation of EV usage as supported by providing some stats regarding global EV usage in the first paragraph of the Introduction. In high-load regime, the aggregate EV demands are beyond the capacity of charging network (due to physical limitations of transformers or several other issues enforced by station operator. Please see Section I, third paragraph, the last sentence as highlighted). This argument also justifies the peak constraints from system operators as well.

Associating the problem to the real-world electricity market is a very fascinating future research direction, where the charging station operator can participate in market and buy the electricity demand of EVs directly from the market using TOU pricing model. Our preliminarily investigation shows that the underlying optimization problem is fundamentally different than our focus in this work and we plan to tackle this scenario as a future study. Last, we appreciate the provided reference by the reviewer and mentioned this future direction in our related work section, with citing the suggested paper. For details, please see Section II, Page 2, last paragraph.   And also the last sentence in Conclusion.

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 3.2:}\\
In the charging network, what standards are these charging stations complying with? Are they level I, Level II, or DC fast chargers? The charging power usually depends on the chargers instead of the vehicle types. Thus, the max charging rates in table III are not valid. If they are level II with SAE J1772 protocol, there is another constraint that the power cannot be controlled continuously, i.e the controllable power range is {0} U [1.5 6.6kW]. Thus, another integer is needed to model this property.
}}

\vspace{5mm}
\noindent\textbf{Response:}

In the revised manuscript, we changed the simulation setting according to this comment and re-run all the simulations. In the new setting, the charging speed of the EVs depends on the installed DC chargers in the stations. It is assumed that the chargers use CHAdeMO charging method and can provide a charging rate up to 50 kW. Moreover, regarding controlling the charging rates, we assumed in the paper that the charging rate of an EV is fixed during a time slot, which is a common assumption in time slot-based system models in EV (or job) scheduling domain (e.g., see [8], [11], [33] in the revised manuscript).  Therefore, charging rates do not change too frequently but only in the beginning of each time slot. It is worth to note that in our algorithm design, most of the times the charging rates are set to the maximum values, in this way, we do not expect too much fluctuations in charging scheduling of each EV.

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 3.3:}\\
 Following the modeling in this paper, it seems the uncertainties of future arrival vehicles are not modeled. A similar charging station with multiple outlets can be found in:
B. Wang, Y. Wang, H. Nazaripouya, C. Qiu, C. C. Chu and R. Gadh, "Predictive Scheduling Framework for Electric Vehicles With Uncertainties of User Behaviors," in IEEE Internet of Things Journal, vol. 4, no. 1, pp. 52-63, Feb. 2017.
Bin Wang et al., "Predictive scheduling for Electric Vehicles considering uncertainty of load and user behaviors," 2016 IEEE/PES Transmission and Distribution Conference and Exposition (T\&D), Dallas, TX, 2016, pp. 1-5.
But impact of future demands from EVs is significant and needs proper treatment. So please justify the advantages of not modeling these uncertainties. In addition, there are MPC based approaches to handling these uncertainties:
N. Chen, L. Gan, S. H. Low, and A. Wierman, "Distributional analysis for model predictive deferrable load control," in 2014 IEEE 53rd Annual Conference on Decision and Control (CDC), 2014, pp. 6433-6438
}}

\vspace{5mm}
\noindent\textbf{Response:}

In Related Work (Page 2 of the revised manuscript), we added a paragraph to compare our approach and prediction-based approaches. We have mentioned that the prediction-based approaches achieve satisfactory performance for the scenarios that follow prediction. Deviation from prediction models, however, degrades their performance. Our approach, on the other hand, has no assumptions on modeling/prediction, and in this way, is robust against any uncertainty in the instances to the problem.

On top of the above argument we would like to further highlight that in several cases, studies that apply prediction-based approaches usually rely on unrealistic assumptions which may not reflect real world scenarios accurately. 
Our algorithms are very simple and easy to implement. And as supported by the trace-driven experiments, the proposed algorithms can achieve satisfactory performance as compared to the optimal solutions, where all the uncertain inputs are given in advance. 
\\

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 3.4:}\\
What is computational complexity of the MILP problem in this paper? Please provide more info about the experiments, e.g. memory size, number of cores, etc. There are emerging parallel algorithms to handle binary/integer variables in MILP problem using multi-core computers. The reviewer is wondering why the problem cannot be solved by existing parallel solutions with multi-core computers and what the advantages of the proposed approaches in this paper.
}}

\vspace{5mm}
\noindent\textbf{Response:}

The underlying MILP problem is an NP-hard problem since it is a time expanded version of integer knapsack problem, so, it is computationally infeasible to solve optimally. 
Our proposed algorithms, however, are ``sub-optimal'' approximate or competitive algorithms with performance guarantees against optimum (see Theorems 3, 4, and 5). We analyzed the computational complexities of our algorithms and the summary of them is listed in Table II. In short, all of them are polynomial algorithms that could be implemented fast.

We would like to emphasize that we study ``online scenarios'' for the LP and MILP problems in the paper, and since the input to the problems are not available fully in advance, we cannot solve them by the commercial solvers. Consequently, the main challenge here is not the computational complexity of the algorithm, but the efficiency of the algorithm in the absence of future demands.

%Thanks for this useful comment.

%We thank the reviewer for pointing this out.

%Thanks for suggesting this point.

%We acknowledge the reviewer for suggesting this point. We agree that the

%We sincerely appreciate you for taking the time to review our paper. Following the concerns and suggestions, the paper has carefully been revised to address the reviewer's comments properly. We also tried to briefly reflect all the clarifications in the revised 4-page manuscript.

%Thanks. We agree that .....

%We agree that ....

%We thank the reviewer for pointing this out.

%Thanks for highlighting this point.

%We thank the reviewer for pointing this precious comment.

%Thanks for pointing this issue.

%We thank the reviewer for suggesting this point.

%\begin{itemize}
%\item[[A7]] D. G. Luenberger, Optimization by Vector Space Methods, John Wiley and Sons, Inc., New York, 1969.   
%\end{itemize}

%\vspace{5mm}
%\noindent\textbf{Response:}\\
%Thanks. We believe that the response to this comment is given within our response to Comment 3.11 above.

%\item In TCOMMIT, Lines 6-8 of SetGamma should be replaced

\bibliography{ref-response}{}
\vspace{-3mm}
\bibliographystyle{ieeetr}

\end{document}

6741 460 573 918

### 2019-08-25 TSC/R1/TSC.tex
adding more responses

\documentclass[journal]{IEEEtran}
%\usepackage{float}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{amssymb,amsmath}
\usepackage[font=small,skip=10pt]{caption}
\usepackage{subcaption}
\usepackage{comment}
\usepackage{color,soul}
%\usepackage{ragged2e} 
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{amsthm}
\usepackage{cite}
\usepackage{array}
%\usepackage{nopageno}
\usepackage{url}
%\usepackage{hyperref}
%\usepackage{ulem}

% *** CITATION PACKAGES ***
%
\usepackage{cite}
\usepackage{color}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{hhline}
%\usepackage[pdftex]{graphicx}

% *** GRAPHICS RELATED PACKAGES1 ***
%

% more space
%\usepackage{txfonts}
\addtolength{\abovedisplayskip}{-2mm}
\addtolength{\belowdisplayskip}{-2mm}
\addtolength{\parskip}{-.15mm}
%\addtolength{\arraycolsep}{-.75mm}
\addtolength{\abovecaptionskip}{-1mm}
\addtolength{\belowcaptionskip}{-1mm}
%\renewcommand{\baselinestretch}{0.9}

\ifCLASSINFOpdf
\usepackage[pdftex]{graphicx}
\graphicspath{{fig/}{../}}
\DeclareGraphicsExtensions{.pdf,.jpeg,.png,.jpg}
\else
\usepackage[dvips]{graphicx}
\graphicspath{{fig/}{../}}
\DeclareGraphicsExtensions{.eps}
\fi

%\usepackage[caption=false,font=footnotesize]{subfig}
%
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
%\setlength{\intextsep}{-1ex} % remove extra space above and below in-line float

\renewcommand{\baselinestretch}{1}

\ifodd 1
\newcommand{\bt}[1]{{\color{blue}#1}}%revise of the text
\newcommand{\rev}[1]{{\color{black}#1}}%revise of the text
\newcommand{\revv}[1]{{\color{black}#1}}%revise of the text
\newcommand{\com}[1]{\textbf{\color{red}(COMMENT: #1)}}%comment of the text
\else
\newcommand{\bt}[1]{#1}
\newcommand{\rev}[1]{#1}
\newcommand{\com}[1]{}
\fi

\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

%\newcommand{\opt}{\textsc{OPT}\xspace}
\newcommand{\sa}{\textsc{SmartAllocate}}
\newcommand{\rc}{\textsc{ReConsider}}
\newcommand{\bc}{\textsc{BetaCover}}
\newcommand{\ics}{\textsc{iCS}\xspace}
\newcommand{\fcs}{\textsc{fCS}\xspace}
\newcommand{\MCSP}{\textsf{SPAN}\xspace}
\newcommand{\dMCSP}{\textsf{dSPAN}\xspace}
\newcommand{\focs}{\textsc{foCS}\xspace}
\newcommand{\iocs}{\textsc{ioCS}\xspace}
\newcommand{\finalalg}{\textsc{ioCS+}\xspace}
\newcommand{\opt}{\textsc{OPT}\xspace}
\newcommand{\alg}{\textsc{ALG}\xspace}
\newcommand{\rtl}{\textsc{GreedyRTL}\xspace}
\newcommand{\iolp}{\textsc{ioLP}\xspace}
\newcommand{\folp}{\textsc{foLP}\xspace}

\newcommand{\be}{\begin{equation}}
	\newcommand{\ee}{\end{equation}}
\newcommand{\bee}{\begin{eqnarray}}
	\newcommand{\eee}{\end{eqnarray}}
\newcommand{\bse}{\begin{subequations}}
	\newcommand{\ese}{\end{subequations}}
%\def\bee#1\eee{\begin{align}#1\end{align}}
\newcommand{\nnb}{\nonumber}

\newtheorem{lem}{Lemma}
\newtheorem{propos}{Proposition}
\newtheorem{thm}{Theorem}
\newtheorem{defi}{Definition}

%in terms of practical feasibility and characterizing the maximum benefits of D2D load balancing is
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}

\makeatletter
\newcommand\semiHuge{\@setfontsize\semiHuge{22.52}{27.38}}
\makeatother
\begin{document}
	%\semiHuge
	\title{Online EV Scheduling Algorithms for Adaptive Charging Networks with Global Peak Constraints}
	\author{\#}

	\author{Bahram Alinia, Mohammad H. Hajiesmaili, Zachary J. Lee, Noel Crespi, and Enrique Mallada

		\thanks{ B. Alinia and N. Crespi are with the department of Networks and Mobile Multimedia Services (RS2M), Institut Mines-Telecom,
			Telecom SudParis, Evry, France (e-mail: bahram.alinia@telecom-sudparis.eu, noel.crespi@mines-telecom.fr).

			M. H. Hajiesmaili and E. Mallada are with the Department of Electrical and Computer Engineering, Johns Hopkins University, Baltimore, MD, USA (e-mail: \{hajiesmaili,mallada\}@jhu.edu).

			Z. J. Lee is with the Department of Electrical Engineering, California Institute of Technology, Pasadena, CA, USA (e-mail: zlee@caltech.edu).
		} }

		\maketitle

\begin{abstract}
%			With the rapid growth of electric vehicles, their high demand charging jobs pose an immense challenge to the grid infrastructure. 
			This paper tackles online scheduling of electric vehicles (EVs) in an adaptive charging network (ACN) with local and global peak constraints. Given the aggregate charging demand of the EVs and the peak constraints of the ACN, it might be infeasible to fully charge all the EVs according to their charging demand. Two alternatives in such resource-limited scenarios are to maximize the social welfare by partially charging the EVs (fractional model) or selecting a subset of  EVs and fully charge them (integral model). 
%			This paper tackles both fractional and integral models. 
			The critical challenge is the need for online solution design since in practical scenario\revv{s} the scheduler has no information of future arrivals of EVs in a time-coupled underlying problem. 
			For the fractional model, we devise both offline and online algorithms. We prove that the offline algorithm is optimal. Using competitive ratio as the performance measure, we prove the online algorithm achieves a competitive ratio of 2. The integral model, however, is more challenging since the underlying problem is NP-hard due to 0/1 selection criteria of EVs. Hence, efficient solution design is challenging even in offline setting. We devise a low-complexity primal-dual scheduling algorithm that achieves a bounded approximation ratio. Built upon the offline approximate algorithm, we propose an online algorithm and analyze its competitive ratio in special cases. Extensive trace-driven experimental results show that the performance of the proposed online algorithms is close to the offline optimum, and outperform the existing solutions. 
%			\rev{In particular, the grid and electricity providers should be aware of the electricity peak.	It is known in electricity market that the spot price is a dominating factor in billing cost. Hence, the utility companies need to identify a global peak constraint for the cost management purpose. This paper studies the online EV charging scheduling problem in a utility that offers EV charging service in a set of CSs, each of which having limited output power (referred to as local peak constraint) while taking into account the global peak constraint. The scheduling problem in this scenario comes with unique challenges that is not tackled previously.}

%			\rev{The problem objective is to maximize total revenue of the CSs.}

\end{abstract}
		\begin{IEEEkeywords}
			Electric Vehicle, Online Scheduling, Approximation Algorithm, Competitive Analysis
		\end{IEEEkeywords}

		\section{Introduction}
\label{sec:intro}	
%		\IEEEPARstart{A}{s} 
%		a result of global warming and environmental concerns through dependence on fossil fuels, there has been a rapid proliferation in deploying renewable energy sources. 
\IEEEPARstart{T}{o} promote quick adoption of renewable energy sources, electrification of vehicles is a trend that has been globally advocated in recent years. \rev{According to a Bloomberg report, EVs will account for more than half of the new car sales by $2040$~\cite{bloomberg}. 		
	%the global sale of EVs increased by $80\%$ in $2015$~\cite{EVSales}.
	%		With the significant advantage of electric vehicles (EVs) in being an environment friendly product, the global interest for EVs is rapidly growing, such that  
	Consequently, it is expected that demand from EV charging will constitute a considerable portion of total demand. 
	Currently, transportation consumes $29\%$ of total energy in the US, while electricity production consumes $40\%$~\cite{Zhao}.} 
%Vehicles seen accounting for 5\% of electricity use by $2040$~\cite{EVSales2}}
%%%\revv{\sout{Hence, rapid electrification of the vehicles makes the total electricity demand of EVs significant.}}

\revv{EV charging demand is a typical example of a deferrable load, and there is often considerable flexibility in the charging schedule. This property makes the problem of EV charging scheduling  important and there is an extensive research along this direction in the literature (see the recent survey~\cite{mukherjee2015review}, and references therein). In most of the existing works, the EV charging demand is treated as a constraint to the problem in a low-load regime~\cite{Tang}.  Motivated by rapid proliferation of EVs, this work tackles the EV scheduling in high-load regime, where given the aggregate charging demand of the EVs and the peak constraints of the charging network, it is not feasible to fully charge all the EVs according to their charging demand.}
%		\subsection{Microgrid: Definition, Potentials, and Challenges}
%		\label{sec:introA}
%		A common trend in the smart grid era is to install renewable energy sources in distributed manner. More specifically, medium or large commercial and industrial  customers such as universities, headquarters, etc.,  can take control of their own energy consumption by local deployment of renewable sources~\cite{Hajiesmaili2016Online}. In this setting, the residual demand, i.e., total demand subtracted by the local renewable supply, can be acquired from the external grid.

%		In addition to clean energy production, the owner of microgrid also enjoys more power sustainability and reliability, and the ability to proactively manage the energy costs.

More specifically, this paper studies resource-constrained EV charging scheduling in an adaptive charging network (ACN) governed by a single operator in a campus-scale location such as a university, a headquarter\rev{s}, etc. \cite{wu2017two}. 
\rev{A notable example is the Caltech ACN~\cite{lee2016adaptive} where individual charging ports are organized into several \textit{charging stations} (CSs) which are dispersed in a \textit{charging network}} with the capability of adaptive charging of the EVs. 
The problem is different from EV charging scheduling \revv{with capacity constraint} in single station scenarios~\cite{Tang,Wen,Shroff2014,WTang,Chen,Xiang,Zhao,Robu} (we refer to~Section~\ref{sec:rel} for detailed discussions on related work), because of the essential need to respect the aggregate peak demand of the ACN. \revv{Note that, the ACN operator might limit the total power drawn from EVs to control costs~\cite{PeakPrice,Zhang2015eEnergy}, reserve the capacity for other loads, and/or participate in demand-response programs.}
%		The EV charging loads are usually flexible and deferrable, which means that their load can be scheduled~\cite{moghaddam2017smart,DWang} to shape the total demand over time. 
%The aim of this paper is to use the deferrable property of EVs and schedule their charging jobs, so as to \rev{maximize the revenue of the ACN}.	
%		We refer to Section~\ref{sec:rel} for the literature review.

%		In particular, real-world pricing scheme for large customers is usually a hybrid time-of-use and peak-based charging model where the peak demand can significantly impact the total energy cost, e.g., the peak price is often more than $100$ times higher than the spot price~\cite{PeakPrice,Zhang2015eEnergy}. Considering total aggregate demand, the peak charge portion could be as large as $20\%-80\%$ of total cost~\cite{Xu2014Reducing}. Consequently, a substantial cost reduction could be achieved if the total peak-demand can be proactively controlled \cite{liao2015dispatch}.

%		\subsection{EV Charging Scheduling in the ACN}
%		With the proliferation of EVs, the charging requirement of the microgrid EVs could be a portion of total microgrid electricity demand.

%		To respond the electricity demand of EVs, CSs are being used where EVs can recourse to charge their battery \cite{He,liao2015dispatch,Tang}. There can be few to many CSs dispersed in an ACN, e.g., each for a parking garage of a building in a university campus. In this scenario, all parking stations are governed by a facility operator and a \textit{global} peak demand constraint is determined such that the aggregate charging demand in the entire network is less than this global peak demand \cite{DWang,Hoog}.

%		The charging scheduling of the EVs with the goal of respecting the \textit{global aggregate peak constraint}, however, is a unique problem which is different from the single station EV charging scheduling. Most of the existing work in the literature, tackle the problem in the single parking station scenario. We refer to Section~\ref{sec:rel} for in-depth discussion. As discussed in Section \ref{sec:problem}, the global optimal solution cannot be obtained by separately solving the single station problems. 
%		On the other hand, there are only a few studies that provide global optimal solution for charging scheduling of EVs \cite{He, Moradijoz, Malhotra,Zeng,Shaaban,DWang}. Despite elegant results, the underlying problems, e.g., charging cost minimization problem in \cite{He}, average operating cost minimization with optimal electricity exchange capacity problem in \cite{DWang}, optimal station capacity problem in~\cite{Moradijoz}, user convenience maximization problem in~\cite{Malhotra}, joint optimization of system profit and user experience in~\cite{Shaaban,Zeng} are different from the problem studied in this paper.

%		\subsection{Problem, Challenges, and Contributions}
We consider a scenario with multiple EVs where each EV has different charging profile in terms of availability, charging demand, charging rate limit, and valuation of getting charged \revv{(for details see Section~\ref{sec:ev})}. We formulate an online EV charging scheduling problem with the goal of \textit{selecting} and \textit{scheduling} a subset of EVs such that: (1) the charging demand of the selected EVs are (fully or partially) satisfied; (2) the charging rate limit of EV batteries are respected, (3) the global peak constraint of the ACN is satisfied~\cite{lee2016adaptive}; (4) the local peak constraint of each CS is respected;  and finally, (5) the total revenue obtained by the valuation of the EVs is maximized.

%		of maximizing the revenue of the ACN. The constraints are the \textit{local} peak constraint of each CS, and the \textit{global} peak constraint that limits the accumulative charging demand drawn from the entire network of stations (decided by the administration of the ACN to control total peak demand~\cite{lee2016adaptive}).

There are two main challenges in the design and implementation of scheduling algorithms for EVs satisfying the goals mentioned above. \rev{Firstly, the problem calls for online scheduling design.} In practice, EVs arrive to the CS in online fashion and the scheduler has no information about the arrival and demand of the future EVs. Secondly, the underlying optimization problem in integral model is NP-hard even in offline case \rev{(see Section~\ref{sec:integral})}. This is because the problem is a mixed integer linear problem and a ``time-expanded'' extension of knapsack problem which is known as a classic NP-hard problem. In this paper, we tackle the challenge of online design by following competitive algorithm design~\cite{borodin2005online} and the challenge of NP-hardness by pursuing approximation algorithm design~\cite{approx} and make the following contributions:

$\vartriangleright$ We first consider a \textit{fractional model} (where EVs can be charged partially and the revenue is proportional accordingly) and design an optimal offline scheduling algorithm. 
%In addition to provide efficient result, the algorithm has a further elegant step to apply a valley filling strategy to further reduce the peak demand of EV charging without degrading total revenue. 
We then develop an efficient online algorithm in which no exact or stochastic information about the future EV arrivals is given. Despite its simplicity, the algorithm is proved to be $2$-competitive with optimal offline solution, i.e., the revenue of the proposed online algorithm is at least $1/2$ of the offline optimum, regardless of input sequence. 
Even though there are competitive algorithms in the literature for similar problems, to the best of our knowledge, our algorithm is the first $2$-competitive algorithm \rev{which considers the} charging rate limits.

$\vartriangleright$ We next study \rev{the} more challenging scenario of \rev{the} \textit{integral model}\rev{, }where EVs must receive all their demand to make revenue. We first propose a polynomial-time primal-dual offline approximate algorithm. We analyze the approximation ratio of the algorithm and by strengthening the linear relaxed version of the mixed integer problem~\cite{Carr}, we obtain an approximation ratio of $\alpha =1+\sum_{j=1}^m {\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}$, where $p_j$ is local peak constraint in station $j$, $q_j$ is the maximum charging rate of the EVs in station $j$ and $s$ is a slackness parameter. We highlight that when $p_j \gg q_j$ and $s$ is \rev{large} enough, then $\alpha \approx m+1$, where $m$ is the number of stations in the ACN. Built on the basis of the offline algorithm, we devise an online algorithm, and discuss its competitive ratio in special cases. 
%In particular, the competitive ratio is $b\Big(1+\frac{p_j}{p_j-q_j}\cdot\frac{s}{s-1}\Big)$ for single station scenario, where $b$ is the number of batches with the same arrival time.

$\vartriangleright$ We conduct a set of  simulations to evaluate the performance of our proposed algorithms. 
%For offline scheduling problem under integral charging model, the results  demonstrate that the proposed approximation algorithm is close to the optimal solution and is significantly better than the obtained theoretical bounds. 
The results of online algorithms for both integral and fractional settings are close to the optimum (within $90\%$ and $94\%$ for integral and fractional models in a representative scenario). In addition, our algorithm outperforms the existing scheduling algorithm in Caltech ACN~\cite{lee2016adaptive} by $35\%$ for integral revenue model.
%The simulation section also discusses on the positive and negative effects of slackness parameter in different scenarios.

%To the best of our knowledge, this problem is not addressed yet in previous studies.

%		\subsection{Paper Organization}
%		The rest of this paper is organized as follows. Section~\ref{sec:rel} reviews the literature. In Section \ref{sec:model}, the system model  and problem formulation are described. 
%		Section \ref{sec:fractional} provides offline and online algorithms for fractional model. We study integral model in Section \ref{sec:integral} and propose online and offline algorithms. The simulation results are reported in Section~\ref{sec:simul}. Section~\ref{sec:conclusion} concludes the paper and highlights future directions.

\section{Related Work}
\label{sec:rel}
\revv{There is an extensive work in the general topic of EV demand management and scheduling~\cite{mukherjee2015review} by considering different scenarios such as optimal operations with EV coordinations~\cite{mukherjee2017distributed}, EV scheduling with incorporation of renewable energy, and energy storage systems~\cite{de2017impact,shafie2018innovative}. In this section, we focus on the literature related to peak-constrained EV charging scheduling in single and multiple stations.}
\subsubsection{Peak-Constrained EV Charging Scheduling}
\label{sec:rel:peakconstrained}			
\revv{There is an extensive literature on EV charging scheduling problem focusing on single CS~\cite{Tang,Wen}, while the local and global peak constraints are omitted or only the local peak is considered.}	As we discuss in Section~\ref{sec:problem}, the global optimal solution cannot be obtained by separately solving the single station problems. Hence, those solutions cannot be directly applied to the multiple CS scenario with global peak constraints.

%A scenario that local and global peak constraints exist is the case that scheduling is required for a charging network for multiple CSs. 
Studies in \cite{He,malhotra2017distributed,Moradijoz,DWang,Zeng,Shaaban} tackled charging scheduling problem in multiple CSs. The authors in~\cite{He} studied a global cost minimization EV charging scheduling problem. However, there is no limit on the maximum peak demand that the system can tolerate. Consequently, the peak can be arbitrary high and beyond the physical limit of the transformers in the charging station~\cite{lee2016adaptive} leading to huge electricity bills~\cite{Zhang2015eEnergy}. Besides, the charger devices installed in the CSs have limitation on the maximum power that they can transfer in each time unit~\cite{Tesla}. 
%We solve the issue by constraining local and global peaks. However, to meet the peak constraints, it may not be feasible to respond to all charging demands. Consequently, only a subset of EVs can be charged~\cite{Xiang}, which is captured in our problem formulation. 
\cite{DWang} considered a multi-microgrid system with global peak constraint where each microgrid has a CS and the goal is to manage electricity exchange between microgrids and main grid to minimize the operating costs. The authors assume that required information about individual EVs is available by forecast which may not represent a real scenario. A similar assumption is made in \cite{Zeng,Shaaban} where the objective is to maximize total utility of EVs and aggregators in a distribution network.
%\rev{To be removed: In our solution, we applied a priority based selection process (based on the EVs' valuation) to respond to the demands to make sure that total peak respects the constraints. The selection process can be made based on different criteria such as the value of each charging request \cite{Lee, Xiang} or the priority.}
%To avoid big billing cost in peak hours, \cite{Moradijoz} proposed a solution based on genetic algorithm to find optimal capacity and location of parking lots for serving demands in peak hours with the goal of maximizing total benefit of all stations. Although authors studied the problem under multiple CS setting, their solution is not applicable to our setting when the CSs are already set up. 
The authors in~\cite{malhotra2017distributed} use a similar model as in this paper, where both local and global peak constraints are considered. However, the authors solve the single-slot problem, which fails to provide a general solution taking into account EVs' arrival and departure times as considered in our study.
Finally, as an alternative approach to control the peak, some studies directly target minimizing the peak~\cite{Zhao, Karfopoulos}. In~\cite{Zhao}, an online algorithm is developed for EV charging to minimize the peak and \cite{Karfopoulos} proposed a valley filling method by leveraging V2G in peak hours. Although the peak is minimized in above works, it cannot guarantee that the minimized peak is tolerable by the underlying charging network.

\subsubsection{Scheduling Under Demand Uncertainty}
A main challenge in EV scheduling problem is to cope with demand uncertainty. Many studies including \cite{Shroff2014,Tang,WTang,Chen,Xiang,Zhao,Robu} addressed online scheduling problem with different objectives. \cite{Shroff2014,Xiang} studied the problem of maximizing social welfare considering the benefit for both users and service provider. \cite{Tang} and \cite{WTang} developed algorithms to minimize the charging price for the CS, where the proposed algorithm in \cite{Tang} is $2.39$-competitive. 
%An online algorithm developed in \cite{Chen} to optimize overall operating profit of the service provider. 
In \cite{Robu}, an online $2$-competitive algorithm is proposed for a single CS, assuming that EVs are capable of being discharged in a negligible amount of time. The assumption, however, is not realistic for EVs.

Our problem in this paper is unique from above works in many respects. First, we study the problem in an ACN where several CSs exist, while none of the above studies solve the problem under this setting. Second, the previous algorithms do not work for both integral and fractional charging models. In addition, \cite{WTang,Chen} put no limit on the charging rate of EVs which makes their solution impractical in real scenarios. Also, \cite{WTang,Tang, Shroff2014,Chen,Zhao} do not consider the peak limit of the CS. 
\revv{Note that some studies~\cite{jin2017optimal} tackle the scenarios of satisfying the large demands (possibly EV demands) by participating in electricity market. This study assumes that the electricity price is given and fixed, and leaves the case of real-time pricing as the future direction. In addition, there are studies that incorporate prediction in online EV charging scheduling~\cite{wang2017predictive,chen2014distributional}. The prediction-based approaches achieve satisfactory performance for the scenarios that follow prediction. Deviation from prediction models, however, degrades their performance. Our approach, on the other hand, has no assumptions on modeling/prediction, and in this way, is robust against any uncertainty in the instances to the problem.} 
\revv{Finally, in~\cite{Alinia2018ITS}, we considered a simplified EV charging scheduling in fractional model without global peak constraints and devised heuristic algorithms (without competitive and approximation analysis) with on-arrival commitment for EVs to notify the amount that they can receive by their departure. }
%In this paper, we consider these limitations and develop online and offline algorithms for fractional and integral revenue models in an ACN and provide theoretical bounds on their performance.

%It is important to note that there is a considerable similarity between EV scheduling problem and classical job scheduling problem \cite{}. However, most algorithm developed for job scheduling problem  do not consider a limit on processing rate of the jobs.

%\cite{Shroff2014} and \cite{Stein2012} study social welfare maximization problem while the profit of both EV owners and CS is considered.  social welfare of the EV owners \cite{Stein2012}, charging cost \cite{Tang,WTang}, and total value of fully charged EVs \cite{Azar}). In addition, \cite{WTang, Tang,Shroff2014,Zhao} do not take into account the peak limitation of CS. }
		\section{System Model and Problem Formulation}
		\label{sec:model}

		\subsection{System Model}
		We consider a time-slotted system model in which the time horizon is divided to $T$ equal length slots ${t=\{1, 2, \dots ,T\}}$ (e.g., $T=24$ with time slots of $1$ hour length).
\subsubsection{Charging Network}
\label{sec:acn}
Our charging network model is inspired by the Caltech ACN~\cite{lee2016adaptive} as illustrated in Fig.~\ref{fig:model-a}. In \rev{the} Caltech EV charging network (located in a parking garage), electricity is distributed through a two-level transformer architecture from a main switch panel to multiple EV switch panels (\rev{$2$} panels in the current Caltech ACN). Each EV switch panel then is connected to several chargers ($\approx$25 chargers \rev{per panel} in the Caltech ACN). The total power drawn from the main switch panel \rev{by} the charging network has a power limit of  $p^\mathsf{total}$, that is determined by the facility operator to control the costs, reserve the capacity for other loads, and/or participate in demand-response programs.  
%This power, where we refer to it as \emph{network power limit} is used for both EV charging as well as non-EV charging purposes (e.g., lighting, fans, etc \cite{lee2016adaptive}). 
In other words, $p^\mathsf{total}$, which we refer to it as the \textit{global peak}, hereafter, limits the maximum aggregate EV charging load at each time slot. 
%The global peak must be less than or equal to the value obtained by subtracting non-EV load from network power limit. 
%When we write \emph{global peak constraint}, it refers to $p^\mathsf{total}$.  
%$p^\mathsf{total}$ is the maximum allowed aggregated electricity consumption by all stations at each slot and limits the total transferable power to EVs.

We assume that there are $m$ EV switch panels that represent $m$ CSs. In addition to the global peak constraint, each CS $j$ has \rev{a} capacity constraint on \rev{its} total power drawn, indicated by $p_j$, and referred to it as the \emph{local peak} constraint. The \rev{value of} $p_j$ is determined by the output power limit of the transformers installed between the main switch panel and EV switch panels and could be different for each EV switch panel.  
%installed chargers in a CS have limited output power to charge EVs ~\cite{Wen,Xiang,Tesla}. Therefore, for CS $j$, $p_j$ cannot be more than sum of output power of its chargers. 
\rev{It is often observed that the charging demand of different CSs (EV switch panels in Fig.~\ref{fig:model-a}) are well below the local peak constraints.}
To increase the flexibility due to heterogeneous charging demand of CSs, in the Caltech ACN, the global peak constraint of the main switch can be \textit{over-provisioned}, i.e., $p^\mathsf{total}$ is less than the aggregate local peaks,  ($\sum_j p_j\geq p^\mathsf{total}$). \rev{While this increases flexibility, it also couples the problem of EV charging scheduling across different CSs.}
%Despite increased flexibility, the over-provisioning property, however, couples the problem of EV charging scheduling across different CSs. 
Our solutions in this paper will be centralized ones which can be obtained through communication between the CSs and a central server as illustrated in Fig. \ref{fig:model-b}.

%We make this clear by a simple example. Assume $m=2, p^\mathsf{total}=50$ kW and $p_1=p_2=25$ kW. In a specific time slot (e.g., $t=1$), the total demand in CS $1$ and $2$ is $40$ kWh and $10$ kWh, respectively. According to local peak constraints, it is not feasible to satisfy all demands in a single time slot. However, if we had $p_1=p2=50$ kW (e.g., by installing more chargers in the stations) we could be able to satisfy all demands by allocating $40 kW$ in $p_1$ and $10 kW$ in $p_2$ while still not violating $p^\mathsf{total}$. In case that $\sum_j p_j\leq p^\mathsf{total}$, the scheduling problem is not challenging and the solution can be obtained by solving the problem locally in each CS. If $\sum_j p_j> p^\mathsf{total}$ (which is the case we consider in this paper), a centralized solution is needed that can be obtained through communication between the CS and a central server as illustrated in Fig. \ref{fig:model-b}.

\begin{figure}	
\centering
\minipage{0.49\textwidth}
				\begin{subfigure}[b]{0.69\textwidth}
					\begin{center}
						\includegraphics[width=\textwidth]{model-a.pdf}
						\caption{Caltech adaptive charging network (ACN)}
						\label{fig:model-a}
					\end{center}
				\end{subfigure}%
				\begin{subfigure}[b]{0.29\textwidth}
					\begin{center}
						\includegraphics[width=\textwidth]{model-b.pdf}
						\caption{Communication model with server}
						\label{fig:model-b}
					\end{center}
				\end{subfigure}%  
\caption{System model \cite{lee2016adaptive}.} 
\label{fig:slackness1}
\endminipage
\end{figure}

		\begin{table} 
			\caption{Summary of key notations}\vspace{-3mm}
			\label{tbl:not}
			\begin{center}
				\begin{tabular}{|c L{6.5cm}|}
					\hline
					\textbf{Notation} & \textbf{Description} \\
					\hline \hline			
					$T$ & Number of time slots, indexed by $t$\\			
					$m$ & Number of CSs, indexed by $j$\\			
					$n$ & Number of EVs, indexed by $i$\\			
					\hline
					\hline
					$a_i$ & Arrival time of EV $i$\\
					$d_i$ & Departure time of EV $i$\\
					$D_i$ & Demand of EV $i$\\
					$v_i$ & Valuation of EV $i$ for receiving its demand $D_i$ \\
					$k_i$ & Maximum charging rate of EV $i$\\
					$h(i)$ & CS of EV $i$\\
					\hline
					\hline
					$q_j$ & Maximum $k_i$ among all EVs in CS $j$\\
					$p_j$ & Maximum aggregate charging rate in station $j$\\
					$p^\mathsf{total}$ & Maximum aggregate charging rate of all stations\\
					\hline
					\hline
					$y_i^t$ & \textbf{opt. variable}, The amount that EV $i$ is charged at $t$ \\
					\hline
				\end{tabular}
			\end{center}
		\end{table}
		\subsubsection{EVs}
		\label{sec:ev} There are $n$ EVs in the system, indexed by $i$.
		%, all available at time $t=1$ to be charged\footnote{This assumption is reasonable for the %official buildings where the starting hour of the working day is fixed for all the %employers. Extensions to the case with different arrival times for the EVs, is part of the %future work.}. 
		EV $i$ is represented by a charging profile $\langle a_i,d_i,v_i,D_i,k_i\rangle$ 
		indicating its arrival time, departure time, willingness to pay, charging demand, and maximum charging rate, respectively. 
		%(depends on physical properties of EVs battery) 
		More specifically, the charging of EV $i$ can be scheduled within its \emph{availability window}, $[a_i,d_i]$. The charging rate at each slot is bounded by $k_i$, a parameter that depends on the physical constraints of the \rev{battery and on-board charger}. It is assumed that the charging profile of each EV is feasible with respect to its maximum charging rate and a slackness parameter $s\geq 1$, which is the minimum ratio between the park time of the EV and its minimum charging time, i.e., ${D_i\leq k_i(d_i-a_i+1)/s}$. The slackness parameter is imposed to tune the flexibility of the charging scheduling. In extreme case $s=1$,  the flexibility is minimum and the flexibility improves as $s$ increases. 
%		Note  that  the slackness  parameter  can  impact  the  total  revenue  and  is  investigated  in  simulation  experiments  in Section~\ref{sec:simul}.
		We assume that EV owners select their CS, perhaps the nearest to them, and so the assignments are given to the problem. Define $h(i)$ as the CS of EV~$i$.
		Moreover, $q_j$ denotes the maximum $k_i$ among all EVs in CS $j$, i.e., $q_j=\max_{h(i)=j} k_i$. 
		\revv{Finally, $v_i$ is the willingness to pay of EV $i$ to receive its entire demand $D_i$ before the departure time $d_i$. Note that in resource-constrained EV scheduling in ACN, it is not feasible to fulfill the entire demand of all EVs, hence, the problem turns into a resource allocation one with the goal of maximizing the aggregate value (a.k.a. utility) obtained from the EVs. In this way, each user can announce its willingness to pay to get charged which is denoted by $v_i$ in the system model.}
		%We assume that there is no gain for the CS if EV $i$ is partially charged.

		% where $P$ defined as $P:\xi\rightarrow  \mathcal{P}$. 
\subsubsection{Revenue Models\label{sec:irm}} We consider two revenue models: 
\textit{(i) Fractional revenue model}: In this model, the fractional charging is allowed, i.e., the revenue from each EV is proportional to the fraction of the demand that is fulfilled \cite{Xiang} (see Eq.~\eqref{Eq:partial_value}). We tackle this model in Section~\ref{sec:fractional}.
\textit{(ii) Integral revenue model}: \rev{In this model, EV $i$ pays $v_i$ if it is fully charged and zero otherwise, i.e., there is no partial revenue for partial charging. }
%In this model, when EV $i$ is received its demand entirely, the gain is $v_{i}$ and zero, otherwise, i.e., there is no partial revenue for fractional charging. 
This is the model that is considered in~\cite{WTang,Shroff2014}. We tackle this model in Section~\ref{sec:integral}.

		%The actual aggregated peak of all parking stations must not exceeds global peak constraint.

			\begin{table*}[!t]
			\centering
	\vspace{-3mm}
			\caption{Proposed algorithms and their properties.}
			\label{tbl:algs}
			\begin{tabular}{ | l | c | c | c |c|}
				\hline
				\textbf{Algorithm} & \textbf{Revenue model} & \textbf{Type} & \textbf{Optimality} & \textbf{Complexity} \\ \hline\hline    
				\fcs& fractional& offline& Optimal & $O(n^2T+nT^2)$\\\hline 
				\ics& integral& offline& ${\Big( 1+\sum_{j=1}^m {\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}\Big)}$-approximate & $O(nT\log T+n^2T)$ \\\hline 
				\focs & fractional& online& $2$-competitive & $O(n^2T)$\\\hline 
				\iocs& integral&  online& $b(1+\frac{p}{p-q}.\frac{s}{s-1})$-competitive, $(m=1)$ & $O(n^2T)$\\\hline
			\end{tabular}
		\end{table*}

		\subsection{Problem Formulation}
		\label{sec:problem}
	We formulate an optimization problem to schedule the charging of the EVs with the objective of maximizing total revenue obtained from charged EVs while respecting local and global peak constraints. 
		Note that each revenue model makes the underlying optimization problem fundamentally different. More specifically, the fractional charging model is a linear problem. 
		Integral revenue model, however, turns the underlying charging scheduling problem to a Mixed Integer Linear Program (MILP). The integer nature originates from the $0/1$-selection decision on EVs. 
%%%Recall that in integral revenue model the revenue is obtained given that the entire demand is fulfilled for the selected EV. 
		%We skip the explicit formulation of the problem under integral revenue model since it could be contemplated as the linear-relaxed version of the integral revenue model (for more explanation, we refer to the discussions in Section~\ref{sec:fractional}).
		We formulate Scheduling Problem for Adaptive charging Network (\MCSP) under fractional revenue model as follows: 
		\bse
		\bee
		\MCSP: \max  && \sum\nolimits_{i=1}^n \frac{v_{i}}{D_i}\sum\nolimits_{t=a_i}^{d_i} y_i^t \label{Pobjec} \nonumber\\
		\text{s.t.} &&\sum\nolimits_{t=a_i}^{d_i} y_i^t\leq D_i,\quad\quad\forall i, \label{ConstPartial} \\
		&&  \sum\nolimits_{i=1}^n y_i^t\leq p^\mathsf{total} ,\quad\quad\forall t,\label{ConstTotal} \\
		&&\sum\nolimits_{i:h(i)=j} y_i^t\leq p_j ,\quad\quad\forall t,j,\label{ConstLocal}\\
		&& y_i^t  \leq \frac{k_i}{D_i}\sum\nolimits_{t^\prime=a_i}^{d_i} y_i^{t^\prime}, \quad\forall i,t,\label{ConstSpeed}\\
%		&& \rev{y_i^t=0,\forall t\in\{t':t'>d_i \vee t'<a_i\}}, \\
		\text{vars.} && y_i^t \geq 0, \quad\quad\forall i, t,\label{ConstPositive}\nonumber
		%&& s_v(t), \quad \forall v,t
		\eee
		\ese
		where $y_i^t$ is the amount that EV $i$ is charged at slot $t$. Constraint (\ref{ConstPartial}) ensures that the aggregate amount received by EV $i$ is at most the demand $D_i$. 
%		Note that under integral revenue model, when we design our algorithm, we do not allow partial charging. 
The global and local peak constraints are represented by constraints (\ref{ConstTotal}) and (\ref{ConstLocal}), respectively.

		\revv{The constraint~\eqref{ConstSpeed} enforces the maximum charging rate of EVs. The straightforward way to express this constraint is to simply state that at each time slot $t$, the charging rate of EV $i$ should be less than or equal to its maximum charging rate, i.e., $y_i^t\leq k_i, \forall i,t$. 
		However, for the sake of effective algorithm design for integral model and reducing the integrality gap of the relaxed linear problem, this constraint is strengthened in the form of Eq.~\eqref{ConstSpeed}. 
		Note that in case that the aggregated charging of EV $i$ during its availability window is equal to its demand, i.e., $\sum_{t^\prime=a_i}^{d_i} y_i^{t^\prime}= D_i$, Eq.~\eqref{ConstSpeed} reduces to the simple form of $y_i^t\leq k_i$.  
		This is a natural way in approximation algorithm design to improve the performance of the algorithms under linear-relaxation based design~\cite{Carr}. }

The \MCSP is an extension of formulated problem in \cite{Jain} where a job scheduling problem in cloud applications is studied. It turns out that the resource allocation problem in cloud systems and the EV charging scheduling problem in a \emph{single station} share similar structure. Indeed, each charging profile in our scheduling problem can be seen as a job in cloud system with a deadline, value, and CPU demand. The \MCSP, however, comes with an additional constraint~\eqref{ConstTotal}, which makes it different from the problem in \cite{Jain}, such that the existing solution \revv{will not} work in the new setting. More importantly, this paper studies both offline and online solutions for the problem in both fractional and integral settings, while \cite{Jain} tackles only the offline integral model.

%(ii) Our solution design and analysis for integral revenue model is based on linear-relaxation primal-dual framework~\cite{Jain}. Therefore, in Section \ref{sec:integral} for integral revenue model, we rely on the \MCSP for the analysis of the proposed algorithms and skip to explicitly formulate the original MILP problem.

%		Also, we cover the fractional revenue model and provide theoretical bounds for the proposed algorithms.

%In the next two sections, we devise several algorithms to solve the \MCSP under the two revenue models (integral and fractional) and for both offline and online scenarios. 
		\section{Fractional Revenue Model}
		\label{sec:fractional}

%\subsection{Overview of Fractional Revenue Model}
%\label{sec:frac.overview}				
		%In the previous section, we devised an approximation algorithm for the integral revenue model in which it is assumed that the obtained revenue is zero if the allocated resource is less than the demand. Although this assumption is reasonable in some scenarios, 
%To develop a solution for the \MCSP, we first consider fractional revenue model.
%However, algorithms for integral revenue model cannot achieve the same performance as the algorithms of this section i.e., \fcs and \focs.

In the fractional model, the revenue of the CS from EV $i$ is directly proportional to the amount of resource that the EV is received, i.e.,
		\begin{equation}
			v_i^{\mathsf{f}}=\frac{\sum_t y_i^t}{D_i}v_i,
			\label{Eq:partial_value}
		\end{equation}
		where $v_i$ is the gain, if the entire demand $D_i$ is fulfilled and $v_i^{\mathsf{f}}$ is the fractional gain.

%Under fractional revenue model and without the binary variable of selecting EVs, the underlying problem turns into a linear one. 
We propose a simple algorithm, called \fcs, with low computational complexity \rev{ of $O(n^2T+nT^2)$} for the fractional model that finds the optimal solution in offline setting. Note that even though linear programs can be solved in polynomial time in general, the complexity of our proposed algorithm is much lower than the general linear program algorithms. Moreover, our proposed offline algorithm applies a valley-filling strategy to reduce the peak. 
%The details of the proposed algorithm \fcs is given in~\cite{alinia2017online}. In the following, the online $2$-competitive algorithm is designed, where no exact information or stochastic modeling of future inputs of the problem is available. 
A summary of proposed algorithms with their complexity and assumptions is given in Table \ref{tbl:algs}.

\revv{
\subsection{Optimal Offline Design}
\label{sec:fopt}				
We refer the proposed algorithm as the \fcs and summarize it as Algorithm~\ref{alg:optimal-off}.
The \fcs works in two phases. In the first phase (Section~\ref{sec:ph1}), the algorithm decides on the amount of resource to be allocated to each EV within its availability window and reserves resources accordingly. In this phase, the details of allocation is not known. The actual resource allocation is done in the second phase (Section~\ref{sec:ph2}) by setting variables $y_i^t$.

Before discussing the details of the algorithm, we give \bt{a definition} and introduce some notations to facilitate our algorithm design.

\begin{defi}
	Time interval $[\delta,\delta']$ is a ``super interval'' for interval $[t,t']$ if $1\leq \delta\leq t \text{~AND~} t' \leq \delta'\leq T$.
	Moreover, $\mathcal{I}_{t,t'}$ is the set of all super intervals of interval $I_{t,t'}$ i.e., ${\mathcal{I}_{t,t'}=\{[\delta,\delta']: 1\leq \delta\leq t \text{~AND~} t'\leq \delta'\leq T\}}$.
\end{defi}

%		For example, $\mathcal{I}_{1,1}=\{I_{1,1},I_{1,2},I_{1,3},\dots ,I_{1,T}\}$. 
The number of super intervals of an interval is at most $T^2$ and at least one (for interval $[1,T]$).

Let $R_i$ be the amount of resource that is reserved for EV $i$ by the \fcs and $I_{t,t'}$ as time interval $[t,t']$.
% with $t,t'\in\{1,\dots ,T\}$ which includes time slots $t,t+1,\dots ,t'$. 
Then, assuming that charging demands are sorted in non-increasing order of their unit values, $A^i_j(t,t')$ is the aggregate residual resource in interval $I_{t,t'}$ at station $j$ assuming that the reservation for EVs $1$ to $i$ is accomplished. We now explain in detail each phase of the algorithm.

\subsubsection{Phase I-Reservation\label{sec:ph1}} In Line~\ref{algline:sort1}, the EVs are sorted in a non-increasing order of their unit values.  
%		i.e., ${v_1\slash D_1\geq v_2\slash D_2\geq\dots \geq v_n\slash D_n}$. 
In Line~\ref{algline:setR}, the \fcs processes demand of EV $i$, picked from top of the ordered list, and sets $R_i$ as the amount to be reserved for EV $i$ which will be allocated in Phase II. In Line~\ref{algline:seta}, the residual resource of all intervals in set $\mathcal{I}_{a_i,d_i}$ decreases by $R_i$ and EV $i$ is added to the set of selected EVs.

\begin{algorithm}[t]%\small%1
	%\footnotesize
	\revv{
	\caption{\fcs}
	\label{alg:optimal-off}
	\DontPrintSemicolon 
	\KwIn{$n$ EVs with their profile, local and global peak constraints $p_j, j=1,\dots ,m$ and $p^\mathsf{total}$ }

	\KwOut{Optimal scheduling under fractional model}
	\BlankLine

	Sort charging requests in non-increasing order of their unit values, i.e., $\frac{v_1}{D_1}\geq \frac{v_2}{D_2}\geq\dots \geq \frac{v_n}{D_n}$\label{algline:sort1}

	%	\slash\slash\textit{\texttt{Use sorted list to process demands}}

	$\mathcal{L}\leftarrow \emptyset$

	\slash\slash\textit{\texttt{Phase I}}

	\For{$i=1,\ldots, n$}{
		%\slash\slash\textit{\texttt{update demand and value}}

		$R_i \leftarrow \min\{D_i, \min\limits_{t,t'} A^{i-1}_{h(i)}(t,t'), \forall t,t': I_{t,t'}\in\mathcal{I}_{a_i,d_i}\}$\label{algline:setR}

		\If{$R_i>0$}{
			$A^{i}_{h(i)}(t,t')\leftarrow A^{i-1}_{h(i)}(t,t')-R_i, \forall t,t': [t,t']\in\mathcal{I}_{a_i,d_i}$ \label{algline:seta}\\
			$\mathcal{L}\leftarrow \mathcal{L}\cup{i}$
	}}
	\slash\slash\textit{\texttt{Phase II}}

	Sort EVs in $\mathcal{L}$ in increasing order of their charging flexibility i.e., $\frac{(d_i-a_i+1)k_i}{D_i}, i\in \mathcal{L}$.

	%	Let $i$ be the index of $i^{th}$ EV in list $\mathcal{L}$

	\For{$i=1,\ldots, |\mathcal{L}|$}{

		Pick EV $i$ from the sorted list $\mathcal{L}$.

		$\emph{feasible}\leftarrow \big(\sum_{t=a_i}^{d_i}\min\{k_i,A^{i-1}_{h(i)}(t,t)\}\big) - R_i$

		\If{feasible $<0$}{
			Re-allocate previously allocated EVs such that $\emph{feasible}\geq 0$
		}
		Arbitrarily allocate $R_i$ to EV $i$ in its availability window\label{algline:fcsallocate}	
	}}
\end{algorithm}

\begin{lem}
	Provided that for EV $i$ we have 
	\bee
	\label{eq:ri}
	R_i\leq\min\left\{D_i, \min_{t,t'} A^{i-1}_j(t,t'), \forall t,t': I_{t,t'}\in\mathcal{I}_{a_i,d_i}\right\}
	\eee
	 with a dummy $A^0_j(t,t')$ defined as
$A^0_j(t,t')=(t'-t+1)\times\min \{p^\mathsf{total},p_{j}\},$
	then there is a feasible allocation to allocate $R_i$ to EV $i$ in its availability window $[a_i,d_i]$. 
	\label{thm:R_feasible}
\end{lem}

In Lemma \ref{thm:R_feasible}, $A^0_j(t,t')$ indicates the available resource when no charging request is processed in $I_{t,t'}$. 
In Eq.~\eqref{eq:ri}, the second term, i.e., $\min_{t,t'} A^{i-1}_{j}(t,t')$, indicates the minimum remaining resource in all super intervals of interval $I_{a_i,d_i}$. For $i\geq 1$, $A^i_j(a_i,d_i)$ is defined as follows:

\begin{equation*}
A^i_j(a_i,d_i)=\begin{cases}
A^{i-1}_j(a_i,d_i)-R_i & j=h(i),\\
A^{i-1}_j(a_i,d_i) & j\neq h(i).
\end{cases} 
\end{equation*}

The optimal value of $R_i, i=1,\dots ,n$ is set according to the following lemma:

\begin{lem}
	Given $n$ EVs sorted in a non-increasing order of the unit values, ${v_1\slash D_1\geq v_2\slash D_2\geq\dots \geq v_n\slash D_n}$, and the value of $R_i$, where $R_i$ is set after $R_{i-1}, i=2,\dots ,n$ by Eq.~\eqref{eq:ri}, then, 
	$$R_i = \min\left\{D_i, \min_{t,t'} A^{i-1}_{h(i)}(t,t'), \forall t,t':I_{t,t'}\in\mathcal{I}_{a_i,d_i}\right\},\forall i,$$
	is the optimal value for $R_i$. 
	\label{thm:R_star}
\end{lem}

\subsubsection{Phase II- Allocation\label{sec:ph2}} Lemma~\ref{thm:R_feasible} shows that there is a feasible scheduling to allocate the reserved resources.
However, despite its feasibility, it is not straightforward to find such \revv{a schedule}. For example, assume that for EV $i$, $R_i=10$ and $k_i=4$. It is possible that all available resources are concentrated in a single time slot but EV $i$ cannot use more than $4$ kWh of it. In this situation, the previously allocated resources in interval $I_{a_i,d_i}$ should be re-allocated such that the concentrated resources are \emph{dispersed} and we have $\sum_{t=a_i}^{d_i}\sigma_t \geq R_i$ where $\sigma_t =\min\{k_i,A^{i-1}_{h(i)}(t,t)\}$ is the maximum resource that can be allocated to EV $i$ at time slot $t$. Since the total amount of allocated resource does not change in the interval, such dispersion is possible and can be done by a simple algorithm in which allocates $\min\{k_i,A^{i-1}_{h(i)}(t,t)\}$ starting from time slot $t=a_i$ until $R_i$ units is allocated. To further reduce the peak of the system, we will develop \sa\ algorithm (See Section \ref{sec:integral}) which acts more intelligent so that Line \ref{algline:fcsallocate} of the \fcs can be replaced by ``Run \sa$(i,R_i)$''.

\begin{thm}
	\label{cor:1}
	\fcs is an optimal solution under fractional revenue model.
\end{thm}

The following theorem characterizes the complexity of \fcs.

\begin{thm}
	\label{thm:complexity}
	The time complexity of \fcs algorithm is $O(n^2T+nT^2)$ where $n$ is the number of EVs and $T$ is number of time slots.
\end{thm}
}

\vspace{-4mm}
\subsection{Online Scenario}
\label{sec:fonline}
In this section, we devise an algorithm for the scenario that EVs arrive in online fashion. The scheduling decisions at each time slot are made given the information of available EVs and neither exact values nor stochastic modeling of future arrivals is available. Our goal is to obtain a \emph{competitive ratio} for the online algorithm. A scheduling algorithm $\mathcal{A}$ is $c$-competitive for $c\geq 1$ if the revenue obtained by the optimal offline algorithm is at most $c$ times the algorithm $\mathcal{A}$'s revenue for any input sequence~\cite{borodin2005online}.

The proposed online algorithm for the fractional model, referred to as \focs, is listed as Algorithm~\ref{alg:focs}. The \focs is a simple yet efficient algorithm that always selects EVs with highest unit value to allocate as follows. First, the algorithm sorts the available EVs at each time slot~$t$ based on their unit value (Line~\ref{algline:sort}). \revv{In this step, the algorithm breaks ties based on EVs' deadline i.e., if two EVs have the same unit value, then the one with earliest deadline comes first in the sorted list.} Next, the \focs selects one EV at a time from the sorted list to allocate with maximum charging rate considering the EV's remaining demand, maximum charging rate, and peak constraints (Lines~\ref{algline:focsfor}-\ref{algline:focssety}). The allocation is continued until all resources are allocated or there is no more EV that could be allocated. 
%For unselected EVs, the value of $y_i^t$ will be $0$ in Line \ref{algline:focssety} of the algorithm. 
The time complexity of the \focs is $O(n^2T)$, determined by cost of its ``\textbf{for}'' loop multiplied by total number of times that the algorithm needs to be run.
% i.e., $T$.

\vspace{-4mm}
\begin{algorithm}%\small%1
\footnotesize
\caption{\focs: $\forall t\in \{1,2,\dots ,T\}$}
\label{alg:focs}
\DontPrintSemicolon 
%\KwIn{Available EVs at time slot $t$, number of CSs $m$, local peak constraint $p_j, j=1,\dots ,m$, global peak constraint $p^{\textrm{total}}$}

%\KwOut{A feasible charging scheduling}

%$\backslash\backslash\texttt{Initialize:}$

\BlankLine

$\mathcal{M}^t\leftarrow$ The set of available EVs that not received their entire demand by $t$

Sort EVs in set $\mathcal{M}^t$ indexed by $i=1,\dots ,|\mathcal{M}^t|$: $v_1/D_1\geq v_2/D_2\geq\dots\geq v_{|\mathcal{M}^t|}/D_{|\mathcal{M}^t|},$  \revv{where ties are broken based on users' deadline (giving priority to the users with earliest deadline) }\label{algline:sort}

\For{$i=1,\ldots,|\mathcal{M}^t|\label{algline:focsfor}$}{

$y_i^t\leftarrow \min\{k_i,D_i-\sum_{\tau=a_i}^{t}y_i^{\tau},p_{h(i)}-\sum_{i':h(i')=h(i)}y_{i'}^t,p^{\textrm{total}}-\sum_{i'}y_{i'}^t\}$ \label{algline:focssety}

}

\end{algorithm}
Despite the simplicity of \focs which makes it easy to implement, its performance is sound and within a constant factor of the offline optimum. We now proceed to analyze the performance of the \focs by first giving some preliminaries.

Fix an optimal scheduling and let $\mathcal{S}_{\focs,t}$ and $\mathcal{S}_{\opt,t}$ be the sets of EVs selected by the \focs and optimal solution at time slot $t$, respectively. Let $y_{i}^t$ and $z_{i}^t$ be the charging rate of EV $i$ set by \focs and \opt, respectively. We define $\Delta_{i}^t$ as follows:
\begin{equation}
\label{eq:delta}
\Delta_{i}^t =
     \begin{cases}
       \min\{z_{i}^t-y_{i}^t,r_{i,t}\} &\quad i\in\mathcal{S}_{\opt,t},z_{i}^t>y_{i}^t, \\
       0& \quad\text{otherwise},  \\
     \end{cases}
\end{equation}
where $r_{i,t}$ is the remaining demand of EV $i$ by the end of time slot $t$. $\Delta_{i}^t>0$ indicates that the optimal algorithm allocated $\Delta_{i}^t$ units more resources to EV $i$ than the \focs by time slot $t$ that could be \emph{feasibly} allocated by \focs to the EV $i$. If for any EV $i\in\mathcal{S}_{\opt,t}$ and time slot $t\in\mathcal{T}$ we have $y_{i}^t=z_{i}^t$, i.e., $\Delta_{i}^t=0$, then the \focs is obviously optimal because it gains whatever the optimal solution gains. \rev{We define \textit{loss} of the \focs imposed by EV $i$ as follows:
\begin{equation}
\label{lBj0}
l_{i,t}=\Delta_{i}^t\frac{v_i}{D_i},
\end{equation}

Note that the loss always takes a non-negative value as $\Delta_i^t\geq 0$.} When \focs sets charging rate of an EV less than its rate in the optimal solution, it gains $\Delta_{i}^t v_i/D_i$ less than the optimal solution from that EV. An upper bound for the distance between the optimal objective value (denote by \opt) and the revenue of the \focs (denote by \alg) is summation of the losses over all time slots and all EVs, i.e., 
\begin{equation}
\label{eq:optdist}
\opt-\alg\leq \sum_{t=1}^T\sum_{i\in\mathcal{S}_{\opt,t}} l_{i,t}.
\end{equation}

%Notice that it is possible that an algorithm does not choose any selected EV by a particular optimal solution but still provide an optimal or near-optimal solution as there can be multiple optimal solutions. In particular, $\mathcal{S}_{\focs,t}\cap \mathcal{S}_{\opt,t}=\emptyset, \forall t$ cannot lead to any conclusion on the competitive ratio of the \focs. 
In addition to the amount of loss, the gain of the algorithm from charging alternative EVs should also be taken into account in comparison between \opt and \alg.

Let $i\in\mathcal{S}_{\opt,t}$, $i\notin\mathcal{S}_{\alg,t}$ and $g_{i,t}$ be the gain that the \focs obtains from charging another EV instead of $i$ at time slot $t$. We are going to show that in the \focs, for each EV $i$ with $l_{i,t}>0$ there must be another EV (denote by $i'$) where $y_{i'}^t\geq \Delta_i^t$ and $\frac{v_{i'}}{D_{i'}}\geq \frac{v_i}{D_i}$ which means in resource allocation phase for EV $i$, the \focs allocated the difference $\Delta_i^t$ to another EV with the same or higher unit value. This can be proved by considering the fact that (i) the selected EVs have higher unit values than the unselected EVs, and (ii) the charging rate of the selected EVs are set to the maximum feasible value. Moreover, the \focs is \emph{``work-conserving''} i.e., it does not let any resource remain unused if there are some EVs that can use it.

Let $g_{i,t}$ denote the gain that \focs obtains from allocating the same amount of resource that optimal algorithm allocated to EV $i$ (with size $z_i^t$) to another EV(s).
If $\Delta_{i}^t=0$, the loss is zero. If $\Delta_{i}^t>0$, then by the charging strategy that the \focs uses we can conclude that (i) $i$ is not finished by the \focs, and (ii)
\rev{no more resources from station $p_{h(i)}$ can be feasibly allocated,} otherwise, the \focs could allocate more resources to EV $i$. Therefore, the $\Delta_{i}^t$ units of the resource \rev{are} allocated to one or multiple other EVs (denote them by set $\mathcal{J}_i^t$) by the \focs. Moreover, it must hold that all the EVs in set $\mathcal{J}_i^t$ have a unit value equal to or higher than $v_i/D_i$ which yields $g_{i,t}\geq l_{i,t}$, otherwise, the \focs should not prefer the EVs in $\mathcal{J}_i^t$ to $i$. \rev{Since the result holds for any arbitrarily EV $i$, we can get the following:}

\begin{equation}
\label{eq:lg}
\sum_{i=1}^n\sum_{t=1}^Tl_{i,t}\leq\sum_{i=1}^n\sum_{t=1}^Tg_{i,t}.
\end{equation}

Moreover, the total gain of \focs, i.e., \alg, is equal to sum of its gains from each single EV:
\begin{equation}
\label{eq:ALG}
\rev{\alg= \sum_{i=1}^n\sum_{t=1}^Tg_{i,t}.}
\end{equation}

With the above discussion and using Eqs. (\ref{eq:optdist}), (\ref{eq:lg}) and (\ref{eq:ALG}) we are able to derive a competitive ratio of $2$ for the \focs.

\begin{thm}
	\label{thm:focscompetitive}
	The \focs is $2$-competitive.
\end{thm}

\emph{Remarks:} When there is only one CS and EVs have no limit on their charging rate, the \focs is identical to the \textsc{FirstFit} algorithm ~\cite{firstfit} which is known to be $2$-competitive for classic job scheduling problem. However, the charging rate limitation is crucial for EV charging problem. Moreover, \cite{firstfit} uses \revv{a} ``charging argument'' to prove the competitive ratio of the proposed algorithm which cannot be directly applied to our problem. Thus, the \focs extends the \textsc{FirstFit} and makes it practical for the EV charging scenario. Moreover, the proof technique used for the competitive analysis of the \focs is fundamentally different from the one used in \cite{firstfit}. 
%%%Finally, in~\cite{Robu} an online $2$-competitive algorithm for EVs with partial charging is proposed. The competitive ratio obtained assuming that charging of EVs is instantly reversible at departure times. This assumption is not practical in reality since similar to charging phase, there is a discharging rate constraint for EVs.

%\begin{thm}
%\label{thm:focscomplexity}
%
%The time complexity of \focs is $O(nT\log n)$.
%\end{thm}
		\section{Integral Revenue Model}
		\label{sec:integral}
%
%		\subsection{Overview of Integral Revenue Model}
%		\label{sec:intoverview}
		The MILP form of the \MCSP in integral model is a generalized form of the $0/1$-knapsack problem which is a well-known NP-hard problem. \rev{To give an intuition, consider the scheduling problem in a single time slot (i.e, $T=1$). Then, allocating power resources to the EVs is equivalent to allocating the capacity of knapsack to the items. }	
		In Section~\ref{subsec:icsalgorithm}, we propose a fast polynomial time offline approximation algorithm for the integral problem. In Section~\ref{sec:onlineint}, we extend the result and propose an online algorithm for the integral model.
%		, where the EVs arrive in slot-by-slot fashion, and the scheduler has no information of the future arrivals.

%The problem is even more challenging when the uncertainty in EVs' arrival is taken into account. At each time slot, the scheduler has no information of unit values of the future charging profiles. Therefore, the scheduler cannot make sure about the efficiency of its current charging decision.
%It can be shown that when there is no assumption on the charging profiles of EVs (including the value of slackness parameter) and the charging decision , no online algorithm can provide a performance guarantee meaning that in the worst case, the ratio of the optimal objective value to the one obtained by the online algorithm can be arbitrary small. In fact, when the online algorithm selects

		\subsection{Offline Scenario}   
		\label{subsec:icsalgorithm}
		We design our offline scheduling algorithm under integral model referred to as \ics, to solve the \MCSP approximately. 
%		Our algorithm design is inspired by the basic algorithm proposed in \cite{Jain}. The algorithm in \cite{Jain} works for a single CS where arrival time of all EVs are the same and there is no global peak constraint. 
Since the performance analysis of the proposed algorithm relies on a dual fitting method and utilizes weak duality property, \revv{we first need to construct the dual problem of \MCSP. Toward this, we introduce variables $\alpha, \beta, \gamma$ and $\pi$. Generally, in primal-dual approximation algorithm design, each constraint (resp. variable) in primal (resp. dual) problem is associated with a variable (resp. constraint) in dual (resp. primal) problem. In our case, constraints (\ref{ConstPartial}) (\ref{ConstTotal}), (\ref{ConstLocal}) and (\ref{ConstSpeed}) in the \MCSP are respectively associated with dual variables $\alpha, \beta, \gamma$ and $\pi$ (for more details see \cite{approx}). The dual problem is formulated as follows:}
		\bse
		\bee
		\min &&\sum_{i=1}^n D_i\alpha _i + \sum_{j=1}^m \sum_{t=1}^T p_j\beta (t)+\sum_{t=1}^T p^\mathsf{total}\gamma (t)\nonumber\\ 
		\textrm{s.t.} && \alpha _i+\beta (t) +\gamma _i + \pi (t)- \frac{k_i}{D_i}\sum_{t'=a_i}^{d_i} \pi _i(t^\prime) \geq \frac{v_{i}}{D_i},\label{ConstDcover} \nonumber\\
		&& \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\forall i, t\in [a_i, d_i],\\
		\textrm{vars.}&&\alpha _i, \beta _i, \gamma,  \pi _i(t)\geq 0,\quad\quad\forall i,t. \nonumber
		\eee
		\ese

		%%%In this section, we explain \ics in details and then in Section~\ref{subsec:analysis}, we analyze approximation factor of the algorithm. The \ics algorithm is listed as Algorithm~1.

		\subsubsection{Explanation of the Main Algorithm} 
		\label{sec:icsexplanation}
		Our algorithm design is inspired by the basic algorithm proposed in \cite{Jain}. \revv{The algorithm in~\cite{Jain}, however, works for a single CS where arrival time of all EVs are the same and there is no global peak constraint.}
		The \ics algorithm (listed as Algorithm \ref{alg:ics}) works in two phases. In the first phase it sorts the charging requests based on their unit values in a non-increasing order. Then, it selects most valuable demand. If the remaining resource is enough to cover the \emph{entire} demand of the EV, it is admitted to receive the demand (Lines~$6$-$7$). 
%		When \ics processes EV $i$, the algorithm checks for the feasibility of allocating $D_i$ units of the resource within its availability window $[a_i,d_i]$ without violating the constraints related to the maximum charging rate $k_i$, local and global peaks (Lines~$6$-$8$).

		\emph{Scheduling of the Selected EV:} \revv{If the feasibility check passed (Line 6 in Algorithm 3)}, \ics calls sub-procedure \sa\ to allocate required resources in interval $[a_i,d_i]$. Then, $\alpha _i$ is set to $v_i\slash D_i$ in order to cover dual constraint in Eq.~\eqref{ConstDcover} (Lines~$7$-$8$).

		In \sa, 
		%%%When EV $i$ is selected to get charged, \sa\ is called for the charging scheduling. 
		let us define $W(t,h(i))=\sum_{i': h(i')=h(i)} y_{i'}^t$ as total workload at time slot $t$ in CS $h(i)$ and $\bar{W}(t,h(i))$ as total available load to allocate at time slot $t$ for CS $h(i)$. We always have ${\bar{W}(t,h(i))+W(t,h(i))=p_{h(i)},  \forall t, i}$. For scheduling, \sa\ applies two main policies: 1) \emph{valley-filling} and, 2) \emph{right-to-left allocation}. \revv{With valley-filling, the slots with more available resources are preferred which helps to reduce the peak of the system.} %%%It also can be seen as a smoothing method which tries to reduce the variance of the allocated resources at different slots. 
%				The simulation results in Section \ref{sec:simul} will confirm this claim. 
				Right-to-left allocation is used when two or more time slots are equal in terms of their remaining resources. 
%				When this policy applies on scheduling of EV~$i$, any EV~$i'$ with $i'>i$ and $d_{i'}<d_i$ has more chance to get charged since the algorithm tends to charge EV $i$ in interval $[d_{i'}+1,d_i]$ (i.e., right hand part of the EV's availability window) and keeps resources in $[a_{i'},d_{i'}]$ for EV $i'$. 
A ranking based approach is used to apply the aforementioned policies. 
		To charge  EV $i$, \sa\ ranks time slots in interval $[a_i,d_i]$. Then, charging is done by allocating resources from the higher ranked time slot to lowest one. The rank of a time slot $t$ is calculated based on remaining resources in the time slot (valley-filling) and value of $t$ (right-to-left allocation).

		\vspace{-3mm}
		\begin{algorithm}%\small%1
			\footnotesize
			\caption{\ics}
			\label{alg:ics}
			\DontPrintSemicolon 
%			\KwIn{$n$ EVs with $a_i, d_i, v_i, D_i,$ and $k_i$ associated with each EV $i$, $m$ CSs, local and global peak constraints $p_j, j=1,\dots ,m$, and $p^\mathsf{total}$}

%			\KwOut{A feasible scheduling of EVs}
			\BlankLine
			%\begin{algorithmic}

			%\slash\slash\textit{\texttt{Initialization}}
			\textbf{initialize}: $y\leftarrow 0, \alpha\leftarrow 0, \beta\leftarrow 0, \gamma\leftarrow 0, \pi\leftarrow 0$

			Sort charging requests in non-decreasing order of their unit values: $v_1/D_1 \geq v_2/D_2\geq\dots \geq v_n/D_n$
%			$\frac{v_1}{D_1} \geq \frac{v_2}{D_2}\geq\dots \geq \frac{v_n}{D_n}$
%			\slash\slash\textit{\texttt{Use sorted list to process demands}}

			\For{(i=1\dots n)}{

				\For{$t=a_i\dots d_i$}{
					$\sigma_t\leftarrow  \min\Big\{p_{h(i)}-\sum_{i':h(i')=h(i)}y_{i'}(t),$ \newline $\qquad p^\mathsf{total}-\sum_{i'=1}^n y_{i'}^t,k_i\Big\}$

				}

%				\slash\slash\textit{\texttt{if enough resources remain for EV $i$}}

				\If{$D_i\leq\sum_{t=a_i}^{d_i}\sigma_t$}
				{
					\sa($i,D_i$)\\
					$\alpha _i\leftarrow v_i/ D_i$
				}
				\Else {
					\If{$(\beta (d_i)=0)$}{
						\bc($i$)}
				}
			}

			\For{(i=1\dots n)}{ 
				\If {EV $i$ is not selected}{
					\rc($i$);
				}
			}
			%\end{algorithmic}
		\end{algorithm}

\emph{Dual Feasibility of the Non-selected EVs:} \bt{If remaining power resource is not enough} to fully charge EV $i$, i.e.,  $D_i>\sum_{t=a_i}^{d_i}\sigma_t$, the EV cannot be selected. However, we still need to satisfy constraint~\eqref{ConstDcover} in dual problem which is done by calling \bc($i$). To cover the constraint~\eqref{ConstDcover} for EV $i$, sum of dual variables for all $t\in [a_i ,d_i]$ should be greater than or equal to ${v_i \slash D_i}$. \bc($i$) sets $\beta (t)$ to ${v_i \slash D_i}$ for all time slots $t$ in interval $[t_\mathsf{cov}, R(d_i)]$ (Lines $3$-$4$ of Algorithm~\ref{alg:betacover}). Observe that  ${\beta (t^\prime)\geq v_i \slash D_i,\forall t^\prime< t_\mathsf{cov}}$ (with $ t_\mathsf{cov}>1$) considering that the demands are sorted in a non-increasing order of the unit-values and $\beta (t')$ is already set to ${v_{i'} \slash D_{i'}}$ when processing the earlier charging demand of EV $i'$ which is not selected. Hence, ${v_{i'}\slash  D_{i'}\geq v_i \slash D_i}$, thereby ${\beta (t)\geq v_i \slash D_i,}$ and the dual constraint in~\eqref{ConstDcover} is satisfied.		
		Lines $1$-$4$ of \bc\ is enough to cover the dual constraint. However, the algorithm continues in Lines $5$-$8$ by setting a variable $\Phi_{i'}(t)$ for time slots $t=1,\dots ,R(d_i)$ to a value dependent to amount of the resource that a selected EV $i'$ received at slot $t$. $\Phi_{i'}(t)$ will be used in approximation analysis of the main algorithm and has no effect on the scheduling of EVs. 
		%We borrowed algorithm \bc($i$) from \cite{Jain} and adjusted it for multiple station mode.		
		\vspace{-3mm}
		\begin{algorithm}%\small%1
			\footnotesize
			\caption{\sa($i,D_i$)}
			\label{SmartAllocate}
			\DontPrintSemicolon 
			\KwIn{EV $i$ to receive $D_i$ from CS $h(i)$}

			Rank time slots in interval $[a_i,d_i]$ such that for any $t_1$ and $t_2$:
			$\mathsf{rank}(t_1)> \mathsf{rank}(t_2)$ iff $\bar{W}(t_1,h(i))>\bar{W}(t_2,h(i))$ OR $\bar{W}(t_1,h(i))==\bar{W}(t_2,h(i)) \wedge t_1>t_2$

			\While {$\sum_{t'=a_i}^{d_i}y_i^{t'}\neq D_i$}{

				Select time slot $t$ with highest rank which is not selected before

				Allocate $\min \left\{k_i,\bar{W}(t,h(i)),D_i-\sum_{\tau=a_i}^{t}y_i^{\tau},p^{\textrm{total}}-\sum_{i'}y_{i'}^t\right\}$ to EV $i$ at $t$

			}
		\end{algorithm}	
		\vspace{-7mm}	
		\begin{algorithm}%\small%1
			\footnotesize
			\caption{\bc($i$)}
			\label{alg:betacover}
			\DontPrintSemicolon 
			%\KwIn{EV $i$ which is not selected to charge}

			\BlankLine

			$t_\mathsf{cov}\leftarrow \min \{t: \beta (t)=0\}$

			$R(d_i)=\max \{t\geq d_i : \forall t^\prime\in (d_i,t], \bar{W}(t^\prime)<q_{h(i)} \}$

			\For{$(t=t_\mathsf{cov}\dots R(d_i))$}{
				$\beta (t)\leftarrow v_i/D_i$
			}

			\For{$(t=1\dots R(d_i))$}{
				\For{$(i'=1\dots n))$}{	
					\If{$y_{i'}^t>0 \wedge \Phi_{i'}(t)=0$}{
						$\Phi_{i'}(t)\leftarrow\big[ \frac{p_{h(i)}}{p_{h(i)}- k_i}\frac{s}{s-1}\big] .\frac{v_i}	{D_i}y_{i'}^t$
					}
				}
			}
		\end{algorithm}
		\vspace{-7mm}
		\begin{algorithm}%\small%1
			\footnotesize		
			\caption{\rc($i$)}
			\label{Replace}
			\DontPrintSemicolon 
%			\KwIn{EV $i$}
%			\KwOut{Updated schedule}

			$\mathcal{L} \leftarrow \emptyset$\\			
			$v_\mathsf{inc}\leftarrow v_i$\\			
			$\sigma_t\leftarrow 0, t=a_i,\dots ,d_i$

			%Define $\delta_i(t)=\min \{k_i,\bar{W}(t,h(i))\}$

			%$\Delta\leftarrow \sum_{t=a_i}^{d_i}\min\{\bar{W}(t,h(i)), k_i\}$

			\For{($i' =i-1\dots 1$)}{ 
				\If {EV $i'$ is selected $\wedge (h(i')=h(i)) \wedge (v_\mathsf{inc}-v_{i'})>0$}{
					Add EV $i'$ to list $\mathcal{L}$

					$v_\mathsf{inc}\leftarrow v_\mathsf{inc}-v_{i'}$

					\For{($t=a_i\dots d_i$)}{
						$\sigma _t\leftarrow\sigma_t + \min\{k_i,y_{i'}^t\}$
					}
				}
			}

			\If {$\sum_{t=a_i}^{d_i}\sigma_t\geq D_i$}{
				Remove EVs in list $\mathcal{L}$ from charging schedule

				\sa($i,D_i$)
			}
		\normalsize
		\end{algorithm}

		\emph{Improving the Gain:} In the second phase, the \ics tries to increase total value of selected EVs by calling \rc($i$) on every unselected EV $i$ (Lines~$12$-$14$).  \rev{The \rc(i) (listed as Algorithm $6$) checks that whether the total revenue can be increased by replacing some selected EVs with EV $i$ or not (Lines $4$-$9$). If such EVs are found, the algorithm stops their charging and allocates EV $i$ using \sa\ (Lines $10-12$).} 
		%We refer to ~\cite{alinia2017online}, for the details and intuition behind this algorithm. 
%		Before giving the details of \rc($i$), we first explain the intuition behind this algorithm. 
%		 Note that if in the scheduling problem we set $T=1, m=1, k_i=p^\mathsf{total}, a_i=d_i=1\ \forall i$, then the problem is equal to the well-known $0$-$1$ knapsack problem~\cite{approx}. In the knapsack problem, a widely used greedy approach sorts items based on their unit values and selects items accordingly. It turns out that in this approach the approximation factor can be arbitrarily bad. For example, consider a knapsack problem with two items with $v_1=2, v_2=p^\mathsf{total}, D_1=1$, and  $D_2=p^\mathsf{total}$. Given these values we have $v_1\slash D_1>v_2\slash D_2$. To maximize total value of selected items, the optimal solution chooses item $2$ while greedy algorithm selects item $1$ which results in a worst-case approximation factor of ${c \slash \opt}$ in general where $c$ is a constant (in this example $c=2$). To resolve it, one approach is to \emph{re-consider} unselected items after running greedy algorithm and replace some selected items in the knapsack with unselected ones and then check whether the result is improved or not. In a simple case, only the largest unselected item can be examined which makes a significant theoretical improvement by providing a worst case approximation factor of $\opt\slash 2$.
%		 
%\ics algorithm leverages the same idea but using a more intelligent replacing method called \rc($i$). \rc($i$) is called on every unselected EV $i$. It tries to find some selected EVs that if they are replaced by EV $i$, total revenue from the selected EVs increases. %%%When \ics calls \rc($i$) on all unselected EVs, an improvement in total revenue of final selected EVs is expected. 
%This is confirmed by the simulation results in Section~\ref{sec:simul}.

		\subsubsection{Analysis}
		\label{subsec:analysis}
		In primal-dual algorithm, the goal is to design an algorithm in a way that it produces a good solution for primal problem (with primal value $\Gamma$) and a feasible solution for the dual problem (with dual value $\Lambda$). Then, assuming that the primal problem is a maximization problem, to prove that the algorithm is $c-$approximation (for $c\geq 1$), the important part is to show that $\Lambda\leq c\Gamma$. Then, based on weak duality theorem we have $\Lambda\geq \opt$, and it is concluded that $\Gamma \geq \frac{1}{c}\times\opt$ where $\opt$ is the optimal value. 
		Based on the above understanding, the following theorem scrutinizes the approximation ratio of the \ics assuming that arrival times are the same for all EVs. 
%		First note that the designed scheduling algorithm outputs a feasible scheduling since it respects the constraints in the primal problem. Also, the algorithm produces a feasible solution for the dual problem by covering the dual problem constraint in (\ref{ConstDcover}) through setting $\alpha _i$ to $\frac{v_i}{D_i}$ when EV $i$ is accepted and, $\beta (t)$ to a value greater than or equal to $\frac{v_i}{D_i}$ for $t\in [a_i, d_i]$ (according to the discussion in Section \ref{sec:icsexplanation}) if EV $i$ is not selected. To obtain an approximation factor for the algorithm, it is enough to bound the total covering cost of the dual constraints.

		\begin{thm}
			\label{thm:approx}
			\ics algorithm is a $\Big( 1+ \sum_{j=1}^m {\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}\Big)$-approximation when EVs have same arrival time.
		\end{thm}
%		
%		\begin{proof}
%			In Appendix~\ref{app:1}.
%		\end{proof}

		Note that in the case that the system is flexible enough, i.e., $s\gg 1$, and the maximum charging rates of stations are much bigger than those of EVs, i.e., $p_j \gg q_j, \forall j$, the approximation ratio approaches $m+1$. And in the case that there is one single station, the approximation ratio is $2$.
%		 Finally, we provide the time complexity of the \ics.

%\begin{thm}
%\label{thm:ics_complexity}
%The time complexity of the \ics algorithm is $O(nT\log T+n^2T)$.
%\end{thm}	
%
%\begin{proof}
%In Appendix \ref{app:ics_complexity}.
%\end{proof}

\subsection{Online Scenario}
\label{sec:onlineint}
Due to the binary selection variable, the online solution design under integral model is more challenging than the one for fractional model. We propose the \iocs that is built upon the offline \ics. In particular, the \iocs calls the \ics at each time slot for the set of available EVs, however, any algorithm that is designed for offline integral model can be used alternatively. Hereinafter, $\mathcal{A}$ refers to the \ics or a similar algorithm.

\vspace{-4mm}
\begin{algorithm}%\small%1
\footnotesize
\caption{\iocs: $\forall t\in \{1,2,\dots ,T\}$}
\label{alg:iocs}
\DontPrintSemicolon 
%\KwIn{$n$ EVs to arrive on the fly, number of CSs $m$, global peak constraint $p^{\textrm{total}}$, local peak constraints $p_j, j=1,\dots ,m$}

%\KwOut{A feasible charging scheduling}

\BlankLine

Let $\mathcal{A}$ be an algorithm that solves the problem with $a_1=\dots =a_n$

$\mathcal{R}^t\leftarrow$ set of EVs arrived at time slot $t$

$\mathcal{M}^t\leftarrow \mathcal{R}^t\cup \{i: t\in\mathcal{T}_i\ \texttt{AND}\ \sum_{t^\prime}y_{i}^{t'}<D_i\}$

%$\backslash\backslash\texttt{Schedule 1}$

Based on the residual in interval $[t,T]$, use algorithm $\mathcal{A}$ to allocate EVs in set $\mathcal{R}^t$ assuming no further arrivals

$\mathcal{S}_{\iocs,t}\leftarrow\{i:i\in\mathcal{M}^t\ \texttt{AND}\ i$ is admitted at $t\}$

$\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}\leftarrow \sum_{i\in\mathcal{S}_{\iocs,t}}v_i$

Assume all reserved resources are freed at time slots $t, t+1, \dots, T$

%$\mathcal{R}^t\leftarrow\mathcal{M}^t$

%$\backslash\backslash\textsl{set of active EVs at time slot t}$

$r_{i,t}\leftarrow$ remaining demand of $i$ at $t, \forall i$

%$\backslash\backslash\texttt{Use modified demands values}$

$D_i^\prime\leftarrow r_{i,t},\ \ v_i^\prime\leftarrow \frac{r_{i,t}}{D_i}v_i, \forall i\in\mathcal{M}^t$

%$\backslash\backslash\texttt{Schedule 2}$

Run $\mathcal{A}$ on $\mathcal{M}^t$ using $D_i^\prime$ and $v_i^\prime, \forall i$ and reconstruct $\mathcal{S}_{\iocs,t}$

$\Gamma_{\mathcal{A},\mathcal{M}^t}\leftarrow \sum_{i\in\mathcal{S}_{\iocs,t}}v_i$ $\backslash\backslash\texttt{Use original values}$

%$a\leftarrow\frac{V^\prime_{\textrm{total}}}{V_{\textrm{total}}}$

\If{$\Gamma_{\mathcal{A},\mathcal{M}^t}>\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$}{

Use the second schedule

}

\Else{

Use the first schedule

}

\end{algorithm}

The \iocs is summarized as Algorithm~\ref{alg:iocs}. At slot $t$, the \iocs compares two scheduling results returned by $\mathcal{A}$ and chooses among them. In the first scheduling, the \iocs keeps all reserved resources in interval $[t,T]$ intact. Then, for utilizing the remaining resources, the algorithm runs $\mathcal{A}$ over arrived EVs at time slot $t$. In this case, the total revenue obtained by the \emph{active} EVs (i.e., EVs that are available but not received their entire demand yet) is denoted by $\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$ (Line $6$ of the algorithm). In the second scheduling, the \iocs considers the case that it can sacrifice the previously admitted EVs by canceling their reservations and allocating the freed resources to more valuable demands. For this purpose, the algorithm modifies the demand and valuation of the previously admitted EVs such that each demand is replaced by the EV's remaining demand, and the valuation of the EV is proportionally calculated based on the remaining demand (Line $9$ of the algorithm) so that the unit values of EVs do not change. Then, the \iocs runs $\mathcal{A}$ over set of active EVs $\mathcal{M}^t$ where the corresponding gain is denoted by $\Gamma_{\mathcal{A},\mathcal{M}^t}$. If $\Gamma_{\mathcal{A},\mathcal{M}^t}>\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$, the \iocs forgets the previously admitted EVs and follows the second scheduling.

\begin{comment}
%We now introduce some notations and then analyze the performance of \iocs. 
Let $\mathcal{S}_{\iocs,t}$ and $\mathcal{S}_{\opt,t}$ be set of active EVs at time slot $t$ that are selected for charging by \iocs and \opt (fix a particular optimal solution), respectively. Note that the set of active EVs for \iocs and \opt might be different. 
%Moreover, define  $\mathcal{U}_{\iocs,t}=\mathcal{S}_{\iocs,1}\cup\dots\cup \mathcal{S}_{\iocs,t}$ and $\mathcal{U}_{\opt,t}=\mathcal{S}_{\opt,1}\cup\dots\cup \mathcal{S}_{\opt,t}$. 
Having $i\in\mathcal{S}_{\iocs,t}$ means that based on the updated schedule at time slot $t$, enough resources reserved for EV $i$ so that the EV will receive its demand $D_i$ before the deadline $d_i$. However, the schedule may change at each slot and $i\in\mathcal{S}_{\iocs,t}$ cannot be a guarantee for EV $i$ to fully receive its demand. In fact, users and the scheduler itself have to wait until the deadline of the EV to find out that the demand is fulfilled or not. This is because the scheduler may cancel some reservations in the next time slots and allocate the freed resources to other EVs.
\end{comment}
% (when Algorithm \ref{alg:iocs} uses the second schedule in Line $15$). 
%Define $A_t$ as the minimum gain of \iocs when the algorithm visited time slots $1$ to $t$. More formally, $A_t=\sum_{i\in\mathcal{U}_{\iocs,t}}v_i$. $A_t$ is the minimum gain that \iocs will obtain by the end of time slot $t$, having the information of released demands up to time slot $t$. Notice that the algorithm may continuously improve its set of selected jobs to increase its gain such that $A_t\geq A_{t-1}, t\in\{2,\dots, T\}$. $A_t$ is formally defined as follows:

The following theorem characterizes the competitive ratio of the \iocs in a special case. 
\begin{thm}
\label{thm:iocscompetitive}
Let $\mathcal{A}$ be \ics in \iocs algorithm and $m=1$. Assuming that EVs are released in $b$ distinct groups where arrival time of EVs in each group are the same, the \iocs is $b\Big(1+\frac{p}{p-q}\frac{s}{s-1}\Big)$-competitive with optimal offline solution, where $p$ is the station peak and $q=\max_i k_i, i=1,\dots ,n$. 
\end{thm}

%\begin{thm}
%\label{thm:iocscomplexity}
%Let $\mathcal{A}$ be \ics in Line $1$ of \iocs. Then, the time complexity of the \iocs  is $O(n^2T)$. 
%\end{thm}

\vspace{-6mm}
\section{Simulation Results}
			\label{sec:simul}
%%%In this section, we report a summary of simulation experiments to evaluate the performance of the proposed algorithms.

						\begin{figure*}[t]	
				\centering
				\begin{subfigure}[b]{0.25\textwidth}
					\begin{center}
						\includegraphics[width=\textwidth]{V-N-M2.pdf}
						\caption{\revv{$m=2$}}
						\label{fig:V-N-M2}
					\end{center}
				\end{subfigure}
				\begin{subfigure}[b]{0.25\textwidth}
					\begin{center}
						\includegraphics[width=\textwidth]{V-N-M4.pdf}
						\caption{\revv{$m=4$}}
						\label{fig:V-N-M4}
					\end{center}
				\end{subfigure}% 	
				\begin{subfigure}[b]{0.25\textwidth}
					\begin{center}
						\includegraphics[width=\textwidth]{V-N-M8.pdf}
						\caption{\revv{$m=8$}}
						\label{fig:V-N-M8}
					\end{center}
				\end{subfigure}% 
				\caption{\revv{Comparison results for $2$, $4$, and $8$ CSs for fractional and integral revenue models.}} 
				\label{fig:V-N-M}
				\vspace{-3mm}
			\end{figure*}
%\subsection{Simulation Setup and Overview}
\textit{Simulation Setup and Overview:} We consider charging scheduling of EVs \revv{during a period of $12$ time slots of length $1$ hour (e.g., from $08$:$00$ to $20$:$00$)}. 
We gathered information of \revv{$12$} popular EV models in the market to use in the simulation. Each EV model is characterized by its battery capacity as shown in Table \ref{tb:models} and maximum charging rate. \revv{Tesla models can get charged with up to $100$ kW using Tesla super chargers. Also, all other models have rapid DC charging capability (up to $50$ kW) with CHAdeMO method. This setting for charging rates is in accordance with future DCFC systems that can have several fast DC chargers installed in the charging station.} 
%Battery capacity varies from \revv{$14$} kWh to \revv{$100$} kWh and the maximum charging rate from \revv{$3.3$} kW to \revv{$22$} kW. 
%As in \cite{Tang,Chen}, we assume that arrival times follow a Poisson distribution and parking times follow an exponential distribution.
% with the mean arrival and parking duration indicated in Table \ref{tb:a-d}. 
The peak intervals include $08$:$00$-$10$:$00$, $12$:$00$-$14$:$00$, and $18$:$00$-$20$:$00$ which is in accordance to NHTS survey~\cite{Santos, Tang}. \revv{The probability of arriving an EV in the peak hours is two times higher than the off-peak periods.
			Demands are uniform random values from 
			$[\frac{1}{2}U_i,U_i]$} where $U_i$ is the battery capacity for EV $i$ in Table~\ref{tb:models}. \revv{The deadline of each EV is set according to slackness parameter $s$ (with default value of $1.2$), its demand and maximum charging rate of the battery as $d_i=a_i+\lceil \frac{D_is}{k_i} \rceil -1$.} 
%			The minimum electricity cost is $\$0.11$ per kWh based on US national electricity price average~\cite{kWhcost}. In our setting, users can submit higher prices than the minimum price in order to ensure receive their requested demand. 
			\revv{EVs are assigned to different CSs randomly and given as input to the algorithms. The willingness to pay by each user for one kWh of power is a random uniform number from interval $[\frac{1}{2} z,\frac{3}{2}z]$ where $z=\$0.11$ is national average price of electricity in the US\cite{kWhcost}.}			
			%The default value of local peak constraint is \rev{$100$} kW and the global peak constraint is \rev{$200$} kW. We investigate the effect of this parameter in~\cite{alinia2017online}. 
			In the simulation, the results are plotted with $95\%$ confidence level and each point represents average result of $50$ random scenarios. Table \ref{tb:comparisons} explains the comparison algorithms \revv{including current implemented algorithm in Caltech ACN referred to as \iolp \cite{lee2016adaptive} and its adapted version for the fractional revenue model \folp. The \iolp and \folp algorithms runs as follows: at each time slot assume that there will be no further arrivals and solve the optimization problem (e.g., by commercial solvers) for the current set of EVs and their remaining demands. In Table \ref{tb:comparisons}, the letters ``\textsc{i}'', ``\textsc{f}'' and ``\textsc{o}'' in front of the algorithms' name refer to integral, fractional and online types, respectively.}

			The measured performance metrics are total revenue, percentage of EVs that received all their demand, and total peak. \revv{To calculate optimal solution in integral revenue model, we used Gurobi solver \cite{optimization2013gurobi}.}

\begin{table}[!t]
				\centering
				\caption{\revv{EV models and their battery capacity.}}
				\label{tb:models}\revv{
				\begin{tabular}{ | l| c | l| c |}
					\hline
					\textbf{Model} & \textbf{Battery} & \textbf{Model} & \textbf{Battery} \\ \hline\hline    
				Mitsubishi i-MiEV & $16$ kWh & Citroen C-Zero & $14$ kWh \\ \hline
				Peugeot iOn  & $16$ kWh & Honda Clarity & $25.5$ kWh\\\hline
				Hyundai Kona & $64$ kWh & Nissan LEAF & $40$ kWh \\ \hline
				Hyundai Ioniq & $28$ kWh & BMW i3 & $22/33$ kWh \\ \hline
				Tesla Model S/X  & $60/100$ kWh & Kia Soul EV  & $27$ kWh\\\hline
				\end{tabular}}
			\end{table}

%\begin{table}[h]
%				\centering
%				\caption{Arrival rates and mean parking times.}
%				\label{tb:a-d}
%				\begin{tabular}{ | l | c | c |}
%					\hline
%					\textbf{Interval} & \textbf{Arrival rate} & \textbf{Mean parking time} \\ \hline\hline    
%					$08$:$00$-$10$:$00$&  $14$&$10$\\\hline  
%					$10$:$00$-$12$:$00$&  $10$&$1/2$\\\hline 
%					$12$:$00$-$14$:$00$&  $20$&$2$\\\hline 
%					$14$:$00$-$18$:$00$&  $10$&$1/2$\\\hline
%					$18$:$00$-$20$:$00$&  $20$&$2$\\\hline
%					$20$:$00$-$24$:$00$&  $10$&$10$\\\hline
%					$24$:$00$-$08$:$00$&  $0$&$0$\\\hline
%				\end{tabular}
%\end{table}

\begin{table}[!t]
\centering
\caption{Acronyms for the algorithms}
\label{tb:comparisons}
\begin{tabular}{ | l| p{6cm}|}
\hline
\textbf{Notation} & \textbf{Description} \\ \hline\hline
\textsc{iOpt} & Optimal value under integral revenue model\\ \hline 	 
\ics & Proposed offline algorithm for \MCSP under integral revenue model\\ \hline
\fcs & Proposed \emph{optimal} algorithm for \MCSP under fractional revenue model\\\hline 
\iocs & Proposed online algorithm for \MCSP under integral revenue model\\ \hline
\focs & Proposed online algorithm for \MCSP under fractional revenue model\\ \hline
\iolp & Algorithm in \cite{lee2016adaptive} (works under integral revenue model)\\ \hline
\folp & Adaptation of algorithm in \cite{lee2016adaptive} for fractional revenue model\\ \hline
GreedyRTL & The algorithm in \cite{Jain} for single station scenario without global peak 			constraint (works under integral revenue model)\\\hline				
\end{tabular}
\end{table}
			%to simulate: Fig. 1 with M=1,4,8			
			\begin{figure*}[t!]	
				\centering
				\begin{subfigure}[b]{0.25\textwidth}
					\begin{center}
						\includegraphics[width=\textwidth]{v-c.pdf}
						\caption{\revv{Total revenue}}
						\label{fig:v-c}
					\end{center}
				\end{subfigure}%
				%\hspace{4mm}
				\begin{subfigure}[b]{0.25\textwidth}
					\begin{center}
						\includegraphics[width=\textwidth]{p-c.pdf}
						\caption{\revv{Actual global peak} 
%							($p^{\mathsf{total}}=480$)
}
						\label{fig:p-c}
					\end{center}
				\end{subfigure}%  
				%\hspace{4mm}
				\begin{subfigure}[b]{0.25\textwidth}
					\begin{center}
						\includegraphics[width=\textwidth]{acc-c.pdf}
						\caption{\revv{\% of full charged EVs}}
						\label{fig:acc-c}
					\end{center}
				\end{subfigure}% 				
				\caption{\revv{Comparison in terms of total revenue, actual peak, and percentage of fully charged EVs by varying local peak value}.} 
				\label{fig:peak_local}
			\vspace{-4mm}
			\end{figure*}
\textit{\revv{Evaluation Based on Total Revenue}:}
\revv{Fig. \ref{fig:V-N-M} depicts the comparison results based on total revenue under fractional and integral models} while the total number of EVs increases from \revv{$100$ to $250$} for $2$, $4$, and $8$ CSs. \revv{The local and global peak constraints are set to $50$ kWh and $200$ kWh, respectively.}

The proposed algorithms compared to the optimal offline solution of integral model ($\textsc{iOPT}$) and $\iolp$.%%% which is the running online algorithm in the Caltech ACN \cite{lee2016adaptive}. 
%The proposed algorithms for fractional revenue model, \fcs and \focs, are compared to fractional version of OLP algorithm (referred to as \folp), which is implemented in Caltech ACN  (see~\cite{alinia2017online} for details). 
Recall that \fcs is optimal offline solution. The notable observations  are  as  follows:  (i)  the  general  trend in scenario of Fig.~\ref{fig:V-N-M} is that  by increasing  the  number  of  EVs,  total  revenue  increases.  This is because with more number of EVs, the scheduler has more freedom to choose more valuable EVs. (ii)  as  explained in Section~\ref{sec:fractional}, under fractional charging model, better results are expected due to increased scheduling flexibility in CSs. According to the simulation data that we extracted from Fig.~\ref{fig:V-N-M}, the gain obtained by \fcs and \focs in Fig. \ref{fig:V-N-M} are respectively \revv{$12\%$ and $10\%$} more than the gain of the \ics and \iocs. (iii) \revv{In Fig. \ref{fig:V-N-M2} and Fig. \ref{fig:V-N-M4}, sum of the local peaks is less than or equal to the global peak while in Fig. \ref{fig:V-N-M8} this sum is two times greater than the global peak. Consequently, the total revenue significantly improved when the number of CSs is increased from $2$ to $4$ while there is a slight improvement from $4$ to $8$ CSs as the global peak constraint prevents the algorithms from charging more EVs.}
 (iv) in integral revenue model, the proposed \iocs algorithm acts significantly better than \iolp. In particular, \iocs improves \iolp by \revv{$38\%, 36\%$, and $32\%$} for $m=2$, $m=4$ and $m=8$, respectively. \revv{In fractional revenue model, however, there is a very slight difference between \focs and \folp.}
 %We highlight that \iocs (\focs) is also better choice in terms of the algorithm complexity compared to \iolp (\folp).
(v) \ics approximates \textsc{iOpt} by \revv{$97\%$, $94\%$, and $95\%$} for $m=2$, $m=4$, and $m=8$, respectively. On average, \iocs is \revv{$90\%$} of \textsc{iOpt} and, \focs is \revv{$94\%$} of its optimal offline solution, \fcs.  
(vi) finally, the results depict that \ics achieves much better results in practice as compared to the theoretical approximation ratio that characterizes the performance in worst-case scenario.

%Also, there is a sharp decline in the gap between the online methods (i.e., \focs and \iocs) and the offline solutions (i.e., \textsc{iOpt}, \ics and \fcs).

\revv{\emph{Comparison Based on Actual Peak:}} The constraint set in the \MCSP assures that any feasible solution respects the local and global peak constraints.
% i.e., at each time slot, the electricity consumed by station $j$ is less than or equal to $p_j$ and accumulative charging rate of all stations are less than or equal to $p^\mathsf{total}$ (note that there is no assumption that $\sum_j p_j\leq p^\mathsf{total}$, in general). 
An efficient scheduling algorithm may take a further step by not only satisfying the peak constraints but to further reduce the peak as much as possible. The proposed offline algorithms (i.e., \ics and \fcs) apply valley-filling policy to reduce the peak. The  online algorithms (i.e., \iocs and \focs) do not apply the same policy as they do not have future knowledge to be able to balance allocated resources. 
%Besides, due to uncertainties in future EV charging load in online scheduling design, it is a natural heuristic to charge EVs at earliest time.
% (i.e., setting the charging rates to the maximum feasible value at each time slot) as applied by \iocs an \focs. 
%This heuristic works well as the uncertainty in EVs' arrival time and demands may not give a second opportunity to the scheduler to charge the current EVs at the next slots. Therefore, although it is expected that \iocs and \focs have higher peak values compared to the offline algorithms, the idea of valley-filling can decrease their average response time.
% (see~\cite{alinia2017online} for the extended version of experiments).
To investigate the effect of employed valley-filling strategy, we conducted a set of simulations by varying local peak constraints. 
%from $50$ kWh to $120$ kWh and $200$ EVs. 
The results of \ics is compared to \iocs and GreedyRTL~\cite{Jain} where the latter is an approximation scheduling for single station scenario with EVs having same arrival time (see the explanations after formulating the \MCSP in Section \ref{sec:problem}). 
%The GreedyRTL algorithm works under integral revenue model. Therefore, results for \fcs and \focs are not plotted. 
%Since GreedyRTL assumes all EVs arrive at the same time, we set all arrival times to $1$. Moreover, we assume that global peak constraint is big enough (i.e., $\sum_{j=1}^m p_j\leq p^\textsf{total}$) such that the solution of GreedyRTL is feasible. We run GreedyRTL in each CS separately and combine the results. 
The results are shown in Fig.~\ref{fig:peak_local}.  
Along with total revenue in Fig.~\ref{fig:v-c}, we also report total \emph{actual} peak in Fig.~\ref{fig:p-c} and percentage of fully charged EVs in Fig.~\ref{fig:acc-c}. 
%As a high level trend, the results show that as the peak values increase, total revenue, total actual peak, and the number of EVs who received all their demand increase.  
In Fig. \ref{fig:v-c}, the results for \ics and GreedyRTL are almost identical while \iocs is \revv{$90\%$} of the other two algorithms, on average. When \revv{$p_j\geq 400$}, the total revenue for \ics and GreedyRTL does not increase in Fig. \ref{fig:v-c} and percentage of fully charged EVs is $100$ for both algorithms according to Fig. \ref{fig:acc-c}. From this point and onward, the scheduling is not challenging for offline methods to obtain optimal answer because of resource sufficiency. However, it is still a challenge to control total actual peak for the system. As a result of valley-filling policy, the value of actual peak of \ics in Fig. \ref{fig:p-c} remains almost unchanged for \revv{$p_{j}\geq 400$}.  \iocs and GreedyRTL, however, continuously increase the peak demand, since they are not using any peak shaving approach.
% and only try to maximize total revenue. 
%According to Fig. \ref{fig:p-c}, \iocs always reaches to the maximum peak of $\sum_j p_j$.

%A glance at Table \ref{tb:models} shows that in general, an EV needs a minimum time of $2$ hours to get $70\%$ of its battery capacity if charging rate is set to the maximum value. However, CSs are allowed to preempt the charging at any time and set charging rate any value lower than the maximum rate. Therefore, average response times can be higher as it can be seen in Fig. \ref{fig:rt-c}.

%\begin{figure}[t]	
%\centering
%				\begin{subfigure}[b]{0.25\textwidth}
%					\begin{center}
%						\includegraphics[width=\textwidth]{v-s-method1.pdf}
%						\caption{Total revenue (\$)}
%						\label{fig:v-s-method1}
%					\end{center}
%				\end{subfigure}%				
%				\begin{subfigure}[b]{0.25\textwidth}
%					\begin{center}
%						\includegraphics[width=\textwidth]{rt-s-method1.pdf}
%						\caption{Response time (hr))}
%						\label{fig:rt-s-method1}
%					\end{center}
%				\end{subfigure}%  
%\caption{The impact of slackness parameter on total revenue and response time when users react by adjusting their demand.} 
%\label{fig:slackness1}
%\end{figure}

%\subsection{The Impact of Slackness Parameter}
%\label{sec:sim:slack}
%This section discusses on the benefits and disadvantages that can be brought by using slackness parameter. To give the charging scheduler more flexibility, a slackness parameter $s\geq 1$ is used and set by the system designer. 
%Recall that charging profile of EV $i$ is feasible if $D_i\leq k_i\frac{d_i-a_i+1}{s}$ holds. Since users have no control on the slackness parameter and the maximum charging rate, they must adjust their demand and availability according to the imposed slackness value. Based on the charging profile feasibility equation, when the slackness value increases users have two choices to react: (i) decrease the demand and depart at the desired deadline or, (ii) extend the deadline and receive the desired demand. In the remaining of this section, we investigate the effects of either case by simulation. To have a clear picture of effects caused by slackness parameter, we generated $100$ initial charging profiles $\langle a_i,d_i,v_i,D_i,k_i\rangle$ for $100$ EVs randomly and uniformly chosen from $10$ different models in Table \ref{tb:models} such that the initial profiles are set up assuming that the CS allows the charging operations to be finished at earliest possible time (i.e., $\frac{D_i}{k_i}$) with $s=1$. For each EV, its demand is randomly chosen from $25\%$ to $100\%$ of its battery capacity and departure in  interval $[a_i+\frac{sD_i}{k_i},T]$, where $a_i+\frac{sD_i}{k_i}$ is the earliest feasible deadline. Then, the EVs are uniformly assigned to $4$ CSs and should choose one of the above strategies to submit a feasible demand according to imposed slackness. 
%\begin{figure}[t]	
%\centering
%							\begin{subfigure}[b]{0.234\textwidth}
%								\begin{center}
%									\includegraphics[width=\textwidth]{v-s-method2.pdf}
%									\caption{Total revenue (\$)}
%									\label{fig:v-s-method2}
%								\end{center}
%							\end{subfigure}%
%							\hspace{1mm}
%							\begin{subfigure}[b]{0.236\textwidth}
%								\begin{center}
%									\includegraphics[width=\textwidth]{rt-s-method2.pdf}
%									\caption{Response time (hr)}
%									\label{fig:rt-s-method2}
%								\end{center}
%							\end{subfigure}% 
%							
%\caption{The impact of slackness parameter on total revenue and response time when users react by adjusting their deadline.} 
%\label{fig:slackness2}
%\end{figure}
%			
%\subsubsection{Case I- Adjusting Demands}
%In this case, if the initial charging profile of an EV does not reflect a feasible charging request based on the slackness parameter, the EV owner decreases its demand so it will be able to leave CS at its initial desired deadline. Note that the valuation of EVs decreases proportionally, as well. Fig.~\ref{fig:slackness1} depicts the result under this policy applied by users. As it can be seen in Fig. \ref{fig:v-s-method1} and Fig. \ref{fig:rt-s-method1}, the general trend is that both total revenue and average response time decrease when slackness value increases. This is justifiable based on users reaction. When users decrease their demand, less electricity is sold which results in less revenue. When total demand decreases, charging can be finished in shorter time which decreases response time. Therefore, if users choose the first policy (adjusting their demand), total revenue degrades while response time improves. Notice that for the algorithms working under integral revenue model (i.e., \textsc{iOPT}, \ics and \iocs) the total revenue increases with slackness parameter at first (when $s$ grows from $1$ to $1.4$) but then it decreases when the slackness increases more (for $s>1.4$). 
%In our view, this happens because increasing the slackness in integral revenue model makes it possible to \emph{fully} charge more EVs at the beginning as the demands decrease. However, when the slackness increases more, it results in opposite effect because the valuation of demands decreases along with the demands' size.	
%			\subsubsection{Case II- Adjusting Deadlines}
%			In this case, we assume that users are reluctant to decrease their desired demands. Instead, they can extend their departure. In Fig.~\ref{fig:slackness2} it can be observed that under this behavior of the users, the results are opposite as compared to the previous case (Fig.~\ref{fig:slackness1}). When deadlines are extended without demand decrement, the scheduler has more chance to compliance the demands through improved scheduling flexibility. Consequently, the total revenue increases by increasing slackness value while average response time degrades. 
%%Also observe the behavior of the online algorithms (i.e., \iocs and \focs) where both total revenue and response time decrease after a specific point that is $s=1.8$. When deadlines extend, more EVs have the opportunity of getting charged	
%					
%We can conclude that when total revenue is more important than the response time, the CS should impose small values of slackness for users that apply the policy of the first case and impose higher values of slackness for the users that apply the second policy. The conclusion is reverse for the case that the objective is to have lower response times.

			%In fact, the slackness parameter controls the maximum demand or earliest deadline that an EV can submit to the system. Remember that demands are in interval $[\textrm{min}\{\frac{d_i-a_i}{sk_i},U_i\},U_i]$ for EV $i$ meaning that the maximum demand that an EV can submit decreases by increasing slackness parameter. A reduction in total demand result in lower charging costs. Therefore, the total revenue decreases with higher values of parameter $s$ as in Fig. \ref{fig:v-s}. 
			%Also, the percentage of EVs that received all of their requested demand increases based on the same fact. The main goal of this simulation is to observe that obtained theoretical result on approximation ratio is confirmed as optimality gap of the SCS algorithm reduces by increasing $s$ in Fig. \ref{fig:v-s}. 
\vspace{0.1mm}
\vspace{-4mm}
			\section{Conclusion}
			\label{sec:conclusion}
This paper proposed offline and online algorithms for the EV charging scheduling problem under fractional and integral revenue models in an adaptive charging network (ACN). The problem is different, and more challenging than the existing single station EV charging scheduling problems since it requires respecting the aggregate peak charging demand of the ACN. 
%More importantly, the problem is online in nature in the sense that the EVs arrive in time and the scheduler has no information regarding future arrivals. 
As the notable contributions, our proposed online algorithm for fractional revenue model achieves constant competitive ratio of $2$. Moreover, the offline integral algorithm achieves a theoretical bound on the optimality gap and approximates the optimum by $92\%$, on average in experiments. As a future work, we plan to study the problem under posted pricing mechanism where the charging station publishes the unit price of the power (which can be varied over time) and the users can accept or reject the offer.
\revv{Another interesting future direction is to tackle the EV charging scheduling in market-based scenarios where the prices change over time.}
%As a future work, we plan to analyze the truthfulness of the algorithms to make sure that it is a dominant strategy for the EV owners to declare their true valuations and availabilities.
\vspace{-4mm}

%\input{intro.tex}
%\input{rel.tex}
%\input{sys.tex}		
%\input{fraction.sol.tex}		
%\input{integral.sol.tex}
%\input{exp.tex}
%%%\vspace{0.1mm}
%\input{conc.tex}
%\newpage
%ss
%\newpage
%\pagestyle{empty}
\bibliography{ref}{}
\vspace{-2.8mm}
\bibliographystyle{ieeetr}

\input{app.tex}

\begin{comment}
\vspace{-10mm}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{alinia.jpg}}]{Bahram Alinia} received a B.Sc degree in computer science from University of Tabriz, Tabriz, Iran and a masters degree in Information Technology Engineering from University of Tehran, Tehran, Iran. He was a Researcher with the School of Computer Science, Institute for Research in Fundamental Sciences, Iran, from 2009 to 2012. He is currently a Ph.D. student in service architecture lab, Institute Telecom SudParis, France and participated in several European projects in the domain of smart grids. His research area includes wireless communications, energy systems, transportation electrification, algorithm design and approximation.
\end{IEEEbiography}
%\vspace{-30mm}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{hajiesmaili.jpg}}]{Mohammad H. Hajiesmaili} received the B.Sc. degree from the Department of Computer Engineering, Sharif University of Technology, Iran, in 2007, and the M.Sc. and Ph.D. degrees from the Electrical and Computer Engineering Department, University of Tehran, Iran, in 2009 and 2014, respectively. He was a Post-Doctoral Fellow with the Department of Information Engineering, the Chinese University of Hong Kong, from 2014 to 2016, and with the Department of Electrical and Computer Engineering, Johns Hopkins University, form 2017 to 2018. He is currently a Research Assistant Professor with the College of Information and Computer Sciences, University of Massachusetts, Amherst. His research interests include optimization, algorithm, and mechanism design in energy systems, electricity market, transportation networks, and multimedia networks.
\end{IEEEbiography}
%\vspace{-30mm}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{crespi.jpg}}]{Prof. No\"{e}l Crespi} holds Masters degrees from the Universities of Orsay (Paris 11) and Kent (UK), a diplome d'ing\'{e}nieur from Telecom ParisTech, a Ph.D and an Habilitation from UPMC (Paris-Sorbonne University). From 1993 he worked at CLIP, Bouygues Telecom and then at Orange Labs in 1995. He took leading roles in the creation of new services with the successful conception and launch of Orange prepaid service, and in standardisation (from rapporteurship of IN standard to coordination of all mobile standards activities for Orange). In 1999, he joined Nortel Networks as telephony program manager, architecting core network products for EMEA region. He joined Institut Mines-Telecom in 2002 and is currently professor and Program Director, leading the Service Architecture Lab. He coordinates the standardisation activities for Institut Mines-Telecom at ITU-T and ETSI. He is also an adjunct professor at KAIST (South Korea), an affiliate professor at Concordia University (Canada), and gest researcher at the University of Goettingen (Germany). He is the scientific director the French-Korean laboratory ILLUMINE. His current research interests are in Data Analytics, Internet of Things and Softwarisation.
http://noelcrespi.wp.tem-tsp.eu/
\end{IEEEbiography}	
\end{comment}
\end{document}

### 2019-08-25 TSC/R1/res.tex
adding more responses

@@
 %\usepackage{subfigure}
+\usepackage{subfig}
 %\usepackage{flushend}
@@
 
-\usepackage[caption=false,font=footnotesize]{subfig}
+%\usepackage[caption=false,font=footnotesize]{subfig}
 %
@@
 
+{\color{red} @Mohammad: I have an implementation for WFAIR algorithm which almost similar to FOCS in this paper. I can update it and add FOCS implementation as well. 
+Then we can refer to it as a sample implementation for our algorithms. The algorithm code is 
+here: https://github.com/bahramalinia/EV-Scheduling.git}
+
 \vspace{3mm}
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
-...
+The constraint (1d) applies on each time slot $t$ for each EV $i$ and enforces respecting maximum charging rate at each $t$ for all $i$.
+The constraint say nothing about the relation between charging rates at different slots (including forcing them to be equal).
 
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
-...
+We added an example in Page xx to demonstrate why the simple approach mentioned by the reviewer is not optimal.
+
+{\color{red}@ Mohammad: I copied the following from TSG response letter. We can update and add it to the paper.}
+
+The proposed approach by the reviewer is a popular, yet straightforward method in the online scheduling.
+However, it turns out that this approach cannot provide an optimal solution to the problem even in fractional revenue model.
+In fact, this approach only provides a 2-competitive solution.
+i.e., the profit obtained by this approach would be $1/2$ of the optimum.
+We bring an example to clarify.
+
+Fig.
+\ref{fig:1a} shows a simple scenario in a single charging station with $T=2$ and $p_1=p^{\text{total}}=1$.
+The charging profile of an EV $i$ is shown in the form of $\pi_i=(a_i,d_i,v_i,D_i,k_i)$ where it is assumed that $k_i=1$ for all $i$.
+At $t=1$, EVs 1 and 2 arrive and the scheduler has no information about the future coming EVs.
+If we run an optimal offline algorithm over the available EVs at $t=1$, it will allocate EV 2 at $t=1$ and postpone charging of EV 1 to $t=2$ according to their deadline.
+Now assume that EV 3 arrives at $t=2$ which has the same demand and unit value as EV 1 (see Fig.
+\ref{fig:1b}).
+Then, by re-computing the optimal solution at $t=2$, the solution is to choose either EV 1 or EV 3 to charge due to capacity constraint.
+Therefore, the final solution obtained by this approach achieves a total revenue of $1+\epsilon$ by charging EVs 2 at $t=1$ and one of the EVs 1 or 3 at $t=2$.
+However, the optimal solution in this example is charging EV 1 at $t=1$ and EV 3 at $t=2$ and obtaining a gain equal to 2.
+This example shows that the competitive ratio of the proposed approach by the reviewer cannot be better than $2-\epsilon$ where $\epsilon$ can be arbitrarily small.
+
+\begin{figure}
+\centering     %%% not \center
+		\subfloat[{EVs $1$ and $2$ arrive at $t=1$.}]{\label{fig:1a}\includegraphics[width=60mm]{Ex1a.pdf}}
+		\hspace{8mm}
+		\subfloat[{EV $3$ arrives at $t=2$.}]{\label{fig:1b}\includegraphics[width=60mm]{Ex1b.pdf}}
+\caption{Worst case scenario when the scheduling algorithm is to re-run an optimal algorithm at each time slot considering only available EVs.
+Dotted line indicates a time slot that is not visited yet and the scheduler has no information about the arriving EVs in that slot.
+The numbers inside parentheses indicate arrival time, deadline, value, demand and maximum charging rate of the EV, respectively.}
+\label{fig:1}
+\end{figure}
 
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
-...
+We agree and this is unfortunately consequence of space limit. To avoid confusion, we added an explanation in Page xx, when describing the results.
 
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
-...
+{\color{red} I should check these papers and add to Related Work if needed.}
 
 \vspace{3mm}
-{\color{blue} The authors claim that if prediction or modelling techniques were used, the performance of the proposed algorithms would deteriorate.
+{\color{blue} The authors claim that if prediction or modeling techniques were used, the performance of the proposed algorithms would deteriorate.
 However, they do not present any results to support their claim.
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
-...
+{\color{red}: This refers to : "The prediction-based approaches achieve satisfactory
+performance for the scenarios that follow prediction. Deviation
+from prediction models, however, degrades their performance.
+Our approach, on the other hand, has no assumptions on
+modeling/prediction, and in this way, is robust against any
+uncertainty in the instances to the problem."}
 
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
-...
+Although this can be an interesting extension, we assumed that in a real scenario, a user chooses only one CS to ask for its demand and may drive to another CS if its demand is not fulfilled.
 
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
-...
+This is an important and interesting point raised by the reviewer. Although we did not study the case for self interested users in this paper, we addressed it in our recent work:
+
+B. Alinia, M. H. Hajiesmaili, and N. Crespi, "Online EV Charging Scheduling with On-Arrival Commitment", IEEE Trans. on Int. Trans. Systems, 2019.
+
+In the above cited paper, we propose "SCOMMIT" algorithm where its core allocation idea is based on users' unit-values except that it also provides on-arrival commitment.
+Since it is proved that SCOMMIT is truthful, we believe that among the proposed algorithms in current manuscript, the FOCS is truthful.
+
+{\color{red} If verified, need to add something in the paper to highlight this}
 
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
-...
+The length of the time slot can be arbitrary set in the algorithms.
+The derived complexities of the algorithms in the paper include parameter $T$ as number of time slots in a day (please see Table xx in the manuscript).
+In large scale scenarios, the effect of increasing $T$ would be negligible in performance of the algorithms as long as it $T/N$ is a constant ($N$ is number of EVs).
+Therefore, when $N$ grows large and $T$ is a constant, $T$ can be removed from the complexities in the Table xx.
+
+Another point is that in real electricity market prices are only allowed to be changed hourly which is the reason most power scheduling algorithms work with one-hour slots.
 
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
-...
+TBD
 

### 2019-08-26 TSC/R1/res.tex
MH-Update1

@@
 
-\title{Response Letter for manuscript TSG-01885-2017 ``Online EV Scheduling Algorithms for Adaptive Charging Networks with Global Peak Constraints'' \\
+\title{Response Letter for manuscript TSUSC-2018-12-0140 \\ ``Online EV Scheduling Algorithms for Adaptive Charging Networks with Global Peak Constraints'' \\
 	\vspace{4mm} \large
@@
 \noindent\textbf{Response:}
+In the revised version, we further clarified the significance of the theoretical results.
+Even though some assumptions are made for the theoretical analysis of the proposed algorithms, we note two important significance of our results: \textit{First}, the algorithms work effectively in practice as demonstrated in real-world trace-driven experiments, for the general cases without those assumptions; and \textit{secondly}, the theoretical analysis of underlying mathematical problems in the general setting are extremely challenging problems in the theoretical computer science literature, in particular, job scheduling problems.
+To the best of our knowledge, there is no deep theoretical understanding of online algorithms for the general setting of this problem.
+In the revised manuscript, we added a subsection, in Section II, and highlighted the theoretical significance of our paper.
+
+In addition, in the paper, we clearly distinguished between the results in this paper and our previous conference paper on IEEE/ACM IWQoS 2018.
+Our work in this paper considers more general problem formulation, with global peak constraints, and a comprehensive revenue model.
+The developed algorithms in Section V, for the integral revenue model, are new in this work.
+Finally, the trace-driven experimental results are more extensive in this paper and provide comparisons with an algorithm that are currently in use in a real-world charging station.
+
+We highlighted both of the revisions in the revised manuscript and also addressed several other comments that are proposed by the reviewers.
 
@@
 Although the presented algorithms in the conference version provide a competitive ratio of $2-1/U$ (with $U$ as "scarcity level"), the proof holds when all EVs have the same maximum charging rate.
-In the current study, we consider hetregenousity in this parameter and prove the online algorithm is 2-competitive.
+In the current study, we consider heterogeneity in this parameter and prove the online algorithm is 2-competitive.
 
-To clarify this, we added an explanation in Section ...
+\textit{To clarify this, we added an explanation in Section ...
+@Bahram: please add a subsection in Related work and explain IWQoS and other theoretical papers.
+This is the most important task for this revision.
+}
 
@@
 
-$\vartriangleright$ \noindent\textbf{Response:} 
-...
+$\vartriangleright$ \noindent\textbf{Response:} We note that the underlying problem in the integral model is an NP-hard problem, which makes it challenging to design a good approximation algorithm even for the offline version of the problem.
+Hence, designing online algorithms for the integral setting is fundamentally more challenging than the fractional case.
+Our work is among the first few works in the direction of developing competitive online algorithms for combinatorial optimization problems.
+While we admit that there are some assumptions for the theoretical analysis, we further highlight that the algorithms work effectively in practice as demonstrated in real-world trace-driven experiments, for the general cases without those assumptions.
+Furthermore, the theoretical analysis of underlying mathematical problems in the general setting are extremely challenging problems in the theoretical computer science literature, in particular, job scheduling problems.
+To the best of our knowledge, there is no deep theoretical understanding of online algorithms for the general setting of this problem.
+Note that ICS works for multiple station, which is different from the existing work, however, the analysis in Theorem 5, restricts the analysis of this general multiple station to one station.
+Last, the result in Theorem 4, is the best known competitive result for this setting, and considering the complexity of the online combinatorial problem, it would be a very challenging task to improve this result.
 
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
-{\color{red}@Mohammad: We should try to distinguish our work from Yao et al. but it seems difficult.}
+The current experiments (i) shows the effect of problem parameters, including the number of charging stations and number of vehicles (in Figure 2), and the impact of peak constraint and demand (in directly) (in Figure 3).
+The impact of arrival and departure times could be interpreted as more/less flexibility in charging scheduling.
+Our result in Figure 3, indeed, investigates the impact of flexibility in charging scheduling.
+
+Our work is substantially different from Yao et al.
+(2017), since the authors consider an offline scenario for managing EV charging scheduling.
+The proposed algorithm in their work is an offline algorithm based on convex relaxation of the underlying combinatorial problem.
+They assume that all the required information for decision making is available in advance.
+Our work, in contrast, tackle another version of EV charging scheduling with global peak constraints.
+\textit{The significance of our work is to consider the online setting in which the input to the problem arrives over time, and develop algorithms that are provably efficient against this uncertainty of the system.} As for comparison, we compared our results with the offline optimal solution (that is equivalent to the optimal solution of the problem studied in Yao's paper without demand-response constraints).
+In the results reported in Figure 3, we have reported the results of offline optimal as \textsc{iOPT}.
 
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
-We listed pseudo-codes for all proposed algorithms and an interested reader can easily convert them to real implementation code.
-We believe that detailed implementation of the algorithms has no added value as the goal here is to provide algorithms and analysis and not focusing on programming challenges.
-
-{\color{red} @Mohammad: I have an implementation for WFAIR algorithm which almost similar to FOCS in this paper. I can update it and add FOCS implementation as well. 
-Then we can refer to it as a sample implementation for our algorithms. The algorithm code is 
-here: https://github.com/bahramalinia/EV-Scheduling.git}
+We listed pseudo-codes for all proposed algorithms (Algorithm 1-7) in the main body of the paper.
+Despite the technical challenges in the analysis, the main body of the algorithms are fairly simple and an interested reader can easily convert them to real implementation code.
+Last, we have provided some sample code implementations of our algorithms in
+%We believe that detailed implementation of the algorithms has no added value as the goal here is to provide algorithms and analysis and not focusing on programming challenges.
+here: https://github.com/bahramalinia/EV-Scheduling.git
 
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
-Thanks for the point. We agree that our problem is strongly NP-Hard and we corrected the related phrases in the manuscript.
+Thanks for the point. We agree that our problem is strongly NP-Hard and we corrected the related phrases in the manuscript. Please see Page ?? of the revised manuscript.
 
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
+Thanks for suggesting the related works. In the revised version we added all of them as well as several more recent papers, that are highlighted in blue.
+
 {\color{red} I should check these papers and add to Related Work if needed.}
@@
 \vspace{3mm}
-{\color{blue} The authors claim that if prediction or modeling techniques were used, the performance of the proposed algorithms would deteriorate.
+{\color{blue} 2.
+The authors claim that if prediction or modeling techniques were used, the performance of the proposed algorithms would deteriorate.
 However, they do not present any results to support their claim.
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
-{\color{red}: This refers to : "The prediction-based approaches achieve satisfactory
-performance for the scenarios that follow prediction. Deviation
-from prediction models, however, degrades their performance.
-Our approach, on the other hand, has no assumptions on
-modeling/prediction, and in this way, is robust against any
-uncertainty in the instances to the problem."}
+This refers to the following statement in the Related Work: "The prediction-based approaches achieve satisfactory performance for the scenarios that follow prediction.
+Deviation from prediction models, however, degrades their performance.
+Our approach, on the other hand, has no assumptions on modeling/prediction, and in this way, is robust against any uncertainty in the instances to the problem."
+
+The above statement provides a high-level difference between prediction-based approaches and our competitive online algorithm design approach.
+Since our approach does not rely on any predicted future information, we are robust against any type of uncertain input to the problem.
+In contrast, the developed algorithms in prediction-based approaches rely on the quality of prediction, and if the quality of prediction is weak, their performance also degrades.
+An interesting future direction of our work, based on this comment, is to extend our \textit{pure} online algorithms with a limited predicted future values.
+In this way, not only the algorithms are robust against uncertainty, their performance in practice can be improved with some future data.
 
 \vspace{3mm}
-{\color{blue} An interesting extension would be to let users define a set of CSs to charge and let the scheduling algorithms take the final decision of the CS to charge.
+{\color{blue} 3.
+An interesting extension would be to let users define a set of CSs to charge and let the scheduling algorithms take the final decision of the CS to charge.
 In this way, the flexibility of the algorithms would increase and the load across the CSs could be better managed.
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
-Although this can be an interesting extension, we assumed that in a real scenario, a user chooses only one CS to ask for its demand and may drive to another CS if its demand is not fulfilled.
+Although this can be an interesting extension, in this version, we assumed that a user chooses only one CS to ask for its demand and may drive to another CS if its demand is not fulfilled.
+We admit that this suggestion is a very elegant extension from the perspective of theoretical problem formulation and algorithm design, and makes the scenario more challenging.
+In addition, this suggestion makes more sense in scenarios in which EVs are heterogeneous and a subset of chargers can satisfy a subset of EVs.
+We do believe that this is an very interesting scenario to consider, however, as mentioned by the reviewer, it increases the complexity of designing and analysis of the algorithms, and is beyond the scope of this submission.
 
@@
 If not, this could come in contrast with the revenue maximization objective function.
-Moreover, this would cause serious implications in the online algorithms which use the valuations to select the EVs to charge.
-}
+Moreover, this would cause serious implications in the online algorithms which use the valuations to select the EVs to charge.}
 \vspace{3mm}
@@
 
-B. Alinia, M. H. Hajiesmaili, and N. Crespi, "Online EV Charging Scheduling with On-Arrival Commitment", IEEE Trans. on Int. Trans. Systems, 2019.
+B. Alinia, M. H. Hajiesmaili, and N. Crespi, "Online EV Charging Scheduling with On-Arrival Commitment", \textit{IEEE Trans. on Int. Transportation Systems (ITS)}, 2019.
 
@@
 Since it is proved that SCOMMIT is truthful, we believe that among the proposed algorithms in current manuscript, the FOCS is truthful.
+In the above paper, also, we tackled another desirable property to commit EVs on their arrival on how much they can get charged during their available window.
 
-{\color{red} If verified, need to add something in the paper to highlight this}
+The focus of this paper, in on more comprehensive online algorithm design for fractional and integral revenue models, and for our ITS paper, we focused on truthfulness and on-arrival commitment.
+It is worth noting that developing solutions that provide competitiveness against offline optimal versus those that provide truthfulness and on-arrival commitment, needs different algorithmic techniques and tools.
+As a notable result, an interesting theoretical observation in our ITS shows that there is no online algorithms that can simultaneously provide on-arrival commitment and bounded competitive ratio.
+See Section 6 and Theorem 5 of our ITS paper for more details.
 
 \vspace{3mm}
-{\color{blue} The length of each time point is set to 1 hour.
+{\color{blue} 5.
+The length of each time point is set to 1 hour.
 This is too long, and the accuracy of the algorithms is reduced.
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
-The length of the time slot can be arbitrary set in the algorithms.
-The derived complexities of the algorithms in the paper include parameter $T$ as number of time slots in a day (please see Table xx in the manuscript).
+The length of the time slot can be arbitrary set in the algorithms and we used 1 hour in experiments since the availability window of our traces was in one hour slots.
+With more fine grained data, it would be possible to run the algorithms in faster timescales, e.g., 5 minutes or so.
+
+We note that the derived complexities of the algorithms in the paper include parameter $T$ as number of time slots in a day (please see Table II in the manuscript).
 In large scale scenarios, the effect of increasing $T$ would be negligible in performance of the algorithms as long as it $T/N$ is a constant ($N$ is number of EVs).
-Therefore, when $N$ grows large and $T$ is a constant, $T$ can be removed from the complexities in the Table xx.
+Therefore, when $N$ grows large and $T$ is a constant, $T$ can be removed from the complexities in the Table II.
 
-Another point is that in real electricity market prices are only allowed to be changed hourly which is the reason most power scheduling algorithms work with one-hour slots.
+%Another point is that in real electricity market prices are only allowed to be changed hourly which is the reason most power scheduling algorithms work with one-hour slots.
 
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
-TBD
+The complexity of the algorithms are low and we just set the charging rate by a simple sorting on arrival of each EV. \textbf{Bahram, please confirm.}
 

### 2019-08-26 TSC/R1/TSC.tex
updating related works

@@
 }
+
+\subsubsection{Worst case analysis in EV scheduling}
+\label{sec:rel:comp}
+\bt{
+The performance of an approximation algorithm is determined by its \emph{approximation ratio} for offline 
+algorithms and \emph{competitive ratio} for online algorithms which compare the algorithm's result to optimal solution. 
+Under integral revenue model, \cite{jain2015near} proposes an offline algorithm for scheduling of batch jobs in cloud computing which is equivalent to EV scheduling problem.
+It is assumed that all jobs are available to be processed at time 0.
+The authors propose a $\frac{C}{C-k}.\frac{s}{s-1}$-approximation algorithm where $C$ is the cloud capacity and $s$ is a ``slackness'' parameter.
+Similarly, \cite{yao2016real} tackles the offline integral problem and proposes a convex relaxation method to find a near-optimal solution.
+No theoretical bound is provided for the algorithm and the performance is examined by simulation results.
+In this paper, we propose \ics for the same problem and provide competitive ratio under specific scenarios.
+In case of fractional revenue model (for offline case), the scheduling problem is by far easier to tackle.
+For example, in this paper we propose \fcs as an optimal solution for offline fractional case.
+
+In online scenarios, the scheduling problem is more challenging. In our recent study \cite{alinia2018competitive}, 
+we proposed two online algorithms referred to as WFAIR and WRAND for EV scheduling problem.
+The proposed algorithms provide a competitive ratio of $2-1/U$ where $U$ is "scarcity level".
+However, \cite{alinia2018competitive} the result only holds when all EVs have the same maximum charging rate.
+Also, \cite{alinia2018competitive} does not study the integral revenue model.
+In this paper, we propose \focs as a 2-competitive online algorithm with no assumption on the input parameters.
+Also, current study investigates both fractional and integral revenue model while considering total peak constraint in the formulation and addressing multiple charging station scenario.
+~\cite{firstfit} proposes two simple and natural online algorithms called \textsc{FirstFit} and \textsc{EndFit} where both are proved to be 2-competitive.
+\focs is extension of these algorithms by taking into account the maximum charging rate of the EVs and multiple charging station scenario (see ``Remarks'' at Section IV).
+As recent studies, \cite{zheng2016online,deng2016whether} provide online algorithms for EV scheduling problem
+
+When online scenario is considered under integral revenue model, the scheduling problem becomes severely difficult and challenging.
+We note that the integral scheduling problem is strongly NP-Hard even in the offline case \cite{de2018complexity}.
+There are very limited studies in this category.
+\cite{lucier2013efficient} provides an online algorithm without considering the maximum processing rate of the jobs where its competitive ratio can be arbitrary bad depending on ``slackness'' parameter'.
+The slackness parameter also appears in our proposed online solution for integral revenue model, \iocs for multiple station scenario where maximum charging rate of the EVs is taken into account.
+}
+
 \section{System Model and Problem Formulation}

### 2019-08-26 TSC/firstSubmit/TSC.tex
updating related works

--- 2019-08-25 TSC/R1/TSC.tex
@@
 \usepackage{color,soul}
-%\usepackage{ragged2e} 
+\usepackage{ragged2e} 
 \usepackage{algorithmicx}
@@
 \ifodd 1
-\newcommand{\bt}[1]{{\color{blue}#1}}%revise of the text
 \newcommand{\rev}[1]{{\color{black}#1}}%revise of the text
@@
 \else
-\newcommand{\bt}[1]{#1}
 \newcommand{\rev}[1]{#1}
@@
 
-Before discussing the details of the algorithm, we give \bt{a definition} and introduce some notations to facilitate our algorithm design.
+Before discussing the details of the algorithm, we give a definitions and introduce some notations to facilitate our algorithm design.
 
@@
 
-\emph{Dual Feasibility of the Non-selected EVs:} \bt{If remaining power resource is not enough} to fully charge EV $i$, i.e.,  $D_i>\sum_{t=a_i}^{d_i}\sigma_t$, the EV cannot be selected.
+\emph{Dual Feasibility of the Non-selected EVs:} If there is not enough resources to fully charge EV $i$, i.e.,  $D_i>\sum_{t=a_i}^{d_i}\sigma_t$, the EV cannot be selected.
 However, we still need to satisfy constraint~\eqref{ConstDcover} in dual problem which is done by calling \bc($i$).

### 2019-08-26 TSC/firstSubmit/app.tex
updating related works

\appendix
%\vspace{-3mm}
\begin{comment}
\subsection{Related Work}
\label{sec:rel}

\subsubsection{Peak-Constrained EV Charging Scheduling}
\label{sec:rel:peakconstrained}			
There is an extensive literature on EV scheduling problem where most of them focused on single CS \cite{Tang,Wen} and the local and global peak constraints are usually omitted or only the local peak is considered.	As discussed in Section \ref{sec:problem}, the global optimal solution cannot be obtained by separately solving the single station problems. Hence, those solutions cannot be directly applied to our problem.

A scenario that local and global peak constraints exist is the case that 
scheduling is required for a charging network for multiple CSs. Studies in \cite{He,Malhotra,Moradijoz,DWang,Zeng,Shaaban} addressed charging scheduling problem in multiple CSs. The authors in~\cite{He} tackled a global EV charging scheduling problem in a system consisting of a central controller and multiple local controllers to minimize total cost. However, there is no limit on the maximum peak demand that the system can tolerate. Consequently, the peak value can be arbitrary high depending on the total demand. 
This may increase the electricity bill of large costumers substantially mainly due to very high peak demand. In addition, high EV penetration level leads to high peak which may pose danger for the grid system \cite{DWang}. Besides, the charger devices installed in the CSs have limitation on the maximum power that they can transfer in each time unit~\cite{Tesla}. We solve the issue by constraining local and global peaks. However, to meet the peak constraints, it may not be feasible to respond to all charging demands. Consequently, only a subset of EVs can be charged~\cite{Xiang}, which is captured in our integral charging model. \cite{DWang} considered a multi-microgrid system with global peak constraint where each microgrid has a CS and the goal is to minimize the operating cost of the system and the exchanged electricity between microgrids and main grid. The authors assume that charging aggregators are able to forecast required information about individual EVs which may not represent a real scenario. A similar assumption is made in \cite{Zeng,Shaaban} where the objective is to maximize total utility of EVs and aggregators in a distribution network.

%\rev{To be removed: In our solution, we applied a priority based selection process (based on the EVs' valuation) to respond to the demands to make sure that total peak respects the constraints. The selection process can be made based on different criteria such as the value of each charging request \cite{Lee, Xiang} or the priority.}

			To avoid big billing cost in peak hours, \cite{Moradijoz} proposed a solution based on genetic algorithm to find optimal capacity and location of parking lots for serving demands in peak hours with the goal of maximizing total benefit of all stations. Although authors studied the problem under multiple CS setting, their solution is not applicable to our setting when the CSs are already set up. \cite{Malhotra} employed a similar model used in this paper, where both local and global peak constraints in a charging network are considered. The objective in \cite{Malhotra} is to maximize user convenience level which is different from the aim of the problem studied in this work. More importantly, the authors solve the single-slot problem, which fails to provide a general solution taking into account EVs' arrival and departure times which are considered in our study.
%			\subsection{Peak-minimizing EV Charging Scheduling}
			As an alternative approach to control the peak, some studies directly targeted minimizing the peak \cite{Zhao, Karfopoulos}. In \cite{Zhao}, an online algorithm is developed for EV charging to minimize the peak by minimizing the impact uncertainty of renewable energies. \cite{Karfopoulos} proposed a valley filling method by leveraging V2G in peak hours. Although the peak is minimized in above works, it cannot guarantee that the minimized peak is tolerable.

\subsubsection{Scheduling Under Demand Uncertainty}
A main challenge in EV scheduling problems is to cope with demand uncertainty. Many studies including \cite{Shroff2014,Tang,WTang,Chen,Xiang,Zhao,Robu} addressed online scheduling problem with different objectives. \cite{Shroff2014,Xiang} studied the problem of maximizing social welfare considering the benefit for both users and service provider. \cite{Tang} and \cite{WTang} developed algorithms to minimize the charging price for the CS, where the proposed algorithm in \cite{Tang} is $2.39$-competitive. 
%An online algorithm developed in \cite{Chen} to optimize overall operating profit of the service provider. 
In \cite{Robu}, an online $2$-competitive algorithm is proposed for a single CS which provides incentives for the users to truthfully report their data.

Our problem in this paper is unique from above works in different aspects. First, we study the problem in an ACN where several CSs exist. None of the above studies solve the problem under this setting. Second, the previous algorithms do not work for both integral and fractional charging models. In addition, \cite{WTang,Chen} put no limit on the charging rate of EVs which makes their solution impractical in real scenarios. Also, \cite{WTang,Tang, Shroff2014,Chen,Zhao} do not consider the peak limitation of the CS. Finally, the study in \cite{Robu} assumes that EVs are capable of getting discharged in a negligible amount of time, resulting in a $2$-competitive algorithm. However, the assumption is not realistic for EVs.
In this paper, we consider these limitations and develop online and offline algorithms for fractional and integral revenue models in an ACN and provide theoretical bounds on their performance.

%It is important to note that there is a considerable similarity between EV scheduling problem and classical job scheduling problem \cite{}. However, most algorithm developed for job scheduling problem  do not consider a limit on processing rate of the jobs.

%\cite{Shroff2014} and \cite{Stein2012} study social welfare maximization problem while the profit of both EV owners and CS is considered.  social welfare of the EV owners \cite{Stein2012}, charging cost \cite{Tang,WTang}, and total value of fully charged EVs \cite{Azar}). In addition, \cite{WTang, Tang,Shroff2014,Zhao} do not take into account the peak limitation of CS. }

%\vspace{-3mm}		
\subsection{Optimal Offline algorithm for Fractional Revenue Model}
\label{sec:fopt}				
We refer the proposed algorithm as the \fcs and summarize it as Algorithm~\ref{alg:optimal-off}.
The \fcs works in two phases. In the first phase (Section~\ref{sec:ph1}), the algorithm decides on the amount of resource to be allocated to each EV within its availability window and reserves resources accordingly. In this phase, the details of allocation is not known. The actual resource allocation is done in the second phase (Section~\ref{sec:ph2}) by setting variables $y_i^t$.

Before discussing the details of the algorithm, we introduce some notations that facilitate our algorithm design. Let $R_i$ be the amount of resource that is reserved for EV $i$ by the \fcs and $I_{t,t'}$ as time interval $[t,t']$.
% with $t,t'\in\{1,\dots ,T\}$ which includes time slots $t,t+1,\dots ,t'$. 
Then, assuming that charging demands are sorted in non-increasing order of their unit values, $A^i_j(t,t')$ is the aggregate residual resource in interval $I_{t,t'}$ at station $j$ assuming that the reservation for EVs $1$ to $i$ is accomplished with a dummy $A^0_j(t,t')$ defined as
$$A^0_j(t,t')=(t'-t+1)\times\min \{p^\mathsf{total},p_{j}\},$$
 that indicates the available resource when no charging request is processed.

		\begin{defi}
			Time interval $[\delta,\delta']$ is a ``super interval'' for interval $[t,t']$ if $1\leq \delta\leq t \text{~AND~} t' \leq \delta'\leq T$.
			Moreover, $\mathcal{I}_{t,t'}$ is the set of all super intervals of interval $I_{t,t'}$ i.e., ${\mathcal{I}_{t,t'}=\{[\delta,\delta']: 1\leq \delta\leq t \text{~AND~} t'\leq \delta'\leq T\}}$.
		\end{defi}

%		For example, $\mathcal{I}_{1,1}=\{I_{1,1},I_{1,2},I_{1,3},\dots ,I_{1,T}\}$. 
	The number of super intervals of an interval is at most $T^2$ and at least one (for interval $[1,T]$). We now explain in detail each phase of the algorithm.

		\subsubsection{Phase I-Reservation\label{sec:ph1}} In Line~\ref{algline:sort1}, the EVs are sorted in a non-increasing order of their unit values.  
%		i.e., ${v_1\slash D_1\geq v_2\slash D_2\geq\dots \geq v_n\slash D_n}$. 
		In Line~\ref{algline:setR}, the \fcs processes demand of EV $i$, picked from top of the ordered list, and sets $R_i$ as the amount to be reserved for EV $i$ which will be allocated in Phase II. In Line~\ref{algline:seta}, the residual resource of all intervals in set $\mathcal{I}_{a_i,d_i}$ decreases by $R_i$ and EV $i$ is added to the set of selected EVs.

			\begin{algorithm}[t]%\small%1
		%\footnotesize
		\caption{\fcs}
		\label{alg:optimal-off}
		\DontPrintSemicolon 
		\KwIn{$n$ EVs with their profile, local and global peak constraints $p_j, j=1,\dots ,m$ and $p^\mathsf{total}$ }

		\KwOut{Optimal scheduling under fractional model}
		\BlankLine

		Sort charging requests in non-increasing order of their unit values, i.e., $\frac{v_1}{D_1}\geq \frac{v_2}{D_2}\geq\dots \geq \frac{v_n}{D_n}$ \label{algline:sort1}

		%	\slash\slash\textit{\texttt{Use sorted list to process demands}}

		$\mathcal{L}\leftarrow \emptyset$

		\slash\slash\textit{\texttt{Phase I}}

		\For{$i=1,\ldots, n$}{
			%\slash\slash\textit{\texttt{update demand and value}}

			$R_i \leftarrow \min\{D_i, \min\limits_{t,t'} A^{i-1}_{h(i)}(t,t'), \forall t,t': I_{t,t'}\in\mathcal{I}_{a_i,d_i}\}$\label{algline:setR}

			\If{$R_i>0$}{
				$A^{i}_{h(i)}(t,t')\leftarrow A^{i-1}_{h(i)}(t,t')-R_i, \forall t,t': [t,t']\in\mathcal{I}_{a_i,d_i}$ \label{algline:seta}\\
				$\mathcal{L}\leftarrow \mathcal{L}\cup{i}$
		}}
		\slash\slash\textit{\texttt{Phase II}}

		Sort EVs in $\mathcal{L}$ in increasing order of their charging flexibility i.e., $\frac{(d_i-a_i+1)k_i}{D_i}, i\in \mathcal{L}$.

		%	Let $i$ be the index of $i^{th}$ EV in list $\mathcal{L}$

		\For{$i=1,\ldots, |\mathcal{L}|$}{

			Pick EV $i$ from the sorted list $\mathcal{L}$.

			$\emph{feasible}\leftarrow \big(\sum_{t=a_i}^{d_i}\min\{k_i,A^{i-1}_{h(i)}(t,t)\}\big) - R_i$

			\If{feasible $<0$}{
				Re-allocate previously allocated EVs such that $\emph{feasible}\geq 0$
			}
		Arbitrarily allocate $R_i$ to EV $i$ in its availability window\label{algline:fcsallocate}	
		}
	\end{algorithm}

		\begin{lem}
			Provided that for EV $i$ we have 
			\bee
			\label{eq:ri}
			R_i\leq\min\left\{D_i, \min_{t,t'} A^{i-1}_j(t,t'), \forall t,t': I_{t,t'}\in\mathcal{I}_{a_i,d_i}\right\},
			\eee
			then there is a feasible allocation to allocate $R_i$ to EV $i$ in its availability window $[a_i,d_i]$. 
			\label{thm:R_feasible}
		\end{lem}

		In Eq.~\eqref{eq:ri}, the second term, i.e., $\min_{t,t'} A^{i-1}_{j}(t,t')$, indicates the minimum remaining resource in all super intervals of interval $I_{a_i,d_i}$. For $i\geq 1$, $A^i_j(a_i,d_i)$ is defined as follows:

		\begin{equation*}
			A^i_j(a_i,d_i)=\begin{cases}
			A^{i-1}_j(a_i,d_i)-R_i & j=h(i),\\
			A^{i-1}_j(a_i,d_i) & j\neq h(i).
			\end{cases} 
		\end{equation*}

The optimal value of $R_i, i=1,\dots ,n$ is set according to the following lemma:

\begin{lem}
			Given $n$ EVs sorted in a non-increasing order of the unit values, ${v_1\slash D_1\geq v_2\slash D_2\geq\dots \geq v_n\slash D_n}$, and the value of $R_i$, where $R_i$ is set after $R_{i-1}, i=2,\dots ,n$ by Eq.~\eqref{eq:ri}, then, 
$$R_i = \min\left\{D_i, \min_{t,t'} A^{i-1}_{h(i)}(t,t'), \forall t,t':I_{t,t'}\in\mathcal{I}_{a_i,d_i}\right\},\forall i,$$
 is the optimal value for $R_i$. 
\label{thm:R_star}
\end{lem}

			\subsubsection{Phase II- Allocation\label{sec:ph2}} Lemma~\ref{thm:R_feasible} shows that there is a feasible scheduling to allocate the reserved resources.
However, despite its feasibility, it is not straightforward to find such scheduling. For example, assume that for EV $i$ it is set that $R_i=10$ and $k_i=4$. It is possible that all available resources are concentrated in a single time slot but EV $i$ cannot use more than $4$ kWh of it. In this situation, the previously allocated resources in interval $I_{a_i,d_i}$ should be re-allocated such that the concentrated resources are \emph{dispersed} and we have $\sum_{t=a_i}^{d_i}\sigma_t \geq R_i$ where $\sigma_t =\min\{k_i,A^{i-1}_{h(i)}(t,t)\}$ is the maximum resource that can be allocated to EV $i$ at time slot $t$. Since the total amount of allocated resource does not change in the interval, such dispersion is possible and can be done by a simple algorithm in which allocates $\min\{k_i,A^{i-1}_{h(i)}(t,t)\}$ starting from time slot $t=a_i$ until $R_i$ units is allocated. To further reduce the peak of the system, we will develop \sa\ algorithm (See Section \ref{sec:integral}) which acts more intelligent so that Line \ref{algline:fcsallocate} of the \fcs can be replaced by ``Run \sa$(i,R_i)$''.

			\begin{thm}
				\label{cor:1}
				\fcs is an optimal solution under fractional revenue model.
			\end{thm}

The following theorem characterizes the complexity of \fcs.

			\begin{thm}
				\label{thm:complexity}
				The time complexity of \fcs algorithm is $O(n^2T+nT^2)$ where $n$ is the number of EVs and $T$ is number of time slots.
			\end{thm}

\vspace{-3mm}

\subsection{OLP algorithm}	
\label{app:olp}

The Online Linear Program (OLP) \cite{lee2016adaptive} is a greedy algorithm that works as follows:
(i) at $t=1$ compute the optimal solution (e.g., by a solver) for the current set of EVs assuming that there will be no further arrival. (ii) use the solution until there is a new arrival. (iii) when an EV arrives, construct and solve a new problem by considering the new arrivals and the remaining demand of previously arrived EVs which are still active. (iv) go back to (ii).

The original OLP algorithm which is implemented in Caltech ACN works only for integral revenue model and under different cost functions including the revenue of the charging stations, which is the case of our study. In this paper, we implemented the algorithm for both integral and fractional model. The difference between the two versions is in the constraint set of the optimization problem that should be solved such that in integral model, the total amount of resource that an EV receives can only be equal to zero or its demand while in fractional model it can be any non-negative value less than or equal to the demand.

\end{comment}

%\vspace{-3mm}
\subsection{Details of the \rc($i$)}
\label{sec:rc}
		Before giving the details of \rc($i$), we first explain the intuition behind this algorithm. 
		 Note that if in the scheduling problem we set $T=1, m=1, k_i=p^\mathsf{total}, a_i=d_i=1\ \forall i$, then the problem is equal to the well-known $0$-$1$ knapsack problem~\cite{approx}. In the knapsack problem, a widely used greedy approach sorts items based on their unit values and selects items accordingly. It turns out that in this approach the approximation factor can be arbitrarily bad. For example, consider a knapsack problem with two items with $v_1=2, v_2=p^\mathsf{total}, D_1=1$, and  $D_2=p^\mathsf{total}$. Given these values we have $v_1\slash D_1>v_2\slash D_2$. To maximize total value of selected items, the optimal solution chooses item $2$ while greedy algorithm selects item $1$ which results in a worst-case approximation factor of ${c \slash \opt}$ in general where $c$ is a constant (in this example $c=2$). To resolve it, one approach is to \emph{re-consider} unselected items after running greedy algorithm and replace some selected items in the knapsack with unselected ones and then check whether the result is improved or not. In a simple case, only the largest unselected item can be examined which makes a significant theoretical improvement by providing a worst case approximation factor of $\opt\slash 2$.

\ics algorithm leverages the same idea but using a more intelligent replacing method called \rc($i$). \rc($i$) is called on every unselected EV $i$. It tries to find some selected EVs that if they are replaced by EV $i$, total revenue from the selected EVs increases. 
%%%When \ics calls \rc($i$) on all unselected EVs, an improvement in total revenue of final selected EVs is expected. 
%This is confirmed by the simulation results in Section~\ref{sec:simul}.

%\vspace{-3mm}
%%end{comment}

\subsection{Proof of Lemma~\ref{thm:R_feasible}}
			\label{app:2}
			We prove the theorem by induction.

			\textbf{Base case}: When $n=1$, there is only one EV that can be easily scheduled in its interval since all charging profiles represent a feasible demand and all resources are free.

			\textbf{Induction step}: Let $k\in\mathbb{Z}^+$ is given and the claim is true for $n=k$ i.e., EVs $1,\dots , k$ can be feasibly scheduled to receive their reserved resources. Now let $n=k+1$. We claim that EV $k+1$ can be feasibly scheduled in its interval. To prove, assume that this claim does not hold. Therefore, there should be at least one interval say $I_{t,t'}$ such that $A^{k+1}_{h(k+1)}(t,t')<0$ and $A^{k}_{h(k+1)}(t,t')\geq 0$. Then, one of the following cases holds: \textit{a})  $I_{t,t'}\notin\mathcal{I}_{a_{k+1},d_{k+1}}$ and \textit{b})  $I_{t,t'}\in\mathcal{I}_{a_{k+1},d_{k+1}}$. 
			%Moreover, we have $R_{k+1}=A^{k}_{a_{k+1},d_{k+1}}-A^{k+1}_{a_{k+1},d_{k+1}}$.

			In case \textit{a}, since $I_{t,t'}\notin\mathcal{I}_{a_{k+1},d_{k+1}}$, reserving resources in interval $I_{a_{k+1},d_{k+1}}$ does not affect remaining resource in $I_{t,t'}$. Therefore, we have $A^{k+1}_{h(k+1)}(t,t')=A^{k}_{h(k+1)}(t,t')\geq 0$.

			In case \textit{b}, according to Eq. (\ref{eq:ri}), we have $R_{k+1}\leq A^{k}_{h(k+1)}(t,t')$. Also, $A^{k+1}_{h(k+1)}(t,t')=A^{k}_{h(k+1)}(t,t')-R_{k+1}$ which gives $A^{k}_{h(k+1)}(t,t')\geq 0$.

			Consequently, in both cases $A^{k}_{h(k+1)}(t,t')\geq 0$ which is a contradiction. Therefore, the original claim holds.

%\vspace{-3mm}
\subsection{Proof of Lemma~\ref{thm:R_star}}
			\label{app:3}
			By induction.

			\textbf{Base case:} When $n=1$, the claim holds since $R_i>\min\{D_i, \min_{t,t'} A^{i-1}_{h(i)}(t,t'), \forall t,t': [t,t']\in\mathcal{I}_{a_i,d_i}\}$ is not feasible and the gain is maximized with maximum value of $R_i$ i.e., $R_i=\min\{D_i, \min_{t,t'} A^{i-1}_{h(i)}(t,t'), \forall t,t': [t,t']\in\mathcal{I}_{a_i,d_i}\}$.

			\textbf{Induction step:} Assume the claim holds for $n=k, k>1$ i.e., $R_i^\star=\min\{D_i, \min_{t,t'} A^{i-1}_{h(i)}(t,t'), \forall t,t': [t,t']\in\mathcal{I}_{a_i,d_i}\}$, is the optimal value for $R_i, i=1,\dots ,k$. Now let $n=k+1$. We claim that $R^\star  _{k+1}=\Gamma$ where  $\Gamma =\min\{D_{k+1}, \min_{t,t'} A^{k}_{h(i)}(t,t'), \forall t,t': (t,t')\in\mathcal{I}_{a_{k+1},d_{k+1}}\}$. To prove, assume $\Gamma$ is not the optimal value of $R_{k+1}$. Therefore, since according to the definition of $R_{k+1}$ it always holds that $R _{k+1}\leq\Gamma$ thus, $R^\star _{k+1}<\Gamma$ and the amount of resource to be reserved for EV $i$ is decreased by $\Gamma - R^\star _{k+1}$. This amount, can be only assigned to EVs $k+2$ to $n$ since $R_i$ is set to its maximum value for $i=1,\dots , k$. However, having $v_{k+1}\slash D_{k+1}\geq v_{i}\slash D_{i}, i=k+2,\dots ,n$ the optimal total revenue can be increased by setting $R_{k+1}=\Gamma$ which is a contradiction.

\subsection{Proof of Theorem~\ref{thm:focscompetitive}}
	\label{app:focscompetitive}

	We first prove the theorem for single station scenario and then extend it to multiple stations. From (\ref{eq:optdist}), (\ref{eq:lg}), and (\ref{eq:ALG}) we obtain the following result
\begin{equation}
\label{eq:compsingle}
\opt-\alg\leq \sum_{i=1}^n\sum_{t=1}^Tg_{i,t}\leq\alg,
\end{equation}
hence, $\opt\leq 2\alg$.

In multi-station setting, the difference with the previous case is that when $\Delta_{i}^t>0, i\in\{1,\dots,n\}$, then \focs may allocate the difference $\Delta_{i}^t$ to one or multiple EVs in any CS that might not be $h(i)$. However, the inequality $l_{i,t}\leq g_{i,t}$ is still valid as \focs is centralized and uses a single sorted list for all EVs. Using similar deductions as in the single station setting, it is easy to verify that the competitive ratio of $2$ is preserved.

		%\subsection{Proof of Theorem~\ref{thm:focscomplexity}}
			%\label{app:focscomplexity}

	%The complexity of the algorithm is identified by sorting operation at each time slot which dominates the $O(n)$ cost of the ``for'' loop. Therefore, the total time complexity is $O(nT\log n)$.

\subsection{Proof of Theorem~\ref{thm:approx}}
			\label{app:1}
			Without loss of generality we assume that $a_i=1, \forall i$, however, the proof holds for any other constant value for arrival time. We sum up all costs of covering dual constraints and then provide a bound for it.

			Each EV is either selected or not selected. For the unselected EVs, $\sum_{j=1}^m \sum_{t=1}^T p_j\beta (t)$ determines the cost. When \bc($i$) is running as a result of charging request disapproval of EV $i$, for any previously accepted request $i'$ the algorithm sets $\Phi_{i'}(t)$ to a value proportional to $y_{i'}^t$ for $t\leq R(d_i)$ (Line 8 of \bc($i$) algorithm). The followings are proved in \cite{Jain} for a single station $h(i')=h(i)=j$:

			\begin{equation}
				\sum_{i'=1}^n \sum_{t=1}^{d_{j}} \Phi_{i'}(t) \leq \bigg[ \frac{p_j}{p_j-q_j}.\frac{s}{s-1} \bigg].\sum_{i'=1}^n v_{i'}
				\label{EqCharge}
			\end{equation}

			\begin{equation}
				\sum_{t=1}^T p_j\beta (t)\leq \sum_{i'=1}^n \sum_{t=1}^{d_{j}} \Phi_{i'}(t).
				\label{EqBound}
			\end{equation}

			For $m$ CSs, we can obtain the following inequality based on (\ref{EqCharge}) and (\ref{EqBound}),

			\begin{align}
				\sum_{j=1}^m \sum_{t=1}^T p_j\beta (t)&\leq \sum_{j=1}^m \Big( \frac{p_j}{p_j-q_j}.\frac{s}{s-1}\sum_{i: h(i)=j}v_{i}\Big)\label{EqMS}.
			\end{align}

			Now for notational convenience let's define $A_j, B_j$ and $C$ as follows:

			\begin{align} 
				A_j&=\frac{p_j}{p_j-q_j}.\frac{s}{s-1},\nonumber\\ 
				B_j&=\sum_{i:h(i)=j}v_i,\nonumber\\ 
				C&=\sum_{j=1}^m B_j=\sum_{i=1}^n v_i\nonumber. 
			\end{align}

			We can write the right hand side of Eq.~\eqref{EqMS} as follows:

			\begin{align}
				\sum_{j=1}^m A_jB_j&=\sum_{j=1}^m \Big[ A_j\big(C-\sum_{i:h(i)\neq j}B_{h(i)}\big)\Big]\nonumber\\
				&=\sum_{j=1}^m A_jC - \sum_{j=1}^m \Big[ A_j\sum_{i:h(i)\neq j}B_{h(i)} \Big]\nonumber\\
				&=\sum_{j=1}^m A_jC - \sum_{j=1}^m \Big[ A_j\big( C-B_{j}\big) \Big]\nonumber\\
				&\leq\sum_{j=1}^m A_jC- \sum_{j=1}^m \Big[ A_j\big( C-\max_j \{B_j\} \big) \Big]\nonumber\\
				&=\max_{j}\{B_{j}\} \sum_{j=1}^m A_j\label{Eqabf}.
			\end{align}
			From (\ref{EqMS}) and (\ref{Eqabf}) we get
			\begin{align}
				\sum_{j=1}^m \sum_{t=1}^T p_j\beta (t)&\leq \max_{j}\{B_{j}\}\sum_{j=1}^m{\frac{p_j}{p_j - q_j}}.\frac{s}{s-1}
			\end{align}

			For the selected EVs, the covering cost is determined by the term $\sum_{i} D_i\alpha _i$ in the dual objective which equals to $\sum_{i\in \mathcal{S}} v_i$ where $\mathcal{S}$ is the set of selected EVs. Therefore, the total cost of covering dual constraints equals to 
			\begin{align}
				&\Lambda =  \sum_{i\in \mathcal{S}}v_i + \max_{j}\{B_{j}\}\sum_{j=1}^{m}{\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}\nonumber\\
				&\leq \sum_{i\in \mathcal{S}}v_i + \sum_{i\in \mathcal{S}}v_i\sum_{j=1}^{m}{\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}\nonumber\\
				&=\Big[ 1+\sum_{j=1}^m{\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}\Big] \sum_{i\in \mathcal{S}}v_i\label{Eq:bound}
			\end{align}
			Given that the primal value obtained from \ics is 
			${\Gamma = \sum_{i\in \mathcal{S}}v_i}$, we get 
			\bee
			\Lambda \leq \Big[ 1+\sum_{j=1}^m{\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}\Big] \Gamma.
			\eee
			Finally, considering the fact that $\Lambda\geq\opt$, we conclude that \ics is $\Big[1+\sum_{j=1}^m{\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}\Big]$-approximation.

%\subsection{Proof of Theorem~\ref{thm:ics_complexity}}	
%\label{app:ics_complexity}

%\ics starts by sorting demands which costs $O(n\log n)$. The inner ``for'' loop in Line $5$ costs $O(nT)$ and running \sa($i,D_i$) and \bc($i$) costs $O(T\log T)$ and $O(nT)$, respectively. Therefore, the total cost of outer ``for'' loop (Line $4$) equals to $O(nT\log T+n^2T)$. The complexity of \rc($i$) called in the ``for'' loop in Line $14$ is $O(nT)$. Therefore, the total cost is $O(nT\log T+n^2T)$.

\vspace{-3mm}
\subsection{Proof of Theorem~\ref{thm:iocscompetitive}}	
\label{app:iocscompetitive}

In the worst case $b=T$ i.e., there are $T$ groups where at each time slot, a group of EVs arrive. Observe that

$$\opt\leq\rho\Gamma_{\mathcal{A},\mathcal{R}^1}+\dots +\rho\Gamma_{\mathcal{A},\mathcal{R}^T}.$$

Put it simply, the increase in optimal gain at each time slot is at most equal to maximum gain that can be obtained from arrived EVs at time slot $t$. Moreover, according to the \iocs, the gain of the algorithm obtained from set of active jobs at each time slot $t$, $\Gamma_{\iocs}^t$, is as follows: $$\Gamma_{\iocs}^t=\max\{\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t},\Gamma_{\mathcal{A},\mathcal{M}^t}\}.$$ Therefore,

$$\Gamma_{\mathcal{A},\mathcal{R}^t}\leq \Gamma_{\iocs}^t, t=1, \dots ,T$$

Thus, $\opt\leq T\Big(1+\frac{p}{p-q}\frac{s}{s-1}\Big).$ If $b<T$, we can obtain $\opt\leq b\Big(1+\frac{p}{p-q}\frac{s}{s-1}\Big)$ by the same analysis.

%It is easy to verify that in a single station scenario, the competitive ratio of \iocs is at most $b\rho$ where $\rho$ is the competitive ratio of algorithm $\mathcal{A}$. As an example, if EVs arrive in two groups and $\mathcal{A}$ is \ics, then \iocs is $2+\frac{2C}{C-k}\frac{s}{s-1}$-competitive. For the proof,

%\subsection{Proof of Theorem~\ref{thm:iocscomplexity}}	
%\label{app:iocscomplexity}

	%The time complexity of \iocs is determined by the cost of algorithm $\mathcal{A}$ that it calls at each time slot. Assuming that $\mathcal{A}$ is \ics, the complexity of \iocs in a single time slot is $O(n^2)$, according to Theorem $\ref{thm:ics_complexity}$. Therefore, the complexity of \iocs is $O(n^2T)$.

%***********************************************

\vspace{-3mm}

%\vspace{-3mm}			
\subsection{Proof of Theorem~\ref{cor:1}}
			\label{app:4}
			By utilizing Lemma \ref{thm:R_star}, \fcs sets $R_i$ to its optimal value for EV $i, i=1,\dots ,n$. Based on Theorem \ref{thm:R_feasible}, since it is feasible to allocate $R_i$ to EV $i, i=1,\dots ,n$, the total gain by \fcs is optimal.

\vspace{-3mm}
\subsection{Proof of Theorem~\ref{thm:complexity}}
			\label{app:5}
			The algorithm starts by sorting the charging profiles which costs $O(n\log n)$. Then, in the first 
			``for'' loop in Lines $4-8$, the algorithm calculates $R_i$ for $i=1,\dots ,n$. This requires us to check that for each EV $i$, there are enough available resources in all time intervals in the set $\mathcal{I}_{a_i,d_i}$. By definition, number of these times slots is $(T-d_i+1)a_i$ which is $O(T^2)$ and their length varies from $1$ to $T$. Therefore, the complexity of the first ``for'' is $O(nT^2)$. Finally, in the second ``for'' loop where the algorithm makes re-allocations, it should check all previously allocated EVs in their availability interval which can be done in $O(n^2T)$ and dominates the cost of sub procedure \sa. Therefore, the total cost is $O(n^2T+nT^2)$.

\vspace{-3mm}

\begin{comment}
\subsection{The Impact of Slackness Parameter}
\label{sec:sim:slack}
This section discusses on the benefits and disadvantages that can be brought by using slackness parameter. To give the charging scheduler more flexibility, a slackness parameter $s\geq 1$ is used and set by the system designer. 
Recall that charging profile of EV $i$ is feasible if $D_i\leq k_i\frac{d_i-a_i+1}{s}$ holds. Since users have no control on the slackness parameter and the maximum charging rate, they must adjust their demand and availability according to the imposed slackness value. Based on the charging profile feasibility equation, when the slackness value increases users have two choices to react: (i) decrease the demand and depart at the desired deadline or, (ii) extend the deadline and receive the desired demand. In the remaining of this section, we investigate the effects of either case by simulation. To have a clear picture of effects caused by slackness parameter, we generated $100$ initial charging profiles $\langle a_i,d_i,v_i,D_i,k_i\rangle$ for $100$ EVs randomly and uniformly chosen from $10$ different models in Table \ref{tb:models} such that the initial profiles are set up assuming that the CS allows the charging operations to be finished at earliest possible time (i.e., $\frac{D_i}{k_i}$) with $s=1$. For each EV, its demand is randomly chosen from $25\%$ to $100\%$ of its battery capacity and departure in  interval $[a_i+\frac{sD_i}{k_i},T]$, where $a_i+\frac{sD_i}{k_i}$ is the earliest feasible deadline. Then, the EVs are uniformly assigned to $4$ CSs and should choose one of the above strategies to submit a feasible demand according to imposed slackness.

\begin{figure}[t]
\centering
				\begin{subfigure}[b]{0.236\textwidth}
					\begin{center}
						\includegraphics[width=\textwidth]{v-s-method1.pdf}
						\caption{Total revenue (\$)}
						\label{fig:v-s-method1}
					\end{center}
				\end{subfigure}%				
				\begin{subfigure}[b]{0.236\textwidth}
					\begin{center}
						\includegraphics[width=\textwidth]{rt-s-method1.pdf}
						\caption{Response time (hr))}
						\label{fig:rt-s-method1}
					\end{center}
				\end{subfigure}%  
\caption{The impact of slackness parameter on total revenue and response time when users react by adjusting their demand.} 
\label{fig:slackness1}
\end{figure}
%\vspace{-1cm}

\begin{figure}[t]	
\vspace{-2mm}
\centering
							\begin{subfigure}[b]{0.236\textwidth}
								\begin{center}
									\includegraphics[width=\textwidth]{v-s-method2.pdf}
									\caption{Total revenue (\$)}
									\label{fig:v-s-method2}
								\end{center}
							\end{subfigure}%
							\hspace{1mm}
							\begin{subfigure}[b]{0.236\textwidth}
								\begin{center}
									\includegraphics[width=\textwidth]{rt-s-method2.pdf}
									\caption{Response time (hr)}
									\label{fig:rt-s-method2}
								\end{center}
							\end{subfigure}%

\caption{The impact of slackness parameter on total revenue and response time when users react by adjusting their deadline.} 
\label{fig:slackness2}
\end{figure}

\subsubsection{Case I- Adjusting Demands}
In this case, if the initial charging profile of an EV does not reflect a feasible charging request based on the slackness parameter, the EV owner decreases its demand so it will be able to leave CS at its initial desired deadline. Note that the valuation of EVs decreases proportionally, as well. Fig.~\ref{fig:slackness1} depicts the result under this policy applied by users. As it can be seen in Fig. \ref{fig:v-s-method1} and Fig. \ref{fig:rt-s-method1}, the general trend is that both total revenue and average response time decrease when slackness value increases. This is justifiable based on users reaction. When users decrease their demand, less electricity is sold which results in less revenue. When total demand decreases, charging can be finished in shorter time which decreases response time. Therefore, if users choose the first policy (adjusting their demand), total revenue degrades while response time improves. Notice that for the algorithms working under integral revenue model (i.e., \textsc{iOPT}, \ics and \iocs) the total revenue increases with slackness parameter at first (when $s$ grows from $1$ to $1.4$) but then it decreases when the slackness increases more (for $s>1.4$). 
In our view, this happens because increasing the slackness in integral revenue model makes it possible to \emph{fully} charge more EVs at the beginning as the demands decrease. However, when the slackness increases more, it results in opposite effect because the valuation of demands decreases along with the demands' size.	
			\subsubsection{Case II- Adjusting Deadlines}
			In this case, we assume that users are reluctant to decrease their desired demands. Instead, they can extend their departure. In Fig.~\ref{fig:slackness2} it can be observed that under this behavior of the users, the results are opposite as compared to the previous case (Fig.~\ref{fig:slackness1}). When deadlines are extended without demand decrement, the scheduler has more chance to compliance the demands through improved scheduling flexibility. Consequently, the total revenue increases by increasing slackness value while average response time degrades. 
%%Also observe the behavior of the online algorithms (i.e., \iocs and \focs) where both total revenue and response time decrease after a specific point that is $s=1.8$. When deadlines extend, more EVs have the opportunity of getting charged	
%					
We can conclude that when total revenue is more important than the response time, the CS should impose small values of slackness for users that apply the policy of the first case and impose higher values of slackness for the users that apply the second policy. The conclusion is reverse for the case that the objective is to have lower response times.

			%In fact, the slackness parameter controls the maximum demand or earliest deadline that an EV can submit to the system. Remember that demands are in interval $[\textrm{min}\{\frac{d_i-a_i}{sk_i},U_i\},U_i]$ for EV $i$ meaning that the maximum demand that an EV can submit decreases by increasing slackness parameter. A reduction in total demand result in lower charging costs. Therefore, the total revenue decreases with higher values of parameter $s$ as in Fig. \ref{fig:v-s}. 
			%Also, the percentage of EVs that received all of their requested demand increases based on the same fact. The main goal of this simulation is to observe that obtained theoretical result on approximation ratio is confirmed as optimality gap of the SCS algorithm reduces by increasing $s$ in Fig. \ref{fig:v-s}.

\end{comment}

### 2019-08-27 TSC/R1/TSC.tex
MH update 2

--- 2019-08-25 TSC/R1/TSC.tex
@@
 In addition, our algorithm outperforms the existing scheduling algorithm in Caltech ACN~\cite{lee2016adaptive} by $35\%$ for integral revenue model.
+
+\bt{This paper represents follow-on work to our previous work~\cite{alinia2018competitive}, where we study a simplified version of the problems studied in this paper in fractional revenue model.
+The competitive analysis in~\cite{alinia2018competitive} provide a competitive ratio of different algorithms when all EVs have the same maximum charging rate.
+Also, \cite{alinia2018competitive} does not study the integral revenue model.
+In this paper, extend the results and propose a 2-competitive online algorithm with no assumption on the input parameters.
+Also, the current study investigates both fractional and integral revenue models while considering global peak constraint in the formulation and addressing multiple charging station scenario.
+Last, we consider more realistic trace-driven experiments in this paper and compare the results to an existing real-world scheduling algorithm.}
 %The simulation section also discusses on the positive and negative effects of slackness parameter in different scenarios.
@@
 \label{sec:rel}
-\revv{There is an extensive work in the general topic of EV demand management and scheduling~\cite{mukherjee2015review} by considering different scenarios such as optimal operations with EV coordinations~\cite{mukherjee2017distributed}, EV scheduling with incorporation of renewable energy, and energy storage systems~\cite{de2017impact,shafie2018innovative}.
-In this section, we focus on the literature related to peak-constrained EV charging scheduling in single and multiple stations.}
+\revv{There is an extensive work in the general topic of EV demand management and scheduling~\cite{mukherjee2015review} by considering different scenarios such as optimal operations with EV coordination and congestion management~\cite{mukherjee2017distributed,rigas2013congestion,hu2013coordinated}, EV scheduling with incorporation of renewable energy, and energy storage systems~\cite{de2017impact,shafie2018innovative}, and pricing and bidding~\cite{huang2014distribution,hou2019bidding} In this section, we focus on the literature related to peak-constrained EV charging scheduling in single and multiple stations.}
 \subsubsection{Peak-Constrained EV Charging Scheduling}
@@
 }
+
+\subsubsection{Worst-case Analysis in Similar Scheduling Problems}
+\label{sec:rel:comp}
+\bt{
+	Similar underlying scheduling problems with slightly different settings has been studied in the literature in both offline and online settings.
+In offline setting, the problem is more interested in integral revenue model where the problem becomes a combinatorial optimization problem and approximation algorithms have been used to find effective solutions.
+The performance of an approximation algorithm is determined by its \emph{approximation ratio} for offline 
+algorithms.
+On the other hand, competitive online algorithms are used in the online setting and \emph{competitive ratio} is the performance metric which compare the algorithm's result to the offline optimal solution.
+Under integral revenue model, \cite{jain2015near} proposes an offline algorithm for scheduling of batch jobs in cloud computing which is similar to EV scheduling problem.
+It is assumed that all jobs are available to be processed at time 0.
+The authors propose a $\frac{C}{C-k}.\frac{s}{s-1}$-approximation algorithm where $C$ is the cloud capacity and $s$ is a ``slackness'' parameter.
+Similarly, \cite{yao2016real} tackles the offline integral problem and proposes a convex relaxation method to find a near-optimal solution.
+No theoretical bound is provided for the algorithm and the performance is examined by simulation results.
+In this paper, we propose \ics for the EV scheduling problem with slightly different settings in the constraint sets, and tackle the problem in online setting in which the full knowledge of the online parameters is not available a priori, and provide competitive ratio under specific scenarios.
+In case of fractional revenue model (for offline case), the scheduling problem is more straightforward to tackle since the underlying problem is linear.
+In this paper, we propose \fcs as an optimal solution for offline fractional case.
+
+In the online scenario, the scheduling problem is fundamentally more challenging. In our recent study \cite{alinia2018competitive}, 
+we proposed two online algorithms referred to as WFAIR and WRAND for EV scheduling problem.
+The proposed algorithms provide a competitive ratio of $2-1/U$ where $U$ is "scarcity level".
+However, \cite{alinia2018competitive} the result only holds when all EVs have the same maximum charging rate.
+Also, \cite{alinia2018competitive} does not study the integral revenue model.
+In this paper, we propose \focs as a 2-competitive online algorithm with no assumption on the input parameters.
+Also, the current study investigates both fractional and integral revenue model while considering total peak constraint in the formulation and addressing multiple charging station scenario.
+In another work~\cite{firstfit}, two simple and natural online algorithms called \textsc{FirstFit} and \textsc{EndFit} were developed and are proved to be 2-competitive.
+\focs is extension of these algorithms by taking into account the maximum charging rate of the EVs and multiple charging station scenario (see ``Remarks'' at Section IV).
+As recent studies, \cite{zheng2016online,deng2016whether} provide online algorithms for EV scheduling problem, however, they do not take into account global peak constraint in the underlying problem.
+
+Another direction is to tackle online scenario under integral revenue model.
+In this setting, the scheduling problem becomes fundamentally more challenging.
+We note that the integral scheduling problem is strongly NP-Hard even in the offline case \cite{de2018complexity}.
+Due to combined online and combinatorial challenges, there are very limited studies in this category.
+\cite{lucier2013efficient} provides an online algorithm without considering the maximum processing rate of the jobs where its competitive ratio can be arbitrary bad depending on ``slackness'' parameter'.
+Our work in Section~\ref{sec:integral} also takes into account a notion of slackness parameter in our proposed online solution, and in addition, considers \iocs for multiple station scenario and maximum charging rate.
+}
+
 \section{System Model and Problem Formulation}
@@
 
-The proposed algorithms compared to the optimal offline solution of integral model ($\textsc{iOPT}$) and $\iolp$.%%% which is the running online algorithm in the Caltech ACN \cite{lee2016adaptive}. 
+The proposed algorithms compared to the optimal offline solution of integral model ($\textsc{iOPT}$) and $\iolp$.
+\bt{Note that comparison with offline optimal could be considered as a baseline comparison with the category of approximate offline algorithms in integral model~\cite{yao2016real}.}
+
+%%% which is the running online algorithm in the Caltech ACN \cite{lee2016adaptive}. 
 %The proposed algorithms for fractional revenue model, \fcs and \focs, are compared to fractional version of OLP algorithm (referred to as \folp), which is implemented in Caltech ACN  (see~\cite{alinia2017online} for details).

### 2019-08-27 TSC/R1/TSC.tex
BA - Update 2

@@
 Using competitive ratio as the performance measure, we prove the online algorithm achieves a competitive ratio of 2.
-The integral model, however, is more challenging since the underlying problem is NP-hard due to 0/1 selection criteria of EVs.
+The integral model, however, is more challenging since the underlying problem is \bt{strongly} NP-hard due to 0/1 selection criteria of EVs.
 Hence, efficient solution design is challenging even in offline setting.
@@
 \rev{Firstly, the problem calls for online scheduling design.} In practice, EVs arrive to the CS in online fashion and the scheduler has no information about the arrival and demand of the future EVs.
-Secondly, the underlying optimization problem in integral model is NP-hard even in offline case \rev{(see Section~\ref{sec:integral})}.
+Secondly, the underlying optimization problem in integral model is \bt{strongly} NP-hard even in offline case \rev{(see Section~\ref{sec:integral})}.
 This is because the problem is a mixed integer linear problem and a ``time-expanded'' extension of knapsack problem which is known as a classic NP-hard problem.
@@
 
-\bt{This paper represents follow-on work to our previous work~\cite{alinia2018competitive}, where we study a simplified version of the problems studied in this paper in fractional revenue model.
-The competitive analysis in~\cite{alinia2018competitive} provide a competitive ratio of different algorithms when all EVs have the same maximum charging rate.
+\bt{This paper represents follow-up work to our previous study~\cite{alinia2018competitive}, where we address a simplified version of the problems studied in this paper in fractional revenue model.
+The competitive analysis in~\cite{alinia2018competitive} is done under the assumption that all EVs have the same maximum charging rate.
 Also, \cite{alinia2018competitive} does not study the integral revenue model.
-In this paper, extend the results and propose a 2-competitive online algorithm with no assumption on the input parameters.
+In this paper, we extend the results and propose a 2-competitive online algorithm with no assumption on the input parameters.
 Also, the current study investigates both fractional and integral revenue models while considering global peak constraint in the formulation and addressing multiple charging station scenario.
@@
 \bt{
-	Similar underlying scheduling problems with slightly different settings has been studied in the literature in both offline and online settings.
+	Similar underlying scheduling problems with slightly different settings have been studied in the literature in both offline and online settings.
 In offline setting, the problem is more interested in integral revenue model where the problem becomes a combinatorial optimization problem and approximation algorithms have been used to find effective solutions.
@@
 algorithms.
-On the other hand, competitive online algorithms are used in the online setting and \emph{competitive ratio} is the performance metric which compare the algorithm's result to the offline optimal solution.
-Under integral revenue model, \cite{jain2015near} proposes an offline algorithm for scheduling of batch jobs in cloud computing which is similar to EV scheduling problem.
+On the other hand, competitive online algorithms are used in the online setting and \emph{competitive ratio} is the performance metric which compares the algorithm's result to the offline optimal solution.
+
+\textbf{Offline integral model}: Under integral revenue model, \cite{jain2015near} proposes an offline algorithm for scheduling of batch jobs in cloud computing which is similar to EV scheduling problem.
 It is assumed that all jobs are available to be processed at time 0.
-The authors propose a $\frac{C}{C-k}.\frac{s}{s-1}$-approximation algorithm where $C$ is the cloud capacity and $s$ is a ``slackness'' parameter.
+The authors propose a $\frac{C}{C-k}.\frac{s}{s-1}$-approximation algorithm where $C$ is the cloud capacity and $s$ is the ``slackness parameter'' (See section \ref{sec:acn} for the definition).
 Similarly, \cite{yao2016real} tackles the offline integral problem and proposes a convex relaxation method to find a near-optimal solution.
@@
 In this paper, we propose \ics for the EV scheduling problem with slightly different settings in the constraint sets, and tackle the problem in online setting in which the full knowledge of the online parameters is not available a priori, and provide competitive ratio under specific scenarios.
-In case of fractional revenue model (for offline case), the scheduling problem is more straightforward to tackle since the underlying problem is linear.
-In this paper, we propose \fcs as an optimal solution for offline fractional case.
-
-In the online scenario, the scheduling problem is fundamentally more challenging. In our recent study \cite{alinia2018competitive}, 
+
+\textbf{Offline fractional model}: In case of fractional revenue model (for offline case), the scheduling problem is more straightforward to tackle since the underlying problem is linear.
+In this paper, we propose \fcs as an optimal solution for offline fractional case with low time complexity.
+
+\textbf{Online fractional model}: In the online scenario, the scheduling problem is fundamentally more challenging. In our recent study \cite{alinia2018competitive}, 
 we proposed two online algorithms referred to as WFAIR and WRAND for EV scheduling problem.
 The proposed algorithms provide a competitive ratio of $2-1/U$ where $U$ is "scarcity level".
-However, \cite{alinia2018competitive} the result only holds when all EVs have the same maximum charging rate.
+However, the result only holds when all EVs have the same maximum charging rate.
 Also, \cite{alinia2018competitive} does not study the integral revenue model.
 In this paper, we propose \focs as a 2-competitive online algorithm with no assumption on the input parameters.
-Also, the current study investigates both fractional and integral revenue model while considering total peak constraint in the formulation and addressing multiple charging station scenario.
+Moreover, the current study investigates both fractional and integral revenue model while considering total peak constraint in the formulation and addressing multiple charging station scenario.
 In another work~\cite{firstfit}, two simple and natural online algorithms called \textsc{FirstFit} and \textsc{EndFit} were developed and are proved to be 2-competitive.
@@
 
-Another direction is to tackle online scenario under integral revenue model.
+\textbf{Online integral model}: Another direction is to tackle online scenario under integral revenue model.
 In this setting, the scheduling problem becomes fundamentally more challenging.
@@
 Due to combined online and combinatorial challenges, there are very limited studies in this category.
-\cite{lucier2013efficient} provides an online algorithm without considering the maximum processing rate of the jobs where its competitive ratio can be arbitrary bad depending on ``slackness'' parameter'.
-Our work in Section~\ref{sec:integral} also takes into account a notion of slackness parameter in our proposed online solution, and in addition, considers \iocs for multiple station scenario and maximum charging rate.
+\cite{lucier2013efficient} provides an online algorithm without considering the maximum processing rate of the jobs where its competitive ratio can be arbitrary bad depending on ``slackness'' parameter.
+Our work in Section~\ref{sec:onlineint} extends this study for multiple station scenario and considering maximum charging rate for the EVs.
 }
@@
 \label{sec:fopt}	
-We refer the proposed algorithm as the \fcs and summarize it as Algorithm~\ref{alg:optimal-off}.
+\bt{
+In this section, we propose an optimal algorithm for offline fractional model.
+As a natural solution, one may think of a greedy algorithm with the strategy as follows: at each time slot, charge the EV with highest unit-value and process others if only the resource cannot be used by this EV (probably due to maximum charging rate constraint).
+This approach is a popular, yet straightforward method in the online scheduling.
+However, it turns out that this approach cannot provide an optimal solution to the problem even in fractional revenue model.
+In fact, this approach only provides a 2-competitive solution.
+i.e., the profit obtained by the algorithm would be $1/2$ of the optimum.
+As an intuition of the proof think of two EVs where the one with lower unit value cannot wait due to its deadline and the EV with higher unit value has a long park time.
+Then, the optimal solution here could be first serving the EV with earlier deadline (and not the one with highest unit values).
+}
+
+We refer the proposed algorithm in this secion as the \fcs and summarize it as Algorithm~\ref{alg:optimal-off}.
 The \fcs works in two phases.
@@
 
-		\vspace{-3mm}
 		\begin{algorithm}%\small%1
@@
 
-\vspace{-4mm}
 \begin{algorithm}%\small%1

### 2019-08-27 TSC/R1/res.tex
BA - Update 2

@@
 \ifodd 1
+\newcommand{\bt}[1]{{\color{red}#1}}%revise of the text
 \newcommand{\rev}[1]{{\color{black}#1}}%revise of the text
@@
 \else
+\newcommand{\bt}[1]{#1}
 \newcommand{\rev}[1]{#1}
@@
 \begin{enumerate}
-\item \textit{...}.
+\item \textit{\color{red} @Mohammad: better to remove this bullet section as we don't have many items to talk about (the only main change is in Related Work)}.
 
@@
 In addition, in the paper, we clearly distinguished between the results in this paper and our previous conference paper on IEEE/ACM IWQoS 2018.
-Our work in this paper considers more general problem formulation, with global peak constraints, and a comprehensive revenue model.
-The developed algorithms in Section V, for the integral revenue model, are new in this work.
+Our work in this paper considers more general problem formulation, with global peak constraints, multiple station scenario and a comprehensive revenue model.
+\bt{Although  ``fractional revenue'' model is studied in both papers (and in some other studies), the proposed algorithms are  different in idea, results and underlying system model.
+Also, the Section V for the integral revenue model is new in this work.
 Finally, the trace-driven experimental results are more extensive in this paper and provide comparisons with an algorithm that are currently in use in a real-world charging station.
+}
 
-We highlighted both of the revisions in the revised manuscript and also addressed several other comments that are proposed by the reviewers.
+%We highlighted both the revision in the revised manuscript and also addressed several other comments that are proposed by the reviewers.
 
@@
 
-\textit{To clarify this, we added an explanation in Section ...
-@Bahram: please add a subsection in Related work and explain IWQoS and other theoretical papers.
-This is the most important task for this revision.
-}
+\bt{To clarify this, we added an explanation in last paragraph of the Introduction section and Section II-3 when describing related works.   }
 
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
+Thanks for the comment.
+This approach is equal to running an optimal algorithm at each time slot considering only available EVs and assuming no more EVs will arrive.
+We added a paragraph in the beginning of Section IV.A to explain this.
+
+{\color{red}@ Mohammad: Should we use the following example in here or in the paper?}
+
 We added an example in Page xx to demonstrate why the simple approach mentioned by the reviewer is not optimal.
-
-{\color{red}@ Mohammad: I copied the following from TSG response letter. We can update and add it to the paper.}
 
@@
 We note that the derived complexities of the algorithms in the paper include parameter $T$ as number of time slots in a day (please see Table II in the manuscript).
-In large scale scenarios, the effect of increasing $T$ would be negligible in performance of the algorithms as long as it $T/N$ is a constant ($N$ is number of EVs).
-Therefore, when $N$ grows large and $T$ is a constant, $T$ can be removed from the complexities in the Table II.
+In large scale scenarios, the effect of increasing $T$ would be negligible in performance of the algorithms as long as it $T/N$ is a constant ($n$ is number of EVs).
+Therefore, when $n$ grows large and $T$ is a constant, $T$ can be removed from the complexities in the Table II.
 
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
-The complexity of the algorithms are low and we just set the charging rate by a simple sorting on arrival of each EV. \textbf{Bahram, please confirm.}
+\bt{As explained in the previous comment, we derived the time complexity of all proposed algorithms (listed in Table II in the paper) which indicate their running time in large scale scenarios (i.e., when $n$ is large).
+If we assume that $T$ is a constant (which is a quite realistic assumption), the complexity of all algorithms simplifies to $O(n^2)$.
+Hence, we believe that a normal PC could be fast enough to run the algorithms.}
 

### 2019-08-28 TSC/R1/TSC.tex
MH - Update 3

@@
 	Similar underlying scheduling problems with slightly different settings have been studied in the literature in both offline and online settings.
-In offline setting, the problem is more interested in integral revenue model where the problem becomes a combinatorial optimization problem and approximation algorithms have been used to find effective solutions.
+In offline setting, the problem is more interesting in integral revenue model where the problem becomes a combinatorial optimization problem and approximation algorithms have been used to find effective solutions.
 The performance of an approximation algorithm is determined by its \emph{approximation ratio} for offline 
@@
 
-\textbf{Offline integral model}: Under integral revenue model, \cite{jain2015near} proposes an offline algorithm for scheduling of batch jobs in cloud computing which is similar to EV scheduling problem.
+\textit{Offline integral model}: Under integral revenue model, \cite{jain2015near} proposes an offline algorithm for scheduling of batch jobs in cloud computing which is similar to EV scheduling problem.
 It is assumed that all jobs are available to be processed at time 0.
@@
 No theoretical bound is provided for the algorithm and the performance is examined by simulation results.
-In this paper, we propose \ics for the EV scheduling problem with slightly different settings in the constraint sets, and tackle the problem in online setting in which the full knowledge of the online parameters is not available a priori, and provide competitive ratio under specific scenarios.
-
-\textbf{Offline fractional model}: In case of fractional revenue model (for offline case), the scheduling problem is more straightforward to tackle since the underlying problem is linear.
+In this paper, we propose \ics for the EV scheduling problem with slightly different settings in the constraint sets, and tackle the problem in online setting in which the full knowledge of the online parameters is not available a priori, and provide approximation ratio under specific scenarios.
+
+\textit{Offline fractional model}: In case of fractional revenue model (for offline case), the scheduling problem is more straightforward to tackle since the underlying problem is linear.
 In this paper, we propose \fcs as an optimal solution for offline fractional case with low time complexity.
 
-\textbf{Online fractional model}: In the online scenario, the scheduling problem is fundamentally more challenging. In our recent study \cite{alinia2018competitive}, 
+\textit{Online fractional model}: In the online scenario, the scheduling problem is fundamentally more challenging. In our recent study \cite{alinia2018competitive}, 
 we proposed two online algorithms referred to as WFAIR and WRAND for EV scheduling problem.
@@
 
-\textbf{Online integral model}: Another direction is to tackle online scenario under integral revenue model.
+\textit{Online integral model}: Another direction is to tackle online scenario under integral revenue model.
 In this setting, the scheduling problem becomes fundamentally more challenging.
@@
 		\begin{table} 
-			\caption{Summary of key notations}\vspace{-3mm}
+			\caption{Summary of key notations}
+%			\vspace{-3mm}
 			\label{tbl:not}
@@
 			\centering
-	\vspace{-3mm}
+%	\vspace{-3mm}
 			\caption{Proposed algorithms and their properties.}
@@
 
-\vspace{-4mm}
+%\vspace{-4mm}
 \subsection{Online Scenario}
@@
 
-\vspace{-4mm}
+%\vspace{-4mm}
 \begin{algorithm}%\small%1
@@
 		%We borrowed algorithm \bc($i$) from \cite{Jain} and adjusted it for multiple station mode.		
-		\vspace{-3mm}
+%		\vspace{-3mm}
 		\begin{algorithm}%\small%1
@@
 		\end{algorithm}	
-		\vspace{-7mm}	
+%		\vspace{-7mm}	
 		\begin{algorithm}%\small%1
@@
 		\end{algorithm}
-		\vspace{-7mm}
+%		\vspace{-7mm}
 		\begin{algorithm}%\small%1
@@
 
-\vspace{-6mm}
+%\vspace{-6mm}
 \section{Simulation Results}
@@
 				\label{fig:V-N-M}
-				\vspace{-3mm}
+%				\vspace{-3mm}
 			\end{figure*}
@@
 				\label{fig:peak_local}
-			\vspace{-4mm}
+%			\vspace{-4mm}
 			\end{figure*}
@@
 \ref{fig:v-s}.
-\vspace{0.1mm}
-\vspace{-4mm}
+%\vspace{0.1mm}
+%\vspace{-4mm}
 			\section{Conclusion}
@@
 %As a future work, we plan to analyze the truthfulness of the algorithms to make sure that it is a dominant strategy for the EV owners to declare their true valuations and availabilities.
-\vspace{-4mm}
+%\vspace{-4mm}
 
@@
 \bibliography{ref}{}
-\vspace{-2.8mm}
+%\vspace{-2.8mm}
 \bibliographystyle{ieeetr}

### 2019-08-28 TSC/R1/TSC.tex
Finalizing main and response file for submission

@@
 	Similar underlying scheduling problems with slightly different settings have been studied in the literature in both offline and online settings.
-In offline setting, the problem is more interesting in integral revenue model where the problem becomes a combinatorial optimization problem and approximation algorithms have been used to find effective solutions.
+In offline setting, the problem is more interesting \bt{under integral revenue model} where the problem becomes a combinatorial optimization problem and approximation algorithms have been used to find effective solutions.
 The performance of an approximation algorithm is determined by its \emph{approximation ratio} for offline 
@@
 		%We skip the explicit formulation of the problem under integral revenue model since it could be contemplated as the linear-relaxed version of the integral revenue model (for more explanation, we refer to the discussions in Section~\ref{sec:fractional}).
-		We formulate Scheduling Problem for Adaptive charging Network (\MCSP) under fractional revenue model as follows: 
+		\bt{We formulate a Scheduling Problem} for Adaptive charging Network (\MCSP) under fractional revenue model as follows: 
 		\bse
@@
 In this section, we propose an optimal algorithm for offline fractional model.
-As a natural solution, one may think of a greedy algorithm with the strategy as follows: at each time slot, charge the EV with highest unit-value and process others if only the resource cannot be used by this EV (probably due to maximum charging rate constraint).
-This approach is a popular, yet straightforward method in the online scheduling.
+As a natural solution, one may think of a greedy algorithm as follows: at each time slot, charge the EV(s) with highest unit-value and process others if only the remaining resource cannot be allocated to the selected EV(s) (e.g., due to maximum charging rate constraint or fulfillment of the EVs' demand).
+This approach is a popular, yet straightforward method in the scheduling.
 However, it turns out that this approach cannot provide an optimal solution to the problem even in fractional revenue model.
-In fact, this approach only provides a 2-competitive solution.
-i.e., the profit obtained by the algorithm would be $1/2$ of the optimum.
-As an intuition of the proof think of two EVs where the one with lower unit value cannot wait due to its deadline and the EV with higher unit value has a long park time.
-Then, the optimal solution here could be first serving the EV with earlier deadline (and not the one with highest unit values).
+In fact, this solution is only 2-approximation (i.e., the profit obtained by the algorithm would be $1/2$ of the optimum).
+As an intuition of the proof think of two EVs in a single charging station with power capacity $p$ and $\frac{v_1}{D_1}-\frac{v_2}{D_2}=\epsilon$  where $\epsilon > 0$ is an arbitrary small number, $a_1=a_2=1, d_1=2, d_2=1$ and $D_1=D_2=k_1=k_2=p$.
+Then, applying the simple greedy, EV 1 will be selected at time slot 1 and EV 2 will have no chance to get charged due to its deadline constraint while EV 1 could wait until time slot 2 and still receive all its demand.
 }
@@
 		\label{subsec:analysis}
-		In primal-dual algorithm, the goal is to design an algorithm in a way that it produces a good solution for primal problem (with primal value $\Gamma$) and a feasible solution for the dual problem (with dual value $\Lambda$).
+		\bt{In a primal-dual algorithm}, the goal is to design an algorithm in a way that it produces a good solution for primal problem (with primal value $\Gamma$) and a feasible solution for the dual problem (with dual value $\Lambda$).
 Then, assuming that the primal problem is a maximization problem, to prove that the algorithm is $c-$approximation (for $c\geq 1$), the important part is to show that $\Lambda\leq c\Gamma$.
@@
 Due to the binary selection variable, the online solution design under integral model is more challenging than the one for fractional model.
-We propose the \iocs that is built upon the offline \ics.
+\bt{We propose \iocs} that is built upon the offline \ics.
 In particular, the \iocs calls the \ics at each time slot for the set of available EVs, however, any algorithm that is designed for offline integral model can be used alternatively.
@@
 For this purpose, the algorithm modifies the demand and valuation of the previously admitted EVs such that each demand is replaced by the EV's remaining demand, and the valuation of the EV is proportionally calculated based on the remaining demand (Line $9$ of the algorithm) so that the unit values of EVs do not change.
-Then, the \iocs runs $\mathcal{A}$ over set of active EVs $\mathcal{M}^t$ where the corresponding gain is denoted by $\Gamma_{\mathcal{A},\mathcal{M}^t}$.
+Then, the \iocs runs $\mathcal{A}$ \bt{on set of} active EVs $\mathcal{M}^t$ where the corresponding gain is denoted by $\Gamma_{\mathcal{A},\mathcal{M}^t}$.
 If $\Gamma_{\mathcal{A},\mathcal{M}^t}>\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$, the \iocs forgets the previously admitted EVs and follows the second scheduling.
@@
 Let $\mathcal{A}$ be \ics in \iocs algorithm and $m=1$.
-Assuming that EVs are released in $b$ distinct groups where arrival time of EVs in each group are the same, the \iocs is $b\Big(1+\frac{p}{p-q}\frac{s}{s-1}\Big)$-competitive with optimal offline solution, where $p$ is the station peak and $q=\max_i k_i, i=1,\dots ,n$.
+Assuming that EVs are released in $b$ distinct groups where arrival time of EVs in each group are the same, the \iocs is $b\Big(1+\frac{p}{p-q}\frac{s}{s-1}\Big)$-competitive \bt{with optimal} offline solution, where $p$ is the station peak and $q=\max_i k_i, i=1,\dots ,n$.
 \end{thm}
@@
 				\end{subfigure}% 
-				\caption{\revv{Comparison results for $2$, $4$, and $8$ CSs for fractional and integral revenue models.}} 
+				\caption{\revv{Comparison results for $2$, $4$, and $8$ CSs for fractional and integral revenue models.
+\bt{In the algorithms' name, letters ``o'', ``f'' and ``i'' indicate online, fractional and integral, respectively.
+Note that a ``non-optimal'' fractional algorithm can potentially achieve better result than an ``optimal'' integral algorithm due to higher flexibility in power allocation.} }}
 				\label{fig:V-N-M}
@@
 % with the mean arrival and parking duration indicated in Table \ref{tb:a-d}. 
-The peak intervals include $08$:$00$-$10$:$00$, $12$:$00$-$14$:$00$, and $18$:$00$-$20$:$00$ which is in accordance to NHTS survey~\cite{Santos, Tang}.
-\revv{The probability of arriving an EV in the peak hours is two times higher than the off-peak periods.
+The peak intervals include $08$:$00$-$10$:$00$, $12$:$00$-$14$:$00$, and $18$:$00$-$20$:$00$ \bt{according to NHTS} survey~\cite{Santos, Tang}.
+\revv{The probability \bt{of an EV's arrival} during the peak hours is two times higher than the off-peak periods.
 			Demands are uniform random values from 
@@
 
-The proposed algorithms compared to the optimal offline solution of integral model ($\textsc{iOPT}$) and $\iolp$.
+\bt{The proposed algorithms are compared to} the optimal offline solution of integral model ($\textsc{iOPT}$) and $\iolp$.
 \bt{Note that comparison with offline optimal could be considered as a baseline comparison with the category of approximate offline algorithms in integral model~\cite{yao2016real}.}
@@
 \bibliographystyle{ieeetr}
+\newpage
+{\color{white}...}    
+\newpage
 

### 2019-08-28 TSC/R1/res.tex
Finalizing main and response file for submission

@@
 \ifodd 1
-\newcommand{\bt}[1]{{\color{red}#1}}%revise of the text
+\newcommand{\bt}[1]{{\color{black}#1}}%revise of the text
 \newcommand{\rev}[1]{{\color{black}#1}}%revise of the text
@@
 This document provides a summary of changes made in the revised manuscript and detailed responses to the comments of the reviewers.
-The major changes in the revised manuscript are summarized below:
-
-\begin{enumerate}
-\item \textit{\color{red} @Mohammad: better to remove this bullet section as we don't have many items to talk about (the only main change is in Related Work)}.
-
-\end{enumerate}
 
@@
 Our work in this paper considers more general problem formulation, with global peak constraints, multiple station scenario and a comprehensive revenue model.
-\bt{Although  ``fractional revenue'' model is studied in both papers (and in some other studies), the proposed algorithms are  different in idea, results and underlying system model.
-Also, the Section V for the integral revenue model is new in this work.
+\bt{Although  ``fractional revenue'' model is studied in both papers (and in some other studies as well), the proposed algorithms are  different in idea, results and underlying system model.
+Also, Section V for the integral revenue model is new in this work.
 Finally, the trace-driven experimental results are more extensive in this paper and provide comparisons with an algorithm that are currently in use in a real-world charging station.
@@
 Our earlier work presents algorithms for only fractional revenue model.
-Current manuscript, which can be considered as journal extension of the previous work, studies both fractional and integral models.
-Although the presented algorithms in the conference version provide a competitive ratio of $2-1/U$ (with $U$ as "scarcity level"), the proof holds when all EVs have the same maximum charging rate.
+Current manuscript, which can be considered as an extension of the previous work, studies both fractional and integral models.
+Although the presented algorithms in the conference version provide a competitive ratio of $2-\frac{1}{U}$ (where $U$ denotes "scarcity level"), the proofs hold when all EVs have the same maximum charging rate.
 In the current study, we consider heterogeneity in this parameter and prove the online algorithm is 2-competitive.
 
-\bt{To clarify this, we added an explanation in last paragraph of the Introduction section and Section II-3 when describing related works.   }
+\bt{To clarify this, we added an explanation in last paragraph of Introduction section in Page 2 and Section II-3 in Page 3 when describing related works.   }
 
@@
 \vspace{3mm}
-
-{\color{red}: @Mohammad: This is not clear for me in most parts}
 
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
-The current experiments (i) shows the effect of problem parameters, including the number of charging stations and number of vehicles (in Figure 2), and the impact of peak constraint and demand (in directly) (in Figure 3).
+The current experiments (i) shows the effect of problem parameters, including the number of charging stations and number of vehicles (in Figure 2), and the impact of peak constraint and demand indirectly (Figure 3).
 The impact of arrival and departure times could be interpreted as more/less flexibility in charging scheduling.
@@
 %We believe that detailed implementation of the algorithms has no added value as the goal here is to provide algorithms and analysis and not focusing on programming challenges.
-here: https://github.com/bahramalinia/EV-Scheduling.git
+here: https://github.com/bahramalinia/EV-Scheduling
 
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
-Thanks for the point. We agree that our problem is strongly NP-Hard and we corrected the related phrases in the manuscript. Please see Page ?? of the revised manuscript.
+Thanks for the point. We agree that our problem is strongly NP-Hard and we corrected the related phrases in the manuscript.
 
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
-The constraint (1d) applies on each time slot $t$ for each EV $i$ and enforces respecting maximum charging rate at each $t$ for all $i$.
+The constraint (1d) applies on each time slot $t$ for each EV $i$ and ensures respecting maximum charging rate at each $t$ for all $i$.
 The constraint say nothing about the relation between charging rates at different slots (including forcing them to be equal).
@@
 Thanks for the comment.  
-This approach is equal to running an optimal algorithm at each time slot considering only available EVs and assuming no more EVs will arrive.
-We added a paragraph in the beginning of Section IV.A to explain this.
-
-{\color{red}@ Mohammad: Should we use the following example in here or in the paper?}
-
-We added an example in Page xx to demonstrate why the simple approach mentioned by the reviewer is not optimal.
-
-The proposed approach by the reviewer is a popular, yet straightforward method in the online scheduling.
+The proposed approach by the reviewer is a popular, yet straightforward method in the scheduling problems.
 However, it turns out that this approach cannot provide an optimal solution to the problem even in fractional revenue model.
-In fact, this approach only provides a 2-competitive solution.
+In fact, this approach only provides a 2-approximation solution.
 i.e., the profit obtained by this approach would be $1/2$ of the optimum.
-We bring an example to clarify.
-
-Fig.
-\ref{fig:1a} shows a simple scenario in a single charging station with $T=2$ and $p_1=p^{\text{total}}=1$.
-The charging profile of an EV $i$ is shown in the form of $\pi_i=(a_i,d_i,v_i,D_i,k_i)$ where it is assumed that $k_i=1$ for all $i$.
-At $t=1$, EVs 1 and 2 arrive and the scheduler has no information about the future coming EVs.
-If we run an optimal offline algorithm over the available EVs at $t=1$, it will allocate EV 2 at $t=1$ and postpone charging of EV 1 to $t=2$ according to their deadline.
-Now assume that EV 3 arrives at $t=2$ which has the same demand and unit value as EV 1 (see Fig.
-\ref{fig:1b}).
-Then, by re-computing the optimal solution at $t=2$, the solution is to choose either EV 1 or EV 3 to charge due to capacity constraint.
-Therefore, the final solution obtained by this approach achieves a total revenue of $1+\epsilon$ by charging EVs 2 at $t=1$ and one of the EVs 1 or 3 at $t=2$.
-However, the optimal solution in this example is charging EV 1 at $t=1$ and EV 3 at $t=2$ and obtaining a gain equal to 2.
-This example shows that the competitive ratio of the proposed approach by the reviewer cannot be better than $2-\epsilon$ where $\epsilon$ can be arbitrarily small.
-
-\begin{figure}
-\centering     %%% not \center
-		\subfloat[{EVs $1$ and $2$ arrive at $t=1$.}]{\label{fig:1a}\includegraphics[width=60mm]{Ex1a.pdf}}
-		\hspace{8mm}
-		\subfloat[{EV $3$ arrives at $t=2$.}]{\label{fig:1b}\includegraphics[width=60mm]{Ex1b.pdf}}
-\caption{Worst case scenario when the scheduling algorithm is to re-run an optimal algorithm at each time slot considering only available EVs.
-Dotted line indicates a time slot that is not visited yet and the scheduler has no information about the arriving EVs in that slot.
-The numbers inside parentheses indicate arrival time, deadline, value, demand and maximum charging rate of the EV, respectively.}
-\label{fig:1}
-\end{figure}
+We added a paragraph in the beginning of Section IV.A to explain this with an example.
 
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
-We agree and this is unfortunately consequence of space limit. To avoid confusion, we added an explanation in Page xx, when describing the results.
+We agree and to avoid confusion, we added an explanation in the caption of Fig. 2 in page 10.
 
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
-...
+Thanks for the subtle comments. We corrected them.
 
@@
 
-{\color{red} I should check these papers and add to Related Work if needed.}
-
 \vspace{3mm}
@@
 In addition, this suggestion makes more sense in scenarios in which EVs are heterogeneous and a subset of chargers can satisfy a subset of EVs.
-We do believe that this is an very interesting scenario to consider, however, as mentioned by the reviewer, it increases the complexity of designing and analysis of the algorithms, and is beyond the scope of this submission.
+We do believe that this is an interesting scenario to consider, however, as mentioned by the reviewer, it increases the complexity of designing and analysis of the algorithms, and is beyond the scope of this submission.
 
@@
 
-B. Alinia, M. H. Hajiesmaili, and N. Crespi, "Online EV Charging Scheduling with On-Arrival Commitment", \textit{IEEE Trans. on Int. Transportation Systems (ITS)}, 2019.
+\begin{itemize}
+\item B. Alinia, M. H. Hajiesmaili, and N. Crespi, "Online EV charging scheduling with on-arrival commitment," \textit{IEEE Transaction on Intelligent Transportation Systems}, Jan. 2019.
+\end{itemize}
 
@@
 Since it is proved that SCOMMIT is truthful, we believe that among the proposed algorithms in current manuscript, the FOCS is truthful.
-In the above paper, also, we tackled another desirable property to commit EVs on their arrival on how much they can get charged during their available window.
+In the above paper, also, we tackled another desirable property to give commitment to the users at their arrival time about the minimum amount of resource they can get by their deadline.
 
-The focus of this paper, in on more comprehensive online algorithm design for fractional and integral revenue models, and for our ITS paper, we focused on truthfulness and on-arrival commitment.
+The focus of this paper is to consider more comprehensive online algorithm design for fractional and integral revenue models, while in the ITS paper, we focused on truthfulness and on-arrival commitment.
 It is worth noting that developing solutions that provide competitiveness against offline optimal versus those that provide truthfulness and on-arrival commitment, needs different algorithmic techniques and tools.
-As a notable result, an interesting theoretical observation in our ITS shows that there is no online algorithms that can simultaneously provide on-arrival commitment and bounded competitive ratio.
+As a notable result, an interesting theoretical observation in our ITS paper shows that there is no online algorithms that can simultaneously provide on-arrival commitment and bound the competitive ratio.
 See Section 6 and Theorem 5 of our ITS paper for more details.
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
-The length of the time slot can be arbitrary set in the algorithms and we used 1 hour in experiments since the availability window of our traces was in one hour slots.
+The length of the time slot can be arbitrary set in the algorithms.
+However, we used 1 hour in the experiments since the availability window in our traces was in one hour slots.
 With more fine grained data, it would be possible to run the algorithms in faster timescales, e.g., 5 minutes or so.
@@
 We note that the derived complexities of the algorithms in the paper include parameter $T$ as number of time slots in a day (please see Table II in the manuscript).
-In large scale scenarios, the effect of increasing $T$ would be negligible in performance of the algorithms as long as it $T/N$ is a constant ($n$ is number of EVs).
-Therefore, when $n$ grows large and $T$ is a constant, $T$ can be removed from the complexities in the Table II.
+In large scale scenarios, the effect of increasing $T$ would be negligible in performance of the algorithms as long as it $T$ is a constant.
 
@@
 $\vartriangleright$ \noindent\textbf{Response:} 
-\bt{As explained in the previous comment, we derived the time complexity of all proposed algorithms (listed in Table II in the paper) which indicate their running time in large scale scenarios (i.e., when $n$ is large).
-If we assume that $T$ is a constant (which is a quite realistic assumption), the complexity of all algorithms simplifies to $O(n^2)$.
+\bt{As explained in the response to the previous comment, we derived the time complexity of all proposed algorithms (listed in Table II in the paper) which indicate their running time in large scale scenarios (i.e., when $n$ as number of EVs grows large).
+If we assume that $T$ is a constant (which is quite realistic assumption), the complexity of all algorithms simplifies to $O(n^2)$.
 Hence, we believe that a normal PC could be fast enough to run the algorithms.}

### 2025-03-09 TSUSC/TSUSC-2018-12-0140.R1-main.tex
move resources from other repos

--- 2019-08-28 TSC/R1/TSC.tex
@@
-\documentclass[journal]{IEEEtran}
+\documentclass[10pt,journal,compsoc]{IEEEtran}
+%\documentclass[journal]{IEEEtran}
 %\usepackage{float}
@@
 %\usepackage{txfonts}
-\addtolength{\abovedisplayskip}{-2mm}
-\addtolength{\belowdisplayskip}{-2mm}
-\addtolength{\parskip}{-.15mm}
+%\addtolength{\abovedisplayskip}{-2mm}
+%\addtolength{\belowdisplayskip}{-2mm}
+%\addtolength{\parskip}{-.15mm}
 %\addtolength{\arraycolsep}{-.75mm}
-\addtolength{\abovecaptionskip}{-1mm}
-\addtolength{\belowcaptionskip}{-1mm}
+%\addtolength{\abovecaptionskip}{-1mm}
+%\addtolength{\belowcaptionskip}{-1mm}
 %\renewcommand{\baselinestretch}{0.9}
@@
 
-			M. H. Hajiesmaili and E. Mallada are with the Department of Electrical and Computer Engineering, Johns Hopkins University, Baltimore, MD, USA (e-mail: \{hajiesmaili,mallada\}@jhu.edu).
+	M.
+H.
+Hajiesmaili is with the College of Information and Computer Sciences, University of Massachusetts Amherst, Amherst, MA, USA (email: hajiesmaili@cs.umass.edu).
+He is supported by NSF through grant CNS 1908298.
 
 	Z. J. Lee is with the Department of Electrical Engineering, California Institute of Technology, Pasadena, CA, USA (e-mail: zlee@caltech.edu).	
-		} }
+	He is supported by the NSF Graduate Research Fellowship Program (Grant No. 1745301) and Resnick Sustainability Institute.
 
-		\maketitle
+	E.
+Mallada is with the Department of Electrical and Computer Engineering, Johns Hopkins University, Baltimore, MD, USA (e-mail: mallada@jhu.edu).
+He is supported by ARO through contract W911NF-17-1-0092, US DoE EERE award DE-EE0008006, and NSF through grants CNS 1544771, EPCN 1711188, AMPS 1736448, and CAREER 1752362.
 
+		}	
+		\vspace{-0.05in}	
+		}
+
+\IEEEtitleabstractindextext{%
 \begin{abstract}
@@
 %			This paper tackles both fractional and integral models. 
-			The critical challenge is the need for online solution design since in practical scenario\revv{s} the scheduler has no information of future arrivals of EVs in a time-coupled underlying problem. 
+			The technical challenge is the need for online solution design since in practical scenario\revv{s} the scheduler has no or limited information of future arrivals in a time-coupled underlying problem.
 			For the fractional model, we devise both offline and online algorithms.
@@
 Using competitive ratio as the performance measure, we prove the online algorithm achieves a competitive ratio of 2.
-The integral model, however, is more challenging since the underlying problem is \bt{strongly} NP-hard due to 0/1 selection criteria of EVs.
+The integral model, however, is more challenging since the underlying problem is strongly NP-hard due to 0/1 selection criteria of EVs.
 Hence, efficient solution design is challenging even in offline setting.
-We devise a low-complexity primal-dual scheduling algorithm that achieves a bounded approximation ratio.
+For offline setting, we devise a low-complexity primal-dual scheduling algorithm that achieves a bounded approximation ratio.
 Built upon the offline approximate algorithm, we propose an online algorithm and analyze its competitive ratio in special cases.
@@
 \end{abstract}
+
+% Note that keywords are not normally used for peerreview papers.
 		\begin{IEEEkeywords}
 			Electric Vehicle, Online Scheduling, Approximation Algorithm, Competitive Analysis
-		\end{IEEEkeywords}
+		\end{IEEEkeywords}	}
 
-		\section{Introduction}
-\label{sec:intro}	
-%		\IEEEPARstart{A}{s} 
-%		a result of global warming and environmental concerns through dependence on fossil fuels, there has been a rapid proliferation in deploying renewable energy sources. 
-\IEEEPARstart{T}{o} promote quick adoption of renewable energy sources, electrification of vehicles is a trend that has been globally advocated in recent years.
-\rev{According to a Bloomberg report, EVs will account for more than half of the new car sales by $2040$~\cite{bloomberg}.
-	%the global sale of EVs increased by $80\%$ in $2015$~\cite{EVSales}.
-	%		With the significant advantage of electric vehicles (EVs) in being an environment friendly product, the global interest for EVs is rapidly growing, such that  
-	Consequently, it is expected that demand from EV charging will constitute a considerable portion of total demand. 
-	Currently, transportation consumes $29\%$ of total energy in the US, while electricity production consumes $40\%$~\cite{Zhao}.} 
-%Vehicles seen accounting for 5\% of electricity use by $2040$~\cite{EVSales2}}
-%%%\revv{\sout{Hence, rapid electrification of the vehicles makes the total electricity demand of EVs significant.}}
+		\maketitle
 
-\revv{EV charging demand is a typical example of a deferrable load, and there is often considerable flexibility in the charging schedule.
-This property makes the problem of EV charging scheduling  important and there is an extensive research along this direction in the literature (see the recent survey~\cite{mukherjee2015review}, and references therein).
-In most of the existing works, the EV charging demand is treated as a constraint to the problem in a low-load regime~\cite{Tang}.
-Motivated by rapid proliferation of EVs, this work tackles the EV scheduling in high-load regime, where given the aggregate charging demand of the EVs and the peak constraints of the charging network, it is not feasible to fully charge all the EVs according to their charging demand.}
-%		\subsection{Microgrid: Definition, Potentials, and Challenges}
-%		\label{sec:introA}
-%		A common trend in the smart grid era is to install renewable energy sources in distributed manner.
-More specifically, medium or large commercial and industrial  customers such as universities, headquarters, etc.,  can take control of their own energy consumption by local deployment of renewable sources~\cite{Hajiesmaili2016Online}.
-In this setting, the residual demand, i.e., total demand subtracted by the local renewable supply, can be acquired from the external grid.
+\input{intro.tex}
 
-%		In addition to clean energy production, the owner of microgrid also enjoys more power sustainability and reliability, and the ability to proactively manage the energy costs.
+\input{relatedWork.tex}
 
-More specifically, this paper studies resource-constrained EV charging scheduling in an adaptive charging network (ACN) governed by a single operator in a campus-scale location such as a university, a headquarter\rev{s}, etc.
-\cite{wu2017two}.
-\rev{A notable example is the Caltech ACN~\cite{lee2016adaptive} where individual charging ports are organized into several \textit{charging stations} (CSs) which are dispersed in a \textit{charging network}} with the capability of adaptive charging of the EVs.
-The problem is different from EV charging scheduling \revv{with capacity constraint} in single station scenarios~\cite{Tang,Wen,Shroff2014,WTang,Chen,Xiang,Zhao,Robu} (we refer to~Section~\ref{sec:rel} for detailed discussions on related work), because of the essential need to respect the aggregate peak demand of the ACN.
-\revv{Note that, the ACN operator might limit the total power drawn from EVs to control costs~\cite{PeakPrice,Zhang2015eEnergy}, reserve the capacity for other loads, and/or participate in demand-response programs.}
-%		The EV charging loads are usually flexible and deferrable, which means that their load can be scheduled~\cite{moghaddam2017smart,DWang} to shape the total demand over time. 
-%The aim of this paper is to use the deferrable property of EVs and schedule their charging jobs, so as to \rev{maximize the revenue of the ACN}.	
-%		We refer to Section~\ref{sec:rel} for the literature review.
+\input{systemModel.tex}
 
-%		In particular, real-world pricing scheme for large customers is usually a hybrid time-of-use and peak-based charging model where the peak demand can significantly impact the total energy cost, e.g., the peak price is often more than $100$ times higher than the spot price~\cite{PeakPrice,Zhang2015eEnergy}.
-Considering total aggregate demand, the peak charge portion could be as large as $20\%-80\%$ of total cost~\cite{Xu2014Reducing}.
-Consequently, a substantial cost reduction could be achieved if the total peak-demand can be proactively controlled \cite{liao2015dispatch}.
+\input{fractional.tex}
 
-%		\subsection{EV Charging Scheduling in the ACN}
-%		With the proliferation of EVs, the charging requirement of the microgrid EVs could be a portion of total microgrid electricity demand.
+\input{integral.tex}
 
-%		To respond the electricity demand of EVs, CSs are being used where EVs can recourse to charge their battery \cite{He,liao2015dispatch,Tang}.
-There can be few to many CSs dispersed in an ACN, e.g., each for a parking garage of a building in a university campus.
-In this scenario, all parking stations are governed by a facility operator and a \textit{global} peak demand constraint is determined such that the aggregate charging demand in the entire network is less than this global peak demand \cite{DWang,Hoog}.
+\input{simulation.tex}
 
-%		The charging scheduling of the EVs with the goal of respecting the \textit{global aggregate peak constraint}, however, is a unique problem which is different from the single station EV charging scheduling.
-Most of the existing work in the literature, tackle the problem in the single parking station scenario.
-We refer to Section~\ref{sec:rel} for in-depth discussion.
-As discussed in Section \ref{sec:problem}, the global optimal solution cannot be obtained by separately solving the single station problems.
-%		On the other hand, there are only a few studies that provide global optimal solution for charging scheduling of EVs \cite{He, Moradijoz, Malhotra,Zeng,Shaaban,DWang}.
-Despite elegant results, the underlying problems, e.g., charging cost minimization problem in \cite{He}, average operating cost minimization with optimal electricity exchange capacity problem in \cite{DWang}, optimal station capacity problem in~\cite{Moradijoz}, user convenience maximization problem in~\cite{Malhotra}, joint optimization of system profit and user experience in~\cite{Shaaban,Zeng} are different from the problem studied in this paper.
+\input{conclusion.tex}
 
-%		\subsection{Problem, Challenges, and Contributions}
-We consider a scenario with multiple EVs where each EV has different charging profile in terms of availability, charging demand, charging rate limit, and valuation of getting charged \revv{(for details see Section~\ref{sec:ev})}.
-We formulate an online EV charging scheduling problem with the goal of \textit{selecting} and \textit{scheduling} a subset of EVs such that: (1) the charging demand of the selected EVs are (fully or partially) satisfied; (2) the charging rate limit of EV batteries are respected, (3) the global peak constraint of the ACN is satisfied~\cite{lee2016adaptive}; (4) the local peak constraint of each CS is respected;  and finally, (5) the total revenue obtained by the valuation of the EVs is maximized.
-
-%		of maximizing the revenue of the ACN.
-The constraints are the \textit{local} peak constraint of each CS, and the \textit{global} peak constraint that limits the accumulative charging demand drawn from the entire network of stations (decided by the administration of the ACN to control total peak demand~\cite{lee2016adaptive}).
-
-There are two main challenges in the design and implementation of scheduling algorithms for EVs satisfying the goals mentioned above.
-\rev{Firstly, the problem calls for online scheduling design.} In practice, EVs arrive to the CS in online fashion and the scheduler has no information about the arrival and demand of the future EVs.
-Secondly, the underlying optimization problem in integral model is \bt{strongly} NP-hard even in offline case \rev{(see Section~\ref{sec:integral})}.
-This is because the problem is a mixed integer linear problem and a ``time-expanded'' extension of knapsack problem which is known as a classic NP-hard problem.
-In this paper, we tackle the challenge of online design by following competitive algorithm design~\cite{borodin2005online} and the challenge of NP-hardness by pursuing approximation algorithm design~\cite{approx} and make the following contributions:
-
-$\vartriangleright$ We first consider a \textit{fractional model} (where EVs can be charged partially and the revenue is proportional accordingly) and design an optimal offline scheduling algorithm. 
-%In addition to provide efficient result, the algorithm has a further elegant step to apply a valley filling strategy to further reduce the peak demand of EV charging without degrading total revenue. 
-We then develop an efficient online algorithm in which no exact or stochastic information about the future EV arrivals is given.
-Despite its simplicity, the algorithm is proved to be $2$-competitive with optimal offline solution, i.e., the revenue of the proposed online algorithm is at least $1/2$ of the offline optimum, regardless of input sequence.
-Even though there are competitive algorithms in the literature for similar problems, to the best of our knowledge, our algorithm is the first $2$-competitive algorithm \rev{which considers the} charging rate limits.
-
-$\vartriangleright$ We next study \rev{the} more challenging scenario of \rev{the} \textit{integral model}\rev{, }where EVs must receive all their demand to make revenue.
-We first propose a polynomial-time primal-dual offline approximate algorithm.
-We analyze the approximation ratio of the algorithm and by strengthening the linear relaxed version of the mixed integer problem~\cite{Carr}, we obtain an approximation ratio of $\alpha =1+\sum_{j=1}^m {\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}$, where $p_j$ is local peak constraint in station $j$, $q_j$ is the maximum charging rate of the EVs in station $j$ and $s$ is a slackness parameter.
-We highlight that when $p_j \gg q_j$ and $s$ is \rev{large} enough, then $\alpha \approx m+1$, where $m$ is the number of stations in the ACN.
-Built on the basis of the offline algorithm, we devise an online algorithm, and discuss its competitive ratio in special cases.
-%In particular, the competitive ratio is $b\Big(1+\frac{p_j}{p_j-q_j}\cdot\frac{s}{s-1}\Big)$ for single station scenario, where $b$ is the number of batches with the same arrival time.
-
-$\vartriangleright$ We conduct a set of  simulations to evaluate the performance of our proposed algorithms. 
-%For offline scheduling problem under integral charging model, the results  demonstrate that the proposed approximation algorithm is close to the optimal solution and is significantly better than the obtained theoretical bounds.
-The results of online algorithms for both integral and fractional settings are close to the optimum (within $90\%$ and $94\%$ for integral and fractional models in a representative scenario).
-In addition, our algorithm outperforms the existing scheduling algorithm in Caltech ACN~\cite{lee2016adaptive} by $35\%$ for integral revenue model.
-
-\bt{This paper represents follow-up work to our previous study~\cite{alinia2018competitive}, where we address a simplified version of the problems studied in this paper in fractional revenue model.
-The competitive analysis in~\cite{alinia2018competitive} is done under the assumption that all EVs have the same maximum charging rate.
-Also, \cite{alinia2018competitive} does not study the integral revenue model.
-In this paper, we extend the results and propose a 2-competitive online algorithm with no assumption on the input parameters.
-Also, the current study investigates both fractional and integral revenue models while considering global peak constraint in the formulation and addressing multiple charging station scenario.
-Last, we consider more realistic trace-driven experiments in this paper and compare the results to an existing real-world scheduling algorithm.}
-%The simulation section also discusses on the positive and negative effects of slackness parameter in different scenarios.
-
-%To the best of our knowledge, this problem is not addressed yet in previous studies.
-
-%		\subsection{Paper Organization}
-%		The rest of this paper is organized as follows. Section~\ref{sec:rel} reviews the literature. In Section \ref{sec:model}, the system model  and problem formulation are described. 
-%		Section \ref{sec:fractional} provides offline and online algorithms for fractional model.
-We study integral model in Section \ref{sec:integral} and propose online and offline algorithms.
-The simulation results are reported in Section~\ref{sec:simul}.
-Section~\ref{sec:conclusion} concludes the paper and highlights future directions.
-
-\section{Related Work}
-\label{sec:rel}
-\revv{There is an extensive work in the general topic of EV demand management and scheduling~\cite{mukherjee2015review} by considering different scenarios such as optimal operations with EV coordination and congestion management~\cite{mukherjee2017distributed,rigas2013congestion,hu2013coordinated}, EV scheduling with incorporation of renewable energy, and energy storage systems~\cite{de2017impact,shafie2018innovative}, and pricing and bidding~\cite{huang2014distribution,hou2019bidding} In this section, we focus on the literature related to peak-constrained EV charging scheduling in single and multiple stations.}
-\subsubsection{Peak-Constrained EV Charging Scheduling}
-\label{sec:rel:peakconstrained}			
-\revv{There is an extensive literature on EV charging scheduling problem focusing on single CS~\cite{Tang,Wen}, while the local and global peak constraints are omitted or only the local peak is considered.}	As we discuss in Section~\ref{sec:problem}, the global optimal solution cannot be obtained by separately solving the single station problems.
-Hence, those solutions cannot be directly applied to the multiple CS scenario with global peak constraints.
-
-%A scenario that local and global peak constraints exist is the case that scheduling is required for a charging network for multiple CSs. 
-Studies in \cite{He,malhotra2017distributed,Moradijoz,DWang,Zeng,Shaaban} tackled charging scheduling problem in multiple CSs.
-The authors in~\cite{He} studied a global cost minimization EV charging scheduling problem.
-However, there is no limit on the maximum peak demand that the system can tolerate.
-Consequently, the peak can be arbitrary high and beyond the physical limit of the transformers in the charging station~\cite{lee2016adaptive} leading to huge electricity bills~\cite{Zhang2015eEnergy}.
-Besides, the charger devices installed in the CSs have limitation on the maximum power that they can transfer in each time unit~\cite{Tesla}.
-%We solve the issue by constraining local and global peaks.
-However, to meet the peak constraints, it may not be feasible to respond to all charging demands.
-Consequently, only a subset of EVs can be charged~\cite{Xiang}, which is captured in our problem formulation.
-\cite{DWang} considered a multi-microgrid system with global peak constraint where each microgrid has a CS and the goal is to manage electricity exchange between microgrids and main grid to minimize the operating costs.
-The authors assume that required information about individual EVs is available by forecast which may not represent a real scenario.
-A similar assumption is made in \cite{Zeng,Shaaban} where the objective is to maximize total utility of EVs and aggregators in a distribution network.
-%\rev{To be removed: In our solution, we applied a priority based selection process (based on the EVs' valuation) to respond to the demands to make sure that total peak respects the constraints.
-The selection process can be made based on different criteria such as the value of each charging request \cite{Lee, Xiang} or the priority.}
-%To avoid big billing cost in peak hours, \cite{Moradijoz} proposed a solution based on genetic algorithm to find optimal capacity and location of parking lots for serving demands in peak hours with the goal of maximizing total benefit of all stations.
-Although authors studied the problem under multiple CS setting, their solution is not applicable to our setting when the CSs are already set up.
-The authors in~\cite{malhotra2017distributed} use a similar model as in this paper, where both local and global peak constraints are considered.
-However, the authors solve the single-slot problem, which fails to provide a general solution taking into account EVs' arrival and departure times as considered in our study.
-Finally, as an alternative approach to control the peak, some studies directly target minimizing the peak~\cite{Zhao, Karfopoulos}.
-In~\cite{Zhao}, an online algorithm is developed for EV charging to minimize the peak and \cite{Karfopoulos} proposed a valley filling method by leveraging V2G in peak hours.
-Although the peak is minimized in above works, it cannot guarantee that the minimized peak is tolerable by the underlying charging network.
-
-\subsubsection{Scheduling Under Demand Uncertainty}
-A main challenge in EV scheduling problem is to cope with demand uncertainty.
-Many studies including \cite{Shroff2014,Tang,WTang,Chen,Xiang,Zhao,Robu} addressed online scheduling problem with different objectives.
-\cite{Shroff2014,Xiang} studied the problem of maximizing social welfare considering the benefit for both users and service provider.
-\cite{Tang} and \cite{WTang} developed algorithms to minimize the charging price for the CS, where the proposed algorithm in \cite{Tang} is $2.39$-competitive.
-%An online algorithm developed in \cite{Chen} to optimize overall operating profit of the service provider. 
-In \cite{Robu}, an online $2$-competitive algorithm is proposed for a single CS, assuming that EVs are capable of being discharged in a negligible amount of time.
-The assumption, however, is not realistic for EVs.
-
-Our problem in this paper is unique from above works in many respects.
-First, we study the problem in an ACN where several CSs exist, while none of the above studies solve the problem under this setting.
-Second, the previous algorithms do not work for both integral and fractional charging models.
-In addition, \cite{WTang,Chen} put no limit on the charging rate of EVs which makes their solution impractical in real scenarios.
-Also, \cite{WTang,Tang, Shroff2014,Chen,Zhao} do not consider the peak limit of the CS.
-\revv{Note that some studies~\cite{jin2017optimal} tackle the scenarios of satisfying the large demands (possibly EV demands) by participating in electricity market.
-This study assumes that the electricity price is given and fixed, and leaves the case of real-time pricing as the future direction.
-In addition, there are studies that incorporate prediction in online EV charging scheduling~\cite{wang2017predictive,chen2014distributional}.
-The prediction-based approaches achieve satisfactory performance for the scenarios that follow prediction.
-Deviation from prediction models, however, degrades their performance.
-Our approach, on the other hand, has no assumptions on modeling/prediction, and in this way, is robust against any uncertainty in the instances to the problem.}
-\revv{Finally, in~\cite{Alinia2018ITS}, we considered a simplified EV charging scheduling in fractional model without global peak constraints and devised heuristic algorithms (without competitive and approximation analysis) with on-arrival commitment for EVs to notify the amount that they can receive by their departure.
-}
-%In this paper, we consider these limitations and develop online and offline algorithms for fractional and integral revenue models in an ACN and provide theoretical bounds on their performance.
-
-%It is important to note that there is a considerable similarity between EV scheduling problem and classical job scheduling problem \cite{}.
-However, most algorithm developed for job scheduling problem  do not consider a limit on processing rate of the jobs.
-
-%\cite{Shroff2014} and \cite{Stein2012} study social welfare maximization problem while the profit of both EV owners and CS is considered.
-social welfare of the EV owners \cite{Stein2012}, charging cost \cite{Tang,WTang}, and total value of fully charged EVs \cite{Azar}).
-In addition, \cite{WTang, Tang,Shroff2014,Zhao} do not take into account the peak limitation of CS.
-}
-
-\subsubsection{Worst-case Analysis in Similar Scheduling Problems}
-\label{sec:rel:comp}
-\bt{
-	Similar underlying scheduling problems with slightly different settings have been studied in the literature in both offline and online settings.
-In offline setting, the problem is more interesting in integral revenue model where the problem becomes a combinatorial optimization problem and approximation algorithms have been used to find effective solutions.
-The performance of an approximation algorithm is determined by its \emph{approximation ratio} for offline 
-algorithms.
-On the other hand, competitive online algorithms are used in the online setting and \emph{competitive ratio} is the performance metric which compares the algorithm's result to the offline optimal solution.
-
-\textit{Offline integral model}: Under integral revenue model, \cite{jain2015near} proposes an offline algorithm for scheduling of batch jobs in cloud computing which is similar to EV scheduling problem.
-It is assumed that all jobs are available to be processed at time 0.
-The authors propose a $\frac{C}{C-k}.\frac{s}{s-1}$-approximation algorithm where $C$ is the cloud capacity and $s$ is the ``slackness parameter'' (See section \ref{sec:acn} for the definition).
-Similarly, \cite{yao2016real} tackles the offline integral problem and proposes a convex relaxation method to find a near-optimal solution.
-No theoretical bound is provided for the algorithm and the performance is examined by simulation results.
-In this paper, we propose \ics for the EV scheduling problem with slightly different settings in the constraint sets, and tackle the problem in online setting in which the full knowledge of the online parameters is not available a priori, and provide approximation ratio under specific scenarios.
-
-\textit{Offline fractional model}: In case of fractional revenue model (for offline case), the scheduling problem is more straightforward to tackle since the underlying problem is linear.
-In this paper, we propose \fcs as an optimal solution for offline fractional case with low time complexity.
-
-\textit{Online fractional model}: In the online scenario, the scheduling problem is fundamentally more challenging. In our recent study \cite{alinia2018competitive}, 
-we proposed two online algorithms referred to as WFAIR and WRAND for EV scheduling problem.
-The proposed algorithms provide a competitive ratio of $2-1/U$ where $U$ is "scarcity level".
-However, the result only holds when all EVs have the same maximum charging rate.
-Also, \cite{alinia2018competitive} does not study the integral revenue model.
-In this paper, we propose \focs as a 2-competitive online algorithm with no assumption on the input parameters.
-Moreover, the current study investigates both fractional and integral revenue model while considering total peak constraint in the formulation and addressing multiple charging station scenario.
-In another work~\cite{firstfit}, two simple and natural online algorithms called \textsc{FirstFit} and \textsc{EndFit} were developed and are proved to be 2-competitive.
-\focs is extension of these algorithms by taking into account the maximum charging rate of the EVs and multiple charging station scenario (see ``Remarks'' at Section IV).
-As recent studies, \cite{zheng2016online,deng2016whether} provide online algorithms for EV scheduling problem, however, they do not take into account global peak constraint in the underlying problem.
-
-\textit{Online integral model}: Another direction is to tackle online scenario under integral revenue model.
-In this setting, the scheduling problem becomes fundamentally more challenging.
-We note that the integral scheduling problem is strongly NP-Hard even in the offline case \cite{de2018complexity}.
-Due to combined online and combinatorial challenges, there are very limited studies in this category.
-\cite{lucier2013efficient} provides an online algorithm without considering the maximum processing rate of the jobs where its competitive ratio can be arbitrary bad depending on ``slackness'' parameter.
-Our work in Section~\ref{sec:onlineint} extends this study for multiple station scenario and considering maximum charging rate for the EVs.
-}
-
-\section{System Model and Problem Formulation}
-		\label{sec:model}
-
-		\subsection{System Model}
-		We consider a time-slotted system model in which the time horizon is divided to $T$ equal length slots ${t=\{1, 2, \dots ,T\}}$ (e.g., $T=24$ with time slots of $1$ hour length).
-\subsubsection{Charging Network}
-\label{sec:acn}
-Our charging network model is inspired by the Caltech ACN~\cite{lee2016adaptive} as illustrated in Fig.~\ref{fig:model-a}.
-In \rev{the} Caltech EV charging network (located in a parking garage), electricity is distributed through a two-level transformer architecture from a main switch panel to multiple EV switch panels (\rev{$2$} panels in the current Caltech ACN).
-Each EV switch panel then is connected to several chargers ($\approx$25 chargers \rev{per panel} in the Caltech ACN).
-The total power drawn from the main switch panel \rev{by} the charging network has a power limit of  $p^\mathsf{total}$, that is determined by the facility operator to control the costs, reserve the capacity for other loads, and/or participate in demand-response programs.
-%This power, where we refer to it as \emph{network power limit} is used for both EV charging as well as non-EV charging purposes (e.g., lighting, fans, etc \cite{lee2016adaptive}). 
-In other words, $p^\mathsf{total}$, which we refer to it as the \textit{global peak}, hereafter, limits the maximum aggregate EV charging load at each time slot. 
-%The global peak must be less than or equal to the value obtained by subtracting non-EV load from network power limit. 
-%When we write \emph{global peak constraint}, it refers to $p^\mathsf{total}$.  
-%$p^\mathsf{total}$ is the maximum allowed aggregated electricity consumption by all stations at each slot and limits the total transferable power to EVs.
-
-We assume that there are $m$ EV switch panels that represent $m$ CSs.
-In addition to the global peak constraint, each CS $j$ has \rev{a} capacity constraint on \rev{its} total power drawn, indicated by $p_j$, and referred to it as the \emph{local peak} constraint.
-The \rev{value of} $p_j$ is determined by the output power limit of the transformers installed between the main switch panel and EV switch panels and could be different for each EV switch panel.
-%installed chargers in a CS have limited output power to charge EVs ~\cite{Wen,Xiang,Tesla}. Therefore, for CS $j$, $p_j$ cannot be more than sum of output power of its chargers. 
-\rev{It is often observed that the charging demand of different CSs (EV switch panels in Fig.~\ref{fig:model-a}) are well below the local peak constraints.}
-To increase the flexibility due to heterogeneous charging demand of CSs, in the Caltech ACN, the global peak constraint of the main switch can be \textit{over-provisioned}, i.e., $p^\mathsf{total}$ is less than the aggregate local peaks,  ($\sum_j p_j\geq p^\mathsf{total}$).
-\rev{While this increases flexibility, it also couples the problem of EV charging scheduling across different CSs.}
-%Despite increased flexibility, the over-provisioning property, however, couples the problem of EV charging scheduling across different CSs. 
-Our solutions in this paper will be centralized ones which can be obtained through communication between the CSs and a central server as illustrated in Fig. \ref{fig:model-b}.
-
-%We make this clear by a simple example.
-Assume $m=2, p^\mathsf{total}=50$ kW and $p_1=p_2=25$ kW.
-In a specific time slot (e.g., $t=1$), the total demand in CS $1$ and $2$ is $40$ kWh and $10$ kWh, respectively.
-According to local peak constraints, it is not feasible to satisfy all demands in a single time slot.
-However, if we had $p_1=p2=50$ kW (e.g., by installing more chargers in the stations) we could be able to satisfy all demands by allocating $40 kW$ in $p_1$ and $10 kW$ in $p_2$ while still not violating $p^\mathsf{total}$.
-In case that $\sum_j p_j\leq p^\mathsf{total}$, the scheduling problem is not challenging and the solution can be obtained by solving the problem locally in each CS.
-If $\sum_j p_j> p^\mathsf{total}$ (which is the case we consider in this paper), a centralized solution is needed that can be obtained through communication between the CS and a central server as illustrated in Fig.
-\ref{fig:model-b}.
-
-\begin{figure}	
-\centering
-\minipage{0.49\textwidth}
-				\begin{subfigure}[b]{0.69\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{model-a.pdf}
-						\caption{Caltech adaptive charging network (ACN)}
-						\label{fig:model-a}
-					\end{center}
-				\end{subfigure}%
-				\begin{subfigure}[b]{0.29\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{model-b.pdf}
-						\caption{Communication model with server}
-						\label{fig:model-b}
-					\end{center}
-				\end{subfigure}%  
-\caption{System model \cite{lee2016adaptive}.} 
-\label{fig:slackness1}
-\endminipage
-\end{figure}
-
-		\begin{table} 
-			\caption{Summary of key notations}
-%			\vspace{-3mm}
-			\label{tbl:not}
-			\begin{center}
-				\begin{tabular}{|c L{6.5cm}|}
-					\hline
-					\textbf{Notation} & \textbf{Description} \\
-					\hline \hline			
-					$T$ & Number of time slots, indexed by $t$\\			
-					$m$ & Number of CSs, indexed by $j$\\			
-					$n$ & Number of EVs, indexed by $i$\\			
-					\hline
-					\hline
-					$a_i$ & Arrival time of EV $i$\\
-					$d_i$ & Departure time of EV $i$\\
-					$D_i$ & Demand of EV $i$\\
-					$v_i$ & Valuation of EV $i$ for receiving its demand $D_i$ \\
-					$k_i$ & Maximum charging rate of EV $i$\\
-					$h(i)$ & CS of EV $i$\\
-					\hline
-					\hline
-					$q_j$ & Maximum $k_i$ among all EVs in CS $j$\\
-					$p_j$ & Maximum aggregate charging rate in station $j$\\
-					$p^\mathsf{total}$ & Maximum aggregate charging rate of all stations\\
-					\hline
-					\hline
-					$y_i^t$ & \textbf{opt. variable}, The amount that EV $i$ is charged at $t$ \\
-					\hline
-				\end{tabular}
-			\end{center}
-		\end{table}
-		\subsubsection{EVs}
-		\label{sec:ev} There are $n$ EVs in the system, indexed by $i$.
-		%, all available at time $t=1$ to be charged\footnote{This assumption is reasonable for the %official buildings where the starting hour of the working day is fixed for all the %employers.
-Extensions to the case with different arrival times for the EVs, is part of the %future work.}.
-		EV $i$ is represented by a charging profile $\langle a_i,d_i,v_i,D_i,k_i\rangle$ 
-		indicating its arrival time, departure time, willingness to pay, charging demand, and maximum charging rate, respectively. 
-		%(depends on physical properties of EVs battery) 
-		More specifically, the charging of EV $i$ can be scheduled within its \emph{availability window}, $[a_i,d_i]$.
-The charging rate at each slot is bounded by $k_i$, a parameter that depends on the physical constraints of the \rev{battery and on-board charger}.
-It is assumed that the charging profile of each EV is feasible with respect to its maximum charging rate and a slackness parameter $s\geq 1$, which is the minimum ratio between the park time of the EV and its minimum charging time, i.e., ${D_i\leq k_i(d_i-a_i+1)/s}$.
-The slackness parameter is imposed to tune the flexibility of the charging scheduling.
-In extreme case $s=1$,  the flexibility is minimum and the flexibility improves as $s$ increases.
-%		Note  that  the slackness  parameter  can  impact  the  total  revenue  and  is  investigated  in  simulation  experiments  in Section~\ref{sec:simul}.
-		We assume that EV owners select their CS, perhaps the nearest to them, and so the assignments are given to the problem. Define $h(i)$ as the CS of EV~$i$.
-		Moreover, $q_j$ denotes the maximum $k_i$ among all EVs in CS $j$, i.e., $q_j=\max_{h(i)=j} k_i$. 
-		\revv{Finally, $v_i$ is the willingness to pay of EV $i$ to receive its entire demand $D_i$ before the departure time $d_i$.
-Note that in resource-constrained EV scheduling in ACN, it is not feasible to fulfill the entire demand of all EVs, hence, the problem turns into a resource allocation one with the goal of maximizing the aggregate value (a.k.a.
-utility) obtained from the EVs.
-In this way, each user can announce its willingness to pay to get charged which is denoted by $v_i$ in the system model.}
-		%We assume that there is no gain for the CS if EV $i$ is partially charged.
-
-		% where $P$ defined as $P:\xi\rightarrow  \mathcal{P}$. 
-\subsubsection{Revenue Models\label{sec:irm}} We consider two revenue models: 
-\textit{(i) Fractional revenue model}: In this model, the fractional charging is allowed, i.e., the revenue from each EV is proportional to the fraction of the demand that is fulfilled \cite{Xiang} (see Eq.~\eqref{Eq:partial_value}).
-We tackle this model in Section~\ref{sec:fractional}.
-\textit{(ii) Integral revenue model}: \rev{In this model, EV $i$ pays $v_i$ if it is fully charged and zero otherwise, i.e., there is no partial revenue for partial charging. }
-%In this model, when EV $i$ is received its demand entirely, the gain is $v_{i}$ and zero, otherwise, i.e., there is no partial revenue for fractional charging. 
-This is the model that is considered in~\cite{WTang,Shroff2014}. We tackle this model in Section~\ref{sec:integral}.
-
-		%The actual aggregated peak of all parking stations must not exceeds global peak constraint.
-
-			\begin{table*}[!t]
-			\centering
-%	\vspace{-3mm}
-			\caption{Proposed algorithms and their properties.}
-			\label{tbl:algs}
-			\begin{tabular}{ | l | c | c | c |c|}
-				\hline
-				\textbf{Algorithm} & \textbf{Revenue model} & \textbf{Type} & \textbf{Optimality} & \textbf{Complexity} \\ \hline\hline    
-				\fcs& fractional& offline& Optimal & $O(n^2T+nT^2)$\\\hline 
-				\ics& integral& offline& ${\Big( 1+\sum_{j=1}^m {\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}\Big)}$-approximate & $O(nT\log T+n^2T)$ \\\hline 
-				\focs & fractional& online& $2$-competitive & $O(n^2T)$\\\hline 
-				\iocs& integral&  online& $b(1+\frac{p}{p-q}.\frac{s}{s-1})$-competitive, $(m=1)$ & $O(n^2T)$\\\hline
-			\end{tabular}
-		\end{table*}
-
-		\subsection{Problem Formulation}
-		\label{sec:problem}
-	We formulate an optimization problem to schedule the charging of the EVs with the objective of maximizing total revenue obtained from charged EVs while respecting local and global peak constraints. 
-		Note that each revenue model makes the underlying optimization problem fundamentally different. More specifically, the fractional charging model is a linear problem. 
-		Integral revenue model, however, turns the underlying charging scheduling problem to a Mixed Integer Linear Program (MILP). The integer nature originates from the $0/1$-selection decision on EVs. 
-%%%Recall that in integral revenue model the revenue is obtained given that the entire demand is fulfilled for the selected EV. 
-		%We skip the explicit formulation of the problem under integral revenue model since it could be contemplated as the linear-relaxed version of the integral revenue model (for more explanation, we refer to the discussions in Section~\ref{sec:fractional}).
-		We formulate Scheduling Problem for Adaptive charging Network (\MCSP) under fractional revenue model as follows: 
-		\bse
-		\bee
-		\MCSP: \max  && \sum\nolimits_{i=1}^n \frac{v_{i}}{D_i}\sum\nolimits_{t=a_i}^{d_i} y_i^t \label{Pobjec} \nonumber\\
-		\text{s.t.} &&\sum\nolimits_{t=a_i}^{d_i} y_i^t\leq D_i,\quad\quad\forall i, \label{ConstPartial} \\
-		&&  \sum\nolimits_{i=1}^n y_i^t\leq p^\mathsf{total} ,\quad\quad\forall t,\label{ConstTotal} \\
-		&&\sum\nolimits_{i:h(i)=j} y_i^t\leq p_j ,\quad\quad\forall t,j,\label{ConstLocal}\\
-		&& y_i^t  \leq \frac{k_i}{D_i}\sum\nolimits_{t^\prime=a_i}^{d_i} y_i^{t^\prime}, \quad\forall i,t,\label{ConstSpeed}\\
-%		&& \rev{y_i^t=0,\forall t\in\{t':t'>d_i \vee t'<a_i\}}, \\
-		\text{vars.} && y_i^t \geq 0, \quad\quad\forall i, t,\label{ConstPositive}\nonumber
-		%&& s_v(t), \quad \forall v,t
-		\eee
-		\ese
-		where $y_i^t$ is the amount that EV $i$ is charged at slot $t$. Constraint (\ref{ConstPartial}) ensures that the aggregate amount received by EV $i$ is at most the demand $D_i$. 
-%		Note that under integral revenue model, when we design our algorithm, we do not allow partial charging. 
-The global and local peak constraints are represented by constraints (\ref{ConstTotal}) and (\ref{ConstLocal}), respectively.
-
-		\revv{The constraint~\eqref{ConstSpeed} enforces the maximum charging rate of EVs.
-The straightforward way to express this constraint is to simply state that at each time slot $t$, the charging rate of EV $i$ should be less than or equal to its maximum charging rate, i.e., $y_i^t\leq k_i, \forall i,t$.
-		However, for the sake of effective algorithm design for integral model and reducing the integrality gap of the relaxed linear problem, this constraint is strengthened in the form of Eq.~\eqref{ConstSpeed}.
-		Note that in case that the aggregated charging of EV $i$ during its availability window is equal to its demand, i.e., $\sum_{t^\prime=a_i}^{d_i} y_i^{t^\prime}= D_i$, Eq.~\eqref{ConstSpeed} reduces to the simple form of $y_i^t\leq k_i$.
-		This is a natural way in approximation algorithm design to improve the performance of the algorithms under linear-relaxation based design~\cite{Carr}. }
-
-The \MCSP is an extension of formulated problem in \cite{Jain} where a job scheduling problem in cloud applications is studied.
-It turns out that the resource allocation problem in cloud systems and the EV charging scheduling problem in a \emph{single station} share similar structure.
-Indeed, each charging profile in our scheduling problem can be seen as a job in cloud system with a deadline, value, and CPU demand.
-The \MCSP, however, comes with an additional constraint~\eqref{ConstTotal}, which makes it different from the problem in \cite{Jain}, such that the existing solution \revv{will not} work in the new setting.
-More importantly, this paper studies both offline and online solutions for the problem in both fractional and integral settings, while \cite{Jain} tackles only the offline integral model.
-
-%(ii) Our solution design and analysis for integral revenue model is based on linear-relaxation primal-dual framework~\cite{Jain}.
-Therefore, in Section \ref{sec:integral} for integral revenue model, we rely on the \MCSP for the analysis of the proposed algorithms and skip to explicitly formulate the original MILP problem.
-
-%		Also, we cover the fractional revenue model and provide theoretical bounds for the proposed algorithms.
-
-%In the next two sections, we devise several algorithms to solve the \MCSP under the two revenue models (integral and fractional) and for both offline and online scenarios. 
-		\section{Fractional Revenue Model}
-		\label{sec:fractional}
-
-%\subsection{Overview of Fractional Revenue Model}
-%\label{sec:frac.overview}				
-		%In the previous section, we devised an approximation algorithm for the integral revenue model in which it is assumed that the obtained revenue is zero if the allocated resource is less than the demand.
-Although this assumption is reasonable in some scenarios,
-%To develop a solution for the \MCSP, we first consider fractional revenue model.
-%However, algorithms for integral revenue model cannot achieve the same performance as the algorithms of this section i.e., \fcs and \focs.
-
-In the fractional model, the revenue of the CS from EV $i$ is directly proportional to the amount of resource that the EV is received, i.e.,
-		\begin{equation}
-			v_i^{\mathsf{f}}=\frac{\sum_t y_i^t}{D_i}v_i,
-			\label{Eq:partial_value}
-		\end{equation}
-		where $v_i$ is the gain, if the entire demand $D_i$ is fulfilled and $v_i^{\mathsf{f}}$ is the fractional gain.
-
-%Under fractional revenue model and without the binary variable of selecting EVs, the underlying problem turns into a linear one. 
-We propose a simple algorithm, called \fcs, with low computational complexity \rev{ of $O(n^2T+nT^2)$} for the fractional model that finds the optimal solution in offline setting.
-Note that even though linear programs can be solved in polynomial time in general, the complexity of our proposed algorithm is much lower than the general linear program algorithms.
-Moreover, our proposed offline algorithm applies a valley-filling strategy to reduce the peak.
-%The details of the proposed algorithm \fcs is given in~\cite{alinia2017online}.
-In the following, the online $2$-competitive algorithm is designed, where no exact information or stochastic modeling of future inputs of the problem is available.
-A summary of proposed algorithms with their complexity and assumptions is given in Table \ref{tbl:algs}.
-
-\revv{
-\subsection{Optimal Offline Design}
-\label{sec:fopt}	
-\bt{
-In this section, we propose an optimal algorithm for offline fractional model.
-As a natural solution, one may think of a greedy algorithm with the strategy as follows: at each time slot, charge the EV with highest unit-value and process others if only the resource cannot be used by this EV (probably due to maximum charging rate constraint).
-This approach is a popular, yet straightforward method in the online scheduling.
-However, it turns out that this approach cannot provide an optimal solution to the problem even in fractional revenue model.
-In fact, this approach only provides a 2-competitive solution.
-i.e., the profit obtained by the algorithm would be $1/2$ of the optimum.
-As an intuition of the proof think of two EVs where the one with lower unit value cannot wait due to its deadline and the EV with higher unit value has a long park time.
-Then, the optimal solution here could be first serving the EV with earlier deadline (and not the one with highest unit values).
-}
-
-We refer the proposed algorithm in this secion as the \fcs and summarize it as Algorithm~\ref{alg:optimal-off}.
-The \fcs works in two phases.
-In the first phase (Section~\ref{sec:ph1}), the algorithm decides on the amount of resource to be allocated to each EV within its availability window and reserves resources accordingly.
-In this phase, the details of allocation is not known.
-The actual resource allocation is done in the second phase (Section~\ref{sec:ph2}) by setting variables $y_i^t$.
-
-Before discussing the details of the algorithm, we give \bt{a definition} and introduce some notations to facilitate our algorithm design.
-
-\begin{defi}
-	Time interval $[\delta,\delta']$ is a ``super interval'' for interval $[t,t']$ if $1\leq \delta\leq t \text{~AND~} t' \leq \delta'\leq T$.
-	Moreover, $\mathcal{I}_{t,t'}$ is the set of all super intervals of interval $I_{t,t'}$ i.e., ${\mathcal{I}_{t,t'}=\{[\delta,\delta']: 1\leq \delta\leq t \text{~AND~} t'\leq \delta'\leq T\}}$.
-\end{defi}
-
-%		For example, $\mathcal{I}_{1,1}=\{I_{1,1},I_{1,2},I_{1,3},\dots ,I_{1,T}\}$. 
-The number of super intervals of an interval is at most $T^2$ and at least one (for interval $[1,T]$).
-
-Let $R_i$ be the amount of resource that is reserved for EV $i$ by the \fcs and $I_{t,t'}$ as time interval $[t,t']$.
-% with $t,t'\in\{1,\dots ,T\}$ which includes time slots $t,t+1,\dots ,t'$. 
-Then, assuming that charging demands are sorted in non-increasing order of their unit values, $A^i_j(t,t')$ is the aggregate residual resource in interval $I_{t,t'}$ at station $j$ assuming that the reservation for EVs $1$ to $i$ is accomplished.
-We now explain in detail each phase of the algorithm.
-
-\subsubsection{Phase I-Reservation\label{sec:ph1}} In Line~\ref{algline:sort1}, the EVs are sorted in a non-increasing order of their unit values.  
-%		i.e., ${v_1\slash D_1\geq v_2\slash D_2\geq\dots \geq v_n\slash D_n}$. 
-In Line~\ref{algline:setR}, the \fcs processes demand of EV $i$, picked from top of the ordered list, and sets $R_i$ as the amount to be reserved for EV $i$ which will be allocated in Phase II.
-In Line~\ref{algline:seta}, the residual resource of all intervals in set $\mathcal{I}_{a_i,d_i}$ decreases by $R_i$ and EV $i$ is added to the set of selected EVs.
-
-\begin{algorithm}[t]%\small%1
-	%\footnotesize
-	\revv{
-	\caption{\fcs}
-	\label{alg:optimal-off}
-	\DontPrintSemicolon 
-	\KwIn{$n$ EVs with their profile, local and global peak constraints $p_j, j=1,\dots ,m$ and $p^\mathsf{total}$ }
-
-	\KwOut{Optimal scheduling under fractional model}
-	\BlankLine
-
-	Sort charging requests in non-increasing order of their unit values, i.e., $\frac{v_1}{D_1}\geq \frac{v_2}{D_2}\geq\dots \geq \frac{v_n}{D_n}$\label{algline:sort1}
-
-	%	\slash\slash\textit{\texttt{Use sorted list to process demands}}
-
-	$\mathcal{L}\leftarrow \emptyset$
-
-	\slash\slash\textit{\texttt{Phase I}}
-
-	\For{$i=1,\ldots, n$}{
-		%\slash\slash\textit{\texttt{update demand and value}}
-
-		$R_i \leftarrow \min\{D_i, \min\limits_{t,t'} A^{i-1}_{h(i)}(t,t'), \forall t,t': I_{t,t'}\in\mathcal{I}_{a_i,d_i}\}$\label{algline:setR}
-
-		\If{$R_i>0$}{
-			$A^{i}_{h(i)}(t,t')\leftarrow A^{i-1}_{h(i)}(t,t')-R_i, \forall t,t': [t,t']\in\mathcal{I}_{a_i,d_i}$ \label{algline:seta}\\
-			$\mathcal{L}\leftarrow \mathcal{L}\cup{i}$
-	}}
-	\slash\slash\textit{\texttt{Phase II}}
-
-	Sort EVs in $\mathcal{L}$ in increasing order of their charging flexibility i.e., $\frac{(d_i-a_i+1)k_i}{D_i}, i\in \mathcal{L}$.
-
-	%	Let $i$ be the index of $i^{th}$ EV in list $\mathcal{L}$
-
-	\For{$i=1,\ldots, |\mathcal{L}|$}{
-
-		Pick EV $i$ from the sorted list $\mathcal{L}$.
-
-		$\emph{feasible}\leftarrow \big(\sum_{t=a_i}^{d_i}\min\{k_i,A^{i-1}_{h(i)}(t,t)\}\big) - R_i$
-
-		\If{feasible $<0$}{
-			Re-allocate previously allocated EVs such that $\emph{feasible}\geq 0$
-		}
-		Arbitrarily allocate $R_i$ to EV $i$ in its availability window\label{algline:fcsallocate}	
-	}}
-\end{algorithm}
-
-\begin{lem}
-	Provided that for EV $i$ we have 
-	\bee
-	\label{eq:ri}
-	R_i\leq\min\left\{D_i, \min_{t,t'} A^{i-1}_j(t,t'), \forall t,t': I_{t,t'}\in\mathcal{I}_{a_i,d_i}\right\}
-	\eee
-	 with a dummy $A^0_j(t,t')$ defined as
-$A^0_j(t,t')=(t'-t+1)\times\min \{p^\mathsf{total},p_{j}\},$
-	then there is a feasible allocation to allocate $R_i$ to EV $i$ in its availability window $[a_i,d_i]$. 
-	\label{thm:R_feasible}
-\end{lem}
-
-In Lemma \ref{thm:R_feasible}, $A^0_j(t,t')$ indicates the available resource when no charging request is processed in $I_{t,t'}$. 
-In Eq.~\eqref{eq:ri}, the second term, i.e., $\min_{t,t'} A^{i-1}_{j}(t,t')$, indicates the minimum remaining resource in all super intervals of interval $I_{a_i,d_i}$.
-For $i\geq 1$, $A^i_j(a_i,d_i)$ is defined as follows:
-
-\begin{equation*}
-A^i_j(a_i,d_i)=\begin{cases}
-A^{i-1}_j(a_i,d_i)-R_i & j=h(i),\\
-A^{i-1}_j(a_i,d_i) & j\neq h(i).
-\end{cases} 
-\end{equation*}
-
-The optimal value of $R_i, i=1,\dots ,n$ is set according to the following lemma:
-
-\begin{lem}
-	Given $n$ EVs sorted in a non-increasing order of the unit values, ${v_1\slash D_1\geq v_2\slash D_2\geq\dots \geq v_n\slash D_n}$, and the value of $R_i$, where $R_i$ is set after $R_{i-1}, i=2,\dots ,n$ by Eq.~\eqref{eq:ri}, then,
-	$$R_i = \min\left\{D_i, \min_{t,t'} A^{i-1}_{h(i)}(t,t'), \forall t,t':I_{t,t'}\in\mathcal{I}_{a_i,d_i}\right\},\forall i,$$
-	is the optimal value for $R_i$. 
-	\label{thm:R_star}
-\end{lem}
-
-\subsubsection{Phase II- Allocation\label{sec:ph2}} Lemma~\ref{thm:R_feasible} shows that there is a feasible scheduling to allocate the reserved resources.
-However, despite its feasibility, it is not straightforward to find such \revv{a schedule}.
-For example, assume that for EV $i$, $R_i=10$ and $k_i=4$.
-It is possible that all available resources are concentrated in a single time slot but EV $i$ cannot use more than $4$ kWh of it.
-In this situation, the previously allocated resources in interval $I_{a_i,d_i}$ should be re-allocated such that the concentrated resources are \emph{dispersed} and we have $\sum_{t=a_i}^{d_i}\sigma_t \geq R_i$ where $\sigma_t =\min\{k_i,A^{i-1}_{h(i)}(t,t)\}$ is the maximum resource that can be allocated to EV $i$ at time slot $t$.
-Since the total amount of allocated resource does not change in the interval, such dispersion is possible and can be done by a simple algorithm in which allocates $\min\{k_i,A^{i-1}_{h(i)}(t,t)\}$ starting from time slot $t=a_i$ until $R_i$ units is allocated.
-To further reduce the peak of the system, we will develop \sa\ algorithm (See Section \ref{sec:integral}) which acts more intelligent so that Line \ref{algline:fcsallocate} of the \fcs can be replaced by ``Run \sa$(i,R_i)$''.
-
-\begin{thm}
-	\label{cor:1}
-	\fcs is an optimal solution under fractional revenue model.
-\end{thm}
-
-The following theorem characterizes the complexity of \fcs.
-
-\begin{thm}
-	\label{thm:complexity}
-	The time complexity of \fcs algorithm is $O(n^2T+nT^2)$ where $n$ is the number of EVs and $T$ is number of time slots.
-\end{thm}
-}
-
-%\vspace{-4mm}
-\subsection{Online Scenario}
-\label{sec:fonline}
-In this section, we devise an algorithm for the scenario that EVs arrive in online fashion.
-The scheduling decisions at each time slot are made given the information of available EVs and neither exact values nor stochastic modeling of future arrivals is available.
-Our goal is to obtain a \emph{competitive ratio} for the online algorithm.
-A scheduling algorithm $\mathcal{A}$ is $c$-competitive for $c\geq 1$ if the revenue obtained by the optimal offline algorithm is at most $c$ times the algorithm $\mathcal{A}$'s revenue for any input sequence~\cite{borodin2005online}.
-
-The proposed online algorithm for the fractional model, referred to as \focs, is listed as Algorithm~\ref{alg:focs}.
-The \focs is a simple yet efficient algorithm that always selects EVs with highest unit value to allocate as follows.
-First, the algorithm sorts the available EVs at each time slot~$t$ based on their unit value (Line~\ref{algline:sort}).
-\revv{In this step, the algorithm breaks ties based on EVs' deadline i.e., if two EVs have the same unit value, then the one with earliest deadline comes first in the sorted list.} Next, the \focs selects one EV at a time from the sorted list to allocate with maximum charging rate considering the EV's remaining demand, maximum charging rate, and peak constraints (Lines~\ref{algline:focsfor}-\ref{algline:focssety}).
-The allocation is continued until all resources are allocated or there is no more EV that could be allocated.
-%For unselected EVs, the value of $y_i^t$ will be $0$ in Line \ref{algline:focssety} of the algorithm. 
-The time complexity of the \focs is $O(n^2T)$, determined by cost of its ``\textbf{for}'' loop multiplied by total number of times that the algorithm needs to be run.
-% i.e., $T$.
-
-%\vspace{-4mm}
-\begin{algorithm}%\small%1
-\footnotesize
-\caption{\focs: $\forall t\in \{1,2,\dots ,T\}$}
-\label{alg:focs}
-\DontPrintSemicolon 
-%\KwIn{Available EVs at time slot $t$, number of CSs $m$, local peak constraint $p_j, j=1,\dots ,m$, global peak constraint $p^{\textrm{total}}$}
-
-%\KwOut{A feasible charging scheduling}
-
-%$\backslash\backslash\texttt{Initialize:}$
-
-\BlankLine
-
-$\mathcal{M}^t\leftarrow$ The set of available EVs that not received their entire demand by $t$
-
-Sort EVs in set $\mathcal{M}^t$ indexed by $i=1,\dots ,|\mathcal{M}^t|$: $v_1/D_1\geq v_2/D_2\geq\dots\geq v_{|\mathcal{M}^t|}/D_{|\mathcal{M}^t|},$  \revv{where ties are broken based on users' deadline (giving priority to the users with earliest deadline) }\label{algline:sort}
-
-\For{$i=1,\ldots,|\mathcal{M}^t|\label{algline:focsfor}$}{
-
-$y_i^t\leftarrow \min\{k_i,D_i-\sum_{\tau=a_i}^{t}y_i^{\tau},p_{h(i)}-\sum_{i':h(i')=h(i)}y_{i'}^t,p^{\textrm{total}}-\sum_{i'}y_{i'}^t\}$ \label{algline:focssety}
-
-}
-
-\end{algorithm}
-Despite the simplicity of \focs which makes it easy to implement, its performance is sound and within a constant factor of the offline optimum.
-We now proceed to analyze the performance of the \focs by first giving some preliminaries.
-
-Fix an optimal scheduling and let $\mathcal{S}_{\focs,t}$ and $\mathcal{S}_{\opt,t}$ be the sets of EVs selected by the \focs and optimal solution at time slot $t$, respectively.
-Let $y_{i}^t$ and $z_{i}^t$ be the charging rate of EV $i$ set by \focs and \opt, respectively.
-We define $\Delta_{i}^t$ as follows:
-\begin{equation}
-\label{eq:delta}
-\Delta_{i}^t =
-     \begin{cases}
-       \min\{z_{i}^t-y_{i}^t,r_{i,t}\} &\quad i\in\mathcal{S}_{\opt,t},z_{i}^t>y_{i}^t, \\
-       0& \quad\text{otherwise},  \\
-     \end{cases}
-\end{equation}
-where $r_{i,t}$ is the remaining demand of EV $i$ by the end of time slot $t$.
-$\Delta_{i}^t>0$ indicates that the optimal algorithm allocated $\Delta_{i}^t$ units more resources to EV $i$ than the \focs by time slot $t$ that could be \emph{feasibly} allocated by \focs to the EV $i$.
-If for any EV $i\in\mathcal{S}_{\opt,t}$ and time slot $t\in\mathcal{T}$ we have $y_{i}^t=z_{i}^t$, i.e., $\Delta_{i}^t=0$, then the \focs is obviously optimal because it gains whatever the optimal solution gains.
-\rev{We define \textit{loss} of the \focs imposed by EV $i$ as follows:
-\begin{equation}
-\label{lBj0}
-l_{i,t}=\Delta_{i}^t\frac{v_i}{D_i},
-\end{equation}
-
-Note that the loss always takes a non-negative value as $\Delta_i^t\geq 0$.} When \focs sets charging rate of an EV less than its rate in the optimal solution, it gains $\Delta_{i}^t v_i/D_i$ less than the optimal solution from that EV.
-An upper bound for the distance between the optimal objective value (denote by \opt) and the revenue of the \focs (denote by \alg) is summation of the losses over all time slots and all EVs, i.e.,
-\begin{equation}
-\label{eq:optdist}
-\opt-\alg\leq \sum_{t=1}^T\sum_{i\in\mathcal{S}_{\opt,t}} l_{i,t}.
-\end{equation}
-
-%Notice that it is possible that an algorithm does not choose any selected EV by a particular optimal solution but still provide an optimal or near-optimal solution as there can be multiple optimal solutions.
-In particular, $\mathcal{S}_{\focs,t}\cap \mathcal{S}_{\opt,t}=\emptyset, \forall t$ cannot lead to any conclusion on the competitive ratio of the \focs.
-In addition to the amount of loss, the gain of the algorithm from charging alternative EVs should also be taken into account in comparison between \opt and \alg.
-
-Let $i\in\mathcal{S}_{\opt,t}$, $i\notin\mathcal{S}_{\alg,t}$ and $g_{i,t}$ be the gain that the \focs obtains from charging another EV instead of $i$ at time slot $t$.
-We are going to show that in the \focs, for each EV $i$ with $l_{i,t}>0$ there must be another EV (denote by $i'$) where $y_{i'}^t\geq \Delta_i^t$ and $\frac{v_{i'}}{D_{i'}}\geq \frac{v_i}{D_i}$ which means in resource allocation phase for EV $i$, the \focs allocated the difference $\Delta_i^t$ to another EV with the same or higher unit value.
-This can be proved by considering the fact that (i) the selected EVs have higher unit values than the unselected EVs, and (ii) the charging rate of the selected EVs are set to the maximum feasible value.
-Moreover, the \focs is \emph{``work-conserving''} i.e., it does not let any resource remain unused if there are some EVs that can use it.
-
-Let $g_{i,t}$ denote the gain that \focs obtains from allocating the same amount of resource that optimal algorithm allocated to EV $i$ (with size $z_i^t$) to another EV(s).
-If $\Delta_{i}^t=0$, the loss is zero. If $\Delta_{i}^t>0$, then by the charging strategy that the \focs uses we can conclude that (i) $i$ is not finished by the \focs, and (ii)
-\rev{no more resources from station $p_{h(i)}$ can be feasibly allocated,} otherwise, the \focs could allocate more resources to EV $i$.
-Therefore, the $\Delta_{i}^t$ units of the resource \rev{are} allocated to one or multiple other EVs (denote them by set $\mathcal{J}_i^t$) by the \focs.
-Moreover, it must hold that all the EVs in set $\mathcal{J}_i^t$ have a unit value equal to or higher than $v_i/D_i$ which yields $g_{i,t}\geq l_{i,t}$, otherwise, the \focs should not prefer the EVs in $\mathcal{J}_i^t$ to $i$.
-\rev{Since the result holds for any arbitrarily EV $i$, we can get the following:}
-
-\begin{equation}
-\label{eq:lg}
-\sum_{i=1}^n\sum_{t=1}^Tl_{i,t}\leq\sum_{i=1}^n\sum_{t=1}^Tg_{i,t}.
-\end{equation}
-
-Moreover, the total gain of \focs, i.e., \alg, is equal to sum of its gains from each single EV:
-\begin{equation}
-\label{eq:ALG}
-\rev{\alg= \sum_{i=1}^n\sum_{t=1}^Tg_{i,t}.}
-\end{equation}
-
-With the above discussion and using Eqs. (\ref{eq:optdist}), (\ref{eq:lg}) and (\ref{eq:ALG}) we are able to derive a competitive ratio of $2$ for the \focs.
-
-\begin{thm}
-	\label{thm:focscompetitive}
-	The \focs is $2$-competitive.
-\end{thm}
-
-\emph{Remarks:} When there is only one CS and EVs have no limit on their charging rate, the \focs is identical to the \textsc{FirstFit} algorithm ~\cite{firstfit} which is known to be $2$-competitive for classic job scheduling problem.
-However, the charging rate limitation is crucial for EV charging problem.
-Moreover, \cite{firstfit} uses \revv{a} ``charging argument'' to prove the competitive ratio of the proposed algorithm which cannot be directly applied to our problem.
-Thus, the \focs extends the \textsc{FirstFit} and makes it practical for the EV charging scenario.
-Moreover, the proof technique used for the competitive analysis of the \focs is fundamentally different from the one used in \cite{firstfit}.
-%%%Finally, in~\cite{Robu} an online $2$-competitive algorithm for EVs with partial charging is proposed.
-The competitive ratio obtained assuming that charging of EVs is instantly reversible at departure times.
-This assumption is not practical in reality since similar to charging phase, there is a discharging rate constraint for EVs.
-
-%\begin{thm}
-%\label{thm:focscomplexity}
-%
-%The time complexity of \focs is $O(nT\log n)$.
-%\end{thm}
-		\section{Integral Revenue Model}
-		\label{sec:integral}
-%
-%		\subsection{Overview of Integral Revenue Model}
-%		\label{sec:intoverview}
-		The MILP form of the \MCSP in integral model is a generalized form of the $0/1$-knapsack problem which is a well-known NP-hard problem.
-\rev{To give an intuition, consider the scheduling problem in a single time slot (i.e, $T=1$).
-Then, allocating power resources to the EVs is equivalent to allocating the capacity of knapsack to the items.
-}
-		In Section~\ref{subsec:icsalgorithm}, we propose a fast polynomial time offline approximation algorithm for the integral problem.
-In Section~\ref{sec:onlineint}, we extend the result and propose an online algorithm for the integral model.
-%		, where the EVs arrive in slot-by-slot fashion, and the scheduler has no information of the future arrivals.
-
-%The problem is even more challenging when the uncertainty in EVs' arrival is taken into account.
-At each time slot, the scheduler has no information of unit values of the future charging profiles.
-Therefore, the scheduler cannot make sure about the efficiency of its current charging decision.
-%It can be shown that when there is no assumption on the charging profiles of EVs (including the value of slackness parameter) and the charging decision , no online algorithm can provide a performance guarantee meaning that in the worst case, the ratio of the optimal objective value to the one obtained by the online algorithm can be arbitrary small.
-In fact, when the online algorithm selects
-
-		\subsection{Offline Scenario}   
-		\label{subsec:icsalgorithm}
-		We design our offline scheduling algorithm under integral model referred to as \ics, to solve the \MCSP approximately. 
-%		Our algorithm design is inspired by the basic algorithm proposed in \cite{Jain}.
-The algorithm in \cite{Jain} works for a single CS where arrival time of all EVs are the same and there is no global peak constraint.
-Since the performance analysis of the proposed algorithm relies on a dual fitting method and utilizes weak duality property, \revv{we first need to construct the dual problem of \MCSP.
-Toward this, we introduce variables $\alpha, \beta, \gamma$ and $\pi$.
-Generally, in primal-dual approximation algorithm design, each constraint (resp.
-variable) in primal (resp.
-dual) problem is associated with a variable (resp.
-constraint) in dual (resp.
-primal) problem.
-In our case, constraints (\ref{ConstPartial}) (\ref{ConstTotal}), (\ref{ConstLocal}) and (\ref{ConstSpeed}) in the \MCSP are respectively associated with dual variables $\alpha, \beta, \gamma$ and $\pi$ (for more details see \cite{approx}).
-The dual problem is formulated as follows:}
-		\bse
-		\bee
-		\min &&\sum_{i=1}^n D_i\alpha _i + \sum_{j=1}^m \sum_{t=1}^T p_j\beta (t)+\sum_{t=1}^T p^\mathsf{total}\gamma (t)\nonumber\\ 
-		\textrm{s.t.} && \alpha _i+\beta (t) +\gamma _i + \pi (t)- \frac{k_i}{D_i}\sum_{t'=a_i}^{d_i} \pi _i(t^\prime) \geq \frac{v_{i}}{D_i},\label{ConstDcover} \nonumber\\
-		&& \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\forall i, t\in [a_i, d_i],\\
-		\textrm{vars.}&&\alpha _i, \beta _i, \gamma,  \pi _i(t)\geq 0,\quad\quad\forall i,t. \nonumber
-		\eee
-		\ese
-
-		%%%In this section, we explain \ics in details and then in Section~\ref{subsec:analysis}, we analyze approximation factor of the algorithm. The \ics algorithm is listed as Algorithm~1.
-
-		\subsubsection{Explanation of the Main Algorithm} 
-		\label{sec:icsexplanation}
-		Our algorithm design is inspired by the basic algorithm proposed in \cite{Jain}.
-\revv{The algorithm in~\cite{Jain}, however, works for a single CS where arrival time of all EVs are the same and there is no global peak constraint.}
-		The \ics algorithm (listed as Algorithm \ref{alg:ics}) works in two phases.
-In the first phase it sorts the charging requests based on their unit values in a non-increasing order.
-Then, it selects most valuable demand.
-If the remaining resource is enough to cover the \emph{entire} demand of the EV, it is admitted to receive the demand (Lines~$6$-$7$).
-%		When \ics processes EV $i$, the algorithm checks for the feasibility of allocating $D_i$ units of the resource within its availability window $[a_i,d_i]$ without violating the constraints related to the maximum charging rate $k_i$, local and global peaks (Lines~$6$-$8$).
-
-		\emph{Scheduling of the Selected EV:} \revv{If the feasibility check passed (Line 6 in Algorithm 3)}, \ics calls sub-procedure \sa\ to allocate required resources in interval $[a_i,d_i]$.
-Then, $\alpha _i$ is set to $v_i\slash D_i$ in order to cover dual constraint in Eq.~\eqref{ConstDcover} (Lines~$7$-$8$).
-
-		In \sa, 
-		%%%When EV $i$ is selected to get charged, \sa\ is called for the charging scheduling. 
-		let us define $W(t,h(i))=\sum_{i': h(i')=h(i)} y_{i'}^t$ as total workload at time slot $t$ in CS $h(i)$ and $\bar{W}(t,h(i))$ as total available load to allocate at time slot $t$ for CS $h(i)$.
-We always have ${\bar{W}(t,h(i))+W(t,h(i))=p_{h(i)},  \forall t, i}$.
-For scheduling, \sa\ applies two main policies: 1) \emph{valley-filling} and, 2) \emph{right-to-left allocation}.
-\revv{With valley-filling, the slots with more available resources are preferred which helps to reduce the peak of the system.} %%%It also can be seen as a smoothing method which tries to reduce the variance of the allocated resources at different slots.
-%				The simulation results in Section \ref{sec:simul} will confirm this claim. 
-				Right-to-left allocation is used when two or more time slots are equal in terms of their remaining resources. 
-%				When this policy applies on scheduling of EV~$i$, any EV~$i'$ with $i'>i$ and $d_{i'}<d_i$ has more chance to get charged since the algorithm tends to charge EV $i$ in interval $[d_{i'}+1,d_i]$ (i.e., right hand part of the EV's availability window) and keeps resources in $[a_{i'},d_{i'}]$ for EV $i'$.
-A ranking based approach is used to apply the aforementioned policies. 
-		To charge  EV $i$, \sa\ ranks time slots in interval $[a_i,d_i]$.
-Then, charging is done by allocating resources from the higher ranked time slot to lowest one.
-The rank of a time slot $t$ is calculated based on remaining resources in the time slot (valley-filling) and value of $t$ (right-to-left allocation).
-
-		\begin{algorithm}%\small%1
-			\footnotesize
-			\caption{\ics}
-			\label{alg:ics}
-			\DontPrintSemicolon 
-%			\KwIn{$n$ EVs with $a_i, d_i, v_i, D_i,$ and $k_i$ associated with each EV $i$, $m$ CSs, local and global peak constraints $p_j, j=1,\dots ,m$, and $p^\mathsf{total}$}
-
-%			\KwOut{A feasible scheduling of EVs}
-			\BlankLine
-			%\begin{algorithmic}
-
-			%\slash\slash\textit{\texttt{Initialization}}
-			\textbf{initialize}: $y\leftarrow 0, \alpha\leftarrow 0, \beta\leftarrow 0, \gamma\leftarrow 0, \pi\leftarrow 0$
-
-			Sort charging requests in non-decreasing order of their unit values: $v_1/D_1 \geq v_2/D_2\geq\dots \geq v_n/D_n$
-%			$\frac{v_1}{D_1} \geq \frac{v_2}{D_2}\geq\dots \geq \frac{v_n}{D_n}$
-%			\slash\slash\textit{\texttt{Use sorted list to process demands}}
-
-			\For{(i=1\dots n)}{
-
-				\For{$t=a_i\dots d_i$}{
-					$\sigma_t\leftarrow  \min\Big\{p_{h(i)}-\sum_{i':h(i')=h(i)}y_{i'}(t),$ \newline $\qquad p^\mathsf{total}-\sum_{i'=1}^n y_{i'}^t,k_i\Big\}$
-
-				}
-
-%				\slash\slash\textit{\texttt{if enough resources remain for EV $i$}}
-
-				\If{$D_i\leq\sum_{t=a_i}^{d_i}\sigma_t$}
-				{
-					\sa($i,D_i$)\\
-					$\alpha _i\leftarrow v_i/ D_i$
-				}
-				\Else {
-					\If{$(\beta (d_i)=0)$}{
-						\bc($i$)}
-				}
-			}
-
-			\For{(i=1\dots n)}{ 
-				\If {EV $i$ is not selected}{
-					\rc($i$);
-				}
-			}
-			%\end{algorithmic}
-		\end{algorithm}
-
-\emph{Dual Feasibility of the Non-selected EVs:} \bt{If remaining power resource is not enough} to fully charge EV $i$, i.e.,  $D_i>\sum_{t=a_i}^{d_i}\sigma_t$, the EV cannot be selected.
-However, we still need to satisfy constraint~\eqref{ConstDcover} in dual problem which is done by calling \bc($i$).
-To cover the constraint~\eqref{ConstDcover} for EV $i$, sum of dual variables for all $t\in [a_i ,d_i]$ should be greater than or equal to ${v_i \slash D_i}$.
-\bc($i$) sets $\beta (t)$ to ${v_i \slash D_i}$ for all time slots $t$ in interval $[t_\mathsf{cov}, R(d_i)]$ (Lines $3$-$4$ of Algorithm~\ref{alg:betacover}).
-Observe that  ${\beta (t^\prime)\geq v_i \slash D_i,\forall t^\prime< t_\mathsf{cov}}$ (with $ t_\mathsf{cov}>1$) considering that the demands are sorted in a non-increasing order of the unit-values and $\beta (t')$ is already set to ${v_{i'} \slash D_{i'}}$ when processing the earlier charging demand of EV $i'$ which is not selected.
-Hence, ${v_{i'}\slash  D_{i'}\geq v_i \slash D_i}$, thereby ${\beta (t)\geq v_i \slash D_i,}$ and the dual constraint in~\eqref{ConstDcover} is satisfied.
-		Lines $1$-$4$ of \bc\ is enough to cover the dual constraint.
-However, the algorithm continues in Lines $5$-$8$ by setting a variable $\Phi_{i'}(t)$ for time slots $t=1,\dots ,R(d_i)$ to a value dependent to amount of the resource that a selected EV $i'$ received at slot $t$.
-$\Phi_{i'}(t)$ will be used in approximation analysis of the main algorithm and has no effect on the scheduling of EVs.
-		%We borrowed algorithm \bc($i$) from \cite{Jain} and adjusted it for multiple station mode.		
-%		\vspace{-3mm}
-		\begin{algorithm}%\small%1
-			\footnotesize
-			\caption{\sa($i,D_i$)}
-			\label{SmartAllocate}
-			\DontPrintSemicolon 
-			\KwIn{EV $i$ to receive $D_i$ from CS $h(i)$}
-
-			Rank time slots in interval $[a_i,d_i]$ such that for any $t_1$ and $t_2$:
-			$\mathsf{rank}(t_1)> \mathsf{rank}(t_2)$ iff $\bar{W}(t_1,h(i))>\bar{W}(t_2,h(i))$ OR $\bar{W}(t_1,h(i))==\bar{W}(t_2,h(i)) \wedge t_1>t_2$
-
-			\While {$\sum_{t'=a_i}^{d_i}y_i^{t'}\neq D_i$}{
-
-				Select time slot $t$ with highest rank which is not selected before
-
-				Allocate $\min \left\{k_i,\bar{W}(t,h(i)),D_i-\sum_{\tau=a_i}^{t}y_i^{\tau},p^{\textrm{total}}-\sum_{i'}y_{i'}^t\right\}$ to EV $i$ at $t$
-
-			}
-		\end{algorithm}	
-%		\vspace{-7mm}	
-		\begin{algorithm}%\small%1
-			\footnotesize
-			\caption{\bc($i$)}
-			\label{alg:betacover}
-			\DontPrintSemicolon 
-			%\KwIn{EV $i$ which is not selected to charge}
-
-			\BlankLine
-
-			$t_\mathsf{cov}\leftarrow \min \{t: \beta (t)=0\}$
-
-			$R(d_i)=\max \{t\geq d_i : \forall t^\prime\in (d_i,t], \bar{W}(t^\prime)<q_{h(i)} \}$
-
-			\For{$(t=t_\mathsf{cov}\dots R(d_i))$}{
-				$\beta (t)\leftarrow v_i/D_i$
-			}
-
-			\For{$(t=1\dots R(d_i))$}{
-				\For{$(i'=1\dots n))$}{	
-					\If{$y_{i'}^t>0 \wedge \Phi_{i'}(t)=0$}{
-						$\Phi_{i'}(t)\leftarrow\big[ \frac{p_{h(i)}}{p_{h(i)}- k_i}\frac{s}{s-1}\big] .\frac{v_i}	{D_i}y_{i'}^t$
-					}
-				}
-			}
-		\end{algorithm}
-%		\vspace{-7mm}
-		\begin{algorithm}%\small%1
-			\footnotesize		
-			\caption{\rc($i$)}
-			\label{Replace}
-			\DontPrintSemicolon 
-%			\KwIn{EV $i$}
-%			\KwOut{Updated schedule}
-
-			$\mathcal{L} \leftarrow \emptyset$\\			
-			$v_\mathsf{inc}\leftarrow v_i$\\			
-			$\sigma_t\leftarrow 0, t=a_i,\dots ,d_i$
-
-			%Define $\delta_i(t)=\min \{k_i,\bar{W}(t,h(i))\}$
-
-			%$\Delta\leftarrow \sum_{t=a_i}^{d_i}\min\{\bar{W}(t,h(i)), k_i\}$
-
-			\For{($i' =i-1\dots 1$)}{ 
-				\If {EV $i'$ is selected $\wedge (h(i')=h(i)) \wedge (v_\mathsf{inc}-v_{i'})>0$}{
-					Add EV $i'$ to list $\mathcal{L}$
-
-					$v_\mathsf{inc}\leftarrow v_\mathsf{inc}-v_{i'}$
-
-					\For{($t=a_i\dots d_i$)}{
-						$\sigma _t\leftarrow\sigma_t + \min\{k_i,y_{i'}^t\}$
-					}
-				}
-			}
-
-			\If {$\sum_{t=a_i}^{d_i}\sigma_t\geq D_i$}{
-				Remove EVs in list $\mathcal{L}$ from charging schedule
-
-				\sa($i,D_i$)
-			}
-		\normalsize
-		\end{algorithm}
-
-		\emph{Improving the Gain:} In the second phase, the \ics tries to increase total value of selected EVs by calling \rc($i$) on every unselected EV $i$ (Lines~$12$-$14$).
-\rev{The \rc(i) (listed as Algorithm $6$) checks that whether the total revenue can be increased by replacing some selected EVs with EV $i$ or not (Lines $4$-$9$).
-If such EVs are found, the algorithm stops their charging and allocates EV $i$ using \sa\ (Lines $10-12$).}
-		%We refer to ~\cite{alinia2017online}, for the details and intuition behind this algorithm. 
-%		Before giving the details of \rc($i$), we first explain the intuition behind this algorithm. 
-%		 Note that if in the scheduling problem we set $T=1, m=1, k_i=p^\mathsf{total}, a_i=d_i=1\ \forall i$, then the problem is equal to the well-known $0$-$1$ knapsack problem~\cite{approx}.
-In the knapsack problem, a widely used greedy approach sorts items based on their unit values and selects items accordingly.
-It turns out that in this approach the approximation factor can be arbitrarily bad.
-For example, consider a knapsack problem with two items with $v_1=2, v_2=p^\mathsf{total}, D_1=1$, and  $D_2=p^\mathsf{total}$.
-Given these values we have $v_1\slash D_1>v_2\slash D_2$.
-To maximize total value of selected items, the optimal solution chooses item $2$ while greedy algorithm selects item $1$ which results in a worst-case approximation factor of ${c \slash \opt}$ in general where $c$ is a constant (in this example $c=2$).
-To resolve it, one approach is to \emph{re-consider} unselected items after running greedy algorithm and replace some selected items in the knapsack with unselected ones and then check whether the result is improved or not.
-In a simple case, only the largest unselected item can be examined which makes a significant theoretical improvement by providing a worst case approximation factor of $\opt\slash 2$.
-%		 
-%\ics algorithm leverages the same idea but using a more intelligent replacing method called \rc($i$).
-\rc($i$) is called on every unselected EV $i$.
-It tries to find some selected EVs that if they are replaced by EV $i$, total revenue from the selected EVs increases.
-%%%When \ics calls \rc($i$) on all unselected EVs, an improvement in total revenue of final selected EVs is expected.
-%This is confirmed by the simulation results in Section~\ref{sec:simul}.
-
-		\subsubsection{Analysis}
-		\label{subsec:analysis}
-		In primal-dual algorithm, the goal is to design an algorithm in a way that it produces a good solution for primal problem (with primal value $\Gamma$) and a feasible solution for the dual problem (with dual value $\Lambda$).
-Then, assuming that the primal problem is a maximization problem, to prove that the algorithm is $c-$approximation (for $c\geq 1$), the important part is to show that $\Lambda\leq c\Gamma$.
-Then, based on weak duality theorem we have $\Lambda\geq \opt$, and it is concluded that $\Gamma \geq \frac{1}{c}\times\opt$ where $\opt$ is the optimal value.
-		Based on the above understanding, the following theorem scrutinizes the approximation ratio of the \ics assuming that arrival times are the same for all EVs. 
-%		First note that the designed scheduling algorithm outputs a feasible scheduling since it respects the constraints in the primal problem.
-Also, the algorithm produces a feasible solution for the dual problem by covering the dual problem constraint in (\ref{ConstDcover}) through setting $\alpha _i$ to $\frac{v_i}{D_i}$ when EV $i$ is accepted and, $\beta (t)$ to a value greater than or equal to $\frac{v_i}{D_i}$ for $t\in [a_i, d_i]$ (according to the discussion in Section \ref{sec:icsexplanation}) if EV $i$ is not selected.
-To obtain an approximation factor for the algorithm, it is enough to bound the total covering cost of the dual constraints.
-
-		\begin{thm}
-			\label{thm:approx}
-			\ics algorithm is a $\Big( 1+ \sum_{j=1}^m {\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}\Big)$-approximation when EVs have same arrival time.
-		\end{thm}
-%		
-%		\begin{proof}
-%			In Appendix~\ref{app:1}.
-%		\end{proof}
-
-		Note that in the case that the system is flexible enough, i.e., $s\gg 1$, and the maximum charging rates of stations are much bigger than those of EVs, i.e., $p_j \gg q_j, \forall j$, the approximation ratio approaches $m+1$.
-And in the case that there is one single station, the approximation ratio is $2$.
-%		 Finally, we provide the time complexity of the \ics.
-
-%\begin{thm}
-%\label{thm:ics_complexity}
-%The time complexity of the \ics algorithm is $O(nT\log T+n^2T)$.
-%\end{thm}	
-%
-%\begin{proof}
-%In Appendix \ref{app:ics_complexity}.
-%\end{proof}
-
-\subsection{Online Scenario}
-\label{sec:onlineint}
-Due to the binary selection variable, the online solution design under integral model is more challenging than the one for fractional model.
-We propose the \iocs that is built upon the offline \ics.
-In particular, the \iocs calls the \ics at each time slot for the set of available EVs, however, any algorithm that is designed for offline integral model can be used alternatively.
-Hereinafter, $\mathcal{A}$ refers to the \ics or a similar algorithm.
-
-\begin{algorithm}%\small%1
-\footnotesize
-\caption{\iocs: $\forall t\in \{1,2,\dots ,T\}$}
-\label{alg:iocs}
-\DontPrintSemicolon 
-%\KwIn{$n$ EVs to arrive on the fly, number of CSs $m$, global peak constraint $p^{\textrm{total}}$, local peak constraints $p_j, j=1,\dots ,m$}
-
-%\KwOut{A feasible charging scheduling}
-
-\BlankLine
-
-Let $\mathcal{A}$ be an algorithm that solves the problem with $a_1=\dots =a_n$
-
-$\mathcal{R}^t\leftarrow$ set of EVs arrived at time slot $t$
-
-$\mathcal{M}^t\leftarrow \mathcal{R}^t\cup \{i: t\in\mathcal{T}_i\ \texttt{AND}\ \sum_{t^\prime}y_{i}^{t'}<D_i\}$
-
-%$\backslash\backslash\texttt{Schedule 1}$
-
-Based on the residual in interval $[t,T]$, use algorithm $\mathcal{A}$ to allocate EVs in set $\mathcal{R}^t$ assuming no further arrivals
-
-$\mathcal{S}_{\iocs,t}\leftarrow\{i:i\in\mathcal{M}^t\ \texttt{AND}\ i$ is admitted at $t\}$
-
-$\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}\leftarrow \sum_{i\in\mathcal{S}_{\iocs,t}}v_i$
-
-Assume all reserved resources are freed at time slots $t, t+1, \dots, T$
-
-%$\mathcal{R}^t\leftarrow\mathcal{M}^t$
-
-%$\backslash\backslash\textsl{set of active EVs at time slot t}$
-
-$r_{i,t}\leftarrow$ remaining demand of $i$ at $t, \forall i$
-
-%$\backslash\backslash\texttt{Use modified demands values}$
-
-$D_i^\prime\leftarrow r_{i,t},\ \ v_i^\prime\leftarrow \frac{r_{i,t}}{D_i}v_i, \forall i\in\mathcal{M}^t$
-
-%$\backslash\backslash\texttt{Schedule 2}$
-
-Run $\mathcal{A}$ on $\mathcal{M}^t$ using $D_i^\prime$ and $v_i^\prime, \forall i$ and reconstruct $\mathcal{S}_{\iocs,t}$
-
-$\Gamma_{\mathcal{A},\mathcal{M}^t}\leftarrow \sum_{i\in\mathcal{S}_{\iocs,t}}v_i$ $\backslash\backslash\texttt{Use original values}$
-
-%$a\leftarrow\frac{V^\prime_{\textrm{total}}}{V_{\textrm{total}}}$
-
-\If{$\Gamma_{\mathcal{A},\mathcal{M}^t}>\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$}{
-
-Use the second schedule
-
-}
-
-\Else{
-
-Use the first schedule
-
-}
-
-\end{algorithm}
-
-The \iocs is summarized as Algorithm~\ref{alg:iocs}.
-At slot $t$, the \iocs compares two scheduling results returned by $\mathcal{A}$ and chooses among them.
-In the first scheduling, the \iocs keeps all reserved resources in interval $[t,T]$ intact.
-Then, for utilizing the remaining resources, the algorithm runs $\mathcal{A}$ over arrived EVs at time slot $t$.
-In this case, the total revenue obtained by the \emph{active} EVs (i.e., EVs that are available but not received their entire demand yet) is denoted by $\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$ (Line $6$ of the algorithm).
-In the second scheduling, the \iocs considers the case that it can sacrifice the previously admitted EVs by canceling their reservations and allocating the freed resources to more valuable demands.
-For this purpose, the algorithm modifies the demand and valuation of the previously admitted EVs such that each demand is replaced by the EV's remaining demand, and the valuation of the EV is proportionally calculated based on the remaining demand (Line $9$ of the algorithm) so that the unit values of EVs do not change.
-Then, the \iocs runs $\mathcal{A}$ over set of active EVs $\mathcal{M}^t$ where the corresponding gain is denoted by $\Gamma_{\mathcal{A},\mathcal{M}^t}$.
-If $\Gamma_{\mathcal{A},\mathcal{M}^t}>\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$, the \iocs forgets the previously admitted EVs and follows the second scheduling.
-
-\begin{comment}
-%We now introduce some notations and then analyze the performance of \iocs. 
-Let $\mathcal{S}_{\iocs,t}$ and $\mathcal{S}_{\opt,t}$ be set of active EVs at time slot $t$ that are selected for charging by \iocs and \opt (fix a particular optimal solution), respectively.
-Note that the set of active EVs for \iocs and \opt might be different.
-%Moreover, define  $\mathcal{U}_{\iocs,t}=\mathcal{S}_{\iocs,1}\cup\dots\cup \mathcal{S}_{\iocs,t}$ and $\mathcal{U}_{\opt,t}=\mathcal{S}_{\opt,1}\cup\dots\cup \mathcal{S}_{\opt,t}$. 
-Having $i\in\mathcal{S}_{\iocs,t}$ means that based on the updated schedule at time slot $t$, enough resources reserved for EV $i$ so that the EV will receive its demand $D_i$ before the deadline $d_i$.
-However, the schedule may change at each slot and $i\in\mathcal{S}_{\iocs,t}$ cannot be a guarantee for EV $i$ to fully receive its demand.
-In fact, users and the scheduler itself have to wait until the deadline of the EV to find out that the demand is fulfilled or not.
-This is because the scheduler may cancel some reservations in the next time slots and allocate the freed resources to other EVs.
-\end{comment}
-% (when Algorithm \ref{alg:iocs} uses the second schedule in Line $15$). 
-%Define $A_t$ as the minimum gain of \iocs when the algorithm visited time slots $1$ to $t$.
-More formally, $A_t=\sum_{i\in\mathcal{U}_{\iocs,t}}v_i$.
-$A_t$ is the minimum gain that \iocs will obtain by the end of time slot $t$, having the information of released demands up to time slot $t$.
-Notice that the algorithm may continuously improve its set of selected jobs to increase its gain such that $A_t\geq A_{t-1}, t\in\{2,\dots, T\}$.
-$A_t$ is formally defined as follows:
-
-The following theorem characterizes the competitive ratio of the \iocs in a special case. 
-\begin{thm}
-\label{thm:iocscompetitive}
-Let $\mathcal{A}$ be \ics in \iocs algorithm and $m=1$.
-Assuming that EVs are released in $b$ distinct groups where arrival time of EVs in each group are the same, the \iocs is $b\Big(1+\frac{p}{p-q}\frac{s}{s-1}\Big)$-competitive with optimal offline solution, where $p$ is the station peak and $q=\max_i k_i, i=1,\dots ,n$.
-\end{thm}
-
-%\begin{thm}
-%\label{thm:iocscomplexity}
-%Let $\mathcal{A}$ be \ics in Line $1$ of \iocs. Then, the time complexity of the \iocs  is $O(n^2T)$. 
-%\end{thm}
-
-%\vspace{-6mm}
-\section{Simulation Results}
-			\label{sec:simul}
-%%%In this section, we report a summary of simulation experiments to evaluate the performance of the proposed algorithms.
-
-						\begin{figure*}[t]	
-				\centering
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{V-N-M2.pdf}
-						\caption{\revv{$m=2$}}
-						\label{fig:V-N-M2}
-					\end{center}
-				\end{subfigure}
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{V-N-M4.pdf}
-						\caption{\revv{$m=4$}}
-						\label{fig:V-N-M4}
-					\end{center}
-				\end{subfigure}% 	
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{V-N-M8.pdf}
-						\caption{\revv{$m=8$}}
-						\label{fig:V-N-M8}
-					\end{center}
-				\end{subfigure}% 
-				\caption{\revv{Comparison results for $2$, $4$, and $8$ CSs for fractional and integral revenue models.}} 
-				\label{fig:V-N-M}
-%				\vspace{-3mm}
-			\end{figure*}
-%\subsection{Simulation Setup and Overview}
-\textit{Simulation Setup and Overview:} We consider charging scheduling of EVs \revv{during a period of $12$ time slots of length $1$ hour (e.g., from $08$:$00$ to $20$:$00$)}. 
-We gathered information of \revv{$12$} popular EV models in the market to use in the simulation.
-Each EV model is characterized by its battery capacity as shown in Table \ref{tb:models} and maximum charging rate.
-\revv{Tesla models can get charged with up to $100$ kW using Tesla super chargers.
-Also, all other models have rapid DC charging capability (up to $50$ kW) with CHAdeMO method.
-This setting for charging rates is in accordance with future DCFC systems that can have several fast DC chargers installed in the charging station.}
-%Battery capacity varies from \revv{$14$} kWh to \revv{$100$} kWh and the maximum charging rate from \revv{$3.3$} kW to \revv{$22$} kW. 
-%As in \cite{Tang,Chen}, we assume that arrival times follow a Poisson distribution and parking times follow an exponential distribution.
-% with the mean arrival and parking duration indicated in Table \ref{tb:a-d}. 
-The peak intervals include $08$:$00$-$10$:$00$, $12$:$00$-$14$:$00$, and $18$:$00$-$20$:$00$ which is in accordance to NHTS survey~\cite{Santos, Tang}.
-\revv{The probability of arriving an EV in the peak hours is two times higher than the off-peak periods.
-			Demands are uniform random values from 
-			$[\frac{1}{2}U_i,U_i]$} where $U_i$ is the battery capacity for EV $i$ in Table~\ref{tb:models}.
-\revv{The deadline of each EV is set according to slackness parameter $s$ (with default value of $1.2$), its demand and maximum charging rate of the battery as $d_i=a_i+\lceil \frac{D_is}{k_i} \rceil -1$.}
-%			The minimum electricity cost is $\$0.11$ per kWh based on US national electricity price average~\cite{kWhcost}.
-In our setting, users can submit higher prices than the minimum price in order to ensure receive their requested demand.
-			\revv{EVs are assigned to different CSs randomly and given as input to the algorithms.
-The willingness to pay by each user for one kWh of power is a random uniform number from interval $[\frac{1}{2} z,\frac{3}{2}z]$ where $z=\$0.11$ is national average price of electricity in the US\cite{kWhcost}.}
-			%The default value of local peak constraint is \rev{$100$} kW and the global peak constraint is \rev{$200$} kW. We investigate the effect of this parameter in~\cite{alinia2017online}. 
-			In the simulation, the results are plotted with $95\%$ confidence level and each point represents average result of $50$ random scenarios.
-Table \ref{tb:comparisons} explains the comparison algorithms \revv{including current implemented algorithm in Caltech ACN referred to as \iolp \cite{lee2016adaptive} and its adapted version for the fractional revenue model \folp.
-The \iolp and \folp algorithms runs as follows: at each time slot assume that there will be no further arrivals and solve the optimization problem (e.g., by commercial solvers) for the current set of EVs and their remaining demands.
-In Table \ref{tb:comparisons}, the letters ``\textsc{i}'', ``\textsc{f}'' and ``\textsc{o}'' in front of the algorithms' name refer to integral, fractional and online types, respectively.}
-
-			The measured performance metrics are total revenue, percentage of EVs that received all their demand, and total peak.
-\revv{To calculate optimal solution in integral revenue model, we used Gurobi solver \cite{optimization2013gurobi}.}
-
-\begin{table}[!t]
-				\centering
-				\caption{\revv{EV models and their battery capacity.}}
-				\label{tb:models}\revv{
-				\begin{tabular}{ | l| c | l| c |}
-					\hline
-					\textbf{Model} & \textbf{Battery} & \textbf{Model} & \textbf{Battery} \\ \hline\hline    
-				Mitsubishi i-MiEV & $16$ kWh & Citroen C-Zero & $14$ kWh \\ \hline
-				Peugeot iOn  & $16$ kWh & Honda Clarity & $25.5$ kWh\\\hline
-				Hyundai Kona & $64$ kWh & Nissan LEAF & $40$ kWh \\ \hline
-				Hyundai Ioniq & $28$ kWh & BMW i3 & $22/33$ kWh \\ \hline
-				Tesla Model S/X  & $60/100$ kWh & Kia Soul EV  & $27$ kWh\\\hline
-				\end{tabular}}
-			\end{table}
-
-%\begin{table}[h]
-%				\centering
-%				\caption{Arrival rates and mean parking times.}
-%				\label{tb:a-d}
-%				\begin{tabular}{ | l | c | c |}
-%					\hline
-%					\textbf{Interval} & \textbf{Arrival rate} & \textbf{Mean parking time} \\ \hline\hline    
-%					$08$:$00$-$10$:$00$&  $14$&$10$\\\hline  
-%					$10$:$00$-$12$:$00$&  $10$&$1/2$\\\hline 
-%					$12$:$00$-$14$:$00$&  $20$&$2$\\\hline 
-%					$14$:$00$-$18$:$00$&  $10$&$1/2$\\\hline
-%					$18$:$00$-$20$:$00$&  $20$&$2$\\\hline
-%					$20$:$00$-$24$:$00$&  $10$&$10$\\\hline
-%					$24$:$00$-$08$:$00$&  $0$&$0$\\\hline
-%				\end{tabular}
-%\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{Acronyms for the algorithms}
-\label{tb:comparisons}
-\begin{tabular}{ | l| p{6cm}|}
-\hline
-\textbf{Notation} & \textbf{Description} \\ \hline\hline
-\textsc{iOpt} & Optimal value under integral revenue model\\ \hline 	 
-\ics & Proposed offline algorithm for \MCSP under integral revenue model\\ \hline
-\fcs & Proposed \emph{optimal} algorithm for \MCSP under fractional revenue model\\\hline 
-\iocs & Proposed online algorithm for \MCSP under integral revenue model\\ \hline
-\focs & Proposed online algorithm for \MCSP under fractional revenue model\\ \hline
-\iolp & Algorithm in \cite{lee2016adaptive} (works under integral revenue model)\\ \hline
-\folp & Adaptation of algorithm in \cite{lee2016adaptive} for fractional revenue model\\ \hline
-GreedyRTL & The algorithm in \cite{Jain} for single station scenario without global peak 			constraint (works under integral revenue model)\\\hline				
-\end{tabular}
-\end{table}
-			%to simulate: Fig. 1 with M=1,4,8			
-			\begin{figure*}[t!]	
-				\centering
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{v-c.pdf}
-						\caption{\revv{Total revenue}}
-						\label{fig:v-c}
-					\end{center}
-				\end{subfigure}%
-				%\hspace{4mm}
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{p-c.pdf}
-						\caption{\revv{Actual global peak} 
-%							($p^{\mathsf{total}}=480$)
-}
-						\label{fig:p-c}
-					\end{center}
-				\end{subfigure}%  
-				%\hspace{4mm}
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{acc-c.pdf}
-						\caption{\revv{\% of full charged EVs}}
-						\label{fig:acc-c}
-					\end{center}
-				\end{subfigure}% 				
-				\caption{\revv{Comparison in terms of total revenue, actual peak, and percentage of fully charged EVs by varying local peak value}.} 
-				\label{fig:peak_local}
-%			\vspace{-4mm}
-			\end{figure*}
-\textit{\revv{Evaluation Based on Total Revenue}:}
-\revv{Fig.
-\ref{fig:V-N-M} depicts the comparison results based on total revenue under fractional and integral models} while the total number of EVs increases from \revv{$100$ to $250$} for $2$, $4$, and $8$ CSs.
-\revv{The local and global peak constraints are set to $50$ kWh and $200$ kWh, respectively.}
-
-The proposed algorithms compared to the optimal offline solution of integral model ($\textsc{iOPT}$) and $\iolp$.
-\bt{Note that comparison with offline optimal could be considered as a baseline comparison with the category of approximate offline algorithms in integral model~\cite{yao2016real}.}
-
-%%% which is the running online algorithm in the Caltech ACN \cite{lee2016adaptive}. 
-%The proposed algorithms for fractional revenue model, \fcs and \focs, are compared to fractional version of OLP algorithm (referred to as \folp), which is implemented in Caltech ACN  (see~\cite{alinia2017online} for details).
-Recall that \fcs is optimal offline solution.
-The notable observations  are  as  follows:  (i)  the  general  trend in scenario of Fig.~\ref{fig:V-N-M} is that  by increasing  the  number  of  EVs,  total  revenue  increases.
-This is because with more number of EVs, the scheduler has more freedom to choose more valuable EVs.
-(ii)  as  explained in Section~\ref{sec:fractional}, under fractional charging model, better results are expected due to increased scheduling flexibility in CSs.
-According to the simulation data that we extracted from Fig.~\ref{fig:V-N-M}, the gain obtained by \fcs and \focs in Fig.
-\ref{fig:V-N-M} are respectively \revv{$12\%$ and $10\%$} more than the gain of the \ics and \iocs.
-(iii) \revv{In Fig.
-\ref{fig:V-N-M2} and Fig.
-\ref{fig:V-N-M4}, sum of the local peaks is less than or equal to the global peak while in Fig.
-\ref{fig:V-N-M8} this sum is two times greater than the global peak.
-Consequently, the total revenue significantly improved when the number of CSs is increased from $2$ to $4$ while there is a slight improvement from $4$ to $8$ CSs as the global peak constraint prevents the algorithms from charging more EVs.}
- (iv) in integral revenue model, the proposed \iocs algorithm acts significantly better than \iolp.
-In particular, \iocs improves \iolp by \revv{$38\%, 36\%$, and $32\%$} for $m=2$, $m=4$ and $m=8$, respectively.
-\revv{In fractional revenue model, however, there is a very slight difference between \focs and \folp.}
- %We highlight that \iocs (\focs) is also better choice in terms of the algorithm complexity compared to \iolp (\folp).
-(v) \ics approximates \textsc{iOpt} by \revv{$97\%$, $94\%$, and $95\%$} for $m=2$, $m=4$, and $m=8$, respectively.
-On average, \iocs is \revv{$90\%$} of \textsc{iOpt} and, \focs is \revv{$94\%$} of its optimal offline solution, \fcs.
-(vi) finally, the results depict that \ics achieves much better results in practice as compared to the theoretical approximation ratio that characterizes the performance in worst-case scenario.
-
-%Also, there is a sharp decline in the gap between the online methods (i.e., \focs and \iocs) and the offline solutions (i.e., \textsc{iOpt}, \ics and \fcs).
-
-\revv{\emph{Comparison Based on Actual Peak:}} The constraint set in the \MCSP assures that any feasible solution respects the local and global peak constraints.
-% i.e., at each time slot, the electricity consumed by station $j$ is less than or equal to $p_j$ and accumulative charging rate of all stations are less than or equal to $p^\mathsf{total}$ (note that there is no assumption that $\sum_j p_j\leq p^\mathsf{total}$, in general).
-An efficient scheduling algorithm may take a further step by not only satisfying the peak constraints but to further reduce the peak as much as possible.
-The proposed offline algorithms (i.e., \ics and \fcs) apply valley-filling policy to reduce the peak.
-The  online algorithms (i.e., \iocs and \focs) do not apply the same policy as they do not have future knowledge to be able to balance allocated resources.
-%Besides, due to uncertainties in future EV charging load in online scheduling design, it is a natural heuristic to charge EVs at earliest time.
-% (i.e., setting the charging rates to the maximum feasible value at each time slot) as applied by \iocs an \focs. 
-%This heuristic works well as the uncertainty in EVs' arrival time and demands may not give a second opportunity to the scheduler to charge the current EVs at the next slots.
-Therefore, although it is expected that \iocs and \focs have higher peak values compared to the offline algorithms, the idea of valley-filling can decrease their average response time.
-% (see~\cite{alinia2017online} for the extended version of experiments).
-To investigate the effect of employed valley-filling strategy, we conducted a set of simulations by varying local peak constraints. 
-%from $50$ kWh to $120$ kWh and $200$ EVs. 
-The results of \ics is compared to \iocs and GreedyRTL~\cite{Jain} where the latter is an approximation scheduling for single station scenario with EVs having same arrival time (see the explanations after formulating the \MCSP in Section \ref{sec:problem}).
-%The GreedyRTL algorithm works under integral revenue model. Therefore, results for \fcs and \focs are not plotted. 
-%Since GreedyRTL assumes all EVs arrive at the same time, we set all arrival times to $1$.
-Moreover, we assume that global peak constraint is big enough (i.e., $\sum_{j=1}^m p_j\leq p^\textsf{total}$) such that the solution of GreedyRTL is feasible.
-We run GreedyRTL in each CS separately and combine the results.
-The results are shown in Fig.~\ref{fig:peak_local}.  
-Along with total revenue in Fig.~\ref{fig:v-c}, we also report total \emph{actual} peak in Fig.~\ref{fig:p-c} and percentage of fully charged EVs in Fig.~\ref{fig:acc-c}. 
-%As a high level trend, the results show that as the peak values increase, total revenue, total actual peak, and the number of EVs who received all their demand increase.  
-In Fig.
-\ref{fig:v-c}, the results for \ics and GreedyRTL are almost identical while \iocs is \revv{$90\%$} of the other two algorithms, on average.
-When \revv{$p_j\geq 400$}, the total revenue for \ics and GreedyRTL does not increase in Fig.
-\ref{fig:v-c} and percentage of fully charged EVs is $100$ for both algorithms according to Fig.
-\ref{fig:acc-c}.
-From this point and onward, the scheduling is not challenging for offline methods to obtain optimal answer because of resource sufficiency.
-However, it is still a challenge to control total actual peak for the system.
-As a result of valley-filling policy, the value of actual peak of \ics in Fig.
-\ref{fig:p-c} remains almost unchanged for \revv{$p_{j}\geq 400$}.
-\iocs and GreedyRTL, however, continuously increase the peak demand, since they are not using any peak shaving approach.
-% and only try to maximize total revenue. 
-%According to Fig. \ref{fig:p-c}, \iocs always reaches to the maximum peak of $\sum_j p_j$.
-
-%A glance at Table \ref{tb:models} shows that in general, an EV needs a minimum time of $2$ hours to get $70\%$ of its battery capacity if charging rate is set to the maximum value.
-However, CSs are allowed to preempt the charging at any time and set charging rate any value lower than the maximum rate.
-Therefore, average response times can be higher as it can be seen in Fig.
-\ref{fig:rt-c}.
-
-%\begin{figure}[t]	
-%\centering
-%				\begin{subfigure}[b]{0.25\textwidth}
-%					\begin{center}
-%						\includegraphics[width=\textwidth]{v-s-method1.pdf}
-%						\caption{Total revenue (\$)}
-%						\label{fig:v-s-method1}
-%					\end{center}
-%				\end{subfigure}%				
-%				\begin{subfigure}[b]{0.25\textwidth}
-%					\begin{center}
-%						\includegraphics[width=\textwidth]{rt-s-method1.pdf}
-%						\caption{Response time (hr))}
-%						\label{fig:rt-s-method1}
-%					\end{center}
-%				\end{subfigure}%  
-%\caption{The impact of slackness parameter on total revenue and response time when users react by adjusting their demand.} 
-%\label{fig:slackness1}
-%\end{figure}
-
-%\subsection{The Impact of Slackness Parameter}
-%\label{sec:sim:slack}
-%This section discusses on the benefits and disadvantages that can be brought by using slackness parameter.
-To give the charging scheduler more flexibility, a slackness parameter $s\geq 1$ is used and set by the system designer.
-%Recall that charging profile of EV $i$ is feasible if $D_i\leq k_i\frac{d_i-a_i+1}{s}$ holds.
-Since users have no control on the slackness parameter and the maximum charging rate, they must adjust their demand and availability according to the imposed slackness value.
-Based on the charging profile feasibility equation, when the slackness value increases users have two choices to react: (i) decrease the demand and depart at the desired deadline or, (ii) extend the deadline and receive the desired demand.
-In the remaining of this section, we investigate the effects of either case by simulation.
-To have a clear picture of effects caused by slackness parameter, we generated $100$ initial charging profiles $\langle a_i,d_i,v_i,D_i,k_i\rangle$ for $100$ EVs randomly and uniformly chosen from $10$ different models in Table \ref{tb:models} such that the initial profiles are set up assuming that the CS allows the charging operations to be finished at earliest possible time (i.e., $\frac{D_i}{k_i}$) with $s=1$.
-For each EV, its demand is randomly chosen from $25\%$ to $100\%$ of its battery capacity and departure in  interval $[a_i+\frac{sD_i}{k_i},T]$, where $a_i+\frac{sD_i}{k_i}$ is the earliest feasible deadline.
-Then, the EVs are uniformly assigned to $4$ CSs and should choose one of the above strategies to submit a feasible demand according to imposed slackness.
-%\begin{figure}[t]	
-%\centering
-%							\begin{subfigure}[b]{0.234\textwidth}
-%								\begin{center}
-%									\includegraphics[width=\textwidth]{v-s-method2.pdf}
-%									\caption{Total revenue (\$)}
-%									\label{fig:v-s-method2}
-%								\end{center}
-%							\end{subfigure}%
-%							\hspace{1mm}
-%							\begin{subfigure}[b]{0.236\textwidth}
-%								\begin{center}
-%									\includegraphics[width=\textwidth]{rt-s-method2.pdf}
-%									\caption{Response time (hr)}
-%									\label{fig:rt-s-method2}
-%								\end{center}
-%							\end{subfigure}% 
-%							
-%\caption{The impact of slackness parameter on total revenue and response time when users react by adjusting their deadline.} 
-%\label{fig:slackness2}
-%\end{figure}
-%			
-%\subsubsection{Case I- Adjusting Demands}
-%In this case, if the initial charging profile of an EV does not reflect a feasible charging request based on the slackness parameter, the EV owner decreases its demand so it will be able to leave CS at its initial desired deadline.
-Note that the valuation of EVs decreases proportionally, as well.
-Fig.~\ref{fig:slackness1} depicts the result under this policy applied by users.
-As it can be seen in Fig.
-\ref{fig:v-s-method1} and Fig.
-\ref{fig:rt-s-method1}, the general trend is that both total revenue and average response time decrease when slackness value increases.
-This is justifiable based on users reaction.
-When users decrease their demand, less electricity is sold which results in less revenue.
-When total demand decreases, charging can be finished in shorter time which decreases response time.
-Therefore, if users choose the first policy (adjusting their demand), total revenue degrades while response time improves.
-Notice that for the algorithms working under integral revenue model (i.e., \textsc{iOPT}, \ics and \iocs) the total revenue increases with slackness parameter at first (when $s$ grows from $1$ to $1.4$) but then it decreases when the slackness increases more (for $s>1.4$).
-%In our view, this happens because increasing the slackness in integral revenue model makes it possible to \emph{fully} charge more EVs at the beginning as the demands decrease.
-However, when the slackness increases more, it results in opposite effect because the valuation of demands decreases along with the demands' size.
-%			\subsubsection{Case II- Adjusting Deadlines}
-%			In this case, we assume that users are reluctant to decrease their desired demands.
-Instead, they can extend their departure.
-In Fig.~\ref{fig:slackness2} it can be observed that under this behavior of the users, the results are opposite as compared to the previous case (Fig.~\ref{fig:slackness1}).
-When deadlines are extended without demand decrement, the scheduler has more chance to compliance the demands through improved scheduling flexibility.
-Consequently, the total revenue increases by increasing slackness value while average response time degrades.
-%%Also observe the behavior of the online algorithms (i.e., \iocs and \focs) where both total revenue and response time decrease after a specific point that is $s=1.8$.
-When deadlines extend, more EVs have the opportunity of getting charged
-%					
-%We can conclude that when total revenue is more important than the response time, the CS should impose small values of slackness for users that apply the policy of the first case and impose higher values of slackness for the users that apply the second policy.
-The conclusion is reverse for the case that the objective is to have lower response times.
-
-			%In fact, the slackness parameter controls the maximum demand or earliest deadline that an EV can submit to the system.
-Remember that demands are in interval $[\textrm{min}\{\frac{d_i-a_i}{sk_i},U_i\},U_i]$ for EV $i$ meaning that the maximum demand that an EV can submit decreases by increasing slackness parameter.
-A reduction in total demand result in lower charging costs.
-Therefore, the total revenue decreases with higher values of parameter $s$ as in Fig.
-\ref{fig:v-s}.
-			%Also, the percentage of EVs that received all of their requested demand increases based on the same fact.
-The main goal of this simulation is to observe that obtained theoretical result on approximation ratio is confirmed as optimality gap of the SCS algorithm reduces by increasing $s$ in Fig.
-\ref{fig:v-s}.
-%\vspace{0.1mm}
-%\vspace{-4mm}
-			\section{Conclusion}
-			\label{sec:conclusion}
-This paper proposed offline and online algorithms for the EV charging scheduling problem under fractional and integral revenue models in an adaptive charging network (ACN).
-The problem is different, and more challenging than the existing single station EV charging scheduling problems since it requires respecting the aggregate peak charging demand of the ACN.
-%More importantly, the problem is online in nature in the sense that the EVs arrive in time and the scheduler has no information regarding future arrivals. 
-As the notable contributions, our proposed online algorithm for fractional revenue model achieves constant competitive ratio of $2$.
-Moreover, the offline integral algorithm achieves a theoretical bound on the optimality gap and approximates the optimum by $92\%$, on average in experiments.
-As a future work, we plan to study the problem under posted pricing mechanism where the charging station publishes the unit price of the power (which can be varied over time) and the users can accept or reject the offer.
-\revv{Another interesting future direction is to tackle the EV charging scheduling in market-based scenarios where the prices change over time.}
-%As a future work, we plan to analyze the truthfulness of the algorithms to make sure that it is a dominant strategy for the EV owners to declare their true valuations and availabilities.
-%\vspace{-4mm}
-
-%\input{intro.tex}
-%\input{rel.tex}
-%\input{sys.tex}		
-%\input{fraction.sol.tex}		
-%\input{integral.sol.tex}
-%\input{exp.tex}
-%%%\vspace{0.1mm}
-%\input{conc.tex}
-%\newpage
-%ss
-%\newpage
-%\pagestyle{empty}
 \bibliography{ref}{}
@@
 \bibliographystyle{ieeetr}
+%\newpage
+%{\color{white}...}    
+%\newpage
+\input{bio.tex}
+%\newpage
+%\pagenumbering{gobble}
+%\input{app.tex}
 
-\input{app.tex}
-
-\begin{comment}
-\vspace{-10mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{alinia.jpg}}]{Bahram Alinia} received a B.Sc degree in computer science from University of Tabriz, Tabriz, Iran and a masters degree in Information Technology Engineering from University of Tehran, Tehran, Iran.
-He was a Researcher with the School of Computer Science, Institute for Research in Fundamental Sciences, Iran, from 2009 to 2012.
-He is currently a Ph.D.
-student in service architecture lab, Institute Telecom SudParis, France and participated in several European projects in the domain of smart grids.
-His research area includes wireless communications, energy systems, transportation electrification, algorithm design and approximation.
-\end{IEEEbiography}
-%\vspace{-30mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{hajiesmaili.jpg}}]{Mohammad H.
-Hajiesmaili} received the B.Sc.
-degree from the Department of Computer Engineering, Sharif University of Technology, Iran, in 2007, and the M.Sc.
-and Ph.D.
-degrees from the Electrical and Computer Engineering Department, University of Tehran, Iran, in 2009 and 2014, respectively.
-He was a Post-Doctoral Fellow with the Department of Information Engineering, the Chinese University of Hong Kong, from 2014 to 2016, and with the Department of Electrical and Computer Engineering, Johns Hopkins University, form 2017 to 2018.
-He is currently a Research Assistant Professor with the College of Information and Computer Sciences, University of Massachusetts, Amherst.
-His research interests include optimization, algorithm, and mechanism design in energy systems, electricity market, transportation networks, and multimedia networks.
-\end{IEEEbiography}
-%\vspace{-30mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{crespi.jpg}}]{Prof.
-No\"{e}l Crespi} holds Masters degrees from the Universities of Orsay (Paris 11) and Kent (UK), a diplome d'ing\'{e}nieur from Telecom ParisTech, a Ph.D and an Habilitation from UPMC (Paris-Sorbonne University).
-From 1993 he worked at CLIP, Bouygues Telecom and then at Orange Labs in 1995.
-He took leading roles in the creation of new services with the successful conception and launch of Orange prepaid service, and in standardisation (from rapporteurship of IN standard to coordination of all mobile standards activities for Orange).
-In 1999, he joined Nortel Networks as telephony program manager, architecting core network products for EMEA region.
-He joined Institut Mines-Telecom in 2002 and is currently professor and Program Director, leading the Service Architecture Lab.
-He coordinates the standardisation activities for Institut Mines-Telecom at ITU-T and ETSI.
-He is also an adjunct professor at KAIST (South Korea), an affiliate professor at Concordia University (Canada), and gest researcher at the University of Goettingen (Germany).
-He is the scientific director the French-Korean laboratory ILLUMINE.
-His current research interests are in Data Analytics, Internet of Things and Softwarisation.
-http://noelcrespi.wp.tem-tsp.eu/
-\end{IEEEbiography}	
-\end{comment}
 \end{document}

### 2025-03-09 TSUSC/bio.tex
move resources from other repos

\vspace{-10mm}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{alinia.png}}]{Bahram Alinia} is an R\&D software engineer in France since 2018. He received a joint PhD degree from Institute Telecom SudParis/Paris-Sorbonne University (UPMC) in 2018, a M.Sc. degree of IT engineering from university of Tehran, Iran,  in 2012, and a B.Sc. degree of computer science from University of Tabriz, Tabriz, Iran in 2008.
%and a masters degree in Information Technology Engineering from University of Tehran, Tehran, Iran. He was a Researcher with the School of Computer Science, Institute for Research in Fundamental Sciences, Iran, from 2009 to 2012. He received a Ph.D. degree in service architecture lab, Institute Telecom SudParis, France and participated in several European projects in the domain of smart grids. His research area includes wireless communications, energy systems, transportation electrification, algorithm design and approximation.
\end{IEEEbiography}
%\vspace{-30mm}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{hajiesmaili.png}}]{Mohammad H. Hajiesmaili} is a Research Assistant Professor in the College of Information and Computer Sciences at the University of Massachusetts Amherst. Before joining UMass, Mohammad was a postdoctoral fellow with the Johns Hopkins University, from 2017 to 2018, and with the Chinese University of Hong Kong, from 2015 to 2016. He received his Ph.D. and M.Sc. degrees from the University of Tehran, and his B.Sc. degree from Sharif University of Technology.
\end{IEEEbiography}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{lee.png}}]{Zachary J. Lee} is a Ph.D. student in Electrical Engineering at the California Institute of Technology (Caltech). He received his M.S.  in Electrical Engineering from Caltech in 2018 and his B.S.Eng. in Electrical Engineering from John Brown University in 2016. He is a recipient of the National Science Foundation Graduate Research Fellowship and Resnick Sustainability Institute Graduate Fellowship. His research is centered on smart electric vehicle charging, where he draws on broad interests in data science, computer science, and energy.
\end{IEEEbiography}
%\vspace{-30mm}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{crespi.png}}]{Prof. No\"{e}l Crespi} holds Masters degrees from the Universities of Orsay (Paris 11) and Kent (UK), a diplome d'ing\'{e}nieur from Telecom ParisTech, a Ph.D and an Habilitation from UPMC (Paris-Sorbonne University). From 1993 he worked at CLIP, Bouygues Telecom and then at Orange Labs in 1995. He took leading roles in the creation of new services with the successful conception and launch of Orange prepaid service, and in standardisation (from rapporteurship of IN standard to coordination of all mobile standards activities for Orange). In 1999, he joined Nortel Networks as telephony program manager, architecting core network products for EMEA region. He joined Institut Mines-Telecom in 2002 and is currently professor and Program Director, leading the Service Architecture Lab. He coordinates the standardisation activities for Institut Mines-Telecom at ITU-T and ETSI. He is also an adjunct professor at KAIST (South Korea), an affiliate professor at Concordia University (Canada), and gest researcher at the University of Goettingen (Germany). He is the scientific director the French-Korean laboratory ILLUMINE. His current research interests are in Data Analytics, Internet of Things and Softwarisation.
http://noelcrespi.wp.tem-tsp.eu/
\end{IEEEbiography}	
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mallada.png}}]{Enrique Mallada} is an assistant professor of electrical and computer engineering at Johns Hopkins University since 2016. Before joining Hopkins, he was a post-doctoral fellow at the Center for the Mathematics of Information at the California Institute of Technology from 2014 to 2016. He received his ingeniero en telecomunicaciones (telecommunications engineering) degree from Universidad ORT, Uruguay, in 2005 and his Ph.D. degree in electrical and computer engineering with a minor in applied mathematics from Cornell University in 2014. Dr. Mallada was awarded the NSF CAREER award in 2018, the ECE Director's Ph.D. Thesis Research Award for his dissertation in 2014, the Cornell University's Jacobs Fellowship in 2011 and the Organization of American States scholarship from 2008 to 2010. His research interests lie in the areas of control, networked dynamics, and optimization, with applications to engineering networks such as power systems and the Internet.
\end{IEEEbiography}

### 2025-03-09 TSUSC/conclusion.tex
move resources from other repos

--- 2019-08-28 TSC/R1/TSC.tex
@@
-\documentclass[journal]{IEEEtran}
-%\usepackage{float}
-\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-\usepackage{amssymb,amsmath}
-\usepackage[font=small,skip=10pt]{caption}
-\usepackage{subcaption}
-\usepackage{comment}
-\usepackage{color,soul}
-%\usepackage{ragged2e} 
-\usepackage{algorithmicx}
-\usepackage{algpseudocode}
-\usepackage{amsthm}
-\usepackage{cite}
-\usepackage{array}
-%\usepackage{nopageno}
-\usepackage{url}
-%\usepackage{hyperref}
-%\usepackage{ulem}
-
-% *** CITATION PACKAGES ***
-%
-\usepackage{cite}
-\usepackage{color}
-\usepackage{xspace}
-\usepackage{multirow}
-\usepackage{hhline}
-%\usepackage[pdftex]{graphicx}
-
-% *** GRAPHICS RELATED PACKAGES1 ***
-%
-
-% more space
-%\usepackage{txfonts}
-\addtolength{\abovedisplayskip}{-2mm}
-\addtolength{\belowdisplayskip}{-2mm}
-\addtolength{\parskip}{-.15mm}
-%\addtolength{\arraycolsep}{-.75mm}
-\addtolength{\abovecaptionskip}{-1mm}
-\addtolength{\belowcaptionskip}{-1mm}
-%\renewcommand{\baselinestretch}{0.9}
-
-\ifCLASSINFOpdf
-\usepackage[pdftex]{graphicx}
-\graphicspath{{fig/}{../}}
-\DeclareGraphicsExtensions{.pdf,.jpeg,.png,.jpg}
-\else
-\usepackage[dvips]{graphicx}
-\graphicspath{{fig/}{../}}
-\DeclareGraphicsExtensions{.eps}
-\fi
-
-%\usepackage[caption=false,font=footnotesize]{subfig}
-%
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-%\setlength{\intextsep}{-1ex} % remove extra space above and below in-line float
-
-\renewcommand{\baselinestretch}{1}
-
-\ifodd 1
-\newcommand{\bt}[1]{{\color{blue}#1}}%revise of the text
-\newcommand{\rev}[1]{{\color{black}#1}}%revise of the text
-\newcommand{\revv}[1]{{\color{black}#1}}%revise of the text
-\newcommand{\com}[1]{\textbf{\color{red}(COMMENT: #1)}}%comment of the text
-\else
-\newcommand{\bt}[1]{#1}
-\newcommand{\rev}[1]{#1}
-\newcommand{\com}[1]{}
-\fi
-
-\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-
-%\newcommand{\opt}{\textsc{OPT}\xspace}
-\newcommand{\sa}{\textsc{SmartAllocate}}
-\newcommand{\rc}{\textsc{ReConsider}}
-\newcommand{\bc}{\textsc{BetaCover}}
-\newcommand{\ics}{\textsc{iCS}\xspace}
-\newcommand{\fcs}{\textsc{fCS}\xspace}
-\newcommand{\MCSP}{\textsf{SPAN}\xspace}
-\newcommand{\dMCSP}{\textsf{dSPAN}\xspace}
-\newcommand{\focs}{\textsc{foCS}\xspace}
-\newcommand{\iocs}{\textsc{ioCS}\xspace}
-\newcommand{\finalalg}{\textsc{ioCS+}\xspace}
-\newcommand{\opt}{\textsc{OPT}\xspace}
-\newcommand{\alg}{\textsc{ALG}\xspace}
-\newcommand{\rtl}{\textsc{GreedyRTL}\xspace}
-\newcommand{\iolp}{\textsc{ioLP}\xspace}
-\newcommand{\folp}{\textsc{foLP}\xspace}
-
-\newcommand{\be}{\begin{equation}}
-	\newcommand{\ee}{\end{equation}}
-\newcommand{\bee}{\begin{eqnarray}}
-	\newcommand{\eee}{\end{eqnarray}}
-\newcommand{\bse}{\begin{subequations}}
-	\newcommand{\ese}{\end{subequations}}
-%\def\bee#1\eee{\begin{align}#1\end{align}}
-\newcommand{\nnb}{\nonumber}
-
-\newtheorem{lem}{Lemma}
-\newtheorem{propos}{Proposition}
-\newtheorem{thm}{Theorem}
-\newtheorem{defi}{Definition}
-
-%in terms of practical feasibility and characterizing the maximum benefits of D2D load balancing is
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{corollary}[theorem]{Corollary}
-
-\makeatletter
-\newcommand\semiHuge{\@setfontsize\semiHuge{22.52}{27.38}}
-\makeatother
-\begin{document}
-	%\semiHuge
-	\title{Online EV Scheduling Algorithms for Adaptive Charging Networks with Global Peak Constraints}
-	\author{\#}
-
-	\author{Bahram Alinia, Mohammad H. Hajiesmaili, Zachary J. Lee, Noel Crespi, and Enrique Mallada
-
-		\thanks{ B. Alinia and N. Crespi are with the department of Networks and Mobile Multimedia Services (RS2M), Institut Mines-Telecom,
-			Telecom SudParis, Evry, France (e-mail: bahram.alinia@telecom-sudparis.eu, noel.crespi@mines-telecom.fr).
-
-			M. H. Hajiesmaili and E. Mallada are with the Department of Electrical and Computer Engineering, Johns Hopkins University, Baltimore, MD, USA (e-mail: \{hajiesmaili,mallada\}@jhu.edu).
-
-			Z. J. Lee is with the Department of Electrical Engineering, California Institute of Technology, Pasadena, CA, USA (e-mail: zlee@caltech.edu).
-		} }
-
-		\maketitle
-
-\begin{abstract}
-%			With the rapid growth of electric vehicles, their high demand charging jobs pose an immense challenge to the grid infrastructure. 
-			This paper tackles online scheduling of electric vehicles (EVs) in an adaptive charging network (ACN) with local and global peak constraints.
-Given the aggregate charging demand of the EVs and the peak constraints of the ACN, it might be infeasible to fully charge all the EVs according to their charging demand.
-Two alternatives in such resource-limited scenarios are to maximize the social welfare by partially charging the EVs (fractional model) or selecting a subset of  EVs and fully charge them (integral model).
-%			This paper tackles both fractional and integral models. 
-			The critical challenge is the need for online solution design since in practical scenario\revv{s} the scheduler has no information of future arrivals of EVs in a time-coupled underlying problem. 
-			For the fractional model, we devise both offline and online algorithms.
-We prove that the offline algorithm is optimal.
-Using competitive ratio as the performance measure, we prove the online algorithm achieves a competitive ratio of 2.
-The integral model, however, is more challenging since the underlying problem is \bt{strongly} NP-hard due to 0/1 selection criteria of EVs.
-Hence, efficient solution design is challenging even in offline setting.
-We devise a low-complexity primal-dual scheduling algorithm that achieves a bounded approximation ratio.
-Built upon the offline approximate algorithm, we propose an online algorithm and analyze its competitive ratio in special cases.
-Extensive trace-driven experimental results show that the performance of the proposed online algorithms is close to the offline optimum, and outperform the existing solutions.
-%			\rev{In particular, the grid and electricity providers should be aware of the electricity peak.	It is known in electricity market that the spot price is a dominating factor in billing cost.
-Hence, the utility companies need to identify a global peak constraint for the cost management purpose.
-This paper studies the online EV charging scheduling problem in a utility that offers EV charging service in a set of CSs, each of which having limited output power (referred to as local peak constraint) while taking into account the global peak constraint.
-The scheduling problem in this scenario comes with unique challenges that is not tackled previously.}
-
-%			\rev{The problem objective is to maximize total revenue of the CSs.}
-
-\end{abstract}
-		\begin{IEEEkeywords}
-			Electric Vehicle, Online Scheduling, Approximation Algorithm, Competitive Analysis
-		\end{IEEEkeywords}
-
-		\section{Introduction}
-\label{sec:intro}	
-%		\IEEEPARstart{A}{s} 
-%		a result of global warming and environmental concerns through dependence on fossil fuels, there has been a rapid proliferation in deploying renewable energy sources. 
-\IEEEPARstart{T}{o} promote quick adoption of renewable energy sources, electrification of vehicles is a trend that has been globally advocated in recent years.
-\rev{According to a Bloomberg report, EVs will account for more than half of the new car sales by $2040$~\cite{bloomberg}.
-	%the global sale of EVs increased by $80\%$ in $2015$~\cite{EVSales}.
-	%		With the significant advantage of electric vehicles (EVs) in being an environment friendly product, the global interest for EVs is rapidly growing, such that  
-	Consequently, it is expected that demand from EV charging will constitute a considerable portion of total demand. 
-	Currently, transportation consumes $29\%$ of total energy in the US, while electricity production consumes $40\%$~\cite{Zhao}.} 
-%Vehicles seen accounting for 5\% of electricity use by $2040$~\cite{EVSales2}}
-%%%\revv{\sout{Hence, rapid electrification of the vehicles makes the total electricity demand of EVs significant.}}
-
-\revv{EV charging demand is a typical example of a deferrable load, and there is often considerable flexibility in the charging schedule.
-This property makes the problem of EV charging scheduling  important and there is an extensive research along this direction in the literature (see the recent survey~\cite{mukherjee2015review}, and references therein).
-In most of the existing works, the EV charging demand is treated as a constraint to the problem in a low-load regime~\cite{Tang}.
-Motivated by rapid proliferation of EVs, this work tackles the EV scheduling in high-load regime, where given the aggregate charging demand of the EVs and the peak constraints of the charging network, it is not feasible to fully charge all the EVs according to their charging demand.}
-%		\subsection{Microgrid: Definition, Potentials, and Challenges}
-%		\label{sec:introA}
-%		A common trend in the smart grid era is to install renewable energy sources in distributed manner.
-More specifically, medium or large commercial and industrial  customers such as universities, headquarters, etc.,  can take control of their own energy consumption by local deployment of renewable sources~\cite{Hajiesmaili2016Online}.
-In this setting, the residual demand, i.e., total demand subtracted by the local renewable supply, can be acquired from the external grid.
-
-%		In addition to clean energy production, the owner of microgrid also enjoys more power sustainability and reliability, and the ability to proactively manage the energy costs.
-
-More specifically, this paper studies resource-constrained EV charging scheduling in an adaptive charging network (ACN) governed by a single operator in a campus-scale location such as a university, a headquarter\rev{s}, etc.
-\cite{wu2017two}.
-\rev{A notable example is the Caltech ACN~\cite{lee2016adaptive} where individual charging ports are organized into several \textit{charging stations} (CSs) which are dispersed in a \textit{charging network}} with the capability of adaptive charging of the EVs.
-The problem is different from EV charging scheduling \revv{with capacity constraint} in single station scenarios~\cite{Tang,Wen,Shroff2014,WTang,Chen,Xiang,Zhao,Robu} (we refer to~Section~\ref{sec:rel} for detailed discussions on related work), because of the essential need to respect the aggregate peak demand of the ACN.
-\revv{Note that, the ACN operator might limit the total power drawn from EVs to control costs~\cite{PeakPrice,Zhang2015eEnergy}, reserve the capacity for other loads, and/or participate in demand-response programs.}
-%		The EV charging loads are usually flexible and deferrable, which means that their load can be scheduled~\cite{moghaddam2017smart,DWang} to shape the total demand over time. 
-%The aim of this paper is to use the deferrable property of EVs and schedule their charging jobs, so as to \rev{maximize the revenue of the ACN}.	
-%		We refer to Section~\ref{sec:rel} for the literature review.
-
-%		In particular, real-world pricing scheme for large customers is usually a hybrid time-of-use and peak-based charging model where the peak demand can significantly impact the total energy cost, e.g., the peak price is often more than $100$ times higher than the spot price~\cite{PeakPrice,Zhang2015eEnergy}.
-Considering total aggregate demand, the peak charge portion could be as large as $20\%-80\%$ of total cost~\cite{Xu2014Reducing}.
-Consequently, a substantial cost reduction could be achieved if the total peak-demand can be proactively controlled \cite{liao2015dispatch}.
-
-%		\subsection{EV Charging Scheduling in the ACN}
-%		With the proliferation of EVs, the charging requirement of the microgrid EVs could be a portion of total microgrid electricity demand.
-
-%		To respond the electricity demand of EVs, CSs are being used where EVs can recourse to charge their battery \cite{He,liao2015dispatch,Tang}.
-There can be few to many CSs dispersed in an ACN, e.g., each for a parking garage of a building in a university campus.
-In this scenario, all parking stations are governed by a facility operator and a \textit{global} peak demand constraint is determined such that the aggregate charging demand in the entire network is less than this global peak demand \cite{DWang,Hoog}.
-
-%		The charging scheduling of the EVs with the goal of respecting the \textit{global aggregate peak constraint}, however, is a unique problem which is different from the single station EV charging scheduling.
-Most of the existing work in the literature, tackle the problem in the single parking station scenario.
-We refer to Section~\ref{sec:rel} for in-depth discussion.
-As discussed in Section \ref{sec:problem}, the global optimal solution cannot be obtained by separately solving the single station problems.
-%		On the other hand, there are only a few studies that provide global optimal solution for charging scheduling of EVs \cite{He, Moradijoz, Malhotra,Zeng,Shaaban,DWang}.
-Despite elegant results, the underlying problems, e.g., charging cost minimization problem in \cite{He}, average operating cost minimization with optimal electricity exchange capacity problem in \cite{DWang}, optimal station capacity problem in~\cite{Moradijoz}, user convenience maximization problem in~\cite{Malhotra}, joint optimization of system profit and user experience in~\cite{Shaaban,Zeng} are different from the problem studied in this paper.
-
-%		\subsection{Problem, Challenges, and Contributions}
-We consider a scenario with multiple EVs where each EV has different charging profile in terms of availability, charging demand, charging rate limit, and valuation of getting charged \revv{(for details see Section~\ref{sec:ev})}.
-We formulate an online EV charging scheduling problem with the goal of \textit{selecting} and \textit{scheduling} a subset of EVs such that: (1) the charging demand of the selected EVs are (fully or partially) satisfied; (2) the charging rate limit of EV batteries are respected, (3) the global peak constraint of the ACN is satisfied~\cite{lee2016adaptive}; (4) the local peak constraint of each CS is respected;  and finally, (5) the total revenue obtained by the valuation of the EVs is maximized.
-
-%		of maximizing the revenue of the ACN.
-The constraints are the \textit{local} peak constraint of each CS, and the \textit{global} peak constraint that limits the accumulative charging demand drawn from the entire network of stations (decided by the administration of the ACN to control total peak demand~\cite{lee2016adaptive}).
-
-There are two main challenges in the design and implementation of scheduling algorithms for EVs satisfying the goals mentioned above.
-\rev{Firstly, the problem calls for online scheduling design.} In practice, EVs arrive to the CS in online fashion and the scheduler has no information about the arrival and demand of the future EVs.
-Secondly, the underlying optimization problem in integral model is \bt{strongly} NP-hard even in offline case \rev{(see Section~\ref{sec:integral})}.
-This is because the problem is a mixed integer linear problem and a ``time-expanded'' extension of knapsack problem which is known as a classic NP-hard problem.
-In this paper, we tackle the challenge of online design by following competitive algorithm design~\cite{borodin2005online} and the challenge of NP-hardness by pursuing approximation algorithm design~\cite{approx} and make the following contributions:
-
-$\vartriangleright$ We first consider a \textit{fractional model} (where EVs can be charged partially and the revenue is proportional accordingly) and design an optimal offline scheduling algorithm. 
-%In addition to provide efficient result, the algorithm has a further elegant step to apply a valley filling strategy to further reduce the peak demand of EV charging without degrading total revenue. 
-We then develop an efficient online algorithm in which no exact or stochastic information about the future EV arrivals is given.
-Despite its simplicity, the algorithm is proved to be $2$-competitive with optimal offline solution, i.e., the revenue of the proposed online algorithm is at least $1/2$ of the offline optimum, regardless of input sequence.
-Even though there are competitive algorithms in the literature for similar problems, to the best of our knowledge, our algorithm is the first $2$-competitive algorithm \rev{which considers the} charging rate limits.
-
-$\vartriangleright$ We next study \rev{the} more challenging scenario of \rev{the} \textit{integral model}\rev{, }where EVs must receive all their demand to make revenue.
-We first propose a polynomial-time primal-dual offline approximate algorithm.
-We analyze the approximation ratio of the algorithm and by strengthening the linear relaxed version of the mixed integer problem~\cite{Carr}, we obtain an approximation ratio of $\alpha =1+\sum_{j=1}^m {\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}$, where $p_j$ is local peak constraint in station $j$, $q_j$ is the maximum charging rate of the EVs in station $j$ and $s$ is a slackness parameter.
-We highlight that when $p_j \gg q_j$ and $s$ is \rev{large} enough, then $\alpha \approx m+1$, where $m$ is the number of stations in the ACN.
-Built on the basis of the offline algorithm, we devise an online algorithm, and discuss its competitive ratio in special cases.
-%In particular, the competitive ratio is $b\Big(1+\frac{p_j}{p_j-q_j}\cdot\frac{s}{s-1}\Big)$ for single station scenario, where $b$ is the number of batches with the same arrival time.
-
-$\vartriangleright$ We conduct a set of  simulations to evaluate the performance of our proposed algorithms. 
-%For offline scheduling problem under integral charging model, the results  demonstrate that the proposed approximation algorithm is close to the optimal solution and is significantly better than the obtained theoretical bounds.
-The results of online algorithms for both integral and fractional settings are close to the optimum (within $90\%$ and $94\%$ for integral and fractional models in a representative scenario).
-In addition, our algorithm outperforms the existing scheduling algorithm in Caltech ACN~\cite{lee2016adaptive} by $35\%$ for integral revenue model.
-
-\bt{This paper represents follow-up work to our previous study~\cite{alinia2018competitive}, where we address a simplified version of the problems studied in this paper in fractional revenue model.
-The competitive analysis in~\cite{alinia2018competitive} is done under the assumption that all EVs have the same maximum charging rate.
-Also, \cite{alinia2018competitive} does not study the integral revenue model.
-In this paper, we extend the results and propose a 2-competitive online algorithm with no assumption on the input parameters.
-Also, the current study investigates both fractional and integral revenue models while considering global peak constraint in the formulation and addressing multiple charging station scenario.
-Last, we consider more realistic trace-driven experiments in this paper and compare the results to an existing real-world scheduling algorithm.}
-%The simulation section also discusses on the positive and negative effects of slackness parameter in different scenarios.
-
-%To the best of our knowledge, this problem is not addressed yet in previous studies.
-
-%		\subsection{Paper Organization}
-%		The rest of this paper is organized as follows. Section~\ref{sec:rel} reviews the literature. In Section \ref{sec:model}, the system model  and problem formulation are described. 
-%		Section \ref{sec:fractional} provides offline and online algorithms for fractional model.
-We study integral model in Section \ref{sec:integral} and propose online and offline algorithms.
-The simulation results are reported in Section~\ref{sec:simul}.
-Section~\ref{sec:conclusion} concludes the paper and highlights future directions.
-
-\section{Related Work}
-\label{sec:rel}
-\revv{There is an extensive work in the general topic of EV demand management and scheduling~\cite{mukherjee2015review} by considering different scenarios such as optimal operations with EV coordination and congestion management~\cite{mukherjee2017distributed,rigas2013congestion,hu2013coordinated}, EV scheduling with incorporation of renewable energy, and energy storage systems~\cite{de2017impact,shafie2018innovative}, and pricing and bidding~\cite{huang2014distribution,hou2019bidding} In this section, we focus on the literature related to peak-constrained EV charging scheduling in single and multiple stations.}
-\subsubsection{Peak-Constrained EV Charging Scheduling}
-\label{sec:rel:peakconstrained}			
-\revv{There is an extensive literature on EV charging scheduling problem focusing on single CS~\cite{Tang,Wen}, while the local and global peak constraints are omitted or only the local peak is considered.}	As we discuss in Section~\ref{sec:problem}, the global optimal solution cannot be obtained by separately solving the single station problems.
-Hence, those solutions cannot be directly applied to the multiple CS scenario with global peak constraints.
-
-%A scenario that local and global peak constraints exist is the case that scheduling is required for a charging network for multiple CSs. 
-Studies in \cite{He,malhotra2017distributed,Moradijoz,DWang,Zeng,Shaaban} tackled charging scheduling problem in multiple CSs.
-The authors in~\cite{He} studied a global cost minimization EV charging scheduling problem.
-However, there is no limit on the maximum peak demand that the system can tolerate.
-Consequently, the peak can be arbitrary high and beyond the physical limit of the transformers in the charging station~\cite{lee2016adaptive} leading to huge electricity bills~\cite{Zhang2015eEnergy}.
-Besides, the charger devices installed in the CSs have limitation on the maximum power that they can transfer in each time unit~\cite{Tesla}.
-%We solve the issue by constraining local and global peaks.
-However, to meet the peak constraints, it may not be feasible to respond to all charging demands.
-Consequently, only a subset of EVs can be charged~\cite{Xiang}, which is captured in our problem formulation.
-\cite{DWang} considered a multi-microgrid system with global peak constraint where each microgrid has a CS and the goal is to manage electricity exchange between microgrids and main grid to minimize the operating costs.
-The authors assume that required information about individual EVs is available by forecast which may not represent a real scenario.
-A similar assumption is made in \cite{Zeng,Shaaban} where the objective is to maximize total utility of EVs and aggregators in a distribution network.
-%\rev{To be removed: In our solution, we applied a priority based selection process (based on the EVs' valuation) to respond to the demands to make sure that total peak respects the constraints.
-The selection process can be made based on different criteria such as the value of each charging request \cite{Lee, Xiang} or the priority.}
-%To avoid big billing cost in peak hours, \cite{Moradijoz} proposed a solution based on genetic algorithm to find optimal capacity and location of parking lots for serving demands in peak hours with the goal of maximizing total benefit of all stations.
-Although authors studied the problem under multiple CS setting, their solution is not applicable to our setting when the CSs are already set up.
-The authors in~\cite{malhotra2017distributed} use a similar model as in this paper, where both local and global peak constraints are considered.
-However, the authors solve the single-slot problem, which fails to provide a general solution taking into account EVs' arrival and departure times as considered in our study.
-Finally, as an alternative approach to control the peak, some studies directly target minimizing the peak~\cite{Zhao, Karfopoulos}.
-In~\cite{Zhao}, an online algorithm is developed for EV charging to minimize the peak and \cite{Karfopoulos} proposed a valley filling method by leveraging V2G in peak hours.
-Although the peak is minimized in above works, it cannot guarantee that the minimized peak is tolerable by the underlying charging network.
-
-\subsubsection{Scheduling Under Demand Uncertainty}
-A main challenge in EV scheduling problem is to cope with demand uncertainty.
-Many studies including \cite{Shroff2014,Tang,WTang,Chen,Xiang,Zhao,Robu} addressed online scheduling problem with different objectives.
-\cite{Shroff2014,Xiang} studied the problem of maximizing social welfare considering the benefit for both users and service provider.
-\cite{Tang} and \cite{WTang} developed algorithms to minimize the charging price for the CS, where the proposed algorithm in \cite{Tang} is $2.39$-competitive.
-%An online algorithm developed in \cite{Chen} to optimize overall operating profit of the service provider. 
-In \cite{Robu}, an online $2$-competitive algorithm is proposed for a single CS, assuming that EVs are capable of being discharged in a negligible amount of time.
-The assumption, however, is not realistic for EVs.
-
-Our problem in this paper is unique from above works in many respects.
-First, we study the problem in an ACN where several CSs exist, while none of the above studies solve the problem under this setting.
-Second, the previous algorithms do not work for both integral and fractional charging models.
-In addition, \cite{WTang,Chen} put no limit on the charging rate of EVs which makes their solution impractical in real scenarios.
-Also, \cite{WTang,Tang, Shroff2014,Chen,Zhao} do not consider the peak limit of the CS.
-\revv{Note that some studies~\cite{jin2017optimal} tackle the scenarios of satisfying the large demands (possibly EV demands) by participating in electricity market.
-This study assumes that the electricity price is given and fixed, and leaves the case of real-time pricing as the future direction.
-In addition, there are studies that incorporate prediction in online EV charging scheduling~\cite{wang2017predictive,chen2014distributional}.
-The prediction-based approaches achieve satisfactory performance for the scenarios that follow prediction.
-Deviation from prediction models, however, degrades their performance.
-Our approach, on the other hand, has no assumptions on modeling/prediction, and in this way, is robust against any uncertainty in the instances to the problem.}
-\revv{Finally, in~\cite{Alinia2018ITS}, we considered a simplified EV charging scheduling in fractional model without global peak constraints and devised heuristic algorithms (without competitive and approximation analysis) with on-arrival commitment for EVs to notify the amount that they can receive by their departure.
-}
-%In this paper, we consider these limitations and develop online and offline algorithms for fractional and integral revenue models in an ACN and provide theoretical bounds on their performance.
-
-%It is important to note that there is a considerable similarity between EV scheduling problem and classical job scheduling problem \cite{}.
-However, most algorithm developed for job scheduling problem  do not consider a limit on processing rate of the jobs.
-
-%\cite{Shroff2014} and \cite{Stein2012} study social welfare maximization problem while the profit of both EV owners and CS is considered.
-social welfare of the EV owners \cite{Stein2012}, charging cost \cite{Tang,WTang}, and total value of fully charged EVs \cite{Azar}).
-In addition, \cite{WTang, Tang,Shroff2014,Zhao} do not take into account the peak limitation of CS.
-}
-
-\subsubsection{Worst-case Analysis in Similar Scheduling Problems}
-\label{sec:rel:comp}
-\bt{
-	Similar underlying scheduling problems with slightly different settings have been studied in the literature in both offline and online settings.
-In offline setting, the problem is more interesting in integral revenue model where the problem becomes a combinatorial optimization problem and approximation algorithms have been used to find effective solutions.
-The performance of an approximation algorithm is determined by its \emph{approximation ratio} for offline 
-algorithms.
-On the other hand, competitive online algorithms are used in the online setting and \emph{competitive ratio} is the performance metric which compares the algorithm's result to the offline optimal solution.
-
-\textit{Offline integral model}: Under integral revenue model, \cite{jain2015near} proposes an offline algorithm for scheduling of batch jobs in cloud computing which is similar to EV scheduling problem.
-It is assumed that all jobs are available to be processed at time 0.
-The authors propose a $\frac{C}{C-k}.\frac{s}{s-1}$-approximation algorithm where $C$ is the cloud capacity and $s$ is the ``slackness parameter'' (See section \ref{sec:acn} for the definition).
-Similarly, \cite{yao2016real} tackles the offline integral problem and proposes a convex relaxation method to find a near-optimal solution.
-No theoretical bound is provided for the algorithm and the performance is examined by simulation results.
-In this paper, we propose \ics for the EV scheduling problem with slightly different settings in the constraint sets, and tackle the problem in online setting in which the full knowledge of the online parameters is not available a priori, and provide approximation ratio under specific scenarios.
-
-\textit{Offline fractional model}: In case of fractional revenue model (for offline case), the scheduling problem is more straightforward to tackle since the underlying problem is linear.
-In this paper, we propose \fcs as an optimal solution for offline fractional case with low time complexity.
-
-\textit{Online fractional model}: In the online scenario, the scheduling problem is fundamentally more challenging. In our recent study \cite{alinia2018competitive}, 
-we proposed two online algorithms referred to as WFAIR and WRAND for EV scheduling problem.
-The proposed algorithms provide a competitive ratio of $2-1/U$ where $U$ is "scarcity level".
-However, the result only holds when all EVs have the same maximum charging rate.
-Also, \cite{alinia2018competitive} does not study the integral revenue model.
-In this paper, we propose \focs as a 2-competitive online algorithm with no assumption on the input parameters.
-Moreover, the current study investigates both fractional and integral revenue model while considering total peak constraint in the formulation and addressing multiple charging station scenario.
-In another work~\cite{firstfit}, two simple and natural online algorithms called \textsc{FirstFit} and \textsc{EndFit} were developed and are proved to be 2-competitive.
-\focs is extension of these algorithms by taking into account the maximum charging rate of the EVs and multiple charging station scenario (see ``Remarks'' at Section IV).
-As recent studies, \cite{zheng2016online,deng2016whether} provide online algorithms for EV scheduling problem, however, they do not take into account global peak constraint in the underlying problem.
-
-\textit{Online integral model}: Another direction is to tackle online scenario under integral revenue model.
-In this setting, the scheduling problem becomes fundamentally more challenging.
-We note that the integral scheduling problem is strongly NP-Hard even in the offline case \cite{de2018complexity}.
-Due to combined online and combinatorial challenges, there are very limited studies in this category.
-\cite{lucier2013efficient} provides an online algorithm without considering the maximum processing rate of the jobs where its competitive ratio can be arbitrary bad depending on ``slackness'' parameter.
-Our work in Section~\ref{sec:onlineint} extends this study for multiple station scenario and considering maximum charging rate for the EVs.
-}
-
-\section{System Model and Problem Formulation}
-		\label{sec:model}
-
-		\subsection{System Model}
-		We consider a time-slotted system model in which the time horizon is divided to $T$ equal length slots ${t=\{1, 2, \dots ,T\}}$ (e.g., $T=24$ with time slots of $1$ hour length).
-\subsubsection{Charging Network}
-\label{sec:acn}
-Our charging network model is inspired by the Caltech ACN~\cite{lee2016adaptive} as illustrated in Fig.~\ref{fig:model-a}.
-In \rev{the} Caltech EV charging network (located in a parking garage), electricity is distributed through a two-level transformer architecture from a main switch panel to multiple EV switch panels (\rev{$2$} panels in the current Caltech ACN).
-Each EV switch panel then is connected to several chargers ($\approx$25 chargers \rev{per panel} in the Caltech ACN).
-The total power drawn from the main switch panel \rev{by} the charging network has a power limit of  $p^\mathsf{total}$, that is determined by the facility operator to control the costs, reserve the capacity for other loads, and/or participate in demand-response programs.
-%This power, where we refer to it as \emph{network power limit} is used for both EV charging as well as non-EV charging purposes (e.g., lighting, fans, etc \cite{lee2016adaptive}). 
-In other words, $p^\mathsf{total}$, which we refer to it as the \textit{global peak}, hereafter, limits the maximum aggregate EV charging load at each time slot. 
-%The global peak must be less than or equal to the value obtained by subtracting non-EV load from network power limit. 
-%When we write \emph{global peak constraint}, it refers to $p^\mathsf{total}$.  
-%$p^\mathsf{total}$ is the maximum allowed aggregated electricity consumption by all stations at each slot and limits the total transferable power to EVs.
-
-We assume that there are $m$ EV switch panels that represent $m$ CSs.
-In addition to the global peak constraint, each CS $j$ has \rev{a} capacity constraint on \rev{its} total power drawn, indicated by $p_j$, and referred to it as the \emph{local peak} constraint.
-The \rev{value of} $p_j$ is determined by the output power limit of the transformers installed between the main switch panel and EV switch panels and could be different for each EV switch panel.
-%installed chargers in a CS have limited output power to charge EVs ~\cite{Wen,Xiang,Tesla}. Therefore, for CS $j$, $p_j$ cannot be more than sum of output power of its chargers. 
-\rev{It is often observed that the charging demand of different CSs (EV switch panels in Fig.~\ref{fig:model-a}) are well below the local peak constraints.}
-To increase the flexibility due to heterogeneous charging demand of CSs, in the Caltech ACN, the global peak constraint of the main switch can be \textit{over-provisioned}, i.e., $p^\mathsf{total}$ is less than the aggregate local peaks,  ($\sum_j p_j\geq p^\mathsf{total}$).
-\rev{While this increases flexibility, it also couples the problem of EV charging scheduling across different CSs.}
-%Despite increased flexibility, the over-provisioning property, however, couples the problem of EV charging scheduling across different CSs. 
-Our solutions in this paper will be centralized ones which can be obtained through communication between the CSs and a central server as illustrated in Fig. \ref{fig:model-b}.
-
-%We make this clear by a simple example.
-Assume $m=2, p^\mathsf{total}=50$ kW and $p_1=p_2=25$ kW.
-In a specific time slot (e.g., $t=1$), the total demand in CS $1$ and $2$ is $40$ kWh and $10$ kWh, respectively.
-According to local peak constraints, it is not feasible to satisfy all demands in a single time slot.
-However, if we had $p_1=p2=50$ kW (e.g., by installing more chargers in the stations) we could be able to satisfy all demands by allocating $40 kW$ in $p_1$ and $10 kW$ in $p_2$ while still not violating $p^\mathsf{total}$.
-In case that $\sum_j p_j\leq p^\mathsf{total}$, the scheduling problem is not challenging and the solution can be obtained by solving the problem locally in each CS.
-If $\sum_j p_j> p^\mathsf{total}$ (which is the case we consider in this paper), a centralized solution is needed that can be obtained through communication between the CS and a central server as illustrated in Fig.
-\ref{fig:model-b}.
-
-\begin{figure}	
-\centering
-\minipage{0.49\textwidth}
-				\begin{subfigure}[b]{0.69\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{model-a.pdf}
-						\caption{Caltech adaptive charging network (ACN)}
-						\label{fig:model-a}
-					\end{center}
-				\end{subfigure}%
-				\begin{subfigure}[b]{0.29\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{model-b.pdf}
-						\caption{Communication model with server}
-						\label{fig:model-b}
-					\end{center}
-				\end{subfigure}%  
-\caption{System model \cite{lee2016adaptive}.} 
-\label{fig:slackness1}
-\endminipage
-\end{figure}
-
-		\begin{table} 
-			\caption{Summary of key notations}
-%			\vspace{-3mm}
-			\label{tbl:not}
-			\begin{center}
-				\begin{tabular}{|c L{6.5cm}|}
-					\hline
-					\textbf{Notation} & \textbf{Description} \\
-					\hline \hline			
-					$T$ & Number of time slots, indexed by $t$\\			
-					$m$ & Number of CSs, indexed by $j$\\			
-					$n$ & Number of EVs, indexed by $i$\\			
-					\hline
-					\hline
-					$a_i$ & Arrival time of EV $i$\\
-					$d_i$ & Departure time of EV $i$\\
-					$D_i$ & Demand of EV $i$\\
-					$v_i$ & Valuation of EV $i$ for receiving its demand $D_i$ \\
-					$k_i$ & Maximum charging rate of EV $i$\\
-					$h(i)$ & CS of EV $i$\\
-					\hline
-					\hline
-					$q_j$ & Maximum $k_i$ among all EVs in CS $j$\\
-					$p_j$ & Maximum aggregate charging rate in station $j$\\
-					$p^\mathsf{total}$ & Maximum aggregate charging rate of all stations\\
-					\hline
-					\hline
-					$y_i^t$ & \textbf{opt. variable}, The amount that EV $i$ is charged at $t$ \\
-					\hline
-				\end{tabular}
-			\end{center}
-		\end{table}
-		\subsubsection{EVs}
-		\label{sec:ev} There are $n$ EVs in the system, indexed by $i$.
-		%, all available at time $t=1$ to be charged\footnote{This assumption is reasonable for the %official buildings where the starting hour of the working day is fixed for all the %employers.
-Extensions to the case with different arrival times for the EVs, is part of the %future work.}.
-		EV $i$ is represented by a charging profile $\langle a_i,d_i,v_i,D_i,k_i\rangle$ 
-		indicating its arrival time, departure time, willingness to pay, charging demand, and maximum charging rate, respectively. 
-		%(depends on physical properties of EVs battery) 
-		More specifically, the charging of EV $i$ can be scheduled within its \emph{availability window}, $[a_i,d_i]$.
-The charging rate at each slot is bounded by $k_i$, a parameter that depends on the physical constraints of the \rev{battery and on-board charger}.
-It is assumed that the charging profile of each EV is feasible with respect to its maximum charging rate and a slackness parameter $s\geq 1$, which is the minimum ratio between the park time of the EV and its minimum charging time, i.e., ${D_i\leq k_i(d_i-a_i+1)/s}$.
-The slackness parameter is imposed to tune the flexibility of the charging scheduling.
-In extreme case $s=1$,  the flexibility is minimum and the flexibility improves as $s$ increases.
-%		Note  that  the slackness  parameter  can  impact  the  total  revenue  and  is  investigated  in  simulation  experiments  in Section~\ref{sec:simul}.
-		We assume that EV owners select their CS, perhaps the nearest to them, and so the assignments are given to the problem. Define $h(i)$ as the CS of EV~$i$.
-		Moreover, $q_j$ denotes the maximum $k_i$ among all EVs in CS $j$, i.e., $q_j=\max_{h(i)=j} k_i$. 
-		\revv{Finally, $v_i$ is the willingness to pay of EV $i$ to receive its entire demand $D_i$ before the departure time $d_i$.
-Note that in resource-constrained EV scheduling in ACN, it is not feasible to fulfill the entire demand of all EVs, hence, the problem turns into a resource allocation one with the goal of maximizing the aggregate value (a.k.a.
-utility) obtained from the EVs.
-In this way, each user can announce its willingness to pay to get charged which is denoted by $v_i$ in the system model.}
-		%We assume that there is no gain for the CS if EV $i$ is partially charged.
-
-		% where $P$ defined as $P:\xi\rightarrow  \mathcal{P}$. 
-\subsubsection{Revenue Models\label{sec:irm}} We consider two revenue models: 
-\textit{(i) Fractional revenue model}: In this model, the fractional charging is allowed, i.e., the revenue from each EV is proportional to the fraction of the demand that is fulfilled \cite{Xiang} (see Eq.~\eqref{Eq:partial_value}).
-We tackle this model in Section~\ref{sec:fractional}.
-\textit{(ii) Integral revenue model}: \rev{In this model, EV $i$ pays $v_i$ if it is fully charged and zero otherwise, i.e., there is no partial revenue for partial charging. }
-%In this model, when EV $i$ is received its demand entirely, the gain is $v_{i}$ and zero, otherwise, i.e., there is no partial revenue for fractional charging. 
-This is the model that is considered in~\cite{WTang,Shroff2014}. We tackle this model in Section~\ref{sec:integral}.
-
-		%The actual aggregated peak of all parking stations must not exceeds global peak constraint.
-
-			\begin{table*}[!t]
-			\centering
-%	\vspace{-3mm}
-			\caption{Proposed algorithms and their properties.}
-			\label{tbl:algs}
-			\begin{tabular}{ | l | c | c | c |c|}
-				\hline
-				\textbf{Algorithm} & \textbf{Revenue model} & \textbf{Type} & \textbf{Optimality} & \textbf{Complexity} \\ \hline\hline    
-				\fcs& fractional& offline& Optimal & $O(n^2T+nT^2)$\\\hline 
-				\ics& integral& offline& ${\Big( 1+\sum_{j=1}^m {\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}\Big)}$-approximate & $O(nT\log T+n^2T)$ \\\hline 
-				\focs & fractional& online& $2$-competitive & $O(n^2T)$\\\hline 
-				\iocs& integral&  online& $b(1+\frac{p}{p-q}.\frac{s}{s-1})$-competitive, $(m=1)$ & $O(n^2T)$\\\hline
-			\end{tabular}
-		\end{table*}
-
-		\subsection{Problem Formulation}
-		\label{sec:problem}
-	We formulate an optimization problem to schedule the charging of the EVs with the objective of maximizing total revenue obtained from charged EVs while respecting local and global peak constraints. 
-		Note that each revenue model makes the underlying optimization problem fundamentally different. More specifically, the fractional charging model is a linear problem. 
-		Integral revenue model, however, turns the underlying charging scheduling problem to a Mixed Integer Linear Program (MILP). The integer nature originates from the $0/1$-selection decision on EVs. 
-%%%Recall that in integral revenue model the revenue is obtained given that the entire demand is fulfilled for the selected EV. 
-		%We skip the explicit formulation of the problem under integral revenue model since it could be contemplated as the linear-relaxed version of the integral revenue model (for more explanation, we refer to the discussions in Section~\ref{sec:fractional}).
-		We formulate Scheduling Problem for Adaptive charging Network (\MCSP) under fractional revenue model as follows: 
-		\bse
-		\bee
-		\MCSP: \max  && \sum\nolimits_{i=1}^n \frac{v_{i}}{D_i}\sum\nolimits_{t=a_i}^{d_i} y_i^t \label{Pobjec} \nonumber\\
-		\text{s.t.} &&\sum\nolimits_{t=a_i}^{d_i} y_i^t\leq D_i,\quad\quad\forall i, \label{ConstPartial} \\
-		&&  \sum\nolimits_{i=1}^n y_i^t\leq p^\mathsf{total} ,\quad\quad\forall t,\label{ConstTotal} \\
-		&&\sum\nolimits_{i:h(i)=j} y_i^t\leq p_j ,\quad\quad\forall t,j,\label{ConstLocal}\\
-		&& y_i^t  \leq \frac{k_i}{D_i}\sum\nolimits_{t^\prime=a_i}^{d_i} y_i^{t^\prime}, \quad\forall i,t,\label{ConstSpeed}\\
-%		&& \rev{y_i^t=0,\forall t\in\{t':t'>d_i \vee t'<a_i\}}, \\
-		\text{vars.} && y_i^t \geq 0, \quad\quad\forall i, t,\label{ConstPositive}\nonumber
-		%&& s_v(t), \quad \forall v,t
-		\eee
-		\ese
-		where $y_i^t$ is the amount that EV $i$ is charged at slot $t$. Constraint (\ref{ConstPartial}) ensures that the aggregate amount received by EV $i$ is at most the demand $D_i$. 
-%		Note that under integral revenue model, when we design our algorithm, we do not allow partial charging. 
-The global and local peak constraints are represented by constraints (\ref{ConstTotal}) and (\ref{ConstLocal}), respectively.
-
-		\revv{The constraint~\eqref{ConstSpeed} enforces the maximum charging rate of EVs.
-The straightforward way to express this constraint is to simply state that at each time slot $t$, the charging rate of EV $i$ should be less than or equal to its maximum charging rate, i.e., $y_i^t\leq k_i, \forall i,t$.
-		However, for the sake of effective algorithm design for integral model and reducing the integrality gap of the relaxed linear problem, this constraint is strengthened in the form of Eq.~\eqref{ConstSpeed}.
-		Note that in case that the aggregated charging of EV $i$ during its availability window is equal to its demand, i.e., $\sum_{t^\prime=a_i}^{d_i} y_i^{t^\prime}= D_i$, Eq.~\eqref{ConstSpeed} reduces to the simple form of $y_i^t\leq k_i$.
-		This is a natural way in approximation algorithm design to improve the performance of the algorithms under linear-relaxation based design~\cite{Carr}. }
-
-The \MCSP is an extension of formulated problem in \cite{Jain} where a job scheduling problem in cloud applications is studied.
-It turns out that the resource allocation problem in cloud systems and the EV charging scheduling problem in a \emph{single station} share similar structure.
-Indeed, each charging profile in our scheduling problem can be seen as a job in cloud system with a deadline, value, and CPU demand.
-The \MCSP, however, comes with an additional constraint~\eqref{ConstTotal}, which makes it different from the problem in \cite{Jain}, such that the existing solution \revv{will not} work in the new setting.
-More importantly, this paper studies both offline and online solutions for the problem in both fractional and integral settings, while \cite{Jain} tackles only the offline integral model.
-
-%(ii) Our solution design and analysis for integral revenue model is based on linear-relaxation primal-dual framework~\cite{Jain}.
-Therefore, in Section \ref{sec:integral} for integral revenue model, we rely on the \MCSP for the analysis of the proposed algorithms and skip to explicitly formulate the original MILP problem.
-
-%		Also, we cover the fractional revenue model and provide theoretical bounds for the proposed algorithms.
-
-%In the next two sections, we devise several algorithms to solve the \MCSP under the two revenue models (integral and fractional) and for both offline and online scenarios. 
-		\section{Fractional Revenue Model}
-		\label{sec:fractional}
-
-%\subsection{Overview of Fractional Revenue Model}
-%\label{sec:frac.overview}				
-		%In the previous section, we devised an approximation algorithm for the integral revenue model in which it is assumed that the obtained revenue is zero if the allocated resource is less than the demand.
-Although this assumption is reasonable in some scenarios,
-%To develop a solution for the \MCSP, we first consider fractional revenue model.
-%However, algorithms for integral revenue model cannot achieve the same performance as the algorithms of this section i.e., \fcs and \focs.
-
-In the fractional model, the revenue of the CS from EV $i$ is directly proportional to the amount of resource that the EV is received, i.e.,
-		\begin{equation}
-			v_i^{\mathsf{f}}=\frac{\sum_t y_i^t}{D_i}v_i,
-			\label{Eq:partial_value}
-		\end{equation}
-		where $v_i$ is the gain, if the entire demand $D_i$ is fulfilled and $v_i^{\mathsf{f}}$ is the fractional gain.
-
-%Under fractional revenue model and without the binary variable of selecting EVs, the underlying problem turns into a linear one. 
-We propose a simple algorithm, called \fcs, with low computational complexity \rev{ of $O(n^2T+nT^2)$} for the fractional model that finds the optimal solution in offline setting.
-Note that even though linear programs can be solved in polynomial time in general, the complexity of our proposed algorithm is much lower than the general linear program algorithms.
-Moreover, our proposed offline algorithm applies a valley-filling strategy to reduce the peak.
-%The details of the proposed algorithm \fcs is given in~\cite{alinia2017online}.
-In the following, the online $2$-competitive algorithm is designed, where no exact information or stochastic modeling of future inputs of the problem is available.
-A summary of proposed algorithms with their complexity and assumptions is given in Table \ref{tbl:algs}.
-
-\revv{
-\subsection{Optimal Offline Design}
-\label{sec:fopt}	
-\bt{
-In this section, we propose an optimal algorithm for offline fractional model.
-As a natural solution, one may think of a greedy algorithm with the strategy as follows: at each time slot, charge the EV with highest unit-value and process others if only the resource cannot be used by this EV (probably due to maximum charging rate constraint).
-This approach is a popular, yet straightforward method in the online scheduling.
-However, it turns out that this approach cannot provide an optimal solution to the problem even in fractional revenue model.
-In fact, this approach only provides a 2-competitive solution.
-i.e., the profit obtained by the algorithm would be $1/2$ of the optimum.
-As an intuition of the proof think of two EVs where the one with lower unit value cannot wait due to its deadline and the EV with higher unit value has a long park time.
-Then, the optimal solution here could be first serving the EV with earlier deadline (and not the one with highest unit values).
-}
-
-We refer the proposed algorithm in this secion as the \fcs and summarize it as Algorithm~\ref{alg:optimal-off}.
-The \fcs works in two phases.
-In the first phase (Section~\ref{sec:ph1}), the algorithm decides on the amount of resource to be allocated to each EV within its availability window and reserves resources accordingly.
-In this phase, the details of allocation is not known.
-The actual resource allocation is done in the second phase (Section~\ref{sec:ph2}) by setting variables $y_i^t$.
-
-Before discussing the details of the algorithm, we give \bt{a definition} and introduce some notations to facilitate our algorithm design.
-
-\begin{defi}
-	Time interval $[\delta,\delta']$ is a ``super interval'' for interval $[t,t']$ if $1\leq \delta\leq t \text{~AND~} t' \leq \delta'\leq T$.
-	Moreover, $\mathcal{I}_{t,t'}$ is the set of all super intervals of interval $I_{t,t'}$ i.e., ${\mathcal{I}_{t,t'}=\{[\delta,\delta']: 1\leq \delta\leq t \text{~AND~} t'\leq \delta'\leq T\}}$.
-\end{defi}
-
-%		For example, $\mathcal{I}_{1,1}=\{I_{1,1},I_{1,2},I_{1,3},\dots ,I_{1,T}\}$. 
-The number of super intervals of an interval is at most $T^2$ and at least one (for interval $[1,T]$).
-
-Let $R_i$ be the amount of resource that is reserved for EV $i$ by the \fcs and $I_{t,t'}$ as time interval $[t,t']$.
-% with $t,t'\in\{1,\dots ,T\}$ which includes time slots $t,t+1,\dots ,t'$. 
-Then, assuming that charging demands are sorted in non-increasing order of their unit values, $A^i_j(t,t')$ is the aggregate residual resource in interval $I_{t,t'}$ at station $j$ assuming that the reservation for EVs $1$ to $i$ is accomplished.
-We now explain in detail each phase of the algorithm.
-
-\subsubsection{Phase I-Reservation\label{sec:ph1}} In Line~\ref{algline:sort1}, the EVs are sorted in a non-increasing order of their unit values.  
-%		i.e., ${v_1\slash D_1\geq v_2\slash D_2\geq\dots \geq v_n\slash D_n}$. 
-In Line~\ref{algline:setR}, the \fcs processes demand of EV $i$, picked from top of the ordered list, and sets $R_i$ as the amount to be reserved for EV $i$ which will be allocated in Phase II.
-In Line~\ref{algline:seta}, the residual resource of all intervals in set $\mathcal{I}_{a_i,d_i}$ decreases by $R_i$ and EV $i$ is added to the set of selected EVs.
-
-\begin{algorithm}[t]%\small%1
-	%\footnotesize
-	\revv{
-	\caption{\fcs}
-	\label{alg:optimal-off}
-	\DontPrintSemicolon 
-	\KwIn{$n$ EVs with their profile, local and global peak constraints $p_j, j=1,\dots ,m$ and $p^\mathsf{total}$ }
-
-	\KwOut{Optimal scheduling under fractional model}
-	\BlankLine
-
-	Sort charging requests in non-increasing order of their unit values, i.e., $\frac{v_1}{D_1}\geq \frac{v_2}{D_2}\geq\dots \geq \frac{v_n}{D_n}$\label{algline:sort1}
-
-	%	\slash\slash\textit{\texttt{Use sorted list to process demands}}
-
-	$\mathcal{L}\leftarrow \emptyset$
-
-	\slash\slash\textit{\texttt{Phase I}}
-
-	\For{$i=1,\ldots, n$}{
-		%\slash\slash\textit{\texttt{update demand and value}}
-
-		$R_i \leftarrow \min\{D_i, \min\limits_{t,t'} A^{i-1}_{h(i)}(t,t'), \forall t,t': I_{t,t'}\in\mathcal{I}_{a_i,d_i}\}$\label{algline:setR}
-
-		\If{$R_i>0$}{
-			$A^{i}_{h(i)}(t,t')\leftarrow A^{i-1}_{h(i)}(t,t')-R_i, \forall t,t': [t,t']\in\mathcal{I}_{a_i,d_i}$ \label{algline:seta}\\
-			$\mathcal{L}\leftarrow \mathcal{L}\cup{i}$
-	}}
-	\slash\slash\textit{\texttt{Phase II}}
-
-	Sort EVs in $\mathcal{L}$ in increasing order of their charging flexibility i.e., $\frac{(d_i-a_i+1)k_i}{D_i}, i\in \mathcal{L}$.
-
-	%	Let $i$ be the index of $i^{th}$ EV in list $\mathcal{L}$
-
-	\For{$i=1,\ldots, |\mathcal{L}|$}{
-
-		Pick EV $i$ from the sorted list $\mathcal{L}$.
-
-		$\emph{feasible}\leftarrow \big(\sum_{t=a_i}^{d_i}\min\{k_i,A^{i-1}_{h(i)}(t,t)\}\big) - R_i$
-
-		\If{feasible $<0$}{
-			Re-allocate previously allocated EVs such that $\emph{feasible}\geq 0$
-		}
-		Arbitrarily allocate $R_i$ to EV $i$ in its availability window\label{algline:fcsallocate}	
-	}}
-\end{algorithm}
-
-\begin{lem}
-	Provided that for EV $i$ we have 
-	\bee
-	\label{eq:ri}
-	R_i\leq\min\left\{D_i, \min_{t,t'} A^{i-1}_j(t,t'), \forall t,t': I_{t,t'}\in\mathcal{I}_{a_i,d_i}\right\}
-	\eee
-	 with a dummy $A^0_j(t,t')$ defined as
-$A^0_j(t,t')=(t'-t+1)\times\min \{p^\mathsf{total},p_{j}\},$
-	then there is a feasible allocation to allocate $R_i$ to EV $i$ in its availability window $[a_i,d_i]$. 
-	\label{thm:R_feasible}
-\end{lem}
-
-In Lemma \ref{thm:R_feasible}, $A^0_j(t,t')$ indicates the available resource when no charging request is processed in $I_{t,t'}$. 
-In Eq.~\eqref{eq:ri}, the second term, i.e., $\min_{t,t'} A^{i-1}_{j}(t,t')$, indicates the minimum remaining resource in all super intervals of interval $I_{a_i,d_i}$.
-For $i\geq 1$, $A^i_j(a_i,d_i)$ is defined as follows:
-
-\begin{equation*}
-A^i_j(a_i,d_i)=\begin{cases}
-A^{i-1}_j(a_i,d_i)-R_i & j=h(i),\\
-A^{i-1}_j(a_i,d_i) & j\neq h(i).
-\end{cases} 
-\end{equation*}
-
-The optimal value of $R_i, i=1,\dots ,n$ is set according to the following lemma:
-
-\begin{lem}
-	Given $n$ EVs sorted in a non-increasing order of the unit values, ${v_1\slash D_1\geq v_2\slash D_2\geq\dots \geq v_n\slash D_n}$, and the value of $R_i$, where $R_i$ is set after $R_{i-1}, i=2,\dots ,n$ by Eq.~\eqref{eq:ri}, then,
-	$$R_i = \min\left\{D_i, \min_{t,t'} A^{i-1}_{h(i)}(t,t'), \forall t,t':I_{t,t'}\in\mathcal{I}_{a_i,d_i}\right\},\forall i,$$
-	is the optimal value for $R_i$. 
-	\label{thm:R_star}
-\end{lem}
-
-\subsubsection{Phase II- Allocation\label{sec:ph2}} Lemma~\ref{thm:R_feasible} shows that there is a feasible scheduling to allocate the reserved resources.
-However, despite its feasibility, it is not straightforward to find such \revv{a schedule}.
-For example, assume that for EV $i$, $R_i=10$ and $k_i=4$.
-It is possible that all available resources are concentrated in a single time slot but EV $i$ cannot use more than $4$ kWh of it.
-In this situation, the previously allocated resources in interval $I_{a_i,d_i}$ should be re-allocated such that the concentrated resources are \emph{dispersed} and we have $\sum_{t=a_i}^{d_i}\sigma_t \geq R_i$ where $\sigma_t =\min\{k_i,A^{i-1}_{h(i)}(t,t)\}$ is the maximum resource that can be allocated to EV $i$ at time slot $t$.
-Since the total amount of allocated resource does not change in the interval, such dispersion is possible and can be done by a simple algorithm in which allocates $\min\{k_i,A^{i-1}_{h(i)}(t,t)\}$ starting from time slot $t=a_i$ until $R_i$ units is allocated.
-To further reduce the peak of the system, we will develop \sa\ algorithm (See Section \ref{sec:integral}) which acts more intelligent so that Line \ref{algline:fcsallocate} of the \fcs can be replaced by ``Run \sa$(i,R_i)$''.
-
-\begin{thm}
-	\label{cor:1}
-	\fcs is an optimal solution under fractional revenue model.
-\end{thm}
-
-The following theorem characterizes the complexity of \fcs.
-
-\begin{thm}
-	\label{thm:complexity}
-	The time complexity of \fcs algorithm is $O(n^2T+nT^2)$ where $n$ is the number of EVs and $T$ is number of time slots.
-\end{thm}
-}
-
-%\vspace{-4mm}
-\subsection{Online Scenario}
-\label{sec:fonline}
-In this section, we devise an algorithm for the scenario that EVs arrive in online fashion.
-The scheduling decisions at each time slot are made given the information of available EVs and neither exact values nor stochastic modeling of future arrivals is available.
-Our goal is to obtain a \emph{competitive ratio} for the online algorithm.
-A scheduling algorithm $\mathcal{A}$ is $c$-competitive for $c\geq 1$ if the revenue obtained by the optimal offline algorithm is at most $c$ times the algorithm $\mathcal{A}$'s revenue for any input sequence~\cite{borodin2005online}.
-
-The proposed online algorithm for the fractional model, referred to as \focs, is listed as Algorithm~\ref{alg:focs}.
-The \focs is a simple yet efficient algorithm that always selects EVs with highest unit value to allocate as follows.
-First, the algorithm sorts the available EVs at each time slot~$t$ based on their unit value (Line~\ref{algline:sort}).
-\revv{In this step, the algorithm breaks ties based on EVs' deadline i.e., if two EVs have the same unit value, then the one with earliest deadline comes first in the sorted list.} Next, the \focs selects one EV at a time from the sorted list to allocate with maximum charging rate considering the EV's remaining demand, maximum charging rate, and peak constraints (Lines~\ref{algline:focsfor}-\ref{algline:focssety}).
-The allocation is continued until all resources are allocated or there is no more EV that could be allocated.
-%For unselected EVs, the value of $y_i^t$ will be $0$ in Line \ref{algline:focssety} of the algorithm. 
-The time complexity of the \focs is $O(n^2T)$, determined by cost of its ``\textbf{for}'' loop multiplied by total number of times that the algorithm needs to be run.
-% i.e., $T$.
-
-%\vspace{-4mm}
-\begin{algorithm}%\small%1
-\footnotesize
-\caption{\focs: $\forall t\in \{1,2,\dots ,T\}$}
-\label{alg:focs}
-\DontPrintSemicolon 
-%\KwIn{Available EVs at time slot $t$, number of CSs $m$, local peak constraint $p_j, j=1,\dots ,m$, global peak constraint $p^{\textrm{total}}$}
-
-%\KwOut{A feasible charging scheduling}
-
-%$\backslash\backslash\texttt{Initialize:}$
-
-\BlankLine
-
-$\mathcal{M}^t\leftarrow$ The set of available EVs that not received their entire demand by $t$
-
-Sort EVs in set $\mathcal{M}^t$ indexed by $i=1,\dots ,|\mathcal{M}^t|$: $v_1/D_1\geq v_2/D_2\geq\dots\geq v_{|\mathcal{M}^t|}/D_{|\mathcal{M}^t|},$  \revv{where ties are broken based on users' deadline (giving priority to the users with earliest deadline) }\label{algline:sort}
-
-\For{$i=1,\ldots,|\mathcal{M}^t|\label{algline:focsfor}$}{
-
-$y_i^t\leftarrow \min\{k_i,D_i-\sum_{\tau=a_i}^{t}y_i^{\tau},p_{h(i)}-\sum_{i':h(i')=h(i)}y_{i'}^t,p^{\textrm{total}}-\sum_{i'}y_{i'}^t\}$ \label{algline:focssety}
-
-}
-
-\end{algorithm}
-Despite the simplicity of \focs which makes it easy to implement, its performance is sound and within a constant factor of the offline optimum.
-We now proceed to analyze the performance of the \focs by first giving some preliminaries.
-
-Fix an optimal scheduling and let $\mathcal{S}_{\focs,t}$ and $\mathcal{S}_{\opt,t}$ be the sets of EVs selected by the \focs and optimal solution at time slot $t$, respectively.
-Let $y_{i}^t$ and $z_{i}^t$ be the charging rate of EV $i$ set by \focs and \opt, respectively.
-We define $\Delta_{i}^t$ as follows:
-\begin{equation}
-\label{eq:delta}
-\Delta_{i}^t =
-     \begin{cases}
-       \min\{z_{i}^t-y_{i}^t,r_{i,t}\} &\quad i\in\mathcal{S}_{\opt,t},z_{i}^t>y_{i}^t, \\
-       0& \quad\text{otherwise},  \\
-     \end{cases}
-\end{equation}
-where $r_{i,t}$ is the remaining demand of EV $i$ by the end of time slot $t$.
-$\Delta_{i}^t>0$ indicates that the optimal algorithm allocated $\Delta_{i}^t$ units more resources to EV $i$ than the \focs by time slot $t$ that could be \emph{feasibly} allocated by \focs to the EV $i$.
-If for any EV $i\in\mathcal{S}_{\opt,t}$ and time slot $t\in\mathcal{T}$ we have $y_{i}^t=z_{i}^t$, i.e., $\Delta_{i}^t=0$, then the \focs is obviously optimal because it gains whatever the optimal solution gains.
-\rev{We define \textit{loss} of the \focs imposed by EV $i$ as follows:
-\begin{equation}
-\label{lBj0}
-l_{i,t}=\Delta_{i}^t\frac{v_i}{D_i},
-\end{equation}
-
-Note that the loss always takes a non-negative value as $\Delta_i^t\geq 0$.} When \focs sets charging rate of an EV less than its rate in the optimal solution, it gains $\Delta_{i}^t v_i/D_i$ less than the optimal solution from that EV.
-An upper bound for the distance between the optimal objective value (denote by \opt) and the revenue of the \focs (denote by \alg) is summation of the losses over all time slots and all EVs, i.e.,
-\begin{equation}
-\label{eq:optdist}
-\opt-\alg\leq \sum_{t=1}^T\sum_{i\in\mathcal{S}_{\opt,t}} l_{i,t}.
-\end{equation}
-
-%Notice that it is possible that an algorithm does not choose any selected EV by a particular optimal solution but still provide an optimal or near-optimal solution as there can be multiple optimal solutions.
-In particular, $\mathcal{S}_{\focs,t}\cap \mathcal{S}_{\opt,t}=\emptyset, \forall t$ cannot lead to any conclusion on the competitive ratio of the \focs.
-In addition to the amount of loss, the gain of the algorithm from charging alternative EVs should also be taken into account in comparison between \opt and \alg.
-
-Let $i\in\mathcal{S}_{\opt,t}$, $i\notin\mathcal{S}_{\alg,t}$ and $g_{i,t}$ be the gain that the \focs obtains from charging another EV instead of $i$ at time slot $t$.
-We are going to show that in the \focs, for each EV $i$ with $l_{i,t}>0$ there must be another EV (denote by $i'$) where $y_{i'}^t\geq \Delta_i^t$ and $\frac{v_{i'}}{D_{i'}}\geq \frac{v_i}{D_i}$ which means in resource allocation phase for EV $i$, the \focs allocated the difference $\Delta_i^t$ to another EV with the same or higher unit value.
-This can be proved by considering the fact that (i) the selected EVs have higher unit values than the unselected EVs, and (ii) the charging rate of the selected EVs are set to the maximum feasible value.
-Moreover, the \focs is \emph{``work-conserving''} i.e., it does not let any resource remain unused if there are some EVs that can use it.
-
-Let $g_{i,t}$ denote the gain that \focs obtains from allocating the same amount of resource that optimal algorithm allocated to EV $i$ (with size $z_i^t$) to another EV(s).
-If $\Delta_{i}^t=0$, the loss is zero. If $\Delta_{i}^t>0$, then by the charging strategy that the \focs uses we can conclude that (i) $i$ is not finished by the \focs, and (ii)
-\rev{no more resources from station $p_{h(i)}$ can be feasibly allocated,} otherwise, the \focs could allocate more resources to EV $i$.
-Therefore, the $\Delta_{i}^t$ units of the resource \rev{are} allocated to one or multiple other EVs (denote them by set $\mathcal{J}_i^t$) by the \focs.
-Moreover, it must hold that all the EVs in set $\mathcal{J}_i^t$ have a unit value equal to or higher than $v_i/D_i$ which yields $g_{i,t}\geq l_{i,t}$, otherwise, the \focs should not prefer the EVs in $\mathcal{J}_i^t$ to $i$.
-\rev{Since the result holds for any arbitrarily EV $i$, we can get the following:}
-
-\begin{equation}
-\label{eq:lg}
-\sum_{i=1}^n\sum_{t=1}^Tl_{i,t}\leq\sum_{i=1}^n\sum_{t=1}^Tg_{i,t}.
-\end{equation}
-
-Moreover, the total gain of \focs, i.e., \alg, is equal to sum of its gains from each single EV:
-\begin{equation}
-\label{eq:ALG}
-\rev{\alg= \sum_{i=1}^n\sum_{t=1}^Tg_{i,t}.}
-\end{equation}
-
-With the above discussion and using Eqs. (\ref{eq:optdist}), (\ref{eq:lg}) and (\ref{eq:ALG}) we are able to derive a competitive ratio of $2$ for the \focs.
-
-\begin{thm}
-	\label{thm:focscompetitive}
-	The \focs is $2$-competitive.
-\end{thm}
-
-\emph{Remarks:} When there is only one CS and EVs have no limit on their charging rate, the \focs is identical to the \textsc{FirstFit} algorithm ~\cite{firstfit} which is known to be $2$-competitive for classic job scheduling problem.
-However, the charging rate limitation is crucial for EV charging problem.
-Moreover, \cite{firstfit} uses \revv{a} ``charging argument'' to prove the competitive ratio of the proposed algorithm which cannot be directly applied to our problem.
-Thus, the \focs extends the \textsc{FirstFit} and makes it practical for the EV charging scenario.
-Moreover, the proof technique used for the competitive analysis of the \focs is fundamentally different from the one used in \cite{firstfit}.
-%%%Finally, in~\cite{Robu} an online $2$-competitive algorithm for EVs with partial charging is proposed.
-The competitive ratio obtained assuming that charging of EVs is instantly reversible at departure times.
-This assumption is not practical in reality since similar to charging phase, there is a discharging rate constraint for EVs.
-
-%\begin{thm}
-%\label{thm:focscomplexity}
-%
-%The time complexity of \focs is $O(nT\log n)$.
-%\end{thm}
-		\section{Integral Revenue Model}
-		\label{sec:integral}
-%
-%		\subsection{Overview of Integral Revenue Model}
-%		\label{sec:intoverview}
-		The MILP form of the \MCSP in integral model is a generalized form of the $0/1$-knapsack problem which is a well-known NP-hard problem.
-\rev{To give an intuition, consider the scheduling problem in a single time slot (i.e, $T=1$).
-Then, allocating power resources to the EVs is equivalent to allocating the capacity of knapsack to the items.
-}
-		In Section~\ref{subsec:icsalgorithm}, we propose a fast polynomial time offline approximation algorithm for the integral problem.
-In Section~\ref{sec:onlineint}, we extend the result and propose an online algorithm for the integral model.
-%		, where the EVs arrive in slot-by-slot fashion, and the scheduler has no information of the future arrivals.
-
-%The problem is even more challenging when the uncertainty in EVs' arrival is taken into account.
-At each time slot, the scheduler has no information of unit values of the future charging profiles.
-Therefore, the scheduler cannot make sure about the efficiency of its current charging decision.
-%It can be shown that when there is no assumption on the charging profiles of EVs (including the value of slackness parameter) and the charging decision , no online algorithm can provide a performance guarantee meaning that in the worst case, the ratio of the optimal objective value to the one obtained by the online algorithm can be arbitrary small.
-In fact, when the online algorithm selects
-
-		\subsection{Offline Scenario}   
-		\label{subsec:icsalgorithm}
-		We design our offline scheduling algorithm under integral model referred to as \ics, to solve the \MCSP approximately. 
-%		Our algorithm design is inspired by the basic algorithm proposed in \cite{Jain}.
-The algorithm in \cite{Jain} works for a single CS where arrival time of all EVs are the same and there is no global peak constraint.
-Since the performance analysis of the proposed algorithm relies on a dual fitting method and utilizes weak duality property, \revv{we first need to construct the dual problem of \MCSP.
-Toward this, we introduce variables $\alpha, \beta, \gamma$ and $\pi$.
-Generally, in primal-dual approximation algorithm design, each constraint (resp.
-variable) in primal (resp.
-dual) problem is associated with a variable (resp.
-constraint) in dual (resp.
-primal) problem.
-In our case, constraints (\ref{ConstPartial}) (\ref{ConstTotal}), (\ref{ConstLocal}) and (\ref{ConstSpeed}) in the \MCSP are respectively associated with dual variables $\alpha, \beta, \gamma$ and $\pi$ (for more details see \cite{approx}).
-The dual problem is formulated as follows:}
-		\bse
-		\bee
-		\min &&\sum_{i=1}^n D_i\alpha _i + \sum_{j=1}^m \sum_{t=1}^T p_j\beta (t)+\sum_{t=1}^T p^\mathsf{total}\gamma (t)\nonumber\\ 
-		\textrm{s.t.} && \alpha _i+\beta (t) +\gamma _i + \pi (t)- \frac{k_i}{D_i}\sum_{t'=a_i}^{d_i} \pi _i(t^\prime) \geq \frac{v_{i}}{D_i},\label{ConstDcover} \nonumber\\
-		&& \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\forall i, t\in [a_i, d_i],\\
-		\textrm{vars.}&&\alpha _i, \beta _i, \gamma,  \pi _i(t)\geq 0,\quad\quad\forall i,t. \nonumber
-		\eee
-		\ese
-
-		%%%In this section, we explain \ics in details and then in Section~\ref{subsec:analysis}, we analyze approximation factor of the algorithm. The \ics algorithm is listed as Algorithm~1.
-
-		\subsubsection{Explanation of the Main Algorithm} 
-		\label{sec:icsexplanation}
-		Our algorithm design is inspired by the basic algorithm proposed in \cite{Jain}.
-\revv{The algorithm in~\cite{Jain}, however, works for a single CS where arrival time of all EVs are the same and there is no global peak constraint.}
-		The \ics algorithm (listed as Algorithm \ref{alg:ics}) works in two phases.
-In the first phase it sorts the charging requests based on their unit values in a non-increasing order.
-Then, it selects most valuable demand.
-If the remaining resource is enough to cover the \emph{entire} demand of the EV, it is admitted to receive the demand (Lines~$6$-$7$).
-%		When \ics processes EV $i$, the algorithm checks for the feasibility of allocating $D_i$ units of the resource within its availability window $[a_i,d_i]$ without violating the constraints related to the maximum charging rate $k_i$, local and global peaks (Lines~$6$-$8$).
-
-		\emph{Scheduling of the Selected EV:} \revv{If the feasibility check passed (Line 6 in Algorithm 3)}, \ics calls sub-procedure \sa\ to allocate required resources in interval $[a_i,d_i]$.
-Then, $\alpha _i$ is set to $v_i\slash D_i$ in order to cover dual constraint in Eq.~\eqref{ConstDcover} (Lines~$7$-$8$).
-
-		In \sa, 
-		%%%When EV $i$ is selected to get charged, \sa\ is called for the charging scheduling. 
-		let us define $W(t,h(i))=\sum_{i': h(i')=h(i)} y_{i'}^t$ as total workload at time slot $t$ in CS $h(i)$ and $\bar{W}(t,h(i))$ as total available load to allocate at time slot $t$ for CS $h(i)$.
-We always have ${\bar{W}(t,h(i))+W(t,h(i))=p_{h(i)},  \forall t, i}$.
-For scheduling, \sa\ applies two main policies: 1) \emph{valley-filling} and, 2) \emph{right-to-left allocation}.
-\revv{With valley-filling, the slots with more available resources are preferred which helps to reduce the peak of the system.} %%%It also can be seen as a smoothing method which tries to reduce the variance of the allocated resources at different slots.
-%				The simulation results in Section \ref{sec:simul} will confirm this claim. 
-				Right-to-left allocation is used when two or more time slots are equal in terms of their remaining resources. 
-%				When this policy applies on scheduling of EV~$i$, any EV~$i'$ with $i'>i$ and $d_{i'}<d_i$ has more chance to get charged since the algorithm tends to charge EV $i$ in interval $[d_{i'}+1,d_i]$ (i.e., right hand part of the EV's availability window) and keeps resources in $[a_{i'},d_{i'}]$ for EV $i'$.
-A ranking based approach is used to apply the aforementioned policies. 
-		To charge  EV $i$, \sa\ ranks time slots in interval $[a_i,d_i]$.
-Then, charging is done by allocating resources from the higher ranked time slot to lowest one.
-The rank of a time slot $t$ is calculated based on remaining resources in the time slot (valley-filling) and value of $t$ (right-to-left allocation).
-
-		\begin{algorithm}%\small%1
-			\footnotesize
-			\caption{\ics}
-			\label{alg:ics}
-			\DontPrintSemicolon 
-%			\KwIn{$n$ EVs with $a_i, d_i, v_i, D_i,$ and $k_i$ associated with each EV $i$, $m$ CSs, local and global peak constraints $p_j, j=1,\dots ,m$, and $p^\mathsf{total}$}
-
-%			\KwOut{A feasible scheduling of EVs}
-			\BlankLine
-			%\begin{algorithmic}
-
-			%\slash\slash\textit{\texttt{Initialization}}
-			\textbf{initialize}: $y\leftarrow 0, \alpha\leftarrow 0, \beta\leftarrow 0, \gamma\leftarrow 0, \pi\leftarrow 0$
-
-			Sort charging requests in non-decreasing order of their unit values: $v_1/D_1 \geq v_2/D_2\geq\dots \geq v_n/D_n$
-%			$\frac{v_1}{D_1} \geq \frac{v_2}{D_2}\geq\dots \geq \frac{v_n}{D_n}$
-%			\slash\slash\textit{\texttt{Use sorted list to process demands}}
-
-			\For{(i=1\dots n)}{
-
-				\For{$t=a_i\dots d_i$}{
-					$\sigma_t\leftarrow  \min\Big\{p_{h(i)}-\sum_{i':h(i')=h(i)}y_{i'}(t),$ \newline $\qquad p^\mathsf{total}-\sum_{i'=1}^n y_{i'}^t,k_i\Big\}$
-
-				}
-
-%				\slash\slash\textit{\texttt{if enough resources remain for EV $i$}}
-
-				\If{$D_i\leq\sum_{t=a_i}^{d_i}\sigma_t$}
-				{
-					\sa($i,D_i$)\\
-					$\alpha _i\leftarrow v_i/ D_i$
-				}
-				\Else {
-					\If{$(\beta (d_i)=0)$}{
-						\bc($i$)}
-				}
-			}
-
-			\For{(i=1\dots n)}{ 
-				\If {EV $i$ is not selected}{
-					\rc($i$);
-				}
-			}
-			%\end{algorithmic}
-		\end{algorithm}
-
-\emph{Dual Feasibility of the Non-selected EVs:} \bt{If remaining power resource is not enough} to fully charge EV $i$, i.e.,  $D_i>\sum_{t=a_i}^{d_i}\sigma_t$, the EV cannot be selected.
-However, we still need to satisfy constraint~\eqref{ConstDcover} in dual problem which is done by calling \bc($i$).
-To cover the constraint~\eqref{ConstDcover} for EV $i$, sum of dual variables for all $t\in [a_i ,d_i]$ should be greater than or equal to ${v_i \slash D_i}$.
-\bc($i$) sets $\beta (t)$ to ${v_i \slash D_i}$ for all time slots $t$ in interval $[t_\mathsf{cov}, R(d_i)]$ (Lines $3$-$4$ of Algorithm~\ref{alg:betacover}).
-Observe that  ${\beta (t^\prime)\geq v_i \slash D_i,\forall t^\prime< t_\mathsf{cov}}$ (with $ t_\mathsf{cov}>1$) considering that the demands are sorted in a non-increasing order of the unit-values and $\beta (t')$ is already set to ${v_{i'} \slash D_{i'}}$ when processing the earlier charging demand of EV $i'$ which is not selected.
-Hence, ${v_{i'}\slash  D_{i'}\geq v_i \slash D_i}$, thereby ${\beta (t)\geq v_i \slash D_i,}$ and the dual constraint in~\eqref{ConstDcover} is satisfied.
-		Lines $1$-$4$ of \bc\ is enough to cover the dual constraint.
-However, the algorithm continues in Lines $5$-$8$ by setting a variable $\Phi_{i'}(t)$ for time slots $t=1,\dots ,R(d_i)$ to a value dependent to amount of the resource that a selected EV $i'$ received at slot $t$.
-$\Phi_{i'}(t)$ will be used in approximation analysis of the main algorithm and has no effect on the scheduling of EVs.
-		%We borrowed algorithm \bc($i$) from \cite{Jain} and adjusted it for multiple station mode.		
-%		\vspace{-3mm}
-		\begin{algorithm}%\small%1
-			\footnotesize
-			\caption{\sa($i,D_i$)}
-			\label{SmartAllocate}
-			\DontPrintSemicolon 
-			\KwIn{EV $i$ to receive $D_i$ from CS $h(i)$}
-
-			Rank time slots in interval $[a_i,d_i]$ such that for any $t_1$ and $t_2$:
-			$\mathsf{rank}(t_1)> \mathsf{rank}(t_2)$ iff $\bar{W}(t_1,h(i))>\bar{W}(t_2,h(i))$ OR $\bar{W}(t_1,h(i))==\bar{W}(t_2,h(i)) \wedge t_1>t_2$
-
-			\While {$\sum_{t'=a_i}^{d_i}y_i^{t'}\neq D_i$}{
-
-				Select time slot $t$ with highest rank which is not selected before
-
-				Allocate $\min \left\{k_i,\bar{W}(t,h(i)),D_i-\sum_{\tau=a_i}^{t}y_i^{\tau},p^{\textrm{total}}-\sum_{i'}y_{i'}^t\right\}$ to EV $i$ at $t$
-
-			}
-		\end{algorithm}	
-%		\vspace{-7mm}	
-		\begin{algorithm}%\small%1
-			\footnotesize
-			\caption{\bc($i$)}
-			\label{alg:betacover}
-			\DontPrintSemicolon 
-			%\KwIn{EV $i$ which is not selected to charge}
-
-			\BlankLine
-
-			$t_\mathsf{cov}\leftarrow \min \{t: \beta (t)=0\}$
-
-			$R(d_i)=\max \{t\geq d_i : \forall t^\prime\in (d_i,t], \bar{W}(t^\prime)<q_{h(i)} \}$
-
-			\For{$(t=t_\mathsf{cov}\dots R(d_i))$}{
-				$\beta (t)\leftarrow v_i/D_i$
-			}
-
-			\For{$(t=1\dots R(d_i))$}{
-				\For{$(i'=1\dots n))$}{	
-					\If{$y_{i'}^t>0 \wedge \Phi_{i'}(t)=0$}{
-						$\Phi_{i'}(t)\leftarrow\big[ \frac{p_{h(i)}}{p_{h(i)}- k_i}\frac{s}{s-1}\big] .\frac{v_i}	{D_i}y_{i'}^t$
-					}
-				}
-			}
-		\end{algorithm}
-%		\vspace{-7mm}
-		\begin{algorithm}%\small%1
-			\footnotesize		
-			\caption{\rc($i$)}
-			\label{Replace}
-			\DontPrintSemicolon 
-%			\KwIn{EV $i$}
-%			\KwOut{Updated schedule}
-
-			$\mathcal{L} \leftarrow \emptyset$\\			
-			$v_\mathsf{inc}\leftarrow v_i$\\			
-			$\sigma_t\leftarrow 0, t=a_i,\dots ,d_i$
-
-			%Define $\delta_i(t)=\min \{k_i,\bar{W}(t,h(i))\}$
-
-			%$\Delta\leftarrow \sum_{t=a_i}^{d_i}\min\{\bar{W}(t,h(i)), k_i\}$
-
-			\For{($i' =i-1\dots 1$)}{ 
-				\If {EV $i'$ is selected $\wedge (h(i')=h(i)) \wedge (v_\mathsf{inc}-v_{i'})>0$}{
-					Add EV $i'$ to list $\mathcal{L}$
-
-					$v_\mathsf{inc}\leftarrow v_\mathsf{inc}-v_{i'}$
-
-					\For{($t=a_i\dots d_i$)}{
-						$\sigma _t\leftarrow\sigma_t + \min\{k_i,y_{i'}^t\}$
-					}
-				}
-			}
-
-			\If {$\sum_{t=a_i}^{d_i}\sigma_t\geq D_i$}{
-				Remove EVs in list $\mathcal{L}$ from charging schedule
-
-				\sa($i,D_i$)
-			}
-		\normalsize
-		\end{algorithm}
-
-		\emph{Improving the Gain:} In the second phase, the \ics tries to increase total value of selected EVs by calling \rc($i$) on every unselected EV $i$ (Lines~$12$-$14$).
-\rev{The \rc(i) (listed as Algorithm $6$) checks that whether the total revenue can be increased by replacing some selected EVs with EV $i$ or not (Lines $4$-$9$).
-If such EVs are found, the algorithm stops their charging and allocates EV $i$ using \sa\ (Lines $10-12$).}
-		%We refer to ~\cite{alinia2017online}, for the details and intuition behind this algorithm. 
-%		Before giving the details of \rc($i$), we first explain the intuition behind this algorithm. 
-%		 Note that if in the scheduling problem we set $T=1, m=1, k_i=p^\mathsf{total}, a_i=d_i=1\ \forall i$, then the problem is equal to the well-known $0$-$1$ knapsack problem~\cite{approx}.
-In the knapsack problem, a widely used greedy approach sorts items based on their unit values and selects items accordingly.
-It turns out that in this approach the approximation factor can be arbitrarily bad.
-For example, consider a knapsack problem with two items with $v_1=2, v_2=p^\mathsf{total}, D_1=1$, and  $D_2=p^\mathsf{total}$.
-Given these values we have $v_1\slash D_1>v_2\slash D_2$.
-To maximize total value of selected items, the optimal solution chooses item $2$ while greedy algorithm selects item $1$ which results in a worst-case approximation factor of ${c \slash \opt}$ in general where $c$ is a constant (in this example $c=2$).
-To resolve it, one approach is to \emph{re-consider} unselected items after running greedy algorithm and replace some selected items in the knapsack with unselected ones and then check whether the result is improved or not.
-In a simple case, only the largest unselected item can be examined which makes a significant theoretical improvement by providing a worst case approximation factor of $\opt\slash 2$.
-%		 
-%\ics algorithm leverages the same idea but using a more intelligent replacing method called \rc($i$).
-\rc($i$) is called on every unselected EV $i$.
-It tries to find some selected EVs that if they are replaced by EV $i$, total revenue from the selected EVs increases.
-%%%When \ics calls \rc($i$) on all unselected EVs, an improvement in total revenue of final selected EVs is expected.
-%This is confirmed by the simulation results in Section~\ref{sec:simul}.
-
-		\subsubsection{Analysis}
-		\label{subsec:analysis}
-		In primal-dual algorithm, the goal is to design an algorithm in a way that it produces a good solution for primal problem (with primal value $\Gamma$) and a feasible solution for the dual problem (with dual value $\Lambda$).
-Then, assuming that the primal problem is a maximization problem, to prove that the algorithm is $c-$approximation (for $c\geq 1$), the important part is to show that $\Lambda\leq c\Gamma$.
-Then, based on weak duality theorem we have $\Lambda\geq \opt$, and it is concluded that $\Gamma \geq \frac{1}{c}\times\opt$ where $\opt$ is the optimal value.
-		Based on the above understanding, the following theorem scrutinizes the approximation ratio of the \ics assuming that arrival times are the same for all EVs. 
-%		First note that the designed scheduling algorithm outputs a feasible scheduling since it respects the constraints in the primal problem.
-Also, the algorithm produces a feasible solution for the dual problem by covering the dual problem constraint in (\ref{ConstDcover}) through setting $\alpha _i$ to $\frac{v_i}{D_i}$ when EV $i$ is accepted and, $\beta (t)$ to a value greater than or equal to $\frac{v_i}{D_i}$ for $t\in [a_i, d_i]$ (according to the discussion in Section \ref{sec:icsexplanation}) if EV $i$ is not selected.
-To obtain an approximation factor for the algorithm, it is enough to bound the total covering cost of the dual constraints.
-
-		\begin{thm}
-			\label{thm:approx}
-			\ics algorithm is a $\Big( 1+ \sum_{j=1}^m {\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}\Big)$-approximation when EVs have same arrival time.
-		\end{thm}
-%		
-%		\begin{proof}
-%			In Appendix~\ref{app:1}.
-%		\end{proof}
-
-		Note that in the case that the system is flexible enough, i.e., $s\gg 1$, and the maximum charging rates of stations are much bigger than those of EVs, i.e., $p_j \gg q_j, \forall j$, the approximation ratio approaches $m+1$.
-And in the case that there is one single station, the approximation ratio is $2$.
-%		 Finally, we provide the time complexity of the \ics.
-
-%\begin{thm}
-%\label{thm:ics_complexity}
-%The time complexity of the \ics algorithm is $O(nT\log T+n^2T)$.
-%\end{thm}	
-%
-%\begin{proof}
-%In Appendix \ref{app:ics_complexity}.
-%\end{proof}
-
-\subsection{Online Scenario}
-\label{sec:onlineint}
-Due to the binary selection variable, the online solution design under integral model is more challenging than the one for fractional model.
-We propose the \iocs that is built upon the offline \ics.
-In particular, the \iocs calls the \ics at each time slot for the set of available EVs, however, any algorithm that is designed for offline integral model can be used alternatively.
-Hereinafter, $\mathcal{A}$ refers to the \ics or a similar algorithm.
-
-\begin{algorithm}%\small%1
-\footnotesize
-\caption{\iocs: $\forall t\in \{1,2,\dots ,T\}$}
-\label{alg:iocs}
-\DontPrintSemicolon 
-%\KwIn{$n$ EVs to arrive on the fly, number of CSs $m$, global peak constraint $p^{\textrm{total}}$, local peak constraints $p_j, j=1,\dots ,m$}
-
-%\KwOut{A feasible charging scheduling}
-
-\BlankLine
-
-Let $\mathcal{A}$ be an algorithm that solves the problem with $a_1=\dots =a_n$
-
-$\mathcal{R}^t\leftarrow$ set of EVs arrived at time slot $t$
-
-$\mathcal{M}^t\leftarrow \mathcal{R}^t\cup \{i: t\in\mathcal{T}_i\ \texttt{AND}\ \sum_{t^\prime}y_{i}^{t'}<D_i\}$
-
-%$\backslash\backslash\texttt{Schedule 1}$
-
-Based on the residual in interval $[t,T]$, use algorithm $\mathcal{A}$ to allocate EVs in set $\mathcal{R}^t$ assuming no further arrivals
-
-$\mathcal{S}_{\iocs,t}\leftarrow\{i:i\in\mathcal{M}^t\ \texttt{AND}\ i$ is admitted at $t\}$
-
-$\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}\leftarrow \sum_{i\in\mathcal{S}_{\iocs,t}}v_i$
-
-Assume all reserved resources are freed at time slots $t, t+1, \dots, T$
-
-%$\mathcal{R}^t\leftarrow\mathcal{M}^t$
-
-%$\backslash\backslash\textsl{set of active EVs at time slot t}$
-
-$r_{i,t}\leftarrow$ remaining demand of $i$ at $t, \forall i$
-
-%$\backslash\backslash\texttt{Use modified demands values}$
-
-$D_i^\prime\leftarrow r_{i,t},\ \ v_i^\prime\leftarrow \frac{r_{i,t}}{D_i}v_i, \forall i\in\mathcal{M}^t$
-
-%$\backslash\backslash\texttt{Schedule 2}$
-
-Run $\mathcal{A}$ on $\mathcal{M}^t$ using $D_i^\prime$ and $v_i^\prime, \forall i$ and reconstruct $\mathcal{S}_{\iocs,t}$
-
-$\Gamma_{\mathcal{A},\mathcal{M}^t}\leftarrow \sum_{i\in\mathcal{S}_{\iocs,t}}v_i$ $\backslash\backslash\texttt{Use original values}$
-
-%$a\leftarrow\frac{V^\prime_{\textrm{total}}}{V_{\textrm{total}}}$
-
-\If{$\Gamma_{\mathcal{A},\mathcal{M}^t}>\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$}{
-
-Use the second schedule
-
-}
-
-\Else{
-
-Use the first schedule
-
-}
-
-\end{algorithm}
-
-The \iocs is summarized as Algorithm~\ref{alg:iocs}.
-At slot $t$, the \iocs compares two scheduling results returned by $\mathcal{A}$ and chooses among them.
-In the first scheduling, the \iocs keeps all reserved resources in interval $[t,T]$ intact.
-Then, for utilizing the remaining resources, the algorithm runs $\mathcal{A}$ over arrived EVs at time slot $t$.
-In this case, the total revenue obtained by the \emph{active} EVs (i.e., EVs that are available but not received their entire demand yet) is denoted by $\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$ (Line $6$ of the algorithm).
-In the second scheduling, the \iocs considers the case that it can sacrifice the previously admitted EVs by canceling their reservations and allocating the freed resources to more valuable demands.
-For this purpose, the algorithm modifies the demand and valuation of the previously admitted EVs such that each demand is replaced by the EV's remaining demand, and the valuation of the EV is proportionally calculated based on the remaining demand (Line $9$ of the algorithm) so that the unit values of EVs do not change.
-Then, the \iocs runs $\mathcal{A}$ over set of active EVs $\mathcal{M}^t$ where the corresponding gain is denoted by $\Gamma_{\mathcal{A},\mathcal{M}^t}$.
-If $\Gamma_{\mathcal{A},\mathcal{M}^t}>\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$, the \iocs forgets the previously admitted EVs and follows the second scheduling.
-
-\begin{comment}
-%We now introduce some notations and then analyze the performance of \iocs. 
-Let $\mathcal{S}_{\iocs,t}$ and $\mathcal{S}_{\opt,t}$ be set of active EVs at time slot $t$ that are selected for charging by \iocs and \opt (fix a particular optimal solution), respectively.
-Note that the set of active EVs for \iocs and \opt might be different.
-%Moreover, define  $\mathcal{U}_{\iocs,t}=\mathcal{S}_{\iocs,1}\cup\dots\cup \mathcal{S}_{\iocs,t}$ and $\mathcal{U}_{\opt,t}=\mathcal{S}_{\opt,1}\cup\dots\cup \mathcal{S}_{\opt,t}$. 
-Having $i\in\mathcal{S}_{\iocs,t}$ means that based on the updated schedule at time slot $t$, enough resources reserved for EV $i$ so that the EV will receive its demand $D_i$ before the deadline $d_i$.
-However, the schedule may change at each slot and $i\in\mathcal{S}_{\iocs,t}$ cannot be a guarantee for EV $i$ to fully receive its demand.
-In fact, users and the scheduler itself have to wait until the deadline of the EV to find out that the demand is fulfilled or not.
-This is because the scheduler may cancel some reservations in the next time slots and allocate the freed resources to other EVs.
-\end{comment}
-% (when Algorithm \ref{alg:iocs} uses the second schedule in Line $15$). 
-%Define $A_t$ as the minimum gain of \iocs when the algorithm visited time slots $1$ to $t$.
-More formally, $A_t=\sum_{i\in\mathcal{U}_{\iocs,t}}v_i$.
-$A_t$ is the minimum gain that \iocs will obtain by the end of time slot $t$, having the information of released demands up to time slot $t$.
-Notice that the algorithm may continuously improve its set of selected jobs to increase its gain such that $A_t\geq A_{t-1}, t\in\{2,\dots, T\}$.
-$A_t$ is formally defined as follows:
-
-The following theorem characterizes the competitive ratio of the \iocs in a special case. 
-\begin{thm}
-\label{thm:iocscompetitive}
-Let $\mathcal{A}$ be \ics in \iocs algorithm and $m=1$.
-Assuming that EVs are released in $b$ distinct groups where arrival time of EVs in each group are the same, the \iocs is $b\Big(1+\frac{p}{p-q}\frac{s}{s-1}\Big)$-competitive with optimal offline solution, where $p$ is the station peak and $q=\max_i k_i, i=1,\dots ,n$.
-\end{thm}
-
-%\begin{thm}
-%\label{thm:iocscomplexity}
-%Let $\mathcal{A}$ be \ics in Line $1$ of \iocs. Then, the time complexity of the \iocs  is $O(n^2T)$. 
-%\end{thm}
-
-%\vspace{-6mm}
-\section{Simulation Results}
-			\label{sec:simul}
-%%%In this section, we report a summary of simulation experiments to evaluate the performance of the proposed algorithms.
-
-						\begin{figure*}[t]	
-				\centering
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{V-N-M2.pdf}
-						\caption{\revv{$m=2$}}
-						\label{fig:V-N-M2}
-					\end{center}
-				\end{subfigure}
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{V-N-M4.pdf}
-						\caption{\revv{$m=4$}}
-						\label{fig:V-N-M4}
-					\end{center}
-				\end{subfigure}% 	
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{V-N-M8.pdf}
-						\caption{\revv{$m=8$}}
-						\label{fig:V-N-M8}
-					\end{center}
-				\end{subfigure}% 
-				\caption{\revv{Comparison results for $2$, $4$, and $8$ CSs for fractional and integral revenue models.}} 
-				\label{fig:V-N-M}
-%				\vspace{-3mm}
-			\end{figure*}
-%\subsection{Simulation Setup and Overview}
-\textit{Simulation Setup and Overview:} We consider charging scheduling of EVs \revv{during a period of $12$ time slots of length $1$ hour (e.g., from $08$:$00$ to $20$:$00$)}. 
-We gathered information of \revv{$12$} popular EV models in the market to use in the simulation.
-Each EV model is characterized by its battery capacity as shown in Table \ref{tb:models} and maximum charging rate.
-\revv{Tesla models can get charged with up to $100$ kW using Tesla super chargers.
-Also, all other models have rapid DC charging capability (up to $50$ kW) with CHAdeMO method.
-This setting for charging rates is in accordance with future DCFC systems that can have several fast DC chargers installed in the charging station.}
-%Battery capacity varies from \revv{$14$} kWh to \revv{$100$} kWh and the maximum charging rate from \revv{$3.3$} kW to \revv{$22$} kW. 
-%As in \cite{Tang,Chen}, we assume that arrival times follow a Poisson distribution and parking times follow an exponential distribution.
-% with the mean arrival and parking duration indicated in Table \ref{tb:a-d}. 
-The peak intervals include $08$:$00$-$10$:$00$, $12$:$00$-$14$:$00$, and $18$:$00$-$20$:$00$ which is in accordance to NHTS survey~\cite{Santos, Tang}.
-\revv{The probability of arriving an EV in the peak hours is two times higher than the off-peak periods.
-			Demands are uniform random values from 
-			$[\frac{1}{2}U_i,U_i]$} where $U_i$ is the battery capacity for EV $i$ in Table~\ref{tb:models}.
-\revv{The deadline of each EV is set according to slackness parameter $s$ (with default value of $1.2$), its demand and maximum charging rate of the battery as $d_i=a_i+\lceil \frac{D_is}{k_i} \rceil -1$.}
-%			The minimum electricity cost is $\$0.11$ per kWh based on US national electricity price average~\cite{kWhcost}.
-In our setting, users can submit higher prices than the minimum price in order to ensure receive their requested demand.
-			\revv{EVs are assigned to different CSs randomly and given as input to the algorithms.
-The willingness to pay by each user for one kWh of power is a random uniform number from interval $[\frac{1}{2} z,\frac{3}{2}z]$ where $z=\$0.11$ is national average price of electricity in the US\cite{kWhcost}.}
-			%The default value of local peak constraint is \rev{$100$} kW and the global peak constraint is \rev{$200$} kW. We investigate the effect of this parameter in~\cite{alinia2017online}. 
-			In the simulation, the results are plotted with $95\%$ confidence level and each point represents average result of $50$ random scenarios.
-Table \ref{tb:comparisons} explains the comparison algorithms \revv{including current implemented algorithm in Caltech ACN referred to as \iolp \cite{lee2016adaptive} and its adapted version for the fractional revenue model \folp.
-The \iolp and \folp algorithms runs as follows: at each time slot assume that there will be no further arrivals and solve the optimization problem (e.g., by commercial solvers) for the current set of EVs and their remaining demands.
-In Table \ref{tb:comparisons}, the letters ``\textsc{i}'', ``\textsc{f}'' and ``\textsc{o}'' in front of the algorithms' name refer to integral, fractional and online types, respectively.}
-
-			The measured performance metrics are total revenue, percentage of EVs that received all their demand, and total peak.
-\revv{To calculate optimal solution in integral revenue model, we used Gurobi solver \cite{optimization2013gurobi}.}
-
-\begin{table}[!t]
-				\centering
-				\caption{\revv{EV models and their battery capacity.}}
-				\label{tb:models}\revv{
-				\begin{tabular}{ | l| c | l| c |}
-					\hline
-					\textbf{Model} & \textbf{Battery} & \textbf{Model} & \textbf{Battery} \\ \hline\hline    
-				Mitsubishi i-MiEV & $16$ kWh & Citroen C-Zero & $14$ kWh \\ \hline
-				Peugeot iOn  & $16$ kWh & Honda Clarity & $25.5$ kWh\\\hline
-				Hyundai Kona & $64$ kWh & Nissan LEAF & $40$ kWh \\ \hline
-				Hyundai Ioniq & $28$ kWh & BMW i3 & $22/33$ kWh \\ \hline
-				Tesla Model S/X  & $60/100$ kWh & Kia Soul EV  & $27$ kWh\\\hline
-				\end{tabular}}
-			\end{table}
-
-%\begin{table}[h]
-%				\centering
-%				\caption{Arrival rates and mean parking times.}
-%				\label{tb:a-d}
-%				\begin{tabular}{ | l | c | c |}
-%					\hline
-%					\textbf{Interval} & \textbf{Arrival rate} & \textbf{Mean parking time} \\ \hline\hline    
-%					$08$:$00$-$10$:$00$&  $14$&$10$\\\hline  
-%					$10$:$00$-$12$:$00$&  $10$&$1/2$\\\hline 
-%					$12$:$00$-$14$:$00$&  $20$&$2$\\\hline 
-%					$14$:$00$-$18$:$00$&  $10$&$1/2$\\\hline
-%					$18$:$00$-$20$:$00$&  $20$&$2$\\\hline
-%					$20$:$00$-$24$:$00$&  $10$&$10$\\\hline
-%					$24$:$00$-$08$:$00$&  $0$&$0$\\\hline
-%				\end{tabular}
-%\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{Acronyms for the algorithms}
-\label{tb:comparisons}
-\begin{tabular}{ | l| p{6cm}|}
-\hline
-\textbf{Notation} & \textbf{Description} \\ \hline\hline
-\textsc{iOpt} & Optimal value under integral revenue model\\ \hline 	 
-\ics & Proposed offline algorithm for \MCSP under integral revenue model\\ \hline
-\fcs & Proposed \emph{optimal} algorithm for \MCSP under fractional revenue model\\\hline 
-\iocs & Proposed online algorithm for \MCSP under integral revenue model\\ \hline
-\focs & Proposed online algorithm for \MCSP under fractional revenue model\\ \hline
-\iolp & Algorithm in \cite{lee2016adaptive} (works under integral revenue model)\\ \hline
-\folp & Adaptation of algorithm in \cite{lee2016adaptive} for fractional revenue model\\ \hline
-GreedyRTL & The algorithm in \cite{Jain} for single station scenario without global peak 			constraint (works under integral revenue model)\\\hline				
-\end{tabular}
-\end{table}
-			%to simulate: Fig. 1 with M=1,4,8			
-			\begin{figure*}[t!]	
-				\centering
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{v-c.pdf}
-						\caption{\revv{Total revenue}}
-						\label{fig:v-c}
-					\end{center}
-				\end{subfigure}%
-				%\hspace{4mm}
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{p-c.pdf}
-						\caption{\revv{Actual global peak} 
-%							($p^{\mathsf{total}}=480$)
-}
-						\label{fig:p-c}
-					\end{center}
-				\end{subfigure}%  
-				%\hspace{4mm}
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{acc-c.pdf}
-						\caption{\revv{\% of full charged EVs}}
-						\label{fig:acc-c}
-					\end{center}
-				\end{subfigure}% 				
-				\caption{\revv{Comparison in terms of total revenue, actual peak, and percentage of fully charged EVs by varying local peak value}.} 
-				\label{fig:peak_local}
-%			\vspace{-4mm}
-			\end{figure*}
-\textit{\revv{Evaluation Based on Total Revenue}:}
-\revv{Fig.
-\ref{fig:V-N-M} depicts the comparison results based on total revenue under fractional and integral models} while the total number of EVs increases from \revv{$100$ to $250$} for $2$, $4$, and $8$ CSs.
-\revv{The local and global peak constraints are set to $50$ kWh and $200$ kWh, respectively.}
-
-The proposed algorithms compared to the optimal offline solution of integral model ($\textsc{iOPT}$) and $\iolp$.
-\bt{Note that comparison with offline optimal could be considered as a baseline comparison with the category of approximate offline algorithms in integral model~\cite{yao2016real}.}
-
-%%% which is the running online algorithm in the Caltech ACN \cite{lee2016adaptive}. 
-%The proposed algorithms for fractional revenue model, \fcs and \focs, are compared to fractional version of OLP algorithm (referred to as \folp), which is implemented in Caltech ACN  (see~\cite{alinia2017online} for details).
-Recall that \fcs is optimal offline solution.
-The notable observations  are  as  follows:  (i)  the  general  trend in scenario of Fig.~\ref{fig:V-N-M} is that  by increasing  the  number  of  EVs,  total  revenue  increases.
-This is because with more number of EVs, the scheduler has more freedom to choose more valuable EVs.
-(ii)  as  explained in Section~\ref{sec:fractional}, under fractional charging model, better results are expected due to increased scheduling flexibility in CSs.
-According to the simulation data that we extracted from Fig.~\ref{fig:V-N-M}, the gain obtained by \fcs and \focs in Fig.
-\ref{fig:V-N-M} are respectively \revv{$12\%$ and $10\%$} more than the gain of the \ics and \iocs.
-(iii) \revv{In Fig.
-\ref{fig:V-N-M2} and Fig.
-\ref{fig:V-N-M4}, sum of the local peaks is less than or equal to the global peak while in Fig.
-\ref{fig:V-N-M8} this sum is two times greater than the global peak.
-Consequently, the total revenue significantly improved when the number of CSs is increased from $2$ to $4$ while there is a slight improvement from $4$ to $8$ CSs as the global peak constraint prevents the algorithms from charging more EVs.}
- (iv) in integral revenue model, the proposed \iocs algorithm acts significantly better than \iolp.
-In particular, \iocs improves \iolp by \revv{$38\%, 36\%$, and $32\%$} for $m=2$, $m=4$ and $m=8$, respectively.
-\revv{In fractional revenue model, however, there is a very slight difference between \focs and \folp.}
- %We highlight that \iocs (\focs) is also better choice in terms of the algorithm complexity compared to \iolp (\folp).
-(v) \ics approximates \textsc{iOpt} by \revv{$97\%$, $94\%$, and $95\%$} for $m=2$, $m=4$, and $m=8$, respectively.
-On average, \iocs is \revv{$90\%$} of \textsc{iOpt} and, \focs is \revv{$94\%$} of its optimal offline solution, \fcs.
-(vi) finally, the results depict that \ics achieves much better results in practice as compared to the theoretical approximation ratio that characterizes the performance in worst-case scenario.
-
-%Also, there is a sharp decline in the gap between the online methods (i.e., \focs and \iocs) and the offline solutions (i.e., \textsc{iOpt}, \ics and \fcs).
-
-\revv{\emph{Comparison Based on Actual Peak:}} The constraint set in the \MCSP assures that any feasible solution respects the local and global peak constraints.
-% i.e., at each time slot, the electricity consumed by station $j$ is less than or equal to $p_j$ and accumulative charging rate of all stations are less than or equal to $p^\mathsf{total}$ (note that there is no assumption that $\sum_j p_j\leq p^\mathsf{total}$, in general).
-An efficient scheduling algorithm may take a further step by not only satisfying the peak constraints but to further reduce the peak as much as possible.
-The proposed offline algorithms (i.e., \ics and \fcs) apply valley-filling policy to reduce the peak.
-The  online algorithms (i.e., \iocs and \focs) do not apply the same policy as they do not have future knowledge to be able to balance allocated resources.
-%Besides, due to uncertainties in future EV charging load in online scheduling design, it is a natural heuristic to charge EVs at earliest time.
-% (i.e., setting the charging rates to the maximum feasible value at each time slot) as applied by \iocs an \focs. 
-%This heuristic works well as the uncertainty in EVs' arrival time and demands may not give a second opportunity to the scheduler to charge the current EVs at the next slots.
-Therefore, although it is expected that \iocs and \focs have higher peak values compared to the offline algorithms, the idea of valley-filling can decrease their average response time.
-% (see~\cite{alinia2017online} for the extended version of experiments).
-To investigate the effect of employed valley-filling strategy, we conducted a set of simulations by varying local peak constraints. 
-%from $50$ kWh to $120$ kWh and $200$ EVs. 
-The results of \ics is compared to \iocs and GreedyRTL~\cite{Jain} where the latter is an approximation scheduling for single station scenario with EVs having same arrival time (see the explanations after formulating the \MCSP in Section \ref{sec:problem}).
-%The GreedyRTL algorithm works under integral revenue model. Therefore, results for \fcs and \focs are not plotted. 
-%Since GreedyRTL assumes all EVs arrive at the same time, we set all arrival times to $1$.
-Moreover, we assume that global peak constraint is big enough (i.e., $\sum_{j=1}^m p_j\leq p^\textsf{total}$) such that the solution of GreedyRTL is feasible.
-We run GreedyRTL in each CS separately and combine the results.
-The results are shown in Fig.~\ref{fig:peak_local}.  
-Along with total revenue in Fig.~\ref{fig:v-c}, we also report total \emph{actual} peak in Fig.~\ref{fig:p-c} and percentage of fully charged EVs in Fig.~\ref{fig:acc-c}. 
-%As a high level trend, the results show that as the peak values increase, total revenue, total actual peak, and the number of EVs who received all their demand increase.  
-In Fig.
-\ref{fig:v-c}, the results for \ics and GreedyRTL are almost identical while \iocs is \revv{$90\%$} of the other two algorithms, on average.
-When \revv{$p_j\geq 400$}, the total revenue for \ics and GreedyRTL does not increase in Fig.
-\ref{fig:v-c} and percentage of fully charged EVs is $100$ for both algorithms according to Fig.
-\ref{fig:acc-c}.
-From this point and onward, the scheduling is not challenging for offline methods to obtain optimal answer because of resource sufficiency.
-However, it is still a challenge to control total actual peak for the system.
-As a result of valley-filling policy, the value of actual peak of \ics in Fig.
-\ref{fig:p-c} remains almost unchanged for \revv{$p_{j}\geq 400$}.
-\iocs and GreedyRTL, however, continuously increase the peak demand, since they are not using any peak shaving approach.
-% and only try to maximize total revenue. 
-%According to Fig. \ref{fig:p-c}, \iocs always reaches to the maximum peak of $\sum_j p_j$.
-
-%A glance at Table \ref{tb:models} shows that in general, an EV needs a minimum time of $2$ hours to get $70\%$ of its battery capacity if charging rate is set to the maximum value.
-However, CSs are allowed to preempt the charging at any time and set charging rate any value lower than the maximum rate.
-Therefore, average response times can be higher as it can be seen in Fig.
-\ref{fig:rt-c}.
-
-%\begin{figure}[t]	
-%\centering
-%				\begin{subfigure}[b]{0.25\textwidth}
-%					\begin{center}
-%						\includegraphics[width=\textwidth]{v-s-method1.pdf}
-%						\caption{Total revenue (\$)}
-%						\label{fig:v-s-method1}
-%					\end{center}
-%				\end{subfigure}%				
-%				\begin{subfigure}[b]{0.25\textwidth}
-%					\begin{center}
-%						\includegraphics[width=\textwidth]{rt-s-method1.pdf}
-%						\caption{Response time (hr))}
-%						\label{fig:rt-s-method1}
-%					\end{center}
-%				\end{subfigure}%  
-%\caption{The impact of slackness parameter on total revenue and response time when users react by adjusting their demand.} 
-%\label{fig:slackness1}
-%\end{figure}
-
-%\subsection{The Impact of Slackness Parameter}
-%\label{sec:sim:slack}
-%This section discusses on the benefits and disadvantages that can be brought by using slackness parameter.
-To give the charging scheduler more flexibility, a slackness parameter $s\geq 1$ is used and set by the system designer.
-%Recall that charging profile of EV $i$ is feasible if $D_i\leq k_i\frac{d_i-a_i+1}{s}$ holds.
-Since users have no control on the slackness parameter and the maximum charging rate, they must adjust their demand and availability according to the imposed slackness value.
-Based on the charging profile feasibility equation, when the slackness value increases users have two choices to react: (i) decrease the demand and depart at the desired deadline or, (ii) extend the deadline and receive the desired demand.
-In the remaining of this section, we investigate the effects of either case by simulation.
-To have a clear picture of effects caused by slackness parameter, we generated $100$ initial charging profiles $\langle a_i,d_i,v_i,D_i,k_i\rangle$ for $100$ EVs randomly and uniformly chosen from $10$ different models in Table \ref{tb:models} such that the initial profiles are set up assuming that the CS allows the charging operations to be finished at earliest possible time (i.e., $\frac{D_i}{k_i}$) with $s=1$.
-For each EV, its demand is randomly chosen from $25\%$ to $100\%$ of its battery capacity and departure in  interval $[a_i+\frac{sD_i}{k_i},T]$, where $a_i+\frac{sD_i}{k_i}$ is the earliest feasible deadline.
-Then, the EVs are uniformly assigned to $4$ CSs and should choose one of the above strategies to submit a feasible demand according to imposed slackness.
-%\begin{figure}[t]	
-%\centering
-%							\begin{subfigure}[b]{0.234\textwidth}
-%								\begin{center}
-%									\includegraphics[width=\textwidth]{v-s-method2.pdf}
-%									\caption{Total revenue (\$)}
-%									\label{fig:v-s-method2}
-%								\end{center}
-%							\end{subfigure}%
-%							\hspace{1mm}
-%							\begin{subfigure}[b]{0.236\textwidth}
-%								\begin{center}
-%									\includegraphics[width=\textwidth]{rt-s-method2.pdf}
-%									\caption{Response time (hr)}
-%									\label{fig:rt-s-method2}
-%								\end{center}
-%							\end{subfigure}% 
-%							
-%\caption{The impact of slackness parameter on total revenue and response time when users react by adjusting their deadline.} 
-%\label{fig:slackness2}
-%\end{figure}
-%			
-%\subsubsection{Case I- Adjusting Demands}
-%In this case, if the initial charging profile of an EV does not reflect a feasible charging request based on the slackness parameter, the EV owner decreases its demand so it will be able to leave CS at its initial desired deadline.
-Note that the valuation of EVs decreases proportionally, as well.
-Fig.~\ref{fig:slackness1} depicts the result under this policy applied by users.
-As it can be seen in Fig.
-\ref{fig:v-s-method1} and Fig.
-\ref{fig:rt-s-method1}, the general trend is that both total revenue and average response time decrease when slackness value increases.
-This is justifiable based on users reaction.
-When users decrease their demand, less electricity is sold which results in less revenue.
-When total demand decreases, charging can be finished in shorter time which decreases response time.
-Therefore, if users choose the first policy (adjusting their demand), total revenue degrades while response time improves.
-Notice that for the algorithms working under integral revenue model (i.e., \textsc{iOPT}, \ics and \iocs) the total revenue increases with slackness parameter at first (when $s$ grows from $1$ to $1.4$) but then it decreases when the slackness increases more (for $s>1.4$).
-%In our view, this happens because increasing the slackness in integral revenue model makes it possible to \emph{fully} charge more EVs at the beginning as the demands decrease.
-However, when the slackness increases more, it results in opposite effect because the valuation of demands decreases along with the demands' size.
-%			\subsubsection{Case II- Adjusting Deadlines}
-%			In this case, we assume that users are reluctant to decrease their desired demands.
-Instead, they can extend their departure.
-In Fig.~\ref{fig:slackness2} it can be observed that under this behavior of the users, the results are opposite as compared to the previous case (Fig.~\ref{fig:slackness1}).
-When deadlines are extended without demand decrement, the scheduler has more chance to compliance the demands through improved scheduling flexibility.
-Consequently, the total revenue increases by increasing slackness value while average response time degrades.
-%%Also observe the behavior of the online algorithms (i.e., \iocs and \focs) where both total revenue and response time decrease after a specific point that is $s=1.8$.
-When deadlines extend, more EVs have the opportunity of getting charged
-%					
-%We can conclude that when total revenue is more important than the response time, the CS should impose small values of slackness for users that apply the policy of the first case and impose higher values of slackness for the users that apply the second policy.
-The conclusion is reverse for the case that the objective is to have lower response times.
-
-			%In fact, the slackness parameter controls the maximum demand or earliest deadline that an EV can submit to the system.
-Remember that demands are in interval $[\textrm{min}\{\frac{d_i-a_i}{sk_i},U_i\},U_i]$ for EV $i$ meaning that the maximum demand that an EV can submit decreases by increasing slackness parameter.
-A reduction in total demand result in lower charging costs.
-Therefore, the total revenue decreases with higher values of parameter $s$ as in Fig.
-\ref{fig:v-s}.
-			%Also, the percentage of EVs that received all of their requested demand increases based on the same fact.
-The main goal of this simulation is to observe that obtained theoretical result on approximation ratio is confirmed as optimality gap of the SCS algorithm reduces by increasing $s$ in Fig.
-\ref{fig:v-s}.
-%\vspace{0.1mm}
-%\vspace{-4mm}
 \section{Conclusion}
@@
 %\pagestyle{empty}
-\bibliography{ref}{}
-%\vspace{-2.8mm}
-\bibliographystyle{ieeetr}
-
-\input{app.tex}
-
-\begin{comment}
-\vspace{-10mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{alinia.jpg}}]{Bahram Alinia} received a B.Sc degree in computer science from University of Tabriz, Tabriz, Iran and a masters degree in Information Technology Engineering from University of Tehran, Tehran, Iran.
-He was a Researcher with the School of Computer Science, Institute for Research in Fundamental Sciences, Iran, from 2009 to 2012.
-He is currently a Ph.D.
-student in service architecture lab, Institute Telecom SudParis, France and participated in several European projects in the domain of smart grids.
-His research area includes wireless communications, energy systems, transportation electrification, algorithm design and approximation.
-\end{IEEEbiography}
-%\vspace{-30mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{hajiesmaili.jpg}}]{Mohammad H.
-Hajiesmaili} received the B.Sc.
-degree from the Department of Computer Engineering, Sharif University of Technology, Iran, in 2007, and the M.Sc.
-and Ph.D.
-degrees from the Electrical and Computer Engineering Department, University of Tehran, Iran, in 2009 and 2014, respectively.
-He was a Post-Doctoral Fellow with the Department of Information Engineering, the Chinese University of Hong Kong, from 2014 to 2016, and with the Department of Electrical and Computer Engineering, Johns Hopkins University, form 2017 to 2018.
-He is currently a Research Assistant Professor with the College of Information and Computer Sciences, University of Massachusetts, Amherst.
-His research interests include optimization, algorithm, and mechanism design in energy systems, electricity market, transportation networks, and multimedia networks.
-\end{IEEEbiography}
-%\vspace{-30mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{crespi.jpg}}]{Prof.
-No\"{e}l Crespi} holds Masters degrees from the Universities of Orsay (Paris 11) and Kent (UK), a diplome d'ing\'{e}nieur from Telecom ParisTech, a Ph.D and an Habilitation from UPMC (Paris-Sorbonne University).
-From 1993 he worked at CLIP, Bouygues Telecom and then at Orange Labs in 1995.
-He took leading roles in the creation of new services with the successful conception and launch of Orange prepaid service, and in standardisation (from rapporteurship of IN standard to coordination of all mobile standards activities for Orange).
-In 1999, he joined Nortel Networks as telephony program manager, architecting core network products for EMEA region.
-He joined Institut Mines-Telecom in 2002 and is currently professor and Program Director, leading the Service Architecture Lab.
-He coordinates the standardisation activities for Institut Mines-Telecom at ITU-T and ETSI.
-He is also an adjunct professor at KAIST (South Korea), an affiliate professor at Concordia University (Canada), and gest researcher at the University of Goettingen (Germany).
-He is the scientific director the French-Korean laboratory ILLUMINE.
-His current research interests are in Data Analytics, Internet of Things and Softwarisation.
-http://noelcrespi.wp.tem-tsp.eu/
-\end{IEEEbiography}	
-\end{comment}
-\end{document}

### 2025-03-09 TSUSC/fractional.tex
move resources from other repos

--- 2019-08-28 TSC/R1/TSC.tex
@@
-\documentclass[journal]{IEEEtran}
-%\usepackage{float}
-\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-\usepackage{amssymb,amsmath}
-\usepackage[font=small,skip=10pt]{caption}
-\usepackage{subcaption}
-\usepackage{comment}
-\usepackage{color,soul}
-%\usepackage{ragged2e} 
-\usepackage{algorithmicx}
-\usepackage{algpseudocode}
-\usepackage{amsthm}
-\usepackage{cite}
-\usepackage{array}
-%\usepackage{nopageno}
-\usepackage{url}
-%\usepackage{hyperref}
-%\usepackage{ulem}
-
-% *** CITATION PACKAGES ***
-%
-\usepackage{cite}
-\usepackage{color}
-\usepackage{xspace}
-\usepackage{multirow}
-\usepackage{hhline}
-%\usepackage[pdftex]{graphicx}
-
-% *** GRAPHICS RELATED PACKAGES1 ***
-%
-
-% more space
-%\usepackage{txfonts}
-\addtolength{\abovedisplayskip}{-2mm}
-\addtolength{\belowdisplayskip}{-2mm}
-\addtolength{\parskip}{-.15mm}
-%\addtolength{\arraycolsep}{-.75mm}
-\addtolength{\abovecaptionskip}{-1mm}
-\addtolength{\belowcaptionskip}{-1mm}
-%\renewcommand{\baselinestretch}{0.9}
-
-\ifCLASSINFOpdf
-\usepackage[pdftex]{graphicx}
-\graphicspath{{fig/}{../}}
-\DeclareGraphicsExtensions{.pdf,.jpeg,.png,.jpg}
-\else
-\usepackage[dvips]{graphicx}
-\graphicspath{{fig/}{../}}
-\DeclareGraphicsExtensions{.eps}
-\fi
-
-%\usepackage[caption=false,font=footnotesize]{subfig}
-%
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-%\setlength{\intextsep}{-1ex} % remove extra space above and below in-line float
-
-\renewcommand{\baselinestretch}{1}
-
-\ifodd 1
-\newcommand{\bt}[1]{{\color{blue}#1}}%revise of the text
-\newcommand{\rev}[1]{{\color{black}#1}}%revise of the text
-\newcommand{\revv}[1]{{\color{black}#1}}%revise of the text
-\newcommand{\com}[1]{\textbf{\color{red}(COMMENT: #1)}}%comment of the text
-\else
-\newcommand{\bt}[1]{#1}
-\newcommand{\rev}[1]{#1}
-\newcommand{\com}[1]{}
-\fi
-
-\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-
-%\newcommand{\opt}{\textsc{OPT}\xspace}
-\newcommand{\sa}{\textsc{SmartAllocate}}
-\newcommand{\rc}{\textsc{ReConsider}}
-\newcommand{\bc}{\textsc{BetaCover}}
-\newcommand{\ics}{\textsc{iCS}\xspace}
-\newcommand{\fcs}{\textsc{fCS}\xspace}
-\newcommand{\MCSP}{\textsf{SPAN}\xspace}
-\newcommand{\dMCSP}{\textsf{dSPAN}\xspace}
-\newcommand{\focs}{\textsc{foCS}\xspace}
-\newcommand{\iocs}{\textsc{ioCS}\xspace}
-\newcommand{\finalalg}{\textsc{ioCS+}\xspace}
-\newcommand{\opt}{\textsc{OPT}\xspace}
-\newcommand{\alg}{\textsc{ALG}\xspace}
-\newcommand{\rtl}{\textsc{GreedyRTL}\xspace}
-\newcommand{\iolp}{\textsc{ioLP}\xspace}
-\newcommand{\folp}{\textsc{foLP}\xspace}
-
-\newcommand{\be}{\begin{equation}}
-	\newcommand{\ee}{\end{equation}}
-\newcommand{\bee}{\begin{eqnarray}}
-	\newcommand{\eee}{\end{eqnarray}}
-\newcommand{\bse}{\begin{subequations}}
-	\newcommand{\ese}{\end{subequations}}
-%\def\bee#1\eee{\begin{align}#1\end{align}}
-\newcommand{\nnb}{\nonumber}
-
-\newtheorem{lem}{Lemma}
-\newtheorem{propos}{Proposition}
-\newtheorem{thm}{Theorem}
-\newtheorem{defi}{Definition}
-
-%in terms of practical feasibility and characterizing the maximum benefits of D2D load balancing is
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{corollary}[theorem]{Corollary}
-
-\makeatletter
-\newcommand\semiHuge{\@setfontsize\semiHuge{22.52}{27.38}}
-\makeatother
-\begin{document}
-	%\semiHuge
-	\title{Online EV Scheduling Algorithms for Adaptive Charging Networks with Global Peak Constraints}
-	\author{\#}
-
-	\author{Bahram Alinia, Mohammad H. Hajiesmaili, Zachary J. Lee, Noel Crespi, and Enrique Mallada
-
-		\thanks{ B. Alinia and N. Crespi are with the department of Networks and Mobile Multimedia Services (RS2M), Institut Mines-Telecom,
-			Telecom SudParis, Evry, France (e-mail: bahram.alinia@telecom-sudparis.eu, noel.crespi@mines-telecom.fr).
-
-			M. H. Hajiesmaili and E. Mallada are with the Department of Electrical and Computer Engineering, Johns Hopkins University, Baltimore, MD, USA (e-mail: \{hajiesmaili,mallada\}@jhu.edu).
-
-			Z. J. Lee is with the Department of Electrical Engineering, California Institute of Technology, Pasadena, CA, USA (e-mail: zlee@caltech.edu).
-		} }
-
-		\maketitle
-
-\begin{abstract}
-%			With the rapid growth of electric vehicles, their high demand charging jobs pose an immense challenge to the grid infrastructure. 
-			This paper tackles online scheduling of electric vehicles (EVs) in an adaptive charging network (ACN) with local and global peak constraints.
-Given the aggregate charging demand of the EVs and the peak constraints of the ACN, it might be infeasible to fully charge all the EVs according to their charging demand.
-Two alternatives in such resource-limited scenarios are to maximize the social welfare by partially charging the EVs (fractional model) or selecting a subset of  EVs and fully charge them (integral model).
-%			This paper tackles both fractional and integral models. 
-			The critical challenge is the need for online solution design since in practical scenario\revv{s} the scheduler has no information of future arrivals of EVs in a time-coupled underlying problem. 
-			For the fractional model, we devise both offline and online algorithms.
-We prove that the offline algorithm is optimal.
-Using competitive ratio as the performance measure, we prove the online algorithm achieves a competitive ratio of 2.
-The integral model, however, is more challenging since the underlying problem is \bt{strongly} NP-hard due to 0/1 selection criteria of EVs.
-Hence, efficient solution design is challenging even in offline setting.
-We devise a low-complexity primal-dual scheduling algorithm that achieves a bounded approximation ratio.
-Built upon the offline approximate algorithm, we propose an online algorithm and analyze its competitive ratio in special cases.
-Extensive trace-driven experimental results show that the performance of the proposed online algorithms is close to the offline optimum, and outperform the existing solutions.
-%			\rev{In particular, the grid and electricity providers should be aware of the electricity peak.	It is known in electricity market that the spot price is a dominating factor in billing cost.
-Hence, the utility companies need to identify a global peak constraint for the cost management purpose.
-This paper studies the online EV charging scheduling problem in a utility that offers EV charging service in a set of CSs, each of which having limited output power (referred to as local peak constraint) while taking into account the global peak constraint.
-The scheduling problem in this scenario comes with unique challenges that is not tackled previously.}
-
-%			\rev{The problem objective is to maximize total revenue of the CSs.}
-
-\end{abstract}
-		\begin{IEEEkeywords}
-			Electric Vehicle, Online Scheduling, Approximation Algorithm, Competitive Analysis
-		\end{IEEEkeywords}
-
-		\section{Introduction}
-\label{sec:intro}	
-%		\IEEEPARstart{A}{s} 
-%		a result of global warming and environmental concerns through dependence on fossil fuels, there has been a rapid proliferation in deploying renewable energy sources. 
-\IEEEPARstart{T}{o} promote quick adoption of renewable energy sources, electrification of vehicles is a trend that has been globally advocated in recent years.
-\rev{According to a Bloomberg report, EVs will account for more than half of the new car sales by $2040$~\cite{bloomberg}.
-	%the global sale of EVs increased by $80\%$ in $2015$~\cite{EVSales}.
-	%		With the significant advantage of electric vehicles (EVs) in being an environment friendly product, the global interest for EVs is rapidly growing, such that  
-	Consequently, it is expected that demand from EV charging will constitute a considerable portion of total demand. 
-	Currently, transportation consumes $29\%$ of total energy in the US, while electricity production consumes $40\%$~\cite{Zhao}.} 
-%Vehicles seen accounting for 5\% of electricity use by $2040$~\cite{EVSales2}}
-%%%\revv{\sout{Hence, rapid electrification of the vehicles makes the total electricity demand of EVs significant.}}
-
-\revv{EV charging demand is a typical example of a deferrable load, and there is often considerable flexibility in the charging schedule.
-This property makes the problem of EV charging scheduling  important and there is an extensive research along this direction in the literature (see the recent survey~\cite{mukherjee2015review}, and references therein).
-In most of the existing works, the EV charging demand is treated as a constraint to the problem in a low-load regime~\cite{Tang}.
-Motivated by rapid proliferation of EVs, this work tackles the EV scheduling in high-load regime, where given the aggregate charging demand of the EVs and the peak constraints of the charging network, it is not feasible to fully charge all the EVs according to their charging demand.}
-%		\subsection{Microgrid: Definition, Potentials, and Challenges}
-%		\label{sec:introA}
-%		A common trend in the smart grid era is to install renewable energy sources in distributed manner.
-More specifically, medium or large commercial and industrial  customers such as universities, headquarters, etc.,  can take control of their own energy consumption by local deployment of renewable sources~\cite{Hajiesmaili2016Online}.
-In this setting, the residual demand, i.e., total demand subtracted by the local renewable supply, can be acquired from the external grid.
-
-%		In addition to clean energy production, the owner of microgrid also enjoys more power sustainability and reliability, and the ability to proactively manage the energy costs.
-
-More specifically, this paper studies resource-constrained EV charging scheduling in an adaptive charging network (ACN) governed by a single operator in a campus-scale location such as a university, a headquarter\rev{s}, etc.
-\cite{wu2017two}.
-\rev{A notable example is the Caltech ACN~\cite{lee2016adaptive} where individual charging ports are organized into several \textit{charging stations} (CSs) which are dispersed in a \textit{charging network}} with the capability of adaptive charging of the EVs.
-The problem is different from EV charging scheduling \revv{with capacity constraint} in single station scenarios~\cite{Tang,Wen,Shroff2014,WTang,Chen,Xiang,Zhao,Robu} (we refer to~Section~\ref{sec:rel} for detailed discussions on related work), because of the essential need to respect the aggregate peak demand of the ACN.
-\revv{Note that, the ACN operator might limit the total power drawn from EVs to control costs~\cite{PeakPrice,Zhang2015eEnergy}, reserve the capacity for other loads, and/or participate in demand-response programs.}
-%		The EV charging loads are usually flexible and deferrable, which means that their load can be scheduled~\cite{moghaddam2017smart,DWang} to shape the total demand over time. 
-%The aim of this paper is to use the deferrable property of EVs and schedule their charging jobs, so as to \rev{maximize the revenue of the ACN}.	
-%		We refer to Section~\ref{sec:rel} for the literature review.
-
-%		In particular, real-world pricing scheme for large customers is usually a hybrid time-of-use and peak-based charging model where the peak demand can significantly impact the total energy cost, e.g., the peak price is often more than $100$ times higher than the spot price~\cite{PeakPrice,Zhang2015eEnergy}.
-Considering total aggregate demand, the peak charge portion could be as large as $20\%-80\%$ of total cost~\cite{Xu2014Reducing}.
-Consequently, a substantial cost reduction could be achieved if the total peak-demand can be proactively controlled \cite{liao2015dispatch}.
-
-%		\subsection{EV Charging Scheduling in the ACN}
-%		With the proliferation of EVs, the charging requirement of the microgrid EVs could be a portion of total microgrid electricity demand.
-
-%		To respond the electricity demand of EVs, CSs are being used where EVs can recourse to charge their battery \cite{He,liao2015dispatch,Tang}.
-There can be few to many CSs dispersed in an ACN, e.g., each for a parking garage of a building in a university campus.
-In this scenario, all parking stations are governed by a facility operator and a \textit{global} peak demand constraint is determined such that the aggregate charging demand in the entire network is less than this global peak demand \cite{DWang,Hoog}.
-
-%		The charging scheduling of the EVs with the goal of respecting the \textit{global aggregate peak constraint}, however, is a unique problem which is different from the single station EV charging scheduling.
-Most of the existing work in the literature, tackle the problem in the single parking station scenario.
-We refer to Section~\ref{sec:rel} for in-depth discussion.
-As discussed in Section \ref{sec:problem}, the global optimal solution cannot be obtained by separately solving the single station problems.
-%		On the other hand, there are only a few studies that provide global optimal solution for charging scheduling of EVs \cite{He, Moradijoz, Malhotra,Zeng,Shaaban,DWang}.
-Despite elegant results, the underlying problems, e.g., charging cost minimization problem in \cite{He}, average operating cost minimization with optimal electricity exchange capacity problem in \cite{DWang}, optimal station capacity problem in~\cite{Moradijoz}, user convenience maximization problem in~\cite{Malhotra}, joint optimization of system profit and user experience in~\cite{Shaaban,Zeng} are different from the problem studied in this paper.
-
-%		\subsection{Problem, Challenges, and Contributions}
-We consider a scenario with multiple EVs where each EV has different charging profile in terms of availability, charging demand, charging rate limit, and valuation of getting charged \revv{(for details see Section~\ref{sec:ev})}.
-We formulate an online EV charging scheduling problem with the goal of \textit{selecting} and \textit{scheduling} a subset of EVs such that: (1) the charging demand of the selected EVs are (fully or partially) satisfied; (2) the charging rate limit of EV batteries are respected, (3) the global peak constraint of the ACN is satisfied~\cite{lee2016adaptive}; (4) the local peak constraint of each CS is respected;  and finally, (5) the total revenue obtained by the valuation of the EVs is maximized.
-
-%		of maximizing the revenue of the ACN.
-The constraints are the \textit{local} peak constraint of each CS, and the \textit{global} peak constraint that limits the accumulative charging demand drawn from the entire network of stations (decided by the administration of the ACN to control total peak demand~\cite{lee2016adaptive}).
-
-There are two main challenges in the design and implementation of scheduling algorithms for EVs satisfying the goals mentioned above.
-\rev{Firstly, the problem calls for online scheduling design.} In practice, EVs arrive to the CS in online fashion and the scheduler has no information about the arrival and demand of the future EVs.
-Secondly, the underlying optimization problem in integral model is \bt{strongly} NP-hard even in offline case \rev{(see Section~\ref{sec:integral})}.
-This is because the problem is a mixed integer linear problem and a ``time-expanded'' extension of knapsack problem which is known as a classic NP-hard problem.
-In this paper, we tackle the challenge of online design by following competitive algorithm design~\cite{borodin2005online} and the challenge of NP-hardness by pursuing approximation algorithm design~\cite{approx} and make the following contributions:
-
-$\vartriangleright$ We first consider a \textit{fractional model} (where EVs can be charged partially and the revenue is proportional accordingly) and design an optimal offline scheduling algorithm. 
-%In addition to provide efficient result, the algorithm has a further elegant step to apply a valley filling strategy to further reduce the peak demand of EV charging without degrading total revenue. 
-We then develop an efficient online algorithm in which no exact or stochastic information about the future EV arrivals is given.
-Despite its simplicity, the algorithm is proved to be $2$-competitive with optimal offline solution, i.e., the revenue of the proposed online algorithm is at least $1/2$ of the offline optimum, regardless of input sequence.
-Even though there are competitive algorithms in the literature for similar problems, to the best of our knowledge, our algorithm is the first $2$-competitive algorithm \rev{which considers the} charging rate limits.
-
-$\vartriangleright$ We next study \rev{the} more challenging scenario of \rev{the} \textit{integral model}\rev{, }where EVs must receive all their demand to make revenue.
-We first propose a polynomial-time primal-dual offline approximate algorithm.
-We analyze the approximation ratio of the algorithm and by strengthening the linear relaxed version of the mixed integer problem~\cite{Carr}, we obtain an approximation ratio of $\alpha =1+\sum_{j=1}^m {\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}$, where $p_j$ is local peak constraint in station $j$, $q_j$ is the maximum charging rate of the EVs in station $j$ and $s$ is a slackness parameter.
-We highlight that when $p_j \gg q_j$ and $s$ is \rev{large} enough, then $\alpha \approx m+1$, where $m$ is the number of stations in the ACN.
-Built on the basis of the offline algorithm, we devise an online algorithm, and discuss its competitive ratio in special cases.
-%In particular, the competitive ratio is $b\Big(1+\frac{p_j}{p_j-q_j}\cdot\frac{s}{s-1}\Big)$ for single station scenario, where $b$ is the number of batches with the same arrival time.
-
-$\vartriangleright$ We conduct a set of  simulations to evaluate the performance of our proposed algorithms. 
-%For offline scheduling problem under integral charging model, the results  demonstrate that the proposed approximation algorithm is close to the optimal solution and is significantly better than the obtained theoretical bounds.
-The results of online algorithms for both integral and fractional settings are close to the optimum (within $90\%$ and $94\%$ for integral and fractional models in a representative scenario).
-In addition, our algorithm outperforms the existing scheduling algorithm in Caltech ACN~\cite{lee2016adaptive} by $35\%$ for integral revenue model.
-
-\bt{This paper represents follow-up work to our previous study~\cite{alinia2018competitive}, where we address a simplified version of the problems studied in this paper in fractional revenue model.
-The competitive analysis in~\cite{alinia2018competitive} is done under the assumption that all EVs have the same maximum charging rate.
-Also, \cite{alinia2018competitive} does not study the integral revenue model.
-In this paper, we extend the results and propose a 2-competitive online algorithm with no assumption on the input parameters.
-Also, the current study investigates both fractional and integral revenue models while considering global peak constraint in the formulation and addressing multiple charging station scenario.
-Last, we consider more realistic trace-driven experiments in this paper and compare the results to an existing real-world scheduling algorithm.}
-%The simulation section also discusses on the positive and negative effects of slackness parameter in different scenarios.
-
-%To the best of our knowledge, this problem is not addressed yet in previous studies.
-
-%		\subsection{Paper Organization}
-%		The rest of this paper is organized as follows. Section~\ref{sec:rel} reviews the literature. In Section \ref{sec:model}, the system model  and problem formulation are described. 
-%		Section \ref{sec:fractional} provides offline and online algorithms for fractional model.
-We study integral model in Section \ref{sec:integral} and propose online and offline algorithms.
-The simulation results are reported in Section~\ref{sec:simul}.
-Section~\ref{sec:conclusion} concludes the paper and highlights future directions.
-
-\section{Related Work}
-\label{sec:rel}
-\revv{There is an extensive work in the general topic of EV demand management and scheduling~\cite{mukherjee2015review} by considering different scenarios such as optimal operations with EV coordination and congestion management~\cite{mukherjee2017distributed,rigas2013congestion,hu2013coordinated}, EV scheduling with incorporation of renewable energy, and energy storage systems~\cite{de2017impact,shafie2018innovative}, and pricing and bidding~\cite{huang2014distribution,hou2019bidding} In this section, we focus on the literature related to peak-constrained EV charging scheduling in single and multiple stations.}
-\subsubsection{Peak-Constrained EV Charging Scheduling}
-\label{sec:rel:peakconstrained}			
-\revv{There is an extensive literature on EV charging scheduling problem focusing on single CS~\cite{Tang,Wen}, while the local and global peak constraints are omitted or only the local peak is considered.}	As we discuss in Section~\ref{sec:problem}, the global optimal solution cannot be obtained by separately solving the single station problems.
-Hence, those solutions cannot be directly applied to the multiple CS scenario with global peak constraints.
-
-%A scenario that local and global peak constraints exist is the case that scheduling is required for a charging network for multiple CSs. 
-Studies in \cite{He,malhotra2017distributed,Moradijoz,DWang,Zeng,Shaaban} tackled charging scheduling problem in multiple CSs.
-The authors in~\cite{He} studied a global cost minimization EV charging scheduling problem.
-However, there is no limit on the maximum peak demand that the system can tolerate.
-Consequently, the peak can be arbitrary high and beyond the physical limit of the transformers in the charging station~\cite{lee2016adaptive} leading to huge electricity bills~\cite{Zhang2015eEnergy}.
-Besides, the charger devices installed in the CSs have limitation on the maximum power that they can transfer in each time unit~\cite{Tesla}.
-%We solve the issue by constraining local and global peaks.
-However, to meet the peak constraints, it may not be feasible to respond to all charging demands.
-Consequently, only a subset of EVs can be charged~\cite{Xiang}, which is captured in our problem formulation.
-\cite{DWang} considered a multi-microgrid system with global peak constraint where each microgrid has a CS and the goal is to manage electricity exchange between microgrids and main grid to minimize the operating costs.
-The authors assume that required information about individual EVs is available by forecast which may not represent a real scenario.
-A similar assumption is made in \cite{Zeng,Shaaban} where the objective is to maximize total utility of EVs and aggregators in a distribution network.
-%\rev{To be removed: In our solution, we applied a priority based selection process (based on the EVs' valuation) to respond to the demands to make sure that total peak respects the constraints.
-The selection process can be made based on different criteria such as the value of each charging request \cite{Lee, Xiang} or the priority.}
-%To avoid big billing cost in peak hours, \cite{Moradijoz} proposed a solution based on genetic algorithm to find optimal capacity and location of parking lots for serving demands in peak hours with the goal of maximizing total benefit of all stations.
-Although authors studied the problem under multiple CS setting, their solution is not applicable to our setting when the CSs are already set up.
-The authors in~\cite{malhotra2017distributed} use a similar model as in this paper, where both local and global peak constraints are considered.
-However, the authors solve the single-slot problem, which fails to provide a general solution taking into account EVs' arrival and departure times as considered in our study.
-Finally, as an alternative approach to control the peak, some studies directly target minimizing the peak~\cite{Zhao, Karfopoulos}.
-In~\cite{Zhao}, an online algorithm is developed for EV charging to minimize the peak and \cite{Karfopoulos} proposed a valley filling method by leveraging V2G in peak hours.
-Although the peak is minimized in above works, it cannot guarantee that the minimized peak is tolerable by the underlying charging network.
-
-\subsubsection{Scheduling Under Demand Uncertainty}
-A main challenge in EV scheduling problem is to cope with demand uncertainty.
-Many studies including \cite{Shroff2014,Tang,WTang,Chen,Xiang,Zhao,Robu} addressed online scheduling problem with different objectives.
-\cite{Shroff2014,Xiang} studied the problem of maximizing social welfare considering the benefit for both users and service provider.
-\cite{Tang} and \cite{WTang} developed algorithms to minimize the charging price for the CS, where the proposed algorithm in \cite{Tang} is $2.39$-competitive.
-%An online algorithm developed in \cite{Chen} to optimize overall operating profit of the service provider. 
-In \cite{Robu}, an online $2$-competitive algorithm is proposed for a single CS, assuming that EVs are capable of being discharged in a negligible amount of time.
-The assumption, however, is not realistic for EVs.
-
-Our problem in this paper is unique from above works in many respects.
-First, we study the problem in an ACN where several CSs exist, while none of the above studies solve the problem under this setting.
-Second, the previous algorithms do not work for both integral and fractional charging models.
-In addition, \cite{WTang,Chen} put no limit on the charging rate of EVs which makes their solution impractical in real scenarios.
-Also, \cite{WTang,Tang, Shroff2014,Chen,Zhao} do not consider the peak limit of the CS.
-\revv{Note that some studies~\cite{jin2017optimal} tackle the scenarios of satisfying the large demands (possibly EV demands) by participating in electricity market.
-This study assumes that the electricity price is given and fixed, and leaves the case of real-time pricing as the future direction.
-In addition, there are studies that incorporate prediction in online EV charging scheduling~\cite{wang2017predictive,chen2014distributional}.
-The prediction-based approaches achieve satisfactory performance for the scenarios that follow prediction.
-Deviation from prediction models, however, degrades their performance.
-Our approach, on the other hand, has no assumptions on modeling/prediction, and in this way, is robust against any uncertainty in the instances to the problem.}
-\revv{Finally, in~\cite{Alinia2018ITS}, we considered a simplified EV charging scheduling in fractional model without global peak constraints and devised heuristic algorithms (without competitive and approximation analysis) with on-arrival commitment for EVs to notify the amount that they can receive by their departure.
-}
-%In this paper, we consider these limitations and develop online and offline algorithms for fractional and integral revenue models in an ACN and provide theoretical bounds on their performance.
-
-%It is important to note that there is a considerable similarity between EV scheduling problem and classical job scheduling problem \cite{}.
-However, most algorithm developed for job scheduling problem  do not consider a limit on processing rate of the jobs.
-
-%\cite{Shroff2014} and \cite{Stein2012} study social welfare maximization problem while the profit of both EV owners and CS is considered.
-social welfare of the EV owners \cite{Stein2012}, charging cost \cite{Tang,WTang}, and total value of fully charged EVs \cite{Azar}).
-In addition, \cite{WTang, Tang,Shroff2014,Zhao} do not take into account the peak limitation of CS.
-}
-
-\subsubsection{Worst-case Analysis in Similar Scheduling Problems}
-\label{sec:rel:comp}
-\bt{
-	Similar underlying scheduling problems with slightly different settings have been studied in the literature in both offline and online settings.
-In offline setting, the problem is more interesting \bt{under integral revenue model} where the problem becomes a combinatorial optimization problem and approximation algorithms have been used to find effective solutions.
-The performance of an approximation algorithm is determined by its \emph{approximation ratio} for offline 
-algorithms.
-On the other hand, competitive online algorithms are used in the online setting and \emph{competitive ratio} is the performance metric which compares the algorithm's result to the offline optimal solution.
-
-\textit{Offline integral model}: Under integral revenue model, \cite{jain2015near} proposes an offline algorithm for scheduling of batch jobs in cloud computing which is similar to EV scheduling problem.
-It is assumed that all jobs are available to be processed at time 0.
-The authors propose a $\frac{C}{C-k}.\frac{s}{s-1}$-approximation algorithm where $C$ is the cloud capacity and $s$ is the ``slackness parameter'' (See section \ref{sec:acn} for the definition).
-Similarly, \cite{yao2016real} tackles the offline integral problem and proposes a convex relaxation method to find a near-optimal solution.
-No theoretical bound is provided for the algorithm and the performance is examined by simulation results.
-In this paper, we propose \ics for the EV scheduling problem with slightly different settings in the constraint sets, and tackle the problem in online setting in which the full knowledge of the online parameters is not available a priori, and provide approximation ratio under specific scenarios.
-
-\textit{Offline fractional model}: In case of fractional revenue model (for offline case), the scheduling problem is more straightforward to tackle since the underlying problem is linear.
-In this paper, we propose \fcs as an optimal solution for offline fractional case with low time complexity.
-
-\textit{Online fractional model}: In the online scenario, the scheduling problem is fundamentally more challenging. In our recent study \cite{alinia2018competitive}, 
-we proposed two online algorithms referred to as WFAIR and WRAND for EV scheduling problem.
-The proposed algorithms provide a competitive ratio of $2-1/U$ where $U$ is "scarcity level".
-However, the result only holds when all EVs have the same maximum charging rate.
-Also, \cite{alinia2018competitive} does not study the integral revenue model.
-In this paper, we propose \focs as a 2-competitive online algorithm with no assumption on the input parameters.
-Moreover, the current study investigates both fractional and integral revenue model while considering total peak constraint in the formulation and addressing multiple charging station scenario.
-In another work~\cite{firstfit}, two simple and natural online algorithms called \textsc{FirstFit} and \textsc{EndFit} were developed and are proved to be 2-competitive.
-\focs is extension of these algorithms by taking into account the maximum charging rate of the EVs and multiple charging station scenario (see ``Remarks'' at Section IV).
-As recent studies, \cite{zheng2016online,deng2016whether} provide online algorithms for EV scheduling problem, however, they do not take into account global peak constraint in the underlying problem.
-
-\textit{Online integral model}: Another direction is to tackle online scenario under integral revenue model.
-In this setting, the scheduling problem becomes fundamentally more challenging.
-We note that the integral scheduling problem is strongly NP-Hard even in the offline case \cite{de2018complexity}.
-Due to combined online and combinatorial challenges, there are very limited studies in this category.
-\cite{lucier2013efficient} provides an online algorithm without considering the maximum processing rate of the jobs where its competitive ratio can be arbitrary bad depending on ``slackness'' parameter.
-Our work in Section~\ref{sec:onlineint} extends this study for multiple station scenario and considering maximum charging rate for the EVs.
-}
-
-\section{System Model and Problem Formulation}
-		\label{sec:model}
-
-		\subsection{System Model}
-		We consider a time-slotted system model in which the time horizon is divided to $T$ equal length slots ${t=\{1, 2, \dots ,T\}}$ (e.g., $T=24$ with time slots of $1$ hour length).
-\subsubsection{Charging Network}
-\label{sec:acn}
-Our charging network model is inspired by the Caltech ACN~\cite{lee2016adaptive} as illustrated in Fig.~\ref{fig:model-a}.
-In \rev{the} Caltech EV charging network (located in a parking garage), electricity is distributed through a two-level transformer architecture from a main switch panel to multiple EV switch panels (\rev{$2$} panels in the current Caltech ACN).
-Each EV switch panel then is connected to several chargers ($\approx$25 chargers \rev{per panel} in the Caltech ACN).
-The total power drawn from the main switch panel \rev{by} the charging network has a power limit of  $p^\mathsf{total}$, that is determined by the facility operator to control the costs, reserve the capacity for other loads, and/or participate in demand-response programs.
-%This power, where we refer to it as \emph{network power limit} is used for both EV charging as well as non-EV charging purposes (e.g., lighting, fans, etc \cite{lee2016adaptive}). 
-In other words, $p^\mathsf{total}$, which we refer to it as the \textit{global peak}, hereafter, limits the maximum aggregate EV charging load at each time slot. 
-%The global peak must be less than or equal to the value obtained by subtracting non-EV load from network power limit. 
-%When we write \emph{global peak constraint}, it refers to $p^\mathsf{total}$.  
-%$p^\mathsf{total}$ is the maximum allowed aggregated electricity consumption by all stations at each slot and limits the total transferable power to EVs.
-
-We assume that there are $m$ EV switch panels that represent $m$ CSs.
-In addition to the global peak constraint, each CS $j$ has \rev{a} capacity constraint on \rev{its} total power drawn, indicated by $p_j$, and referred to it as the \emph{local peak} constraint.
-The \rev{value of} $p_j$ is determined by the output power limit of the transformers installed between the main switch panel and EV switch panels and could be different for each EV switch panel.
-%installed chargers in a CS have limited output power to charge EVs ~\cite{Wen,Xiang,Tesla}. Therefore, for CS $j$, $p_j$ cannot be more than sum of output power of its chargers. 
-\rev{It is often observed that the charging demand of different CSs (EV switch panels in Fig.~\ref{fig:model-a}) are well below the local peak constraints.}
-To increase the flexibility due to heterogeneous charging demand of CSs, in the Caltech ACN, the global peak constraint of the main switch can be \textit{over-provisioned}, i.e., $p^\mathsf{total}$ is less than the aggregate local peaks,  ($\sum_j p_j\geq p^\mathsf{total}$).
-\rev{While this increases flexibility, it also couples the problem of EV charging scheduling across different CSs.}
-%Despite increased flexibility, the over-provisioning property, however, couples the problem of EV charging scheduling across different CSs. 
-Our solutions in this paper will be centralized ones which can be obtained through communication between the CSs and a central server as illustrated in Fig. \ref{fig:model-b}.
-
-%We make this clear by a simple example.
-Assume $m=2, p^\mathsf{total}=50$ kW and $p_1=p_2=25$ kW.
-In a specific time slot (e.g., $t=1$), the total demand in CS $1$ and $2$ is $40$ kWh and $10$ kWh, respectively.
-According to local peak constraints, it is not feasible to satisfy all demands in a single time slot.
-However, if we had $p_1=p2=50$ kW (e.g., by installing more chargers in the stations) we could be able to satisfy all demands by allocating $40 kW$ in $p_1$ and $10 kW$ in $p_2$ while still not violating $p^\mathsf{total}$.
-In case that $\sum_j p_j\leq p^\mathsf{total}$, the scheduling problem is not challenging and the solution can be obtained by solving the problem locally in each CS.
-If $\sum_j p_j> p^\mathsf{total}$ (which is the case we consider in this paper), a centralized solution is needed that can be obtained through communication between the CS and a central server as illustrated in Fig.
-\ref{fig:model-b}.
-
-\begin{figure}	
-\centering
-\minipage{0.49\textwidth}
-				\begin{subfigure}[b]{0.69\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{model-a.pdf}
-						\caption{Caltech adaptive charging network (ACN)}
-						\label{fig:model-a}
-					\end{center}
-				\end{subfigure}%
-				\begin{subfigure}[b]{0.29\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{model-b.pdf}
-						\caption{Communication model with server}
-						\label{fig:model-b}
-					\end{center}
-				\end{subfigure}%  
-\caption{System model \cite{lee2016adaptive}.} 
-\label{fig:slackness1}
-\endminipage
-\end{figure}
-
-		\begin{table} 
-			\caption{Summary of key notations}
-%			\vspace{-3mm}
-			\label{tbl:not}
-			\begin{center}
-				\begin{tabular}{|c L{6.5cm}|}
-					\hline
-					\textbf{Notation} & \textbf{Description} \\
-					\hline \hline			
-					$T$ & Number of time slots, indexed by $t$\\			
-					$m$ & Number of CSs, indexed by $j$\\			
-					$n$ & Number of EVs, indexed by $i$\\			
-					\hline
-					\hline
-					$a_i$ & Arrival time of EV $i$\\
-					$d_i$ & Departure time of EV $i$\\
-					$D_i$ & Demand of EV $i$\\
-					$v_i$ & Valuation of EV $i$ for receiving its demand $D_i$ \\
-					$k_i$ & Maximum charging rate of EV $i$\\
-					$h(i)$ & CS of EV $i$\\
-					\hline
-					\hline
-					$q_j$ & Maximum $k_i$ among all EVs in CS $j$\\
-					$p_j$ & Maximum aggregate charging rate in station $j$\\
-					$p^\mathsf{total}$ & Maximum aggregate charging rate of all stations\\
-					\hline
-					\hline
-					$y_i^t$ & \textbf{opt. variable}, The amount that EV $i$ is charged at $t$ \\
-					\hline
-				\end{tabular}
-			\end{center}
-		\end{table}
-		\subsubsection{EVs}
-		\label{sec:ev} There are $n$ EVs in the system, indexed by $i$.
-		%, all available at time $t=1$ to be charged\footnote{This assumption is reasonable for the %official buildings where the starting hour of the working day is fixed for all the %employers.
-Extensions to the case with different arrival times for the EVs, is part of the %future work.}.
-		EV $i$ is represented by a charging profile $\langle a_i,d_i,v_i,D_i,k_i\rangle$ 
-		indicating its arrival time, departure time, willingness to pay, charging demand, and maximum charging rate, respectively. 
-		%(depends on physical properties of EVs battery) 
-		More specifically, the charging of EV $i$ can be scheduled within its \emph{availability window}, $[a_i,d_i]$.
-The charging rate at each slot is bounded by $k_i$, a parameter that depends on the physical constraints of the \rev{battery and on-board charger}.
-It is assumed that the charging profile of each EV is feasible with respect to its maximum charging rate and a slackness parameter $s\geq 1$, which is the minimum ratio between the park time of the EV and its minimum charging time, i.e., ${D_i\leq k_i(d_i-a_i+1)/s}$.
-The slackness parameter is imposed to tune the flexibility of the charging scheduling.
-In extreme case $s=1$,  the flexibility is minimum and the flexibility improves as $s$ increases.
-%		Note  that  the slackness  parameter  can  impact  the  total  revenue  and  is  investigated  in  simulation  experiments  in Section~\ref{sec:simul}.
-		We assume that EV owners select their CS, perhaps the nearest to them, and so the assignments are given to the problem. Define $h(i)$ as the CS of EV~$i$.
-		Moreover, $q_j$ denotes the maximum $k_i$ among all EVs in CS $j$, i.e., $q_j=\max_{h(i)=j} k_i$. 
-		\revv{Finally, $v_i$ is the willingness to pay of EV $i$ to receive its entire demand $D_i$ before the departure time $d_i$.
-Note that in resource-constrained EV scheduling in ACN, it is not feasible to fulfill the entire demand of all EVs, hence, the problem turns into a resource allocation one with the goal of maximizing the aggregate value (a.k.a.
-utility) obtained from the EVs.
-In this way, each user can announce its willingness to pay to get charged which is denoted by $v_i$ in the system model.}
-		%We assume that there is no gain for the CS if EV $i$ is partially charged.
-
-		% where $P$ defined as $P:\xi\rightarrow  \mathcal{P}$. 
-\subsubsection{Revenue Models\label{sec:irm}} We consider two revenue models: 
-\textit{(i) Fractional revenue model}: In this model, the fractional charging is allowed, i.e., the revenue from each EV is proportional to the fraction of the demand that is fulfilled \cite{Xiang} (see Eq.~\eqref{Eq:partial_value}).
-We tackle this model in Section~\ref{sec:fractional}.
-\textit{(ii) Integral revenue model}: \rev{In this model, EV $i$ pays $v_i$ if it is fully charged and zero otherwise, i.e., there is no partial revenue for partial charging. }
-%In this model, when EV $i$ is received its demand entirely, the gain is $v_{i}$ and zero, otherwise, i.e., there is no partial revenue for fractional charging. 
-This is the model that is considered in~\cite{WTang,Shroff2014}. We tackle this model in Section~\ref{sec:integral}.
-
-		%The actual aggregated peak of all parking stations must not exceeds global peak constraint.
-
-			\begin{table*}[!t]
-			\centering
-%	\vspace{-3mm}
-			\caption{Proposed algorithms and their properties.}
-			\label{tbl:algs}
-			\begin{tabular}{ | l | c | c | c |c|}
-				\hline
-				\textbf{Algorithm} & \textbf{Revenue model} & \textbf{Type} & \textbf{Optimality} & \textbf{Complexity} \\ \hline\hline    
-				\fcs& fractional& offline& Optimal & $O(n^2T+nT^2)$\\\hline 
-				\ics& integral& offline& ${\Big( 1+\sum_{j=1}^m {\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}\Big)}$-approximate & $O(nT\log T+n^2T)$ \\\hline 
-				\focs & fractional& online& $2$-competitive & $O(n^2T)$\\\hline 
-				\iocs& integral&  online& $b(1+\frac{p}{p-q}.\frac{s}{s-1})$-competitive, $(m=1)$ & $O(n^2T)$\\\hline
-			\end{tabular}
-		\end{table*}
-
-		\subsection{Problem Formulation}
-		\label{sec:problem}
-	We formulate an optimization problem to schedule the charging of the EVs with the objective of maximizing total revenue obtained from charged EVs while respecting local and global peak constraints. 
-		Note that each revenue model makes the underlying optimization problem fundamentally different. More specifically, the fractional charging model is a linear problem. 
-		Integral revenue model, however, turns the underlying charging scheduling problem to a Mixed Integer Linear Program (MILP). The integer nature originates from the $0/1$-selection decision on EVs. 
-%%%Recall that in integral revenue model the revenue is obtained given that the entire demand is fulfilled for the selected EV. 
-		%We skip the explicit formulation of the problem under integral revenue model since it could be contemplated as the linear-relaxed version of the integral revenue model (for more explanation, we refer to the discussions in Section~\ref{sec:fractional}).
-		\bt{We formulate a Scheduling Problem} for Adaptive charging Network (\MCSP) under fractional revenue model as follows: 
-		\bse
-		\bee
-		\MCSP: \max  && \sum\nolimits_{i=1}^n \frac{v_{i}}{D_i}\sum\nolimits_{t=a_i}^{d_i} y_i^t \label{Pobjec} \nonumber\\
-		\text{s.t.} &&\sum\nolimits_{t=a_i}^{d_i} y_i^t\leq D_i,\quad\quad\forall i, \label{ConstPartial} \\
-		&&  \sum\nolimits_{i=1}^n y_i^t\leq p^\mathsf{total} ,\quad\quad\forall t,\label{ConstTotal} \\
-		&&\sum\nolimits_{i:h(i)=j} y_i^t\leq p_j ,\quad\quad\forall t,j,\label{ConstLocal}\\
-		&& y_i^t  \leq \frac{k_i}{D_i}\sum\nolimits_{t^\prime=a_i}^{d_i} y_i^{t^\prime}, \quad\forall i,t,\label{ConstSpeed}\\
-%		&& \rev{y_i^t=0,\forall t\in\{t':t'>d_i \vee t'<a_i\}}, \\
-		\text{vars.} && y_i^t \geq 0, \quad\quad\forall i, t,\label{ConstPositive}\nonumber
-		%&& s_v(t), \quad \forall v,t
-		\eee
-		\ese
-		where $y_i^t$ is the amount that EV $i$ is charged at slot $t$. Constraint (\ref{ConstPartial}) ensures that the aggregate amount received by EV $i$ is at most the demand $D_i$. 
-%		Note that under integral revenue model, when we design our algorithm, we do not allow partial charging. 
-The global and local peak constraints are represented by constraints (\ref{ConstTotal}) and (\ref{ConstLocal}), respectively.
-
-		\revv{The constraint~\eqref{ConstSpeed} enforces the maximum charging rate of EVs.
-The straightforward way to express this constraint is to simply state that at each time slot $t$, the charging rate of EV $i$ should be less than or equal to its maximum charging rate, i.e., $y_i^t\leq k_i, \forall i,t$.
-		However, for the sake of effective algorithm design for integral model and reducing the integrality gap of the relaxed linear problem, this constraint is strengthened in the form of Eq.~\eqref{ConstSpeed}.
-		Note that in case that the aggregated charging of EV $i$ during its availability window is equal to its demand, i.e., $\sum_{t^\prime=a_i}^{d_i} y_i^{t^\prime}= D_i$, Eq.~\eqref{ConstSpeed} reduces to the simple form of $y_i^t\leq k_i$.
-		This is a natural way in approximation algorithm design to improve the performance of the algorithms under linear-relaxation based design~\cite{Carr}. }
-
-The \MCSP is an extension of formulated problem in \cite{Jain} where a job scheduling problem in cloud applications is studied.
-It turns out that the resource allocation problem in cloud systems and the EV charging scheduling problem in a \emph{single station} share similar structure.
-Indeed, each charging profile in our scheduling problem can be seen as a job in cloud system with a deadline, value, and CPU demand.
-The \MCSP, however, comes with an additional constraint~\eqref{ConstTotal}, which makes it different from the problem in \cite{Jain}, such that the existing solution \revv{will not} work in the new setting.
-More importantly, this paper studies both offline and online solutions for the problem in both fractional and integral settings, while \cite{Jain} tackles only the offline integral model.
-
-%(ii) Our solution design and analysis for integral revenue model is based on linear-relaxation primal-dual framework~\cite{Jain}.
-Therefore, in Section \ref{sec:integral} for integral revenue model, we rely on the \MCSP for the analysis of the proposed algorithms and skip to explicitly formulate the original MILP problem.
-
-%		Also, we cover the fractional revenue model and provide theoretical bounds for the proposed algorithms.
-
-%In the next two sections, we devise several algorithms to solve the \MCSP under the two revenue models (integral and fractional) and for both offline and online scenarios. 
 \section{Fractional Revenue Model}
@@
 		where $v_i$ is the gain, if the entire demand $D_i$ is fulfilled and $v_i^{\mathsf{f}}$ is the fractional gain.  
-
 %Under fractional revenue model and without the binary variable of selecting EVs, the underlying problem turns into a linear one. 
@@
 In the following, the online $2$-competitive algorithm is designed, where no exact information or stochastic modeling of future inputs of the problem is available.
-A summary of proposed algorithms with their complexity and assumptions is given in Table \ref{tbl:algs}.
+A summary of proposed algorithms with their complexity is given in Table~\ref{tbl:algs}.
 
-\revv{
 \subsection{Optimal Offline Design}
 \label{sec:fopt}
-\bt{
+
 In this section, we propose an optimal algorithm for offline fractional model.
 As a natural solution, one may think of a greedy algorithm as follows: at each time slot, charge the EV(s) with highest unit-value and process others if only the remaining resource cannot be allocated to the selected EV(s) (e.g., due to maximum charging rate constraint or fulfillment of the EVs' demand).
-This approach is a popular, yet straightforward method in the scheduling.
+This approach is a popular and straightforward method in the scheduling.
 However, it turns out that this approach cannot provide an optimal solution to the problem even in fractional revenue model.
@@
 Then, applying the simple greedy, EV 1 will be selected at time slot 1 and EV 2 will have no chance to get charged due to its deadline constraint while EV 1 could wait until time slot 2 and still receive all its demand.
-}
 
@@
 
-Before discussing the details of the algorithm, we give \bt{a definition} and introduce some notations to facilitate our algorithm design.
+Before discussing the details of the algorithm, we give formally define the notion of ``super interval'' to facilitate our algorithm design.
 
@@
 \end{thm}
-}
 
@@
 %\end{thm}
-		\section{Integral Revenue Model}
-		\label{sec:integral}
-%
-%		\subsection{Overview of Integral Revenue Model}
-%		\label{sec:intoverview}
-		The MILP form of the \MCSP in integral model is a generalized form of the $0/1$-knapsack problem which is a well-known NP-hard problem.
-\rev{To give an intuition, consider the scheduling problem in a single time slot (i.e, $T=1$).
-Then, allocating power resources to the EVs is equivalent to allocating the capacity of knapsack to the items.
-}
-		In Section~\ref{subsec:icsalgorithm}, we propose a fast polynomial time offline approximation algorithm for the integral problem.
-In Section~\ref{sec:onlineint}, we extend the result and propose an online algorithm for the integral model.
-%		, where the EVs arrive in slot-by-slot fashion, and the scheduler has no information of the future arrivals.
-
-%The problem is even more challenging when the uncertainty in EVs' arrival is taken into account.
-At each time slot, the scheduler has no information of unit values of the future charging profiles.
-Therefore, the scheduler cannot make sure about the efficiency of its current charging decision.
-%It can be shown that when there is no assumption on the charging profiles of EVs (including the value of slackness parameter) and the charging decision , no online algorithm can provide a performance guarantee meaning that in the worst case, the ratio of the optimal objective value to the one obtained by the online algorithm can be arbitrary small.
-In fact, when the online algorithm selects
-
-		\subsection{Offline Scenario}   
-		\label{subsec:icsalgorithm}
-		We design our offline scheduling algorithm under integral model referred to as \ics, to solve the \MCSP approximately. 
-%		Our algorithm design is inspired by the basic algorithm proposed in \cite{Jain}.
-The algorithm in \cite{Jain} works for a single CS where arrival time of all EVs are the same and there is no global peak constraint.
-Since the performance analysis of the proposed algorithm relies on a dual fitting method and utilizes weak duality property, \revv{we first need to construct the dual problem of \MCSP.
-Toward this, we introduce variables $\alpha, \beta, \gamma$ and $\pi$.
-Generally, in primal-dual approximation algorithm design, each constraint (resp.
-variable) in primal (resp.
-dual) problem is associated with a variable (resp.
-constraint) in dual (resp.
-primal) problem.
-In our case, constraints (\ref{ConstPartial}) (\ref{ConstTotal}), (\ref{ConstLocal}) and (\ref{ConstSpeed}) in the \MCSP are respectively associated with dual variables $\alpha, \beta, \gamma$ and $\pi$ (for more details see \cite{approx}).
-The dual problem is formulated as follows:}
-		\bse
-		\bee
-		\min &&\sum_{i=1}^n D_i\alpha _i + \sum_{j=1}^m \sum_{t=1}^T p_j\beta (t)+\sum_{t=1}^T p^\mathsf{total}\gamma (t)\nonumber\\ 
-		\textrm{s.t.} && \alpha _i+\beta (t) +\gamma _i + \pi (t)- \frac{k_i}{D_i}\sum_{t'=a_i}^{d_i} \pi _i(t^\prime) \geq \frac{v_{i}}{D_i},\label{ConstDcover} \nonumber\\
-		&& \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\forall i, t\in [a_i, d_i],\\
-		\textrm{vars.}&&\alpha _i, \beta _i, \gamma,  \pi _i(t)\geq 0,\quad\quad\forall i,t. \nonumber
-		\eee
-		\ese
-
-		%%%In this section, we explain \ics in details and then in Section~\ref{subsec:analysis}, we analyze approximation factor of the algorithm. The \ics algorithm is listed as Algorithm~1.
-
-		\subsubsection{Explanation of the Main Algorithm} 
-		\label{sec:icsexplanation}
-		Our algorithm design is inspired by the basic algorithm proposed in \cite{Jain}.
-\revv{The algorithm in~\cite{Jain}, however, works for a single CS where arrival time of all EVs are the same and there is no global peak constraint.}
-		The \ics algorithm (listed as Algorithm \ref{alg:ics}) works in two phases.
-In the first phase it sorts the charging requests based on their unit values in a non-increasing order.
-Then, it selects most valuable demand.
-If the remaining resource is enough to cover the \emph{entire} demand of the EV, it is admitted to receive the demand (Lines~$6$-$7$).
-%		When \ics processes EV $i$, the algorithm checks for the feasibility of allocating $D_i$ units of the resource within its availability window $[a_i,d_i]$ without violating the constraints related to the maximum charging rate $k_i$, local and global peaks (Lines~$6$-$8$).
-
-		\emph{Scheduling of the Selected EV:} \revv{If the feasibility check passed (Line 6 in Algorithm 3)}, \ics calls sub-procedure \sa\ to allocate required resources in interval $[a_i,d_i]$.
-Then, $\alpha _i$ is set to $v_i\slash D_i$ in order to cover dual constraint in Eq.~\eqref{ConstDcover} (Lines~$7$-$8$).
-
-		In \sa, 
-		%%%When EV $i$ is selected to get charged, \sa\ is called for the charging scheduling. 
-		let us define $W(t,h(i))=\sum_{i': h(i')=h(i)} y_{i'}^t$ as total workload at time slot $t$ in CS $h(i)$ and $\bar{W}(t,h(i))$ as total available load to allocate at time slot $t$ for CS $h(i)$.
-We always have ${\bar{W}(t,h(i))+W(t,h(i))=p_{h(i)},  \forall t, i}$.
-For scheduling, \sa\ applies two main policies: 1) \emph{valley-filling} and, 2) \emph{right-to-left allocation}.
-\revv{With valley-filling, the slots with more available resources are preferred which helps to reduce the peak of the system.} %%%It also can be seen as a smoothing method which tries to reduce the variance of the allocated resources at different slots.
-%				The simulation results in Section \ref{sec:simul} will confirm this claim. 
-				Right-to-left allocation is used when two or more time slots are equal in terms of their remaining resources. 
-%				When this policy applies on scheduling of EV~$i$, any EV~$i'$ with $i'>i$ and $d_{i'}<d_i$ has more chance to get charged since the algorithm tends to charge EV $i$ in interval $[d_{i'}+1,d_i]$ (i.e., right hand part of the EV's availability window) and keeps resources in $[a_{i'},d_{i'}]$ for EV $i'$.
-A ranking based approach is used to apply the aforementioned policies. 
-		To charge  EV $i$, \sa\ ranks time slots in interval $[a_i,d_i]$.
-Then, charging is done by allocating resources from the higher ranked time slot to lowest one.
-The rank of a time slot $t$ is calculated based on remaining resources in the time slot (valley-filling) and value of $t$ (right-to-left allocation).
-
-		\begin{algorithm}%\small%1
-			\footnotesize
-			\caption{\ics}
-			\label{alg:ics}
-			\DontPrintSemicolon 
-%			\KwIn{$n$ EVs with $a_i, d_i, v_i, D_i,$ and $k_i$ associated with each EV $i$, $m$ CSs, local and global peak constraints $p_j, j=1,\dots ,m$, and $p^\mathsf{total}$}
-
-%			\KwOut{A feasible scheduling of EVs}
-			\BlankLine
-			%\begin{algorithmic}
-
-			%\slash\slash\textit{\texttt{Initialization}}
-			\textbf{initialize}: $y\leftarrow 0, \alpha\leftarrow 0, \beta\leftarrow 0, \gamma\leftarrow 0, \pi\leftarrow 0$
-
-			Sort charging requests in non-decreasing order of their unit values: $v_1/D_1 \geq v_2/D_2\geq\dots \geq v_n/D_n$
-%			$\frac{v_1}{D_1} \geq \frac{v_2}{D_2}\geq\dots \geq \frac{v_n}{D_n}$
-%			\slash\slash\textit{\texttt{Use sorted list to process demands}}
-
-			\For{(i=1\dots n)}{
-
-				\For{$t=a_i\dots d_i$}{
-					$\sigma_t\leftarrow  \min\Big\{p_{h(i)}-\sum_{i':h(i')=h(i)}y_{i'}(t),$ \newline $\qquad p^\mathsf{total}-\sum_{i'=1}^n y_{i'}^t,k_i\Big\}$
-
-				}
-
-%				\slash\slash\textit{\texttt{if enough resources remain for EV $i$}}
-
-				\If{$D_i\leq\sum_{t=a_i}^{d_i}\sigma_t$}
-				{
-					\sa($i,D_i$)\\
-					$\alpha _i\leftarrow v_i/ D_i$
-				}
-				\Else {
-					\If{$(\beta (d_i)=0)$}{
-						\bc($i$)}
-				}
-			}
-
-			\For{(i=1\dots n)}{ 
-				\If {EV $i$ is not selected}{
-					\rc($i$);
-				}
-			}
-			%\end{algorithmic}
-		\end{algorithm}
-
-\emph{Dual Feasibility of the Non-selected EVs:} \bt{If remaining power resource is not enough} to fully charge EV $i$, i.e.,  $D_i>\sum_{t=a_i}^{d_i}\sigma_t$, the EV cannot be selected.
-However, we still need to satisfy constraint~\eqref{ConstDcover} in dual problem which is done by calling \bc($i$).
-To cover the constraint~\eqref{ConstDcover} for EV $i$, sum of dual variables for all $t\in [a_i ,d_i]$ should be greater than or equal to ${v_i \slash D_i}$.
-\bc($i$) sets $\beta (t)$ to ${v_i \slash D_i}$ for all time slots $t$ in interval $[t_\mathsf{cov}, R(d_i)]$ (Lines $3$-$4$ of Algorithm~\ref{alg:betacover}).
-Observe that  ${\beta (t^\prime)\geq v_i \slash D_i,\forall t^\prime< t_\mathsf{cov}}$ (with $ t_\mathsf{cov}>1$) considering that the demands are sorted in a non-increasing order of the unit-values and $\beta (t')$ is already set to ${v_{i'} \slash D_{i'}}$ when processing the earlier charging demand of EV $i'$ which is not selected.
-Hence, ${v_{i'}\slash  D_{i'}\geq v_i \slash D_i}$, thereby ${\beta (t)\geq v_i \slash D_i,}$ and the dual constraint in~\eqref{ConstDcover} is satisfied.
-		Lines $1$-$4$ of \bc\ is enough to cover the dual constraint.
-However, the algorithm continues in Lines $5$-$8$ by setting a variable $\Phi_{i'}(t)$ for time slots $t=1,\dots ,R(d_i)$ to a value dependent to amount of the resource that a selected EV $i'$ received at slot $t$.
-$\Phi_{i'}(t)$ will be used in approximation analysis of the main algorithm and has no effect on the scheduling of EVs.
-		%We borrowed algorithm \bc($i$) from \cite{Jain} and adjusted it for multiple station mode.		
-%		\vspace{-3mm}
-		\begin{algorithm}%\small%1
-			\footnotesize
-			\caption{\sa($i,D_i$)}
-			\label{SmartAllocate}
-			\DontPrintSemicolon 
-			\KwIn{EV $i$ to receive $D_i$ from CS $h(i)$}
-
-			Rank time slots in interval $[a_i,d_i]$ such that for any $t_1$ and $t_2$:
-			$\mathsf{rank}(t_1)> \mathsf{rank}(t_2)$ iff $\bar{W}(t_1,h(i))>\bar{W}(t_2,h(i))$ OR $\bar{W}(t_1,h(i))==\bar{W}(t_2,h(i)) \wedge t_1>t_2$
-
-			\While {$\sum_{t'=a_i}^{d_i}y_i^{t'}\neq D_i$}{
-
-				Select time slot $t$ with highest rank which is not selected before
-
-				Allocate $\min \left\{k_i,\bar{W}(t,h(i)),D_i-\sum_{\tau=a_i}^{t}y_i^{\tau},p^{\textrm{total}}-\sum_{i'}y_{i'}^t\right\}$ to EV $i$ at $t$
-
-			}
-		\end{algorithm}	
-%		\vspace{-7mm}	
-		\begin{algorithm}%\small%1
-			\footnotesize
-			\caption{\bc($i$)}
-			\label{alg:betacover}
-			\DontPrintSemicolon 
-			%\KwIn{EV $i$ which is not selected to charge}
-
-			\BlankLine
-
-			$t_\mathsf{cov}\leftarrow \min \{t: \beta (t)=0\}$
-
-			$R(d_i)=\max \{t\geq d_i : \forall t^\prime\in (d_i,t], \bar{W}(t^\prime)<q_{h(i)} \}$
-
-			\For{$(t=t_\mathsf{cov}\dots R(d_i))$}{
-				$\beta (t)\leftarrow v_i/D_i$
-			}
-
-			\For{$(t=1\dots R(d_i))$}{
-				\For{$(i'=1\dots n))$}{	
-					\If{$y_{i'}^t>0 \wedge \Phi_{i'}(t)=0$}{
-						$\Phi_{i'}(t)\leftarrow\big[ \frac{p_{h(i)}}{p_{h(i)}- k_i}\frac{s}{s-1}\big] .\frac{v_i}	{D_i}y_{i'}^t$
-					}
-				}
-			}
-		\end{algorithm}
-%		\vspace{-7mm}
-		\begin{algorithm}%\small%1
-			\footnotesize		
-			\caption{\rc($i$)}
-			\label{Replace}
-			\DontPrintSemicolon 
-%			\KwIn{EV $i$}
-%			\KwOut{Updated schedule}
-
-			$\mathcal{L} \leftarrow \emptyset$\\			
-			$v_\mathsf{inc}\leftarrow v_i$\\			
-			$\sigma_t\leftarrow 0, t=a_i,\dots ,d_i$
-
-			%Define $\delta_i(t)=\min \{k_i,\bar{W}(t,h(i))\}$
-
-			%$\Delta\leftarrow \sum_{t=a_i}^{d_i}\min\{\bar{W}(t,h(i)), k_i\}$
-
-			\For{($i' =i-1\dots 1$)}{ 
-				\If {EV $i'$ is selected $\wedge (h(i')=h(i)) \wedge (v_\mathsf{inc}-v_{i'})>0$}{
-					Add EV $i'$ to list $\mathcal{L}$
-
-					$v_\mathsf{inc}\leftarrow v_\mathsf{inc}-v_{i'}$
-
-					\For{($t=a_i\dots d_i$)}{
-						$\sigma _t\leftarrow\sigma_t + \min\{k_i,y_{i'}^t\}$
-					}
-				}
-			}
-
-			\If {$\sum_{t=a_i}^{d_i}\sigma_t\geq D_i$}{
-				Remove EVs in list $\mathcal{L}$ from charging schedule
-
-				\sa($i,D_i$)
-			}
-		\normalsize
-		\end{algorithm}
-
-		\emph{Improving the Gain:} In the second phase, the \ics tries to increase total value of selected EVs by calling \rc($i$) on every unselected EV $i$ (Lines~$12$-$14$).
-\rev{The \rc(i) (listed as Algorithm $6$) checks that whether the total revenue can be increased by replacing some selected EVs with EV $i$ or not (Lines $4$-$9$).
-If such EVs are found, the algorithm stops their charging and allocates EV $i$ using \sa\ (Lines $10-12$).}
-		%We refer to ~\cite{alinia2017online}, for the details and intuition behind this algorithm. 
-%		Before giving the details of \rc($i$), we first explain the intuition behind this algorithm. 
-%		 Note that if in the scheduling problem we set $T=1, m=1, k_i=p^\mathsf{total}, a_i=d_i=1\ \forall i$, then the problem is equal to the well-known $0$-$1$ knapsack problem~\cite{approx}.
-In the knapsack problem, a widely used greedy approach sorts items based on their unit values and selects items accordingly.
-It turns out that in this approach the approximation factor can be arbitrarily bad.
-For example, consider a knapsack problem with two items with $v_1=2, v_2=p^\mathsf{total}, D_1=1$, and  $D_2=p^\mathsf{total}$.
-Given these values we have $v_1\slash D_1>v_2\slash D_2$.
-To maximize total value of selected items, the optimal solution chooses item $2$ while greedy algorithm selects item $1$ which results in a worst-case approximation factor of ${c \slash \opt}$ in general where $c$ is a constant (in this example $c=2$).
-To resolve it, one approach is to \emph{re-consider} unselected items after running greedy algorithm and replace some selected items in the knapsack with unselected ones and then check whether the result is improved or not.
-In a simple case, only the largest unselected item can be examined which makes a significant theoretical improvement by providing a worst case approximation factor of $\opt\slash 2$.
-%		 
-%\ics algorithm leverages the same idea but using a more intelligent replacing method called \rc($i$).
-\rc($i$) is called on every unselected EV $i$.
-It tries to find some selected EVs that if they are replaced by EV $i$, total revenue from the selected EVs increases.
-%%%When \ics calls \rc($i$) on all unselected EVs, an improvement in total revenue of final selected EVs is expected.
-%This is confirmed by the simulation results in Section~\ref{sec:simul}.
-
-		\subsubsection{Analysis}
-		\label{subsec:analysis}
-		\bt{In a primal-dual algorithm}, the goal is to design an algorithm in a way that it produces a good solution for primal problem (with primal value $\Gamma$) and a feasible solution for the dual problem (with dual value $\Lambda$).
-Then, assuming that the primal problem is a maximization problem, to prove that the algorithm is $c-$approximation (for $c\geq 1$), the important part is to show that $\Lambda\leq c\Gamma$.
-Then, based on weak duality theorem we have $\Lambda\geq \opt$, and it is concluded that $\Gamma \geq \frac{1}{c}\times\opt$ where $\opt$ is the optimal value.
-		Based on the above understanding, the following theorem scrutinizes the approximation ratio of the \ics assuming that arrival times are the same for all EVs. 
-%		First note that the designed scheduling algorithm outputs a feasible scheduling since it respects the constraints in the primal problem.
-Also, the algorithm produces a feasible solution for the dual problem by covering the dual problem constraint in (\ref{ConstDcover}) through setting $\alpha _i$ to $\frac{v_i}{D_i}$ when EV $i$ is accepted and, $\beta (t)$ to a value greater than or equal to $\frac{v_i}{D_i}$ for $t\in [a_i, d_i]$ (according to the discussion in Section \ref{sec:icsexplanation}) if EV $i$ is not selected.
-To obtain an approximation factor for the algorithm, it is enough to bound the total covering cost of the dual constraints.
-
-		\begin{thm}
-			\label{thm:approx}
-			\ics algorithm is a $\Big( 1+ \sum_{j=1}^m {\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}\Big)$-approximation when EVs have same arrival time.
-		\end{thm}
-%		
-%		\begin{proof}
-%			In Appendix~\ref{app:1}.
-%		\end{proof}
-
-		Note that in the case that the system is flexible enough, i.e., $s\gg 1$, and the maximum charging rates of stations are much bigger than those of EVs, i.e., $p_j \gg q_j, \forall j$, the approximation ratio approaches $m+1$.
-And in the case that there is one single station, the approximation ratio is $2$.
-%		 Finally, we provide the time complexity of the \ics.
-
-%\begin{thm}
-%\label{thm:ics_complexity}
-%The time complexity of the \ics algorithm is $O(nT\log T+n^2T)$.
-%\end{thm}	
-%
-%\begin{proof}
-%In Appendix \ref{app:ics_complexity}.
-%\end{proof}
-
-\subsection{Online Scenario}
-\label{sec:onlineint}
-Due to the binary selection variable, the online solution design under integral model is more challenging than the one for fractional model.
-\bt{We propose \iocs} that is built upon the offline \ics.
-In particular, the \iocs calls the \ics at each time slot for the set of available EVs, however, any algorithm that is designed for offline integral model can be used alternatively.
-Hereinafter, $\mathcal{A}$ refers to the \ics or a similar algorithm.
-
-\begin{algorithm}%\small%1
-\footnotesize
-\caption{\iocs: $\forall t\in \{1,2,\dots ,T\}$}
-\label{alg:iocs}
-\DontPrintSemicolon 
-%\KwIn{$n$ EVs to arrive on the fly, number of CSs $m$, global peak constraint $p^{\textrm{total}}$, local peak constraints $p_j, j=1,\dots ,m$}
-
-%\KwOut{A feasible charging scheduling}
-
-\BlankLine
-
-Let $\mathcal{A}$ be an algorithm that solves the problem with $a_1=\dots =a_n$
-
-$\mathcal{R}^t\leftarrow$ set of EVs arrived at time slot $t$
-
-$\mathcal{M}^t\leftarrow \mathcal{R}^t\cup \{i: t\in\mathcal{T}_i\ \texttt{AND}\ \sum_{t^\prime}y_{i}^{t'}<D_i\}$
-
-%$\backslash\backslash\texttt{Schedule 1}$
-
-Based on the residual in interval $[t,T]$, use algorithm $\mathcal{A}$ to allocate EVs in set $\mathcal{R}^t$ assuming no further arrivals
-
-$\mathcal{S}_{\iocs,t}\leftarrow\{i:i\in\mathcal{M}^t\ \texttt{AND}\ i$ is admitted at $t\}$
-
-$\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}\leftarrow \sum_{i\in\mathcal{S}_{\iocs,t}}v_i$
-
-Assume all reserved resources are freed at time slots $t, t+1, \dots, T$
-
-%$\mathcal{R}^t\leftarrow\mathcal{M}^t$
-
-%$\backslash\backslash\textsl{set of active EVs at time slot t}$
-
-$r_{i,t}\leftarrow$ remaining demand of $i$ at $t, \forall i$
-
-%$\backslash\backslash\texttt{Use modified demands values}$
-
-$D_i^\prime\leftarrow r_{i,t},\ \ v_i^\prime\leftarrow \frac{r_{i,t}}{D_i}v_i, \forall i\in\mathcal{M}^t$
-
-%$\backslash\backslash\texttt{Schedule 2}$
-
-Run $\mathcal{A}$ on $\mathcal{M}^t$ using $D_i^\prime$ and $v_i^\prime, \forall i$ and reconstruct $\mathcal{S}_{\iocs,t}$
-
-$\Gamma_{\mathcal{A},\mathcal{M}^t}\leftarrow \sum_{i\in\mathcal{S}_{\iocs,t}}v_i$ $\backslash\backslash\texttt{Use original values}$
-
-%$a\leftarrow\frac{V^\prime_{\textrm{total}}}{V_{\textrm{total}}}$
-
-\If{$\Gamma_{\mathcal{A},\mathcal{M}^t}>\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$}{
-
-Use the second schedule
-
-}
-
-\Else{
-
-Use the first schedule
-
-}
-
-\end{algorithm}
-
-The \iocs is summarized as Algorithm~\ref{alg:iocs}.
-At slot $t$, the \iocs compares two scheduling results returned by $\mathcal{A}$ and chooses among them.
-In the first scheduling, the \iocs keeps all reserved resources in interval $[t,T]$ intact.
-Then, for utilizing the remaining resources, the algorithm runs $\mathcal{A}$ over arrived EVs at time slot $t$.
-In this case, the total revenue obtained by the \emph{active} EVs (i.e., EVs that are available but not received their entire demand yet) is denoted by $\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$ (Line $6$ of the algorithm).
-In the second scheduling, the \iocs considers the case that it can sacrifice the previously admitted EVs by canceling their reservations and allocating the freed resources to more valuable demands.
-For this purpose, the algorithm modifies the demand and valuation of the previously admitted EVs such that each demand is replaced by the EV's remaining demand, and the valuation of the EV is proportionally calculated based on the remaining demand (Line $9$ of the algorithm) so that the unit values of EVs do not change.
-Then, the \iocs runs $\mathcal{A}$ \bt{on set of} active EVs $\mathcal{M}^t$ where the corresponding gain is denoted by $\Gamma_{\mathcal{A},\mathcal{M}^t}$.
-If $\Gamma_{\mathcal{A},\mathcal{M}^t}>\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$, the \iocs forgets the previously admitted EVs and follows the second scheduling.
-
-\begin{comment}
-%We now introduce some notations and then analyze the performance of \iocs. 
-Let $\mathcal{S}_{\iocs,t}$ and $\mathcal{S}_{\opt,t}$ be set of active EVs at time slot $t$ that are selected for charging by \iocs and \opt (fix a particular optimal solution), respectively.
-Note that the set of active EVs for \iocs and \opt might be different.
-%Moreover, define  $\mathcal{U}_{\iocs,t}=\mathcal{S}_{\iocs,1}\cup\dots\cup \mathcal{S}_{\iocs,t}$ and $\mathcal{U}_{\opt,t}=\mathcal{S}_{\opt,1}\cup\dots\cup \mathcal{S}_{\opt,t}$. 
-Having $i\in\mathcal{S}_{\iocs,t}$ means that based on the updated schedule at time slot $t$, enough resources reserved for EV $i$ so that the EV will receive its demand $D_i$ before the deadline $d_i$.
-However, the schedule may change at each slot and $i\in\mathcal{S}_{\iocs,t}$ cannot be a guarantee for EV $i$ to fully receive its demand.
-In fact, users and the scheduler itself have to wait until the deadline of the EV to find out that the demand is fulfilled or not.
-This is because the scheduler may cancel some reservations in the next time slots and allocate the freed resources to other EVs.
-\end{comment}
-% (when Algorithm \ref{alg:iocs} uses the second schedule in Line $15$). 
-%Define $A_t$ as the minimum gain of \iocs when the algorithm visited time slots $1$ to $t$.
-More formally, $A_t=\sum_{i\in\mathcal{U}_{\iocs,t}}v_i$.
-$A_t$ is the minimum gain that \iocs will obtain by the end of time slot $t$, having the information of released demands up to time slot $t$.
-Notice that the algorithm may continuously improve its set of selected jobs to increase its gain such that $A_t\geq A_{t-1}, t\in\{2,\dots, T\}$.
-$A_t$ is formally defined as follows:
-
-The following theorem characterizes the competitive ratio of the \iocs in a special case. 
-\begin{thm}
-\label{thm:iocscompetitive}
-Let $\mathcal{A}$ be \ics in \iocs algorithm and $m=1$.
-Assuming that EVs are released in $b$ distinct groups where arrival time of EVs in each group are the same, the \iocs is $b\Big(1+\frac{p}{p-q}\frac{s}{s-1}\Big)$-competitive \bt{with optimal} offline solution, where $p$ is the station peak and $q=\max_i k_i, i=1,\dots ,n$.
-\end{thm}
-
-%\begin{thm}
-%\label{thm:iocscomplexity}
-%Let $\mathcal{A}$ be \ics in Line $1$ of \iocs. Then, the time complexity of the \iocs  is $O(n^2T)$. 
-%\end{thm}
-
-%\vspace{-6mm}
-\section{Simulation Results}
-			\label{sec:simul}
-%%%In this section, we report a summary of simulation experiments to evaluate the performance of the proposed algorithms.
-
-						\begin{figure*}[t]	
-				\centering
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{V-N-M2.pdf}
-						\caption{\revv{$m=2$}}
-						\label{fig:V-N-M2}
-					\end{center}
-				\end{subfigure}
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{V-N-M4.pdf}
-						\caption{\revv{$m=4$}}
-						\label{fig:V-N-M4}
-					\end{center}
-				\end{subfigure}% 	
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{V-N-M8.pdf}
-						\caption{\revv{$m=8$}}
-						\label{fig:V-N-M8}
-					\end{center}
-				\end{subfigure}% 
-				\caption{\revv{Comparison results for $2$, $4$, and $8$ CSs for fractional and integral revenue models.
-\bt{In the algorithms' name, letters ``o'', ``f'' and ``i'' indicate online, fractional and integral, respectively.
-Note that a ``non-optimal'' fractional algorithm can potentially achieve better result than an ``optimal'' integral algorithm due to higher flexibility in power allocation.} }}
-				\label{fig:V-N-M}
-%				\vspace{-3mm}
-			\end{figure*}
-%\subsection{Simulation Setup and Overview}
-\textit{Simulation Setup and Overview:} We consider charging scheduling of EVs \revv{during a period of $12$ time slots of length $1$ hour (e.g., from $08$:$00$ to $20$:$00$)}. 
-We gathered information of \revv{$12$} popular EV models in the market to use in the simulation.
-Each EV model is characterized by its battery capacity as shown in Table \ref{tb:models} and maximum charging rate.
-\revv{Tesla models can get charged with up to $100$ kW using Tesla super chargers.
-Also, all other models have rapid DC charging capability (up to $50$ kW) with CHAdeMO method.
-This setting for charging rates is in accordance with future DCFC systems that can have several fast DC chargers installed in the charging station.}
-%Battery capacity varies from \revv{$14$} kWh to \revv{$100$} kWh and the maximum charging rate from \revv{$3.3$} kW to \revv{$22$} kW. 
-%As in \cite{Tang,Chen}, we assume that arrival times follow a Poisson distribution and parking times follow an exponential distribution.
-% with the mean arrival and parking duration indicated in Table \ref{tb:a-d}. 
-The peak intervals include $08$:$00$-$10$:$00$, $12$:$00$-$14$:$00$, and $18$:$00$-$20$:$00$ \bt{according to NHTS} survey~\cite{Santos, Tang}.
-\revv{The probability \bt{of an EV's arrival} during the peak hours is two times higher than the off-peak periods.
-			Demands are uniform random values from 
-			$[\frac{1}{2}U_i,U_i]$} where $U_i$ is the battery capacity for EV $i$ in Table~\ref{tb:models}.
-\revv{The deadline of each EV is set according to slackness parameter $s$ (with default value of $1.2$), its demand and maximum charging rate of the battery as $d_i=a_i+\lceil \frac{D_is}{k_i} \rceil -1$.}
-%			The minimum electricity cost is $\$0.11$ per kWh based on US national electricity price average~\cite{kWhcost}.
-In our setting, users can submit higher prices than the minimum price in order to ensure receive their requested demand.
-			\revv{EVs are assigned to different CSs randomly and given as input to the algorithms.
-The willingness to pay by each user for one kWh of power is a random uniform number from interval $[\frac{1}{2} z,\frac{3}{2}z]$ where $z=\$0.11$ is national average price of electricity in the US\cite{kWhcost}.}
-			%The default value of local peak constraint is \rev{$100$} kW and the global peak constraint is \rev{$200$} kW. We investigate the effect of this parameter in~\cite{alinia2017online}. 
-			In the simulation, the results are plotted with $95\%$ confidence level and each point represents average result of $50$ random scenarios.
-Table \ref{tb:comparisons} explains the comparison algorithms \revv{including current implemented algorithm in Caltech ACN referred to as \iolp \cite{lee2016adaptive} and its adapted version for the fractional revenue model \folp.
-The \iolp and \folp algorithms runs as follows: at each time slot assume that there will be no further arrivals and solve the optimization problem (e.g., by commercial solvers) for the current set of EVs and their remaining demands.
-In Table \ref{tb:comparisons}, the letters ``\textsc{i}'', ``\textsc{f}'' and ``\textsc{o}'' in front of the algorithms' name refer to integral, fractional and online types, respectively.}
-
-			The measured performance metrics are total revenue, percentage of EVs that received all their demand, and total peak.
-\revv{To calculate optimal solution in integral revenue model, we used Gurobi solver \cite{optimization2013gurobi}.}
-
-\begin{table}[!t]
-				\centering
-				\caption{\revv{EV models and their battery capacity.}}
-				\label{tb:models}\revv{
-				\begin{tabular}{ | l| c | l| c |}
-					\hline
-					\textbf{Model} & \textbf{Battery} & \textbf{Model} & \textbf{Battery} \\ \hline\hline    
-				Mitsubishi i-MiEV & $16$ kWh & Citroen C-Zero & $14$ kWh \\ \hline
-				Peugeot iOn  & $16$ kWh & Honda Clarity & $25.5$ kWh\\\hline
-				Hyundai Kona & $64$ kWh & Nissan LEAF & $40$ kWh \\ \hline
-				Hyundai Ioniq & $28$ kWh & BMW i3 & $22/33$ kWh \\ \hline
-				Tesla Model S/X  & $60/100$ kWh & Kia Soul EV  & $27$ kWh\\\hline
-				\end{tabular}}
-			\end{table}
-
-%\begin{table}[h]
-%				\centering
-%				\caption{Arrival rates and mean parking times.}
-%				\label{tb:a-d}
-%				\begin{tabular}{ | l | c | c |}
-%					\hline
-%					\textbf{Interval} & \textbf{Arrival rate} & \textbf{Mean parking time} \\ \hline\hline    
-%					$08$:$00$-$10$:$00$&  $14$&$10$\\\hline  
-%					$10$:$00$-$12$:$00$&  $10$&$1/2$\\\hline 
-%					$12$:$00$-$14$:$00$&  $20$&$2$\\\hline 
-%					$14$:$00$-$18$:$00$&  $10$&$1/2$\\\hline
-%					$18$:$00$-$20$:$00$&  $20$&$2$\\\hline
-%					$20$:$00$-$24$:$00$&  $10$&$10$\\\hline
-%					$24$:$00$-$08$:$00$&  $0$&$0$\\\hline
-%				\end{tabular}
-%\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{Acronyms for the algorithms}
-\label{tb:comparisons}
-\begin{tabular}{ | l| p{6cm}|}
-\hline
-\textbf{Notation} & \textbf{Description} \\ \hline\hline
-\textsc{iOpt} & Optimal value under integral revenue model\\ \hline 	 
-\ics & Proposed offline algorithm for \MCSP under integral revenue model\\ \hline
-\fcs & Proposed \emph{optimal} algorithm for \MCSP under fractional revenue model\\\hline 
-\iocs & Proposed online algorithm for \MCSP under integral revenue model\\ \hline
-\focs & Proposed online algorithm for \MCSP under fractional revenue model\\ \hline
-\iolp & Algorithm in \cite{lee2016adaptive} (works under integral revenue model)\\ \hline
-\folp & Adaptation of algorithm in \cite{lee2016adaptive} for fractional revenue model\\ \hline
-GreedyRTL & The algorithm in \cite{Jain} for single station scenario without global peak 			constraint (works under integral revenue model)\\\hline				
-\end{tabular}
-\end{table}
-			%to simulate: Fig. 1 with M=1,4,8			
-			\begin{figure*}[t!]	
-				\centering
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{v-c.pdf}
-						\caption{\revv{Total revenue}}
-						\label{fig:v-c}
-					\end{center}
-				\end{subfigure}%
-				%\hspace{4mm}
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{p-c.pdf}
-						\caption{\revv{Actual global peak} 
-%							($p^{\mathsf{total}}=480$)
-}
-						\label{fig:p-c}
-					\end{center}
-				\end{subfigure}%  
-				%\hspace{4mm}
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{acc-c.pdf}
-						\caption{\revv{\% of full charged EVs}}
-						\label{fig:acc-c}
-					\end{center}
-				\end{subfigure}% 				
-				\caption{\revv{Comparison in terms of total revenue, actual peak, and percentage of fully charged EVs by varying local peak value}.} 
-				\label{fig:peak_local}
-%			\vspace{-4mm}
-			\end{figure*}
-\textit{\revv{Evaluation Based on Total Revenue}:}
-\revv{Fig.
-\ref{fig:V-N-M} depicts the comparison results based on total revenue under fractional and integral models} while the total number of EVs increases from \revv{$100$ to $250$} for $2$, $4$, and $8$ CSs.
-\revv{The local and global peak constraints are set to $50$ kWh and $200$ kWh, respectively.}
-
-\bt{The proposed algorithms are compared to} the optimal offline solution of integral model ($\textsc{iOPT}$) and $\iolp$.
-\bt{Note that comparison with offline optimal could be considered as a baseline comparison with the category of approximate offline algorithms in integral model~\cite{yao2016real}.}
-
-%%% which is the running online algorithm in the Caltech ACN \cite{lee2016adaptive}. 
-%The proposed algorithms for fractional revenue model, \fcs and \focs, are compared to fractional version of OLP algorithm (referred to as \folp), which is implemented in Caltech ACN  (see~\cite{alinia2017online} for details).
-Recall that \fcs is optimal offline solution.
-The notable observations  are  as  follows:  (i)  the  general  trend in scenario of Fig.~\ref{fig:V-N-M} is that  by increasing  the  number  of  EVs,  total  revenue  increases.
-This is because with more number of EVs, the scheduler has more freedom to choose more valuable EVs.
-(ii)  as  explained in Section~\ref{sec:fractional}, under fractional charging model, better results are expected due to increased scheduling flexibility in CSs.
-According to the simulation data that we extracted from Fig.~\ref{fig:V-N-M}, the gain obtained by \fcs and \focs in Fig.
-\ref{fig:V-N-M} are respectively \revv{$12\%$ and $10\%$} more than the gain of the \ics and \iocs.
-(iii) \revv{In Fig.
-\ref{fig:V-N-M2} and Fig.
-\ref{fig:V-N-M4}, sum of the local peaks is less than or equal to the global peak while in Fig.
-\ref{fig:V-N-M8} this sum is two times greater than the global peak.
-Consequently, the total revenue significantly improved when the number of CSs is increased from $2$ to $4$ while there is a slight improvement from $4$ to $8$ CSs as the global peak constraint prevents the algorithms from charging more EVs.}
- (iv) in integral revenue model, the proposed \iocs algorithm acts significantly better than \iolp.
-In particular, \iocs improves \iolp by \revv{$38\%, 36\%$, and $32\%$} for $m=2$, $m=4$ and $m=8$, respectively.
-\revv{In fractional revenue model, however, there is a very slight difference between \focs and \folp.}
- %We highlight that \iocs (\focs) is also better choice in terms of the algorithm complexity compared to \iolp (\folp).
-(v) \ics approximates \textsc{iOpt} by \revv{$97\%$, $94\%$, and $95\%$} for $m=2$, $m=4$, and $m=8$, respectively.
-On average, \iocs is \revv{$90\%$} of \textsc{iOpt} and, \focs is \revv{$94\%$} of its optimal offline solution, \fcs.
-(vi) finally, the results depict that \ics achieves much better results in practice as compared to the theoretical approximation ratio that characterizes the performance in worst-case scenario.
-
-%Also, there is a sharp decline in the gap between the online methods (i.e., \focs and \iocs) and the offline solutions (i.e., \textsc{iOpt}, \ics and \fcs).
-
-\revv{\emph{Comparison Based on Actual Peak:}} The constraint set in the \MCSP assures that any feasible solution respects the local and global peak constraints.
-% i.e., at each time slot, the electricity consumed by station $j$ is less than or equal to $p_j$ and accumulative charging rate of all stations are less than or equal to $p^\mathsf{total}$ (note that there is no assumption that $\sum_j p_j\leq p^\mathsf{total}$, in general).
-An efficient scheduling algorithm may take a further step by not only satisfying the peak constraints but to further reduce the peak as much as possible.
-The proposed offline algorithms (i.e., \ics and \fcs) apply valley-filling policy to reduce the peak.
-The  online algorithms (i.e., \iocs and \focs) do not apply the same policy as they do not have future knowledge to be able to balance allocated resources.
-%Besides, due to uncertainties in future EV charging load in online scheduling design, it is a natural heuristic to charge EVs at earliest time.
-% (i.e., setting the charging rates to the maximum feasible value at each time slot) as applied by \iocs an \focs. 
-%This heuristic works well as the uncertainty in EVs' arrival time and demands may not give a second opportunity to the scheduler to charge the current EVs at the next slots.
-Therefore, although it is expected that \iocs and \focs have higher peak values compared to the offline algorithms, the idea of valley-filling can decrease their average response time.
-% (see~\cite{alinia2017online} for the extended version of experiments).
-To investigate the effect of employed valley-filling strategy, we conducted a set of simulations by varying local peak constraints. 
-%from $50$ kWh to $120$ kWh and $200$ EVs. 
-The results of \ics is compared to \iocs and GreedyRTL~\cite{Jain} where the latter is an approximation scheduling for single station scenario with EVs having same arrival time (see the explanations after formulating the \MCSP in Section \ref{sec:problem}).
-%The GreedyRTL algorithm works under integral revenue model. Therefore, results for \fcs and \focs are not plotted. 
-%Since GreedyRTL assumes all EVs arrive at the same time, we set all arrival times to $1$.
-Moreover, we assume that global peak constraint is big enough (i.e., $\sum_{j=1}^m p_j\leq p^\textsf{total}$) such that the solution of GreedyRTL is feasible.
-We run GreedyRTL in each CS separately and combine the results.
-The results are shown in Fig.~\ref{fig:peak_local}.  
-Along with total revenue in Fig.~\ref{fig:v-c}, we also report total \emph{actual} peak in Fig.~\ref{fig:p-c} and percentage of fully charged EVs in Fig.~\ref{fig:acc-c}. 
-%As a high level trend, the results show that as the peak values increase, total revenue, total actual peak, and the number of EVs who received all their demand increase.  
-In Fig.
-\ref{fig:v-c}, the results for \ics and GreedyRTL are almost identical while \iocs is \revv{$90\%$} of the other two algorithms, on average.
-When \revv{$p_j\geq 400$}, the total revenue for \ics and GreedyRTL does not increase in Fig.
-\ref{fig:v-c} and percentage of fully charged EVs is $100$ for both algorithms according to Fig.
-\ref{fig:acc-c}.
-From this point and onward, the scheduling is not challenging for offline methods to obtain optimal answer because of resource sufficiency.
-However, it is still a challenge to control total actual peak for the system.
-As a result of valley-filling policy, the value of actual peak of \ics in Fig.
-\ref{fig:p-c} remains almost unchanged for \revv{$p_{j}\geq 400$}.
-\iocs and GreedyRTL, however, continuously increase the peak demand, since they are not using any peak shaving approach.
-% and only try to maximize total revenue. 
-%According to Fig. \ref{fig:p-c}, \iocs always reaches to the maximum peak of $\sum_j p_j$.
-
-%A glance at Table \ref{tb:models} shows that in general, an EV needs a minimum time of $2$ hours to get $70\%$ of its battery capacity if charging rate is set to the maximum value.
-However, CSs are allowed to preempt the charging at any time and set charging rate any value lower than the maximum rate.
-Therefore, average response times can be higher as it can be seen in Fig.
-\ref{fig:rt-c}.
-
-%\begin{figure}[t]	
-%\centering
-%				\begin{subfigure}[b]{0.25\textwidth}
-%					\begin{center}
-%						\includegraphics[width=\textwidth]{v-s-method1.pdf}
-%						\caption{Total revenue (\$)}
-%						\label{fig:v-s-method1}
-%					\end{center}
-%				\end{subfigure}%				
-%				\begin{subfigure}[b]{0.25\textwidth}
-%					\begin{center}
-%						\includegraphics[width=\textwidth]{rt-s-method1.pdf}
-%						\caption{Response time (hr))}
-%						\label{fig:rt-s-method1}
-%					\end{center}
-%				\end{subfigure}%  
-%\caption{The impact of slackness parameter on total revenue and response time when users react by adjusting their demand.} 
-%\label{fig:slackness1}
-%\end{figure}
-
-%\subsection{The Impact of Slackness Parameter}
-%\label{sec:sim:slack}
-%This section discusses on the benefits and disadvantages that can be brought by using slackness parameter.
-To give the charging scheduler more flexibility, a slackness parameter $s\geq 1$ is used and set by the system designer.
-%Recall that charging profile of EV $i$ is feasible if $D_i\leq k_i\frac{d_i-a_i+1}{s}$ holds.
-Since users have no control on the slackness parameter and the maximum charging rate, they must adjust their demand and availability according to the imposed slackness value.
-Based on the charging profile feasibility equation, when the slackness value increases users have two choices to react: (i) decrease the demand and depart at the desired deadline or, (ii) extend the deadline and receive the desired demand.
-In the remaining of this section, we investigate the effects of either case by simulation.
-To have a clear picture of effects caused by slackness parameter, we generated $100$ initial charging profiles $\langle a_i,d_i,v_i,D_i,k_i\rangle$ for $100$ EVs randomly and uniformly chosen from $10$ different models in Table \ref{tb:models} such that the initial profiles are set up assuming that the CS allows the charging operations to be finished at earliest possible time (i.e., $\frac{D_i}{k_i}$) with $s=1$.
-For each EV, its demand is randomly chosen from $25\%$ to $100\%$ of its battery capacity and departure in  interval $[a_i+\frac{sD_i}{k_i},T]$, where $a_i+\frac{sD_i}{k_i}$ is the earliest feasible deadline.
-Then, the EVs are uniformly assigned to $4$ CSs and should choose one of the above strategies to submit a feasible demand according to imposed slackness.
-%\begin{figure}[t]	
-%\centering
-%							\begin{subfigure}[b]{0.234\textwidth}
-%								\begin{center}
-%									\includegraphics[width=\textwidth]{v-s-method2.pdf}
-%									\caption{Total revenue (\$)}
-%									\label{fig:v-s-method2}
-%								\end{center}
-%							\end{subfigure}%
-%							\hspace{1mm}
-%							\begin{subfigure}[b]{0.236\textwidth}
-%								\begin{center}
-%									\includegraphics[width=\textwidth]{rt-s-method2.pdf}
-%									\caption{Response time (hr)}
-%									\label{fig:rt-s-method2}
-%								\end{center}
-%							\end{subfigure}% 
-%							
-%\caption{The impact of slackness parameter on total revenue and response time when users react by adjusting their deadline.} 
-%\label{fig:slackness2}
-%\end{figure}
-%			
-%\subsubsection{Case I- Adjusting Demands}
-%In this case, if the initial charging profile of an EV does not reflect a feasible charging request based on the slackness parameter, the EV owner decreases its demand so it will be able to leave CS at its initial desired deadline.
-Note that the valuation of EVs decreases proportionally, as well.
-Fig.~\ref{fig:slackness1} depicts the result under this policy applied by users.
-As it can be seen in Fig.
-\ref{fig:v-s-method1} and Fig.
-\ref{fig:rt-s-method1}, the general trend is that both total revenue and average response time decrease when slackness value increases.
-This is justifiable based on users reaction.
-When users decrease their demand, less electricity is sold which results in less revenue.
-When total demand decreases, charging can be finished in shorter time which decreases response time.
-Therefore, if users choose the first policy (adjusting their demand), total revenue degrades while response time improves.
-Notice that for the algorithms working under integral revenue model (i.e., \textsc{iOPT}, \ics and \iocs) the total revenue increases with slackness parameter at first (when $s$ grows from $1$ to $1.4$) but then it decreases when the slackness increases more (for $s>1.4$).
-%In our view, this happens because increasing the slackness in integral revenue model makes it possible to \emph{fully} charge more EVs at the beginning as the demands decrease.
-However, when the slackness increases more, it results in opposite effect because the valuation of demands decreases along with the demands' size.
-%			\subsubsection{Case II- Adjusting Deadlines}
-%			In this case, we assume that users are reluctant to decrease their desired demands.
-Instead, they can extend their departure.
-In Fig.~\ref{fig:slackness2} it can be observed that under this behavior of the users, the results are opposite as compared to the previous case (Fig.~\ref{fig:slackness1}).
-When deadlines are extended without demand decrement, the scheduler has more chance to compliance the demands through improved scheduling flexibility.
-Consequently, the total revenue increases by increasing slackness value while average response time degrades.
-%%Also observe the behavior of the online algorithms (i.e., \iocs and \focs) where both total revenue and response time decrease after a specific point that is $s=1.8$.
-When deadlines extend, more EVs have the opportunity of getting charged
-%					
-%We can conclude that when total revenue is more important than the response time, the CS should impose small values of slackness for users that apply the policy of the first case and impose higher values of slackness for the users that apply the second policy.
-The conclusion is reverse for the case that the objective is to have lower response times.
-
-			%In fact, the slackness parameter controls the maximum demand or earliest deadline that an EV can submit to the system.
-Remember that demands are in interval $[\textrm{min}\{\frac{d_i-a_i}{sk_i},U_i\},U_i]$ for EV $i$ meaning that the maximum demand that an EV can submit decreases by increasing slackness parameter.
-A reduction in total demand result in lower charging costs.
-Therefore, the total revenue decreases with higher values of parameter $s$ as in Fig.
-\ref{fig:v-s}.
-			%Also, the percentage of EVs that received all of their requested demand increases based on the same fact.
-The main goal of this simulation is to observe that obtained theoretical result on approximation ratio is confirmed as optimality gap of the SCS algorithm reduces by increasing $s$ in Fig.
-\ref{fig:v-s}.
-%\vspace{0.1mm}
-%\vspace{-4mm}
-			\section{Conclusion}
-			\label{sec:conclusion}
-This paper proposed offline and online algorithms for the EV charging scheduling problem under fractional and integral revenue models in an adaptive charging network (ACN).
-The problem is different, and more challenging than the existing single station EV charging scheduling problems since it requires respecting the aggregate peak charging demand of the ACN.
-%More importantly, the problem is online in nature in the sense that the EVs arrive in time and the scheduler has no information regarding future arrivals. 
-As the notable contributions, our proposed online algorithm for fractional revenue model achieves constant competitive ratio of $2$.
-Moreover, the offline integral algorithm achieves a theoretical bound on the optimality gap and approximates the optimum by $92\%$, on average in experiments.
-As a future work, we plan to study the problem under posted pricing mechanism where the charging station publishes the unit price of the power (which can be varied over time) and the users can accept or reject the offer.
-\revv{Another interesting future direction is to tackle the EV charging scheduling in market-based scenarios where the prices change over time.}
-%As a future work, we plan to analyze the truthfulness of the algorithms to make sure that it is a dominant strategy for the EV owners to declare their true valuations and availabilities.
-%\vspace{-4mm}
-
-%\input{intro.tex}
-%\input{rel.tex}
-%\input{sys.tex}		
-%\input{fraction.sol.tex}		
-%\input{integral.sol.tex}
-%\input{exp.tex}
-%%%\vspace{0.1mm}
-%\input{conc.tex}
-%\newpage
-%ss
-%\newpage
-%\pagestyle{empty}
-\bibliography{ref}{}
-%\vspace{-2.8mm}
-\bibliographystyle{ieeetr}
-\newpage
-{\color{white}...}    
-\newpage
-
-\input{app.tex}
-
-\begin{comment}
-\vspace{-10mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{alinia.jpg}}]{Bahram Alinia} received a B.Sc degree in computer science from University of Tabriz, Tabriz, Iran and a masters degree in Information Technology Engineering from University of Tehran, Tehran, Iran.
-He was a Researcher with the School of Computer Science, Institute for Research in Fundamental Sciences, Iran, from 2009 to 2012.
-He is currently a Ph.D.
-student in service architecture lab, Institute Telecom SudParis, France and participated in several European projects in the domain of smart grids.
-His research area includes wireless communications, energy systems, transportation electrification, algorithm design and approximation.
-\end{IEEEbiography}
-%\vspace{-30mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{hajiesmaili.jpg}}]{Mohammad H.
-Hajiesmaili} received the B.Sc.
-degree from the Department of Computer Engineering, Sharif University of Technology, Iran, in 2007, and the M.Sc.
-and Ph.D.
-degrees from the Electrical and Computer Engineering Department, University of Tehran, Iran, in 2009 and 2014, respectively.
-He was a Post-Doctoral Fellow with the Department of Information Engineering, the Chinese University of Hong Kong, from 2014 to 2016, and with the Department of Electrical and Computer Engineering, Johns Hopkins University, form 2017 to 2018.
-He is currently a Research Assistant Professor with the College of Information and Computer Sciences, University of Massachusetts, Amherst.
-His research interests include optimization, algorithm, and mechanism design in energy systems, electricity market, transportation networks, and multimedia networks.
-\end{IEEEbiography}
-%\vspace{-30mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{crespi.jpg}}]{Prof.
-No\"{e}l Crespi} holds Masters degrees from the Universities of Orsay (Paris 11) and Kent (UK), a diplome d'ing\'{e}nieur from Telecom ParisTech, a Ph.D and an Habilitation from UPMC (Paris-Sorbonne University).
-From 1993 he worked at CLIP, Bouygues Telecom and then at Orange Labs in 1995.
-He took leading roles in the creation of new services with the successful conception and launch of Orange prepaid service, and in standardisation (from rapporteurship of IN standard to coordination of all mobile standards activities for Orange).
-In 1999, he joined Nortel Networks as telephony program manager, architecting core network products for EMEA region.
-He joined Institut Mines-Telecom in 2002 and is currently professor and Program Director, leading the Service Architecture Lab.
-He coordinates the standardisation activities for Institut Mines-Telecom at ITU-T and ETSI.
-He is also an adjunct professor at KAIST (South Korea), an affiliate professor at Concordia University (Canada), and gest researcher at the University of Goettingen (Germany).
-He is the scientific director the French-Korean laboratory ILLUMINE.
-His current research interests are in Data Analytics, Internet of Things and Softwarisation.
-http://noelcrespi.wp.tem-tsp.eu/
-\end{IEEEbiography}	
-\end{comment}
-\end{document}

### 2025-03-09 TSUSC/integral.tex
move resources from other repos

--- 2019-08-26 TSC/firstSubmit/TSC.tex
@@
-\documentclass[journal]{IEEEtran}
-%\usepackage{float}
-\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-\usepackage{amssymb,amsmath}
-\usepackage[font=small,skip=10pt]{caption}
-\usepackage{subcaption}
-\usepackage{comment}
-\usepackage{color,soul}
-\usepackage{ragged2e} 
-\usepackage{algorithmicx}
-\usepackage{algpseudocode}
-\usepackage{amsthm}
-\usepackage{cite}
-\usepackage{array}
-%\usepackage{nopageno}
-\usepackage{url}
-%\usepackage{hyperref}
-%\usepackage{ulem}
-
-% *** CITATION PACKAGES ***
-%
-\usepackage{cite}
-\usepackage{color}
-\usepackage{xspace}
-\usepackage{multirow}
-\usepackage{hhline}
-%\usepackage[pdftex]{graphicx}
-
-% *** GRAPHICS RELATED PACKAGES1 ***
-%
-
-% more space
-%\usepackage{txfonts}
-\addtolength{\abovedisplayskip}{-2mm}
-\addtolength{\belowdisplayskip}{-2mm}
-\addtolength{\parskip}{-.15mm}
-%\addtolength{\arraycolsep}{-.75mm}
-\addtolength{\abovecaptionskip}{-1mm}
-\addtolength{\belowcaptionskip}{-1mm}
-%\renewcommand{\baselinestretch}{0.9}
-
-\ifCLASSINFOpdf
-\usepackage[pdftex]{graphicx}
-\graphicspath{{fig/}{../}}
-\DeclareGraphicsExtensions{.pdf,.jpeg,.png,.jpg}
-\else
-\usepackage[dvips]{graphicx}
-\graphicspath{{fig/}{../}}
-\DeclareGraphicsExtensions{.eps}
-\fi
-
-%\usepackage[caption=false,font=footnotesize]{subfig}
-%
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-%\setlength{\intextsep}{-1ex} % remove extra space above and below in-line float
-
-\renewcommand{\baselinestretch}{1}
-
-\ifodd 1
-\newcommand{\rev}[1]{{\color{black}#1}}%revise of the text
-\newcommand{\revv}[1]{{\color{black}#1}}%revise of the text
-\newcommand{\com}[1]{\textbf{\color{red}(COMMENT: #1)}}%comment of the text
-\else
-\newcommand{\rev}[1]{#1}
-\newcommand{\com}[1]{}
-\fi
-
-\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-
-%\newcommand{\opt}{\textsc{OPT}\xspace}
-\newcommand{\sa}{\textsc{SmartAllocate}}
-\newcommand{\rc}{\textsc{ReConsider}}
-\newcommand{\bc}{\textsc{BetaCover}}
-\newcommand{\ics}{\textsc{iCS}\xspace}
-\newcommand{\fcs}{\textsc{fCS}\xspace}
-\newcommand{\MCSP}{\textsf{SPAN}\xspace}
-\newcommand{\dMCSP}{\textsf{dSPAN}\xspace}
-\newcommand{\focs}{\textsc{foCS}\xspace}
-\newcommand{\iocs}{\textsc{ioCS}\xspace}
-\newcommand{\finalalg}{\textsc{ioCS+}\xspace}
-\newcommand{\opt}{\textsc{OPT}\xspace}
-\newcommand{\alg}{\textsc{ALG}\xspace}
-\newcommand{\rtl}{\textsc{GreedyRTL}\xspace}
-\newcommand{\iolp}{\textsc{ioLP}\xspace}
-\newcommand{\folp}{\textsc{foLP}\xspace}
-
-\newcommand{\be}{\begin{equation}}
-	\newcommand{\ee}{\end{equation}}
-\newcommand{\bee}{\begin{eqnarray}}
-	\newcommand{\eee}{\end{eqnarray}}
-\newcommand{\bse}{\begin{subequations}}
-	\newcommand{\ese}{\end{subequations}}
-%\def\bee#1\eee{\begin{align}#1\end{align}}
-\newcommand{\nnb}{\nonumber}
-
-\newtheorem{lem}{Lemma}
-\newtheorem{propos}{Proposition}
-\newtheorem{thm}{Theorem}
-\newtheorem{defi}{Definition}
-
-%in terms of practical feasibility and characterizing the maximum benefits of D2D load balancing is
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{corollary}[theorem]{Corollary}
-
-\makeatletter
-\newcommand\semiHuge{\@setfontsize\semiHuge{22.52}{27.38}}
-\makeatother
-\begin{document}
-	%\semiHuge
-	\title{Online EV Scheduling Algorithms for Adaptive Charging Networks with Global Peak Constraints}
-	\author{\#}
-
-	\author{Bahram Alinia, Mohammad H. Hajiesmaili, Zachary J. Lee, Noel Crespi, and Enrique Mallada
-
-		\thanks{ B. Alinia and N. Crespi are with the department of Networks and Mobile Multimedia Services (RS2M), Institut Mines-Telecom,
-			Telecom SudParis, Evry, France (e-mail: bahram.alinia@telecom-sudparis.eu, noel.crespi@mines-telecom.fr).
-
-			M. H. Hajiesmaili and E. Mallada are with the Department of Electrical and Computer Engineering, Johns Hopkins University, Baltimore, MD, USA (e-mail: \{hajiesmaili,mallada\}@jhu.edu).
-
-			Z. J. Lee is with the Department of Electrical Engineering, California Institute of Technology, Pasadena, CA, USA (e-mail: zlee@caltech.edu).
-		} }
-
-		\maketitle
-
-\begin{abstract}
-%			With the rapid growth of electric vehicles, their high demand charging jobs pose an immense challenge to the grid infrastructure. 
-			This paper tackles online scheduling of electric vehicles (EVs) in an adaptive charging network (ACN) with local and global peak constraints.
-Given the aggregate charging demand of the EVs and the peak constraints of the ACN, it might be infeasible to fully charge all the EVs according to their charging demand.
-Two alternatives in such resource-limited scenarios are to maximize the social welfare by partially charging the EVs (fractional model) or selecting a subset of  EVs and fully charge them (integral model).
-%			This paper tackles both fractional and integral models. 
-			The critical challenge is the need for online solution design since in practical scenario\revv{s} the scheduler has no information of future arrivals of EVs in a time-coupled underlying problem. 
-			For the fractional model, we devise both offline and online algorithms.
-We prove that the offline algorithm is optimal.
-Using competitive ratio as the performance measure, we prove the online algorithm achieves a competitive ratio of 2.
-The integral model, however, is more challenging since the underlying problem is NP-hard due to 0/1 selection criteria of EVs.
-Hence, efficient solution design is challenging even in offline setting.
-We devise a low-complexity primal-dual scheduling algorithm that achieves a bounded approximation ratio.
-Built upon the offline approximate algorithm, we propose an online algorithm and analyze its competitive ratio in special cases.
-Extensive trace-driven experimental results show that the performance of the proposed online algorithms is close to the offline optimum, and outperform the existing solutions.
-%			\rev{In particular, the grid and electricity providers should be aware of the electricity peak.	It is known in electricity market that the spot price is a dominating factor in billing cost.
-Hence, the utility companies need to identify a global peak constraint for the cost management purpose.
-This paper studies the online EV charging scheduling problem in a utility that offers EV charging service in a set of CSs, each of which having limited output power (referred to as local peak constraint) while taking into account the global peak constraint.
-The scheduling problem in this scenario comes with unique challenges that is not tackled previously.}
-
-%			\rev{The problem objective is to maximize total revenue of the CSs.}
-
-\end{abstract}
-		\begin{IEEEkeywords}
-			Electric Vehicle, Online Scheduling, Approximation Algorithm, Competitive Analysis
-		\end{IEEEkeywords}
-
-		\section{Introduction}
-\label{sec:intro}	
-%		\IEEEPARstart{A}{s} 
-%		a result of global warming and environmental concerns through dependence on fossil fuels, there has been a rapid proliferation in deploying renewable energy sources. 
-\IEEEPARstart{T}{o} promote quick adoption of renewable energy sources, electrification of vehicles is a trend that has been globally advocated in recent years.
-\rev{According to a Bloomberg report, EVs will account for more than half of the new car sales by $2040$~\cite{bloomberg}.
-	%the global sale of EVs increased by $80\%$ in $2015$~\cite{EVSales}.
-	%		With the significant advantage of electric vehicles (EVs) in being an environment friendly product, the global interest for EVs is rapidly growing, such that  
-	Consequently, it is expected that demand from EV charging will constitute a considerable portion of total demand. 
-	Currently, transportation consumes $29\%$ of total energy in the US, while electricity production consumes $40\%$~\cite{Zhao}.} 
-%Vehicles seen accounting for 5\% of electricity use by $2040$~\cite{EVSales2}}
-%%%\revv{\sout{Hence, rapid electrification of the vehicles makes the total electricity demand of EVs significant.}}
-
-\revv{EV charging demand is a typical example of a deferrable load, and there is often considerable flexibility in the charging schedule.
-This property makes the problem of EV charging scheduling  important and there is an extensive research along this direction in the literature (see the recent survey~\cite{mukherjee2015review}, and references therein).
-In most of the existing works, the EV charging demand is treated as a constraint to the problem in a low-load regime~\cite{Tang}.
-Motivated by rapid proliferation of EVs, this work tackles the EV scheduling in high-load regime, where given the aggregate charging demand of the EVs and the peak constraints of the charging network, it is not feasible to fully charge all the EVs according to their charging demand.}
-%		\subsection{Microgrid: Definition, Potentials, and Challenges}
-%		\label{sec:introA}
-%		A common trend in the smart grid era is to install renewable energy sources in distributed manner.
-More specifically, medium or large commercial and industrial  customers such as universities, headquarters, etc.,  can take control of their own energy consumption by local deployment of renewable sources~\cite{Hajiesmaili2016Online}.
-In this setting, the residual demand, i.e., total demand subtracted by the local renewable supply, can be acquired from the external grid.
-
-%		In addition to clean energy production, the owner of microgrid also enjoys more power sustainability and reliability, and the ability to proactively manage the energy costs.
-
-More specifically, this paper studies resource-constrained EV charging scheduling in an adaptive charging network (ACN) governed by a single operator in a campus-scale location such as a university, a headquarter\rev{s}, etc.
-\cite{wu2017two}.
-\rev{A notable example is the Caltech ACN~\cite{lee2016adaptive} where individual charging ports are organized into several \textit{charging stations} (CSs) which are dispersed in a \textit{charging network}} with the capability of adaptive charging of the EVs.
-The problem is different from EV charging scheduling \revv{with capacity constraint} in single station scenarios~\cite{Tang,Wen,Shroff2014,WTang,Chen,Xiang,Zhao,Robu} (we refer to~Section~\ref{sec:rel} for detailed discussions on related work), because of the essential need to respect the aggregate peak demand of the ACN.
-\revv{Note that, the ACN operator might limit the total power drawn from EVs to control costs~\cite{PeakPrice,Zhang2015eEnergy}, reserve the capacity for other loads, and/or participate in demand-response programs.}
-%		The EV charging loads are usually flexible and deferrable, which means that their load can be scheduled~\cite{moghaddam2017smart,DWang} to shape the total demand over time. 
-%The aim of this paper is to use the deferrable property of EVs and schedule their charging jobs, so as to \rev{maximize the revenue of the ACN}.	
-%		We refer to Section~\ref{sec:rel} for the literature review.
-
-%		In particular, real-world pricing scheme for large customers is usually a hybrid time-of-use and peak-based charging model where the peak demand can significantly impact the total energy cost, e.g., the peak price is often more than $100$ times higher than the spot price~\cite{PeakPrice,Zhang2015eEnergy}.
-Considering total aggregate demand, the peak charge portion could be as large as $20\%-80\%$ of total cost~\cite{Xu2014Reducing}.
-Consequently, a substantial cost reduction could be achieved if the total peak-demand can be proactively controlled \cite{liao2015dispatch}.
-
-%		\subsection{EV Charging Scheduling in the ACN}
-%		With the proliferation of EVs, the charging requirement of the microgrid EVs could be a portion of total microgrid electricity demand.
-
-%		To respond the electricity demand of EVs, CSs are being used where EVs can recourse to charge their battery \cite{He,liao2015dispatch,Tang}.
-There can be few to many CSs dispersed in an ACN, e.g., each for a parking garage of a building in a university campus.
-In this scenario, all parking stations are governed by a facility operator and a \textit{global} peak demand constraint is determined such that the aggregate charging demand in the entire network is less than this global peak demand \cite{DWang,Hoog}.
-
-%		The charging scheduling of the EVs with the goal of respecting the \textit{global aggregate peak constraint}, however, is a unique problem which is different from the single station EV charging scheduling.
-Most of the existing work in the literature, tackle the problem in the single parking station scenario.
-We refer to Section~\ref{sec:rel} for in-depth discussion.
-As discussed in Section \ref{sec:problem}, the global optimal solution cannot be obtained by separately solving the single station problems.
-%		On the other hand, there are only a few studies that provide global optimal solution for charging scheduling of EVs \cite{He, Moradijoz, Malhotra,Zeng,Shaaban,DWang}.
-Despite elegant results, the underlying problems, e.g., charging cost minimization problem in \cite{He}, average operating cost minimization with optimal electricity exchange capacity problem in \cite{DWang}, optimal station capacity problem in~\cite{Moradijoz}, user convenience maximization problem in~\cite{Malhotra}, joint optimization of system profit and user experience in~\cite{Shaaban,Zeng} are different from the problem studied in this paper.
-
-%		\subsection{Problem, Challenges, and Contributions}
-We consider a scenario with multiple EVs where each EV has different charging profile in terms of availability, charging demand, charging rate limit, and valuation of getting charged \revv{(for details see Section~\ref{sec:ev})}.
-We formulate an online EV charging scheduling problem with the goal of \textit{selecting} and \textit{scheduling} a subset of EVs such that: (1) the charging demand of the selected EVs are (fully or partially) satisfied; (2) the charging rate limit of EV batteries are respected, (3) the global peak constraint of the ACN is satisfied~\cite{lee2016adaptive}; (4) the local peak constraint of each CS is respected;  and finally, (5) the total revenue obtained by the valuation of the EVs is maximized.
-
-%		of maximizing the revenue of the ACN.
-The constraints are the \textit{local} peak constraint of each CS, and the \textit{global} peak constraint that limits the accumulative charging demand drawn from the entire network of stations (decided by the administration of the ACN to control total peak demand~\cite{lee2016adaptive}).
-
-There are two main challenges in the design and implementation of scheduling algorithms for EVs satisfying the goals mentioned above.
-\rev{Firstly, the problem calls for online scheduling design.} In practice, EVs arrive to the CS in online fashion and the scheduler has no information about the arrival and demand of the future EVs.
-Secondly, the underlying optimization problem in integral model is NP-hard even in offline case \rev{(see Section~\ref{sec:integral})}.
-This is because the problem is a mixed integer linear problem and a ``time-expanded'' extension of knapsack problem which is known as a classic NP-hard problem.
-In this paper, we tackle the challenge of online design by following competitive algorithm design~\cite{borodin2005online} and the challenge of NP-hardness by pursuing approximation algorithm design~\cite{approx} and make the following contributions:
-
-$\vartriangleright$ We first consider a \textit{fractional model} (where EVs can be charged partially and the revenue is proportional accordingly) and design an optimal offline scheduling algorithm. 
-%In addition to provide efficient result, the algorithm has a further elegant step to apply a valley filling strategy to further reduce the peak demand of EV charging without degrading total revenue. 
-We then develop an efficient online algorithm in which no exact or stochastic information about the future EV arrivals is given.
-Despite its simplicity, the algorithm is proved to be $2$-competitive with optimal offline solution, i.e., the revenue of the proposed online algorithm is at least $1/2$ of the offline optimum, regardless of input sequence.
-Even though there are competitive algorithms in the literature for similar problems, to the best of our knowledge, our algorithm is the first $2$-competitive algorithm \rev{which considers the} charging rate limits.
-
-$\vartriangleright$ We next study \rev{the} more challenging scenario of \rev{the} \textit{integral model}\rev{, }where EVs must receive all their demand to make revenue.
-We first propose a polynomial-time primal-dual offline approximate algorithm.
-We analyze the approximation ratio of the algorithm and by strengthening the linear relaxed version of the mixed integer problem~\cite{Carr}, we obtain an approximation ratio of $\alpha =1+\sum_{j=1}^m {\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}$, where $p_j$ is local peak constraint in station $j$, $q_j$ is the maximum charging rate of the EVs in station $j$ and $s$ is a slackness parameter.
-We highlight that when $p_j \gg q_j$ and $s$ is \rev{large} enough, then $\alpha \approx m+1$, where $m$ is the number of stations in the ACN.
-Built on the basis of the offline algorithm, we devise an online algorithm, and discuss its competitive ratio in special cases.
-%In particular, the competitive ratio is $b\Big(1+\frac{p_j}{p_j-q_j}\cdot\frac{s}{s-1}\Big)$ for single station scenario, where $b$ is the number of batches with the same arrival time.
-
-$\vartriangleright$ We conduct a set of  simulations to evaluate the performance of our proposed algorithms. 
-%For offline scheduling problem under integral charging model, the results  demonstrate that the proposed approximation algorithm is close to the optimal solution and is significantly better than the obtained theoretical bounds.
-The results of online algorithms for both integral and fractional settings are close to the optimum (within $90\%$ and $94\%$ for integral and fractional models in a representative scenario).
-In addition, our algorithm outperforms the existing scheduling algorithm in Caltech ACN~\cite{lee2016adaptive} by $35\%$ for integral revenue model.
-%The simulation section also discusses on the positive and negative effects of slackness parameter in different scenarios.
-
-%To the best of our knowledge, this problem is not addressed yet in previous studies.
-
-%		\subsection{Paper Organization}
-%		The rest of this paper is organized as follows. Section~\ref{sec:rel} reviews the literature. In Section \ref{sec:model}, the system model  and problem formulation are described. 
-%		Section \ref{sec:fractional} provides offline and online algorithms for fractional model.
-We study integral model in Section \ref{sec:integral} and propose online and offline algorithms.
-The simulation results are reported in Section~\ref{sec:simul}.
-Section~\ref{sec:conclusion} concludes the paper and highlights future directions.
-
-\section{Related Work}
-\label{sec:rel}
-\revv{There is an extensive work in the general topic of EV demand management and scheduling~\cite{mukherjee2015review} by considering different scenarios such as optimal operations with EV coordinations~\cite{mukherjee2017distributed}, EV scheduling with incorporation of renewable energy, and energy storage systems~\cite{de2017impact,shafie2018innovative}.
-In this section, we focus on the literature related to peak-constrained EV charging scheduling in single and multiple stations.}
-\subsubsection{Peak-Constrained EV Charging Scheduling}
-\label{sec:rel:peakconstrained}			
-\revv{There is an extensive literature on EV charging scheduling problem focusing on single CS~\cite{Tang,Wen}, while the local and global peak constraints are omitted or only the local peak is considered.}	As we discuss in Section~\ref{sec:problem}, the global optimal solution cannot be obtained by separately solving the single station problems.
-Hence, those solutions cannot be directly applied to the multiple CS scenario with global peak constraints.
-
-%A scenario that local and global peak constraints exist is the case that scheduling is required for a charging network for multiple CSs. 
-Studies in \cite{He,malhotra2017distributed,Moradijoz,DWang,Zeng,Shaaban} tackled charging scheduling problem in multiple CSs.
-The authors in~\cite{He} studied a global cost minimization EV charging scheduling problem.
-However, there is no limit on the maximum peak demand that the system can tolerate.
-Consequently, the peak can be arbitrary high and beyond the physical limit of the transformers in the charging station~\cite{lee2016adaptive} leading to huge electricity bills~\cite{Zhang2015eEnergy}.
-Besides, the charger devices installed in the CSs have limitation on the maximum power that they can transfer in each time unit~\cite{Tesla}.
-%We solve the issue by constraining local and global peaks.
-However, to meet the peak constraints, it may not be feasible to respond to all charging demands.
-Consequently, only a subset of EVs can be charged~\cite{Xiang}, which is captured in our problem formulation.
-\cite{DWang} considered a multi-microgrid system with global peak constraint where each microgrid has a CS and the goal is to manage electricity exchange between microgrids and main grid to minimize the operating costs.
-The authors assume that required information about individual EVs is available by forecast which may not represent a real scenario.
-A similar assumption is made in \cite{Zeng,Shaaban} where the objective is to maximize total utility of EVs and aggregators in a distribution network.
-%\rev{To be removed: In our solution, we applied a priority based selection process (based on the EVs' valuation) to respond to the demands to make sure that total peak respects the constraints.
-The selection process can be made based on different criteria such as the value of each charging request \cite{Lee, Xiang} or the priority.}
-%To avoid big billing cost in peak hours, \cite{Moradijoz} proposed a solution based on genetic algorithm to find optimal capacity and location of parking lots for serving demands in peak hours with the goal of maximizing total benefit of all stations.
-Although authors studied the problem under multiple CS setting, their solution is not applicable to our setting when the CSs are already set up.
-The authors in~\cite{malhotra2017distributed} use a similar model as in this paper, where both local and global peak constraints are considered.
-However, the authors solve the single-slot problem, which fails to provide a general solution taking into account EVs' arrival and departure times as considered in our study.
-Finally, as an alternative approach to control the peak, some studies directly target minimizing the peak~\cite{Zhao, Karfopoulos}.
-In~\cite{Zhao}, an online algorithm is developed for EV charging to minimize the peak and \cite{Karfopoulos} proposed a valley filling method by leveraging V2G in peak hours.
-Although the peak is minimized in above works, it cannot guarantee that the minimized peak is tolerable by the underlying charging network.
-
-\subsubsection{Scheduling Under Demand Uncertainty}
-A main challenge in EV scheduling problem is to cope with demand uncertainty.
-Many studies including \cite{Shroff2014,Tang,WTang,Chen,Xiang,Zhao,Robu} addressed online scheduling problem with different objectives.
-\cite{Shroff2014,Xiang} studied the problem of maximizing social welfare considering the benefit for both users and service provider.
-\cite{Tang} and \cite{WTang} developed algorithms to minimize the charging price for the CS, where the proposed algorithm in \cite{Tang} is $2.39$-competitive.
-%An online algorithm developed in \cite{Chen} to optimize overall operating profit of the service provider. 
-In \cite{Robu}, an online $2$-competitive algorithm is proposed for a single CS, assuming that EVs are capable of being discharged in a negligible amount of time.
-The assumption, however, is not realistic for EVs.
-
-Our problem in this paper is unique from above works in many respects.
-First, we study the problem in an ACN where several CSs exist, while none of the above studies solve the problem under this setting.
-Second, the previous algorithms do not work for both integral and fractional charging models.
-In addition, \cite{WTang,Chen} put no limit on the charging rate of EVs which makes their solution impractical in real scenarios.
-Also, \cite{WTang,Tang, Shroff2014,Chen,Zhao} do not consider the peak limit of the CS.
-\revv{Note that some studies~\cite{jin2017optimal} tackle the scenarios of satisfying the large demands (possibly EV demands) by participating in electricity market.
-This study assumes that the electricity price is given and fixed, and leaves the case of real-time pricing as the future direction.
-In addition, there are studies that incorporate prediction in online EV charging scheduling~\cite{wang2017predictive,chen2014distributional}.
-The prediction-based approaches achieve satisfactory performance for the scenarios that follow prediction.
-Deviation from prediction models, however, degrades their performance.
-Our approach, on the other hand, has no assumptions on modeling/prediction, and in this way, is robust against any uncertainty in the instances to the problem.}
-\revv{Finally, in~\cite{Alinia2018ITS}, we considered a simplified EV charging scheduling in fractional model without global peak constraints and devised heuristic algorithms (without competitive and approximation analysis) with on-arrival commitment for EVs to notify the amount that they can receive by their departure.
-}
-%In this paper, we consider these limitations and develop online and offline algorithms for fractional and integral revenue models in an ACN and provide theoretical bounds on their performance.
-
-%It is important to note that there is a considerable similarity between EV scheduling problem and classical job scheduling problem \cite{}.
-However, most algorithm developed for job scheduling problem  do not consider a limit on processing rate of the jobs.
-
-%\cite{Shroff2014} and \cite{Stein2012} study social welfare maximization problem while the profit of both EV owners and CS is considered.
-social welfare of the EV owners \cite{Stein2012}, charging cost \cite{Tang,WTang}, and total value of fully charged EVs \cite{Azar}).
-In addition, \cite{WTang, Tang,Shroff2014,Zhao} do not take into account the peak limitation of CS.
-}
-		\section{System Model and Problem Formulation}
-		\label{sec:model}
-
-		\subsection{System Model}
-		We consider a time-slotted system model in which the time horizon is divided to $T$ equal length slots ${t=\{1, 2, \dots ,T\}}$ (e.g., $T=24$ with time slots of $1$ hour length).
-\subsubsection{Charging Network}
-\label{sec:acn}
-Our charging network model is inspired by the Caltech ACN~\cite{lee2016adaptive} as illustrated in Fig.~\ref{fig:model-a}.
-In \rev{the} Caltech EV charging network (located in a parking garage), electricity is distributed through a two-level transformer architecture from a main switch panel to multiple EV switch panels (\rev{$2$} panels in the current Caltech ACN).
-Each EV switch panel then is connected to several chargers ($\approx$25 chargers \rev{per panel} in the Caltech ACN).
-The total power drawn from the main switch panel \rev{by} the charging network has a power limit of  $p^\mathsf{total}$, that is determined by the facility operator to control the costs, reserve the capacity for other loads, and/or participate in demand-response programs.
-%This power, where we refer to it as \emph{network power limit} is used for both EV charging as well as non-EV charging purposes (e.g., lighting, fans, etc \cite{lee2016adaptive}). 
-In other words, $p^\mathsf{total}$, which we refer to it as the \textit{global peak}, hereafter, limits the maximum aggregate EV charging load at each time slot. 
-%The global peak must be less than or equal to the value obtained by subtracting non-EV load from network power limit. 
-%When we write \emph{global peak constraint}, it refers to $p^\mathsf{total}$.  
-%$p^\mathsf{total}$ is the maximum allowed aggregated electricity consumption by all stations at each slot and limits the total transferable power to EVs.
-
-We assume that there are $m$ EV switch panels that represent $m$ CSs.
-In addition to the global peak constraint, each CS $j$ has \rev{a} capacity constraint on \rev{its} total power drawn, indicated by $p_j$, and referred to it as the \emph{local peak} constraint.
-The \rev{value of} $p_j$ is determined by the output power limit of the transformers installed between the main switch panel and EV switch panels and could be different for each EV switch panel.
-%installed chargers in a CS have limited output power to charge EVs ~\cite{Wen,Xiang,Tesla}. Therefore, for CS $j$, $p_j$ cannot be more than sum of output power of its chargers. 
-\rev{It is often observed that the charging demand of different CSs (EV switch panels in Fig.~\ref{fig:model-a}) are well below the local peak constraints.}
-To increase the flexibility due to heterogeneous charging demand of CSs, in the Caltech ACN, the global peak constraint of the main switch can be \textit{over-provisioned}, i.e., $p^\mathsf{total}$ is less than the aggregate local peaks,  ($\sum_j p_j\geq p^\mathsf{total}$).
-\rev{While this increases flexibility, it also couples the problem of EV charging scheduling across different CSs.}
-%Despite increased flexibility, the over-provisioning property, however, couples the problem of EV charging scheduling across different CSs. 
-Our solutions in this paper will be centralized ones which can be obtained through communication between the CSs and a central server as illustrated in Fig. \ref{fig:model-b}.
-
-%We make this clear by a simple example.
-Assume $m=2, p^\mathsf{total}=50$ kW and $p_1=p_2=25$ kW.
-In a specific time slot (e.g., $t=1$), the total demand in CS $1$ and $2$ is $40$ kWh and $10$ kWh, respectively.
-According to local peak constraints, it is not feasible to satisfy all demands in a single time slot.
-However, if we had $p_1=p2=50$ kW (e.g., by installing more chargers in the stations) we could be able to satisfy all demands by allocating $40 kW$ in $p_1$ and $10 kW$ in $p_2$ while still not violating $p^\mathsf{total}$.
-In case that $\sum_j p_j\leq p^\mathsf{total}$, the scheduling problem is not challenging and the solution can be obtained by solving the problem locally in each CS.
-If $\sum_j p_j> p^\mathsf{total}$ (which is the case we consider in this paper), a centralized solution is needed that can be obtained through communication between the CS and a central server as illustrated in Fig.
-\ref{fig:model-b}.
-
-\begin{figure}	
-\centering
-\minipage{0.49\textwidth}
-				\begin{subfigure}[b]{0.69\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{model-a.pdf}
-						\caption{Caltech adaptive charging network (ACN)}
-						\label{fig:model-a}
-					\end{center}
-				\end{subfigure}%
-				\begin{subfigure}[b]{0.29\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{model-b.pdf}
-						\caption{Communication model with server}
-						\label{fig:model-b}
-					\end{center}
-				\end{subfigure}%  
-\caption{System model \cite{lee2016adaptive}.} 
-\label{fig:slackness1}
-\endminipage
-\end{figure}
-
-		\begin{table} 
-			\caption{Summary of key notations}\vspace{-3mm}
-			\label{tbl:not}
-			\begin{center}
-				\begin{tabular}{|c L{6.5cm}|}
-					\hline
-					\textbf{Notation} & \textbf{Description} \\
-					\hline \hline			
-					$T$ & Number of time slots, indexed by $t$\\			
-					$m$ & Number of CSs, indexed by $j$\\			
-					$n$ & Number of EVs, indexed by $i$\\			
-					\hline
-					\hline
-					$a_i$ & Arrival time of EV $i$\\
-					$d_i$ & Departure time of EV $i$\\
-					$D_i$ & Demand of EV $i$\\
-					$v_i$ & Valuation of EV $i$ for receiving its demand $D_i$ \\
-					$k_i$ & Maximum charging rate of EV $i$\\
-					$h(i)$ & CS of EV $i$\\
-					\hline
-					\hline
-					$q_j$ & Maximum $k_i$ among all EVs in CS $j$\\
-					$p_j$ & Maximum aggregate charging rate in station $j$\\
-					$p^\mathsf{total}$ & Maximum aggregate charging rate of all stations\\
-					\hline
-					\hline
-					$y_i^t$ & \textbf{opt. variable}, The amount that EV $i$ is charged at $t$ \\
-					\hline
-				\end{tabular}
-			\end{center}
-		\end{table}
-		\subsubsection{EVs}
-		\label{sec:ev} There are $n$ EVs in the system, indexed by $i$.
-		%, all available at time $t=1$ to be charged\footnote{This assumption is reasonable for the %official buildings where the starting hour of the working day is fixed for all the %employers.
-Extensions to the case with different arrival times for the EVs, is part of the %future work.}.
-		EV $i$ is represented by a charging profile $\langle a_i,d_i,v_i,D_i,k_i\rangle$ 
-		indicating its arrival time, departure time, willingness to pay, charging demand, and maximum charging rate, respectively. 
-		%(depends on physical properties of EVs battery) 
-		More specifically, the charging of EV $i$ can be scheduled within its \emph{availability window}, $[a_i,d_i]$.
-The charging rate at each slot is bounded by $k_i$, a parameter that depends on the physical constraints of the \rev{battery and on-board charger}.
-It is assumed that the charging profile of each EV is feasible with respect to its maximum charging rate and a slackness parameter $s\geq 1$, which is the minimum ratio between the park time of the EV and its minimum charging time, i.e., ${D_i\leq k_i(d_i-a_i+1)/s}$.
-The slackness parameter is imposed to tune the flexibility of the charging scheduling.
-In extreme case $s=1$,  the flexibility is minimum and the flexibility improves as $s$ increases.
-%		Note  that  the slackness  parameter  can  impact  the  total  revenue  and  is  investigated  in  simulation  experiments  in Section~\ref{sec:simul}.
-		We assume that EV owners select their CS, perhaps the nearest to them, and so the assignments are given to the problem. Define $h(i)$ as the CS of EV~$i$.
-		Moreover, $q_j$ denotes the maximum $k_i$ among all EVs in CS $j$, i.e., $q_j=\max_{h(i)=j} k_i$. 
-		\revv{Finally, $v_i$ is the willingness to pay of EV $i$ to receive its entire demand $D_i$ before the departure time $d_i$.
-Note that in resource-constrained EV scheduling in ACN, it is not feasible to fulfill the entire demand of all EVs, hence, the problem turns into a resource allocation one with the goal of maximizing the aggregate value (a.k.a.
-utility) obtained from the EVs.
-In this way, each user can announce its willingness to pay to get charged which is denoted by $v_i$ in the system model.}
-		%We assume that there is no gain for the CS if EV $i$ is partially charged.
-
-		% where $P$ defined as $P:\xi\rightarrow  \mathcal{P}$. 
-\subsubsection{Revenue Models\label{sec:irm}} We consider two revenue models: 
-\textit{(i) Fractional revenue model}: In this model, the fractional charging is allowed, i.e., the revenue from each EV is proportional to the fraction of the demand that is fulfilled \cite{Xiang} (see Eq.~\eqref{Eq:partial_value}).
-We tackle this model in Section~\ref{sec:fractional}.
-\textit{(ii) Integral revenue model}: \rev{In this model, EV $i$ pays $v_i$ if it is fully charged and zero otherwise, i.e., there is no partial revenue for partial charging. }
-%In this model, when EV $i$ is received its demand entirely, the gain is $v_{i}$ and zero, otherwise, i.e., there is no partial revenue for fractional charging. 
-This is the model that is considered in~\cite{WTang,Shroff2014}. We tackle this model in Section~\ref{sec:integral}.
-
-		%The actual aggregated peak of all parking stations must not exceeds global peak constraint.
-
-			\begin{table*}[!t]
-			\centering
-	\vspace{-3mm}
-			\caption{Proposed algorithms and their properties.}
-			\label{tbl:algs}
-			\begin{tabular}{ | l | c | c | c |c|}
-				\hline
-				\textbf{Algorithm} & \textbf{Revenue model} & \textbf{Type} & \textbf{Optimality} & \textbf{Complexity} \\ \hline\hline    
-				\fcs& fractional& offline& Optimal & $O(n^2T+nT^2)$\\\hline 
-				\ics& integral& offline& ${\Big( 1+\sum_{j=1}^m {\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}\Big)}$-approximate & $O(nT\log T+n^2T)$ \\\hline 
-				\focs & fractional& online& $2$-competitive & $O(n^2T)$\\\hline 
-				\iocs& integral&  online& $b(1+\frac{p}{p-q}.\frac{s}{s-1})$-competitive, $(m=1)$ & $O(n^2T)$\\\hline
-			\end{tabular}
-		\end{table*}
-
-		\subsection{Problem Formulation}
-		\label{sec:problem}
-	We formulate an optimization problem to schedule the charging of the EVs with the objective of maximizing total revenue obtained from charged EVs while respecting local and global peak constraints. 
-		Note that each revenue model makes the underlying optimization problem fundamentally different. More specifically, the fractional charging model is a linear problem. 
-		Integral revenue model, however, turns the underlying charging scheduling problem to a Mixed Integer Linear Program (MILP). The integer nature originates from the $0/1$-selection decision on EVs. 
-%%%Recall that in integral revenue model the revenue is obtained given that the entire demand is fulfilled for the selected EV. 
-		%We skip the explicit formulation of the problem under integral revenue model since it could be contemplated as the linear-relaxed version of the integral revenue model (for more explanation, we refer to the discussions in Section~\ref{sec:fractional}).
-		We formulate Scheduling Problem for Adaptive charging Network (\MCSP) under fractional revenue model as follows: 
-		\bse
-		\bee
-		\MCSP: \max  && \sum\nolimits_{i=1}^n \frac{v_{i}}{D_i}\sum\nolimits_{t=a_i}^{d_i} y_i^t \label{Pobjec} \nonumber\\
-		\text{s.t.} &&\sum\nolimits_{t=a_i}^{d_i} y_i^t\leq D_i,\quad\quad\forall i, \label{ConstPartial} \\
-		&&  \sum\nolimits_{i=1}^n y_i^t\leq p^\mathsf{total} ,\quad\quad\forall t,\label{ConstTotal} \\
-		&&\sum\nolimits_{i:h(i)=j} y_i^t\leq p_j ,\quad\quad\forall t,j,\label{ConstLocal}\\
-		&& y_i^t  \leq \frac{k_i}{D_i}\sum\nolimits_{t^\prime=a_i}^{d_i} y_i^{t^\prime}, \quad\forall i,t,\label{ConstSpeed}\\
-%		&& \rev{y_i^t=0,\forall t\in\{t':t'>d_i \vee t'<a_i\}}, \\
-		\text{vars.} && y_i^t \geq 0, \quad\quad\forall i, t,\label{ConstPositive}\nonumber
-		%&& s_v(t), \quad \forall v,t
-		\eee
-		\ese
-		where $y_i^t$ is the amount that EV $i$ is charged at slot $t$. Constraint (\ref{ConstPartial}) ensures that the aggregate amount received by EV $i$ is at most the demand $D_i$. 
-%		Note that under integral revenue model, when we design our algorithm, we do not allow partial charging. 
-The global and local peak constraints are represented by constraints (\ref{ConstTotal}) and (\ref{ConstLocal}), respectively.
-
-		\revv{The constraint~\eqref{ConstSpeed} enforces the maximum charging rate of EVs.
-The straightforward way to express this constraint is to simply state that at each time slot $t$, the charging rate of EV $i$ should be less than or equal to its maximum charging rate, i.e., $y_i^t\leq k_i, \forall i,t$.
-		However, for the sake of effective algorithm design for integral model and reducing the integrality gap of the relaxed linear problem, this constraint is strengthened in the form of Eq.~\eqref{ConstSpeed}.
-		Note that in case that the aggregated charging of EV $i$ during its availability window is equal to its demand, i.e., $\sum_{t^\prime=a_i}^{d_i} y_i^{t^\prime}= D_i$, Eq.~\eqref{ConstSpeed} reduces to the simple form of $y_i^t\leq k_i$.
-		This is a natural way in approximation algorithm design to improve the performance of the algorithms under linear-relaxation based design~\cite{Carr}. }
-
-The \MCSP is an extension of formulated problem in \cite{Jain} where a job scheduling problem in cloud applications is studied.
-It turns out that the resource allocation problem in cloud systems and the EV charging scheduling problem in a \emph{single station} share similar structure.
-Indeed, each charging profile in our scheduling problem can be seen as a job in cloud system with a deadline, value, and CPU demand.
-The \MCSP, however, comes with an additional constraint~\eqref{ConstTotal}, which makes it different from the problem in \cite{Jain}, such that the existing solution \revv{will not} work in the new setting.
-More importantly, this paper studies both offline and online solutions for the problem in both fractional and integral settings, while \cite{Jain} tackles only the offline integral model.
-
-%(ii) Our solution design and analysis for integral revenue model is based on linear-relaxation primal-dual framework~\cite{Jain}.
-Therefore, in Section \ref{sec:integral} for integral revenue model, we rely on the \MCSP for the analysis of the proposed algorithms and skip to explicitly formulate the original MILP problem.
-
-%		Also, we cover the fractional revenue model and provide theoretical bounds for the proposed algorithms.
-
-%In the next two sections, we devise several algorithms to solve the \MCSP under the two revenue models (integral and fractional) and for both offline and online scenarios. 
-		\section{Fractional Revenue Model}
-		\label{sec:fractional}
-
-%\subsection{Overview of Fractional Revenue Model}
-%\label{sec:frac.overview}				
-		%In the previous section, we devised an approximation algorithm for the integral revenue model in which it is assumed that the obtained revenue is zero if the allocated resource is less than the demand.
-Although this assumption is reasonable in some scenarios,
-%To develop a solution for the \MCSP, we first consider fractional revenue model.
-%However, algorithms for integral revenue model cannot achieve the same performance as the algorithms of this section i.e., \fcs and \focs.
-
-In the fractional model, the revenue of the CS from EV $i$ is directly proportional to the amount of resource that the EV is received, i.e.,
-		\begin{equation}
-			v_i^{\mathsf{f}}=\frac{\sum_t y_i^t}{D_i}v_i,
-			\label{Eq:partial_value}
-		\end{equation}
-		where $v_i$ is the gain, if the entire demand $D_i$ is fulfilled and $v_i^{\mathsf{f}}$ is the fractional gain.
-
-%Under fractional revenue model and without the binary variable of selecting EVs, the underlying problem turns into a linear one. 
-We propose a simple algorithm, called \fcs, with low computational complexity \rev{ of $O(n^2T+nT^2)$} for the fractional model that finds the optimal solution in offline setting.
-Note that even though linear programs can be solved in polynomial time in general, the complexity of our proposed algorithm is much lower than the general linear program algorithms.
-Moreover, our proposed offline algorithm applies a valley-filling strategy to reduce the peak.
-%The details of the proposed algorithm \fcs is given in~\cite{alinia2017online}.
-In the following, the online $2$-competitive algorithm is designed, where no exact information or stochastic modeling of future inputs of the problem is available.
-A summary of proposed algorithms with their complexity and assumptions is given in Table \ref{tbl:algs}.
-
-\revv{
-\subsection{Optimal Offline Design}
-\label{sec:fopt}				
-We refer the proposed algorithm as the \fcs and summarize it as Algorithm~\ref{alg:optimal-off}.
-The \fcs works in two phases.
-In the first phase (Section~\ref{sec:ph1}), the algorithm decides on the amount of resource to be allocated to each EV within its availability window and reserves resources accordingly.
-In this phase, the details of allocation is not known.
-The actual resource allocation is done in the second phase (Section~\ref{sec:ph2}) by setting variables $y_i^t$.
-
-Before discussing the details of the algorithm, we give a definitions and introduce some notations to facilitate our algorithm design.
-
-\begin{defi}
-	Time interval $[\delta,\delta']$ is a ``super interval'' for interval $[t,t']$ if $1\leq \delta\leq t \text{~AND~} t' \leq \delta'\leq T$.
-	Moreover, $\mathcal{I}_{t,t'}$ is the set of all super intervals of interval $I_{t,t'}$ i.e., ${\mathcal{I}_{t,t'}=\{[\delta,\delta']: 1\leq \delta\leq t \text{~AND~} t'\leq \delta'\leq T\}}$.
-\end{defi}
-
-%		For example, $\mathcal{I}_{1,1}=\{I_{1,1},I_{1,2},I_{1,3},\dots ,I_{1,T}\}$. 
-The number of super intervals of an interval is at most $T^2$ and at least one (for interval $[1,T]$).
-
-Let $R_i$ be the amount of resource that is reserved for EV $i$ by the \fcs and $I_{t,t'}$ as time interval $[t,t']$.
-% with $t,t'\in\{1,\dots ,T\}$ which includes time slots $t,t+1,\dots ,t'$. 
-Then, assuming that charging demands are sorted in non-increasing order of their unit values, $A^i_j(t,t')$ is the aggregate residual resource in interval $I_{t,t'}$ at station $j$ assuming that the reservation for EVs $1$ to $i$ is accomplished.
-We now explain in detail each phase of the algorithm.
-
-\subsubsection{Phase I-Reservation\label{sec:ph1}} In Line~\ref{algline:sort1}, the EVs are sorted in a non-increasing order of their unit values.  
-%		i.e., ${v_1\slash D_1\geq v_2\slash D_2\geq\dots \geq v_n\slash D_n}$. 
-In Line~\ref{algline:setR}, the \fcs processes demand of EV $i$, picked from top of the ordered list, and sets $R_i$ as the amount to be reserved for EV $i$ which will be allocated in Phase II.
-In Line~\ref{algline:seta}, the residual resource of all intervals in set $\mathcal{I}_{a_i,d_i}$ decreases by $R_i$ and EV $i$ is added to the set of selected EVs.
-
-\begin{algorithm}[t]%\small%1
-	%\footnotesize
-	\revv{
-	\caption{\fcs}
-	\label{alg:optimal-off}
-	\DontPrintSemicolon 
-	\KwIn{$n$ EVs with their profile, local and global peak constraints $p_j, j=1,\dots ,m$ and $p^\mathsf{total}$ }
-
-	\KwOut{Optimal scheduling under fractional model}
-	\BlankLine
-
-	Sort charging requests in non-increasing order of their unit values, i.e., $\frac{v_1}{D_1}\geq \frac{v_2}{D_2}\geq\dots \geq \frac{v_n}{D_n}$\label{algline:sort1}
-
-	%	\slash\slash\textit{\texttt{Use sorted list to process demands}}
-
-	$\mathcal{L}\leftarrow \emptyset$
-
-	\slash\slash\textit{\texttt{Phase I}}
-
-	\For{$i=1,\ldots, n$}{
-		%\slash\slash\textit{\texttt{update demand and value}}
-
-		$R_i \leftarrow \min\{D_i, \min\limits_{t,t'} A^{i-1}_{h(i)}(t,t'), \forall t,t': I_{t,t'}\in\mathcal{I}_{a_i,d_i}\}$\label{algline:setR}
-
-		\If{$R_i>0$}{
-			$A^{i}_{h(i)}(t,t')\leftarrow A^{i-1}_{h(i)}(t,t')-R_i, \forall t,t': [t,t']\in\mathcal{I}_{a_i,d_i}$ \label{algline:seta}\\
-			$\mathcal{L}\leftarrow \mathcal{L}\cup{i}$
-	}}
-	\slash\slash\textit{\texttt{Phase II}}
-
-	Sort EVs in $\mathcal{L}$ in increasing order of their charging flexibility i.e., $\frac{(d_i-a_i+1)k_i}{D_i}, i\in \mathcal{L}$.
-
-	%	Let $i$ be the index of $i^{th}$ EV in list $\mathcal{L}$
-
-	\For{$i=1,\ldots, |\mathcal{L}|$}{
-
-		Pick EV $i$ from the sorted list $\mathcal{L}$.
-
-		$\emph{feasible}\leftarrow \big(\sum_{t=a_i}^{d_i}\min\{k_i,A^{i-1}_{h(i)}(t,t)\}\big) - R_i$
-
-		\If{feasible $<0$}{
-			Re-allocate previously allocated EVs such that $\emph{feasible}\geq 0$
-		}
-		Arbitrarily allocate $R_i$ to EV $i$ in its availability window\label{algline:fcsallocate}	
-	}}
-\end{algorithm}
-
-\begin{lem}
-	Provided that for EV $i$ we have 
-	\bee
-	\label{eq:ri}
-	R_i\leq\min\left\{D_i, \min_{t,t'} A^{i-1}_j(t,t'), \forall t,t': I_{t,t'}\in\mathcal{I}_{a_i,d_i}\right\}
-	\eee
-	 with a dummy $A^0_j(t,t')$ defined as
-$A^0_j(t,t')=(t'-t+1)\times\min \{p^\mathsf{total},p_{j}\},$
-	then there is a feasible allocation to allocate $R_i$ to EV $i$ in its availability window $[a_i,d_i]$. 
-	\label{thm:R_feasible}
-\end{lem}
-
-In Lemma \ref{thm:R_feasible}, $A^0_j(t,t')$ indicates the available resource when no charging request is processed in $I_{t,t'}$. 
-In Eq.~\eqref{eq:ri}, the second term, i.e., $\min_{t,t'} A^{i-1}_{j}(t,t')$, indicates the minimum remaining resource in all super intervals of interval $I_{a_i,d_i}$.
-For $i\geq 1$, $A^i_j(a_i,d_i)$ is defined as follows:
-
-\begin{equation*}
-A^i_j(a_i,d_i)=\begin{cases}
-A^{i-1}_j(a_i,d_i)-R_i & j=h(i),\\
-A^{i-1}_j(a_i,d_i) & j\neq h(i).
-\end{cases} 
-\end{equation*}
-
-The optimal value of $R_i, i=1,\dots ,n$ is set according to the following lemma:
-
-\begin{lem}
-	Given $n$ EVs sorted in a non-increasing order of the unit values, ${v_1\slash D_1\geq v_2\slash D_2\geq\dots \geq v_n\slash D_n}$, and the value of $R_i$, where $R_i$ is set after $R_{i-1}, i=2,\dots ,n$ by Eq.~\eqref{eq:ri}, then,
-	$$R_i = \min\left\{D_i, \min_{t,t'} A^{i-1}_{h(i)}(t,t'), \forall t,t':I_{t,t'}\in\mathcal{I}_{a_i,d_i}\right\},\forall i,$$
-	is the optimal value for $R_i$. 
-	\label{thm:R_star}
-\end{lem}
-
-\subsubsection{Phase II- Allocation\label{sec:ph2}} Lemma~\ref{thm:R_feasible} shows that there is a feasible scheduling to allocate the reserved resources.
-However, despite its feasibility, it is not straightforward to find such \revv{a schedule}.
-For example, assume that for EV $i$, $R_i=10$ and $k_i=4$.
-It is possible that all available resources are concentrated in a single time slot but EV $i$ cannot use more than $4$ kWh of it.
-In this situation, the previously allocated resources in interval $I_{a_i,d_i}$ should be re-allocated such that the concentrated resources are \emph{dispersed} and we have $\sum_{t=a_i}^{d_i}\sigma_t \geq R_i$ where $\sigma_t =\min\{k_i,A^{i-1}_{h(i)}(t,t)\}$ is the maximum resource that can be allocated to EV $i$ at time slot $t$.
-Since the total amount of allocated resource does not change in the interval, such dispersion is possible and can be done by a simple algorithm in which allocates $\min\{k_i,A^{i-1}_{h(i)}(t,t)\}$ starting from time slot $t=a_i$ until $R_i$ units is allocated.
-To further reduce the peak of the system, we will develop \sa\ algorithm (See Section \ref{sec:integral}) which acts more intelligent so that Line \ref{algline:fcsallocate} of the \fcs can be replaced by ``Run \sa$(i,R_i)$''.
-
-\begin{thm}
-	\label{cor:1}
-	\fcs is an optimal solution under fractional revenue model.
-\end{thm}
-
-The following theorem characterizes the complexity of \fcs.
-
-\begin{thm}
-	\label{thm:complexity}
-	The time complexity of \fcs algorithm is $O(n^2T+nT^2)$ where $n$ is the number of EVs and $T$ is number of time slots.
-\end{thm}
-}
-
-\vspace{-4mm}
-\subsection{Online Scenario}
-\label{sec:fonline}
-In this section, we devise an algorithm for the scenario that EVs arrive in online fashion.
-The scheduling decisions at each time slot are made given the information of available EVs and neither exact values nor stochastic modeling of future arrivals is available.
-Our goal is to obtain a \emph{competitive ratio} for the online algorithm.
-A scheduling algorithm $\mathcal{A}$ is $c$-competitive for $c\geq 1$ if the revenue obtained by the optimal offline algorithm is at most $c$ times the algorithm $\mathcal{A}$'s revenue for any input sequence~\cite{borodin2005online}.
-
-The proposed online algorithm for the fractional model, referred to as \focs, is listed as Algorithm~\ref{alg:focs}.
-The \focs is a simple yet efficient algorithm that always selects EVs with highest unit value to allocate as follows.
-First, the algorithm sorts the available EVs at each time slot~$t$ based on their unit value (Line~\ref{algline:sort}).
-\revv{In this step, the algorithm breaks ties based on EVs' deadline i.e., if two EVs have the same unit value, then the one with earliest deadline comes first in the sorted list.} Next, the \focs selects one EV at a time from the sorted list to allocate with maximum charging rate considering the EV's remaining demand, maximum charging rate, and peak constraints (Lines~\ref{algline:focsfor}-\ref{algline:focssety}).
-The allocation is continued until all resources are allocated or there is no more EV that could be allocated.
-%For unselected EVs, the value of $y_i^t$ will be $0$ in Line \ref{algline:focssety} of the algorithm. 
-The time complexity of the \focs is $O(n^2T)$, determined by cost of its ``\textbf{for}'' loop multiplied by total number of times that the algorithm needs to be run.
-% i.e., $T$.
-
-\vspace{-4mm}
-\begin{algorithm}%\small%1
-\footnotesize
-\caption{\focs: $\forall t\in \{1,2,\dots ,T\}$}
-\label{alg:focs}
-\DontPrintSemicolon 
-%\KwIn{Available EVs at time slot $t$, number of CSs $m$, local peak constraint $p_j, j=1,\dots ,m$, global peak constraint $p^{\textrm{total}}$}
-
-%\KwOut{A feasible charging scheduling}
-
-%$\backslash\backslash\texttt{Initialize:}$
-
-\BlankLine
-
-$\mathcal{M}^t\leftarrow$ The set of available EVs that not received their entire demand by $t$
-
-Sort EVs in set $\mathcal{M}^t$ indexed by $i=1,\dots ,|\mathcal{M}^t|$: $v_1/D_1\geq v_2/D_2\geq\dots\geq v_{|\mathcal{M}^t|}/D_{|\mathcal{M}^t|},$  \revv{where ties are broken based on users' deadline (giving priority to the users with earliest deadline) }\label{algline:sort}
-
-\For{$i=1,\ldots,|\mathcal{M}^t|\label{algline:focsfor}$}{
-
-$y_i^t\leftarrow \min\{k_i,D_i-\sum_{\tau=a_i}^{t}y_i^{\tau},p_{h(i)}-\sum_{i':h(i')=h(i)}y_{i'}^t,p^{\textrm{total}}-\sum_{i'}y_{i'}^t\}$ \label{algline:focssety}
-
-}
-
-\end{algorithm}
-Despite the simplicity of \focs which makes it easy to implement, its performance is sound and within a constant factor of the offline optimum.
-We now proceed to analyze the performance of the \focs by first giving some preliminaries.
-
-Fix an optimal scheduling and let $\mathcal{S}_{\focs,t}$ and $\mathcal{S}_{\opt,t}$ be the sets of EVs selected by the \focs and optimal solution at time slot $t$, respectively.
-Let $y_{i}^t$ and $z_{i}^t$ be the charging rate of EV $i$ set by \focs and \opt, respectively.
-We define $\Delta_{i}^t$ as follows:
-\begin{equation}
-\label{eq:delta}
-\Delta_{i}^t =
-     \begin{cases}
-       \min\{z_{i}^t-y_{i}^t,r_{i,t}\} &\quad i\in\mathcal{S}_{\opt,t},z_{i}^t>y_{i}^t, \\
-       0& \quad\text{otherwise},  \\
-     \end{cases}
-\end{equation}
-where $r_{i,t}$ is the remaining demand of EV $i$ by the end of time slot $t$.
-$\Delta_{i}^t>0$ indicates that the optimal algorithm allocated $\Delta_{i}^t$ units more resources to EV $i$ than the \focs by time slot $t$ that could be \emph{feasibly} allocated by \focs to the EV $i$.
-If for any EV $i\in\mathcal{S}_{\opt,t}$ and time slot $t\in\mathcal{T}$ we have $y_{i}^t=z_{i}^t$, i.e., $\Delta_{i}^t=0$, then the \focs is obviously optimal because it gains whatever the optimal solution gains.
-\rev{We define \textit{loss} of the \focs imposed by EV $i$ as follows:
-\begin{equation}
-\label{lBj0}
-l_{i,t}=\Delta_{i}^t\frac{v_i}{D_i},
-\end{equation}
-
-Note that the loss always takes a non-negative value as $\Delta_i^t\geq 0$.} When \focs sets charging rate of an EV less than its rate in the optimal solution, it gains $\Delta_{i}^t v_i/D_i$ less than the optimal solution from that EV.
-An upper bound for the distance between the optimal objective value (denote by \opt) and the revenue of the \focs (denote by \alg) is summation of the losses over all time slots and all EVs, i.e.,
-\begin{equation}
-\label{eq:optdist}
-\opt-\alg\leq \sum_{t=1}^T\sum_{i\in\mathcal{S}_{\opt,t}} l_{i,t}.
-\end{equation}
-
-%Notice that it is possible that an algorithm does not choose any selected EV by a particular optimal solution but still provide an optimal or near-optimal solution as there can be multiple optimal solutions.
-In particular, $\mathcal{S}_{\focs,t}\cap \mathcal{S}_{\opt,t}=\emptyset, \forall t$ cannot lead to any conclusion on the competitive ratio of the \focs.
-In addition to the amount of loss, the gain of the algorithm from charging alternative EVs should also be taken into account in comparison between \opt and \alg.
-
-Let $i\in\mathcal{S}_{\opt,t}$, $i\notin\mathcal{S}_{\alg,t}$ and $g_{i,t}$ be the gain that the \focs obtains from charging another EV instead of $i$ at time slot $t$.
-We are going to show that in the \focs, for each EV $i$ with $l_{i,t}>0$ there must be another EV (denote by $i'$) where $y_{i'}^t\geq \Delta_i^t$ and $\frac{v_{i'}}{D_{i'}}\geq \frac{v_i}{D_i}$ which means in resource allocation phase for EV $i$, the \focs allocated the difference $\Delta_i^t$ to another EV with the same or higher unit value.
-This can be proved by considering the fact that (i) the selected EVs have higher unit values than the unselected EVs, and (ii) the charging rate of the selected EVs are set to the maximum feasible value.
-Moreover, the \focs is \emph{``work-conserving''} i.e., it does not let any resource remain unused if there are some EVs that can use it.
-
-Let $g_{i,t}$ denote the gain that \focs obtains from allocating the same amount of resource that optimal algorithm allocated to EV $i$ (with size $z_i^t$) to another EV(s).
-If $\Delta_{i}^t=0$, the loss is zero. If $\Delta_{i}^t>0$, then by the charging strategy that the \focs uses we can conclude that (i) $i$ is not finished by the \focs, and (ii)
-\rev{no more resources from station $p_{h(i)}$ can be feasibly allocated,} otherwise, the \focs could allocate more resources to EV $i$.
-Therefore, the $\Delta_{i}^t$ units of the resource \rev{are} allocated to one or multiple other EVs (denote them by set $\mathcal{J}_i^t$) by the \focs.
-Moreover, it must hold that all the EVs in set $\mathcal{J}_i^t$ have a unit value equal to or higher than $v_i/D_i$ which yields $g_{i,t}\geq l_{i,t}$, otherwise, the \focs should not prefer the EVs in $\mathcal{J}_i^t$ to $i$.
-\rev{Since the result holds for any arbitrarily EV $i$, we can get the following:}
-
-\begin{equation}
-\label{eq:lg}
-\sum_{i=1}^n\sum_{t=1}^Tl_{i,t}\leq\sum_{i=1}^n\sum_{t=1}^Tg_{i,t}.
-\end{equation}
-
-Moreover, the total gain of \focs, i.e., \alg, is equal to sum of its gains from each single EV:
-\begin{equation}
-\label{eq:ALG}
-\rev{\alg= \sum_{i=1}^n\sum_{t=1}^Tg_{i,t}.}
-\end{equation}
-
-With the above discussion and using Eqs. (\ref{eq:optdist}), (\ref{eq:lg}) and (\ref{eq:ALG}) we are able to derive a competitive ratio of $2$ for the \focs.
-
-\begin{thm}
-	\label{thm:focscompetitive}
-	The \focs is $2$-competitive.
-\end{thm}
-
-\emph{Remarks:} When there is only one CS and EVs have no limit on their charging rate, the \focs is identical to the \textsc{FirstFit} algorithm ~\cite{firstfit} which is known to be $2$-competitive for classic job scheduling problem.
-However, the charging rate limitation is crucial for EV charging problem.
-Moreover, \cite{firstfit} uses \revv{a} ``charging argument'' to prove the competitive ratio of the proposed algorithm which cannot be directly applied to our problem.
-Thus, the \focs extends the \textsc{FirstFit} and makes it practical for the EV charging scenario.
-Moreover, the proof technique used for the competitive analysis of the \focs is fundamentally different from the one used in \cite{firstfit}.
-%%%Finally, in~\cite{Robu} an online $2$-competitive algorithm for EVs with partial charging is proposed.
-The competitive ratio obtained assuming that charging of EVs is instantly reversible at departure times.
-This assumption is not practical in reality since similar to charging phase, there is a discharging rate constraint for EVs.
-
-%\begin{thm}
-%\label{thm:focscomplexity}
-%
-%The time complexity of \focs is $O(nT\log n)$.
-%\end{thm}
 \section{Integral Revenue Model}
@@
 
-\emph{Dual Feasibility of the Non-selected EVs:} If there is not enough resources to fully charge EV $i$, i.e.,  $D_i>\sum_{t=a_i}^{d_i}\sigma_t$, the EV cannot be selected.
+\emph{Dual Feasibility of the Non-selected EVs:} If remaining power resource is not enough to fully charge EV $i$, i.e.,  $D_i>\sum_{t=a_i}^{d_i}\sigma_t$, the EV cannot be selected.
 However, we still need to satisfy constraint~\eqref{ConstDcover} in dual problem which is done by calling \bc($i$).
@@
 		\label{subsec:analysis}
-		In primal-dual algorithm, the goal is to design an algorithm in a way that it produces a good solution for primal problem (with primal value $\Gamma$) and a feasible solution for the dual problem (with dual value $\Lambda$).
+		In a primal-dual algorithm, the goal is to design an algorithm in a way that it produces a good solution for primal problem (with primal value $\Gamma$) and a feasible solution for the dual problem (with dual value $\Lambda$).
 Then, assuming that the primal problem is a maximization problem, to prove that the algorithm is $c-$approximation (for $c\geq 1$), the important part is to show that $\Lambda\leq c\Gamma$.
@@
 Due to the binary selection variable, the online solution design under integral model is more challenging than the one for fractional model.
-We propose the \iocs that is built upon the offline \ics.
+We propose \iocs that is built upon the offline \ics.
 In particular, the \iocs calls the \ics at each time slot for the set of available EVs, however, any algorithm that is designed for offline integral model can be used alternatively.
@@
 For this purpose, the algorithm modifies the demand and valuation of the previously admitted EVs such that each demand is replaced by the EV's remaining demand, and the valuation of the EV is proportionally calculated based on the remaining demand (Line $9$ of the algorithm) so that the unit values of EVs do not change.
-Then, the \iocs runs $\mathcal{A}$ over set of active EVs $\mathcal{M}^t$ where the corresponding gain is denoted by $\Gamma_{\mathcal{A},\mathcal{M}^t}$.
+Then, the \iocs runs $\mathcal{A}$ on set of active EVs $\mathcal{M}^t$ where the corresponding gain is denoted by $\Gamma_{\mathcal{A},\mathcal{M}^t}$.
 If $\Gamma_{\mathcal{A},\mathcal{M}^t}>\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$, the \iocs forgets the previously admitted EVs and follows the second scheduling.
@@
 
-\vspace{-6mm}
-\section{Simulation Results}
-			\label{sec:simul}
-%%%In this section, we report a summary of simulation experiments to evaluate the performance of the proposed algorithms.
-
-						\begin{figure*}[t]	
-				\centering
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{V-N-M2.pdf}
-						\caption{\revv{$m=2$}}
-						\label{fig:V-N-M2}
-					\end{center}
-				\end{subfigure}
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{V-N-M4.pdf}
-						\caption{\revv{$m=4$}}
-						\label{fig:V-N-M4}
-					\end{center}
-				\end{subfigure}% 	
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{V-N-M8.pdf}
-						\caption{\revv{$m=8$}}
-						\label{fig:V-N-M8}
-					\end{center}
-				\end{subfigure}% 
-				\caption{\revv{Comparison results for $2$, $4$, and $8$ CSs for fractional and integral revenue models.}} 
-				\label{fig:V-N-M}
-				\vspace{-3mm}
-			\end{figure*}
-%\subsection{Simulation Setup and Overview}
-\textit{Simulation Setup and Overview:} We consider charging scheduling of EVs \revv{during a period of $12$ time slots of length $1$ hour (e.g., from $08$:$00$ to $20$:$00$)}. 
-We gathered information of \revv{$12$} popular EV models in the market to use in the simulation.
-Each EV model is characterized by its battery capacity as shown in Table \ref{tb:models} and maximum charging rate.
-\revv{Tesla models can get charged with up to $100$ kW using Tesla super chargers.
-Also, all other models have rapid DC charging capability (up to $50$ kW) with CHAdeMO method.
-This setting for charging rates is in accordance with future DCFC systems that can have several fast DC chargers installed in the charging station.}
-%Battery capacity varies from \revv{$14$} kWh to \revv{$100$} kWh and the maximum charging rate from \revv{$3.3$} kW to \revv{$22$} kW. 
-%As in \cite{Tang,Chen}, we assume that arrival times follow a Poisson distribution and parking times follow an exponential distribution.
-% with the mean arrival and parking duration indicated in Table \ref{tb:a-d}. 
-The peak intervals include $08$:$00$-$10$:$00$, $12$:$00$-$14$:$00$, and $18$:$00$-$20$:$00$ which is in accordance to NHTS survey~\cite{Santos, Tang}.
-\revv{The probability of arriving an EV in the peak hours is two times higher than the off-peak periods.
-			Demands are uniform random values from 
-			$[\frac{1}{2}U_i,U_i]$} where $U_i$ is the battery capacity for EV $i$ in Table~\ref{tb:models}.
-\revv{The deadline of each EV is set according to slackness parameter $s$ (with default value of $1.2$), its demand and maximum charging rate of the battery as $d_i=a_i+\lceil \frac{D_is}{k_i} \rceil -1$.}
-%			The minimum electricity cost is $\$0.11$ per kWh based on US national electricity price average~\cite{kWhcost}.
-In our setting, users can submit higher prices than the minimum price in order to ensure receive their requested demand.
-			\revv{EVs are assigned to different CSs randomly and given as input to the algorithms.
-The willingness to pay by each user for one kWh of power is a random uniform number from interval $[\frac{1}{2} z,\frac{3}{2}z]$ where $z=\$0.11$ is national average price of electricity in the US\cite{kWhcost}.}
-			%The default value of local peak constraint is \rev{$100$} kW and the global peak constraint is \rev{$200$} kW. We investigate the effect of this parameter in~\cite{alinia2017online}. 
-			In the simulation, the results are plotted with $95\%$ confidence level and each point represents average result of $50$ random scenarios.
-Table \ref{tb:comparisons} explains the comparison algorithms \revv{including current implemented algorithm in Caltech ACN referred to as \iolp \cite{lee2016adaptive} and its adapted version for the fractional revenue model \folp.
-The \iolp and \folp algorithms runs as follows: at each time slot assume that there will be no further arrivals and solve the optimization problem (e.g., by commercial solvers) for the current set of EVs and their remaining demands.
-In Table \ref{tb:comparisons}, the letters ``\textsc{i}'', ``\textsc{f}'' and ``\textsc{o}'' in front of the algorithms' name refer to integral, fractional and online types, respectively.}
-
-			The measured performance metrics are total revenue, percentage of EVs that received all their demand, and total peak.
-\revv{To calculate optimal solution in integral revenue model, we used Gurobi solver \cite{optimization2013gurobi}.}
-
-\begin{table}[!t]
-				\centering
-				\caption{\revv{EV models and their battery capacity.}}
-				\label{tb:models}\revv{
-				\begin{tabular}{ | l| c | l| c |}
-					\hline
-					\textbf{Model} & \textbf{Battery} & \textbf{Model} & \textbf{Battery} \\ \hline\hline    
-				Mitsubishi i-MiEV & $16$ kWh & Citroen C-Zero & $14$ kWh \\ \hline
-				Peugeot iOn  & $16$ kWh & Honda Clarity & $25.5$ kWh\\\hline
-				Hyundai Kona & $64$ kWh & Nissan LEAF & $40$ kWh \\ \hline
-				Hyundai Ioniq & $28$ kWh & BMW i3 & $22/33$ kWh \\ \hline
-				Tesla Model S/X  & $60/100$ kWh & Kia Soul EV  & $27$ kWh\\\hline
-				\end{tabular}}
-			\end{table}
-
-%\begin{table}[h]
-%				\centering
-%				\caption{Arrival rates and mean parking times.}
-%				\label{tb:a-d}
-%				\begin{tabular}{ | l | c | c |}
-%					\hline
-%					\textbf{Interval} & \textbf{Arrival rate} & \textbf{Mean parking time} \\ \hline\hline    
-%					$08$:$00$-$10$:$00$&  $14$&$10$\\\hline  
-%					$10$:$00$-$12$:$00$&  $10$&$1/2$\\\hline 
-%					$12$:$00$-$14$:$00$&  $20$&$2$\\\hline 
-%					$14$:$00$-$18$:$00$&  $10$&$1/2$\\\hline
-%					$18$:$00$-$20$:$00$&  $20$&$2$\\\hline
-%					$20$:$00$-$24$:$00$&  $10$&$10$\\\hline
-%					$24$:$00$-$08$:$00$&  $0$&$0$\\\hline
-%				\end{tabular}
-%\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{Acronyms for the algorithms}
-\label{tb:comparisons}
-\begin{tabular}{ | l| p{6cm}|}
-\hline
-\textbf{Notation} & \textbf{Description} \\ \hline\hline
-\textsc{iOpt} & Optimal value under integral revenue model\\ \hline 	 
-\ics & Proposed offline algorithm for \MCSP under integral revenue model\\ \hline
-\fcs & Proposed \emph{optimal} algorithm for \MCSP under fractional revenue model\\\hline 
-\iocs & Proposed online algorithm for \MCSP under integral revenue model\\ \hline
-\focs & Proposed online algorithm for \MCSP under fractional revenue model\\ \hline
-\iolp & Algorithm in \cite{lee2016adaptive} (works under integral revenue model)\\ \hline
-\folp & Adaptation of algorithm in \cite{lee2016adaptive} for fractional revenue model\\ \hline
-GreedyRTL & The algorithm in \cite{Jain} for single station scenario without global peak 			constraint (works under integral revenue model)\\\hline				
-\end{tabular}
-\end{table}
-			%to simulate: Fig. 1 with M=1,4,8			
-			\begin{figure*}[t!]	
-				\centering
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{v-c.pdf}
-						\caption{\revv{Total revenue}}
-						\label{fig:v-c}
-					\end{center}
-				\end{subfigure}%
-				%\hspace{4mm}
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{p-c.pdf}
-						\caption{\revv{Actual global peak} 
-%							($p^{\mathsf{total}}=480$)
-}
-						\label{fig:p-c}
-					\end{center}
-				\end{subfigure}%  
-				%\hspace{4mm}
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{acc-c.pdf}
-						\caption{\revv{\% of full charged EVs}}
-						\label{fig:acc-c}
-					\end{center}
-				\end{subfigure}% 				
-				\caption{\revv{Comparison in terms of total revenue, actual peak, and percentage of fully charged EVs by varying local peak value}.} 
-				\label{fig:peak_local}
-			\vspace{-4mm}
-			\end{figure*}
-\textit{\revv{Evaluation Based on Total Revenue}:}
-\revv{Fig.
-\ref{fig:V-N-M} depicts the comparison results based on total revenue under fractional and integral models} while the total number of EVs increases from \revv{$100$ to $250$} for $2$, $4$, and $8$ CSs.
-\revv{The local and global peak constraints are set to $50$ kWh and $200$ kWh, respectively.}
-
-The proposed algorithms compared to the optimal offline solution of integral model ($\textsc{iOPT}$) and $\iolp$.%%% which is the running online algorithm in the Caltech ACN \cite{lee2016adaptive}. 
-%The proposed algorithms for fractional revenue model, \fcs and \focs, are compared to fractional version of OLP algorithm (referred to as \folp), which is implemented in Caltech ACN  (see~\cite{alinia2017online} for details).
-Recall that \fcs is optimal offline solution.
-The notable observations  are  as  follows:  (i)  the  general  trend in scenario of Fig.~\ref{fig:V-N-M} is that  by increasing  the  number  of  EVs,  total  revenue  increases.
-This is because with more number of EVs, the scheduler has more freedom to choose more valuable EVs.
-(ii)  as  explained in Section~\ref{sec:fractional}, under fractional charging model, better results are expected due to increased scheduling flexibility in CSs.
-According to the simulation data that we extracted from Fig.~\ref{fig:V-N-M}, the gain obtained by \fcs and \focs in Fig.
-\ref{fig:V-N-M} are respectively \revv{$12\%$ and $10\%$} more than the gain of the \ics and \iocs.
-(iii) \revv{In Fig.
-\ref{fig:V-N-M2} and Fig.
-\ref{fig:V-N-M4}, sum of the local peaks is less than or equal to the global peak while in Fig.
-\ref{fig:V-N-M8} this sum is two times greater than the global peak.
-Consequently, the total revenue significantly improved when the number of CSs is increased from $2$ to $4$ while there is a slight improvement from $4$ to $8$ CSs as the global peak constraint prevents the algorithms from charging more EVs.}
- (iv) in integral revenue model, the proposed \iocs algorithm acts significantly better than \iolp.
-In particular, \iocs improves \iolp by \revv{$38\%, 36\%$, and $32\%$} for $m=2$, $m=4$ and $m=8$, respectively.
-\revv{In fractional revenue model, however, there is a very slight difference between \focs and \folp.}
- %We highlight that \iocs (\focs) is also better choice in terms of the algorithm complexity compared to \iolp (\folp).
-(v) \ics approximates \textsc{iOpt} by \revv{$97\%$, $94\%$, and $95\%$} for $m=2$, $m=4$, and $m=8$, respectively.
-On average, \iocs is \revv{$90\%$} of \textsc{iOpt} and, \focs is \revv{$94\%$} of its optimal offline solution, \fcs.
-(vi) finally, the results depict that \ics achieves much better results in practice as compared to the theoretical approximation ratio that characterizes the performance in worst-case scenario.
-
-%Also, there is a sharp decline in the gap between the online methods (i.e., \focs and \iocs) and the offline solutions (i.e., \textsc{iOpt}, \ics and \fcs).
-
-\revv{\emph{Comparison Based on Actual Peak:}} The constraint set in the \MCSP assures that any feasible solution respects the local and global peak constraints.
-% i.e., at each time slot, the electricity consumed by station $j$ is less than or equal to $p_j$ and accumulative charging rate of all stations are less than or equal to $p^\mathsf{total}$ (note that there is no assumption that $\sum_j p_j\leq p^\mathsf{total}$, in general).
-An efficient scheduling algorithm may take a further step by not only satisfying the peak constraints but to further reduce the peak as much as possible.
-The proposed offline algorithms (i.e., \ics and \fcs) apply valley-filling policy to reduce the peak.
-The  online algorithms (i.e., \iocs and \focs) do not apply the same policy as they do not have future knowledge to be able to balance allocated resources.
-%Besides, due to uncertainties in future EV charging load in online scheduling design, it is a natural heuristic to charge EVs at earliest time.
-% (i.e., setting the charging rates to the maximum feasible value at each time slot) as applied by \iocs an \focs. 
-%This heuristic works well as the uncertainty in EVs' arrival time and demands may not give a second opportunity to the scheduler to charge the current EVs at the next slots.
-Therefore, although it is expected that \iocs and \focs have higher peak values compared to the offline algorithms, the idea of valley-filling can decrease their average response time.
-% (see~\cite{alinia2017online} for the extended version of experiments).
-To investigate the effect of employed valley-filling strategy, we conducted a set of simulations by varying local peak constraints. 
-%from $50$ kWh to $120$ kWh and $200$ EVs. 
-The results of \ics is compared to \iocs and GreedyRTL~\cite{Jain} where the latter is an approximation scheduling for single station scenario with EVs having same arrival time (see the explanations after formulating the \MCSP in Section \ref{sec:problem}).
-%The GreedyRTL algorithm works under integral revenue model. Therefore, results for \fcs and \focs are not plotted. 
-%Since GreedyRTL assumes all EVs arrive at the same time, we set all arrival times to $1$.
-Moreover, we assume that global peak constraint is big enough (i.e., $\sum_{j=1}^m p_j\leq p^\textsf{total}$) such that the solution of GreedyRTL is feasible.
-We run GreedyRTL in each CS separately and combine the results.
-The results are shown in Fig.~\ref{fig:peak_local}.  
-Along with total revenue in Fig.~\ref{fig:v-c}, we also report total \emph{actual} peak in Fig.~\ref{fig:p-c} and percentage of fully charged EVs in Fig.~\ref{fig:acc-c}. 
-%As a high level trend, the results show that as the peak values increase, total revenue, total actual peak, and the number of EVs who received all their demand increase.  
-In Fig.
-\ref{fig:v-c}, the results for \ics and GreedyRTL are almost identical while \iocs is \revv{$90\%$} of the other two algorithms, on average.
-When \revv{$p_j\geq 400$}, the total revenue for \ics and GreedyRTL does not increase in Fig.
-\ref{fig:v-c} and percentage of fully charged EVs is $100$ for both algorithms according to Fig.
-\ref{fig:acc-c}.
-From this point and onward, the scheduling is not challenging for offline methods to obtain optimal answer because of resource sufficiency.
-However, it is still a challenge to control total actual peak for the system.
-As a result of valley-filling policy, the value of actual peak of \ics in Fig.
-\ref{fig:p-c} remains almost unchanged for \revv{$p_{j}\geq 400$}.
-\iocs and GreedyRTL, however, continuously increase the peak demand, since they are not using any peak shaving approach.
-% and only try to maximize total revenue. 
-%According to Fig. \ref{fig:p-c}, \iocs always reaches to the maximum peak of $\sum_j p_j$.
-
-%A glance at Table \ref{tb:models} shows that in general, an EV needs a minimum time of $2$ hours to get $70\%$ of its battery capacity if charging rate is set to the maximum value.
-However, CSs are allowed to preempt the charging at any time and set charging rate any value lower than the maximum rate.
-Therefore, average response times can be higher as it can be seen in Fig.
-\ref{fig:rt-c}.
-
-%\begin{figure}[t]	
-%\centering
-%				\begin{subfigure}[b]{0.25\textwidth}
-%					\begin{center}
-%						\includegraphics[width=\textwidth]{v-s-method1.pdf}
-%						\caption{Total revenue (\$)}
-%						\label{fig:v-s-method1}
-%					\end{center}
-%				\end{subfigure}%				
-%				\begin{subfigure}[b]{0.25\textwidth}
-%					\begin{center}
-%						\includegraphics[width=\textwidth]{rt-s-method1.pdf}
-%						\caption{Response time (hr))}
-%						\label{fig:rt-s-method1}
-%					\end{center}
-%				\end{subfigure}%  
-%\caption{The impact of slackness parameter on total revenue and response time when users react by adjusting their demand.} 
-%\label{fig:slackness1}
-%\end{figure}
-
-%\subsection{The Impact of Slackness Parameter}
-%\label{sec:sim:slack}
-%This section discusses on the benefits and disadvantages that can be brought by using slackness parameter.
-To give the charging scheduler more flexibility, a slackness parameter $s\geq 1$ is used and set by the system designer.
-%Recall that charging profile of EV $i$ is feasible if $D_i\leq k_i\frac{d_i-a_i+1}{s}$ holds.
-Since users have no control on the slackness parameter and the maximum charging rate, they must adjust their demand and availability according to the imposed slackness value.
-Based on the charging profile feasibility equation, when the slackness value increases users have two choices to react: (i) decrease the demand and depart at the desired deadline or, (ii) extend the deadline and receive the desired demand.
-In the remaining of this section, we investigate the effects of either case by simulation.
-To have a clear picture of effects caused by slackness parameter, we generated $100$ initial charging profiles $\langle a_i,d_i,v_i,D_i,k_i\rangle$ for $100$ EVs randomly and uniformly chosen from $10$ different models in Table \ref{tb:models} such that the initial profiles are set up assuming that the CS allows the charging operations to be finished at earliest possible time (i.e., $\frac{D_i}{k_i}$) with $s=1$.
-For each EV, its demand is randomly chosen from $25\%$ to $100\%$ of its battery capacity and departure in  interval $[a_i+\frac{sD_i}{k_i},T]$, where $a_i+\frac{sD_i}{k_i}$ is the earliest feasible deadline.
-Then, the EVs are uniformly assigned to $4$ CSs and should choose one of the above strategies to submit a feasible demand according to imposed slackness.
-%\begin{figure}[t]	
-%\centering
-%							\begin{subfigure}[b]{0.234\textwidth}
-%								\begin{center}
-%									\includegraphics[width=\textwidth]{v-s-method2.pdf}
-%									\caption{Total revenue (\$)}
-%									\label{fig:v-s-method2}
-%								\end{center}
-%							\end{subfigure}%
-%							\hspace{1mm}
-%							\begin{subfigure}[b]{0.236\textwidth}
-%								\begin{center}
-%									\includegraphics[width=\textwidth]{rt-s-method2.pdf}
-%									\caption{Response time (hr)}
-%									\label{fig:rt-s-method2}
-%								\end{center}
-%							\end{subfigure}% 
-%							
-%\caption{The impact of slackness parameter on total revenue and response time when users react by adjusting their deadline.} 
-%\label{fig:slackness2}
-%\end{figure}
-%			
-%\subsubsection{Case I- Adjusting Demands}
-%In this case, if the initial charging profile of an EV does not reflect a feasible charging request based on the slackness parameter, the EV owner decreases its demand so it will be able to leave CS at its initial desired deadline.
-Note that the valuation of EVs decreases proportionally, as well.
-Fig.~\ref{fig:slackness1} depicts the result under this policy applied by users.
-As it can be seen in Fig.
-\ref{fig:v-s-method1} and Fig.
-\ref{fig:rt-s-method1}, the general trend is that both total revenue and average response time decrease when slackness value increases.
-This is justifiable based on users reaction.
-When users decrease their demand, less electricity is sold which results in less revenue.
-When total demand decreases, charging can be finished in shorter time which decreases response time.
-Therefore, if users choose the first policy (adjusting their demand), total revenue degrades while response time improves.
-Notice that for the algorithms working under integral revenue model (i.e., \textsc{iOPT}, \ics and \iocs) the total revenue increases with slackness parameter at first (when $s$ grows from $1$ to $1.4$) but then it decreases when the slackness increases more (for $s>1.4$).
-%In our view, this happens because increasing the slackness in integral revenue model makes it possible to \emph{fully} charge more EVs at the beginning as the demands decrease.
-However, when the slackness increases more, it results in opposite effect because the valuation of demands decreases along with the demands' size.
-%			\subsubsection{Case II- Adjusting Deadlines}
-%			In this case, we assume that users are reluctant to decrease their desired demands.
-Instead, they can extend their departure.
-In Fig.~\ref{fig:slackness2} it can be observed that under this behavior of the users, the results are opposite as compared to the previous case (Fig.~\ref{fig:slackness1}).
-When deadlines are extended without demand decrement, the scheduler has more chance to compliance the demands through improved scheduling flexibility.
-Consequently, the total revenue increases by increasing slackness value while average response time degrades.
-%%Also observe the behavior of the online algorithms (i.e., \iocs and \focs) where both total revenue and response time decrease after a specific point that is $s=1.8$.
-When deadlines extend, more EVs have the opportunity of getting charged
-%					
-%We can conclude that when total revenue is more important than the response time, the CS should impose small values of slackness for users that apply the policy of the first case and impose higher values of slackness for the users that apply the second policy.
-The conclusion is reverse for the case that the objective is to have lower response times.
-
-			%In fact, the slackness parameter controls the maximum demand or earliest deadline that an EV can submit to the system.
-Remember that demands are in interval $[\textrm{min}\{\frac{d_i-a_i}{sk_i},U_i\},U_i]$ for EV $i$ meaning that the maximum demand that an EV can submit decreases by increasing slackness parameter.
-A reduction in total demand result in lower charging costs.
-Therefore, the total revenue decreases with higher values of parameter $s$ as in Fig.
-\ref{fig:v-s}.
-			%Also, the percentage of EVs that received all of their requested demand increases based on the same fact.
-The main goal of this simulation is to observe that obtained theoretical result on approximation ratio is confirmed as optimality gap of the SCS algorithm reduces by increasing $s$ in Fig.
-\ref{fig:v-s}.
-\vspace{0.1mm}
-\vspace{-4mm}
-			\section{Conclusion}
-			\label{sec:conclusion}
-This paper proposed offline and online algorithms for the EV charging scheduling problem under fractional and integral revenue models in an adaptive charging network (ACN).
-The problem is different, and more challenging than the existing single station EV charging scheduling problems since it requires respecting the aggregate peak charging demand of the ACN.
-%More importantly, the problem is online in nature in the sense that the EVs arrive in time and the scheduler has no information regarding future arrivals. 
-As the notable contributions, our proposed online algorithm for fractional revenue model achieves constant competitive ratio of $2$.
-Moreover, the offline integral algorithm achieves a theoretical bound on the optimality gap and approximates the optimum by $92\%$, on average in experiments.
-As a future work, we plan to study the problem under posted pricing mechanism where the charging station publishes the unit price of the power (which can be varied over time) and the users can accept or reject the offer.
-\revv{Another interesting future direction is to tackle the EV charging scheduling in market-based scenarios where the prices change over time.}
-%As a future work, we plan to analyze the truthfulness of the algorithms to make sure that it is a dominant strategy for the EV owners to declare their true valuations and availabilities.
-\vspace{-4mm}
-
-%\input{intro.tex}
-%\input{rel.tex}
-%\input{sys.tex}		
-%\input{fraction.sol.tex}		
-%\input{integral.sol.tex}
-%\input{exp.tex}
-%%%\vspace{0.1mm}
-%\input{conc.tex}
-%\newpage
-%ss
-%\newpage
-%\pagestyle{empty}
-\bibliography{ref}{}
-\vspace{-2.8mm}
-\bibliographystyle{ieeetr}
-
-\input{app.tex}
-
-\begin{comment}
-\vspace{-10mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{alinia.jpg}}]{Bahram Alinia} received a B.Sc degree in computer science from University of Tabriz, Tabriz, Iran and a masters degree in Information Technology Engineering from University of Tehran, Tehran, Iran.
-He was a Researcher with the School of Computer Science, Institute for Research in Fundamental Sciences, Iran, from 2009 to 2012.
-He is currently a Ph.D.
-student in service architecture lab, Institute Telecom SudParis, France and participated in several European projects in the domain of smart grids.
-His research area includes wireless communications, energy systems, transportation electrification, algorithm design and approximation.
-\end{IEEEbiography}
-%\vspace{-30mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{hajiesmaili.jpg}}]{Mohammad H.
-Hajiesmaili} received the B.Sc.
-degree from the Department of Computer Engineering, Sharif University of Technology, Iran, in 2007, and the M.Sc.
-and Ph.D.
-degrees from the Electrical and Computer Engineering Department, University of Tehran, Iran, in 2009 and 2014, respectively.
-He was a Post-Doctoral Fellow with the Department of Information Engineering, the Chinese University of Hong Kong, from 2014 to 2016, and with the Department of Electrical and Computer Engineering, Johns Hopkins University, form 2017 to 2018.
-He is currently a Research Assistant Professor with the College of Information and Computer Sciences, University of Massachusetts, Amherst.
-His research interests include optimization, algorithm, and mechanism design in energy systems, electricity market, transportation networks, and multimedia networks.
-\end{IEEEbiography}
-%\vspace{-30mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{crespi.jpg}}]{Prof.
-No\"{e}l Crespi} holds Masters degrees from the Universities of Orsay (Paris 11) and Kent (UK), a diplome d'ing\'{e}nieur from Telecom ParisTech, a Ph.D and an Habilitation from UPMC (Paris-Sorbonne University).
-From 1993 he worked at CLIP, Bouygues Telecom and then at Orange Labs in 1995.
-He took leading roles in the creation of new services with the successful conception and launch of Orange prepaid service, and in standardisation (from rapporteurship of IN standard to coordination of all mobile standards activities for Orange).
-In 1999, he joined Nortel Networks as telephony program manager, architecting core network products for EMEA region.
-He joined Institut Mines-Telecom in 2002 and is currently professor and Program Director, leading the Service Architecture Lab.
-He coordinates the standardisation activities for Institut Mines-Telecom at ITU-T and ETSI.
-He is also an adjunct professor at KAIST (South Korea), an affiliate professor at Concordia University (Canada), and gest researcher at the University of Goettingen (Germany).
-He is the scientific director the French-Korean laboratory ILLUMINE.
-His current research interests are in Data Analytics, Internet of Things and Softwarisation.
-http://noelcrespi.wp.tem-tsp.eu/
-\end{IEEEbiography}	
-\end{comment}
-\end{document}
+%\vspace{-6mm}

### 2025-03-09 TSUSC/intro.tex
move resources from other repos

--- 2019-08-27 TSC/R1/TSC.tex
@@
-\documentclass[journal]{IEEEtran}
-%\usepackage{float}
-\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-\usepackage{amssymb,amsmath}
-\usepackage[font=small,skip=10pt]{caption}
-\usepackage{subcaption}
-\usepackage{comment}
-\usepackage{color,soul}
-%\usepackage{ragged2e} 
-\usepackage{algorithmicx}
-\usepackage{algpseudocode}
-\usepackage{amsthm}
-\usepackage{cite}
-\usepackage{array}
-%\usepackage{nopageno}
-\usepackage{url}
-%\usepackage{hyperref}
-%\usepackage{ulem}
-
-% *** CITATION PACKAGES ***
-%
-\usepackage{cite}
-\usepackage{color}
-\usepackage{xspace}
-\usepackage{multirow}
-\usepackage{hhline}
-%\usepackage[pdftex]{graphicx}
-
-% *** GRAPHICS RELATED PACKAGES1 ***
-%
-
-% more space
-%\usepackage{txfonts}
-\addtolength{\abovedisplayskip}{-2mm}
-\addtolength{\belowdisplayskip}{-2mm}
-\addtolength{\parskip}{-.15mm}
-%\addtolength{\arraycolsep}{-.75mm}
-\addtolength{\abovecaptionskip}{-1mm}
-\addtolength{\belowcaptionskip}{-1mm}
-%\renewcommand{\baselinestretch}{0.9}
-
-\ifCLASSINFOpdf
-\usepackage[pdftex]{graphicx}
-\graphicspath{{fig/}{../}}
-\DeclareGraphicsExtensions{.pdf,.jpeg,.png,.jpg}
-\else
-\usepackage[dvips]{graphicx}
-\graphicspath{{fig/}{../}}
-\DeclareGraphicsExtensions{.eps}
-\fi
-
-%\usepackage[caption=false,font=footnotesize]{subfig}
-%
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-%\setlength{\intextsep}{-1ex} % remove extra space above and below in-line float
-
-\renewcommand{\baselinestretch}{1}
-
-\ifodd 1
-\newcommand{\bt}[1]{{\color{blue}#1}}%revise of the text
-\newcommand{\rev}[1]{{\color{black}#1}}%revise of the text
-\newcommand{\revv}[1]{{\color{black}#1}}%revise of the text
-\newcommand{\com}[1]{\textbf{\color{red}(COMMENT: #1)}}%comment of the text
-\else
-\newcommand{\bt}[1]{#1}
-\newcommand{\rev}[1]{#1}
-\newcommand{\com}[1]{}
-\fi
-
-\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-
-%\newcommand{\opt}{\textsc{OPT}\xspace}
-\newcommand{\sa}{\textsc{SmartAllocate}}
-\newcommand{\rc}{\textsc{ReConsider}}
-\newcommand{\bc}{\textsc{BetaCover}}
-\newcommand{\ics}{\textsc{iCS}\xspace}
-\newcommand{\fcs}{\textsc{fCS}\xspace}
-\newcommand{\MCSP}{\textsf{SPAN}\xspace}
-\newcommand{\dMCSP}{\textsf{dSPAN}\xspace}
-\newcommand{\focs}{\textsc{foCS}\xspace}
-\newcommand{\iocs}{\textsc{ioCS}\xspace}
-\newcommand{\finalalg}{\textsc{ioCS+}\xspace}
-\newcommand{\opt}{\textsc{OPT}\xspace}
-\newcommand{\alg}{\textsc{ALG}\xspace}
-\newcommand{\rtl}{\textsc{GreedyRTL}\xspace}
-\newcommand{\iolp}{\textsc{ioLP}\xspace}
-\newcommand{\folp}{\textsc{foLP}\xspace}
-
-\newcommand{\be}{\begin{equation}}
-	\newcommand{\ee}{\end{equation}}
-\newcommand{\bee}{\begin{eqnarray}}
-	\newcommand{\eee}{\end{eqnarray}}
-\newcommand{\bse}{\begin{subequations}}
-	\newcommand{\ese}{\end{subequations}}
-%\def\bee#1\eee{\begin{align}#1\end{align}}
-\newcommand{\nnb}{\nonumber}
-
-\newtheorem{lem}{Lemma}
-\newtheorem{propos}{Proposition}
-\newtheorem{thm}{Theorem}
-\newtheorem{defi}{Definition}
-
-%in terms of practical feasibility and characterizing the maximum benefits of D2D load balancing is
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{corollary}[theorem]{Corollary}
-
-\makeatletter
-\newcommand\semiHuge{\@setfontsize\semiHuge{22.52}{27.38}}
-\makeatother
-\begin{document}
-	%\semiHuge
-	\title{Online EV Scheduling Algorithms for Adaptive Charging Networks with Global Peak Constraints}
-	\author{\#}
-
-	\author{Bahram Alinia, Mohammad H. Hajiesmaili, Zachary J. Lee, Noel Crespi, and Enrique Mallada
-
-		\thanks{ B. Alinia and N. Crespi are with the department of Networks and Mobile Multimedia Services (RS2M), Institut Mines-Telecom,
-			Telecom SudParis, Evry, France (e-mail: bahram.alinia@telecom-sudparis.eu, noel.crespi@mines-telecom.fr).
-
-			M. H. Hajiesmaili and E. Mallada are with the Department of Electrical and Computer Engineering, Johns Hopkins University, Baltimore, MD, USA (e-mail: \{hajiesmaili,mallada\}@jhu.edu).
-
-			Z. J. Lee is with the Department of Electrical Engineering, California Institute of Technology, Pasadena, CA, USA (e-mail: zlee@caltech.edu).
-		} }
-
-		\maketitle
-
-\begin{abstract}
-%			With the rapid growth of electric vehicles, their high demand charging jobs pose an immense challenge to the grid infrastructure. 
-			This paper tackles online scheduling of electric vehicles (EVs) in an adaptive charging network (ACN) with local and global peak constraints.
-Given the aggregate charging demand of the EVs and the peak constraints of the ACN, it might be infeasible to fully charge all the EVs according to their charging demand.
-Two alternatives in such resource-limited scenarios are to maximize the social welfare by partially charging the EVs (fractional model) or selecting a subset of  EVs and fully charge them (integral model).
-%			This paper tackles both fractional and integral models. 
-			The critical challenge is the need for online solution design since in practical scenario\revv{s} the scheduler has no information of future arrivals of EVs in a time-coupled underlying problem. 
-			For the fractional model, we devise both offline and online algorithms.
-We prove that the offline algorithm is optimal.
-Using competitive ratio as the performance measure, we prove the online algorithm achieves a competitive ratio of 2.
-The integral model, however, is more challenging since the underlying problem is \bt{strongly} NP-hard due to 0/1 selection criteria of EVs.
-Hence, efficient solution design is challenging even in offline setting.
-We devise a low-complexity primal-dual scheduling algorithm that achieves a bounded approximation ratio.
-Built upon the offline approximate algorithm, we propose an online algorithm and analyze its competitive ratio in special cases.
-Extensive trace-driven experimental results show that the performance of the proposed online algorithms is close to the offline optimum, and outperform the existing solutions.
-%			\rev{In particular, the grid and electricity providers should be aware of the electricity peak.	It is known in electricity market that the spot price is a dominating factor in billing cost.
-Hence, the utility companies need to identify a global peak constraint for the cost management purpose.
-This paper studies the online EV charging scheduling problem in a utility that offers EV charging service in a set of CSs, each of which having limited output power (referred to as local peak constraint) while taking into account the global peak constraint.
-The scheduling problem in this scenario comes with unique challenges that is not tackled previously.}
-
-%			\rev{The problem objective is to maximize total revenue of the CSs.}
-
-\end{abstract}
-		\begin{IEEEkeywords}
-			Electric Vehicle, Online Scheduling, Approximation Algorithm, Competitive Analysis
-		\end{IEEEkeywords}
-
 \section{Introduction}
@@
 \cite{wu2017two}.
-\rev{A notable example is the Caltech ACN~\cite{lee2016adaptive} where individual charging ports are organized into several \textit{charging stations} (CSs) which are dispersed in a \textit{charging network}} with the capability of adaptive charging of the EVs.
+\rev{A notable example is the Caltech ACN~\cite{lee2016adaptive,lee2018adaptive} where individual charging ports are organized into several \textit{charging stations} (CSs) which are dispersed in a \textit{charging network}} with the capability of adaptive charging of the EVs.
 The problem is different from EV charging scheduling \revv{with capacity constraint} in single station scenarios~\cite{Tang,Wen,Shroff2014,WTang,Chen,Xiang,Zhao,Robu} (we refer to~Section~\ref{sec:rel} for detailed discussions on related work), because of the essential need to respect the aggregate peak demand of the ACN.
@@
 We consider a scenario with multiple EVs where each EV has different charging profile in terms of availability, charging demand, charging rate limit, and valuation of getting charged \revv{(for details see Section~\ref{sec:ev})}.
-We formulate an online EV charging scheduling problem with the goal of \textit{selecting} and \textit{scheduling} a subset of EVs such that: (1) the charging demand of the selected EVs are (fully or partially) satisfied; (2) the charging rate limit of EV batteries are respected, (3) the global peak constraint of the ACN is satisfied~\cite{lee2016adaptive}; (4) the local peak constraint of each CS is respected;  and finally, (5) the total revenue obtained by the valuation of the EVs is maximized.
+We formulate an online EV charging scheduling problem with the goal of \textit{selecting} and \textit{scheduling} a subset of EVs such that: (1) the charging demand of the selected EVs are (fully or partially) satisfied; (2) the charging rate limit of EV batteries are respected, (3) the global peak constraint of the ACN is satisfied~\cite{lee2018adaptive}; (4) the local peak constraint of each CS is respected;  and finally, (5) the total revenue obtained by the valuation of the EVs is maximized.
 
 %		of maximizing the revenue of the ACN.
-The constraints are the \textit{local} peak constraint of each CS, and the \textit{global} peak constraint that limits the accumulative charging demand drawn from the entire network of stations (decided by the administration of the ACN to control total peak demand~\cite{lee2016adaptive}).
+The constraints are the \textit{local} peak constraint of each CS, and the \textit{global} peak constraint that limits the accumulative charging demand drawn from the entire network of stations (decided by the administration of the ACN to control total peak demand~\cite{lee2018adaptive}).
 
@@
 \rev{Firstly, the problem calls for online scheduling design.} In practice, EVs arrive to the CS in online fashion and the scheduler has no information about the arrival and demand of the future EVs.
-Secondly, the underlying optimization problem in integral model is \bt{strongly} NP-hard even in offline case \rev{(see Section~\ref{sec:integral})}.
+Secondly, the underlying optimization problem in integral model is strongly NP-hard even in offline case \rev{(see Section~\ref{sec:integral})}.
 This is because the problem is a mixed integer linear problem and a ``time-expanded'' extension of knapsack problem which is known as a classic NP-hard problem.
@@
 Despite its simplicity, the algorithm is proved to be $2$-competitive with optimal offline solution, i.e., the revenue of the proposed online algorithm is at least $1/2$ of the offline optimum, regardless of input sequence.
-Even though there are competitive algorithms in the literature for similar problems, to the best of our knowledge, our algorithm is the first $2$-competitive algorithm \rev{which considers the} charging rate limits.
+Even though there are competitive algorithms in the literature for similar problems, to the best of our knowledge, our algorithm is the first $2$-competitive algorithm which considers the charging rate limits.
 
-$\vartriangleright$ We next study \rev{the} more challenging scenario of \rev{the} \textit{integral model}\rev{, }where EVs must receive all their demand to make revenue.
+$\vartriangleright$ We next study \rev{the} more challenging scenario of the \textit{integral model}, where EVs must receive all their demand to make revenue.
 We first propose a polynomial-time primal-dual offline approximate algorithm.
@@
 The results of online algorithms for both integral and fractional settings are close to the optimum (within $90\%$ and $94\%$ for integral and fractional models in a representative scenario).
-In addition, our algorithm outperforms the existing scheduling algorithm in Caltech ACN~\cite{lee2016adaptive} by $35\%$ for integral revenue model.
+In addition, our algorithm outperforms the existing scheduling algorithm in Caltech ACN~\cite{lee2018adaptive} by $35\%$ for integral revenue model.
 
-\bt{This paper represents follow-up work to our previous study~\cite{alinia2018competitive}, where we address a simplified version of the problems studied in this paper in fractional revenue model.
+This paper represents follow-up work to our previous study~\cite{alinia2018competitive}, where we address a simplified version of the problems studied in this paper in fractional revenue model.
 The competitive analysis in~\cite{alinia2018competitive} is done under the assumption that all EVs have the same maximum charging rate.
@@
 In this paper, we extend the results and propose a 2-competitive online algorithm with no assumption on the input parameters.
-Also, the current study investigates both fractional and integral revenue models while considering global peak constraint in the formulation and addressing multiple charging station scenario.
-Last, we consider more realistic trace-driven experiments in this paper and compare the results to an existing real-world scheduling algorithm.}
+Also, this paper investigates both fractional and integral models while considering global peak constraint and addressing multiple charging station scenario.
+Last, we consider more realistic trace-driven experiments in this paper and compare the results to an existing real-world scheduling algorithm.
 %The simulation section also discusses on the positive and negative effects of slackness parameter in different scenarios.
@@
 Section~\ref{sec:conclusion} concludes the paper and highlights future directions.
-
-\section{Related Work}
-\label{sec:rel}
-\revv{There is an extensive work in the general topic of EV demand management and scheduling~\cite{mukherjee2015review} by considering different scenarios such as optimal operations with EV coordination and congestion management~\cite{mukherjee2017distributed,rigas2013congestion,hu2013coordinated}, EV scheduling with incorporation of renewable energy, and energy storage systems~\cite{de2017impact,shafie2018innovative}, and pricing and bidding~\cite{huang2014distribution,hou2019bidding} In this section, we focus on the literature related to peak-constrained EV charging scheduling in single and multiple stations.}
-\subsubsection{Peak-Constrained EV Charging Scheduling}
-\label{sec:rel:peakconstrained}			
-\revv{There is an extensive literature on EV charging scheduling problem focusing on single CS~\cite{Tang,Wen}, while the local and global peak constraints are omitted or only the local peak is considered.}	As we discuss in Section~\ref{sec:problem}, the global optimal solution cannot be obtained by separately solving the single station problems.
-Hence, those solutions cannot be directly applied to the multiple CS scenario with global peak constraints.
-
-%A scenario that local and global peak constraints exist is the case that scheduling is required for a charging network for multiple CSs. 
-Studies in \cite{He,malhotra2017distributed,Moradijoz,DWang,Zeng,Shaaban} tackled charging scheduling problem in multiple CSs.
-The authors in~\cite{He} studied a global cost minimization EV charging scheduling problem.
-However, there is no limit on the maximum peak demand that the system can tolerate.
-Consequently, the peak can be arbitrary high and beyond the physical limit of the transformers in the charging station~\cite{lee2016adaptive} leading to huge electricity bills~\cite{Zhang2015eEnergy}.
-Besides, the charger devices installed in the CSs have limitation on the maximum power that they can transfer in each time unit~\cite{Tesla}.
-%We solve the issue by constraining local and global peaks.
-However, to meet the peak constraints, it may not be feasible to respond to all charging demands.
-Consequently, only a subset of EVs can be charged~\cite{Xiang}, which is captured in our problem formulation.
-\cite{DWang} considered a multi-microgrid system with global peak constraint where each microgrid has a CS and the goal is to manage electricity exchange between microgrids and main grid to minimize the operating costs.
-The authors assume that required information about individual EVs is available by forecast which may not represent a real scenario.
-A similar assumption is made in \cite{Zeng,Shaaban} where the objective is to maximize total utility of EVs and aggregators in a distribution network.
-%\rev{To be removed: In our solution, we applied a priority based selection process (based on the EVs' valuation) to respond to the demands to make sure that total peak respects the constraints.
-The selection process can be made based on different criteria such as the value of each charging request \cite{Lee, Xiang} or the priority.}
-%To avoid big billing cost in peak hours, \cite{Moradijoz} proposed a solution based on genetic algorithm to find optimal capacity and location of parking lots for serving demands in peak hours with the goal of maximizing total benefit of all stations.
-Although authors studied the problem under multiple CS setting, their solution is not applicable to our setting when the CSs are already set up.
-The authors in~\cite{malhotra2017distributed} use a similar model as in this paper, where both local and global peak constraints are considered.
-However, the authors solve the single-slot problem, which fails to provide a general solution taking into account EVs' arrival and departure times as considered in our study.
-Finally, as an alternative approach to control the peak, some studies directly target minimizing the peak~\cite{Zhao, Karfopoulos}.
-In~\cite{Zhao}, an online algorithm is developed for EV charging to minimize the peak and \cite{Karfopoulos} proposed a valley filling method by leveraging V2G in peak hours.
-Although the peak is minimized in above works, it cannot guarantee that the minimized peak is tolerable by the underlying charging network.
-
-\subsubsection{Scheduling Under Demand Uncertainty}
-A main challenge in EV scheduling problem is to cope with demand uncertainty.
-Many studies including \cite{Shroff2014,Tang,WTang,Chen,Xiang,Zhao,Robu} addressed online scheduling problem with different objectives.
-\cite{Shroff2014,Xiang} studied the problem of maximizing social welfare considering the benefit for both users and service provider.
-\cite{Tang} and \cite{WTang} developed algorithms to minimize the charging price for the CS, where the proposed algorithm in \cite{Tang} is $2.39$-competitive.
-%An online algorithm developed in \cite{Chen} to optimize overall operating profit of the service provider. 
-In \cite{Robu}, an online $2$-competitive algorithm is proposed for a single CS, assuming that EVs are capable of being discharged in a negligible amount of time.
-The assumption, however, is not realistic for EVs.
-
-Our problem in this paper is unique from above works in many respects.
-First, we study the problem in an ACN where several CSs exist, while none of the above studies solve the problem under this setting.
-Second, the previous algorithms do not work for both integral and fractional charging models.
-In addition, \cite{WTang,Chen} put no limit on the charging rate of EVs which makes their solution impractical in real scenarios.
-Also, \cite{WTang,Tang, Shroff2014,Chen,Zhao} do not consider the peak limit of the CS.
-\revv{Note that some studies~\cite{jin2017optimal} tackle the scenarios of satisfying the large demands (possibly EV demands) by participating in electricity market.
-This study assumes that the electricity price is given and fixed, and leaves the case of real-time pricing as the future direction.
-In addition, there are studies that incorporate prediction in online EV charging scheduling~\cite{wang2017predictive,chen2014distributional}.
-The prediction-based approaches achieve satisfactory performance for the scenarios that follow prediction.
-Deviation from prediction models, however, degrades their performance.
-Our approach, on the other hand, has no assumptions on modeling/prediction, and in this way, is robust against any uncertainty in the instances to the problem.}
-\revv{Finally, in~\cite{Alinia2018ITS}, we considered a simplified EV charging scheduling in fractional model without global peak constraints and devised heuristic algorithms (without competitive and approximation analysis) with on-arrival commitment for EVs to notify the amount that they can receive by their departure.
-}
-%In this paper, we consider these limitations and develop online and offline algorithms for fractional and integral revenue models in an ACN and provide theoretical bounds on their performance.
-
-%It is important to note that there is a considerable similarity between EV scheduling problem and classical job scheduling problem \cite{}.
-However, most algorithm developed for job scheduling problem  do not consider a limit on processing rate of the jobs.
-
-%\cite{Shroff2014} and \cite{Stein2012} study social welfare maximization problem while the profit of both EV owners and CS is considered.
-social welfare of the EV owners \cite{Stein2012}, charging cost \cite{Tang,WTang}, and total value of fully charged EVs \cite{Azar}).
-In addition, \cite{WTang, Tang,Shroff2014,Zhao} do not take into account the peak limitation of CS.
-}
-
-\subsubsection{Worst-case Analysis in Similar Scheduling Problems}
-\label{sec:rel:comp}
-\bt{
-	Similar underlying scheduling problems with slightly different settings have been studied in the literature in both offline and online settings.
-In offline setting, the problem is more interested in integral revenue model where the problem becomes a combinatorial optimization problem and approximation algorithms have been used to find effective solutions.
-The performance of an approximation algorithm is determined by its \emph{approximation ratio} for offline 
-algorithms.
-On the other hand, competitive online algorithms are used in the online setting and \emph{competitive ratio} is the performance metric which compares the algorithm's result to the offline optimal solution.
-
-\textbf{Offline integral model}: Under integral revenue model, \cite{jain2015near} proposes an offline algorithm for scheduling of batch jobs in cloud computing which is similar to EV scheduling problem.
-It is assumed that all jobs are available to be processed at time 0.
-The authors propose a $\frac{C}{C-k}.\frac{s}{s-1}$-approximation algorithm where $C$ is the cloud capacity and $s$ is the ``slackness parameter'' (See section \ref{sec:acn} for the definition).
-Similarly, \cite{yao2016real} tackles the offline integral problem and proposes a convex relaxation method to find a near-optimal solution.
-No theoretical bound is provided for the algorithm and the performance is examined by simulation results.
-In this paper, we propose \ics for the EV scheduling problem with slightly different settings in the constraint sets, and tackle the problem in online setting in which the full knowledge of the online parameters is not available a priori, and provide competitive ratio under specific scenarios.
-
-\textbf{Offline fractional model}: In case of fractional revenue model (for offline case), the scheduling problem is more straightforward to tackle since the underlying problem is linear.
-In this paper, we propose \fcs as an optimal solution for offline fractional case with low time complexity.
-
-\textbf{Online fractional model}: In the online scenario, the scheduling problem is fundamentally more challenging. In our recent study \cite{alinia2018competitive}, 
-we proposed two online algorithms referred to as WFAIR and WRAND for EV scheduling problem.
-The proposed algorithms provide a competitive ratio of $2-1/U$ where $U$ is "scarcity level".
-However, the result only holds when all EVs have the same maximum charging rate.
-Also, \cite{alinia2018competitive} does not study the integral revenue model.
-In this paper, we propose \focs as a 2-competitive online algorithm with no assumption on the input parameters.
-Moreover, the current study investigates both fractional and integral revenue model while considering total peak constraint in the formulation and addressing multiple charging station scenario.
-In another work~\cite{firstfit}, two simple and natural online algorithms called \textsc{FirstFit} and \textsc{EndFit} were developed and are proved to be 2-competitive.
-\focs is extension of these algorithms by taking into account the maximum charging rate of the EVs and multiple charging station scenario (see ``Remarks'' at Section IV).
-As recent studies, \cite{zheng2016online,deng2016whether} provide online algorithms for EV scheduling problem, however, they do not take into account global peak constraint in the underlying problem.
-
-\textbf{Online integral model}: Another direction is to tackle online scenario under integral revenue model.
-In this setting, the scheduling problem becomes fundamentally more challenging.
-We note that the integral scheduling problem is strongly NP-Hard even in the offline case \cite{de2018complexity}.
-Due to combined online and combinatorial challenges, there are very limited studies in this category.
-\cite{lucier2013efficient} provides an online algorithm without considering the maximum processing rate of the jobs where its competitive ratio can be arbitrary bad depending on ``slackness'' parameter.
-Our work in Section~\ref{sec:onlineint} extends this study for multiple station scenario and considering maximum charging rate for the EVs.
-}
-
-\section{System Model and Problem Formulation}
-		\label{sec:model}
-
-		\subsection{System Model}
-		We consider a time-slotted system model in which the time horizon is divided to $T$ equal length slots ${t=\{1, 2, \dots ,T\}}$ (e.g., $T=24$ with time slots of $1$ hour length).
-\subsubsection{Charging Network}
-\label{sec:acn}
-Our charging network model is inspired by the Caltech ACN~\cite{lee2016adaptive} as illustrated in Fig.~\ref{fig:model-a}.
-In \rev{the} Caltech EV charging network (located in a parking garage), electricity is distributed through a two-level transformer architecture from a main switch panel to multiple EV switch panels (\rev{$2$} panels in the current Caltech ACN).
-Each EV switch panel then is connected to several chargers ($\approx$25 chargers \rev{per panel} in the Caltech ACN).
-The total power drawn from the main switch panel \rev{by} the charging network has a power limit of  $p^\mathsf{total}$, that is determined by the facility operator to control the costs, reserve the capacity for other loads, and/or participate in demand-response programs.
-%This power, where we refer to it as \emph{network power limit} is used for both EV charging as well as non-EV charging purposes (e.g., lighting, fans, etc \cite{lee2016adaptive}). 
-In other words, $p^\mathsf{total}$, which we refer to it as the \textit{global peak}, hereafter, limits the maximum aggregate EV charging load at each time slot. 
-%The global peak must be less than or equal to the value obtained by subtracting non-EV load from network power limit. 
-%When we write \emph{global peak constraint}, it refers to $p^\mathsf{total}$.  
-%$p^\mathsf{total}$ is the maximum allowed aggregated electricity consumption by all stations at each slot and limits the total transferable power to EVs.
-
-We assume that there are $m$ EV switch panels that represent $m$ CSs.
-In addition to the global peak constraint, each CS $j$ has \rev{a} capacity constraint on \rev{its} total power drawn, indicated by $p_j$, and referred to it as the \emph{local peak} constraint.
-The \rev{value of} $p_j$ is determined by the output power limit of the transformers installed between the main switch panel and EV switch panels and could be different for each EV switch panel.
-%installed chargers in a CS have limited output power to charge EVs ~\cite{Wen,Xiang,Tesla}. Therefore, for CS $j$, $p_j$ cannot be more than sum of output power of its chargers. 
-\rev{It is often observed that the charging demand of different CSs (EV switch panels in Fig.~\ref{fig:model-a}) are well below the local peak constraints.}
-To increase the flexibility due to heterogeneous charging demand of CSs, in the Caltech ACN, the global peak constraint of the main switch can be \textit{over-provisioned}, i.e., $p^\mathsf{total}$ is less than the aggregate local peaks,  ($\sum_j p_j\geq p^\mathsf{total}$).
-\rev{While this increases flexibility, it also couples the problem of EV charging scheduling across different CSs.}
-%Despite increased flexibility, the over-provisioning property, however, couples the problem of EV charging scheduling across different CSs. 
-Our solutions in this paper will be centralized ones which can be obtained through communication between the CSs and a central server as illustrated in Fig. \ref{fig:model-b}.
-
-%We make this clear by a simple example.
-Assume $m=2, p^\mathsf{total}=50$ kW and $p_1=p_2=25$ kW.
-In a specific time slot (e.g., $t=1$), the total demand in CS $1$ and $2$ is $40$ kWh and $10$ kWh, respectively.
-According to local peak constraints, it is not feasible to satisfy all demands in a single time slot.
-However, if we had $p_1=p2=50$ kW (e.g., by installing more chargers in the stations) we could be able to satisfy all demands by allocating $40 kW$ in $p_1$ and $10 kW$ in $p_2$ while still not violating $p^\mathsf{total}$.
-In case that $\sum_j p_j\leq p^\mathsf{total}$, the scheduling problem is not challenging and the solution can be obtained by solving the problem locally in each CS.
-If $\sum_j p_j> p^\mathsf{total}$ (which is the case we consider in this paper), a centralized solution is needed that can be obtained through communication between the CS and a central server as illustrated in Fig.
-\ref{fig:model-b}.
-
-\begin{figure}	
-\centering
-\minipage{0.49\textwidth}
-				\begin{subfigure}[b]{0.69\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{model-a.pdf}
-						\caption{Caltech adaptive charging network (ACN)}
-						\label{fig:model-a}
-					\end{center}
-				\end{subfigure}%
-				\begin{subfigure}[b]{0.29\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{model-b.pdf}
-						\caption{Communication model with server}
-						\label{fig:model-b}
-					\end{center}
-				\end{subfigure}%  
-\caption{System model \cite{lee2016adaptive}.} 
-\label{fig:slackness1}
-\endminipage
-\end{figure}
-
-		\begin{table} 
-			\caption{Summary of key notations}\vspace{-3mm}
-			\label{tbl:not}
-			\begin{center}
-				\begin{tabular}{|c L{6.5cm}|}
-					\hline
-					\textbf{Notation} & \textbf{Description} \\
-					\hline \hline			
-					$T$ & Number of time slots, indexed by $t$\\			
-					$m$ & Number of CSs, indexed by $j$\\			
-					$n$ & Number of EVs, indexed by $i$\\			
-					\hline
-					\hline
-					$a_i$ & Arrival time of EV $i$\\
-					$d_i$ & Departure time of EV $i$\\
-					$D_i$ & Demand of EV $i$\\
-					$v_i$ & Valuation of EV $i$ for receiving its demand $D_i$ \\
-					$k_i$ & Maximum charging rate of EV $i$\\
-					$h(i)$ & CS of EV $i$\\
-					\hline
-					\hline
-					$q_j$ & Maximum $k_i$ among all EVs in CS $j$\\
-					$p_j$ & Maximum aggregate charging rate in station $j$\\
-					$p^\mathsf{total}$ & Maximum aggregate charging rate of all stations\\
-					\hline
-					\hline
-					$y_i^t$ & \textbf{opt. variable}, The amount that EV $i$ is charged at $t$ \\
-					\hline
-				\end{tabular}
-			\end{center}
-		\end{table}
-		\subsubsection{EVs}
-		\label{sec:ev} There are $n$ EVs in the system, indexed by $i$.
-		%, all available at time $t=1$ to be charged\footnote{This assumption is reasonable for the %official buildings where the starting hour of the working day is fixed for all the %employers.
-Extensions to the case with different arrival times for the EVs, is part of the %future work.}.
-		EV $i$ is represented by a charging profile $\langle a_i,d_i,v_i,D_i,k_i\rangle$ 
-		indicating its arrival time, departure time, willingness to pay, charging demand, and maximum charging rate, respectively. 
-		%(depends on physical properties of EVs battery) 
-		More specifically, the charging of EV $i$ can be scheduled within its \emph{availability window}, $[a_i,d_i]$.
-The charging rate at each slot is bounded by $k_i$, a parameter that depends on the physical constraints of the \rev{battery and on-board charger}.
-It is assumed that the charging profile of each EV is feasible with respect to its maximum charging rate and a slackness parameter $s\geq 1$, which is the minimum ratio between the park time of the EV and its minimum charging time, i.e., ${D_i\leq k_i(d_i-a_i+1)/s}$.
-The slackness parameter is imposed to tune the flexibility of the charging scheduling.
-In extreme case $s=1$,  the flexibility is minimum and the flexibility improves as $s$ increases.
-%		Note  that  the slackness  parameter  can  impact  the  total  revenue  and  is  investigated  in  simulation  experiments  in Section~\ref{sec:simul}.
-		We assume that EV owners select their CS, perhaps the nearest to them, and so the assignments are given to the problem. Define $h(i)$ as the CS of EV~$i$.
-		Moreover, $q_j$ denotes the maximum $k_i$ among all EVs in CS $j$, i.e., $q_j=\max_{h(i)=j} k_i$. 
-		\revv{Finally, $v_i$ is the willingness to pay of EV $i$ to receive its entire demand $D_i$ before the departure time $d_i$.
-Note that in resource-constrained EV scheduling in ACN, it is not feasible to fulfill the entire demand of all EVs, hence, the problem turns into a resource allocation one with the goal of maximizing the aggregate value (a.k.a.
-utility) obtained from the EVs.
-In this way, each user can announce its willingness to pay to get charged which is denoted by $v_i$ in the system model.}
-		%We assume that there is no gain for the CS if EV $i$ is partially charged.
-
-		% where $P$ defined as $P:\xi\rightarrow  \mathcal{P}$. 
-\subsubsection{Revenue Models\label{sec:irm}} We consider two revenue models: 
-\textit{(i) Fractional revenue model}: In this model, the fractional charging is allowed, i.e., the revenue from each EV is proportional to the fraction of the demand that is fulfilled \cite{Xiang} (see Eq.~\eqref{Eq:partial_value}).
-We tackle this model in Section~\ref{sec:fractional}.
-\textit{(ii) Integral revenue model}: \rev{In this model, EV $i$ pays $v_i$ if it is fully charged and zero otherwise, i.e., there is no partial revenue for partial charging. }
-%In this model, when EV $i$ is received its demand entirely, the gain is $v_{i}$ and zero, otherwise, i.e., there is no partial revenue for fractional charging. 
-This is the model that is considered in~\cite{WTang,Shroff2014}. We tackle this model in Section~\ref{sec:integral}.
-
-		%The actual aggregated peak of all parking stations must not exceeds global peak constraint.
-
-			\begin{table*}[!t]
-			\centering
-	\vspace{-3mm}
-			\caption{Proposed algorithms and their properties.}
-			\label{tbl:algs}
-			\begin{tabular}{ | l | c | c | c |c|}
-				\hline
-				\textbf{Algorithm} & \textbf{Revenue model} & \textbf{Type} & \textbf{Optimality} & \textbf{Complexity} \\ \hline\hline    
-				\fcs& fractional& offline& Optimal & $O(n^2T+nT^2)$\\\hline 
-				\ics& integral& offline& ${\Big( 1+\sum_{j=1}^m {\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}\Big)}$-approximate & $O(nT\log T+n^2T)$ \\\hline 
-				\focs & fractional& online& $2$-competitive & $O(n^2T)$\\\hline 
-				\iocs& integral&  online& $b(1+\frac{p}{p-q}.\frac{s}{s-1})$-competitive, $(m=1)$ & $O(n^2T)$\\\hline
-			\end{tabular}
-		\end{table*}
-
-		\subsection{Problem Formulation}
-		\label{sec:problem}
-	We formulate an optimization problem to schedule the charging of the EVs with the objective of maximizing total revenue obtained from charged EVs while respecting local and global peak constraints. 
-		Note that each revenue model makes the underlying optimization problem fundamentally different. More specifically, the fractional charging model is a linear problem. 
-		Integral revenue model, however, turns the underlying charging scheduling problem to a Mixed Integer Linear Program (MILP). The integer nature originates from the $0/1$-selection decision on EVs. 
-%%%Recall that in integral revenue model the revenue is obtained given that the entire demand is fulfilled for the selected EV. 
-		%We skip the explicit formulation of the problem under integral revenue model since it could be contemplated as the linear-relaxed version of the integral revenue model (for more explanation, we refer to the discussions in Section~\ref{sec:fractional}).
-		We formulate Scheduling Problem for Adaptive charging Network (\MCSP) under fractional revenue model as follows: 
-		\bse
-		\bee
-		\MCSP: \max  && \sum\nolimits_{i=1}^n \frac{v_{i}}{D_i}\sum\nolimits_{t=a_i}^{d_i} y_i^t \label{Pobjec} \nonumber\\
-		\text{s.t.} &&\sum\nolimits_{t=a_i}^{d_i} y_i^t\leq D_i,\quad\quad\forall i, \label{ConstPartial} \\
-		&&  \sum\nolimits_{i=1}^n y_i^t\leq p^\mathsf{total} ,\quad\quad\forall t,\label{ConstTotal} \\
-		&&\sum\nolimits_{i:h(i)=j} y_i^t\leq p_j ,\quad\quad\forall t,j,\label{ConstLocal}\\
-		&& y_i^t  \leq \frac{k_i}{D_i}\sum\nolimits_{t^\prime=a_i}^{d_i} y_i^{t^\prime}, \quad\forall i,t,\label{ConstSpeed}\\
-%		&& \rev{y_i^t=0,\forall t\in\{t':t'>d_i \vee t'<a_i\}}, \\
-		\text{vars.} && y_i^t \geq 0, \quad\quad\forall i, t,\label{ConstPositive}\nonumber
-		%&& s_v(t), \quad \forall v,t
-		\eee
-		\ese
-		where $y_i^t$ is the amount that EV $i$ is charged at slot $t$. Constraint (\ref{ConstPartial}) ensures that the aggregate amount received by EV $i$ is at most the demand $D_i$. 
-%		Note that under integral revenue model, when we design our algorithm, we do not allow partial charging. 
-The global and local peak constraints are represented by constraints (\ref{ConstTotal}) and (\ref{ConstLocal}), respectively.
-
-		\revv{The constraint~\eqref{ConstSpeed} enforces the maximum charging rate of EVs.
-The straightforward way to express this constraint is to simply state that at each time slot $t$, the charging rate of EV $i$ should be less than or equal to its maximum charging rate, i.e., $y_i^t\leq k_i, \forall i,t$.
-		However, for the sake of effective algorithm design for integral model and reducing the integrality gap of the relaxed linear problem, this constraint is strengthened in the form of Eq.~\eqref{ConstSpeed}.
-		Note that in case that the aggregated charging of EV $i$ during its availability window is equal to its demand, i.e., $\sum_{t^\prime=a_i}^{d_i} y_i^{t^\prime}= D_i$, Eq.~\eqref{ConstSpeed} reduces to the simple form of $y_i^t\leq k_i$.
-		This is a natural way in approximation algorithm design to improve the performance of the algorithms under linear-relaxation based design~\cite{Carr}. }
-
-The \MCSP is an extension of formulated problem in \cite{Jain} where a job scheduling problem in cloud applications is studied.
-It turns out that the resource allocation problem in cloud systems and the EV charging scheduling problem in a \emph{single station} share similar structure.
-Indeed, each charging profile in our scheduling problem can be seen as a job in cloud system with a deadline, value, and CPU demand.
-The \MCSP, however, comes with an additional constraint~\eqref{ConstTotal}, which makes it different from the problem in \cite{Jain}, such that the existing solution \revv{will not} work in the new setting.
-More importantly, this paper studies both offline and online solutions for the problem in both fractional and integral settings, while \cite{Jain} tackles only the offline integral model.
-
-%(ii) Our solution design and analysis for integral revenue model is based on linear-relaxation primal-dual framework~\cite{Jain}.
-Therefore, in Section \ref{sec:integral} for integral revenue model, we rely on the \MCSP for the analysis of the proposed algorithms and skip to explicitly formulate the original MILP problem.
-
-%		Also, we cover the fractional revenue model and provide theoretical bounds for the proposed algorithms.
-
-%In the next two sections, we devise several algorithms to solve the \MCSP under the two revenue models (integral and fractional) and for both offline and online scenarios. 
-		\section{Fractional Revenue Model}
-		\label{sec:fractional}
-
-%\subsection{Overview of Fractional Revenue Model}
-%\label{sec:frac.overview}				
-		%In the previous section, we devised an approximation algorithm for the integral revenue model in which it is assumed that the obtained revenue is zero if the allocated resource is less than the demand.
-Although this assumption is reasonable in some scenarios,
-%To develop a solution for the \MCSP, we first consider fractional revenue model.
-%However, algorithms for integral revenue model cannot achieve the same performance as the algorithms of this section i.e., \fcs and \focs.
-
-In the fractional model, the revenue of the CS from EV $i$ is directly proportional to the amount of resource that the EV is received, i.e.,
-		\begin{equation}
-			v_i^{\mathsf{f}}=\frac{\sum_t y_i^t}{D_i}v_i,
-			\label{Eq:partial_value}
-		\end{equation}
-		where $v_i$ is the gain, if the entire demand $D_i$ is fulfilled and $v_i^{\mathsf{f}}$ is the fractional gain.
-
-%Under fractional revenue model and without the binary variable of selecting EVs, the underlying problem turns into a linear one. 
-We propose a simple algorithm, called \fcs, with low computational complexity \rev{ of $O(n^2T+nT^2)$} for the fractional model that finds the optimal solution in offline setting.
-Note that even though linear programs can be solved in polynomial time in general, the complexity of our proposed algorithm is much lower than the general linear program algorithms.
-Moreover, our proposed offline algorithm applies a valley-filling strategy to reduce the peak.
-%The details of the proposed algorithm \fcs is given in~\cite{alinia2017online}.
-In the following, the online $2$-competitive algorithm is designed, where no exact information or stochastic modeling of future inputs of the problem is available.
-A summary of proposed algorithms with their complexity and assumptions is given in Table \ref{tbl:algs}.
-
-\revv{
-\subsection{Optimal Offline Design}
-\label{sec:fopt}	
-\bt{
-In this section, we propose an optimal algorithm for offline fractional model.
-As a natural solution, one may think of a greedy algorithm with the strategy as follows: at each time slot, charge the EV with highest unit-value and process others if only the resource cannot be used by this EV (probably due to maximum charging rate constraint).
-This approach is a popular, yet straightforward method in the online scheduling.
-However, it turns out that this approach cannot provide an optimal solution to the problem even in fractional revenue model.
-In fact, this approach only provides a 2-competitive solution.
-i.e., the profit obtained by the algorithm would be $1/2$ of the optimum.
-As an intuition of the proof think of two EVs where the one with lower unit value cannot wait due to its deadline and the EV with higher unit value has a long park time.
-Then, the optimal solution here could be first serving the EV with earlier deadline (and not the one with highest unit values).
-}
-
-We refer the proposed algorithm in this secion as the \fcs and summarize it as Algorithm~\ref{alg:optimal-off}.
-The \fcs works in two phases.
-In the first phase (Section~\ref{sec:ph1}), the algorithm decides on the amount of resource to be allocated to each EV within its availability window and reserves resources accordingly.
-In this phase, the details of allocation is not known.
-The actual resource allocation is done in the second phase (Section~\ref{sec:ph2}) by setting variables $y_i^t$.
-
-Before discussing the details of the algorithm, we give \bt{a definition} and introduce some notations to facilitate our algorithm design.
-
-\begin{defi}
-	Time interval $[\delta,\delta']$ is a ``super interval'' for interval $[t,t']$ if $1\leq \delta\leq t \text{~AND~} t' \leq \delta'\leq T$.
-	Moreover, $\mathcal{I}_{t,t'}$ is the set of all super intervals of interval $I_{t,t'}$ i.e., ${\mathcal{I}_{t,t'}=\{[\delta,\delta']: 1\leq \delta\leq t \text{~AND~} t'\leq \delta'\leq T\}}$.
-\end{defi}
-
-%		For example, $\mathcal{I}_{1,1}=\{I_{1,1},I_{1,2},I_{1,3},\dots ,I_{1,T}\}$. 
-The number of super intervals of an interval is at most $T^2$ and at least one (for interval $[1,T]$).
-
-Let $R_i$ be the amount of resource that is reserved for EV $i$ by the \fcs and $I_{t,t'}$ as time interval $[t,t']$.
-% with $t,t'\in\{1,\dots ,T\}$ which includes time slots $t,t+1,\dots ,t'$. 
-Then, assuming that charging demands are sorted in non-increasing order of their unit values, $A^i_j(t,t')$ is the aggregate residual resource in interval $I_{t,t'}$ at station $j$ assuming that the reservation for EVs $1$ to $i$ is accomplished.
-We now explain in detail each phase of the algorithm.
-
-\subsubsection{Phase I-Reservation\label{sec:ph1}} In Line~\ref{algline:sort1}, the EVs are sorted in a non-increasing order of their unit values.  
-%		i.e., ${v_1\slash D_1\geq v_2\slash D_2\geq\dots \geq v_n\slash D_n}$. 
-In Line~\ref{algline:setR}, the \fcs processes demand of EV $i$, picked from top of the ordered list, and sets $R_i$ as the amount to be reserved for EV $i$ which will be allocated in Phase II.
-In Line~\ref{algline:seta}, the residual resource of all intervals in set $\mathcal{I}_{a_i,d_i}$ decreases by $R_i$ and EV $i$ is added to the set of selected EVs.
-
-\begin{algorithm}[t]%\small%1
-	%\footnotesize
-	\revv{
-	\caption{\fcs}
-	\label{alg:optimal-off}
-	\DontPrintSemicolon 
-	\KwIn{$n$ EVs with their profile, local and global peak constraints $p_j, j=1,\dots ,m$ and $p^\mathsf{total}$ }
-
-	\KwOut{Optimal scheduling under fractional model}
-	\BlankLine
-
-	Sort charging requests in non-increasing order of their unit values, i.e., $\frac{v_1}{D_1}\geq \frac{v_2}{D_2}\geq\dots \geq \frac{v_n}{D_n}$\label{algline:sort1}
-
-	%	\slash\slash\textit{\texttt{Use sorted list to process demands}}
-
-	$\mathcal{L}\leftarrow \emptyset$
-
-	\slash\slash\textit{\texttt{Phase I}}
-
-	\For{$i=1,\ldots, n$}{
-		%\slash\slash\textit{\texttt{update demand and value}}
-
-		$R_i \leftarrow \min\{D_i, \min\limits_{t,t'} A^{i-1}_{h(i)}(t,t'), \forall t,t': I_{t,t'}\in\mathcal{I}_{a_i,d_i}\}$\label{algline:setR}
-
-		\If{$R_i>0$}{
-			$A^{i}_{h(i)}(t,t')\leftarrow A^{i-1}_{h(i)}(t,t')-R_i, \forall t,t': [t,t']\in\mathcal{I}_{a_i,d_i}$ \label{algline:seta}\\
-			$\mathcal{L}\leftarrow \mathcal{L}\cup{i}$
-	}}
-	\slash\slash\textit{\texttt{Phase II}}
-
-	Sort EVs in $\mathcal{L}$ in increasing order of their charging flexibility i.e., $\frac{(d_i-a_i+1)k_i}{D_i}, i\in \mathcal{L}$.
-
-	%	Let $i$ be the index of $i^{th}$ EV in list $\mathcal{L}$
-
-	\For{$i=1,\ldots, |\mathcal{L}|$}{
-
-		Pick EV $i$ from the sorted list $\mathcal{L}$.
-
-		$\emph{feasible}\leftarrow \big(\sum_{t=a_i}^{d_i}\min\{k_i,A^{i-1}_{h(i)}(t,t)\}\big) - R_i$
-
-		\If{feasible $<0$}{
-			Re-allocate previously allocated EVs such that $\emph{feasible}\geq 0$
-		}
-		Arbitrarily allocate $R_i$ to EV $i$ in its availability window\label{algline:fcsallocate}	
-	}}
-\end{algorithm}
-
-\begin{lem}
-	Provided that for EV $i$ we have 
-	\bee
-	\label{eq:ri}
-	R_i\leq\min\left\{D_i, \min_{t,t'} A^{i-1}_j(t,t'), \forall t,t': I_{t,t'}\in\mathcal{I}_{a_i,d_i}\right\}
-	\eee
-	 with a dummy $A^0_j(t,t')$ defined as
-$A^0_j(t,t')=(t'-t+1)\times\min \{p^\mathsf{total},p_{j}\},$
-	then there is a feasible allocation to allocate $R_i$ to EV $i$ in its availability window $[a_i,d_i]$. 
-	\label{thm:R_feasible}
-\end{lem}
-
-In Lemma \ref{thm:R_feasible}, $A^0_j(t,t')$ indicates the available resource when no charging request is processed in $I_{t,t'}$. 
-In Eq.~\eqref{eq:ri}, the second term, i.e., $\min_{t,t'} A^{i-1}_{j}(t,t')$, indicates the minimum remaining resource in all super intervals of interval $I_{a_i,d_i}$.
-For $i\geq 1$, $A^i_j(a_i,d_i)$ is defined as follows:
-
-\begin{equation*}
-A^i_j(a_i,d_i)=\begin{cases}
-A^{i-1}_j(a_i,d_i)-R_i & j=h(i),\\
-A^{i-1}_j(a_i,d_i) & j\neq h(i).
-\end{cases} 
-\end{equation*}
-
-The optimal value of $R_i, i=1,\dots ,n$ is set according to the following lemma:
-
-\begin{lem}
-	Given $n$ EVs sorted in a non-increasing order of the unit values, ${v_1\slash D_1\geq v_2\slash D_2\geq\dots \geq v_n\slash D_n}$, and the value of $R_i$, where $R_i$ is set after $R_{i-1}, i=2,\dots ,n$ by Eq.~\eqref{eq:ri}, then,
-	$$R_i = \min\left\{D_i, \min_{t,t'} A^{i-1}_{h(i)}(t,t'), \forall t,t':I_{t,t'}\in\mathcal{I}_{a_i,d_i}\right\},\forall i,$$
-	is the optimal value for $R_i$. 
-	\label{thm:R_star}
-\end{lem}
-
-\subsubsection{Phase II- Allocation\label{sec:ph2}} Lemma~\ref{thm:R_feasible} shows that there is a feasible scheduling to allocate the reserved resources.
-However, despite its feasibility, it is not straightforward to find such \revv{a schedule}.
-For example, assume that for EV $i$, $R_i=10$ and $k_i=4$.
-It is possible that all available resources are concentrated in a single time slot but EV $i$ cannot use more than $4$ kWh of it.
-In this situation, the previously allocated resources in interval $I_{a_i,d_i}$ should be re-allocated such that the concentrated resources are \emph{dispersed} and we have $\sum_{t=a_i}^{d_i}\sigma_t \geq R_i$ where $\sigma_t =\min\{k_i,A^{i-1}_{h(i)}(t,t)\}$ is the maximum resource that can be allocated to EV $i$ at time slot $t$.
-Since the total amount of allocated resource does not change in the interval, such dispersion is possible and can be done by a simple algorithm in which allocates $\min\{k_i,A^{i-1}_{h(i)}(t,t)\}$ starting from time slot $t=a_i$ until $R_i$ units is allocated.
-To further reduce the peak of the system, we will develop \sa\ algorithm (See Section \ref{sec:integral}) which acts more intelligent so that Line \ref{algline:fcsallocate} of the \fcs can be replaced by ``Run \sa$(i,R_i)$''.
-
-\begin{thm}
-	\label{cor:1}
-	\fcs is an optimal solution under fractional revenue model.
-\end{thm}
-
-The following theorem characterizes the complexity of \fcs.
-
-\begin{thm}
-	\label{thm:complexity}
-	The time complexity of \fcs algorithm is $O(n^2T+nT^2)$ where $n$ is the number of EVs and $T$ is number of time slots.
-\end{thm}
-}
-
-\vspace{-4mm}
-\subsection{Online Scenario}
-\label{sec:fonline}
-In this section, we devise an algorithm for the scenario that EVs arrive in online fashion.
-The scheduling decisions at each time slot are made given the information of available EVs and neither exact values nor stochastic modeling of future arrivals is available.
-Our goal is to obtain a \emph{competitive ratio} for the online algorithm.
-A scheduling algorithm $\mathcal{A}$ is $c$-competitive for $c\geq 1$ if the revenue obtained by the optimal offline algorithm is at most $c$ times the algorithm $\mathcal{A}$'s revenue for any input sequence~\cite{borodin2005online}.
-
-The proposed online algorithm for the fractional model, referred to as \focs, is listed as Algorithm~\ref{alg:focs}.
-The \focs is a simple yet efficient algorithm that always selects EVs with highest unit value to allocate as follows.
-First, the algorithm sorts the available EVs at each time slot~$t$ based on their unit value (Line~\ref{algline:sort}).
-\revv{In this step, the algorithm breaks ties based on EVs' deadline i.e., if two EVs have the same unit value, then the one with earliest deadline comes first in the sorted list.} Next, the \focs selects one EV at a time from the sorted list to allocate with maximum charging rate considering the EV's remaining demand, maximum charging rate, and peak constraints (Lines~\ref{algline:focsfor}-\ref{algline:focssety}).
-The allocation is continued until all resources are allocated or there is no more EV that could be allocated.
-%For unselected EVs, the value of $y_i^t$ will be $0$ in Line \ref{algline:focssety} of the algorithm. 
-The time complexity of the \focs is $O(n^2T)$, determined by cost of its ``\textbf{for}'' loop multiplied by total number of times that the algorithm needs to be run.
-% i.e., $T$.
-
-\vspace{-4mm}
-\begin{algorithm}%\small%1
-\footnotesize
-\caption{\focs: $\forall t\in \{1,2,\dots ,T\}$}
-\label{alg:focs}
-\DontPrintSemicolon 
-%\KwIn{Available EVs at time slot $t$, number of CSs $m$, local peak constraint $p_j, j=1,\dots ,m$, global peak constraint $p^{\textrm{total}}$}
-
-%\KwOut{A feasible charging scheduling}
-
-%$\backslash\backslash\texttt{Initialize:}$
-
-\BlankLine
-
-$\mathcal{M}^t\leftarrow$ The set of available EVs that not received their entire demand by $t$
-
-Sort EVs in set $\mathcal{M}^t$ indexed by $i=1,\dots ,|\mathcal{M}^t|$: $v_1/D_1\geq v_2/D_2\geq\dots\geq v_{|\mathcal{M}^t|}/D_{|\mathcal{M}^t|},$  \revv{where ties are broken based on users' deadline (giving priority to the users with earliest deadline) }\label{algline:sort}
-
-\For{$i=1,\ldots,|\mathcal{M}^t|\label{algline:focsfor}$}{
-
-$y_i^t\leftarrow \min\{k_i,D_i-\sum_{\tau=a_i}^{t}y_i^{\tau},p_{h(i)}-\sum_{i':h(i')=h(i)}y_{i'}^t,p^{\textrm{total}}-\sum_{i'}y_{i'}^t\}$ \label{algline:focssety}
-
-}
-
-\end{algorithm}
-Despite the simplicity of \focs which makes it easy to implement, its performance is sound and within a constant factor of the offline optimum.
-We now proceed to analyze the performance of the \focs by first giving some preliminaries.
-
-Fix an optimal scheduling and let $\mathcal{S}_{\focs,t}$ and $\mathcal{S}_{\opt,t}$ be the sets of EVs selected by the \focs and optimal solution at time slot $t$, respectively.
-Let $y_{i}^t$ and $z_{i}^t$ be the charging rate of EV $i$ set by \focs and \opt, respectively.
-We define $\Delta_{i}^t$ as follows:
-\begin{equation}
-\label{eq:delta}
-\Delta_{i}^t =
-     \begin{cases}
-       \min\{z_{i}^t-y_{i}^t,r_{i,t}\} &\quad i\in\mathcal{S}_{\opt,t},z_{i}^t>y_{i}^t, \\
-       0& \quad\text{otherwise},  \\
-     \end{cases}
-\end{equation}
-where $r_{i,t}$ is the remaining demand of EV $i$ by the end of time slot $t$.
-$\Delta_{i}^t>0$ indicates that the optimal algorithm allocated $\Delta_{i}^t$ units more resources to EV $i$ than the \focs by time slot $t$ that could be \emph{feasibly} allocated by \focs to the EV $i$.
-If for any EV $i\in\mathcal{S}_{\opt,t}$ and time slot $t\in\mathcal{T}$ we have $y_{i}^t=z_{i}^t$, i.e., $\Delta_{i}^t=0$, then the \focs is obviously optimal because it gains whatever the optimal solution gains.
-\rev{We define \textit{loss} of the \focs imposed by EV $i$ as follows:
-\begin{equation}
-\label{lBj0}
-l_{i,t}=\Delta_{i}^t\frac{v_i}{D_i},
-\end{equation}
-
-Note that the loss always takes a non-negative value as $\Delta_i^t\geq 0$.} When \focs sets charging rate of an EV less than its rate in the optimal solution, it gains $\Delta_{i}^t v_i/D_i$ less than the optimal solution from that EV.
-An upper bound for the distance between the optimal objective value (denote by \opt) and the revenue of the \focs (denote by \alg) is summation of the losses over all time slots and all EVs, i.e.,
-\begin{equation}
-\label{eq:optdist}
-\opt-\alg\leq \sum_{t=1}^T\sum_{i\in\mathcal{S}_{\opt,t}} l_{i,t}.
-\end{equation}
-
-%Notice that it is possible that an algorithm does not choose any selected EV by a particular optimal solution but still provide an optimal or near-optimal solution as there can be multiple optimal solutions.
-In particular, $\mathcal{S}_{\focs,t}\cap \mathcal{S}_{\opt,t}=\emptyset, \forall t$ cannot lead to any conclusion on the competitive ratio of the \focs.
-In addition to the amount of loss, the gain of the algorithm from charging alternative EVs should also be taken into account in comparison between \opt and \alg.
-
-Let $i\in\mathcal{S}_{\opt,t}$, $i\notin\mathcal{S}_{\alg,t}$ and $g_{i,t}$ be the gain that the \focs obtains from charging another EV instead of $i$ at time slot $t$.
-We are going to show that in the \focs, for each EV $i$ with $l_{i,t}>0$ there must be another EV (denote by $i'$) where $y_{i'}^t\geq \Delta_i^t$ and $\frac{v_{i'}}{D_{i'}}\geq \frac{v_i}{D_i}$ which means in resource allocation phase for EV $i$, the \focs allocated the difference $\Delta_i^t$ to another EV with the same or higher unit value.
-This can be proved by considering the fact that (i) the selected EVs have higher unit values than the unselected EVs, and (ii) the charging rate of the selected EVs are set to the maximum feasible value.
-Moreover, the \focs is \emph{``work-conserving''} i.e., it does not let any resource remain unused if there are some EVs that can use it.
-
-Let $g_{i,t}$ denote the gain that \focs obtains from allocating the same amount of resource that optimal algorithm allocated to EV $i$ (with size $z_i^t$) to another EV(s).
-If $\Delta_{i}^t=0$, the loss is zero. If $\Delta_{i}^t>0$, then by the charging strategy that the \focs uses we can conclude that (i) $i$ is not finished by the \focs, and (ii)
-\rev{no more resources from station $p_{h(i)}$ can be feasibly allocated,} otherwise, the \focs could allocate more resources to EV $i$.
-Therefore, the $\Delta_{i}^t$ units of the resource \rev{are} allocated to one or multiple other EVs (denote them by set $\mathcal{J}_i^t$) by the \focs.
-Moreover, it must hold that all the EVs in set $\mathcal{J}_i^t$ have a unit value equal to or higher than $v_i/D_i$ which yields $g_{i,t}\geq l_{i,t}$, otherwise, the \focs should not prefer the EVs in $\mathcal{J}_i^t$ to $i$.
-\rev{Since the result holds for any arbitrarily EV $i$, we can get the following:}
-
-\begin{equation}
-\label{eq:lg}
-\sum_{i=1}^n\sum_{t=1}^Tl_{i,t}\leq\sum_{i=1}^n\sum_{t=1}^Tg_{i,t}.
-\end{equation}
-
-Moreover, the total gain of \focs, i.e., \alg, is equal to sum of its gains from each single EV:
-\begin{equation}
-\label{eq:ALG}
-\rev{\alg= \sum_{i=1}^n\sum_{t=1}^Tg_{i,t}.}
-\end{equation}
-
-With the above discussion and using Eqs. (\ref{eq:optdist}), (\ref{eq:lg}) and (\ref{eq:ALG}) we are able to derive a competitive ratio of $2$ for the \focs.
-
-\begin{thm}
-	\label{thm:focscompetitive}
-	The \focs is $2$-competitive.
-\end{thm}
-
-\emph{Remarks:} When there is only one CS and EVs have no limit on their charging rate, the \focs is identical to the \textsc{FirstFit} algorithm ~\cite{firstfit} which is known to be $2$-competitive for classic job scheduling problem.
-However, the charging rate limitation is crucial for EV charging problem.
-Moreover, \cite{firstfit} uses \revv{a} ``charging argument'' to prove the competitive ratio of the proposed algorithm which cannot be directly applied to our problem.
-Thus, the \focs extends the \textsc{FirstFit} and makes it practical for the EV charging scenario.
-Moreover, the proof technique used for the competitive analysis of the \focs is fundamentally different from the one used in \cite{firstfit}.
-%%%Finally, in~\cite{Robu} an online $2$-competitive algorithm for EVs with partial charging is proposed.
-The competitive ratio obtained assuming that charging of EVs is instantly reversible at departure times.
-This assumption is not practical in reality since similar to charging phase, there is a discharging rate constraint for EVs.
-
-%\begin{thm}
-%\label{thm:focscomplexity}
-%
-%The time complexity of \focs is $O(nT\log n)$.
-%\end{thm}
-		\section{Integral Revenue Model}
-		\label{sec:integral}
-%
-%		\subsection{Overview of Integral Revenue Model}
-%		\label{sec:intoverview}
-		The MILP form of the \MCSP in integral model is a generalized form of the $0/1$-knapsack problem which is a well-known NP-hard problem.
-\rev{To give an intuition, consider the scheduling problem in a single time slot (i.e, $T=1$).
-Then, allocating power resources to the EVs is equivalent to allocating the capacity of knapsack to the items.
-}
-		In Section~\ref{subsec:icsalgorithm}, we propose a fast polynomial time offline approximation algorithm for the integral problem.
-In Section~\ref{sec:onlineint}, we extend the result and propose an online algorithm for the integral model.
-%		, where the EVs arrive in slot-by-slot fashion, and the scheduler has no information of the future arrivals.
-
-%The problem is even more challenging when the uncertainty in EVs' arrival is taken into account.
-At each time slot, the scheduler has no information of unit values of the future charging profiles.
-Therefore, the scheduler cannot make sure about the efficiency of its current charging decision.
-%It can be shown that when there is no assumption on the charging profiles of EVs (including the value of slackness parameter) and the charging decision , no online algorithm can provide a performance guarantee meaning that in the worst case, the ratio of the optimal objective value to the one obtained by the online algorithm can be arbitrary small.
-In fact, when the online algorithm selects
-
-		\subsection{Offline Scenario}   
-		\label{subsec:icsalgorithm}
-		We design our offline scheduling algorithm under integral model referred to as \ics, to solve the \MCSP approximately. 
-%		Our algorithm design is inspired by the basic algorithm proposed in \cite{Jain}.
-The algorithm in \cite{Jain} works for a single CS where arrival time of all EVs are the same and there is no global peak constraint.
-Since the performance analysis of the proposed algorithm relies on a dual fitting method and utilizes weak duality property, \revv{we first need to construct the dual problem of \MCSP.
-Toward this, we introduce variables $\alpha, \beta, \gamma$ and $\pi$.
-Generally, in primal-dual approximation algorithm design, each constraint (resp.
-variable) in primal (resp.
-dual) problem is associated with a variable (resp.
-constraint) in dual (resp.
-primal) problem.
-In our case, constraints (\ref{ConstPartial}) (\ref{ConstTotal}), (\ref{ConstLocal}) and (\ref{ConstSpeed}) in the \MCSP are respectively associated with dual variables $\alpha, \beta, \gamma$ and $\pi$ (for more details see \cite{approx}).
-The dual problem is formulated as follows:}
-		\bse
-		\bee
-		\min &&\sum_{i=1}^n D_i\alpha _i + \sum_{j=1}^m \sum_{t=1}^T p_j\beta (t)+\sum_{t=1}^T p^\mathsf{total}\gamma (t)\nonumber\\ 
-		\textrm{s.t.} && \alpha _i+\beta (t) +\gamma _i + \pi (t)- \frac{k_i}{D_i}\sum_{t'=a_i}^{d_i} \pi _i(t^\prime) \geq \frac{v_{i}}{D_i},\label{ConstDcover} \nonumber\\
-		&& \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\forall i, t\in [a_i, d_i],\\
-		\textrm{vars.}&&\alpha _i, \beta _i, \gamma,  \pi _i(t)\geq 0,\quad\quad\forall i,t. \nonumber
-		\eee
-		\ese
-
-		%%%In this section, we explain \ics in details and then in Section~\ref{subsec:analysis}, we analyze approximation factor of the algorithm. The \ics algorithm is listed as Algorithm~1.
-
-		\subsubsection{Explanation of the Main Algorithm} 
-		\label{sec:icsexplanation}
-		Our algorithm design is inspired by the basic algorithm proposed in \cite{Jain}.
-\revv{The algorithm in~\cite{Jain}, however, works for a single CS where arrival time of all EVs are the same and there is no global peak constraint.}
-		The \ics algorithm (listed as Algorithm \ref{alg:ics}) works in two phases.
-In the first phase it sorts the charging requests based on their unit values in a non-increasing order.
-Then, it selects most valuable demand.
-If the remaining resource is enough to cover the \emph{entire} demand of the EV, it is admitted to receive the demand (Lines~$6$-$7$).
-%		When \ics processes EV $i$, the algorithm checks for the feasibility of allocating $D_i$ units of the resource within its availability window $[a_i,d_i]$ without violating the constraints related to the maximum charging rate $k_i$, local and global peaks (Lines~$6$-$8$).
-
-		\emph{Scheduling of the Selected EV:} \revv{If the feasibility check passed (Line 6 in Algorithm 3)}, \ics calls sub-procedure \sa\ to allocate required resources in interval $[a_i,d_i]$.
-Then, $\alpha _i$ is set to $v_i\slash D_i$ in order to cover dual constraint in Eq.~\eqref{ConstDcover} (Lines~$7$-$8$).
-
-		In \sa, 
-		%%%When EV $i$ is selected to get charged, \sa\ is called for the charging scheduling. 
-		let us define $W(t,h(i))=\sum_{i': h(i')=h(i)} y_{i'}^t$ as total workload at time slot $t$ in CS $h(i)$ and $\bar{W}(t,h(i))$ as total available load to allocate at time slot $t$ for CS $h(i)$.
-We always have ${\bar{W}(t,h(i))+W(t,h(i))=p_{h(i)},  \forall t, i}$.
-For scheduling, \sa\ applies two main policies: 1) \emph{valley-filling} and, 2) \emph{right-to-left allocation}.
-\revv{With valley-filling, the slots with more available resources are preferred which helps to reduce the peak of the system.} %%%It also can be seen as a smoothing method which tries to reduce the variance of the allocated resources at different slots.
-%				The simulation results in Section \ref{sec:simul} will confirm this claim. 
-				Right-to-left allocation is used when two or more time slots are equal in terms of their remaining resources. 
-%				When this policy applies on scheduling of EV~$i$, any EV~$i'$ with $i'>i$ and $d_{i'}<d_i$ has more chance to get charged since the algorithm tends to charge EV $i$ in interval $[d_{i'}+1,d_i]$ (i.e., right hand part of the EV's availability window) and keeps resources in $[a_{i'},d_{i'}]$ for EV $i'$.
-A ranking based approach is used to apply the aforementioned policies. 
-		To charge  EV $i$, \sa\ ranks time slots in interval $[a_i,d_i]$.
-Then, charging is done by allocating resources from the higher ranked time slot to lowest one.
-The rank of a time slot $t$ is calculated based on remaining resources in the time slot (valley-filling) and value of $t$ (right-to-left allocation).
-
-		\begin{algorithm}%\small%1
-			\footnotesize
-			\caption{\ics}
-			\label{alg:ics}
-			\DontPrintSemicolon 
-%			\KwIn{$n$ EVs with $a_i, d_i, v_i, D_i,$ and $k_i$ associated with each EV $i$, $m$ CSs, local and global peak constraints $p_j, j=1,\dots ,m$, and $p^\mathsf{total}$}
-
-%			\KwOut{A feasible scheduling of EVs}
-			\BlankLine
-			%\begin{algorithmic}
-
-			%\slash\slash\textit{\texttt{Initialization}}
-			\textbf{initialize}: $y\leftarrow 0, \alpha\leftarrow 0, \beta\leftarrow 0, \gamma\leftarrow 0, \pi\leftarrow 0$
-
-			Sort charging requests in non-decreasing order of their unit values: $v_1/D_1 \geq v_2/D_2\geq\dots \geq v_n/D_n$
-%			$\frac{v_1}{D_1} \geq \frac{v_2}{D_2}\geq\dots \geq \frac{v_n}{D_n}$
-%			\slash\slash\textit{\texttt{Use sorted list to process demands}}
-
-			\For{(i=1\dots n)}{
-
-				\For{$t=a_i\dots d_i$}{
-					$\sigma_t\leftarrow  \min\Big\{p_{h(i)}-\sum_{i':h(i')=h(i)}y_{i'}(t),$ \newline $\qquad p^\mathsf{total}-\sum_{i'=1}^n y_{i'}^t,k_i\Big\}$
-
-				}
-
-%				\slash\slash\textit{\texttt{if enough resources remain for EV $i$}}
-
-				\If{$D_i\leq\sum_{t=a_i}^{d_i}\sigma_t$}
-				{
-					\sa($i,D_i$)\\
-					$\alpha _i\leftarrow v_i/ D_i$
-				}
-				\Else {
-					\If{$(\beta (d_i)=0)$}{
-						\bc($i$)}
-				}
-			}
-
-			\For{(i=1\dots n)}{ 
-				\If {EV $i$ is not selected}{
-					\rc($i$);
-				}
-			}
-			%\end{algorithmic}
-		\end{algorithm}
-
-\emph{Dual Feasibility of the Non-selected EVs:} \bt{If remaining power resource is not enough} to fully charge EV $i$, i.e.,  $D_i>\sum_{t=a_i}^{d_i}\sigma_t$, the EV cannot be selected.
-However, we still need to satisfy constraint~\eqref{ConstDcover} in dual problem which is done by calling \bc($i$).
-To cover the constraint~\eqref{ConstDcover} for EV $i$, sum of dual variables for all $t\in [a_i ,d_i]$ should be greater than or equal to ${v_i \slash D_i}$.
-\bc($i$) sets $\beta (t)$ to ${v_i \slash D_i}$ for all time slots $t$ in interval $[t_\mathsf{cov}, R(d_i)]$ (Lines $3$-$4$ of Algorithm~\ref{alg:betacover}).
-Observe that  ${\beta (t^\prime)\geq v_i \slash D_i,\forall t^\prime< t_\mathsf{cov}}$ (with $ t_\mathsf{cov}>1$) considering that the demands are sorted in a non-increasing order of the unit-values and $\beta (t')$ is already set to ${v_{i'} \slash D_{i'}}$ when processing the earlier charging demand of EV $i'$ which is not selected.
-Hence, ${v_{i'}\slash  D_{i'}\geq v_i \slash D_i}$, thereby ${\beta (t)\geq v_i \slash D_i,}$ and the dual constraint in~\eqref{ConstDcover} is satisfied.
-		Lines $1$-$4$ of \bc\ is enough to cover the dual constraint.
-However, the algorithm continues in Lines $5$-$8$ by setting a variable $\Phi_{i'}(t)$ for time slots $t=1,\dots ,R(d_i)$ to a value dependent to amount of the resource that a selected EV $i'$ received at slot $t$.
-$\Phi_{i'}(t)$ will be used in approximation analysis of the main algorithm and has no effect on the scheduling of EVs.
-		%We borrowed algorithm \bc($i$) from \cite{Jain} and adjusted it for multiple station mode.		
-		\vspace{-3mm}
-		\begin{algorithm}%\small%1
-			\footnotesize
-			\caption{\sa($i,D_i$)}
-			\label{SmartAllocate}
-			\DontPrintSemicolon 
-			\KwIn{EV $i$ to receive $D_i$ from CS $h(i)$}
-
-			Rank time slots in interval $[a_i,d_i]$ such that for any $t_1$ and $t_2$:
-			$\mathsf{rank}(t_1)> \mathsf{rank}(t_2)$ iff $\bar{W}(t_1,h(i))>\bar{W}(t_2,h(i))$ OR $\bar{W}(t_1,h(i))==\bar{W}(t_2,h(i)) \wedge t_1>t_2$
-
-			\While {$\sum_{t'=a_i}^{d_i}y_i^{t'}\neq D_i$}{
-
-				Select time slot $t$ with highest rank which is not selected before
-
-				Allocate $\min \left\{k_i,\bar{W}(t,h(i)),D_i-\sum_{\tau=a_i}^{t}y_i^{\tau},p^{\textrm{total}}-\sum_{i'}y_{i'}^t\right\}$ to EV $i$ at $t$
-
-			}
-		\end{algorithm}	
-		\vspace{-7mm}	
-		\begin{algorithm}%\small%1
-			\footnotesize
-			\caption{\bc($i$)}
-			\label{alg:betacover}
-			\DontPrintSemicolon 
-			%\KwIn{EV $i$ which is not selected to charge}
-
-			\BlankLine
-
-			$t_\mathsf{cov}\leftarrow \min \{t: \beta (t)=0\}$
-
-			$R(d_i)=\max \{t\geq d_i : \forall t^\prime\in (d_i,t], \bar{W}(t^\prime)<q_{h(i)} \}$
-
-			\For{$(t=t_\mathsf{cov}\dots R(d_i))$}{
-				$\beta (t)\leftarrow v_i/D_i$
-			}
-
-			\For{$(t=1\dots R(d_i))$}{
-				\For{$(i'=1\dots n))$}{	
-					\If{$y_{i'}^t>0 \wedge \Phi_{i'}(t)=0$}{
-						$\Phi_{i'}(t)\leftarrow\big[ \frac{p_{h(i)}}{p_{h(i)}- k_i}\frac{s}{s-1}\big] .\frac{v_i}	{D_i}y_{i'}^t$
-					}
-				}
-			}
-		\end{algorithm}
-		\vspace{-7mm}
-		\begin{algorithm}%\small%1
-			\footnotesize		
-			\caption{\rc($i$)}
-			\label{Replace}
-			\DontPrintSemicolon 
-%			\KwIn{EV $i$}
-%			\KwOut{Updated schedule}
-
-			$\mathcal{L} \leftarrow \emptyset$\\			
-			$v_\mathsf{inc}\leftarrow v_i$\\			
-			$\sigma_t\leftarrow 0, t=a_i,\dots ,d_i$
-
-			%Define $\delta_i(t)=\min \{k_i,\bar{W}(t,h(i))\}$
-
-			%$\Delta\leftarrow \sum_{t=a_i}^{d_i}\min\{\bar{W}(t,h(i)), k_i\}$
-
-			\For{($i' =i-1\dots 1$)}{ 
-				\If {EV $i'$ is selected $\wedge (h(i')=h(i)) \wedge (v_\mathsf{inc}-v_{i'})>0$}{
-					Add EV $i'$ to list $\mathcal{L}$
-
-					$v_\mathsf{inc}\leftarrow v_\mathsf{inc}-v_{i'}$
-
-					\For{($t=a_i\dots d_i$)}{
-						$\sigma _t\leftarrow\sigma_t + \min\{k_i,y_{i'}^t\}$
-					}
-				}
-			}
-
-			\If {$\sum_{t=a_i}^{d_i}\sigma_t\geq D_i$}{
-				Remove EVs in list $\mathcal{L}$ from charging schedule
-
-				\sa($i,D_i$)
-			}
-		\normalsize
-		\end{algorithm}
-
-		\emph{Improving the Gain:} In the second phase, the \ics tries to increase total value of selected EVs by calling \rc($i$) on every unselected EV $i$ (Lines~$12$-$14$).
-\rev{The \rc(i) (listed as Algorithm $6$) checks that whether the total revenue can be increased by replacing some selected EVs with EV $i$ or not (Lines $4$-$9$).
-If such EVs are found, the algorithm stops their charging and allocates EV $i$ using \sa\ (Lines $10-12$).}
-		%We refer to ~\cite{alinia2017online}, for the details and intuition behind this algorithm. 
-%		Before giving the details of \rc($i$), we first explain the intuition behind this algorithm. 
-%		 Note that if in the scheduling problem we set $T=1, m=1, k_i=p^\mathsf{total}, a_i=d_i=1\ \forall i$, then the problem is equal to the well-known $0$-$1$ knapsack problem~\cite{approx}.
-In the knapsack problem, a widely used greedy approach sorts items based on their unit values and selects items accordingly.
-It turns out that in this approach the approximation factor can be arbitrarily bad.
-For example, consider a knapsack problem with two items with $v_1=2, v_2=p^\mathsf{total}, D_1=1$, and  $D_2=p^\mathsf{total}$.
-Given these values we have $v_1\slash D_1>v_2\slash D_2$.
-To maximize total value of selected items, the optimal solution chooses item $2$ while greedy algorithm selects item $1$ which results in a worst-case approximation factor of ${c \slash \opt}$ in general where $c$ is a constant (in this example $c=2$).
-To resolve it, one approach is to \emph{re-consider} unselected items after running greedy algorithm and replace some selected items in the knapsack with unselected ones and then check whether the result is improved or not.
-In a simple case, only the largest unselected item can be examined which makes a significant theoretical improvement by providing a worst case approximation factor of $\opt\slash 2$.
-%		 
-%\ics algorithm leverages the same idea but using a more intelligent replacing method called \rc($i$).
-\rc($i$) is called on every unselected EV $i$.
-It tries to find some selected EVs that if they are replaced by EV $i$, total revenue from the selected EVs increases.
-%%%When \ics calls \rc($i$) on all unselected EVs, an improvement in total revenue of final selected EVs is expected.
-%This is confirmed by the simulation results in Section~\ref{sec:simul}.
-
-		\subsubsection{Analysis}
-		\label{subsec:analysis}
-		In primal-dual algorithm, the goal is to design an algorithm in a way that it produces a good solution for primal problem (with primal value $\Gamma$) and a feasible solution for the dual problem (with dual value $\Lambda$).
-Then, assuming that the primal problem is a maximization problem, to prove that the algorithm is $c-$approximation (for $c\geq 1$), the important part is to show that $\Lambda\leq c\Gamma$.
-Then, based on weak duality theorem we have $\Lambda\geq \opt$, and it is concluded that $\Gamma \geq \frac{1}{c}\times\opt$ where $\opt$ is the optimal value.
-		Based on the above understanding, the following theorem scrutinizes the approximation ratio of the \ics assuming that arrival times are the same for all EVs. 
-%		First note that the designed scheduling algorithm outputs a feasible scheduling since it respects the constraints in the primal problem.
-Also, the algorithm produces a feasible solution for the dual problem by covering the dual problem constraint in (\ref{ConstDcover}) through setting $\alpha _i$ to $\frac{v_i}{D_i}$ when EV $i$ is accepted and, $\beta (t)$ to a value greater than or equal to $\frac{v_i}{D_i}$ for $t\in [a_i, d_i]$ (according to the discussion in Section \ref{sec:icsexplanation}) if EV $i$ is not selected.
-To obtain an approximation factor for the algorithm, it is enough to bound the total covering cost of the dual constraints.
-
-		\begin{thm}
-			\label{thm:approx}
-			\ics algorithm is a $\Big( 1+ \sum_{j=1}^m {\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}\Big)$-approximation when EVs have same arrival time.
-		\end{thm}
-%		
-%		\begin{proof}
-%			In Appendix~\ref{app:1}.
-%		\end{proof}
-
-		Note that in the case that the system is flexible enough, i.e., $s\gg 1$, and the maximum charging rates of stations are much bigger than those of EVs, i.e., $p_j \gg q_j, \forall j$, the approximation ratio approaches $m+1$.
-And in the case that there is one single station, the approximation ratio is $2$.
-%		 Finally, we provide the time complexity of the \ics.
-
-%\begin{thm}
-%\label{thm:ics_complexity}
-%The time complexity of the \ics algorithm is $O(nT\log T+n^2T)$.
-%\end{thm}	
-%
-%\begin{proof}
-%In Appendix \ref{app:ics_complexity}.
-%\end{proof}
-
-\subsection{Online Scenario}
-\label{sec:onlineint}
-Due to the binary selection variable, the online solution design under integral model is more challenging than the one for fractional model.
-We propose the \iocs that is built upon the offline \ics.
-In particular, the \iocs calls the \ics at each time slot for the set of available EVs, however, any algorithm that is designed for offline integral model can be used alternatively.
-Hereinafter, $\mathcal{A}$ refers to the \ics or a similar algorithm.
-
-\begin{algorithm}%\small%1
-\footnotesize
-\caption{\iocs: $\forall t\in \{1,2,\dots ,T\}$}
-\label{alg:iocs}
-\DontPrintSemicolon 
-%\KwIn{$n$ EVs to arrive on the fly, number of CSs $m$, global peak constraint $p^{\textrm{total}}$, local peak constraints $p_j, j=1,\dots ,m$}
-
-%\KwOut{A feasible charging scheduling}
-
-\BlankLine
-
-Let $\mathcal{A}$ be an algorithm that solves the problem with $a_1=\dots =a_n$
-
-$\mathcal{R}^t\leftarrow$ set of EVs arrived at time slot $t$
-
-$\mathcal{M}^t\leftarrow \mathcal{R}^t\cup \{i: t\in\mathcal{T}_i\ \texttt{AND}\ \sum_{t^\prime}y_{i}^{t'}<D_i\}$
-
-%$\backslash\backslash\texttt{Schedule 1}$
-
-Based on the residual in interval $[t,T]$, use algorithm $\mathcal{A}$ to allocate EVs in set $\mathcal{R}^t$ assuming no further arrivals
-
-$\mathcal{S}_{\iocs,t}\leftarrow\{i:i\in\mathcal{M}^t\ \texttt{AND}\ i$ is admitted at $t\}$
-
-$\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}\leftarrow \sum_{i\in\mathcal{S}_{\iocs,t}}v_i$
-
-Assume all reserved resources are freed at time slots $t, t+1, \dots, T$
-
-%$\mathcal{R}^t\leftarrow\mathcal{M}^t$
-
-%$\backslash\backslash\textsl{set of active EVs at time slot t}$
-
-$r_{i,t}\leftarrow$ remaining demand of $i$ at $t, \forall i$
-
-%$\backslash\backslash\texttt{Use modified demands values}$
-
-$D_i^\prime\leftarrow r_{i,t},\ \ v_i^\prime\leftarrow \frac{r_{i,t}}{D_i}v_i, \forall i\in\mathcal{M}^t$
-
-%$\backslash\backslash\texttt{Schedule 2}$
-
-Run $\mathcal{A}$ on $\mathcal{M}^t$ using $D_i^\prime$ and $v_i^\prime, \forall i$ and reconstruct $\mathcal{S}_{\iocs,t}$
-
-$\Gamma_{\mathcal{A},\mathcal{M}^t}\leftarrow \sum_{i\in\mathcal{S}_{\iocs,t}}v_i$ $\backslash\backslash\texttt{Use original values}$
-
-%$a\leftarrow\frac{V^\prime_{\textrm{total}}}{V_{\textrm{total}}}$
-
-\If{$\Gamma_{\mathcal{A},\mathcal{M}^t}>\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$}{
-
-Use the second schedule
-
-}
-
-\Else{
-
-Use the first schedule
-
-}
-
-\end{algorithm}
-
-The \iocs is summarized as Algorithm~\ref{alg:iocs}.
-At slot $t$, the \iocs compares two scheduling results returned by $\mathcal{A}$ and chooses among them.
-In the first scheduling, the \iocs keeps all reserved resources in interval $[t,T]$ intact.
-Then, for utilizing the remaining resources, the algorithm runs $\mathcal{A}$ over arrived EVs at time slot $t$.
-In this case, the total revenue obtained by the \emph{active} EVs (i.e., EVs that are available but not received their entire demand yet) is denoted by $\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$ (Line $6$ of the algorithm).
-In the second scheduling, the \iocs considers the case that it can sacrifice the previously admitted EVs by canceling their reservations and allocating the freed resources to more valuable demands.
-For this purpose, the algorithm modifies the demand and valuation of the previously admitted EVs such that each demand is replaced by the EV's remaining demand, and the valuation of the EV is proportionally calculated based on the remaining demand (Line $9$ of the algorithm) so that the unit values of EVs do not change.
-Then, the \iocs runs $\mathcal{A}$ over set of active EVs $\mathcal{M}^t$ where the corresponding gain is denoted by $\Gamma_{\mathcal{A},\mathcal{M}^t}$.
-If $\Gamma_{\mathcal{A},\mathcal{M}^t}>\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$, the \iocs forgets the previously admitted EVs and follows the second scheduling.
-
-\begin{comment}
-%We now introduce some notations and then analyze the performance of \iocs. 
-Let $\mathcal{S}_{\iocs,t}$ and $\mathcal{S}_{\opt,t}$ be set of active EVs at time slot $t$ that are selected for charging by \iocs and \opt (fix a particular optimal solution), respectively.
-Note that the set of active EVs for \iocs and \opt might be different.
-%Moreover, define  $\mathcal{U}_{\iocs,t}=\mathcal{S}_{\iocs,1}\cup\dots\cup \mathcal{S}_{\iocs,t}$ and $\mathcal{U}_{\opt,t}=\mathcal{S}_{\opt,1}\cup\dots\cup \mathcal{S}_{\opt,t}$. 
-Having $i\in\mathcal{S}_{\iocs,t}$ means that based on the updated schedule at time slot $t$, enough resources reserved for EV $i$ so that the EV will receive its demand $D_i$ before the deadline $d_i$.
-However, the schedule may change at each slot and $i\in\mathcal{S}_{\iocs,t}$ cannot be a guarantee for EV $i$ to fully receive its demand.
-In fact, users and the scheduler itself have to wait until the deadline of the EV to find out that the demand is fulfilled or not.
-This is because the scheduler may cancel some reservations in the next time slots and allocate the freed resources to other EVs.
-\end{comment}
-% (when Algorithm \ref{alg:iocs} uses the second schedule in Line $15$). 
-%Define $A_t$ as the minimum gain of \iocs when the algorithm visited time slots $1$ to $t$.
-More formally, $A_t=\sum_{i\in\mathcal{U}_{\iocs,t}}v_i$.
-$A_t$ is the minimum gain that \iocs will obtain by the end of time slot $t$, having the information of released demands up to time slot $t$.
-Notice that the algorithm may continuously improve its set of selected jobs to increase its gain such that $A_t\geq A_{t-1}, t\in\{2,\dots, T\}$.
-$A_t$ is formally defined as follows:
-
-The following theorem characterizes the competitive ratio of the \iocs in a special case. 
-\begin{thm}
-\label{thm:iocscompetitive}
-Let $\mathcal{A}$ be \ics in \iocs algorithm and $m=1$.
-Assuming that EVs are released in $b$ distinct groups where arrival time of EVs in each group are the same, the \iocs is $b\Big(1+\frac{p}{p-q}\frac{s}{s-1}\Big)$-competitive with optimal offline solution, where $p$ is the station peak and $q=\max_i k_i, i=1,\dots ,n$.
-\end{thm}
-
-%\begin{thm}
-%\label{thm:iocscomplexity}
-%Let $\mathcal{A}$ be \ics in Line $1$ of \iocs. Then, the time complexity of the \iocs  is $O(n^2T)$. 
-%\end{thm}
-
-\vspace{-6mm}
-\section{Simulation Results}
-			\label{sec:simul}
-%%%In this section, we report a summary of simulation experiments to evaluate the performance of the proposed algorithms.
-
-						\begin{figure*}[t]	
-				\centering
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{V-N-M2.pdf}
-						\caption{\revv{$m=2$}}
-						\label{fig:V-N-M2}
-					\end{center}
-				\end{subfigure}
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{V-N-M4.pdf}
-						\caption{\revv{$m=4$}}
-						\label{fig:V-N-M4}
-					\end{center}
-				\end{subfigure}% 	
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{V-N-M8.pdf}
-						\caption{\revv{$m=8$}}
-						\label{fig:V-N-M8}
-					\end{center}
-				\end{subfigure}% 
-				\caption{\revv{Comparison results for $2$, $4$, and $8$ CSs for fractional and integral revenue models.}} 
-				\label{fig:V-N-M}
-				\vspace{-3mm}
-			\end{figure*}
-%\subsection{Simulation Setup and Overview}
-\textit{Simulation Setup and Overview:} We consider charging scheduling of EVs \revv{during a period of $12$ time slots of length $1$ hour (e.g., from $08$:$00$ to $20$:$00$)}. 
-We gathered information of \revv{$12$} popular EV models in the market to use in the simulation.
-Each EV model is characterized by its battery capacity as shown in Table \ref{tb:models} and maximum charging rate.
-\revv{Tesla models can get charged with up to $100$ kW using Tesla super chargers.
-Also, all other models have rapid DC charging capability (up to $50$ kW) with CHAdeMO method.
-This setting for charging rates is in accordance with future DCFC systems that can have several fast DC chargers installed in the charging station.}
-%Battery capacity varies from \revv{$14$} kWh to \revv{$100$} kWh and the maximum charging rate from \revv{$3.3$} kW to \revv{$22$} kW. 
-%As in \cite{Tang,Chen}, we assume that arrival times follow a Poisson distribution and parking times follow an exponential distribution.
-% with the mean arrival and parking duration indicated in Table \ref{tb:a-d}. 
-The peak intervals include $08$:$00$-$10$:$00$, $12$:$00$-$14$:$00$, and $18$:$00$-$20$:$00$ which is in accordance to NHTS survey~\cite{Santos, Tang}.
-\revv{The probability of arriving an EV in the peak hours is two times higher than the off-peak periods.
-			Demands are uniform random values from 
-			$[\frac{1}{2}U_i,U_i]$} where $U_i$ is the battery capacity for EV $i$ in Table~\ref{tb:models}.
-\revv{The deadline of each EV is set according to slackness parameter $s$ (with default value of $1.2$), its demand and maximum charging rate of the battery as $d_i=a_i+\lceil \frac{D_is}{k_i} \rceil -1$.}
-%			The minimum electricity cost is $\$0.11$ per kWh based on US national electricity price average~\cite{kWhcost}.
-In our setting, users can submit higher prices than the minimum price in order to ensure receive their requested demand.
-			\revv{EVs are assigned to different CSs randomly and given as input to the algorithms.
-The willingness to pay by each user for one kWh of power is a random uniform number from interval $[\frac{1}{2} z,\frac{3}{2}z]$ where $z=\$0.11$ is national average price of electricity in the US\cite{kWhcost}.}
-			%The default value of local peak constraint is \rev{$100$} kW and the global peak constraint is \rev{$200$} kW. We investigate the effect of this parameter in~\cite{alinia2017online}. 
-			In the simulation, the results are plotted with $95\%$ confidence level and each point represents average result of $50$ random scenarios.
-Table \ref{tb:comparisons} explains the comparison algorithms \revv{including current implemented algorithm in Caltech ACN referred to as \iolp \cite{lee2016adaptive} and its adapted version for the fractional revenue model \folp.
-The \iolp and \folp algorithms runs as follows: at each time slot assume that there will be no further arrivals and solve the optimization problem (e.g., by commercial solvers) for the current set of EVs and their remaining demands.
-In Table \ref{tb:comparisons}, the letters ``\textsc{i}'', ``\textsc{f}'' and ``\textsc{o}'' in front of the algorithms' name refer to integral, fractional and online types, respectively.}
-
-			The measured performance metrics are total revenue, percentage of EVs that received all their demand, and total peak.
-\revv{To calculate optimal solution in integral revenue model, we used Gurobi solver \cite{optimization2013gurobi}.}
-
-\begin{table}[!t]
-				\centering
-				\caption{\revv{EV models and their battery capacity.}}
-				\label{tb:models}\revv{
-				\begin{tabular}{ | l| c | l| c |}
-					\hline
-					\textbf{Model} & \textbf{Battery} & \textbf{Model} & \textbf{Battery} \\ \hline\hline    
-				Mitsubishi i-MiEV & $16$ kWh & Citroen C-Zero & $14$ kWh \\ \hline
-				Peugeot iOn  & $16$ kWh & Honda Clarity & $25.5$ kWh\\\hline
-				Hyundai Kona & $64$ kWh & Nissan LEAF & $40$ kWh \\ \hline
-				Hyundai Ioniq & $28$ kWh & BMW i3 & $22/33$ kWh \\ \hline
-				Tesla Model S/X  & $60/100$ kWh & Kia Soul EV  & $27$ kWh\\\hline
-				\end{tabular}}
-			\end{table}
-
-%\begin{table}[h]
-%				\centering
-%				\caption{Arrival rates and mean parking times.}
-%				\label{tb:a-d}
-%				\begin{tabular}{ | l | c | c |}
-%					\hline
-%					\textbf{Interval} & \textbf{Arrival rate} & \textbf{Mean parking time} \\ \hline\hline    
-%					$08$:$00$-$10$:$00$&  $14$&$10$\\\hline  
-%					$10$:$00$-$12$:$00$&  $10$&$1/2$\\\hline 
-%					$12$:$00$-$14$:$00$&  $20$&$2$\\\hline 
-%					$14$:$00$-$18$:$00$&  $10$&$1/2$\\\hline
-%					$18$:$00$-$20$:$00$&  $20$&$2$\\\hline
-%					$20$:$00$-$24$:$00$&  $10$&$10$\\\hline
-%					$24$:$00$-$08$:$00$&  $0$&$0$\\\hline
-%				\end{tabular}
-%\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{Acronyms for the algorithms}
-\label{tb:comparisons}
-\begin{tabular}{ | l| p{6cm}|}
-\hline
-\textbf{Notation} & \textbf{Description} \\ \hline\hline
-\textsc{iOpt} & Optimal value under integral revenue model\\ \hline 	 
-\ics & Proposed offline algorithm for \MCSP under integral revenue model\\ \hline
-\fcs & Proposed \emph{optimal} algorithm for \MCSP under fractional revenue model\\\hline 
-\iocs & Proposed online algorithm for \MCSP under integral revenue model\\ \hline
-\focs & Proposed online algorithm for \MCSP under fractional revenue model\\ \hline
-\iolp & Algorithm in \cite{lee2016adaptive} (works under integral revenue model)\\ \hline
-\folp & Adaptation of algorithm in \cite{lee2016adaptive} for fractional revenue model\\ \hline
-GreedyRTL & The algorithm in \cite{Jain} for single station scenario without global peak 			constraint (works under integral revenue model)\\\hline				
-\end{tabular}
-\end{table}
-			%to simulate: Fig. 1 with M=1,4,8			
-			\begin{figure*}[t!]	
-				\centering
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{v-c.pdf}
-						\caption{\revv{Total revenue}}
-						\label{fig:v-c}
-					\end{center}
-				\end{subfigure}%
-				%\hspace{4mm}
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{p-c.pdf}
-						\caption{\revv{Actual global peak} 
-%							($p^{\mathsf{total}}=480$)
-}
-						\label{fig:p-c}
-					\end{center}
-				\end{subfigure}%  
-				%\hspace{4mm}
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{acc-c.pdf}
-						\caption{\revv{\% of full charged EVs}}
-						\label{fig:acc-c}
-					\end{center}
-				\end{subfigure}% 				
-				\caption{\revv{Comparison in terms of total revenue, actual peak, and percentage of fully charged EVs by varying local peak value}.} 
-				\label{fig:peak_local}
-			\vspace{-4mm}
-			\end{figure*}
-\textit{\revv{Evaluation Based on Total Revenue}:}
-\revv{Fig.
-\ref{fig:V-N-M} depicts the comparison results based on total revenue under fractional and integral models} while the total number of EVs increases from \revv{$100$ to $250$} for $2$, $4$, and $8$ CSs.
-\revv{The local and global peak constraints are set to $50$ kWh and $200$ kWh, respectively.}
-
-The proposed algorithms compared to the optimal offline solution of integral model ($\textsc{iOPT}$) and $\iolp$.
-\bt{Note that comparison with offline optimal could be considered as a baseline comparison with the category of approximate offline algorithms in integral model~\cite{yao2016real}.}
-
-%%% which is the running online algorithm in the Caltech ACN \cite{lee2016adaptive}. 
-%The proposed algorithms for fractional revenue model, \fcs and \focs, are compared to fractional version of OLP algorithm (referred to as \folp), which is implemented in Caltech ACN  (see~\cite{alinia2017online} for details).
-Recall that \fcs is optimal offline solution.
-The notable observations  are  as  follows:  (i)  the  general  trend in scenario of Fig.~\ref{fig:V-N-M} is that  by increasing  the  number  of  EVs,  total  revenue  increases.
-This is because with more number of EVs, the scheduler has more freedom to choose more valuable EVs.
-(ii)  as  explained in Section~\ref{sec:fractional}, under fractional charging model, better results are expected due to increased scheduling flexibility in CSs.
-According to the simulation data that we extracted from Fig.~\ref{fig:V-N-M}, the gain obtained by \fcs and \focs in Fig.
-\ref{fig:V-N-M} are respectively \revv{$12\%$ and $10\%$} more than the gain of the \ics and \iocs.
-(iii) \revv{In Fig.
-\ref{fig:V-N-M2} and Fig.
-\ref{fig:V-N-M4}, sum of the local peaks is less than or equal to the global peak while in Fig.
-\ref{fig:V-N-M8} this sum is two times greater than the global peak.
-Consequently, the total revenue significantly improved when the number of CSs is increased from $2$ to $4$ while there is a slight improvement from $4$ to $8$ CSs as the global peak constraint prevents the algorithms from charging more EVs.}
- (iv) in integral revenue model, the proposed \iocs algorithm acts significantly better than \iolp.
-In particular, \iocs improves \iolp by \revv{$38\%, 36\%$, and $32\%$} for $m=2$, $m=4$ and $m=8$, respectively.
-\revv{In fractional revenue model, however, there is a very slight difference between \focs and \folp.}
- %We highlight that \iocs (\focs) is also better choice in terms of the algorithm complexity compared to \iolp (\folp).
-(v) \ics approximates \textsc{iOpt} by \revv{$97\%$, $94\%$, and $95\%$} for $m=2$, $m=4$, and $m=8$, respectively.
-On average, \iocs is \revv{$90\%$} of \textsc{iOpt} and, \focs is \revv{$94\%$} of its optimal offline solution, \fcs.
-(vi) finally, the results depict that \ics achieves much better results in practice as compared to the theoretical approximation ratio that characterizes the performance in worst-case scenario.
-
-%Also, there is a sharp decline in the gap between the online methods (i.e., \focs and \iocs) and the offline solutions (i.e., \textsc{iOpt}, \ics and \fcs).
-
-\revv{\emph{Comparison Based on Actual Peak:}} The constraint set in the \MCSP assures that any feasible solution respects the local and global peak constraints.
-% i.e., at each time slot, the electricity consumed by station $j$ is less than or equal to $p_j$ and accumulative charging rate of all stations are less than or equal to $p^\mathsf{total}$ (note that there is no assumption that $\sum_j p_j\leq p^\mathsf{total}$, in general).
-An efficient scheduling algorithm may take a further step by not only satisfying the peak constraints but to further reduce the peak as much as possible.
-The proposed offline algorithms (i.e., \ics and \fcs) apply valley-filling policy to reduce the peak.
-The  online algorithms (i.e., \iocs and \focs) do not apply the same policy as they do not have future knowledge to be able to balance allocated resources.
-%Besides, due to uncertainties in future EV charging load in online scheduling design, it is a natural heuristic to charge EVs at earliest time.
-% (i.e., setting the charging rates to the maximum feasible value at each time slot) as applied by \iocs an \focs. 
-%This heuristic works well as the uncertainty in EVs' arrival time and demands may not give a second opportunity to the scheduler to charge the current EVs at the next slots.
-Therefore, although it is expected that \iocs and \focs have higher peak values compared to the offline algorithms, the idea of valley-filling can decrease their average response time.
-% (see~\cite{alinia2017online} for the extended version of experiments).
-To investigate the effect of employed valley-filling strategy, we conducted a set of simulations by varying local peak constraints. 
-%from $50$ kWh to $120$ kWh and $200$ EVs. 
-The results of \ics is compared to \iocs and GreedyRTL~\cite{Jain} where the latter is an approximation scheduling for single station scenario with EVs having same arrival time (see the explanations after formulating the \MCSP in Section \ref{sec:problem}).
-%The GreedyRTL algorithm works under integral revenue model. Therefore, results for \fcs and \focs are not plotted. 
-%Since GreedyRTL assumes all EVs arrive at the same time, we set all arrival times to $1$.
-Moreover, we assume that global peak constraint is big enough (i.e., $\sum_{j=1}^m p_j\leq p^\textsf{total}$) such that the solution of GreedyRTL is feasible.
-We run GreedyRTL in each CS separately and combine the results.
-The results are shown in Fig.~\ref{fig:peak_local}.  
-Along with total revenue in Fig.~\ref{fig:v-c}, we also report total \emph{actual} peak in Fig.~\ref{fig:p-c} and percentage of fully charged EVs in Fig.~\ref{fig:acc-c}. 
-%As a high level trend, the results show that as the peak values increase, total revenue, total actual peak, and the number of EVs who received all their demand increase.  
-In Fig.
-\ref{fig:v-c}, the results for \ics and GreedyRTL are almost identical while \iocs is \revv{$90\%$} of the other two algorithms, on average.
-When \revv{$p_j\geq 400$}, the total revenue for \ics and GreedyRTL does not increase in Fig.
-\ref{fig:v-c} and percentage of fully charged EVs is $100$ for both algorithms according to Fig.
-\ref{fig:acc-c}.
-From this point and onward, the scheduling is not challenging for offline methods to obtain optimal answer because of resource sufficiency.
-However, it is still a challenge to control total actual peak for the system.
-As a result of valley-filling policy, the value of actual peak of \ics in Fig.
-\ref{fig:p-c} remains almost unchanged for \revv{$p_{j}\geq 400$}.
-\iocs and GreedyRTL, however, continuously increase the peak demand, since they are not using any peak shaving approach.
-% and only try to maximize total revenue. 
-%According to Fig. \ref{fig:p-c}, \iocs always reaches to the maximum peak of $\sum_j p_j$.
-
-%A glance at Table \ref{tb:models} shows that in general, an EV needs a minimum time of $2$ hours to get $70\%$ of its battery capacity if charging rate is set to the maximum value.
-However, CSs are allowed to preempt the charging at any time and set charging rate any value lower than the maximum rate.
-Therefore, average response times can be higher as it can be seen in Fig.
-\ref{fig:rt-c}.
-
-%\begin{figure}[t]	
-%\centering
-%				\begin{subfigure}[b]{0.25\textwidth}
-%					\begin{center}
-%						\includegraphics[width=\textwidth]{v-s-method1.pdf}
-%						\caption{Total revenue (\$)}
-%						\label{fig:v-s-method1}
-%					\end{center}
-%				\end{subfigure}%				
-%				\begin{subfigure}[b]{0.25\textwidth}
-%					\begin{center}
-%						\includegraphics[width=\textwidth]{rt-s-method1.pdf}
-%						\caption{Response time (hr))}
-%						\label{fig:rt-s-method1}
-%					\end{center}
-%				\end{subfigure}%  
-%\caption{The impact of slackness parameter on total revenue and response time when users react by adjusting their demand.} 
-%\label{fig:slackness1}
-%\end{figure}
-
-%\subsection{The Impact of Slackness Parameter}
-%\label{sec:sim:slack}
-%This section discusses on the benefits and disadvantages that can be brought by using slackness parameter.
-To give the charging scheduler more flexibility, a slackness parameter $s\geq 1$ is used and set by the system designer.
-%Recall that charging profile of EV $i$ is feasible if $D_i\leq k_i\frac{d_i-a_i+1}{s}$ holds.
-Since users have no control on the slackness parameter and the maximum charging rate, they must adjust their demand and availability according to the imposed slackness value.
-Based on the charging profile feasibility equation, when the slackness value increases users have two choices to react: (i) decrease the demand and depart at the desired deadline or, (ii) extend the deadline and receive the desired demand.
-In the remaining of this section, we investigate the effects of either case by simulation.
-To have a clear picture of effects caused by slackness parameter, we generated $100$ initial charging profiles $\langle a_i,d_i,v_i,D_i,k_i\rangle$ for $100$ EVs randomly and uniformly chosen from $10$ different models in Table \ref{tb:models} such that the initial profiles are set up assuming that the CS allows the charging operations to be finished at earliest possible time (i.e., $\frac{D_i}{k_i}$) with $s=1$.
-For each EV, its demand is randomly chosen from $25\%$ to $100\%$ of its battery capacity and departure in  interval $[a_i+\frac{sD_i}{k_i},T]$, where $a_i+\frac{sD_i}{k_i}$ is the earliest feasible deadline.
-Then, the EVs are uniformly assigned to $4$ CSs and should choose one of the above strategies to submit a feasible demand according to imposed slackness.
-%\begin{figure}[t]	
-%\centering
-%							\begin{subfigure}[b]{0.234\textwidth}
-%								\begin{center}
-%									\includegraphics[width=\textwidth]{v-s-method2.pdf}
-%									\caption{Total revenue (\$)}
-%									\label{fig:v-s-method2}
-%								\end{center}
-%							\end{subfigure}%
-%							\hspace{1mm}
-%							\begin{subfigure}[b]{0.236\textwidth}
-%								\begin{center}
-%									\includegraphics[width=\textwidth]{rt-s-method2.pdf}
-%									\caption{Response time (hr)}
-%									\label{fig:rt-s-method2}
-%								\end{center}
-%							\end{subfigure}% 
-%							
-%\caption{The impact of slackness parameter on total revenue and response time when users react by adjusting their deadline.} 
-%\label{fig:slackness2}
-%\end{figure}
-%			
-%\subsubsection{Case I- Adjusting Demands}
-%In this case, if the initial charging profile of an EV does not reflect a feasible charging request based on the slackness parameter, the EV owner decreases its demand so it will be able to leave CS at its initial desired deadline.
-Note that the valuation of EVs decreases proportionally, as well.
-Fig.~\ref{fig:slackness1} depicts the result under this policy applied by users.
-As it can be seen in Fig.
-\ref{fig:v-s-method1} and Fig.
-\ref{fig:rt-s-method1}, the general trend is that both total revenue and average response time decrease when slackness value increases.
-This is justifiable based on users reaction.
-When users decrease their demand, less electricity is sold which results in less revenue.
-When total demand decreases, charging can be finished in shorter time which decreases response time.
-Therefore, if users choose the first policy (adjusting their demand), total revenue degrades while response time improves.
-Notice that for the algorithms working under integral revenue model (i.e., \textsc{iOPT}, \ics and \iocs) the total revenue increases with slackness parameter at first (when $s$ grows from $1$ to $1.4$) but then it decreases when the slackness increases more (for $s>1.4$).
-%In our view, this happens because increasing the slackness in integral revenue model makes it possible to \emph{fully} charge more EVs at the beginning as the demands decrease.
-However, when the slackness increases more, it results in opposite effect because the valuation of demands decreases along with the demands' size.
-%			\subsubsection{Case II- Adjusting Deadlines}
-%			In this case, we assume that users are reluctant to decrease their desired demands.
-Instead, they can extend their departure.
-In Fig.~\ref{fig:slackness2} it can be observed that under this behavior of the users, the results are opposite as compared to the previous case (Fig.~\ref{fig:slackness1}).
-When deadlines are extended without demand decrement, the scheduler has more chance to compliance the demands through improved scheduling flexibility.
-Consequently, the total revenue increases by increasing slackness value while average response time degrades.
-%%Also observe the behavior of the online algorithms (i.e., \iocs and \focs) where both total revenue and response time decrease after a specific point that is $s=1.8$.
-When deadlines extend, more EVs have the opportunity of getting charged
-%					
-%We can conclude that when total revenue is more important than the response time, the CS should impose small values of slackness for users that apply the policy of the first case and impose higher values of slackness for the users that apply the second policy.
-The conclusion is reverse for the case that the objective is to have lower response times.
-
-			%In fact, the slackness parameter controls the maximum demand or earliest deadline that an EV can submit to the system.
-Remember that demands are in interval $[\textrm{min}\{\frac{d_i-a_i}{sk_i},U_i\},U_i]$ for EV $i$ meaning that the maximum demand that an EV can submit decreases by increasing slackness parameter.
-A reduction in total demand result in lower charging costs.
-Therefore, the total revenue decreases with higher values of parameter $s$ as in Fig.
-\ref{fig:v-s}.
-			%Also, the percentage of EVs that received all of their requested demand increases based on the same fact.
-The main goal of this simulation is to observe that obtained theoretical result on approximation ratio is confirmed as optimality gap of the SCS algorithm reduces by increasing $s$ in Fig.
-\ref{fig:v-s}.
-\vspace{0.1mm}
-\vspace{-4mm}
-			\section{Conclusion}
-			\label{sec:conclusion}
-This paper proposed offline and online algorithms for the EV charging scheduling problem under fractional and integral revenue models in an adaptive charging network (ACN).
-The problem is different, and more challenging than the existing single station EV charging scheduling problems since it requires respecting the aggregate peak charging demand of the ACN.
-%More importantly, the problem is online in nature in the sense that the EVs arrive in time and the scheduler has no information regarding future arrivals. 
-As the notable contributions, our proposed online algorithm for fractional revenue model achieves constant competitive ratio of $2$.
-Moreover, the offline integral algorithm achieves a theoretical bound on the optimality gap and approximates the optimum by $92\%$, on average in experiments.
-As a future work, we plan to study the problem under posted pricing mechanism where the charging station publishes the unit price of the power (which can be varied over time) and the users can accept or reject the offer.
-\revv{Another interesting future direction is to tackle the EV charging scheduling in market-based scenarios where the prices change over time.}
-%As a future work, we plan to analyze the truthfulness of the algorithms to make sure that it is a dominant strategy for the EV owners to declare their true valuations and availabilities.
-\vspace{-4mm}
-
-%\input{intro.tex}
-%\input{rel.tex}
-%\input{sys.tex}		
-%\input{fraction.sol.tex}		
-%\input{integral.sol.tex}
-%\input{exp.tex}
-%%%\vspace{0.1mm}
-%\input{conc.tex}
-%\newpage
-%ss
-%\newpage
-%\pagestyle{empty}
-\bibliography{ref}{}
-\vspace{-2.8mm}
-\bibliographystyle{ieeetr}
-
-\input{app.tex}
-
-\begin{comment}
-\vspace{-10mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{alinia.jpg}}]{Bahram Alinia} received a B.Sc degree in computer science from University of Tabriz, Tabriz, Iran and a masters degree in Information Technology Engineering from University of Tehran, Tehran, Iran.
-He was a Researcher with the School of Computer Science, Institute for Research in Fundamental Sciences, Iran, from 2009 to 2012.
-He is currently a Ph.D.
-student in service architecture lab, Institute Telecom SudParis, France and participated in several European projects in the domain of smart grids.
-His research area includes wireless communications, energy systems, transportation electrification, algorithm design and approximation.
-\end{IEEEbiography}
-%\vspace{-30mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{hajiesmaili.jpg}}]{Mohammad H.
-Hajiesmaili} received the B.Sc.
-degree from the Department of Computer Engineering, Sharif University of Technology, Iran, in 2007, and the M.Sc.
-and Ph.D.
-degrees from the Electrical and Computer Engineering Department, University of Tehran, Iran, in 2009 and 2014, respectively.
-He was a Post-Doctoral Fellow with the Department of Information Engineering, the Chinese University of Hong Kong, from 2014 to 2016, and with the Department of Electrical and Computer Engineering, Johns Hopkins University, form 2017 to 2018.
-He is currently a Research Assistant Professor with the College of Information and Computer Sciences, University of Massachusetts, Amherst.
-His research interests include optimization, algorithm, and mechanism design in energy systems, electricity market, transportation networks, and multimedia networks.
-\end{IEEEbiography}
-%\vspace{-30mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{crespi.jpg}}]{Prof.
-No\"{e}l Crespi} holds Masters degrees from the Universities of Orsay (Paris 11) and Kent (UK), a diplome d'ing\'{e}nieur from Telecom ParisTech, a Ph.D and an Habilitation from UPMC (Paris-Sorbonne University).
-From 1993 he worked at CLIP, Bouygues Telecom and then at Orange Labs in 1995.
-He took leading roles in the creation of new services with the successful conception and launch of Orange prepaid service, and in standardisation (from rapporteurship of IN standard to coordination of all mobile standards activities for Orange).
-In 1999, he joined Nortel Networks as telephony program manager, architecting core network products for EMEA region.
-He joined Institut Mines-Telecom in 2002 and is currently professor and Program Director, leading the Service Architecture Lab.
-He coordinates the standardisation activities for Institut Mines-Telecom at ITU-T and ETSI.
-He is also an adjunct professor at KAIST (South Korea), an affiliate professor at Concordia University (Canada), and gest researcher at the University of Goettingen (Germany).
-He is the scientific director the French-Korean laboratory ILLUMINE.
-His current research interests are in Data Analytics, Internet of Things and Softwarisation.
-http://noelcrespi.wp.tem-tsp.eu/
-\end{IEEEbiography}	
-\end{comment}
-\end{document}

### 2025-03-09 TSUSC/relatedWork.tex
move resources from other repos

\section{Related Work}
\label{sec:rel}
There is an extensive work in the broad topic of EV demand management and scheduling~\cite{mukherjee2015review} such as as optimal operations with EV coordination and congestion management~\cite{rigas2013congestion,hu2013coordinated}, EV scheduling with incorporation of renewable energy, and energy storage systems~\cite{de2017impact,shafie2018innovative}, and pricing and bidding~\cite{huang2014distribution}. 
We focus on the literature related to peak-constrained EV charging scheduling.
\subsubsection{Peak-Constrained EV Charging Scheduling}
\label{sec:rel:peakconstrained}			
There is an extensive literature on EV charging scheduling problem focusing on single station~\cite{Tang,Wen}, while the local and global peak constraints are omitted or only the local peak is considered. As we discuss in Section~\ref{sec:problem}, the global optimal solution cannot be obtained by separately solving the single station problems. Hence, those solutions cannot be directly applied to the multiple station scenario with global peak constraints.

%A scenario that local and global peak constraints exist is the case that scheduling is required for a charging network for multiple stations. 
Studies in \cite{He,malhotra2017distributed,Moradijoz,DWang,Zeng,Shaaban} tackled charging scheduling problem in multiple stations. The authors in~\cite{He} studied a global cost minimization EV charging scheduling problem, without taking into account the the maximum peak demand that the system can tolerate.  
%We solve the issue by constraining local and global peaks. However, to meet the peak constraints, it may not be feasible to respond to all charging demands. Consequently, only a subset of EVs can be charged~\cite{Xiang}, which is captured in our problem formulation. 
\cite{DWang,Zeng,Shaaban} considered an \textit{offline} multi-microgrid system with global peak constraint where each microgrid has a station and the goal is to manage electricity exchange between microgrids to minimize the operating costs. The authors assume that required information about EVs is available by forecast which may not represent a real scenario.

%A similar assumption is made in \cite{Zeng,Shaaban} where the objective is to maximize total utility of EVs and aggregators in a distribution network.
%\rev{To be removed: In our solution, we applied a priority based selection process (based on the EVs' valuation) to respond to the demands to make sure that total peak respects the constraints. The selection process can be made based on different criteria such as the value of each charging request \cite{Lee, Xiang} or the priority.}
%To avoid big billing cost in peak hours, \cite{Moradijoz} proposed a solution based on genetic algorithm to find optimal capacity and location of parking lots for serving demands in peak hours with the goal of maximizing total benefit of all stations. Although authors studied the problem under multiple station setting, their solution is not applicable to our setting when the stations are already set up. 
The authors in~\cite{malhotra2017distributed} use a similar model as in this paper, where both local and global peak constraints are considered. However, the authors solve the single-slot problem, which fails to provide a general solution taking into account EVs' arrival and departure times as considered in our study.
Finally, as an alternative approach to control the peak~\cite{Zhang2015eEnergy,lee2019learning}, some studies directly target minimizing the peak~\cite{Zhao}. 
%In~\cite{Zhao}, an online algorithm is developed for EV charging to minimize the peak and \cite{Karfopoulos} proposed a valley filling method by leveraging V2G in peak hours. 
Although the peak is minimized in above works, it cannot guarantee that the minimized peak is tolerable by the ACN.

\subsubsection{Scheduling Under Demand Uncertainty}
A main challenge in EV scheduling problem is to cope with demand uncertainty. Many studies including \cite{Shroff2014,Tang,WTang,Chen,Xiang,Zhao,Robu,Hajiesmaili2016Online,hajiesmaili2017crowd} addressed online scheduling problem with different objectives, including social welfare, station revenue maximization, and maximum utilization of renewable sources.

%\cite{Shroff2014,Xiang} studied the problem of maximizing social welfare considering the benefit for both users and service provider. \cite{Tang} and \cite{WTang} developed algorithms to minimize the charging price for the station, where the proposed algorithm in \cite{Tang} is $2.39$-competitive. 
%An online algorithm developed in \cite{Chen} to optimize overall operating profit of the service provider. 
%In \cite{Robu}, an online $2$-competitive algorithm is proposed for a single station, assuming that EVs are capable of being discharged in a negligible amount of time. The assumption, however, is not realistic for EVs.

Our problem in this paper is unique from above works in many respects. First, we study the problem in an ACN where several stations exist, while none of the above studies solve the problem under this setting. Second, the previous algorithms do not work for both integral and fractional charging models. In more relevant theoretical problems, \cite{WTang,Chen} put no limit on the charging rate of EVs which makes their solution impractical in real scenarios. Also, \cite{WTang,Tang, Shroff2014,Chen,Zhao} do not consider the peak limit of the station. 
%\revv{Note that some studies~\cite{jin2017optimal} tackle the scenarios of satisfying the large demands (possibly EV demands) by participating in electricity market. This study assumes that the electricity price is given and fixed, and leaves the case of real-time pricing as the future direction. In addition, there are studies that incorporate prediction in online EV charging scheduling~\cite{wang2017predictive,chen2014distributional}. The prediction-based approaches achieve satisfactory performance for the scenarios that follow prediction. Deviation from prediction models, however, degrades their performance. Our approach, on the other hand, has no assumptions on modeling/prediction, and in this way, is robust against any uncertainty in the instances to the problem.} 
Finally, in~\cite{Alinia2018ITS}, we considered a simplified EV charging scheduling in fractional model without global peak constraints and devised heuristic algorithms (without competitive and approximation analysis) with on-arrival commitment for EVs to notify the amount that they can receive by their departure.
%In this paper, we consider these limitations and develop online and offline algorithms for fractional and integral revenue models in an ACN and provide theoretical bounds on their performance.

%It is important to note that there is a considerable similarity between EV scheduling problem and classical job scheduling problem \cite{}. However, most algorithm developed for job scheduling problem  do not consider a limit on processing rate of the jobs.

%\cite{Shroff2014} and \cite{Stein2012} study social welfare maximization problem while the profit of both EV owners and station is considered.  social welfare of the EV owners \cite{Stein2012}, charging cost \cite{Tang,WTang}, and total value of fully charged EVs \cite{Azar}). In addition, \cite{WTang, Tang,Shroff2014,Zhao} do not take into account the peak limitation of station. }

\subsubsection{Worst-case Analysis in Similar Scheduling Problems}
\label{sec:rel:comp}
	Similar underlying scheduling problems with slightly different settings have been studied in the literature in both offline and online settings. In offline setting, the problem is more interesting under integral revenue model where the problem becomes a combinatorial optimization problem and approximation algorithms have been used to find effective solutions. 
The performance of an approximation algorithm is determined by its \emph{approximation ratio} for offline 
algorithms. On the other hand, competitive online algorithms are used in the online setting and \emph{competitive ratio} is the performance metric which compares the algorithm's result to the offline optimal solution.

\textit{Offline integral model}: Under integral revenue model, \cite{Jain} proposes an offline algorithm for scheduling of batch jobs in cloud computing which is similar to EV scheduling problem. It is assumed that all jobs are available to be processed at time 0. The authors propose a $\frac{C}{C-k}.\frac{s}{s-1}$-approximation algorithm where $C$ is the cloud capacity and $s$ is the ``slackness parameter'' (see section \ref{sec:acn} for the definition). 
Similarly, \cite{yao2016real} tackles the offline integral problem and proposes a convex relaxation method to find a near-optimal solution. No theoretical bound is provided for the algorithm and the performance is examined by simulation results. In this paper, we propose \ics for the EV scheduling problem with slightly different settings in the constraint sets, and tackle the problem in online setting and provide approximation analysis under several scenarios.

%\textit{Offline fractional model}: In case of fractional revenue model (for offline case), the scheduling problem is more straightforward to tackle since the underlying problem is linear. In this paper, we propose \fcs as an optimal solution for offline fractional case with low time complexity.

\textit{Online fractional model}: In our recent study \cite{alinia2018competitive}, 
we proposed two online algorithms referred to as WFAIR and WRAND for EV scheduling problem. The proposed algorithms provide a competitive ratio of $2-1/U$ where $U$ is "scarcity level". However, the result only holds when all EVs have the same maximum charging rate. Also, \cite{alinia2018competitive} does not study the integral revenue model. In this paper, we propose \focs as an online algorithm. Moreover, the current study investigates both fractional and integral revenue model while considering total peak constraint in the formulation and addressing multiple charging station scenario. 
In another work~\cite{firstfit}, two simple and natural online algorithms called \textsc{FirstFit} and \textsc{EndFit} were developed and are proved to be 2-competitive. \focs is an extension of these algorithms by taking into account the maximum charging rate of the EVs and multiple charging station scenario (see ``Remarks'' at Section IV). As recent study, \cite{zheng2016online} provides online algorithms for EV scheduling problem, however, they do not take into account global peak constraint in the underlying problem.

\textit{Online integral model}: Another direction is to tackle online scenario under integral revenue model, where the scheduling problem becomes fundamentally more challenging. We note that the integral scheduling problem is strongly NP-Hard even in the offline case \cite{de2018complexity}. Due to combined online and combinatorial challenges, there are very limited studies in this category. \cite{lucier2013efficient} provides an online algorithm without considering the maximum processing rate of the jobs where its competitive ratio can be arbitrary bad depending on ``slackness'' parameter. 
Our work extends this study for multiple station scenario and considering maximum charging rate for the EVs.

### 2025-03-09 TSUSC/simulation.tex
move resources from other repos

--- 2019-08-28 TSC/R1/TSC.tex
@@
-\documentclass[journal]{IEEEtran}
-%\usepackage{float}
-\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-\usepackage{amssymb,amsmath}
-\usepackage[font=small,skip=10pt]{caption}
-\usepackage{subcaption}
-\usepackage{comment}
-\usepackage{color,soul}
-%\usepackage{ragged2e} 
-\usepackage{algorithmicx}
-\usepackage{algpseudocode}
-\usepackage{amsthm}
-\usepackage{cite}
-\usepackage{array}
-%\usepackage{nopageno}
-\usepackage{url}
-%\usepackage{hyperref}
-%\usepackage{ulem}
-
-% *** CITATION PACKAGES ***
-%
-\usepackage{cite}
-\usepackage{color}
-\usepackage{xspace}
-\usepackage{multirow}
-\usepackage{hhline}
-%\usepackage[pdftex]{graphicx}
-
-% *** GRAPHICS RELATED PACKAGES1 ***
-%
-
-% more space
-%\usepackage{txfonts}
-\addtolength{\abovedisplayskip}{-2mm}
-\addtolength{\belowdisplayskip}{-2mm}
-\addtolength{\parskip}{-.15mm}
-%\addtolength{\arraycolsep}{-.75mm}
-\addtolength{\abovecaptionskip}{-1mm}
-\addtolength{\belowcaptionskip}{-1mm}
-%\renewcommand{\baselinestretch}{0.9}
-
-\ifCLASSINFOpdf
-\usepackage[pdftex]{graphicx}
-\graphicspath{{fig/}{../}}
-\DeclareGraphicsExtensions{.pdf,.jpeg,.png,.jpg}
-\else
-\usepackage[dvips]{graphicx}
-\graphicspath{{fig/}{../}}
-\DeclareGraphicsExtensions{.eps}
-\fi
-
-%\usepackage[caption=false,font=footnotesize]{subfig}
-%
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-%\setlength{\intextsep}{-1ex} % remove extra space above and below in-line float
-
-\renewcommand{\baselinestretch}{1}
-
-\ifodd 1
-\newcommand{\bt}[1]{{\color{blue}#1}}%revise of the text
-\newcommand{\rev}[1]{{\color{black}#1}}%revise of the text
-\newcommand{\revv}[1]{{\color{black}#1}}%revise of the text
-\newcommand{\com}[1]{\textbf{\color{red}(COMMENT: #1)}}%comment of the text
-\else
-\newcommand{\bt}[1]{#1}
-\newcommand{\rev}[1]{#1}
-\newcommand{\com}[1]{}
-\fi
-
-\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-
-%\newcommand{\opt}{\textsc{OPT}\xspace}
-\newcommand{\sa}{\textsc{SmartAllocate}}
-\newcommand{\rc}{\textsc{ReConsider}}
-\newcommand{\bc}{\textsc{BetaCover}}
-\newcommand{\ics}{\textsc{iCS}\xspace}
-\newcommand{\fcs}{\textsc{fCS}\xspace}
-\newcommand{\MCSP}{\textsf{SPAN}\xspace}
-\newcommand{\dMCSP}{\textsf{dSPAN}\xspace}
-\newcommand{\focs}{\textsc{foCS}\xspace}
-\newcommand{\iocs}{\textsc{ioCS}\xspace}
-\newcommand{\finalalg}{\textsc{ioCS+}\xspace}
-\newcommand{\opt}{\textsc{OPT}\xspace}
-\newcommand{\alg}{\textsc{ALG}\xspace}
-\newcommand{\rtl}{\textsc{GreedyRTL}\xspace}
-\newcommand{\iolp}{\textsc{ioLP}\xspace}
-\newcommand{\folp}{\textsc{foLP}\xspace}
-
-\newcommand{\be}{\begin{equation}}
-	\newcommand{\ee}{\end{equation}}
-\newcommand{\bee}{\begin{eqnarray}}
-	\newcommand{\eee}{\end{eqnarray}}
-\newcommand{\bse}{\begin{subequations}}
-	\newcommand{\ese}{\end{subequations}}
-%\def\bee#1\eee{\begin{align}#1\end{align}}
-\newcommand{\nnb}{\nonumber}
-
-\newtheorem{lem}{Lemma}
-\newtheorem{propos}{Proposition}
-\newtheorem{thm}{Theorem}
-\newtheorem{defi}{Definition}
-
-%in terms of practical feasibility and characterizing the maximum benefits of D2D load balancing is
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{corollary}[theorem]{Corollary}
-
-\makeatletter
-\newcommand\semiHuge{\@setfontsize\semiHuge{22.52}{27.38}}
-\makeatother
-\begin{document}
-	%\semiHuge
-	\title{Online EV Scheduling Algorithms for Adaptive Charging Networks with Global Peak Constraints}
-	\author{\#}
-
-	\author{Bahram Alinia, Mohammad H. Hajiesmaili, Zachary J. Lee, Noel Crespi, and Enrique Mallada
-
-		\thanks{ B. Alinia and N. Crespi are with the department of Networks and Mobile Multimedia Services (RS2M), Institut Mines-Telecom,
-			Telecom SudParis, Evry, France (e-mail: bahram.alinia@telecom-sudparis.eu, noel.crespi@mines-telecom.fr).
-
-			M. H. Hajiesmaili and E. Mallada are with the Department of Electrical and Computer Engineering, Johns Hopkins University, Baltimore, MD, USA (e-mail: \{hajiesmaili,mallada\}@jhu.edu).
-
-			Z. J. Lee is with the Department of Electrical Engineering, California Institute of Technology, Pasadena, CA, USA (e-mail: zlee@caltech.edu).
-		} }
-
-		\maketitle
-
-\begin{abstract}
-%			With the rapid growth of electric vehicles, their high demand charging jobs pose an immense challenge to the grid infrastructure. 
-			This paper tackles online scheduling of electric vehicles (EVs) in an adaptive charging network (ACN) with local and global peak constraints.
-Given the aggregate charging demand of the EVs and the peak constraints of the ACN, it might be infeasible to fully charge all the EVs according to their charging demand.
-Two alternatives in such resource-limited scenarios are to maximize the social welfare by partially charging the EVs (fractional model) or selecting a subset of  EVs and fully charge them (integral model).
-%			This paper tackles both fractional and integral models. 
-			The critical challenge is the need for online solution design since in practical scenario\revv{s} the scheduler has no information of future arrivals of EVs in a time-coupled underlying problem. 
-			For the fractional model, we devise both offline and online algorithms.
-We prove that the offline algorithm is optimal.
-Using competitive ratio as the performance measure, we prove the online algorithm achieves a competitive ratio of 2.
-The integral model, however, is more challenging since the underlying problem is \bt{strongly} NP-hard due to 0/1 selection criteria of EVs.
-Hence, efficient solution design is challenging even in offline setting.
-We devise a low-complexity primal-dual scheduling algorithm that achieves a bounded approximation ratio.
-Built upon the offline approximate algorithm, we propose an online algorithm and analyze its competitive ratio in special cases.
-Extensive trace-driven experimental results show that the performance of the proposed online algorithms is close to the offline optimum, and outperform the existing solutions.
-%			\rev{In particular, the grid and electricity providers should be aware of the electricity peak.	It is known in electricity market that the spot price is a dominating factor in billing cost.
-Hence, the utility companies need to identify a global peak constraint for the cost management purpose.
-This paper studies the online EV charging scheduling problem in a utility that offers EV charging service in a set of CSs, each of which having limited output power (referred to as local peak constraint) while taking into account the global peak constraint.
-The scheduling problem in this scenario comes with unique challenges that is not tackled previously.}
-
-%			\rev{The problem objective is to maximize total revenue of the CSs.}
-
-\end{abstract}
-		\begin{IEEEkeywords}
-			Electric Vehicle, Online Scheduling, Approximation Algorithm, Competitive Analysis
-		\end{IEEEkeywords}
-
-		\section{Introduction}
-\label{sec:intro}	
-%		\IEEEPARstart{A}{s} 
-%		a result of global warming and environmental concerns through dependence on fossil fuels, there has been a rapid proliferation in deploying renewable energy sources. 
-\IEEEPARstart{T}{o} promote quick adoption of renewable energy sources, electrification of vehicles is a trend that has been globally advocated in recent years.
-\rev{According to a Bloomberg report, EVs will account for more than half of the new car sales by $2040$~\cite{bloomberg}.
-	%the global sale of EVs increased by $80\%$ in $2015$~\cite{EVSales}.
-	%		With the significant advantage of electric vehicles (EVs) in being an environment friendly product, the global interest for EVs is rapidly growing, such that  
-	Consequently, it is expected that demand from EV charging will constitute a considerable portion of total demand. 
-	Currently, transportation consumes $29\%$ of total energy in the US, while electricity production consumes $40\%$~\cite{Zhao}.} 
-%Vehicles seen accounting for 5\% of electricity use by $2040$~\cite{EVSales2}}
-%%%\revv{\sout{Hence, rapid electrification of the vehicles makes the total electricity demand of EVs significant.}}
-
-\revv{EV charging demand is a typical example of a deferrable load, and there is often considerable flexibility in the charging schedule.
-This property makes the problem of EV charging scheduling  important and there is an extensive research along this direction in the literature (see the recent survey~\cite{mukherjee2015review}, and references therein).
-In most of the existing works, the EV charging demand is treated as a constraint to the problem in a low-load regime~\cite{Tang}.
-Motivated by rapid proliferation of EVs, this work tackles the EV scheduling in high-load regime, where given the aggregate charging demand of the EVs and the peak constraints of the charging network, it is not feasible to fully charge all the EVs according to their charging demand.}
-%		\subsection{Microgrid: Definition, Potentials, and Challenges}
-%		\label{sec:introA}
-%		A common trend in the smart grid era is to install renewable energy sources in distributed manner.
-More specifically, medium or large commercial and industrial  customers such as universities, headquarters, etc.,  can take control of their own energy consumption by local deployment of renewable sources~\cite{Hajiesmaili2016Online}.
-In this setting, the residual demand, i.e., total demand subtracted by the local renewable supply, can be acquired from the external grid.
-
-%		In addition to clean energy production, the owner of microgrid also enjoys more power sustainability and reliability, and the ability to proactively manage the energy costs.
-
-More specifically, this paper studies resource-constrained EV charging scheduling in an adaptive charging network (ACN) governed by a single operator in a campus-scale location such as a university, a headquarter\rev{s}, etc.
-\cite{wu2017two}.
-\rev{A notable example is the Caltech ACN~\cite{lee2016adaptive} where individual charging ports are organized into several \textit{charging stations} (CSs) which are dispersed in a \textit{charging network}} with the capability of adaptive charging of the EVs.
-The problem is different from EV charging scheduling \revv{with capacity constraint} in single station scenarios~\cite{Tang,Wen,Shroff2014,WTang,Chen,Xiang,Zhao,Robu} (we refer to~Section~\ref{sec:rel} for detailed discussions on related work), because of the essential need to respect the aggregate peak demand of the ACN.
-\revv{Note that, the ACN operator might limit the total power drawn from EVs to control costs~\cite{PeakPrice,Zhang2015eEnergy}, reserve the capacity for other loads, and/or participate in demand-response programs.}
-%		The EV charging loads are usually flexible and deferrable, which means that their load can be scheduled~\cite{moghaddam2017smart,DWang} to shape the total demand over time. 
-%The aim of this paper is to use the deferrable property of EVs and schedule their charging jobs, so as to \rev{maximize the revenue of the ACN}.	
-%		We refer to Section~\ref{sec:rel} for the literature review.
-
-%		In particular, real-world pricing scheme for large customers is usually a hybrid time-of-use and peak-based charging model where the peak demand can significantly impact the total energy cost, e.g., the peak price is often more than $100$ times higher than the spot price~\cite{PeakPrice,Zhang2015eEnergy}.
-Considering total aggregate demand, the peak charge portion could be as large as $20\%-80\%$ of total cost~\cite{Xu2014Reducing}.
-Consequently, a substantial cost reduction could be achieved if the total peak-demand can be proactively controlled \cite{liao2015dispatch}.
-
-%		\subsection{EV Charging Scheduling in the ACN}
-%		With the proliferation of EVs, the charging requirement of the microgrid EVs could be a portion of total microgrid electricity demand.
-
-%		To respond the electricity demand of EVs, CSs are being used where EVs can recourse to charge their battery \cite{He,liao2015dispatch,Tang}.
-There can be few to many CSs dispersed in an ACN, e.g., each for a parking garage of a building in a university campus.
-In this scenario, all parking stations are governed by a facility operator and a \textit{global} peak demand constraint is determined such that the aggregate charging demand in the entire network is less than this global peak demand \cite{DWang,Hoog}.
-
-%		The charging scheduling of the EVs with the goal of respecting the \textit{global aggregate peak constraint}, however, is a unique problem which is different from the single station EV charging scheduling.
-Most of the existing work in the literature, tackle the problem in the single parking station scenario.
-We refer to Section~\ref{sec:rel} for in-depth discussion.
-As discussed in Section \ref{sec:problem}, the global optimal solution cannot be obtained by separately solving the single station problems.
-%		On the other hand, there are only a few studies that provide global optimal solution for charging scheduling of EVs \cite{He, Moradijoz, Malhotra,Zeng,Shaaban,DWang}.
-Despite elegant results, the underlying problems, e.g., charging cost minimization problem in \cite{He}, average operating cost minimization with optimal electricity exchange capacity problem in \cite{DWang}, optimal station capacity problem in~\cite{Moradijoz}, user convenience maximization problem in~\cite{Malhotra}, joint optimization of system profit and user experience in~\cite{Shaaban,Zeng} are different from the problem studied in this paper.
-
-%		\subsection{Problem, Challenges, and Contributions}
-We consider a scenario with multiple EVs where each EV has different charging profile in terms of availability, charging demand, charging rate limit, and valuation of getting charged \revv{(for details see Section~\ref{sec:ev})}.
-We formulate an online EV charging scheduling problem with the goal of \textit{selecting} and \textit{scheduling} a subset of EVs such that: (1) the charging demand of the selected EVs are (fully or partially) satisfied; (2) the charging rate limit of EV batteries are respected, (3) the global peak constraint of the ACN is satisfied~\cite{lee2016adaptive}; (4) the local peak constraint of each CS is respected;  and finally, (5) the total revenue obtained by the valuation of the EVs is maximized.
-
-%		of maximizing the revenue of the ACN.
-The constraints are the \textit{local} peak constraint of each CS, and the \textit{global} peak constraint that limits the accumulative charging demand drawn from the entire network of stations (decided by the administration of the ACN to control total peak demand~\cite{lee2016adaptive}).
-
-There are two main challenges in the design and implementation of scheduling algorithms for EVs satisfying the goals mentioned above.
-\rev{Firstly, the problem calls for online scheduling design.} In practice, EVs arrive to the CS in online fashion and the scheduler has no information about the arrival and demand of the future EVs.
-Secondly, the underlying optimization problem in integral model is \bt{strongly} NP-hard even in offline case \rev{(see Section~\ref{sec:integral})}.
-This is because the problem is a mixed integer linear problem and a ``time-expanded'' extension of knapsack problem which is known as a classic NP-hard problem.
-In this paper, we tackle the challenge of online design by following competitive algorithm design~\cite{borodin2005online} and the challenge of NP-hardness by pursuing approximation algorithm design~\cite{approx} and make the following contributions:
-
-$\vartriangleright$ We first consider a \textit{fractional model} (where EVs can be charged partially and the revenue is proportional accordingly) and design an optimal offline scheduling algorithm. 
-%In addition to provide efficient result, the algorithm has a further elegant step to apply a valley filling strategy to further reduce the peak demand of EV charging without degrading total revenue. 
-We then develop an efficient online algorithm in which no exact or stochastic information about the future EV arrivals is given.
-Despite its simplicity, the algorithm is proved to be $2$-competitive with optimal offline solution, i.e., the revenue of the proposed online algorithm is at least $1/2$ of the offline optimum, regardless of input sequence.
-Even though there are competitive algorithms in the literature for similar problems, to the best of our knowledge, our algorithm is the first $2$-competitive algorithm \rev{which considers the} charging rate limits.
-
-$\vartriangleright$ We next study \rev{the} more challenging scenario of \rev{the} \textit{integral model}\rev{, }where EVs must receive all their demand to make revenue.
-We first propose a polynomial-time primal-dual offline approximate algorithm.
-We analyze the approximation ratio of the algorithm and by strengthening the linear relaxed version of the mixed integer problem~\cite{Carr}, we obtain an approximation ratio of $\alpha =1+\sum_{j=1}^m {\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}$, where $p_j$ is local peak constraint in station $j$, $q_j$ is the maximum charging rate of the EVs in station $j$ and $s$ is a slackness parameter.
-We highlight that when $p_j \gg q_j$ and $s$ is \rev{large} enough, then $\alpha \approx m+1$, where $m$ is the number of stations in the ACN.
-Built on the basis of the offline algorithm, we devise an online algorithm, and discuss its competitive ratio in special cases.
-%In particular, the competitive ratio is $b\Big(1+\frac{p_j}{p_j-q_j}\cdot\frac{s}{s-1}\Big)$ for single station scenario, where $b$ is the number of batches with the same arrival time.
-
-$\vartriangleright$ We conduct a set of  simulations to evaluate the performance of our proposed algorithms. 
-%For offline scheduling problem under integral charging model, the results  demonstrate that the proposed approximation algorithm is close to the optimal solution and is significantly better than the obtained theoretical bounds.
-The results of online algorithms for both integral and fractional settings are close to the optimum (within $90\%$ and $94\%$ for integral and fractional models in a representative scenario).
-In addition, our algorithm outperforms the existing scheduling algorithm in Caltech ACN~\cite{lee2016adaptive} by $35\%$ for integral revenue model.
-
-\bt{This paper represents follow-up work to our previous study~\cite{alinia2018competitive}, where we address a simplified version of the problems studied in this paper in fractional revenue model.
-The competitive analysis in~\cite{alinia2018competitive} is done under the assumption that all EVs have the same maximum charging rate.
-Also, \cite{alinia2018competitive} does not study the integral revenue model.
-In this paper, we extend the results and propose a 2-competitive online algorithm with no assumption on the input parameters.
-Also, the current study investigates both fractional and integral revenue models while considering global peak constraint in the formulation and addressing multiple charging station scenario.
-Last, we consider more realistic trace-driven experiments in this paper and compare the results to an existing real-world scheduling algorithm.}
-%The simulation section also discusses on the positive and negative effects of slackness parameter in different scenarios.
-
-%To the best of our knowledge, this problem is not addressed yet in previous studies.
-
-%		\subsection{Paper Organization}
-%		The rest of this paper is organized as follows. Section~\ref{sec:rel} reviews the literature. In Section \ref{sec:model}, the system model  and problem formulation are described. 
-%		Section \ref{sec:fractional} provides offline and online algorithms for fractional model.
-We study integral model in Section \ref{sec:integral} and propose online and offline algorithms.
-The simulation results are reported in Section~\ref{sec:simul}.
-Section~\ref{sec:conclusion} concludes the paper and highlights future directions.
-
-\section{Related Work}
-\label{sec:rel}
-\revv{There is an extensive work in the general topic of EV demand management and scheduling~\cite{mukherjee2015review} by considering different scenarios such as optimal operations with EV coordination and congestion management~\cite{mukherjee2017distributed,rigas2013congestion,hu2013coordinated}, EV scheduling with incorporation of renewable energy, and energy storage systems~\cite{de2017impact,shafie2018innovative}, and pricing and bidding~\cite{huang2014distribution,hou2019bidding} In this section, we focus on the literature related to peak-constrained EV charging scheduling in single and multiple stations.}
-\subsubsection{Peak-Constrained EV Charging Scheduling}
-\label{sec:rel:peakconstrained}			
-\revv{There is an extensive literature on EV charging scheduling problem focusing on single CS~\cite{Tang,Wen}, while the local and global peak constraints are omitted or only the local peak is considered.}	As we discuss in Section~\ref{sec:problem}, the global optimal solution cannot be obtained by separately solving the single station problems.
-Hence, those solutions cannot be directly applied to the multiple CS scenario with global peak constraints.
-
-%A scenario that local and global peak constraints exist is the case that scheduling is required for a charging network for multiple CSs. 
-Studies in \cite{He,malhotra2017distributed,Moradijoz,DWang,Zeng,Shaaban} tackled charging scheduling problem in multiple CSs.
-The authors in~\cite{He} studied a global cost minimization EV charging scheduling problem.
-However, there is no limit on the maximum peak demand that the system can tolerate.
-Consequently, the peak can be arbitrary high and beyond the physical limit of the transformers in the charging station~\cite{lee2016adaptive} leading to huge electricity bills~\cite{Zhang2015eEnergy}.
-Besides, the charger devices installed in the CSs have limitation on the maximum power that they can transfer in each time unit~\cite{Tesla}.
-%We solve the issue by constraining local and global peaks.
-However, to meet the peak constraints, it may not be feasible to respond to all charging demands.
-Consequently, only a subset of EVs can be charged~\cite{Xiang}, which is captured in our problem formulation.
-\cite{DWang} considered a multi-microgrid system with global peak constraint where each microgrid has a CS and the goal is to manage electricity exchange between microgrids and main grid to minimize the operating costs.
-The authors assume that required information about individual EVs is available by forecast which may not represent a real scenario.
-A similar assumption is made in \cite{Zeng,Shaaban} where the objective is to maximize total utility of EVs and aggregators in a distribution network.
-%\rev{To be removed: In our solution, we applied a priority based selection process (based on the EVs' valuation) to respond to the demands to make sure that total peak respects the constraints.
-The selection process can be made based on different criteria such as the value of each charging request \cite{Lee, Xiang} or the priority.}
-%To avoid big billing cost in peak hours, \cite{Moradijoz} proposed a solution based on genetic algorithm to find optimal capacity and location of parking lots for serving demands in peak hours with the goal of maximizing total benefit of all stations.
-Although authors studied the problem under multiple CS setting, their solution is not applicable to our setting when the CSs are already set up.
-The authors in~\cite{malhotra2017distributed} use a similar model as in this paper, where both local and global peak constraints are considered.
-However, the authors solve the single-slot problem, which fails to provide a general solution taking into account EVs' arrival and departure times as considered in our study.
-Finally, as an alternative approach to control the peak, some studies directly target minimizing the peak~\cite{Zhao, Karfopoulos}.
-In~\cite{Zhao}, an online algorithm is developed for EV charging to minimize the peak and \cite{Karfopoulos} proposed a valley filling method by leveraging V2G in peak hours.
-Although the peak is minimized in above works, it cannot guarantee that the minimized peak is tolerable by the underlying charging network.
-
-\subsubsection{Scheduling Under Demand Uncertainty}
-A main challenge in EV scheduling problem is to cope with demand uncertainty.
-Many studies including \cite{Shroff2014,Tang,WTang,Chen,Xiang,Zhao,Robu} addressed online scheduling problem with different objectives.
-\cite{Shroff2014,Xiang} studied the problem of maximizing social welfare considering the benefit for both users and service provider.
-\cite{Tang} and \cite{WTang} developed algorithms to minimize the charging price for the CS, where the proposed algorithm in \cite{Tang} is $2.39$-competitive.
-%An online algorithm developed in \cite{Chen} to optimize overall operating profit of the service provider. 
-In \cite{Robu}, an online $2$-competitive algorithm is proposed for a single CS, assuming that EVs are capable of being discharged in a negligible amount of time.
-The assumption, however, is not realistic for EVs.
-
-Our problem in this paper is unique from above works in many respects.
-First, we study the problem in an ACN where several CSs exist, while none of the above studies solve the problem under this setting.
-Second, the previous algorithms do not work for both integral and fractional charging models.
-In addition, \cite{WTang,Chen} put no limit on the charging rate of EVs which makes their solution impractical in real scenarios.
-Also, \cite{WTang,Tang, Shroff2014,Chen,Zhao} do not consider the peak limit of the CS.
-\revv{Note that some studies~\cite{jin2017optimal} tackle the scenarios of satisfying the large demands (possibly EV demands) by participating in electricity market.
-This study assumes that the electricity price is given and fixed, and leaves the case of real-time pricing as the future direction.
-In addition, there are studies that incorporate prediction in online EV charging scheduling~\cite{wang2017predictive,chen2014distributional}.
-The prediction-based approaches achieve satisfactory performance for the scenarios that follow prediction.
-Deviation from prediction models, however, degrades their performance.
-Our approach, on the other hand, has no assumptions on modeling/prediction, and in this way, is robust against any uncertainty in the instances to the problem.}
-\revv{Finally, in~\cite{Alinia2018ITS}, we considered a simplified EV charging scheduling in fractional model without global peak constraints and devised heuristic algorithms (without competitive and approximation analysis) with on-arrival commitment for EVs to notify the amount that they can receive by their departure.
-}
-%In this paper, we consider these limitations and develop online and offline algorithms for fractional and integral revenue models in an ACN and provide theoretical bounds on their performance.
-
-%It is important to note that there is a considerable similarity between EV scheduling problem and classical job scheduling problem \cite{}.
-However, most algorithm developed for job scheduling problem  do not consider a limit on processing rate of the jobs.
-
-%\cite{Shroff2014} and \cite{Stein2012} study social welfare maximization problem while the profit of both EV owners and CS is considered.
-social welfare of the EV owners \cite{Stein2012}, charging cost \cite{Tang,WTang}, and total value of fully charged EVs \cite{Azar}).
-In addition, \cite{WTang, Tang,Shroff2014,Zhao} do not take into account the peak limitation of CS.
-}
-
-\subsubsection{Worst-case Analysis in Similar Scheduling Problems}
-\label{sec:rel:comp}
-\bt{
-	Similar underlying scheduling problems with slightly different settings have been studied in the literature in both offline and online settings.
-In offline setting, the problem is more interesting in integral revenue model where the problem becomes a combinatorial optimization problem and approximation algorithms have been used to find effective solutions.
-The performance of an approximation algorithm is determined by its \emph{approximation ratio} for offline 
-algorithms.
-On the other hand, competitive online algorithms are used in the online setting and \emph{competitive ratio} is the performance metric which compares the algorithm's result to the offline optimal solution.
-
-\textit{Offline integral model}: Under integral revenue model, \cite{jain2015near} proposes an offline algorithm for scheduling of batch jobs in cloud computing which is similar to EV scheduling problem.
-It is assumed that all jobs are available to be processed at time 0.
-The authors propose a $\frac{C}{C-k}.\frac{s}{s-1}$-approximation algorithm where $C$ is the cloud capacity and $s$ is the ``slackness parameter'' (See section \ref{sec:acn} for the definition).
-Similarly, \cite{yao2016real} tackles the offline integral problem and proposes a convex relaxation method to find a near-optimal solution.
-No theoretical bound is provided for the algorithm and the performance is examined by simulation results.
-In this paper, we propose \ics for the EV scheduling problem with slightly different settings in the constraint sets, and tackle the problem in online setting in which the full knowledge of the online parameters is not available a priori, and provide approximation ratio under specific scenarios.
-
-\textit{Offline fractional model}: In case of fractional revenue model (for offline case), the scheduling problem is more straightforward to tackle since the underlying problem is linear.
-In this paper, we propose \fcs as an optimal solution for offline fractional case with low time complexity.
-
-\textit{Online fractional model}: In the online scenario, the scheduling problem is fundamentally more challenging. In our recent study \cite{alinia2018competitive}, 
-we proposed two online algorithms referred to as WFAIR and WRAND for EV scheduling problem.
-The proposed algorithms provide a competitive ratio of $2-1/U$ where $U$ is "scarcity level".
-However, the result only holds when all EVs have the same maximum charging rate.
-Also, \cite{alinia2018competitive} does not study the integral revenue model.
-In this paper, we propose \focs as a 2-competitive online algorithm with no assumption on the input parameters.
-Moreover, the current study investigates both fractional and integral revenue model while considering total peak constraint in the formulation and addressing multiple charging station scenario.
-In another work~\cite{firstfit}, two simple and natural online algorithms called \textsc{FirstFit} and \textsc{EndFit} were developed and are proved to be 2-competitive.
-\focs is extension of these algorithms by taking into account the maximum charging rate of the EVs and multiple charging station scenario (see ``Remarks'' at Section IV).
-As recent studies, \cite{zheng2016online,deng2016whether} provide online algorithms for EV scheduling problem, however, they do not take into account global peak constraint in the underlying problem.
-
-\textit{Online integral model}: Another direction is to tackle online scenario under integral revenue model.
-In this setting, the scheduling problem becomes fundamentally more challenging.
-We note that the integral scheduling problem is strongly NP-Hard even in the offline case \cite{de2018complexity}.
-Due to combined online and combinatorial challenges, there are very limited studies in this category.
-\cite{lucier2013efficient} provides an online algorithm without considering the maximum processing rate of the jobs where its competitive ratio can be arbitrary bad depending on ``slackness'' parameter.
-Our work in Section~\ref{sec:onlineint} extends this study for multiple station scenario and considering maximum charging rate for the EVs.
-}
-
-\section{System Model and Problem Formulation}
-		\label{sec:model}
-
-		\subsection{System Model}
-		We consider a time-slotted system model in which the time horizon is divided to $T$ equal length slots ${t=\{1, 2, \dots ,T\}}$ (e.g., $T=24$ with time slots of $1$ hour length).
-\subsubsection{Charging Network}
-\label{sec:acn}
-Our charging network model is inspired by the Caltech ACN~\cite{lee2016adaptive} as illustrated in Fig.~\ref{fig:model-a}.
-In \rev{the} Caltech EV charging network (located in a parking garage), electricity is distributed through a two-level transformer architecture from a main switch panel to multiple EV switch panels (\rev{$2$} panels in the current Caltech ACN).
-Each EV switch panel then is connected to several chargers ($\approx$25 chargers \rev{per panel} in the Caltech ACN).
-The total power drawn from the main switch panel \rev{by} the charging network has a power limit of  $p^\mathsf{total}$, that is determined by the facility operator to control the costs, reserve the capacity for other loads, and/or participate in demand-response programs.
-%This power, where we refer to it as \emph{network power limit} is used for both EV charging as well as non-EV charging purposes (e.g., lighting, fans, etc \cite{lee2016adaptive}). 
-In other words, $p^\mathsf{total}$, which we refer to it as the \textit{global peak}, hereafter, limits the maximum aggregate EV charging load at each time slot. 
-%The global peak must be less than or equal to the value obtained by subtracting non-EV load from network power limit. 
-%When we write \emph{global peak constraint}, it refers to $p^\mathsf{total}$.  
-%$p^\mathsf{total}$ is the maximum allowed aggregated electricity consumption by all stations at each slot and limits the total transferable power to EVs.
-
-We assume that there are $m$ EV switch panels that represent $m$ CSs.
-In addition to the global peak constraint, each CS $j$ has \rev{a} capacity constraint on \rev{its} total power drawn, indicated by $p_j$, and referred to it as the \emph{local peak} constraint.
-The \rev{value of} $p_j$ is determined by the output power limit of the transformers installed between the main switch panel and EV switch panels and could be different for each EV switch panel.
-%installed chargers in a CS have limited output power to charge EVs ~\cite{Wen,Xiang,Tesla}. Therefore, for CS $j$, $p_j$ cannot be more than sum of output power of its chargers. 
-\rev{It is often observed that the charging demand of different CSs (EV switch panels in Fig.~\ref{fig:model-a}) are well below the local peak constraints.}
-To increase the flexibility due to heterogeneous charging demand of CSs, in the Caltech ACN, the global peak constraint of the main switch can be \textit{over-provisioned}, i.e., $p^\mathsf{total}$ is less than the aggregate local peaks,  ($\sum_j p_j\geq p^\mathsf{total}$).
-\rev{While this increases flexibility, it also couples the problem of EV charging scheduling across different CSs.}
-%Despite increased flexibility, the over-provisioning property, however, couples the problem of EV charging scheduling across different CSs. 
-Our solutions in this paper will be centralized ones which can be obtained through communication between the CSs and a central server as illustrated in Fig. \ref{fig:model-b}.
-
-%We make this clear by a simple example.
-Assume $m=2, p^\mathsf{total}=50$ kW and $p_1=p_2=25$ kW.
-In a specific time slot (e.g., $t=1$), the total demand in CS $1$ and $2$ is $40$ kWh and $10$ kWh, respectively.
-According to local peak constraints, it is not feasible to satisfy all demands in a single time slot.
-However, if we had $p_1=p2=50$ kW (e.g., by installing more chargers in the stations) we could be able to satisfy all demands by allocating $40 kW$ in $p_1$ and $10 kW$ in $p_2$ while still not violating $p^\mathsf{total}$.
-In case that $\sum_j p_j\leq p^\mathsf{total}$, the scheduling problem is not challenging and the solution can be obtained by solving the problem locally in each CS.
-If $\sum_j p_j> p^\mathsf{total}$ (which is the case we consider in this paper), a centralized solution is needed that can be obtained through communication between the CS and a central server as illustrated in Fig.
-\ref{fig:model-b}.
-
-\begin{figure}	
-\centering
-\minipage{0.49\textwidth}
-				\begin{subfigure}[b]{0.69\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{model-a.pdf}
-						\caption{Caltech adaptive charging network (ACN)}
-						\label{fig:model-a}
-					\end{center}
-				\end{subfigure}%
-				\begin{subfigure}[b]{0.29\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{model-b.pdf}
-						\caption{Communication model with server}
-						\label{fig:model-b}
-					\end{center}
-				\end{subfigure}%  
-\caption{System model \cite{lee2016adaptive}.} 
-\label{fig:slackness1}
-\endminipage
-\end{figure}
-
-		\begin{table} 
-			\caption{Summary of key notations}
-%			\vspace{-3mm}
-			\label{tbl:not}
-			\begin{center}
-				\begin{tabular}{|c L{6.5cm}|}
-					\hline
-					\textbf{Notation} & \textbf{Description} \\
-					\hline \hline			
-					$T$ & Number of time slots, indexed by $t$\\			
-					$m$ & Number of CSs, indexed by $j$\\			
-					$n$ & Number of EVs, indexed by $i$\\			
-					\hline
-					\hline
-					$a_i$ & Arrival time of EV $i$\\
-					$d_i$ & Departure time of EV $i$\\
-					$D_i$ & Demand of EV $i$\\
-					$v_i$ & Valuation of EV $i$ for receiving its demand $D_i$ \\
-					$k_i$ & Maximum charging rate of EV $i$\\
-					$h(i)$ & CS of EV $i$\\
-					\hline
-					\hline
-					$q_j$ & Maximum $k_i$ among all EVs in CS $j$\\
-					$p_j$ & Maximum aggregate charging rate in station $j$\\
-					$p^\mathsf{total}$ & Maximum aggregate charging rate of all stations\\
-					\hline
-					\hline
-					$y_i^t$ & \textbf{opt. variable}, The amount that EV $i$ is charged at $t$ \\
-					\hline
-				\end{tabular}
-			\end{center}
-		\end{table}
-		\subsubsection{EVs}
-		\label{sec:ev} There are $n$ EVs in the system, indexed by $i$.
-		%, all available at time $t=1$ to be charged\footnote{This assumption is reasonable for the %official buildings where the starting hour of the working day is fixed for all the %employers.
-Extensions to the case with different arrival times for the EVs, is part of the %future work.}.
-		EV $i$ is represented by a charging profile $\langle a_i,d_i,v_i,D_i,k_i\rangle$ 
-		indicating its arrival time, departure time, willingness to pay, charging demand, and maximum charging rate, respectively. 
-		%(depends on physical properties of EVs battery) 
-		More specifically, the charging of EV $i$ can be scheduled within its \emph{availability window}, $[a_i,d_i]$.
-The charging rate at each slot is bounded by $k_i$, a parameter that depends on the physical constraints of the \rev{battery and on-board charger}.
-It is assumed that the charging profile of each EV is feasible with respect to its maximum charging rate and a slackness parameter $s\geq 1$, which is the minimum ratio between the park time of the EV and its minimum charging time, i.e., ${D_i\leq k_i(d_i-a_i+1)/s}$.
-The slackness parameter is imposed to tune the flexibility of the charging scheduling.
-In extreme case $s=1$,  the flexibility is minimum and the flexibility improves as $s$ increases.
-%		Note  that  the slackness  parameter  can  impact  the  total  revenue  and  is  investigated  in  simulation  experiments  in Section~\ref{sec:simul}.
-		We assume that EV owners select their CS, perhaps the nearest to them, and so the assignments are given to the problem. Define $h(i)$ as the CS of EV~$i$.
-		Moreover, $q_j$ denotes the maximum $k_i$ among all EVs in CS $j$, i.e., $q_j=\max_{h(i)=j} k_i$. 
-		\revv{Finally, $v_i$ is the willingness to pay of EV $i$ to receive its entire demand $D_i$ before the departure time $d_i$.
-Note that in resource-constrained EV scheduling in ACN, it is not feasible to fulfill the entire demand of all EVs, hence, the problem turns into a resource allocation one with the goal of maximizing the aggregate value (a.k.a.
-utility) obtained from the EVs.
-In this way, each user can announce its willingness to pay to get charged which is denoted by $v_i$ in the system model.}
-		%We assume that there is no gain for the CS if EV $i$ is partially charged.
-
-		% where $P$ defined as $P:\xi\rightarrow  \mathcal{P}$. 
-\subsubsection{Revenue Models\label{sec:irm}} We consider two revenue models: 
-\textit{(i) Fractional revenue model}: In this model, the fractional charging is allowed, i.e., the revenue from each EV is proportional to the fraction of the demand that is fulfilled \cite{Xiang} (see Eq.~\eqref{Eq:partial_value}).
-We tackle this model in Section~\ref{sec:fractional}.
-\textit{(ii) Integral revenue model}: \rev{In this model, EV $i$ pays $v_i$ if it is fully charged and zero otherwise, i.e., there is no partial revenue for partial charging. }
-%In this model, when EV $i$ is received its demand entirely, the gain is $v_{i}$ and zero, otherwise, i.e., there is no partial revenue for fractional charging. 
-This is the model that is considered in~\cite{WTang,Shroff2014}. We tackle this model in Section~\ref{sec:integral}.
-
-		%The actual aggregated peak of all parking stations must not exceeds global peak constraint.
-
-			\begin{table*}[!t]
-			\centering
-%	\vspace{-3mm}
-			\caption{Proposed algorithms and their properties.}
-			\label{tbl:algs}
-			\begin{tabular}{ | l | c | c | c |c|}
-				\hline
-				\textbf{Algorithm} & \textbf{Revenue model} & \textbf{Type} & \textbf{Optimality} & \textbf{Complexity} \\ \hline\hline    
-				\fcs& fractional& offline& Optimal & $O(n^2T+nT^2)$\\\hline 
-				\ics& integral& offline& ${\Big( 1+\sum_{j=1}^m {\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}\Big)}$-approximate & $O(nT\log T+n^2T)$ \\\hline 
-				\focs & fractional& online& $2$-competitive & $O(n^2T)$\\\hline 
-				\iocs& integral&  online& $b(1+\frac{p}{p-q}.\frac{s}{s-1})$-competitive, $(m=1)$ & $O(n^2T)$\\\hline
-			\end{tabular}
-		\end{table*}
-
-		\subsection{Problem Formulation}
-		\label{sec:problem}
-	We formulate an optimization problem to schedule the charging of the EVs with the objective of maximizing total revenue obtained from charged EVs while respecting local and global peak constraints. 
-		Note that each revenue model makes the underlying optimization problem fundamentally different. More specifically, the fractional charging model is a linear problem. 
-		Integral revenue model, however, turns the underlying charging scheduling problem to a Mixed Integer Linear Program (MILP). The integer nature originates from the $0/1$-selection decision on EVs. 
-%%%Recall that in integral revenue model the revenue is obtained given that the entire demand is fulfilled for the selected EV. 
-		%We skip the explicit formulation of the problem under integral revenue model since it could be contemplated as the linear-relaxed version of the integral revenue model (for more explanation, we refer to the discussions in Section~\ref{sec:fractional}).
-		We formulate Scheduling Problem for Adaptive charging Network (\MCSP) under fractional revenue model as follows: 
-		\bse
-		\bee
-		\MCSP: \max  && \sum\nolimits_{i=1}^n \frac{v_{i}}{D_i}\sum\nolimits_{t=a_i}^{d_i} y_i^t \label{Pobjec} \nonumber\\
-		\text{s.t.} &&\sum\nolimits_{t=a_i}^{d_i} y_i^t\leq D_i,\quad\quad\forall i, \label{ConstPartial} \\
-		&&  \sum\nolimits_{i=1}^n y_i^t\leq p^\mathsf{total} ,\quad\quad\forall t,\label{ConstTotal} \\
-		&&\sum\nolimits_{i:h(i)=j} y_i^t\leq p_j ,\quad\quad\forall t,j,\label{ConstLocal}\\
-		&& y_i^t  \leq \frac{k_i}{D_i}\sum\nolimits_{t^\prime=a_i}^{d_i} y_i^{t^\prime}, \quad\forall i,t,\label{ConstSpeed}\\
-%		&& \rev{y_i^t=0,\forall t\in\{t':t'>d_i \vee t'<a_i\}}, \\
-		\text{vars.} && y_i^t \geq 0, \quad\quad\forall i, t,\label{ConstPositive}\nonumber
-		%&& s_v(t), \quad \forall v,t
-		\eee
-		\ese
-		where $y_i^t$ is the amount that EV $i$ is charged at slot $t$. Constraint (\ref{ConstPartial}) ensures that the aggregate amount received by EV $i$ is at most the demand $D_i$. 
-%		Note that under integral revenue model, when we design our algorithm, we do not allow partial charging. 
-The global and local peak constraints are represented by constraints (\ref{ConstTotal}) and (\ref{ConstLocal}), respectively.
-
-		\revv{The constraint~\eqref{ConstSpeed} enforces the maximum charging rate of EVs.
-The straightforward way to express this constraint is to simply state that at each time slot $t$, the charging rate of EV $i$ should be less than or equal to its maximum charging rate, i.e., $y_i^t\leq k_i, \forall i,t$.
-		However, for the sake of effective algorithm design for integral model and reducing the integrality gap of the relaxed linear problem, this constraint is strengthened in the form of Eq.~\eqref{ConstSpeed}.
-		Note that in case that the aggregated charging of EV $i$ during its availability window is equal to its demand, i.e., $\sum_{t^\prime=a_i}^{d_i} y_i^{t^\prime}= D_i$, Eq.~\eqref{ConstSpeed} reduces to the simple form of $y_i^t\leq k_i$.
-		This is a natural way in approximation algorithm design to improve the performance of the algorithms under linear-relaxation based design~\cite{Carr}. }
-
-The \MCSP is an extension of formulated problem in \cite{Jain} where a job scheduling problem in cloud applications is studied.
-It turns out that the resource allocation problem in cloud systems and the EV charging scheduling problem in a \emph{single station} share similar structure.
-Indeed, each charging profile in our scheduling problem can be seen as a job in cloud system with a deadline, value, and CPU demand.
-The \MCSP, however, comes with an additional constraint~\eqref{ConstTotal}, which makes it different from the problem in \cite{Jain}, such that the existing solution \revv{will not} work in the new setting.
-More importantly, this paper studies both offline and online solutions for the problem in both fractional and integral settings, while \cite{Jain} tackles only the offline integral model.
-
-%(ii) Our solution design and analysis for integral revenue model is based on linear-relaxation primal-dual framework~\cite{Jain}.
-Therefore, in Section \ref{sec:integral} for integral revenue model, we rely on the \MCSP for the analysis of the proposed algorithms and skip to explicitly formulate the original MILP problem.
-
-%		Also, we cover the fractional revenue model and provide theoretical bounds for the proposed algorithms.
-
-%In the next two sections, we devise several algorithms to solve the \MCSP under the two revenue models (integral and fractional) and for both offline and online scenarios. 
-		\section{Fractional Revenue Model}
-		\label{sec:fractional}
-
-%\subsection{Overview of Fractional Revenue Model}
-%\label{sec:frac.overview}				
-		%In the previous section, we devised an approximation algorithm for the integral revenue model in which it is assumed that the obtained revenue is zero if the allocated resource is less than the demand.
-Although this assumption is reasonable in some scenarios,
-%To develop a solution for the \MCSP, we first consider fractional revenue model.
-%However, algorithms for integral revenue model cannot achieve the same performance as the algorithms of this section i.e., \fcs and \focs.
-
-In the fractional model, the revenue of the CS from EV $i$ is directly proportional to the amount of resource that the EV is received, i.e.,
-		\begin{equation}
-			v_i^{\mathsf{f}}=\frac{\sum_t y_i^t}{D_i}v_i,
-			\label{Eq:partial_value}
-		\end{equation}
-		where $v_i$ is the gain, if the entire demand $D_i$ is fulfilled and $v_i^{\mathsf{f}}$ is the fractional gain.
-
-%Under fractional revenue model and without the binary variable of selecting EVs, the underlying problem turns into a linear one. 
-We propose a simple algorithm, called \fcs, with low computational complexity \rev{ of $O(n^2T+nT^2)$} for the fractional model that finds the optimal solution in offline setting.
-Note that even though linear programs can be solved in polynomial time in general, the complexity of our proposed algorithm is much lower than the general linear program algorithms.
-Moreover, our proposed offline algorithm applies a valley-filling strategy to reduce the peak.
-%The details of the proposed algorithm \fcs is given in~\cite{alinia2017online}.
-In the following, the online $2$-competitive algorithm is designed, where no exact information or stochastic modeling of future inputs of the problem is available.
-A summary of proposed algorithms with their complexity and assumptions is given in Table \ref{tbl:algs}.
-
-\revv{
-\subsection{Optimal Offline Design}
-\label{sec:fopt}	
-\bt{
-In this section, we propose an optimal algorithm for offline fractional model.
-As a natural solution, one may think of a greedy algorithm with the strategy as follows: at each time slot, charge the EV with highest unit-value and process others if only the resource cannot be used by this EV (probably due to maximum charging rate constraint).
-This approach is a popular, yet straightforward method in the online scheduling.
-However, it turns out that this approach cannot provide an optimal solution to the problem even in fractional revenue model.
-In fact, this approach only provides a 2-competitive solution.
-i.e., the profit obtained by the algorithm would be $1/2$ of the optimum.
-As an intuition of the proof think of two EVs where the one with lower unit value cannot wait due to its deadline and the EV with higher unit value has a long park time.
-Then, the optimal solution here could be first serving the EV with earlier deadline (and not the one with highest unit values).
-}
-
-We refer the proposed algorithm in this secion as the \fcs and summarize it as Algorithm~\ref{alg:optimal-off}.
-The \fcs works in two phases.
-In the first phase (Section~\ref{sec:ph1}), the algorithm decides on the amount of resource to be allocated to each EV within its availability window and reserves resources accordingly.
-In this phase, the details of allocation is not known.
-The actual resource allocation is done in the second phase (Section~\ref{sec:ph2}) by setting variables $y_i^t$.
-
-Before discussing the details of the algorithm, we give \bt{a definition} and introduce some notations to facilitate our algorithm design.
-
-\begin{defi}
-	Time interval $[\delta,\delta']$ is a ``super interval'' for interval $[t,t']$ if $1\leq \delta\leq t \text{~AND~} t' \leq \delta'\leq T$.
-	Moreover, $\mathcal{I}_{t,t'}$ is the set of all super intervals of interval $I_{t,t'}$ i.e., ${\mathcal{I}_{t,t'}=\{[\delta,\delta']: 1\leq \delta\leq t \text{~AND~} t'\leq \delta'\leq T\}}$.
-\end{defi}
-
-%		For example, $\mathcal{I}_{1,1}=\{I_{1,1},I_{1,2},I_{1,3},\dots ,I_{1,T}\}$. 
-The number of super intervals of an interval is at most $T^2$ and at least one (for interval $[1,T]$).
-
-Let $R_i$ be the amount of resource that is reserved for EV $i$ by the \fcs and $I_{t,t'}$ as time interval $[t,t']$.
-% with $t,t'\in\{1,\dots ,T\}$ which includes time slots $t,t+1,\dots ,t'$. 
-Then, assuming that charging demands are sorted in non-increasing order of their unit values, $A^i_j(t,t')$ is the aggregate residual resource in interval $I_{t,t'}$ at station $j$ assuming that the reservation for EVs $1$ to $i$ is accomplished.
-We now explain in detail each phase of the algorithm.
-
-\subsubsection{Phase I-Reservation\label{sec:ph1}} In Line~\ref{algline:sort1}, the EVs are sorted in a non-increasing order of their unit values.  
-%		i.e., ${v_1\slash D_1\geq v_2\slash D_2\geq\dots \geq v_n\slash D_n}$. 
-In Line~\ref{algline:setR}, the \fcs processes demand of EV $i$, picked from top of the ordered list, and sets $R_i$ as the amount to be reserved for EV $i$ which will be allocated in Phase II.
-In Line~\ref{algline:seta}, the residual resource of all intervals in set $\mathcal{I}_{a_i,d_i}$ decreases by $R_i$ and EV $i$ is added to the set of selected EVs.
-
-\begin{algorithm}[t]%\small%1
-	%\footnotesize
-	\revv{
-	\caption{\fcs}
-	\label{alg:optimal-off}
-	\DontPrintSemicolon 
-	\KwIn{$n$ EVs with their profile, local and global peak constraints $p_j, j=1,\dots ,m$ and $p^\mathsf{total}$ }
-
-	\KwOut{Optimal scheduling under fractional model}
-	\BlankLine
-
-	Sort charging requests in non-increasing order of their unit values, i.e., $\frac{v_1}{D_1}\geq \frac{v_2}{D_2}\geq\dots \geq \frac{v_n}{D_n}$\label{algline:sort1}
-
-	%	\slash\slash\textit{\texttt{Use sorted list to process demands}}
-
-	$\mathcal{L}\leftarrow \emptyset$
-
-	\slash\slash\textit{\texttt{Phase I}}
-
-	\For{$i=1,\ldots, n$}{
-		%\slash\slash\textit{\texttt{update demand and value}}
-
-		$R_i \leftarrow \min\{D_i, \min\limits_{t,t'} A^{i-1}_{h(i)}(t,t'), \forall t,t': I_{t,t'}\in\mathcal{I}_{a_i,d_i}\}$\label{algline:setR}
-
-		\If{$R_i>0$}{
-			$A^{i}_{h(i)}(t,t')\leftarrow A^{i-1}_{h(i)}(t,t')-R_i, \forall t,t': [t,t']\in\mathcal{I}_{a_i,d_i}$ \label{algline:seta}\\
-			$\mathcal{L}\leftarrow \mathcal{L}\cup{i}$
-	}}
-	\slash\slash\textit{\texttt{Phase II}}
-
-	Sort EVs in $\mathcal{L}$ in increasing order of their charging flexibility i.e., $\frac{(d_i-a_i+1)k_i}{D_i}, i\in \mathcal{L}$.
-
-	%	Let $i$ be the index of $i^{th}$ EV in list $\mathcal{L}$
-
-	\For{$i=1,\ldots, |\mathcal{L}|$}{
-
-		Pick EV $i$ from the sorted list $\mathcal{L}$.
-
-		$\emph{feasible}\leftarrow \big(\sum_{t=a_i}^{d_i}\min\{k_i,A^{i-1}_{h(i)}(t,t)\}\big) - R_i$
-
-		\If{feasible $<0$}{
-			Re-allocate previously allocated EVs such that $\emph{feasible}\geq 0$
-		}
-		Arbitrarily allocate $R_i$ to EV $i$ in its availability window\label{algline:fcsallocate}	
-	}}
-\end{algorithm}
-
-\begin{lem}
-	Provided that for EV $i$ we have 
-	\bee
-	\label{eq:ri}
-	R_i\leq\min\left\{D_i, \min_{t,t'} A^{i-1}_j(t,t'), \forall t,t': I_{t,t'}\in\mathcal{I}_{a_i,d_i}\right\}
-	\eee
-	 with a dummy $A^0_j(t,t')$ defined as
-$A^0_j(t,t')=(t'-t+1)\times\min \{p^\mathsf{total},p_{j}\},$
-	then there is a feasible allocation to allocate $R_i$ to EV $i$ in its availability window $[a_i,d_i]$. 
-	\label{thm:R_feasible}
-\end{lem}
-
-In Lemma \ref{thm:R_feasible}, $A^0_j(t,t')$ indicates the available resource when no charging request is processed in $I_{t,t'}$. 
-In Eq.~\eqref{eq:ri}, the second term, i.e., $\min_{t,t'} A^{i-1}_{j}(t,t')$, indicates the minimum remaining resource in all super intervals of interval $I_{a_i,d_i}$.
-For $i\geq 1$, $A^i_j(a_i,d_i)$ is defined as follows:
-
-\begin{equation*}
-A^i_j(a_i,d_i)=\begin{cases}
-A^{i-1}_j(a_i,d_i)-R_i & j=h(i),\\
-A^{i-1}_j(a_i,d_i) & j\neq h(i).
-\end{cases} 
-\end{equation*}
-
-The optimal value of $R_i, i=1,\dots ,n$ is set according to the following lemma:
-
-\begin{lem}
-	Given $n$ EVs sorted in a non-increasing order of the unit values, ${v_1\slash D_1\geq v_2\slash D_2\geq\dots \geq v_n\slash D_n}$, and the value of $R_i$, where $R_i$ is set after $R_{i-1}, i=2,\dots ,n$ by Eq.~\eqref{eq:ri}, then,
-	$$R_i = \min\left\{D_i, \min_{t,t'} A^{i-1}_{h(i)}(t,t'), \forall t,t':I_{t,t'}\in\mathcal{I}_{a_i,d_i}\right\},\forall i,$$
-	is the optimal value for $R_i$. 
-	\label{thm:R_star}
-\end{lem}
-
-\subsubsection{Phase II- Allocation\label{sec:ph2}} Lemma~\ref{thm:R_feasible} shows that there is a feasible scheduling to allocate the reserved resources.
-However, despite its feasibility, it is not straightforward to find such \revv{a schedule}.
-For example, assume that for EV $i$, $R_i=10$ and $k_i=4$.
-It is possible that all available resources are concentrated in a single time slot but EV $i$ cannot use more than $4$ kWh of it.
-In this situation, the previously allocated resources in interval $I_{a_i,d_i}$ should be re-allocated such that the concentrated resources are \emph{dispersed} and we have $\sum_{t=a_i}^{d_i}\sigma_t \geq R_i$ where $\sigma_t =\min\{k_i,A^{i-1}_{h(i)}(t,t)\}$ is the maximum resource that can be allocated to EV $i$ at time slot $t$.
-Since the total amount of allocated resource does not change in the interval, such dispersion is possible and can be done by a simple algorithm in which allocates $\min\{k_i,A^{i-1}_{h(i)}(t,t)\}$ starting from time slot $t=a_i$ until $R_i$ units is allocated.
-To further reduce the peak of the system, we will develop \sa\ algorithm (See Section \ref{sec:integral}) which acts more intelligent so that Line \ref{algline:fcsallocate} of the \fcs can be replaced by ``Run \sa$(i,R_i)$''.
-
-\begin{thm}
-	\label{cor:1}
-	\fcs is an optimal solution under fractional revenue model.
-\end{thm}
-
-The following theorem characterizes the complexity of \fcs.
-
-\begin{thm}
-	\label{thm:complexity}
-	The time complexity of \fcs algorithm is $O(n^2T+nT^2)$ where $n$ is the number of EVs and $T$ is number of time slots.
-\end{thm}
-}
-
-%\vspace{-4mm}
-\subsection{Online Scenario}
-\label{sec:fonline}
-In this section, we devise an algorithm for the scenario that EVs arrive in online fashion.
-The scheduling decisions at each time slot are made given the information of available EVs and neither exact values nor stochastic modeling of future arrivals is available.
-Our goal is to obtain a \emph{competitive ratio} for the online algorithm.
-A scheduling algorithm $\mathcal{A}$ is $c$-competitive for $c\geq 1$ if the revenue obtained by the optimal offline algorithm is at most $c$ times the algorithm $\mathcal{A}$'s revenue for any input sequence~\cite{borodin2005online}.
-
-The proposed online algorithm for the fractional model, referred to as \focs, is listed as Algorithm~\ref{alg:focs}.
-The \focs is a simple yet efficient algorithm that always selects EVs with highest unit value to allocate as follows.
-First, the algorithm sorts the available EVs at each time slot~$t$ based on their unit value (Line~\ref{algline:sort}).
-\revv{In this step, the algorithm breaks ties based on EVs' deadline i.e., if two EVs have the same unit value, then the one with earliest deadline comes first in the sorted list.} Next, the \focs selects one EV at a time from the sorted list to allocate with maximum charging rate considering the EV's remaining demand, maximum charging rate, and peak constraints (Lines~\ref{algline:focsfor}-\ref{algline:focssety}).
-The allocation is continued until all resources are allocated or there is no more EV that could be allocated.
-%For unselected EVs, the value of $y_i^t$ will be $0$ in Line \ref{algline:focssety} of the algorithm. 
-The time complexity of the \focs is $O(n^2T)$, determined by cost of its ``\textbf{for}'' loop multiplied by total number of times that the algorithm needs to be run.
-% i.e., $T$.
-
-%\vspace{-4mm}
-\begin{algorithm}%\small%1
-\footnotesize
-\caption{\focs: $\forall t\in \{1,2,\dots ,T\}$}
-\label{alg:focs}
-\DontPrintSemicolon 
-%\KwIn{Available EVs at time slot $t$, number of CSs $m$, local peak constraint $p_j, j=1,\dots ,m$, global peak constraint $p^{\textrm{total}}$}
-
-%\KwOut{A feasible charging scheduling}
-
-%$\backslash\backslash\texttt{Initialize:}$
-
-\BlankLine
-
-$\mathcal{M}^t\leftarrow$ The set of available EVs that not received their entire demand by $t$
-
-Sort EVs in set $\mathcal{M}^t$ indexed by $i=1,\dots ,|\mathcal{M}^t|$: $v_1/D_1\geq v_2/D_2\geq\dots\geq v_{|\mathcal{M}^t|}/D_{|\mathcal{M}^t|},$  \revv{where ties are broken based on users' deadline (giving priority to the users with earliest deadline) }\label{algline:sort}
-
-\For{$i=1,\ldots,|\mathcal{M}^t|\label{algline:focsfor}$}{
-
-$y_i^t\leftarrow \min\{k_i,D_i-\sum_{\tau=a_i}^{t}y_i^{\tau},p_{h(i)}-\sum_{i':h(i')=h(i)}y_{i'}^t,p^{\textrm{total}}-\sum_{i'}y_{i'}^t\}$ \label{algline:focssety}
-
-}
-
-\end{algorithm}
-Despite the simplicity of \focs which makes it easy to implement, its performance is sound and within a constant factor of the offline optimum.
-We now proceed to analyze the performance of the \focs by first giving some preliminaries.
-
-Fix an optimal scheduling and let $\mathcal{S}_{\focs,t}$ and $\mathcal{S}_{\opt,t}$ be the sets of EVs selected by the \focs and optimal solution at time slot $t$, respectively.
-Let $y_{i}^t$ and $z_{i}^t$ be the charging rate of EV $i$ set by \focs and \opt, respectively.
-We define $\Delta_{i}^t$ as follows:
-\begin{equation}
-\label{eq:delta}
-\Delta_{i}^t =
-     \begin{cases}
-       \min\{z_{i}^t-y_{i}^t,r_{i,t}\} &\quad i\in\mathcal{S}_{\opt,t},z_{i}^t>y_{i}^t, \\
-       0& \quad\text{otherwise},  \\
-     \end{cases}
-\end{equation}
-where $r_{i,t}$ is the remaining demand of EV $i$ by the end of time slot $t$.
-$\Delta_{i}^t>0$ indicates that the optimal algorithm allocated $\Delta_{i}^t$ units more resources to EV $i$ than the \focs by time slot $t$ that could be \emph{feasibly} allocated by \focs to the EV $i$.
-If for any EV $i\in\mathcal{S}_{\opt,t}$ and time slot $t\in\mathcal{T}$ we have $y_{i}^t=z_{i}^t$, i.e., $\Delta_{i}^t=0$, then the \focs is obviously optimal because it gains whatever the optimal solution gains.
-\rev{We define \textit{loss} of the \focs imposed by EV $i$ as follows:
-\begin{equation}
-\label{lBj0}
-l_{i,t}=\Delta_{i}^t\frac{v_i}{D_i},
-\end{equation}
-
-Note that the loss always takes a non-negative value as $\Delta_i^t\geq 0$.} When \focs sets charging rate of an EV less than its rate in the optimal solution, it gains $\Delta_{i}^t v_i/D_i$ less than the optimal solution from that EV.
-An upper bound for the distance between the optimal objective value (denote by \opt) and the revenue of the \focs (denote by \alg) is summation of the losses over all time slots and all EVs, i.e.,
-\begin{equation}
-\label{eq:optdist}
-\opt-\alg\leq \sum_{t=1}^T\sum_{i\in\mathcal{S}_{\opt,t}} l_{i,t}.
-\end{equation}
-
-%Notice that it is possible that an algorithm does not choose any selected EV by a particular optimal solution but still provide an optimal or near-optimal solution as there can be multiple optimal solutions.
-In particular, $\mathcal{S}_{\focs,t}\cap \mathcal{S}_{\opt,t}=\emptyset, \forall t$ cannot lead to any conclusion on the competitive ratio of the \focs.
-In addition to the amount of loss, the gain of the algorithm from charging alternative EVs should also be taken into account in comparison between \opt and \alg.
-
-Let $i\in\mathcal{S}_{\opt,t}$, $i\notin\mathcal{S}_{\alg,t}$ and $g_{i,t}$ be the gain that the \focs obtains from charging another EV instead of $i$ at time slot $t$.
-We are going to show that in the \focs, for each EV $i$ with $l_{i,t}>0$ there must be another EV (denote by $i'$) where $y_{i'}^t\geq \Delta_i^t$ and $\frac{v_{i'}}{D_{i'}}\geq \frac{v_i}{D_i}$ which means in resource allocation phase for EV $i$, the \focs allocated the difference $\Delta_i^t$ to another EV with the same or higher unit value.
-This can be proved by considering the fact that (i) the selected EVs have higher unit values than the unselected EVs, and (ii) the charging rate of the selected EVs are set to the maximum feasible value.
-Moreover, the \focs is \emph{``work-conserving''} i.e., it does not let any resource remain unused if there are some EVs that can use it.
-
-Let $g_{i,t}$ denote the gain that \focs obtains from allocating the same amount of resource that optimal algorithm allocated to EV $i$ (with size $z_i^t$) to another EV(s).
-If $\Delta_{i}^t=0$, the loss is zero. If $\Delta_{i}^t>0$, then by the charging strategy that the \focs uses we can conclude that (i) $i$ is not finished by the \focs, and (ii)
-\rev{no more resources from station $p_{h(i)}$ can be feasibly allocated,} otherwise, the \focs could allocate more resources to EV $i$.
-Therefore, the $\Delta_{i}^t$ units of the resource \rev{are} allocated to one or multiple other EVs (denote them by set $\mathcal{J}_i^t$) by the \focs.
-Moreover, it must hold that all the EVs in set $\mathcal{J}_i^t$ have a unit value equal to or higher than $v_i/D_i$ which yields $g_{i,t}\geq l_{i,t}$, otherwise, the \focs should not prefer the EVs in $\mathcal{J}_i^t$ to $i$.
-\rev{Since the result holds for any arbitrarily EV $i$, we can get the following:}
-
-\begin{equation}
-\label{eq:lg}
-\sum_{i=1}^n\sum_{t=1}^Tl_{i,t}\leq\sum_{i=1}^n\sum_{t=1}^Tg_{i,t}.
-\end{equation}
-
-Moreover, the total gain of \focs, i.e., \alg, is equal to sum of its gains from each single EV:
-\begin{equation}
-\label{eq:ALG}
-\rev{\alg= \sum_{i=1}^n\sum_{t=1}^Tg_{i,t}.}
-\end{equation}
-
-With the above discussion and using Eqs. (\ref{eq:optdist}), (\ref{eq:lg}) and (\ref{eq:ALG}) we are able to derive a competitive ratio of $2$ for the \focs.
-
-\begin{thm}
-	\label{thm:focscompetitive}
-	The \focs is $2$-competitive.
-\end{thm}
-
-\emph{Remarks:} When there is only one CS and EVs have no limit on their charging rate, the \focs is identical to the \textsc{FirstFit} algorithm ~\cite{firstfit} which is known to be $2$-competitive for classic job scheduling problem.
-However, the charging rate limitation is crucial for EV charging problem.
-Moreover, \cite{firstfit} uses \revv{a} ``charging argument'' to prove the competitive ratio of the proposed algorithm which cannot be directly applied to our problem.
-Thus, the \focs extends the \textsc{FirstFit} and makes it practical for the EV charging scenario.
-Moreover, the proof technique used for the competitive analysis of the \focs is fundamentally different from the one used in \cite{firstfit}.
-%%%Finally, in~\cite{Robu} an online $2$-competitive algorithm for EVs with partial charging is proposed.
-The competitive ratio obtained assuming that charging of EVs is instantly reversible at departure times.
-This assumption is not practical in reality since similar to charging phase, there is a discharging rate constraint for EVs.
-
-%\begin{thm}
-%\label{thm:focscomplexity}
-%
-%The time complexity of \focs is $O(nT\log n)$.
-%\end{thm}
-		\section{Integral Revenue Model}
-		\label{sec:integral}
-%
-%		\subsection{Overview of Integral Revenue Model}
-%		\label{sec:intoverview}
-		The MILP form of the \MCSP in integral model is a generalized form of the $0/1$-knapsack problem which is a well-known NP-hard problem.
-\rev{To give an intuition, consider the scheduling problem in a single time slot (i.e, $T=1$).
-Then, allocating power resources to the EVs is equivalent to allocating the capacity of knapsack to the items.
-}
-		In Section~\ref{subsec:icsalgorithm}, we propose a fast polynomial time offline approximation algorithm for the integral problem.
-In Section~\ref{sec:onlineint}, we extend the result and propose an online algorithm for the integral model.
-%		, where the EVs arrive in slot-by-slot fashion, and the scheduler has no information of the future arrivals.
-
-%The problem is even more challenging when the uncertainty in EVs' arrival is taken into account.
-At each time slot, the scheduler has no information of unit values of the future charging profiles.
-Therefore, the scheduler cannot make sure about the efficiency of its current charging decision.
-%It can be shown that when there is no assumption on the charging profiles of EVs (including the value of slackness parameter) and the charging decision , no online algorithm can provide a performance guarantee meaning that in the worst case, the ratio of the optimal objective value to the one obtained by the online algorithm can be arbitrary small.
-In fact, when the online algorithm selects
-
-		\subsection{Offline Scenario}   
-		\label{subsec:icsalgorithm}
-		We design our offline scheduling algorithm under integral model referred to as \ics, to solve the \MCSP approximately. 
-%		Our algorithm design is inspired by the basic algorithm proposed in \cite{Jain}.
-The algorithm in \cite{Jain} works for a single CS where arrival time of all EVs are the same and there is no global peak constraint.
-Since the performance analysis of the proposed algorithm relies on a dual fitting method and utilizes weak duality property, \revv{we first need to construct the dual problem of \MCSP.
-Toward this, we introduce variables $\alpha, \beta, \gamma$ and $\pi$.
-Generally, in primal-dual approximation algorithm design, each constraint (resp.
-variable) in primal (resp.
-dual) problem is associated with a variable (resp.
-constraint) in dual (resp.
-primal) problem.
-In our case, constraints (\ref{ConstPartial}) (\ref{ConstTotal}), (\ref{ConstLocal}) and (\ref{ConstSpeed}) in the \MCSP are respectively associated with dual variables $\alpha, \beta, \gamma$ and $\pi$ (for more details see \cite{approx}).
-The dual problem is formulated as follows:}
-		\bse
-		\bee
-		\min &&\sum_{i=1}^n D_i\alpha _i + \sum_{j=1}^m \sum_{t=1}^T p_j\beta (t)+\sum_{t=1}^T p^\mathsf{total}\gamma (t)\nonumber\\ 
-		\textrm{s.t.} && \alpha _i+\beta (t) +\gamma _i + \pi (t)- \frac{k_i}{D_i}\sum_{t'=a_i}^{d_i} \pi _i(t^\prime) \geq \frac{v_{i}}{D_i},\label{ConstDcover} \nonumber\\
-		&& \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\forall i, t\in [a_i, d_i],\\
-		\textrm{vars.}&&\alpha _i, \beta _i, \gamma,  \pi _i(t)\geq 0,\quad\quad\forall i,t. \nonumber
-		\eee
-		\ese
-
-		%%%In this section, we explain \ics in details and then in Section~\ref{subsec:analysis}, we analyze approximation factor of the algorithm. The \ics algorithm is listed as Algorithm~1.
-
-		\subsubsection{Explanation of the Main Algorithm} 
-		\label{sec:icsexplanation}
-		Our algorithm design is inspired by the basic algorithm proposed in \cite{Jain}.
-\revv{The algorithm in~\cite{Jain}, however, works for a single CS where arrival time of all EVs are the same and there is no global peak constraint.}
-		The \ics algorithm (listed as Algorithm \ref{alg:ics}) works in two phases.
-In the first phase it sorts the charging requests based on their unit values in a non-increasing order.
-Then, it selects most valuable demand.
-If the remaining resource is enough to cover the \emph{entire} demand of the EV, it is admitted to receive the demand (Lines~$6$-$7$).
-%		When \ics processes EV $i$, the algorithm checks for the feasibility of allocating $D_i$ units of the resource within its availability window $[a_i,d_i]$ without violating the constraints related to the maximum charging rate $k_i$, local and global peaks (Lines~$6$-$8$).
-
-		\emph{Scheduling of the Selected EV:} \revv{If the feasibility check passed (Line 6 in Algorithm 3)}, \ics calls sub-procedure \sa\ to allocate required resources in interval $[a_i,d_i]$.
-Then, $\alpha _i$ is set to $v_i\slash D_i$ in order to cover dual constraint in Eq.~\eqref{ConstDcover} (Lines~$7$-$8$).
-
-		In \sa, 
-		%%%When EV $i$ is selected to get charged, \sa\ is called for the charging scheduling. 
-		let us define $W(t,h(i))=\sum_{i': h(i')=h(i)} y_{i'}^t$ as total workload at time slot $t$ in CS $h(i)$ and $\bar{W}(t,h(i))$ as total available load to allocate at time slot $t$ for CS $h(i)$.
-We always have ${\bar{W}(t,h(i))+W(t,h(i))=p_{h(i)},  \forall t, i}$.
-For scheduling, \sa\ applies two main policies: 1) \emph{valley-filling} and, 2) \emph{right-to-left allocation}.
-\revv{With valley-filling, the slots with more available resources are preferred which helps to reduce the peak of the system.} %%%It also can be seen as a smoothing method which tries to reduce the variance of the allocated resources at different slots.
-%				The simulation results in Section \ref{sec:simul} will confirm this claim. 
-				Right-to-left allocation is used when two or more time slots are equal in terms of their remaining resources. 
-%				When this policy applies on scheduling of EV~$i$, any EV~$i'$ with $i'>i$ and $d_{i'}<d_i$ has more chance to get charged since the algorithm tends to charge EV $i$ in interval $[d_{i'}+1,d_i]$ (i.e., right hand part of the EV's availability window) and keeps resources in $[a_{i'},d_{i'}]$ for EV $i'$.
-A ranking based approach is used to apply the aforementioned policies. 
-		To charge  EV $i$, \sa\ ranks time slots in interval $[a_i,d_i]$.
-Then, charging is done by allocating resources from the higher ranked time slot to lowest one.
-The rank of a time slot $t$ is calculated based on remaining resources in the time slot (valley-filling) and value of $t$ (right-to-left allocation).
-
-		\begin{algorithm}%\small%1
-			\footnotesize
-			\caption{\ics}
-			\label{alg:ics}
-			\DontPrintSemicolon 
-%			\KwIn{$n$ EVs with $a_i, d_i, v_i, D_i,$ and $k_i$ associated with each EV $i$, $m$ CSs, local and global peak constraints $p_j, j=1,\dots ,m$, and $p^\mathsf{total}$}
-
-%			\KwOut{A feasible scheduling of EVs}
-			\BlankLine
-			%\begin{algorithmic}
-
-			%\slash\slash\textit{\texttt{Initialization}}
-			\textbf{initialize}: $y\leftarrow 0, \alpha\leftarrow 0, \beta\leftarrow 0, \gamma\leftarrow 0, \pi\leftarrow 0$
-
-			Sort charging requests in non-decreasing order of their unit values: $v_1/D_1 \geq v_2/D_2\geq\dots \geq v_n/D_n$
-%			$\frac{v_1}{D_1} \geq \frac{v_2}{D_2}\geq\dots \geq \frac{v_n}{D_n}$
-%			\slash\slash\textit{\texttt{Use sorted list to process demands}}
-
-			\For{(i=1\dots n)}{
-
-				\For{$t=a_i\dots d_i$}{
-					$\sigma_t\leftarrow  \min\Big\{p_{h(i)}-\sum_{i':h(i')=h(i)}y_{i'}(t),$ \newline $\qquad p^\mathsf{total}-\sum_{i'=1}^n y_{i'}^t,k_i\Big\}$
-
-				}
-
-%				\slash\slash\textit{\texttt{if enough resources remain for EV $i$}}
-
-				\If{$D_i\leq\sum_{t=a_i}^{d_i}\sigma_t$}
-				{
-					\sa($i,D_i$)\\
-					$\alpha _i\leftarrow v_i/ D_i$
-				}
-				\Else {
-					\If{$(\beta (d_i)=0)$}{
-						\bc($i$)}
-				}
-			}
-
-			\For{(i=1\dots n)}{ 
-				\If {EV $i$ is not selected}{
-					\rc($i$);
-				}
-			}
-			%\end{algorithmic}
-		\end{algorithm}
-
-\emph{Dual Feasibility of the Non-selected EVs:} \bt{If remaining power resource is not enough} to fully charge EV $i$, i.e.,  $D_i>\sum_{t=a_i}^{d_i}\sigma_t$, the EV cannot be selected.
-However, we still need to satisfy constraint~\eqref{ConstDcover} in dual problem which is done by calling \bc($i$).
-To cover the constraint~\eqref{ConstDcover} for EV $i$, sum of dual variables for all $t\in [a_i ,d_i]$ should be greater than or equal to ${v_i \slash D_i}$.
-\bc($i$) sets $\beta (t)$ to ${v_i \slash D_i}$ for all time slots $t$ in interval $[t_\mathsf{cov}, R(d_i)]$ (Lines $3$-$4$ of Algorithm~\ref{alg:betacover}).
-Observe that  ${\beta (t^\prime)\geq v_i \slash D_i,\forall t^\prime< t_\mathsf{cov}}$ (with $ t_\mathsf{cov}>1$) considering that the demands are sorted in a non-increasing order of the unit-values and $\beta (t')$ is already set to ${v_{i'} \slash D_{i'}}$ when processing the earlier charging demand of EV $i'$ which is not selected.
-Hence, ${v_{i'}\slash  D_{i'}\geq v_i \slash D_i}$, thereby ${\beta (t)\geq v_i \slash D_i,}$ and the dual constraint in~\eqref{ConstDcover} is satisfied.
-		Lines $1$-$4$ of \bc\ is enough to cover the dual constraint.
-However, the algorithm continues in Lines $5$-$8$ by setting a variable $\Phi_{i'}(t)$ for time slots $t=1,\dots ,R(d_i)$ to a value dependent to amount of the resource that a selected EV $i'$ received at slot $t$.
-$\Phi_{i'}(t)$ will be used in approximation analysis of the main algorithm and has no effect on the scheduling of EVs.
-		%We borrowed algorithm \bc($i$) from \cite{Jain} and adjusted it for multiple station mode.		
-%		\vspace{-3mm}
-		\begin{algorithm}%\small%1
-			\footnotesize
-			\caption{\sa($i,D_i$)}
-			\label{SmartAllocate}
-			\DontPrintSemicolon 
-			\KwIn{EV $i$ to receive $D_i$ from CS $h(i)$}
-
-			Rank time slots in interval $[a_i,d_i]$ such that for any $t_1$ and $t_2$:
-			$\mathsf{rank}(t_1)> \mathsf{rank}(t_2)$ iff $\bar{W}(t_1,h(i))>\bar{W}(t_2,h(i))$ OR $\bar{W}(t_1,h(i))==\bar{W}(t_2,h(i)) \wedge t_1>t_2$
-
-			\While {$\sum_{t'=a_i}^{d_i}y_i^{t'}\neq D_i$}{
-
-				Select time slot $t$ with highest rank which is not selected before
-
-				Allocate $\min \left\{k_i,\bar{W}(t,h(i)),D_i-\sum_{\tau=a_i}^{t}y_i^{\tau},p^{\textrm{total}}-\sum_{i'}y_{i'}^t\right\}$ to EV $i$ at $t$
-
-			}
-		\end{algorithm}	
-%		\vspace{-7mm}	
-		\begin{algorithm}%\small%1
-			\footnotesize
-			\caption{\bc($i$)}
-			\label{alg:betacover}
-			\DontPrintSemicolon 
-			%\KwIn{EV $i$ which is not selected to charge}
-
-			\BlankLine
-
-			$t_\mathsf{cov}\leftarrow \min \{t: \beta (t)=0\}$
-
-			$R(d_i)=\max \{t\geq d_i : \forall t^\prime\in (d_i,t], \bar{W}(t^\prime)<q_{h(i)} \}$
-
-			\For{$(t=t_\mathsf{cov}\dots R(d_i))$}{
-				$\beta (t)\leftarrow v_i/D_i$
-			}
-
-			\For{$(t=1\dots R(d_i))$}{
-				\For{$(i'=1\dots n))$}{	
-					\If{$y_{i'}^t>0 \wedge \Phi_{i'}(t)=0$}{
-						$\Phi_{i'}(t)\leftarrow\big[ \frac{p_{h(i)}}{p_{h(i)}- k_i}\frac{s}{s-1}\big] .\frac{v_i}	{D_i}y_{i'}^t$
-					}
-				}
-			}
-		\end{algorithm}
-%		\vspace{-7mm}
-		\begin{algorithm}%\small%1
-			\footnotesize		
-			\caption{\rc($i$)}
-			\label{Replace}
-			\DontPrintSemicolon 
-%			\KwIn{EV $i$}
-%			\KwOut{Updated schedule}
-
-			$\mathcal{L} \leftarrow \emptyset$\\			
-			$v_\mathsf{inc}\leftarrow v_i$\\			
-			$\sigma_t\leftarrow 0, t=a_i,\dots ,d_i$
-
-			%Define $\delta_i(t)=\min \{k_i,\bar{W}(t,h(i))\}$
-
-			%$\Delta\leftarrow \sum_{t=a_i}^{d_i}\min\{\bar{W}(t,h(i)), k_i\}$
-
-			\For{($i' =i-1\dots 1$)}{ 
-				\If {EV $i'$ is selected $\wedge (h(i')=h(i)) \wedge (v_\mathsf{inc}-v_{i'})>0$}{
-					Add EV $i'$ to list $\mathcal{L}$
-
-					$v_\mathsf{inc}\leftarrow v_\mathsf{inc}-v_{i'}$
-
-					\For{($t=a_i\dots d_i$)}{
-						$\sigma _t\leftarrow\sigma_t + \min\{k_i,y_{i'}^t\}$
-					}
-				}
-			}
-
-			\If {$\sum_{t=a_i}^{d_i}\sigma_t\geq D_i$}{
-				Remove EVs in list $\mathcal{L}$ from charging schedule
-
-				\sa($i,D_i$)
-			}
-		\normalsize
-		\end{algorithm}
-
-		\emph{Improving the Gain:} In the second phase, the \ics tries to increase total value of selected EVs by calling \rc($i$) on every unselected EV $i$ (Lines~$12$-$14$).
-\rev{The \rc(i) (listed as Algorithm $6$) checks that whether the total revenue can be increased by replacing some selected EVs with EV $i$ or not (Lines $4$-$9$).
-If such EVs are found, the algorithm stops their charging and allocates EV $i$ using \sa\ (Lines $10-12$).}
-		%We refer to ~\cite{alinia2017online}, for the details and intuition behind this algorithm. 
-%		Before giving the details of \rc($i$), we first explain the intuition behind this algorithm. 
-%		 Note that if in the scheduling problem we set $T=1, m=1, k_i=p^\mathsf{total}, a_i=d_i=1\ \forall i$, then the problem is equal to the well-known $0$-$1$ knapsack problem~\cite{approx}.
-In the knapsack problem, a widely used greedy approach sorts items based on their unit values and selects items accordingly.
-It turns out that in this approach the approximation factor can be arbitrarily bad.
-For example, consider a knapsack problem with two items with $v_1=2, v_2=p^\mathsf{total}, D_1=1$, and  $D_2=p^\mathsf{total}$.
-Given these values we have $v_1\slash D_1>v_2\slash D_2$.
-To maximize total value of selected items, the optimal solution chooses item $2$ while greedy algorithm selects item $1$ which results in a worst-case approximation factor of ${c \slash \opt}$ in general where $c$ is a constant (in this example $c=2$).
-To resolve it, one approach is to \emph{re-consider} unselected items after running greedy algorithm and replace some selected items in the knapsack with unselected ones and then check whether the result is improved or not.
-In a simple case, only the largest unselected item can be examined which makes a significant theoretical improvement by providing a worst case approximation factor of $\opt\slash 2$.
-%		 
-%\ics algorithm leverages the same idea but using a more intelligent replacing method called \rc($i$).
-\rc($i$) is called on every unselected EV $i$.
-It tries to find some selected EVs that if they are replaced by EV $i$, total revenue from the selected EVs increases.
-%%%When \ics calls \rc($i$) on all unselected EVs, an improvement in total revenue of final selected EVs is expected.
-%This is confirmed by the simulation results in Section~\ref{sec:simul}.
-
-		\subsubsection{Analysis}
-		\label{subsec:analysis}
-		In primal-dual algorithm, the goal is to design an algorithm in a way that it produces a good solution for primal problem (with primal value $\Gamma$) and a feasible solution for the dual problem (with dual value $\Lambda$).
-Then, assuming that the primal problem is a maximization problem, to prove that the algorithm is $c-$approximation (for $c\geq 1$), the important part is to show that $\Lambda\leq c\Gamma$.
-Then, based on weak duality theorem we have $\Lambda\geq \opt$, and it is concluded that $\Gamma \geq \frac{1}{c}\times\opt$ where $\opt$ is the optimal value.
-		Based on the above understanding, the following theorem scrutinizes the approximation ratio of the \ics assuming that arrival times are the same for all EVs. 
-%		First note that the designed scheduling algorithm outputs a feasible scheduling since it respects the constraints in the primal problem.
-Also, the algorithm produces a feasible solution for the dual problem by covering the dual problem constraint in (\ref{ConstDcover}) through setting $\alpha _i$ to $\frac{v_i}{D_i}$ when EV $i$ is accepted and, $\beta (t)$ to a value greater than or equal to $\frac{v_i}{D_i}$ for $t\in [a_i, d_i]$ (according to the discussion in Section \ref{sec:icsexplanation}) if EV $i$ is not selected.
-To obtain an approximation factor for the algorithm, it is enough to bound the total covering cost of the dual constraints.
-
-		\begin{thm}
-			\label{thm:approx}
-			\ics algorithm is a $\Big( 1+ \sum_{j=1}^m {\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}\Big)$-approximation when EVs have same arrival time.
-		\end{thm}
-%		
-%		\begin{proof}
-%			In Appendix~\ref{app:1}.
-%		\end{proof}
-
-		Note that in the case that the system is flexible enough, i.e., $s\gg 1$, and the maximum charging rates of stations are much bigger than those of EVs, i.e., $p_j \gg q_j, \forall j$, the approximation ratio approaches $m+1$.
-And in the case that there is one single station, the approximation ratio is $2$.
-%		 Finally, we provide the time complexity of the \ics.
-
-%\begin{thm}
-%\label{thm:ics_complexity}
-%The time complexity of the \ics algorithm is $O(nT\log T+n^2T)$.
-%\end{thm}	
-%
-%\begin{proof}
-%In Appendix \ref{app:ics_complexity}.
-%\end{proof}
-
-\subsection{Online Scenario}
-\label{sec:onlineint}
-Due to the binary selection variable, the online solution design under integral model is more challenging than the one for fractional model.
-We propose the \iocs that is built upon the offline \ics.
-In particular, the \iocs calls the \ics at each time slot for the set of available EVs, however, any algorithm that is designed for offline integral model can be used alternatively.
-Hereinafter, $\mathcal{A}$ refers to the \ics or a similar algorithm.
-
-\begin{algorithm}%\small%1
-\footnotesize
-\caption{\iocs: $\forall t\in \{1,2,\dots ,T\}$}
-\label{alg:iocs}
-\DontPrintSemicolon 
-%\KwIn{$n$ EVs to arrive on the fly, number of CSs $m$, global peak constraint $p^{\textrm{total}}$, local peak constraints $p_j, j=1,\dots ,m$}
-
-%\KwOut{A feasible charging scheduling}
-
-\BlankLine
-
-Let $\mathcal{A}$ be an algorithm that solves the problem with $a_1=\dots =a_n$
-
-$\mathcal{R}^t\leftarrow$ set of EVs arrived at time slot $t$
-
-$\mathcal{M}^t\leftarrow \mathcal{R}^t\cup \{i: t\in\mathcal{T}_i\ \texttt{AND}\ \sum_{t^\prime}y_{i}^{t'}<D_i\}$
-
-%$\backslash\backslash\texttt{Schedule 1}$
-
-Based on the residual in interval $[t,T]$, use algorithm $\mathcal{A}$ to allocate EVs in set $\mathcal{R}^t$ assuming no further arrivals
-
-$\mathcal{S}_{\iocs,t}\leftarrow\{i:i\in\mathcal{M}^t\ \texttt{AND}\ i$ is admitted at $t\}$
-
-$\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}\leftarrow \sum_{i\in\mathcal{S}_{\iocs,t}}v_i$
-
-Assume all reserved resources are freed at time slots $t, t+1, \dots, T$
-
-%$\mathcal{R}^t\leftarrow\mathcal{M}^t$
-
-%$\backslash\backslash\textsl{set of active EVs at time slot t}$
-
-$r_{i,t}\leftarrow$ remaining demand of $i$ at $t, \forall i$
-
-%$\backslash\backslash\texttt{Use modified demands values}$
-
-$D_i^\prime\leftarrow r_{i,t},\ \ v_i^\prime\leftarrow \frac{r_{i,t}}{D_i}v_i, \forall i\in\mathcal{M}^t$
-
-%$\backslash\backslash\texttt{Schedule 2}$
-
-Run $\mathcal{A}$ on $\mathcal{M}^t$ using $D_i^\prime$ and $v_i^\prime, \forall i$ and reconstruct $\mathcal{S}_{\iocs,t}$
-
-$\Gamma_{\mathcal{A},\mathcal{M}^t}\leftarrow \sum_{i\in\mathcal{S}_{\iocs,t}}v_i$ $\backslash\backslash\texttt{Use original values}$
-
-%$a\leftarrow\frac{V^\prime_{\textrm{total}}}{V_{\textrm{total}}}$
-
-\If{$\Gamma_{\mathcal{A},\mathcal{M}^t}>\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$}{
-
-Use the second schedule
-
-}
-
-\Else{
-
-Use the first schedule
-
-}
-
-\end{algorithm}
-
-The \iocs is summarized as Algorithm~\ref{alg:iocs}.
-At slot $t$, the \iocs compares two scheduling results returned by $\mathcal{A}$ and chooses among them.
-In the first scheduling, the \iocs keeps all reserved resources in interval $[t,T]$ intact.
-Then, for utilizing the remaining resources, the algorithm runs $\mathcal{A}$ over arrived EVs at time slot $t$.
-In this case, the total revenue obtained by the \emph{active} EVs (i.e., EVs that are available but not received their entire demand yet) is denoted by $\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$ (Line $6$ of the algorithm).
-In the second scheduling, the \iocs considers the case that it can sacrifice the previously admitted EVs by canceling their reservations and allocating the freed resources to more valuable demands.
-For this purpose, the algorithm modifies the demand and valuation of the previously admitted EVs such that each demand is replaced by the EV's remaining demand, and the valuation of the EV is proportionally calculated based on the remaining demand (Line $9$ of the algorithm) so that the unit values of EVs do not change.
-Then, the \iocs runs $\mathcal{A}$ over set of active EVs $\mathcal{M}^t$ where the corresponding gain is denoted by $\Gamma_{\mathcal{A},\mathcal{M}^t}$.
-If $\Gamma_{\mathcal{A},\mathcal{M}^t}>\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$, the \iocs forgets the previously admitted EVs and follows the second scheduling.
-
-\begin{comment}
-%We now introduce some notations and then analyze the performance of \iocs. 
-Let $\mathcal{S}_{\iocs,t}$ and $\mathcal{S}_{\opt,t}$ be set of active EVs at time slot $t$ that are selected for charging by \iocs and \opt (fix a particular optimal solution), respectively.
-Note that the set of active EVs for \iocs and \opt might be different.
-%Moreover, define  $\mathcal{U}_{\iocs,t}=\mathcal{S}_{\iocs,1}\cup\dots\cup \mathcal{S}_{\iocs,t}$ and $\mathcal{U}_{\opt,t}=\mathcal{S}_{\opt,1}\cup\dots\cup \mathcal{S}_{\opt,t}$. 
-Having $i\in\mathcal{S}_{\iocs,t}$ means that based on the updated schedule at time slot $t$, enough resources reserved for EV $i$ so that the EV will receive its demand $D_i$ before the deadline $d_i$.
-However, the schedule may change at each slot and $i\in\mathcal{S}_{\iocs,t}$ cannot be a guarantee for EV $i$ to fully receive its demand.
-In fact, users and the scheduler itself have to wait until the deadline of the EV to find out that the demand is fulfilled or not.
-This is because the scheduler may cancel some reservations in the next time slots and allocate the freed resources to other EVs.
-\end{comment}
-% (when Algorithm \ref{alg:iocs} uses the second schedule in Line $15$). 
-%Define $A_t$ as the minimum gain of \iocs when the algorithm visited time slots $1$ to $t$.
-More formally, $A_t=\sum_{i\in\mathcal{U}_{\iocs,t}}v_i$.
-$A_t$ is the minimum gain that \iocs will obtain by the end of time slot $t$, having the information of released demands up to time slot $t$.
-Notice that the algorithm may continuously improve its set of selected jobs to increase its gain such that $A_t\geq A_{t-1}, t\in\{2,\dots, T\}$.
-$A_t$ is formally defined as follows:
-
-The following theorem characterizes the competitive ratio of the \iocs in a special case. 
-\begin{thm}
-\label{thm:iocscompetitive}
-Let $\mathcal{A}$ be \ics in \iocs algorithm and $m=1$.
-Assuming that EVs are released in $b$ distinct groups where arrival time of EVs in each group are the same, the \iocs is $b\Big(1+\frac{p}{p-q}\frac{s}{s-1}\Big)$-competitive with optimal offline solution, where $p$ is the station peak and $q=\max_i k_i, i=1,\dots ,n$.
-\end{thm}
-
-%\begin{thm}
-%\label{thm:iocscomplexity}
-%Let $\mathcal{A}$ be \ics in Line $1$ of \iocs. Then, the time complexity of the \iocs  is $O(n^2T)$. 
-%\end{thm}
-
-%\vspace{-6mm}
 \section{Simulation Results}
@@
 					\begin{center}
-						\includegraphics[width=\textwidth]{V-N-M2.pdf}
+						\includegraphics[width=\textwidth]{V-N-M2.png}
 						\caption{\revv{$m=2$}}
@@
 					\begin{center}
-						\includegraphics[width=\textwidth]{V-N-M4.pdf}
+						\includegraphics[width=\textwidth]{V-N-M4.png}
 						\caption{\revv{$m=4$}}
@@
 					\begin{center}
-						\includegraphics[width=\textwidth]{V-N-M8.pdf}
+						\includegraphics[width=\textwidth]{V-N-M8.png}
 						\caption{\revv{$m=8$}}
@@
 				\end{subfigure}% 
-				\caption{\revv{Comparison results for $2$, $4$, and $8$ CSs for fractional and integral revenue models.}} 
+				\caption{Comparison results for $2$, $4$, and $8$ CSs for fractional and integral revenue models.
+In the algorithms' name, letters ``o'', ``f'' and ``i'' indicate online, fractional and integral, respectively.
+Note that a ``non-optimal'' fractional algorithm can potentially achieve better result than an ``optimal'' integral algorithm due to higher flexibility in power allocation.}
 				\label{fig:V-N-M}
@@
 % with the mean arrival and parking duration indicated in Table \ref{tb:a-d}. 
-The peak intervals include $08$:$00$-$10$:$00$, $12$:$00$-$14$:$00$, and $18$:$00$-$20$:$00$ which is in accordance to NHTS survey~\cite{Santos, Tang}.
-\revv{The probability of arriving an EV in the peak hours is two times higher than the off-peak periods.
+The peak intervals include $08$:$00$-$10$:$00$, $12$:$00$-$14$:$00$, and $18$:$00$-$20$:$00$ according to NHTS survey~\cite{Santos, Tang}.
+\revv{The probability of an EV's arrival during the peak hours is two times higher than the off-peak periods.
 			Demands are uniform random values from 
@@
 			In the simulation, the results are plotted with $95\%$ confidence level and each point represents average result of $50$ random scenarios.
-Table \ref{tb:comparisons} explains the comparison algorithms \revv{including current implemented algorithm in Caltech ACN referred to as \iolp \cite{lee2016adaptive} and its adapted version for the fractional revenue model \folp.
-The \iolp and \folp algorithms runs as follows: at each time slot assume that there will be no further arrivals and solve the optimization problem (e.g., by commercial solvers) for the current set of EVs and their remaining demands.
-In Table \ref{tb:comparisons}, the letters ``\textsc{i}'', ``\textsc{f}'' and ``\textsc{o}'' in front of the algorithms' name refer to integral, fractional and online types, respectively.}
+
+Table \ref{tb:comparisons} explains the comparison algorithms including current implemented algorithm in Caltech ACN referred to as \folp \cite{lee2018adaptive} and its adapted version for the integral revenue model \iolp.
+The \iolp and \folp algorithms run as follows: at each time slot assume that there will be no further arrivals and solve the optimization problem (e.g., by commercial solvers) for the current set of EVs and their remaining demands.
+In Table \ref{tb:comparisons}, the letters ``\textsc{i}'', ``\textsc{f}'' and ``\textsc{o}'' in front of the algorithms' name refer to integral, fractional and online types, respectively.
 
@@
 \focs & Proposed online algorithm for \MCSP under fractional revenue model\\ \hline
-\iolp & Algorithm in \cite{lee2016adaptive} (works under integral revenue model)\\ \hline
-\folp & Adaptation of algorithm in \cite{lee2016adaptive} for fractional revenue model\\ \hline
+\iolp & Algorithm in \cite{lee2018adaptive} (works under integral revenue model)\\ \hline
+\folp & Adaptation of algorithm in \cite{lee2018adaptive} for fractional revenue model\\ \hline
 GreedyRTL & The algorithm in \cite{Jain} for single station scenario without global peak 			constraint (works under integral revenue model)\\\hline				
@@
 					\begin{center}
-						\includegraphics[width=\textwidth]{v-c.pdf}
+						\includegraphics[width=\textwidth]{v-c.png}
 						\caption{\revv{Total revenue}}
@@
 					\begin{center}
-						\includegraphics[width=\textwidth]{p-c.pdf}
+						\includegraphics[width=\textwidth]{p-c.png}
 						\caption{\revv{Actual global peak} 
@@
 					\begin{center}
-						\includegraphics[width=\textwidth]{acc-c.pdf}
+						\includegraphics[width=\textwidth]{acc-c.png}
 						\caption{\revv{\% of full charged EVs}}
@@
 			\end{figure*}
-\textit{\revv{Evaluation Based on Total Revenue}:}
+\textit{Evaluation Based on Total Revenue:}
 \revv{Fig.
-\ref{fig:V-N-M} depicts the comparison results based on total revenue under fractional and integral models} while the total number of EVs increases from \revv{$100$ to $250$} for $2$, $4$, and $8$ CSs.
+\ref{fig:V-N-M} depicts the comparison results based on total revenue under fractional and integral models} while the total number of EVs increases from $100$ to $250$ for $2$, $4$, and $8$ CSs.
 \revv{The local and global peak constraints are set to $50$ kWh and $200$ kWh, respectively.}
 
-The proposed algorithms compared to the optimal offline solution of integral model ($\textsc{iOPT}$) and $\iolp$.
-\bt{Note that comparison with offline optimal could be considered as a baseline comparison with the category of approximate offline algorithms in integral model~\cite{yao2016real}.}
+The proposed algorithms are compared to the optimal offline solution of integral model ($\textsc{iOPT}$) and $\iolp$.
+Note that comparison with offline optimal could be considered as a baseline comparison with the category of approximate offline algorithms in integral model~\cite{yao2016real}.
 
-%%% which is the running online algorithm in the Caltech ACN \cite{lee2016adaptive}. 
+%%% which is the running online algorithm in the Caltech ACN \cite{lee2018adaptive}. 
 %The proposed algorithms for fractional revenue model, \fcs and \focs, are compared to fractional version of OLP algorithm (referred to as \folp), which is implemented in Caltech ACN  (see~\cite{alinia2017online} for details).
@@
 %\vspace{-4mm}
-			\section{Conclusion}
-			\label{sec:conclusion}
-This paper proposed offline and online algorithms for the EV charging scheduling problem under fractional and integral revenue models in an adaptive charging network (ACN).
-The problem is different, and more challenging than the existing single station EV charging scheduling problems since it requires respecting the aggregate peak charging demand of the ACN.
-%More importantly, the problem is online in nature in the sense that the EVs arrive in time and the scheduler has no information regarding future arrivals. 
-As the notable contributions, our proposed online algorithm for fractional revenue model achieves constant competitive ratio of $2$.
-Moreover, the offline integral algorithm achieves a theoretical bound on the optimality gap and approximates the optimum by $92\%$, on average in experiments.
-As a future work, we plan to study the problem under posted pricing mechanism where the charging station publishes the unit price of the power (which can be varied over time) and the users can accept or reject the offer.
-\revv{Another interesting future direction is to tackle the EV charging scheduling in market-based scenarios where the prices change over time.}
-%As a future work, we plan to analyze the truthfulness of the algorithms to make sure that it is a dominant strategy for the EV owners to declare their true valuations and availabilities.
-%\vspace{-4mm}
-
-%\input{intro.tex}
-%\input{rel.tex}
-%\input{sys.tex}		
-%\input{fraction.sol.tex}		
-%\input{integral.sol.tex}
-%\input{exp.tex}
-%%%\vspace{0.1mm}
-%\input{conc.tex}
-%\newpage
-%ss
-%\newpage
-%\pagestyle{empty}
-\bibliography{ref}{}
-%\vspace{-2.8mm}
-\bibliographystyle{ieeetr}
-
-\input{app.tex}
-
-\begin{comment}
-\vspace{-10mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{alinia.jpg}}]{Bahram Alinia} received a B.Sc degree in computer science from University of Tabriz, Tabriz, Iran and a masters degree in Information Technology Engineering from University of Tehran, Tehran, Iran.
-He was a Researcher with the School of Computer Science, Institute for Research in Fundamental Sciences, Iran, from 2009 to 2012.
-He is currently a Ph.D.
-student in service architecture lab, Institute Telecom SudParis, France and participated in several European projects in the domain of smart grids.
-His research area includes wireless communications, energy systems, transportation electrification, algorithm design and approximation.
-\end{IEEEbiography}
-%\vspace{-30mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{hajiesmaili.jpg}}]{Mohammad H.
-Hajiesmaili} received the B.Sc.
-degree from the Department of Computer Engineering, Sharif University of Technology, Iran, in 2007, and the M.Sc.
-and Ph.D.
-degrees from the Electrical and Computer Engineering Department, University of Tehran, Iran, in 2009 and 2014, respectively.
-He was a Post-Doctoral Fellow with the Department of Information Engineering, the Chinese University of Hong Kong, from 2014 to 2016, and with the Department of Electrical and Computer Engineering, Johns Hopkins University, form 2017 to 2018.
-He is currently a Research Assistant Professor with the College of Information and Computer Sciences, University of Massachusetts, Amherst.
-His research interests include optimization, algorithm, and mechanism design in energy systems, electricity market, transportation networks, and multimedia networks.
-\end{IEEEbiography}
-%\vspace{-30mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{crespi.jpg}}]{Prof.
-No\"{e}l Crespi} holds Masters degrees from the Universities of Orsay (Paris 11) and Kent (UK), a diplome d'ing\'{e}nieur from Telecom ParisTech, a Ph.D and an Habilitation from UPMC (Paris-Sorbonne University).
-From 1993 he worked at CLIP, Bouygues Telecom and then at Orange Labs in 1995.
-He took leading roles in the creation of new services with the successful conception and launch of Orange prepaid service, and in standardisation (from rapporteurship of IN standard to coordination of all mobile standards activities for Orange).
-In 1999, he joined Nortel Networks as telephony program manager, architecting core network products for EMEA region.
-He joined Institut Mines-Telecom in 2002 and is currently professor and Program Director, leading the Service Architecture Lab.
-He coordinates the standardisation activities for Institut Mines-Telecom at ITU-T and ETSI.
-He is also an adjunct professor at KAIST (South Korea), an affiliate professor at Concordia University (Canada), and gest researcher at the University of Goettingen (Germany).
-He is the scientific director the French-Korean laboratory ILLUMINE.
-His current research interests are in Data Analytics, Internet of Things and Softwarisation.
-http://noelcrespi.wp.tem-tsp.eu/
-\end{IEEEbiography}	
-\end{comment}
-\end{document}

### 2025-03-09 TSUSC/systemModel.tex
move resources from other repos

--- 2019-08-26 TSC/firstSubmit/TSC.tex
@@
-\documentclass[journal]{IEEEtran}
-%\usepackage{float}
-\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-\usepackage{amssymb,amsmath}
-\usepackage[font=small,skip=10pt]{caption}
-\usepackage{subcaption}
-\usepackage{comment}
-\usepackage{color,soul}
-\usepackage{ragged2e} 
-\usepackage{algorithmicx}
-\usepackage{algpseudocode}
-\usepackage{amsthm}
-\usepackage{cite}
-\usepackage{array}
-%\usepackage{nopageno}
-\usepackage{url}
-%\usepackage{hyperref}
-%\usepackage{ulem}
-
-% *** CITATION PACKAGES ***
-%
-\usepackage{cite}
-\usepackage{color}
-\usepackage{xspace}
-\usepackage{multirow}
-\usepackage{hhline}
-%\usepackage[pdftex]{graphicx}
-
-% *** GRAPHICS RELATED PACKAGES1 ***
-%
-
-% more space
-%\usepackage{txfonts}
-\addtolength{\abovedisplayskip}{-2mm}
-\addtolength{\belowdisplayskip}{-2mm}
-\addtolength{\parskip}{-.15mm}
-%\addtolength{\arraycolsep}{-.75mm}
-\addtolength{\abovecaptionskip}{-1mm}
-\addtolength{\belowcaptionskip}{-1mm}
-%\renewcommand{\baselinestretch}{0.9}
-
-\ifCLASSINFOpdf
-\usepackage[pdftex]{graphicx}
-\graphicspath{{fig/}{../}}
-\DeclareGraphicsExtensions{.pdf,.jpeg,.png,.jpg}
-\else
-\usepackage[dvips]{graphicx}
-\graphicspath{{fig/}{../}}
-\DeclareGraphicsExtensions{.eps}
-\fi
-
-%\usepackage[caption=false,font=footnotesize]{subfig}
-%
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-%\setlength{\intextsep}{-1ex} % remove extra space above and below in-line float
-
-\renewcommand{\baselinestretch}{1}
-
-\ifodd 1
-\newcommand{\rev}[1]{{\color{black}#1}}%revise of the text
-\newcommand{\revv}[1]{{\color{black}#1}}%revise of the text
-\newcommand{\com}[1]{\textbf{\color{red}(COMMENT: #1)}}%comment of the text
-\else
-\newcommand{\rev}[1]{#1}
-\newcommand{\com}[1]{}
-\fi
-
-\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-
-%\newcommand{\opt}{\textsc{OPT}\xspace}
-\newcommand{\sa}{\textsc{SmartAllocate}}
-\newcommand{\rc}{\textsc{ReConsider}}
-\newcommand{\bc}{\textsc{BetaCover}}
-\newcommand{\ics}{\textsc{iCS}\xspace}
-\newcommand{\fcs}{\textsc{fCS}\xspace}
-\newcommand{\MCSP}{\textsf{SPAN}\xspace}
-\newcommand{\dMCSP}{\textsf{dSPAN}\xspace}
-\newcommand{\focs}{\textsc{foCS}\xspace}
-\newcommand{\iocs}{\textsc{ioCS}\xspace}
-\newcommand{\finalalg}{\textsc{ioCS+}\xspace}
-\newcommand{\opt}{\textsc{OPT}\xspace}
-\newcommand{\alg}{\textsc{ALG}\xspace}
-\newcommand{\rtl}{\textsc{GreedyRTL}\xspace}
-\newcommand{\iolp}{\textsc{ioLP}\xspace}
-\newcommand{\folp}{\textsc{foLP}\xspace}
-
-\newcommand{\be}{\begin{equation}}
-	\newcommand{\ee}{\end{equation}}
-\newcommand{\bee}{\begin{eqnarray}}
-	\newcommand{\eee}{\end{eqnarray}}
-\newcommand{\bse}{\begin{subequations}}
-	\newcommand{\ese}{\end{subequations}}
-%\def\bee#1\eee{\begin{align}#1\end{align}}
-\newcommand{\nnb}{\nonumber}
-
-\newtheorem{lem}{Lemma}
-\newtheorem{propos}{Proposition}
-\newtheorem{thm}{Theorem}
-\newtheorem{defi}{Definition}
-
-%in terms of practical feasibility and characterizing the maximum benefits of D2D load balancing is
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{corollary}[theorem]{Corollary}
-
-\makeatletter
-\newcommand\semiHuge{\@setfontsize\semiHuge{22.52}{27.38}}
-\makeatother
-\begin{document}
-	%\semiHuge
-	\title{Online EV Scheduling Algorithms for Adaptive Charging Networks with Global Peak Constraints}
-	\author{\#}
-
-	\author{Bahram Alinia, Mohammad H. Hajiesmaili, Zachary J. Lee, Noel Crespi, and Enrique Mallada
-
-		\thanks{ B. Alinia and N. Crespi are with the department of Networks and Mobile Multimedia Services (RS2M), Institut Mines-Telecom,
-			Telecom SudParis, Evry, France (e-mail: bahram.alinia@telecom-sudparis.eu, noel.crespi@mines-telecom.fr).
-
-			M. H. Hajiesmaili and E. Mallada are with the Department of Electrical and Computer Engineering, Johns Hopkins University, Baltimore, MD, USA (e-mail: \{hajiesmaili,mallada\}@jhu.edu).
-
-			Z. J. Lee is with the Department of Electrical Engineering, California Institute of Technology, Pasadena, CA, USA (e-mail: zlee@caltech.edu).
-		} }
-
-		\maketitle
-
-\begin{abstract}
-%			With the rapid growth of electric vehicles, their high demand charging jobs pose an immense challenge to the grid infrastructure. 
-			This paper tackles online scheduling of electric vehicles (EVs) in an adaptive charging network (ACN) with local and global peak constraints.
-Given the aggregate charging demand of the EVs and the peak constraints of the ACN, it might be infeasible to fully charge all the EVs according to their charging demand.
-Two alternatives in such resource-limited scenarios are to maximize the social welfare by partially charging the EVs (fractional model) or selecting a subset of  EVs and fully charge them (integral model).
-%			This paper tackles both fractional and integral models. 
-			The critical challenge is the need for online solution design since in practical scenario\revv{s} the scheduler has no information of future arrivals of EVs in a time-coupled underlying problem. 
-			For the fractional model, we devise both offline and online algorithms.
-We prove that the offline algorithm is optimal.
-Using competitive ratio as the performance measure, we prove the online algorithm achieves a competitive ratio of 2.
-The integral model, however, is more challenging since the underlying problem is NP-hard due to 0/1 selection criteria of EVs.
-Hence, efficient solution design is challenging even in offline setting.
-We devise a low-complexity primal-dual scheduling algorithm that achieves a bounded approximation ratio.
-Built upon the offline approximate algorithm, we propose an online algorithm and analyze its competitive ratio in special cases.
-Extensive trace-driven experimental results show that the performance of the proposed online algorithms is close to the offline optimum, and outperform the existing solutions.
-%			\rev{In particular, the grid and electricity providers should be aware of the electricity peak.	It is known in electricity market that the spot price is a dominating factor in billing cost.
-Hence, the utility companies need to identify a global peak constraint for the cost management purpose.
-This paper studies the online EV charging scheduling problem in a utility that offers EV charging service in a set of CSs, each of which having limited output power (referred to as local peak constraint) while taking into account the global peak constraint.
-The scheduling problem in this scenario comes with unique challenges that is not tackled previously.}
-
-%			\rev{The problem objective is to maximize total revenue of the CSs.}
-
-\end{abstract}
-		\begin{IEEEkeywords}
-			Electric Vehicle, Online Scheduling, Approximation Algorithm, Competitive Analysis
-		\end{IEEEkeywords}
-
-		\section{Introduction}
-\label{sec:intro}	
-%		\IEEEPARstart{A}{s} 
-%		a result of global warming and environmental concerns through dependence on fossil fuels, there has been a rapid proliferation in deploying renewable energy sources. 
-\IEEEPARstart{T}{o} promote quick adoption of renewable energy sources, electrification of vehicles is a trend that has been globally advocated in recent years.
-\rev{According to a Bloomberg report, EVs will account for more than half of the new car sales by $2040$~\cite{bloomberg}.
-	%the global sale of EVs increased by $80\%$ in $2015$~\cite{EVSales}.
-	%		With the significant advantage of electric vehicles (EVs) in being an environment friendly product, the global interest for EVs is rapidly growing, such that  
-	Consequently, it is expected that demand from EV charging will constitute a considerable portion of total demand. 
-	Currently, transportation consumes $29\%$ of total energy in the US, while electricity production consumes $40\%$~\cite{Zhao}.} 
-%Vehicles seen accounting for 5\% of electricity use by $2040$~\cite{EVSales2}}
-%%%\revv{\sout{Hence, rapid electrification of the vehicles makes the total electricity demand of EVs significant.}}
-
-\revv{EV charging demand is a typical example of a deferrable load, and there is often considerable flexibility in the charging schedule.
-This property makes the problem of EV charging scheduling  important and there is an extensive research along this direction in the literature (see the recent survey~\cite{mukherjee2015review}, and references therein).
-In most of the existing works, the EV charging demand is treated as a constraint to the problem in a low-load regime~\cite{Tang}.
-Motivated by rapid proliferation of EVs, this work tackles the EV scheduling in high-load regime, where given the aggregate charging demand of the EVs and the peak constraints of the charging network, it is not feasible to fully charge all the EVs according to their charging demand.}
-%		\subsection{Microgrid: Definition, Potentials, and Challenges}
-%		\label{sec:introA}
-%		A common trend in the smart grid era is to install renewable energy sources in distributed manner.
-More specifically, medium or large commercial and industrial  customers such as universities, headquarters, etc.,  can take control of their own energy consumption by local deployment of renewable sources~\cite{Hajiesmaili2016Online}.
-In this setting, the residual demand, i.e., total demand subtracted by the local renewable supply, can be acquired from the external grid.
-
-%		In addition to clean energy production, the owner of microgrid also enjoys more power sustainability and reliability, and the ability to proactively manage the energy costs.
-
-More specifically, this paper studies resource-constrained EV charging scheduling in an adaptive charging network (ACN) governed by a single operator in a campus-scale location such as a university, a headquarter\rev{s}, etc.
-\cite{wu2017two}.
-\rev{A notable example is the Caltech ACN~\cite{lee2016adaptive} where individual charging ports are organized into several \textit{charging stations} (CSs) which are dispersed in a \textit{charging network}} with the capability of adaptive charging of the EVs.
-The problem is different from EV charging scheduling \revv{with capacity constraint} in single station scenarios~\cite{Tang,Wen,Shroff2014,WTang,Chen,Xiang,Zhao,Robu} (we refer to~Section~\ref{sec:rel} for detailed discussions on related work), because of the essential need to respect the aggregate peak demand of the ACN.
-\revv{Note that, the ACN operator might limit the total power drawn from EVs to control costs~\cite{PeakPrice,Zhang2015eEnergy}, reserve the capacity for other loads, and/or participate in demand-response programs.}
-%		The EV charging loads are usually flexible and deferrable, which means that their load can be scheduled~\cite{moghaddam2017smart,DWang} to shape the total demand over time. 
-%The aim of this paper is to use the deferrable property of EVs and schedule their charging jobs, so as to \rev{maximize the revenue of the ACN}.	
-%		We refer to Section~\ref{sec:rel} for the literature review.
-
-%		In particular, real-world pricing scheme for large customers is usually a hybrid time-of-use and peak-based charging model where the peak demand can significantly impact the total energy cost, e.g., the peak price is often more than $100$ times higher than the spot price~\cite{PeakPrice,Zhang2015eEnergy}.
-Considering total aggregate demand, the peak charge portion could be as large as $20\%-80\%$ of total cost~\cite{Xu2014Reducing}.
-Consequently, a substantial cost reduction could be achieved if the total peak-demand can be proactively controlled \cite{liao2015dispatch}.
-
-%		\subsection{EV Charging Scheduling in the ACN}
-%		With the proliferation of EVs, the charging requirement of the microgrid EVs could be a portion of total microgrid electricity demand.
-
-%		To respond the electricity demand of EVs, CSs are being used where EVs can recourse to charge their battery \cite{He,liao2015dispatch,Tang}.
-There can be few to many CSs dispersed in an ACN, e.g., each for a parking garage of a building in a university campus.
-In this scenario, all parking stations are governed by a facility operator and a \textit{global} peak demand constraint is determined such that the aggregate charging demand in the entire network is less than this global peak demand \cite{DWang,Hoog}.
-
-%		The charging scheduling of the EVs with the goal of respecting the \textit{global aggregate peak constraint}, however, is a unique problem which is different from the single station EV charging scheduling.
-Most of the existing work in the literature, tackle the problem in the single parking station scenario.
-We refer to Section~\ref{sec:rel} for in-depth discussion.
-As discussed in Section \ref{sec:problem}, the global optimal solution cannot be obtained by separately solving the single station problems.
-%		On the other hand, there are only a few studies that provide global optimal solution for charging scheduling of EVs \cite{He, Moradijoz, Malhotra,Zeng,Shaaban,DWang}.
-Despite elegant results, the underlying problems, e.g., charging cost minimization problem in \cite{He}, average operating cost minimization with optimal electricity exchange capacity problem in \cite{DWang}, optimal station capacity problem in~\cite{Moradijoz}, user convenience maximization problem in~\cite{Malhotra}, joint optimization of system profit and user experience in~\cite{Shaaban,Zeng} are different from the problem studied in this paper.
-
-%		\subsection{Problem, Challenges, and Contributions}
-We consider a scenario with multiple EVs where each EV has different charging profile in terms of availability, charging demand, charging rate limit, and valuation of getting charged \revv{(for details see Section~\ref{sec:ev})}.
-We formulate an online EV charging scheduling problem with the goal of \textit{selecting} and \textit{scheduling} a subset of EVs such that: (1) the charging demand of the selected EVs are (fully or partially) satisfied; (2) the charging rate limit of EV batteries are respected, (3) the global peak constraint of the ACN is satisfied~\cite{lee2016adaptive}; (4) the local peak constraint of each CS is respected;  and finally, (5) the total revenue obtained by the valuation of the EVs is maximized.
-
-%		of maximizing the revenue of the ACN.
-The constraints are the \textit{local} peak constraint of each CS, and the \textit{global} peak constraint that limits the accumulative charging demand drawn from the entire network of stations (decided by the administration of the ACN to control total peak demand~\cite{lee2016adaptive}).
-
-There are two main challenges in the design and implementation of scheduling algorithms for EVs satisfying the goals mentioned above.
-\rev{Firstly, the problem calls for online scheduling design.} In practice, EVs arrive to the CS in online fashion and the scheduler has no information about the arrival and demand of the future EVs.
-Secondly, the underlying optimization problem in integral model is NP-hard even in offline case \rev{(see Section~\ref{sec:integral})}.
-This is because the problem is a mixed integer linear problem and a ``time-expanded'' extension of knapsack problem which is known as a classic NP-hard problem.
-In this paper, we tackle the challenge of online design by following competitive algorithm design~\cite{borodin2005online} and the challenge of NP-hardness by pursuing approximation algorithm design~\cite{approx} and make the following contributions:
-
-$\vartriangleright$ We first consider a \textit{fractional model} (where EVs can be charged partially and the revenue is proportional accordingly) and design an optimal offline scheduling algorithm. 
-%In addition to provide efficient result, the algorithm has a further elegant step to apply a valley filling strategy to further reduce the peak demand of EV charging without degrading total revenue. 
-We then develop an efficient online algorithm in which no exact or stochastic information about the future EV arrivals is given.
-Despite its simplicity, the algorithm is proved to be $2$-competitive with optimal offline solution, i.e., the revenue of the proposed online algorithm is at least $1/2$ of the offline optimum, regardless of input sequence.
-Even though there are competitive algorithms in the literature for similar problems, to the best of our knowledge, our algorithm is the first $2$-competitive algorithm \rev{which considers the} charging rate limits.
-
-$\vartriangleright$ We next study \rev{the} more challenging scenario of \rev{the} \textit{integral model}\rev{, }where EVs must receive all their demand to make revenue.
-We first propose a polynomial-time primal-dual offline approximate algorithm.
-We analyze the approximation ratio of the algorithm and by strengthening the linear relaxed version of the mixed integer problem~\cite{Carr}, we obtain an approximation ratio of $\alpha =1+\sum_{j=1}^m {\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}$, where $p_j$ is local peak constraint in station $j$, $q_j$ is the maximum charging rate of the EVs in station $j$ and $s$ is a slackness parameter.
-We highlight that when $p_j \gg q_j$ and $s$ is \rev{large} enough, then $\alpha \approx m+1$, where $m$ is the number of stations in the ACN.
-Built on the basis of the offline algorithm, we devise an online algorithm, and discuss its competitive ratio in special cases.
-%In particular, the competitive ratio is $b\Big(1+\frac{p_j}{p_j-q_j}\cdot\frac{s}{s-1}\Big)$ for single station scenario, where $b$ is the number of batches with the same arrival time.
-
-$\vartriangleright$ We conduct a set of  simulations to evaluate the performance of our proposed algorithms. 
-%For offline scheduling problem under integral charging model, the results  demonstrate that the proposed approximation algorithm is close to the optimal solution and is significantly better than the obtained theoretical bounds.
-The results of online algorithms for both integral and fractional settings are close to the optimum (within $90\%$ and $94\%$ for integral and fractional models in a representative scenario).
-In addition, our algorithm outperforms the existing scheduling algorithm in Caltech ACN~\cite{lee2016adaptive} by $35\%$ for integral revenue model.
-%The simulation section also discusses on the positive and negative effects of slackness parameter in different scenarios.
-
-%To the best of our knowledge, this problem is not addressed yet in previous studies.
-
-%		\subsection{Paper Organization}
-%		The rest of this paper is organized as follows. Section~\ref{sec:rel} reviews the literature. In Section \ref{sec:model}, the system model  and problem formulation are described. 
-%		Section \ref{sec:fractional} provides offline and online algorithms for fractional model.
-We study integral model in Section \ref{sec:integral} and propose online and offline algorithms.
-The simulation results are reported in Section~\ref{sec:simul}.
-Section~\ref{sec:conclusion} concludes the paper and highlights future directions.
-
-\section{Related Work}
-\label{sec:rel}
-\revv{There is an extensive work in the general topic of EV demand management and scheduling~\cite{mukherjee2015review} by considering different scenarios such as optimal operations with EV coordinations~\cite{mukherjee2017distributed}, EV scheduling with incorporation of renewable energy, and energy storage systems~\cite{de2017impact,shafie2018innovative}.
-In this section, we focus on the literature related to peak-constrained EV charging scheduling in single and multiple stations.}
-\subsubsection{Peak-Constrained EV Charging Scheduling}
-\label{sec:rel:peakconstrained}			
-\revv{There is an extensive literature on EV charging scheduling problem focusing on single CS~\cite{Tang,Wen}, while the local and global peak constraints are omitted or only the local peak is considered.}	As we discuss in Section~\ref{sec:problem}, the global optimal solution cannot be obtained by separately solving the single station problems.
-Hence, those solutions cannot be directly applied to the multiple CS scenario with global peak constraints.
-
-%A scenario that local and global peak constraints exist is the case that scheduling is required for a charging network for multiple CSs. 
-Studies in \cite{He,malhotra2017distributed,Moradijoz,DWang,Zeng,Shaaban} tackled charging scheduling problem in multiple CSs.
-The authors in~\cite{He} studied a global cost minimization EV charging scheduling problem.
-However, there is no limit on the maximum peak demand that the system can tolerate.
-Consequently, the peak can be arbitrary high and beyond the physical limit of the transformers in the charging station~\cite{lee2016adaptive} leading to huge electricity bills~\cite{Zhang2015eEnergy}.
-Besides, the charger devices installed in the CSs have limitation on the maximum power that they can transfer in each time unit~\cite{Tesla}.
-%We solve the issue by constraining local and global peaks.
-However, to meet the peak constraints, it may not be feasible to respond to all charging demands.
-Consequently, only a subset of EVs can be charged~\cite{Xiang}, which is captured in our problem formulation.
-\cite{DWang} considered a multi-microgrid system with global peak constraint where each microgrid has a CS and the goal is to manage electricity exchange between microgrids and main grid to minimize the operating costs.
-The authors assume that required information about individual EVs is available by forecast which may not represent a real scenario.
-A similar assumption is made in \cite{Zeng,Shaaban} where the objective is to maximize total utility of EVs and aggregators in a distribution network.
-%\rev{To be removed: In our solution, we applied a priority based selection process (based on the EVs' valuation) to respond to the demands to make sure that total peak respects the constraints.
-The selection process can be made based on different criteria such as the value of each charging request \cite{Lee, Xiang} or the priority.}
-%To avoid big billing cost in peak hours, \cite{Moradijoz} proposed a solution based on genetic algorithm to find optimal capacity and location of parking lots for serving demands in peak hours with the goal of maximizing total benefit of all stations.
-Although authors studied the problem under multiple CS setting, their solution is not applicable to our setting when the CSs are already set up.
-The authors in~\cite{malhotra2017distributed} use a similar model as in this paper, where both local and global peak constraints are considered.
-However, the authors solve the single-slot problem, which fails to provide a general solution taking into account EVs' arrival and departure times as considered in our study.
-Finally, as an alternative approach to control the peak, some studies directly target minimizing the peak~\cite{Zhao, Karfopoulos}.
-In~\cite{Zhao}, an online algorithm is developed for EV charging to minimize the peak and \cite{Karfopoulos} proposed a valley filling method by leveraging V2G in peak hours.
-Although the peak is minimized in above works, it cannot guarantee that the minimized peak is tolerable by the underlying charging network.
-
-\subsubsection{Scheduling Under Demand Uncertainty}
-A main challenge in EV scheduling problem is to cope with demand uncertainty.
-Many studies including \cite{Shroff2014,Tang,WTang,Chen,Xiang,Zhao,Robu} addressed online scheduling problem with different objectives.
-\cite{Shroff2014,Xiang} studied the problem of maximizing social welfare considering the benefit for both users and service provider.
-\cite{Tang} and \cite{WTang} developed algorithms to minimize the charging price for the CS, where the proposed algorithm in \cite{Tang} is $2.39$-competitive.
-%An online algorithm developed in \cite{Chen} to optimize overall operating profit of the service provider. 
-In \cite{Robu}, an online $2$-competitive algorithm is proposed for a single CS, assuming that EVs are capable of being discharged in a negligible amount of time.
-The assumption, however, is not realistic for EVs.
-
-Our problem in this paper is unique from above works in many respects.
-First, we study the problem in an ACN where several CSs exist, while none of the above studies solve the problem under this setting.
-Second, the previous algorithms do not work for both integral and fractional charging models.
-In addition, \cite{WTang,Chen} put no limit on the charging rate of EVs which makes their solution impractical in real scenarios.
-Also, \cite{WTang,Tang, Shroff2014,Chen,Zhao} do not consider the peak limit of the CS.
-\revv{Note that some studies~\cite{jin2017optimal} tackle the scenarios of satisfying the large demands (possibly EV demands) by participating in electricity market.
-This study assumes that the electricity price is given and fixed, and leaves the case of real-time pricing as the future direction.
-In addition, there are studies that incorporate prediction in online EV charging scheduling~\cite{wang2017predictive,chen2014distributional}.
-The prediction-based approaches achieve satisfactory performance for the scenarios that follow prediction.
-Deviation from prediction models, however, degrades their performance.
-Our approach, on the other hand, has no assumptions on modeling/prediction, and in this way, is robust against any uncertainty in the instances to the problem.}
-\revv{Finally, in~\cite{Alinia2018ITS}, we considered a simplified EV charging scheduling in fractional model without global peak constraints and devised heuristic algorithms (without competitive and approximation analysis) with on-arrival commitment for EVs to notify the amount that they can receive by their departure.
-}
-%In this paper, we consider these limitations and develop online and offline algorithms for fractional and integral revenue models in an ACN and provide theoretical bounds on their performance.
-
-%It is important to note that there is a considerable similarity between EV scheduling problem and classical job scheduling problem \cite{}.
-However, most algorithm developed for job scheduling problem  do not consider a limit on processing rate of the jobs.
-
-%\cite{Shroff2014} and \cite{Stein2012} study social welfare maximization problem while the profit of both EV owners and CS is considered.
-social welfare of the EV owners \cite{Stein2012}, charging cost \cite{Tang,WTang}, and total value of fully charged EVs \cite{Azar}).
-In addition, \cite{WTang, Tang,Shroff2014,Zhao} do not take into account the peak limitation of CS.
-}
 \section{System Model and Problem Formulation}
@@
 \label{sec:acn}
-Our charging network model is inspired by the Caltech ACN~\cite{lee2016adaptive} as illustrated in Fig.~\ref{fig:model-a}.
+Our charging network model is inspired by the Caltech ACN~\cite{lee2018adaptive} as illustrated in Fig.~\ref{fig:model-a}.
 In \rev{the} Caltech EV charging network (located in a parking garage), electricity is distributed through a two-level transformer architecture from a main switch panel to multiple EV switch panels (\rev{$2$} panels in the current Caltech ACN).
@@
 The total power drawn from the main switch panel \rev{by} the charging network has a power limit of  $p^\mathsf{total}$, that is determined by the facility operator to control the costs, reserve the capacity for other loads, and/or participate in demand-response programs.
-%This power, where we refer to it as \emph{network power limit} is used for both EV charging as well as non-EV charging purposes (e.g., lighting, fans, etc \cite{lee2016adaptive}). 
+%This power, where we refer to it as \emph{network power limit} is used for both EV charging as well as non-EV charging purposes (e.g., lighting, fans, etc \cite{lee2018adaptive}). 
 In other words, $p^\mathsf{total}$, which we refer to it as the \textit{global peak}, hereafter, limits the maximum aggregate EV charging load at each time slot. 
@@
 \rev{It is often observed that the charging demand of different CSs (EV switch panels in Fig.~\ref{fig:model-a}) are well below the local peak constraints.}
-To increase the flexibility due to heterogeneous charging demand of CSs, in the Caltech ACN, the global peak constraint of the main switch can be \textit{over-provisioned}, i.e., $p^\mathsf{total}$ is less than the aggregate local peaks,  ($\sum_j p_j\geq p^\mathsf{total}$).
-\rev{While this increases flexibility, it also couples the problem of EV charging scheduling across different CSs.}
+To reduce costs by taking advantage of flexibility due to heterogeneous charging demand of CSs, in the Caltech ACN, the global peak constraint of the main switch can be \textit{over-provisioned}, i.e., $p^\mathsf{total}$ is less than the aggregate local peaks,  ($\sum_j p_j\geq p^\mathsf{total}$).
+\rev{While this decreases costs, it also couples the problem of EV charging scheduling across different CSs.}
 %Despite increased flexibility, the over-provisioning property, however, couples the problem of EV charging scheduling across different CSs. 
@@
 					\begin{center}
-						\includegraphics[width=\textwidth]{model-a.pdf}
+						\includegraphics[width=\textwidth]{model-a.png}
 						\caption{Caltech adaptive charging network (ACN)}
@@
 					\begin{center}
-						\includegraphics[width=\textwidth]{model-b.pdf}
+						\includegraphics[width=\textwidth]{model-b.png}
 						\caption{Communication model with server}
@@
 				\end{subfigure}%  
-\caption{System model \cite{lee2016adaptive}.} 
+\caption{System model \cite{lee2018adaptive}.} 
 \label{fig:slackness1}
@@
 		Moreover, $q_j$ denotes the maximum $k_i$ among all EVs in CS $j$, i.e., $q_j=\max_{h(i)=j} k_i$. 
-		\revv{Finally, $v_i$ is the willingness to pay of EV $i$ to receive its entire demand $D_i$ before the departure time $d_i$.
+		Finally, $v_i$ is the willingness to pay of EV $i$ to receive its entire demand $D_i$ before the departure time $d_i$.
 Note that in resource-constrained EV scheduling in ACN, it is not feasible to fulfill the entire demand of all EVs, hence, the problem turns into a resource allocation one with the goal of maximizing the aggregate value (a.k.a.
 utility) obtained from the EVs.
-In this way, each user can announce its willingness to pay to get charged which is denoted by $v_i$ in the system model.}
+In this way, each user can announce $v_i$ as its willingness to pay to get charged.
 		%We assume that there is no gain for the CS if EV $i$ is partially charged.
@@
 %In the next two sections, we devise several algorithms to solve the \MCSP under the two revenue models (integral and fractional) and for both offline and online scenarios.
-		\section{Fractional Revenue Model}
-		\label{sec:fractional}
-
-%\subsection{Overview of Fractional Revenue Model}
-%\label{sec:frac.overview}				
-		%In the previous section, we devised an approximation algorithm for the integral revenue model in which it is assumed that the obtained revenue is zero if the allocated resource is less than the demand.
-Although this assumption is reasonable in some scenarios,
-%To develop a solution for the \MCSP, we first consider fractional revenue model.
-%However, algorithms for integral revenue model cannot achieve the same performance as the algorithms of this section i.e., \fcs and \focs.
-
-In the fractional model, the revenue of the CS from EV $i$ is directly proportional to the amount of resource that the EV is received, i.e.,
-		\begin{equation}
-			v_i^{\mathsf{f}}=\frac{\sum_t y_i^t}{D_i}v_i,
-			\label{Eq:partial_value}
-		\end{equation}
-		where $v_i$ is the gain, if the entire demand $D_i$ is fulfilled and $v_i^{\mathsf{f}}$ is the fractional gain.
-
-%Under fractional revenue model and without the binary variable of selecting EVs, the underlying problem turns into a linear one. 
-We propose a simple algorithm, called \fcs, with low computational complexity \rev{ of $O(n^2T+nT^2)$} for the fractional model that finds the optimal solution in offline setting.
-Note that even though linear programs can be solved in polynomial time in general, the complexity of our proposed algorithm is much lower than the general linear program algorithms.
-Moreover, our proposed offline algorithm applies a valley-filling strategy to reduce the peak.
-%The details of the proposed algorithm \fcs is given in~\cite{alinia2017online}.
-In the following, the online $2$-competitive algorithm is designed, where no exact information or stochastic modeling of future inputs of the problem is available.
-A summary of proposed algorithms with their complexity and assumptions is given in Table \ref{tbl:algs}.
-
-\revv{
-\subsection{Optimal Offline Design}
-\label{sec:fopt}				
-We refer the proposed algorithm as the \fcs and summarize it as Algorithm~\ref{alg:optimal-off}.
-The \fcs works in two phases.
-In the first phase (Section~\ref{sec:ph1}), the algorithm decides on the amount of resource to be allocated to each EV within its availability window and reserves resources accordingly.
-In this phase, the details of allocation is not known.
-The actual resource allocation is done in the second phase (Section~\ref{sec:ph2}) by setting variables $y_i^t$.
-
-Before discussing the details of the algorithm, we give a definitions and introduce some notations to facilitate our algorithm design.
-
-\begin{defi}
-	Time interval $[\delta,\delta']$ is a ``super interval'' for interval $[t,t']$ if $1\leq \delta\leq t \text{~AND~} t' \leq \delta'\leq T$.
-	Moreover, $\mathcal{I}_{t,t'}$ is the set of all super intervals of interval $I_{t,t'}$ i.e., ${\mathcal{I}_{t,t'}=\{[\delta,\delta']: 1\leq \delta\leq t \text{~AND~} t'\leq \delta'\leq T\}}$.
-\end{defi}
-
-%		For example, $\mathcal{I}_{1,1}=\{I_{1,1},I_{1,2},I_{1,3},\dots ,I_{1,T}\}$. 
-The number of super intervals of an interval is at most $T^2$ and at least one (for interval $[1,T]$).
-
-Let $R_i$ be the amount of resource that is reserved for EV $i$ by the \fcs and $I_{t,t'}$ as time interval $[t,t']$.
-% with $t,t'\in\{1,\dots ,T\}$ which includes time slots $t,t+1,\dots ,t'$. 
-Then, assuming that charging demands are sorted in non-increasing order of their unit values, $A^i_j(t,t')$ is the aggregate residual resource in interval $I_{t,t'}$ at station $j$ assuming that the reservation for EVs $1$ to $i$ is accomplished.
-We now explain in detail each phase of the algorithm.
-
-\subsubsection{Phase I-Reservation\label{sec:ph1}} In Line~\ref{algline:sort1}, the EVs are sorted in a non-increasing order of their unit values.  
-%		i.e., ${v_1\slash D_1\geq v_2\slash D_2\geq\dots \geq v_n\slash D_n}$. 
-In Line~\ref{algline:setR}, the \fcs processes demand of EV $i$, picked from top of the ordered list, and sets $R_i$ as the amount to be reserved for EV $i$ which will be allocated in Phase II.
-In Line~\ref{algline:seta}, the residual resource of all intervals in set $\mathcal{I}_{a_i,d_i}$ decreases by $R_i$ and EV $i$ is added to the set of selected EVs.
-
-\begin{algorithm}[t]%\small%1
-	%\footnotesize
-	\revv{
-	\caption{\fcs}
-	\label{alg:optimal-off}
-	\DontPrintSemicolon 
-	\KwIn{$n$ EVs with their profile, local and global peak constraints $p_j, j=1,\dots ,m$ and $p^\mathsf{total}$ }
-
-	\KwOut{Optimal scheduling under fractional model}
-	\BlankLine
-
-	Sort charging requests in non-increasing order of their unit values, i.e., $\frac{v_1}{D_1}\geq \frac{v_2}{D_2}\geq\dots \geq \frac{v_n}{D_n}$\label{algline:sort1}
-
-	%	\slash\slash\textit{\texttt{Use sorted list to process demands}}
-
-	$\mathcal{L}\leftarrow \emptyset$
-
-	\slash\slash\textit{\texttt{Phase I}}
-
-	\For{$i=1,\ldots, n$}{
-		%\slash\slash\textit{\texttt{update demand and value}}
-
-		$R_i \leftarrow \min\{D_i, \min\limits_{t,t'} A^{i-1}_{h(i)}(t,t'), \forall t,t': I_{t,t'}\in\mathcal{I}_{a_i,d_i}\}$\label{algline:setR}
-
-		\If{$R_i>0$}{
-			$A^{i}_{h(i)}(t,t')\leftarrow A^{i-1}_{h(i)}(t,t')-R_i, \forall t,t': [t,t']\in\mathcal{I}_{a_i,d_i}$ \label{algline:seta}\\
-			$\mathcal{L}\leftarrow \mathcal{L}\cup{i}$
-	}}
-	\slash\slash\textit{\texttt{Phase II}}
-
-	Sort EVs in $\mathcal{L}$ in increasing order of their charging flexibility i.e., $\frac{(d_i-a_i+1)k_i}{D_i}, i\in \mathcal{L}$.
-
-	%	Let $i$ be the index of $i^{th}$ EV in list $\mathcal{L}$
-
-	\For{$i=1,\ldots, |\mathcal{L}|$}{
-
-		Pick EV $i$ from the sorted list $\mathcal{L}$.
-
-		$\emph{feasible}\leftarrow \big(\sum_{t=a_i}^{d_i}\min\{k_i,A^{i-1}_{h(i)}(t,t)\}\big) - R_i$
-
-		\If{feasible $<0$}{
-			Re-allocate previously allocated EVs such that $\emph{feasible}\geq 0$
-		}
-		Arbitrarily allocate $R_i$ to EV $i$ in its availability window\label{algline:fcsallocate}	
-	}}
-\end{algorithm}
-
-\begin{lem}
-	Provided that for EV $i$ we have 
-	\bee
-	\label{eq:ri}
-	R_i\leq\min\left\{D_i, \min_{t,t'} A^{i-1}_j(t,t'), \forall t,t': I_{t,t'}\in\mathcal{I}_{a_i,d_i}\right\}
-	\eee
-	 with a dummy $A^0_j(t,t')$ defined as
-$A^0_j(t,t')=(t'-t+1)\times\min \{p^\mathsf{total},p_{j}\},$
-	then there is a feasible allocation to allocate $R_i$ to EV $i$ in its availability window $[a_i,d_i]$. 
-	\label{thm:R_feasible}
-\end{lem}
-
-In Lemma \ref{thm:R_feasible}, $A^0_j(t,t')$ indicates the available resource when no charging request is processed in $I_{t,t'}$. 
-In Eq.~\eqref{eq:ri}, the second term, i.e., $\min_{t,t'} A^{i-1}_{j}(t,t')$, indicates the minimum remaining resource in all super intervals of interval $I_{a_i,d_i}$.
-For $i\geq 1$, $A^i_j(a_i,d_i)$ is defined as follows:
-
-\begin{equation*}
-A^i_j(a_i,d_i)=\begin{cases}
-A^{i-1}_j(a_i,d_i)-R_i & j=h(i),\\
-A^{i-1}_j(a_i,d_i) & j\neq h(i).
-\end{cases} 
-\end{equation*}
-
-The optimal value of $R_i, i=1,\dots ,n$ is set according to the following lemma:
-
-\begin{lem}
-	Given $n$ EVs sorted in a non-increasing order of the unit values, ${v_1\slash D_1\geq v_2\slash D_2\geq\dots \geq v_n\slash D_n}$, and the value of $R_i$, where $R_i$ is set after $R_{i-1}, i=2,\dots ,n$ by Eq.~\eqref{eq:ri}, then,
-	$$R_i = \min\left\{D_i, \min_{t,t'} A^{i-1}_{h(i)}(t,t'), \forall t,t':I_{t,t'}\in\mathcal{I}_{a_i,d_i}\right\},\forall i,$$
-	is the optimal value for $R_i$. 
-	\label{thm:R_star}
-\end{lem}
-
-\subsubsection{Phase II- Allocation\label{sec:ph2}} Lemma~\ref{thm:R_feasible} shows that there is a feasible scheduling to allocate the reserved resources.
-However, despite its feasibility, it is not straightforward to find such \revv{a schedule}.
-For example, assume that for EV $i$, $R_i=10$ and $k_i=4$.
-It is possible that all available resources are concentrated in a single time slot but EV $i$ cannot use more than $4$ kWh of it.
-In this situation, the previously allocated resources in interval $I_{a_i,d_i}$ should be re-allocated such that the concentrated resources are \emph{dispersed} and we have $\sum_{t=a_i}^{d_i}\sigma_t \geq R_i$ where $\sigma_t =\min\{k_i,A^{i-1}_{h(i)}(t,t)\}$ is the maximum resource that can be allocated to EV $i$ at time slot $t$.
-Since the total amount of allocated resource does not change in the interval, such dispersion is possible and can be done by a simple algorithm in which allocates $\min\{k_i,A^{i-1}_{h(i)}(t,t)\}$ starting from time slot $t=a_i$ until $R_i$ units is allocated.
-To further reduce the peak of the system, we will develop \sa\ algorithm (See Section \ref{sec:integral}) which acts more intelligent so that Line \ref{algline:fcsallocate} of the \fcs can be replaced by ``Run \sa$(i,R_i)$''.
-
-\begin{thm}
-	\label{cor:1}
-	\fcs is an optimal solution under fractional revenue model.
-\end{thm}
-
-The following theorem characterizes the complexity of \fcs.
-
-\begin{thm}
-	\label{thm:complexity}
-	The time complexity of \fcs algorithm is $O(n^2T+nT^2)$ where $n$ is the number of EVs and $T$ is number of time slots.
-\end{thm}
-}
-
-\vspace{-4mm}
-\subsection{Online Scenario}
-\label{sec:fonline}
-In this section, we devise an algorithm for the scenario that EVs arrive in online fashion.
-The scheduling decisions at each time slot are made given the information of available EVs and neither exact values nor stochastic modeling of future arrivals is available.
-Our goal is to obtain a \emph{competitive ratio} for the online algorithm.
-A scheduling algorithm $\mathcal{A}$ is $c$-competitive for $c\geq 1$ if the revenue obtained by the optimal offline algorithm is at most $c$ times the algorithm $\mathcal{A}$'s revenue for any input sequence~\cite{borodin2005online}.
-
-The proposed online algorithm for the fractional model, referred to as \focs, is listed as Algorithm~\ref{alg:focs}.
-The \focs is a simple yet efficient algorithm that always selects EVs with highest unit value to allocate as follows.
-First, the algorithm sorts the available EVs at each time slot~$t$ based on their unit value (Line~\ref{algline:sort}).
-\revv{In this step, the algorithm breaks ties based on EVs' deadline i.e., if two EVs have the same unit value, then the one with earliest deadline comes first in the sorted list.} Next, the \focs selects one EV at a time from the sorted list to allocate with maximum charging rate considering the EV's remaining demand, maximum charging rate, and peak constraints (Lines~\ref{algline:focsfor}-\ref{algline:focssety}).
-The allocation is continued until all resources are allocated or there is no more EV that could be allocated.
-%For unselected EVs, the value of $y_i^t$ will be $0$ in Line \ref{algline:focssety} of the algorithm. 
-The time complexity of the \focs is $O(n^2T)$, determined by cost of its ``\textbf{for}'' loop multiplied by total number of times that the algorithm needs to be run.
-% i.e., $T$.
-
-\vspace{-4mm}
-\begin{algorithm}%\small%1
-\footnotesize
-\caption{\focs: $\forall t\in \{1,2,\dots ,T\}$}
-\label{alg:focs}
-\DontPrintSemicolon 
-%\KwIn{Available EVs at time slot $t$, number of CSs $m$, local peak constraint $p_j, j=1,\dots ,m$, global peak constraint $p^{\textrm{total}}$}
-
-%\KwOut{A feasible charging scheduling}
-
-%$\backslash\backslash\texttt{Initialize:}$
-
-\BlankLine
-
-$\mathcal{M}^t\leftarrow$ The set of available EVs that not received their entire demand by $t$
-
-Sort EVs in set $\mathcal{M}^t$ indexed by $i=1,\dots ,|\mathcal{M}^t|$: $v_1/D_1\geq v_2/D_2\geq\dots\geq v_{|\mathcal{M}^t|}/D_{|\mathcal{M}^t|},$  \revv{where ties are broken based on users' deadline (giving priority to the users with earliest deadline) }\label{algline:sort}
-
-\For{$i=1,\ldots,|\mathcal{M}^t|\label{algline:focsfor}$}{
-
-$y_i^t\leftarrow \min\{k_i,D_i-\sum_{\tau=a_i}^{t}y_i^{\tau},p_{h(i)}-\sum_{i':h(i')=h(i)}y_{i'}^t,p^{\textrm{total}}-\sum_{i'}y_{i'}^t\}$ \label{algline:focssety}
-
-}
-
-\end{algorithm}
-Despite the simplicity of \focs which makes it easy to implement, its performance is sound and within a constant factor of the offline optimum.
-We now proceed to analyze the performance of the \focs by first giving some preliminaries.
-
-Fix an optimal scheduling and let $\mathcal{S}_{\focs,t}$ and $\mathcal{S}_{\opt,t}$ be the sets of EVs selected by the \focs and optimal solution at time slot $t$, respectively.
-Let $y_{i}^t$ and $z_{i}^t$ be the charging rate of EV $i$ set by \focs and \opt, respectively.
-We define $\Delta_{i}^t$ as follows:
-\begin{equation}
-\label{eq:delta}
-\Delta_{i}^t =
-     \begin{cases}
-       \min\{z_{i}^t-y_{i}^t,r_{i,t}\} &\quad i\in\mathcal{S}_{\opt,t},z_{i}^t>y_{i}^t, \\
-       0& \quad\text{otherwise},  \\
-     \end{cases}
-\end{equation}
-where $r_{i,t}$ is the remaining demand of EV $i$ by the end of time slot $t$.
-$\Delta_{i}^t>0$ indicates that the optimal algorithm allocated $\Delta_{i}^t$ units more resources to EV $i$ than the \focs by time slot $t$ that could be \emph{feasibly} allocated by \focs to the EV $i$.
-If for any EV $i\in\mathcal{S}_{\opt,t}$ and time slot $t\in\mathcal{T}$ we have $y_{i}^t=z_{i}^t$, i.e., $\Delta_{i}^t=0$, then the \focs is obviously optimal because it gains whatever the optimal solution gains.
-\rev{We define \textit{loss} of the \focs imposed by EV $i$ as follows:
-\begin{equation}
-\label{lBj0}
-l_{i,t}=\Delta_{i}^t\frac{v_i}{D_i},
-\end{equation}
-
-Note that the loss always takes a non-negative value as $\Delta_i^t\geq 0$.} When \focs sets charging rate of an EV less than its rate in the optimal solution, it gains $\Delta_{i}^t v_i/D_i$ less than the optimal solution from that EV.
-An upper bound for the distance between the optimal objective value (denote by \opt) and the revenue of the \focs (denote by \alg) is summation of the losses over all time slots and all EVs, i.e.,
-\begin{equation}
-\label{eq:optdist}
-\opt-\alg\leq \sum_{t=1}^T\sum_{i\in\mathcal{S}_{\opt,t}} l_{i,t}.
-\end{equation}
-
-%Notice that it is possible that an algorithm does not choose any selected EV by a particular optimal solution but still provide an optimal or near-optimal solution as there can be multiple optimal solutions.
-In particular, $\mathcal{S}_{\focs,t}\cap \mathcal{S}_{\opt,t}=\emptyset, \forall t$ cannot lead to any conclusion on the competitive ratio of the \focs.
-In addition to the amount of loss, the gain of the algorithm from charging alternative EVs should also be taken into account in comparison between \opt and \alg.
-
-Let $i\in\mathcal{S}_{\opt,t}$, $i\notin\mathcal{S}_{\alg,t}$ and $g_{i,t}$ be the gain that the \focs obtains from charging another EV instead of $i$ at time slot $t$.
-We are going to show that in the \focs, for each EV $i$ with $l_{i,t}>0$ there must be another EV (denote by $i'$) where $y_{i'}^t\geq \Delta_i^t$ and $\frac{v_{i'}}{D_{i'}}\geq \frac{v_i}{D_i}$ which means in resource allocation phase for EV $i$, the \focs allocated the difference $\Delta_i^t$ to another EV with the same or higher unit value.
-This can be proved by considering the fact that (i) the selected EVs have higher unit values than the unselected EVs, and (ii) the charging rate of the selected EVs are set to the maximum feasible value.
-Moreover, the \focs is \emph{``work-conserving''} i.e., it does not let any resource remain unused if there are some EVs that can use it.
-
-Let $g_{i,t}$ denote the gain that \focs obtains from allocating the same amount of resource that optimal algorithm allocated to EV $i$ (with size $z_i^t$) to another EV(s).
-If $\Delta_{i}^t=0$, the loss is zero. If $\Delta_{i}^t>0$, then by the charging strategy that the \focs uses we can conclude that (i) $i$ is not finished by the \focs, and (ii)
-\rev{no more resources from station $p_{h(i)}$ can be feasibly allocated,} otherwise, the \focs could allocate more resources to EV $i$.
-Therefore, the $\Delta_{i}^t$ units of the resource \rev{are} allocated to one or multiple other EVs (denote them by set $\mathcal{J}_i^t$) by the \focs.
-Moreover, it must hold that all the EVs in set $\mathcal{J}_i^t$ have a unit value equal to or higher than $v_i/D_i$ which yields $g_{i,t}\geq l_{i,t}$, otherwise, the \focs should not prefer the EVs in $\mathcal{J}_i^t$ to $i$.
-\rev{Since the result holds for any arbitrarily EV $i$, we can get the following:}
-
-\begin{equation}
-\label{eq:lg}
-\sum_{i=1}^n\sum_{t=1}^Tl_{i,t}\leq\sum_{i=1}^n\sum_{t=1}^Tg_{i,t}.
-\end{equation}
-
-Moreover, the total gain of \focs, i.e., \alg, is equal to sum of its gains from each single EV:
-\begin{equation}
-\label{eq:ALG}
-\rev{\alg= \sum_{i=1}^n\sum_{t=1}^Tg_{i,t}.}
-\end{equation}
-
-With the above discussion and using Eqs. (\ref{eq:optdist}), (\ref{eq:lg}) and (\ref{eq:ALG}) we are able to derive a competitive ratio of $2$ for the \focs.
-
-\begin{thm}
-	\label{thm:focscompetitive}
-	The \focs is $2$-competitive.
-\end{thm}
-
-\emph{Remarks:} When there is only one CS and EVs have no limit on their charging rate, the \focs is identical to the \textsc{FirstFit} algorithm ~\cite{firstfit} which is known to be $2$-competitive for classic job scheduling problem.
-However, the charging rate limitation is crucial for EV charging problem.
-Moreover, \cite{firstfit} uses \revv{a} ``charging argument'' to prove the competitive ratio of the proposed algorithm which cannot be directly applied to our problem.
-Thus, the \focs extends the \textsc{FirstFit} and makes it practical for the EV charging scenario.
-Moreover, the proof technique used for the competitive analysis of the \focs is fundamentally different from the one used in \cite{firstfit}.
-%%%Finally, in~\cite{Robu} an online $2$-competitive algorithm for EVs with partial charging is proposed.
-The competitive ratio obtained assuming that charging of EVs is instantly reversible at departure times.
-This assumption is not practical in reality since similar to charging phase, there is a discharging rate constraint for EVs.
-
-%\begin{thm}
-%\label{thm:focscomplexity}
-%
-%The time complexity of \focs is $O(nT\log n)$.
-%\end{thm}
-		\section{Integral Revenue Model}
-		\label{sec:integral}
-%
-%		\subsection{Overview of Integral Revenue Model}
-%		\label{sec:intoverview}
-		The MILP form of the \MCSP in integral model is a generalized form of the $0/1$-knapsack problem which is a well-known NP-hard problem.
-\rev{To give an intuition, consider the scheduling problem in a single time slot (i.e, $T=1$).
-Then, allocating power resources to the EVs is equivalent to allocating the capacity of knapsack to the items.
-}
-		In Section~\ref{subsec:icsalgorithm}, we propose a fast polynomial time offline approximation algorithm for the integral problem.
-In Section~\ref{sec:onlineint}, we extend the result and propose an online algorithm for the integral model.
-%		, where the EVs arrive in slot-by-slot fashion, and the scheduler has no information of the future arrivals.
-
-%The problem is even more challenging when the uncertainty in EVs' arrival is taken into account.
-At each time slot, the scheduler has no information of unit values of the future charging profiles.
-Therefore, the scheduler cannot make sure about the efficiency of its current charging decision.
-%It can be shown that when there is no assumption on the charging profiles of EVs (including the value of slackness parameter) and the charging decision , no online algorithm can provide a performance guarantee meaning that in the worst case, the ratio of the optimal objective value to the one obtained by the online algorithm can be arbitrary small.
-In fact, when the online algorithm selects
-
-		\subsection{Offline Scenario}   
-		\label{subsec:icsalgorithm}
-		We design our offline scheduling algorithm under integral model referred to as \ics, to solve the \MCSP approximately. 
-%		Our algorithm design is inspired by the basic algorithm proposed in \cite{Jain}.
-The algorithm in \cite{Jain} works for a single CS where arrival time of all EVs are the same and there is no global peak constraint.
-Since the performance analysis of the proposed algorithm relies on a dual fitting method and utilizes weak duality property, \revv{we first need to construct the dual problem of \MCSP.
-Toward this, we introduce variables $\alpha, \beta, \gamma$ and $\pi$.
-Generally, in primal-dual approximation algorithm design, each constraint (resp.
-variable) in primal (resp.
-dual) problem is associated with a variable (resp.
-constraint) in dual (resp.
-primal) problem.
-In our case, constraints (\ref{ConstPartial}) (\ref{ConstTotal}), (\ref{ConstLocal}) and (\ref{ConstSpeed}) in the \MCSP are respectively associated with dual variables $\alpha, \beta, \gamma$ and $\pi$ (for more details see \cite{approx}).
-The dual problem is formulated as follows:}
-		\bse
-		\bee
-		\min &&\sum_{i=1}^n D_i\alpha _i + \sum_{j=1}^m \sum_{t=1}^T p_j\beta (t)+\sum_{t=1}^T p^\mathsf{total}\gamma (t)\nonumber\\ 
-		\textrm{s.t.} && \alpha _i+\beta (t) +\gamma _i + \pi (t)- \frac{k_i}{D_i}\sum_{t'=a_i}^{d_i} \pi _i(t^\prime) \geq \frac{v_{i}}{D_i},\label{ConstDcover} \nonumber\\
-		&& \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\forall i, t\in [a_i, d_i],\\
-		\textrm{vars.}&&\alpha _i, \beta _i, \gamma,  \pi _i(t)\geq 0,\quad\quad\forall i,t. \nonumber
-		\eee
-		\ese
-
-		%%%In this section, we explain \ics in details and then in Section~\ref{subsec:analysis}, we analyze approximation factor of the algorithm. The \ics algorithm is listed as Algorithm~1.
-
-		\subsubsection{Explanation of the Main Algorithm} 
-		\label{sec:icsexplanation}
-		Our algorithm design is inspired by the basic algorithm proposed in \cite{Jain}.
-\revv{The algorithm in~\cite{Jain}, however, works for a single CS where arrival time of all EVs are the same and there is no global peak constraint.}
-		The \ics algorithm (listed as Algorithm \ref{alg:ics}) works in two phases.
-In the first phase it sorts the charging requests based on their unit values in a non-increasing order.
-Then, it selects most valuable demand.
-If the remaining resource is enough to cover the \emph{entire} demand of the EV, it is admitted to receive the demand (Lines~$6$-$7$).
-%		When \ics processes EV $i$, the algorithm checks for the feasibility of allocating $D_i$ units of the resource within its availability window $[a_i,d_i]$ without violating the constraints related to the maximum charging rate $k_i$, local and global peaks (Lines~$6$-$8$).
-
-		\emph{Scheduling of the Selected EV:} \revv{If the feasibility check passed (Line 6 in Algorithm 3)}, \ics calls sub-procedure \sa\ to allocate required resources in interval $[a_i,d_i]$.
-Then, $\alpha _i$ is set to $v_i\slash D_i$ in order to cover dual constraint in Eq.~\eqref{ConstDcover} (Lines~$7$-$8$).
-
-		In \sa, 
-		%%%When EV $i$ is selected to get charged, \sa\ is called for the charging scheduling. 
-		let us define $W(t,h(i))=\sum_{i': h(i')=h(i)} y_{i'}^t$ as total workload at time slot $t$ in CS $h(i)$ and $\bar{W}(t,h(i))$ as total available load to allocate at time slot $t$ for CS $h(i)$.
-We always have ${\bar{W}(t,h(i))+W(t,h(i))=p_{h(i)},  \forall t, i}$.
-For scheduling, \sa\ applies two main policies: 1) \emph{valley-filling} and, 2) \emph{right-to-left allocation}.
-\revv{With valley-filling, the slots with more available resources are preferred which helps to reduce the peak of the system.} %%%It also can be seen as a smoothing method which tries to reduce the variance of the allocated resources at different slots.
-%				The simulation results in Section \ref{sec:simul} will confirm this claim. 
-				Right-to-left allocation is used when two or more time slots are equal in terms of their remaining resources. 
-%				When this policy applies on scheduling of EV~$i$, any EV~$i'$ with $i'>i$ and $d_{i'}<d_i$ has more chance to get charged since the algorithm tends to charge EV $i$ in interval $[d_{i'}+1,d_i]$ (i.e., right hand part of the EV's availability window) and keeps resources in $[a_{i'},d_{i'}]$ for EV $i'$.
-A ranking based approach is used to apply the aforementioned policies. 
-		To charge  EV $i$, \sa\ ranks time slots in interval $[a_i,d_i]$.
-Then, charging is done by allocating resources from the higher ranked time slot to lowest one.
-The rank of a time slot $t$ is calculated based on remaining resources in the time slot (valley-filling) and value of $t$ (right-to-left allocation).
-
-		\vspace{-3mm}
-		\begin{algorithm}%\small%1
-			\footnotesize
-			\caption{\ics}
-			\label{alg:ics}
-			\DontPrintSemicolon 
-%			\KwIn{$n$ EVs with $a_i, d_i, v_i, D_i,$ and $k_i$ associated with each EV $i$, $m$ CSs, local and global peak constraints $p_j, j=1,\dots ,m$, and $p^\mathsf{total}$}
-
-%			\KwOut{A feasible scheduling of EVs}
-			\BlankLine
-			%\begin{algorithmic}
-
-			%\slash\slash\textit{\texttt{Initialization}}
-			\textbf{initialize}: $y\leftarrow 0, \alpha\leftarrow 0, \beta\leftarrow 0, \gamma\leftarrow 0, \pi\leftarrow 0$
-
-			Sort charging requests in non-decreasing order of their unit values: $v_1/D_1 \geq v_2/D_2\geq\dots \geq v_n/D_n$
-%			$\frac{v_1}{D_1} \geq \frac{v_2}{D_2}\geq\dots \geq \frac{v_n}{D_n}$
-%			\slash\slash\textit{\texttt{Use sorted list to process demands}}
-
-			\For{(i=1\dots n)}{
-
-				\For{$t=a_i\dots d_i$}{
-					$\sigma_t\leftarrow  \min\Big\{p_{h(i)}-\sum_{i':h(i')=h(i)}y_{i'}(t),$ \newline $\qquad p^\mathsf{total}-\sum_{i'=1}^n y_{i'}^t,k_i\Big\}$
-
-				}
-
-%				\slash\slash\textit{\texttt{if enough resources remain for EV $i$}}
-
-				\If{$D_i\leq\sum_{t=a_i}^{d_i}\sigma_t$}
-				{
-					\sa($i,D_i$)\\
-					$\alpha _i\leftarrow v_i/ D_i$
-				}
-				\Else {
-					\If{$(\beta (d_i)=0)$}{
-						\bc($i$)}
-				}
-			}
-
-			\For{(i=1\dots n)}{ 
-				\If {EV $i$ is not selected}{
-					\rc($i$);
-				}
-			}
-			%\end{algorithmic}
-		\end{algorithm}
-
-\emph{Dual Feasibility of the Non-selected EVs:} If there is not enough resources to fully charge EV $i$, i.e.,  $D_i>\sum_{t=a_i}^{d_i}\sigma_t$, the EV cannot be selected.
-However, we still need to satisfy constraint~\eqref{ConstDcover} in dual problem which is done by calling \bc($i$).
-To cover the constraint~\eqref{ConstDcover} for EV $i$, sum of dual variables for all $t\in [a_i ,d_i]$ should be greater than or equal to ${v_i \slash D_i}$.
-\bc($i$) sets $\beta (t)$ to ${v_i \slash D_i}$ for all time slots $t$ in interval $[t_\mathsf{cov}, R(d_i)]$ (Lines $3$-$4$ of Algorithm~\ref{alg:betacover}).
-Observe that  ${\beta (t^\prime)\geq v_i \slash D_i,\forall t^\prime< t_\mathsf{cov}}$ (with $ t_\mathsf{cov}>1$) considering that the demands are sorted in a non-increasing order of the unit-values and $\beta (t')$ is already set to ${v_{i'} \slash D_{i'}}$ when processing the earlier charging demand of EV $i'$ which is not selected.
-Hence, ${v_{i'}\slash  D_{i'}\geq v_i \slash D_i}$, thereby ${\beta (t)\geq v_i \slash D_i,}$ and the dual constraint in~\eqref{ConstDcover} is satisfied.
-		Lines $1$-$4$ of \bc\ is enough to cover the dual constraint.
-However, the algorithm continues in Lines $5$-$8$ by setting a variable $\Phi_{i'}(t)$ for time slots $t=1,\dots ,R(d_i)$ to a value dependent to amount of the resource that a selected EV $i'$ received at slot $t$.
-$\Phi_{i'}(t)$ will be used in approximation analysis of the main algorithm and has no effect on the scheduling of EVs.
-		%We borrowed algorithm \bc($i$) from \cite{Jain} and adjusted it for multiple station mode.		
-		\vspace{-3mm}
-		\begin{algorithm}%\small%1
-			\footnotesize
-			\caption{\sa($i,D_i$)}
-			\label{SmartAllocate}
-			\DontPrintSemicolon 
-			\KwIn{EV $i$ to receive $D_i$ from CS $h(i)$}
-
-			Rank time slots in interval $[a_i,d_i]$ such that for any $t_1$ and $t_2$:
-			$\mathsf{rank}(t_1)> \mathsf{rank}(t_2)$ iff $\bar{W}(t_1,h(i))>\bar{W}(t_2,h(i))$ OR $\bar{W}(t_1,h(i))==\bar{W}(t_2,h(i)) \wedge t_1>t_2$
-
-			\While {$\sum_{t'=a_i}^{d_i}y_i^{t'}\neq D_i$}{
-
-				Select time slot $t$ with highest rank which is not selected before
-
-				Allocate $\min \left\{k_i,\bar{W}(t,h(i)),D_i-\sum_{\tau=a_i}^{t}y_i^{\tau},p^{\textrm{total}}-\sum_{i'}y_{i'}^t\right\}$ to EV $i$ at $t$
-
-			}
-		\end{algorithm}	
-		\vspace{-7mm}	
-		\begin{algorithm}%\small%1
-			\footnotesize
-			\caption{\bc($i$)}
-			\label{alg:betacover}
-			\DontPrintSemicolon 
-			%\KwIn{EV $i$ which is not selected to charge}
-
-			\BlankLine
-
-			$t_\mathsf{cov}\leftarrow \min \{t: \beta (t)=0\}$
-
-			$R(d_i)=\max \{t\geq d_i : \forall t^\prime\in (d_i,t], \bar{W}(t^\prime)<q_{h(i)} \}$
-
-			\For{$(t=t_\mathsf{cov}\dots R(d_i))$}{
-				$\beta (t)\leftarrow v_i/D_i$
-			}
-
-			\For{$(t=1\dots R(d_i))$}{
-				\For{$(i'=1\dots n))$}{	
-					\If{$y_{i'}^t>0 \wedge \Phi_{i'}(t)=0$}{
-						$\Phi_{i'}(t)\leftarrow\big[ \frac{p_{h(i)}}{p_{h(i)}- k_i}\frac{s}{s-1}\big] .\frac{v_i}	{D_i}y_{i'}^t$
-					}
-				}
-			}
-		\end{algorithm}
-		\vspace{-7mm}
-		\begin{algorithm}%\small%1
-			\footnotesize		
-			\caption{\rc($i$)}
-			\label{Replace}
-			\DontPrintSemicolon 
-%			\KwIn{EV $i$}
-%			\KwOut{Updated schedule}
-
-			$\mathcal{L} \leftarrow \emptyset$\\			
-			$v_\mathsf{inc}\leftarrow v_i$\\			
-			$\sigma_t\leftarrow 0, t=a_i,\dots ,d_i$
-
-			%Define $\delta_i(t)=\min \{k_i,\bar{W}(t,h(i))\}$
-
-			%$\Delta\leftarrow \sum_{t=a_i}^{d_i}\min\{\bar{W}(t,h(i)), k_i\}$
-
-			\For{($i' =i-1\dots 1$)}{ 
-				\If {EV $i'$ is selected $\wedge (h(i')=h(i)) \wedge (v_\mathsf{inc}-v_{i'})>0$}{
-					Add EV $i'$ to list $\mathcal{L}$
-
-					$v_\mathsf{inc}\leftarrow v_\mathsf{inc}-v_{i'}$
-
-					\For{($t=a_i\dots d_i$)}{
-						$\sigma _t\leftarrow\sigma_t + \min\{k_i,y_{i'}^t\}$
-					}
-				}
-			}
-
-			\If {$\sum_{t=a_i}^{d_i}\sigma_t\geq D_i$}{
-				Remove EVs in list $\mathcal{L}$ from charging schedule
-
-				\sa($i,D_i$)
-			}
-		\normalsize
-		\end{algorithm}
-
-		\emph{Improving the Gain:} In the second phase, the \ics tries to increase total value of selected EVs by calling \rc($i$) on every unselected EV $i$ (Lines~$12$-$14$).
-\rev{The \rc(i) (listed as Algorithm $6$) checks that whether the total revenue can be increased by replacing some selected EVs with EV $i$ or not (Lines $4$-$9$).
-If such EVs are found, the algorithm stops their charging and allocates EV $i$ using \sa\ (Lines $10-12$).}
-		%We refer to ~\cite{alinia2017online}, for the details and intuition behind this algorithm. 
-%		Before giving the details of \rc($i$), we first explain the intuition behind this algorithm. 
-%		 Note that if in the scheduling problem we set $T=1, m=1, k_i=p^\mathsf{total}, a_i=d_i=1\ \forall i$, then the problem is equal to the well-known $0$-$1$ knapsack problem~\cite{approx}.
-In the knapsack problem, a widely used greedy approach sorts items based on their unit values and selects items accordingly.
-It turns out that in this approach the approximation factor can be arbitrarily bad.
-For example, consider a knapsack problem with two items with $v_1=2, v_2=p^\mathsf{total}, D_1=1$, and  $D_2=p^\mathsf{total}$.
-Given these values we have $v_1\slash D_1>v_2\slash D_2$.
-To maximize total value of selected items, the optimal solution chooses item $2$ while greedy algorithm selects item $1$ which results in a worst-case approximation factor of ${c \slash \opt}$ in general where $c$ is a constant (in this example $c=2$).
-To resolve it, one approach is to \emph{re-consider} unselected items after running greedy algorithm and replace some selected items in the knapsack with unselected ones and then check whether the result is improved or not.
-In a simple case, only the largest unselected item can be examined which makes a significant theoretical improvement by providing a worst case approximation factor of $\opt\slash 2$.
-%		 
-%\ics algorithm leverages the same idea but using a more intelligent replacing method called \rc($i$).
-\rc($i$) is called on every unselected EV $i$.
-It tries to find some selected EVs that if they are replaced by EV $i$, total revenue from the selected EVs increases.
-%%%When \ics calls \rc($i$) on all unselected EVs, an improvement in total revenue of final selected EVs is expected.
-%This is confirmed by the simulation results in Section~\ref{sec:simul}.
-
-		\subsubsection{Analysis}
-		\label{subsec:analysis}
-		In primal-dual algorithm, the goal is to design an algorithm in a way that it produces a good solution for primal problem (with primal value $\Gamma$) and a feasible solution for the dual problem (with dual value $\Lambda$).
-Then, assuming that the primal problem is a maximization problem, to prove that the algorithm is $c-$approximation (for $c\geq 1$), the important part is to show that $\Lambda\leq c\Gamma$.
-Then, based on weak duality theorem we have $\Lambda\geq \opt$, and it is concluded that $\Gamma \geq \frac{1}{c}\times\opt$ where $\opt$ is the optimal value.
-		Based on the above understanding, the following theorem scrutinizes the approximation ratio of the \ics assuming that arrival times are the same for all EVs. 
-%		First note that the designed scheduling algorithm outputs a feasible scheduling since it respects the constraints in the primal problem.
-Also, the algorithm produces a feasible solution for the dual problem by covering the dual problem constraint in (\ref{ConstDcover}) through setting $\alpha _i$ to $\frac{v_i}{D_i}$ when EV $i$ is accepted and, $\beta (t)$ to a value greater than or equal to $\frac{v_i}{D_i}$ for $t\in [a_i, d_i]$ (according to the discussion in Section \ref{sec:icsexplanation}) if EV $i$ is not selected.
-To obtain an approximation factor for the algorithm, it is enough to bound the total covering cost of the dual constraints.
-
-		\begin{thm}
-			\label{thm:approx}
-			\ics algorithm is a $\Big( 1+ \sum_{j=1}^m {\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}\Big)$-approximation when EVs have same arrival time.
-		\end{thm}
-%		
-%		\begin{proof}
-%			In Appendix~\ref{app:1}.
-%		\end{proof}
-
-		Note that in the case that the system is flexible enough, i.e., $s\gg 1$, and the maximum charging rates of stations are much bigger than those of EVs, i.e., $p_j \gg q_j, \forall j$, the approximation ratio approaches $m+1$.
-And in the case that there is one single station, the approximation ratio is $2$.
-%		 Finally, we provide the time complexity of the \ics.
-
-%\begin{thm}
-%\label{thm:ics_complexity}
-%The time complexity of the \ics algorithm is $O(nT\log T+n^2T)$.
-%\end{thm}	
-%
-%\begin{proof}
-%In Appendix \ref{app:ics_complexity}.
-%\end{proof}
-
-\subsection{Online Scenario}
-\label{sec:onlineint}
-Due to the binary selection variable, the online solution design under integral model is more challenging than the one for fractional model.
-We propose the \iocs that is built upon the offline \ics.
-In particular, the \iocs calls the \ics at each time slot for the set of available EVs, however, any algorithm that is designed for offline integral model can be used alternatively.
-Hereinafter, $\mathcal{A}$ refers to the \ics or a similar algorithm.
-
-\vspace{-4mm}
-\begin{algorithm}%\small%1
-\footnotesize
-\caption{\iocs: $\forall t\in \{1,2,\dots ,T\}$}
-\label{alg:iocs}
-\DontPrintSemicolon 
-%\KwIn{$n$ EVs to arrive on the fly, number of CSs $m$, global peak constraint $p^{\textrm{total}}$, local peak constraints $p_j, j=1,\dots ,m$}
-
-%\KwOut{A feasible charging scheduling}
-
-\BlankLine
-
-Let $\mathcal{A}$ be an algorithm that solves the problem with $a_1=\dots =a_n$
-
-$\mathcal{R}^t\leftarrow$ set of EVs arrived at time slot $t$
-
-$\mathcal{M}^t\leftarrow \mathcal{R}^t\cup \{i: t\in\mathcal{T}_i\ \texttt{AND}\ \sum_{t^\prime}y_{i}^{t'}<D_i\}$
-
-%$\backslash\backslash\texttt{Schedule 1}$
-
-Based on the residual in interval $[t,T]$, use algorithm $\mathcal{A}$ to allocate EVs in set $\mathcal{R}^t$ assuming no further arrivals
-
-$\mathcal{S}_{\iocs,t}\leftarrow\{i:i\in\mathcal{M}^t\ \texttt{AND}\ i$ is admitted at $t\}$
-
-$\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}\leftarrow \sum_{i\in\mathcal{S}_{\iocs,t}}v_i$
-
-Assume all reserved resources are freed at time slots $t, t+1, \dots, T$
-
-%$\mathcal{R}^t\leftarrow\mathcal{M}^t$
-
-%$\backslash\backslash\textsl{set of active EVs at time slot t}$
-
-$r_{i,t}\leftarrow$ remaining demand of $i$ at $t, \forall i$
-
-%$\backslash\backslash\texttt{Use modified demands values}$
-
-$D_i^\prime\leftarrow r_{i,t},\ \ v_i^\prime\leftarrow \frac{r_{i,t}}{D_i}v_i, \forall i\in\mathcal{M}^t$
-
-%$\backslash\backslash\texttt{Schedule 2}$
-
-Run $\mathcal{A}$ on $\mathcal{M}^t$ using $D_i^\prime$ and $v_i^\prime, \forall i$ and reconstruct $\mathcal{S}_{\iocs,t}$
-
-$\Gamma_{\mathcal{A},\mathcal{M}^t}\leftarrow \sum_{i\in\mathcal{S}_{\iocs,t}}v_i$ $\backslash\backslash\texttt{Use original values}$
-
-%$a\leftarrow\frac{V^\prime_{\textrm{total}}}{V_{\textrm{total}}}$
-
-\If{$\Gamma_{\mathcal{A},\mathcal{M}^t}>\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$}{
-
-Use the second schedule
-
-}
-
-\Else{
-
-Use the first schedule
-
-}
-
-\end{algorithm}
-
-The \iocs is summarized as Algorithm~\ref{alg:iocs}.
-At slot $t$, the \iocs compares two scheduling results returned by $\mathcal{A}$ and chooses among them.
-In the first scheduling, the \iocs keeps all reserved resources in interval $[t,T]$ intact.
-Then, for utilizing the remaining resources, the algorithm runs $\mathcal{A}$ over arrived EVs at time slot $t$.
-In this case, the total revenue obtained by the \emph{active} EVs (i.e., EVs that are available but not received their entire demand yet) is denoted by $\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$ (Line $6$ of the algorithm).
-In the second scheduling, the \iocs considers the case that it can sacrifice the previously admitted EVs by canceling their reservations and allocating the freed resources to more valuable demands.
-For this purpose, the algorithm modifies the demand and valuation of the previously admitted EVs such that each demand is replaced by the EV's remaining demand, and the valuation of the EV is proportionally calculated based on the remaining demand (Line $9$ of the algorithm) so that the unit values of EVs do not change.
-Then, the \iocs runs $\mathcal{A}$ over set of active EVs $\mathcal{M}^t$ where the corresponding gain is denoted by $\Gamma_{\mathcal{A},\mathcal{M}^t}$.
-If $\Gamma_{\mathcal{A},\mathcal{M}^t}>\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$, the \iocs forgets the previously admitted EVs and follows the second scheduling.
-
-\begin{comment}
-%We now introduce some notations and then analyze the performance of \iocs. 
-Let $\mathcal{S}_{\iocs,t}$ and $\mathcal{S}_{\opt,t}$ be set of active EVs at time slot $t$ that are selected for charging by \iocs and \opt (fix a particular optimal solution), respectively.
-Note that the set of active EVs for \iocs and \opt might be different.
-%Moreover, define  $\mathcal{U}_{\iocs,t}=\mathcal{S}_{\iocs,1}\cup\dots\cup \mathcal{S}_{\iocs,t}$ and $\mathcal{U}_{\opt,t}=\mathcal{S}_{\opt,1}\cup\dots\cup \mathcal{S}_{\opt,t}$. 
-Having $i\in\mathcal{S}_{\iocs,t}$ means that based on the updated schedule at time slot $t$, enough resources reserved for EV $i$ so that the EV will receive its demand $D_i$ before the deadline $d_i$.
-However, the schedule may change at each slot and $i\in\mathcal{S}_{\iocs,t}$ cannot be a guarantee for EV $i$ to fully receive its demand.
-In fact, users and the scheduler itself have to wait until the deadline of the EV to find out that the demand is fulfilled or not.
-This is because the scheduler may cancel some reservations in the next time slots and allocate the freed resources to other EVs.
-\end{comment}
-% (when Algorithm \ref{alg:iocs} uses the second schedule in Line $15$). 
-%Define $A_t$ as the minimum gain of \iocs when the algorithm visited time slots $1$ to $t$.
-More formally, $A_t=\sum_{i\in\mathcal{U}_{\iocs,t}}v_i$.
-$A_t$ is the minimum gain that \iocs will obtain by the end of time slot $t$, having the information of released demands up to time slot $t$.
-Notice that the algorithm may continuously improve its set of selected jobs to increase its gain such that $A_t\geq A_{t-1}, t\in\{2,\dots, T\}$.
-$A_t$ is formally defined as follows:
-
-The following theorem characterizes the competitive ratio of the \iocs in a special case. 
-\begin{thm}
-\label{thm:iocscompetitive}
-Let $\mathcal{A}$ be \ics in \iocs algorithm and $m=1$.
-Assuming that EVs are released in $b$ distinct groups where arrival time of EVs in each group are the same, the \iocs is $b\Big(1+\frac{p}{p-q}\frac{s}{s-1}\Big)$-competitive with optimal offline solution, where $p$ is the station peak and $q=\max_i k_i, i=1,\dots ,n$.
-\end{thm}
-
-%\begin{thm}
-%\label{thm:iocscomplexity}
-%Let $\mathcal{A}$ be \ics in Line $1$ of \iocs. Then, the time complexity of the \iocs  is $O(n^2T)$. 
-%\end{thm}
-
-\vspace{-6mm}
-\section{Simulation Results}
-			\label{sec:simul}
-%%%In this section, we report a summary of simulation experiments to evaluate the performance of the proposed algorithms.
-
-						\begin{figure*}[t]	
-				\centering
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{V-N-M2.pdf}
-						\caption{\revv{$m=2$}}
-						\label{fig:V-N-M2}
-					\end{center}
-				\end{subfigure}
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{V-N-M4.pdf}
-						\caption{\revv{$m=4$}}
-						\label{fig:V-N-M4}
-					\end{center}
-				\end{subfigure}% 	
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{V-N-M8.pdf}
-						\caption{\revv{$m=8$}}
-						\label{fig:V-N-M8}
-					\end{center}
-				\end{subfigure}% 
-				\caption{\revv{Comparison results for $2$, $4$, and $8$ CSs for fractional and integral revenue models.}} 
-				\label{fig:V-N-M}
-				\vspace{-3mm}
-			\end{figure*}
-%\subsection{Simulation Setup and Overview}
-\textit{Simulation Setup and Overview:} We consider charging scheduling of EVs \revv{during a period of $12$ time slots of length $1$ hour (e.g., from $08$:$00$ to $20$:$00$)}. 
-We gathered information of \revv{$12$} popular EV models in the market to use in the simulation.
-Each EV model is characterized by its battery capacity as shown in Table \ref{tb:models} and maximum charging rate.
-\revv{Tesla models can get charged with up to $100$ kW using Tesla super chargers.
-Also, all other models have rapid DC charging capability (up to $50$ kW) with CHAdeMO method.
-This setting for charging rates is in accordance with future DCFC systems that can have several fast DC chargers installed in the charging station.}
-%Battery capacity varies from \revv{$14$} kWh to \revv{$100$} kWh and the maximum charging rate from \revv{$3.3$} kW to \revv{$22$} kW. 
-%As in \cite{Tang,Chen}, we assume that arrival times follow a Poisson distribution and parking times follow an exponential distribution.
-% with the mean arrival and parking duration indicated in Table \ref{tb:a-d}. 
-The peak intervals include $08$:$00$-$10$:$00$, $12$:$00$-$14$:$00$, and $18$:$00$-$20$:$00$ which is in accordance to NHTS survey~\cite{Santos, Tang}.
-\revv{The probability of arriving an EV in the peak hours is two times higher than the off-peak periods.
-			Demands are uniform random values from 
-			$[\frac{1}{2}U_i,U_i]$} where $U_i$ is the battery capacity for EV $i$ in Table~\ref{tb:models}.
-\revv{The deadline of each EV is set according to slackness parameter $s$ (with default value of $1.2$), its demand and maximum charging rate of the battery as $d_i=a_i+\lceil \frac{D_is}{k_i} \rceil -1$.}
-%			The minimum electricity cost is $\$0.11$ per kWh based on US national electricity price average~\cite{kWhcost}.
-In our setting, users can submit higher prices than the minimum price in order to ensure receive their requested demand.
-			\revv{EVs are assigned to different CSs randomly and given as input to the algorithms.
-The willingness to pay by each user for one kWh of power is a random uniform number from interval $[\frac{1}{2} z,\frac{3}{2}z]$ where $z=\$0.11$ is national average price of electricity in the US\cite{kWhcost}.}
-			%The default value of local peak constraint is \rev{$100$} kW and the global peak constraint is \rev{$200$} kW. We investigate the effect of this parameter in~\cite{alinia2017online}. 
-			In the simulation, the results are plotted with $95\%$ confidence level and each point represents average result of $50$ random scenarios.
-Table \ref{tb:comparisons} explains the comparison algorithms \revv{including current implemented algorithm in Caltech ACN referred to as \iolp \cite{lee2016adaptive} and its adapted version for the fractional revenue model \folp.
-The \iolp and \folp algorithms runs as follows: at each time slot assume that there will be no further arrivals and solve the optimization problem (e.g., by commercial solvers) for the current set of EVs and their remaining demands.
-In Table \ref{tb:comparisons}, the letters ``\textsc{i}'', ``\textsc{f}'' and ``\textsc{o}'' in front of the algorithms' name refer to integral, fractional and online types, respectively.}
-
-			The measured performance metrics are total revenue, percentage of EVs that received all their demand, and total peak.
-\revv{To calculate optimal solution in integral revenue model, we used Gurobi solver \cite{optimization2013gurobi}.}
-
-\begin{table}[!t]
-				\centering
-				\caption{\revv{EV models and their battery capacity.}}
-				\label{tb:models}\revv{
-				\begin{tabular}{ | l| c | l| c |}
-					\hline
-					\textbf{Model} & \textbf{Battery} & \textbf{Model} & \textbf{Battery} \\ \hline\hline    
-				Mitsubishi i-MiEV & $16$ kWh & Citroen C-Zero & $14$ kWh \\ \hline
-				Peugeot iOn  & $16$ kWh & Honda Clarity & $25.5$ kWh\\\hline
-				Hyundai Kona & $64$ kWh & Nissan LEAF & $40$ kWh \\ \hline
-				Hyundai Ioniq & $28$ kWh & BMW i3 & $22/33$ kWh \\ \hline
-				Tesla Model S/X  & $60/100$ kWh & Kia Soul EV  & $27$ kWh\\\hline
-				\end{tabular}}
-			\end{table}
-
-%\begin{table}[h]
-%				\centering
-%				\caption{Arrival rates and mean parking times.}
-%				\label{tb:a-d}
-%				\begin{tabular}{ | l | c | c |}
-%					\hline
-%					\textbf{Interval} & \textbf{Arrival rate} & \textbf{Mean parking time} \\ \hline\hline    
-%					$08$:$00$-$10$:$00$&  $14$&$10$\\\hline  
-%					$10$:$00$-$12$:$00$&  $10$&$1/2$\\\hline 
-%					$12$:$00$-$14$:$00$&  $20$&$2$\\\hline 
-%					$14$:$00$-$18$:$00$&  $10$&$1/2$\\\hline
-%					$18$:$00$-$20$:$00$&  $20$&$2$\\\hline
-%					$20$:$00$-$24$:$00$&  $10$&$10$\\\hline
-%					$24$:$00$-$08$:$00$&  $0$&$0$\\\hline
-%				\end{tabular}
-%\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{Acronyms for the algorithms}
-\label{tb:comparisons}
-\begin{tabular}{ | l| p{6cm}|}
-\hline
-\textbf{Notation} & \textbf{Description} \\ \hline\hline
-\textsc{iOpt} & Optimal value under integral revenue model\\ \hline 	 
-\ics & Proposed offline algorithm for \MCSP under integral revenue model\\ \hline
-\fcs & Proposed \emph{optimal} algorithm for \MCSP under fractional revenue model\\\hline 
-\iocs & Proposed online algorithm for \MCSP under integral revenue model\\ \hline
-\focs & Proposed online algorithm for \MCSP under fractional revenue model\\ \hline
-\iolp & Algorithm in \cite{lee2016adaptive} (works under integral revenue model)\\ \hline
-\folp & Adaptation of algorithm in \cite{lee2016adaptive} for fractional revenue model\\ \hline
-GreedyRTL & The algorithm in \cite{Jain} for single station scenario without global peak 			constraint (works under integral revenue model)\\\hline				
-\end{tabular}
-\end{table}
-			%to simulate: Fig. 1 with M=1,4,8			
-			\begin{figure*}[t!]	
-				\centering
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{v-c.pdf}
-						\caption{\revv{Total revenue}}
-						\label{fig:v-c}
-					\end{center}
-				\end{subfigure}%
-				%\hspace{4mm}
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{p-c.pdf}
-						\caption{\revv{Actual global peak} 
-%							($p^{\mathsf{total}}=480$)
-}
-						\label{fig:p-c}
-					\end{center}
-				\end{subfigure}%  
-				%\hspace{4mm}
-				\begin{subfigure}[b]{0.25\textwidth}
-					\begin{center}
-						\includegraphics[width=\textwidth]{acc-c.pdf}
-						\caption{\revv{\% of full charged EVs}}
-						\label{fig:acc-c}
-					\end{center}
-				\end{subfigure}% 				
-				\caption{\revv{Comparison in terms of total revenue, actual peak, and percentage of fully charged EVs by varying local peak value}.} 
-				\label{fig:peak_local}
-			\vspace{-4mm}
-			\end{figure*}
-\textit{\revv{Evaluation Based on Total Revenue}:}
-\revv{Fig.
-\ref{fig:V-N-M} depicts the comparison results based on total revenue under fractional and integral models} while the total number of EVs increases from \revv{$100$ to $250$} for $2$, $4$, and $8$ CSs.
-\revv{The local and global peak constraints are set to $50$ kWh and $200$ kWh, respectively.}
-
-The proposed algorithms compared to the optimal offline solution of integral model ($\textsc{iOPT}$) and $\iolp$.%%% which is the running online algorithm in the Caltech ACN \cite{lee2016adaptive}. 
-%The proposed algorithms for fractional revenue model, \fcs and \focs, are compared to fractional version of OLP algorithm (referred to as \folp), which is implemented in Caltech ACN  (see~\cite{alinia2017online} for details).
-Recall that \fcs is optimal offline solution.
-The notable observations  are  as  follows:  (i)  the  general  trend in scenario of Fig.~\ref{fig:V-N-M} is that  by increasing  the  number  of  EVs,  total  revenue  increases.
-This is because with more number of EVs, the scheduler has more freedom to choose more valuable EVs.
-(ii)  as  explained in Section~\ref{sec:fractional}, under fractional charging model, better results are expected due to increased scheduling flexibility in CSs.
-According to the simulation data that we extracted from Fig.~\ref{fig:V-N-M}, the gain obtained by \fcs and \focs in Fig.
-\ref{fig:V-N-M} are respectively \revv{$12\%$ and $10\%$} more than the gain of the \ics and \iocs.
-(iii) \revv{In Fig.
-\ref{fig:V-N-M2} and Fig.
-\ref{fig:V-N-M4}, sum of the local peaks is less than or equal to the global peak while in Fig.
-\ref{fig:V-N-M8} this sum is two times greater than the global peak.
-Consequently, the total revenue significantly improved when the number of CSs is increased from $2$ to $4$ while there is a slight improvement from $4$ to $8$ CSs as the global peak constraint prevents the algorithms from charging more EVs.}
- (iv) in integral revenue model, the proposed \iocs algorithm acts significantly better than \iolp.
-In particular, \iocs improves \iolp by \revv{$38\%, 36\%$, and $32\%$} for $m=2$, $m=4$ and $m=8$, respectively.
-\revv{In fractional revenue model, however, there is a very slight difference between \focs and \folp.}
- %We highlight that \iocs (\focs) is also better choice in terms of the algorithm complexity compared to \iolp (\folp).
-(v) \ics approximates \textsc{iOpt} by \revv{$97\%$, $94\%$, and $95\%$} for $m=2$, $m=4$, and $m=8$, respectively.
-On average, \iocs is \revv{$90\%$} of \textsc{iOpt} and, \focs is \revv{$94\%$} of its optimal offline solution, \fcs.
-(vi) finally, the results depict that \ics achieves much better results in practice as compared to the theoretical approximation ratio that characterizes the performance in worst-case scenario.
-
-%Also, there is a sharp decline in the gap between the online methods (i.e., \focs and \iocs) and the offline solutions (i.e., \textsc{iOpt}, \ics and \fcs).
-
-\revv{\emph{Comparison Based on Actual Peak:}} The constraint set in the \MCSP assures that any feasible solution respects the local and global peak constraints.
-% i.e., at each time slot, the electricity consumed by station $j$ is less than or equal to $p_j$ and accumulative charging rate of all stations are less than or equal to $p^\mathsf{total}$ (note that there is no assumption that $\sum_j p_j\leq p^\mathsf{total}$, in general).
-An efficient scheduling algorithm may take a further step by not only satisfying the peak constraints but to further reduce the peak as much as possible.
-The proposed offline algorithms (i.e., \ics and \fcs) apply valley-filling policy to reduce the peak.
-The  online algorithms (i.e., \iocs and \focs) do not apply the same policy as they do not have future knowledge to be able to balance allocated resources.
-%Besides, due to uncertainties in future EV charging load in online scheduling design, it is a natural heuristic to charge EVs at earliest time.
-% (i.e., setting the charging rates to the maximum feasible value at each time slot) as applied by \iocs an \focs. 
-%This heuristic works well as the uncertainty in EVs' arrival time and demands may not give a second opportunity to the scheduler to charge the current EVs at the next slots.
-Therefore, although it is expected that \iocs and \focs have higher peak values compared to the offline algorithms, the idea of valley-filling can decrease their average response time.
-% (see~\cite{alinia2017online} for the extended version of experiments).
-To investigate the effect of employed valley-filling strategy, we conducted a set of simulations by varying local peak constraints. 
-%from $50$ kWh to $120$ kWh and $200$ EVs. 
-The results of \ics is compared to \iocs and GreedyRTL~\cite{Jain} where the latter is an approximation scheduling for single station scenario with EVs having same arrival time (see the explanations after formulating the \MCSP in Section \ref{sec:problem}).
-%The GreedyRTL algorithm works under integral revenue model. Therefore, results for \fcs and \focs are not plotted. 
-%Since GreedyRTL assumes all EVs arrive at the same time, we set all arrival times to $1$.
-Moreover, we assume that global peak constraint is big enough (i.e., $\sum_{j=1}^m p_j\leq p^\textsf{total}$) such that the solution of GreedyRTL is feasible.
-We run GreedyRTL in each CS separately and combine the results.
-The results are shown in Fig.~\ref{fig:peak_local}.  
-Along with total revenue in Fig.~\ref{fig:v-c}, we also report total \emph{actual} peak in Fig.~\ref{fig:p-c} and percentage of fully charged EVs in Fig.~\ref{fig:acc-c}. 
-%As a high level trend, the results show that as the peak values increase, total revenue, total actual peak, and the number of EVs who received all their demand increase.  
-In Fig.
-\ref{fig:v-c}, the results for \ics and GreedyRTL are almost identical while \iocs is \revv{$90\%$} of the other two algorithms, on average.
-When \revv{$p_j\geq 400$}, the total revenue for \ics and GreedyRTL does not increase in Fig.
-\ref{fig:v-c} and percentage of fully charged EVs is $100$ for both algorithms according to Fig.
-\ref{fig:acc-c}.
-From this point and onward, the scheduling is not challenging for offline methods to obtain optimal answer because of resource sufficiency.
-However, it is still a challenge to control total actual peak for the system.
-As a result of valley-filling policy, the value of actual peak of \ics in Fig.
-\ref{fig:p-c} remains almost unchanged for \revv{$p_{j}\geq 400$}.
-\iocs and GreedyRTL, however, continuously increase the peak demand, since they are not using any peak shaving approach.
-% and only try to maximize total revenue. 
-%According to Fig. \ref{fig:p-c}, \iocs always reaches to the maximum peak of $\sum_j p_j$.
-
-%A glance at Table \ref{tb:models} shows that in general, an EV needs a minimum time of $2$ hours to get $70\%$ of its battery capacity if charging rate is set to the maximum value.
-However, CSs are allowed to preempt the charging at any time and set charging rate any value lower than the maximum rate.
-Therefore, average response times can be higher as it can be seen in Fig.
-\ref{fig:rt-c}.
-
-%\begin{figure}[t]	
-%\centering
-%				\begin{subfigure}[b]{0.25\textwidth}
-%					\begin{center}
-%						\includegraphics[width=\textwidth]{v-s-method1.pdf}
-%						\caption{Total revenue (\$)}
-%						\label{fig:v-s-method1}
-%					\end{center}
-%				\end{subfigure}%				
-%				\begin{subfigure}[b]{0.25\textwidth}
-%					\begin{center}
-%						\includegraphics[width=\textwidth]{rt-s-method1.pdf}
-%						\caption{Response time (hr))}
-%						\label{fig:rt-s-method1}
-%					\end{center}
-%				\end{subfigure}%  
-%\caption{The impact of slackness parameter on total revenue and response time when users react by adjusting their demand.} 
-%\label{fig:slackness1}
-%\end{figure}
-
-%\subsection{The Impact of Slackness Parameter}
-%\label{sec:sim:slack}
-%This section discusses on the benefits and disadvantages that can be brought by using slackness parameter.
-To give the charging scheduler more flexibility, a slackness parameter $s\geq 1$ is used and set by the system designer.
-%Recall that charging profile of EV $i$ is feasible if $D_i\leq k_i\frac{d_i-a_i+1}{s}$ holds.
-Since users have no control on the slackness parameter and the maximum charging rate, they must adjust their demand and availability according to the imposed slackness value.
-Based on the charging profile feasibility equation, when the slackness value increases users have two choices to react: (i) decrease the demand and depart at the desired deadline or, (ii) extend the deadline and receive the desired demand.
-In the remaining of this section, we investigate the effects of either case by simulation.
-To have a clear picture of effects caused by slackness parameter, we generated $100$ initial charging profiles $\langle a_i,d_i,v_i,D_i,k_i\rangle$ for $100$ EVs randomly and uniformly chosen from $10$ different models in Table \ref{tb:models} such that the initial profiles are set up assuming that the CS allows the charging operations to be finished at earliest possible time (i.e., $\frac{D_i}{k_i}$) with $s=1$.
-For each EV, its demand is randomly chosen from $25\%$ to $100\%$ of its battery capacity and departure in  interval $[a_i+\frac{sD_i}{k_i},T]$, where $a_i+\frac{sD_i}{k_i}$ is the earliest feasible deadline.
-Then, the EVs are uniformly assigned to $4$ CSs and should choose one of the above strategies to submit a feasible demand according to imposed slackness.
-%\begin{figure}[t]	
-%\centering
-%							\begin{subfigure}[b]{0.234\textwidth}
-%								\begin{center}
-%									\includegraphics[width=\textwidth]{v-s-method2.pdf}
-%									\caption{Total revenue (\$)}
-%									\label{fig:v-s-method2}
-%								\end{center}
-%							\end{subfigure}%
-%							\hspace{1mm}
-%							\begin{subfigure}[b]{0.236\textwidth}
-%								\begin{center}
-%									\includegraphics[width=\textwidth]{rt-s-method2.pdf}
-%									\caption{Response time (hr)}
-%									\label{fig:rt-s-method2}
-%								\end{center}
-%							\end{subfigure}% 
-%							
-%\caption{The impact of slackness parameter on total revenue and response time when users react by adjusting their deadline.} 
-%\label{fig:slackness2}
-%\end{figure}
-%			
-%\subsubsection{Case I- Adjusting Demands}
-%In this case, if the initial charging profile of an EV does not reflect a feasible charging request based on the slackness parameter, the EV owner decreases its demand so it will be able to leave CS at its initial desired deadline.
-Note that the valuation of EVs decreases proportionally, as well.
-Fig.~\ref{fig:slackness1} depicts the result under this policy applied by users.
-As it can be seen in Fig.
-\ref{fig:v-s-method1} and Fig.
-\ref{fig:rt-s-method1}, the general trend is that both total revenue and average response time decrease when slackness value increases.
-This is justifiable based on users reaction.
-When users decrease their demand, less electricity is sold which results in less revenue.
-When total demand decreases, charging can be finished in shorter time which decreases response time.
-Therefore, if users choose the first policy (adjusting their demand), total revenue degrades while response time improves.
-Notice that for the algorithms working under integral revenue model (i.e., \textsc{iOPT}, \ics and \iocs) the total revenue increases with slackness parameter at first (when $s$ grows from $1$ to $1.4$) but then it decreases when the slackness increases more (for $s>1.4$).
-%In our view, this happens because increasing the slackness in integral revenue model makes it possible to \emph{fully} charge more EVs at the beginning as the demands decrease.
-However, when the slackness increases more, it results in opposite effect because the valuation of demands decreases along with the demands' size.
-%			\subsubsection{Case II- Adjusting Deadlines}
-%			In this case, we assume that users are reluctant to decrease their desired demands.
-Instead, they can extend their departure.
-In Fig.~\ref{fig:slackness2} it can be observed that under this behavior of the users, the results are opposite as compared to the previous case (Fig.~\ref{fig:slackness1}).
-When deadlines are extended without demand decrement, the scheduler has more chance to compliance the demands through improved scheduling flexibility.
-Consequently, the total revenue increases by increasing slackness value while average response time degrades.
-%%Also observe the behavior of the online algorithms (i.e., \iocs and \focs) where both total revenue and response time decrease after a specific point that is $s=1.8$.
-When deadlines extend, more EVs have the opportunity of getting charged
-%					
-%We can conclude that when total revenue is more important than the response time, the CS should impose small values of slackness for users that apply the policy of the first case and impose higher values of slackness for the users that apply the second policy.
-The conclusion is reverse for the case that the objective is to have lower response times.
-
-			%In fact, the slackness parameter controls the maximum demand or earliest deadline that an EV can submit to the system.
-Remember that demands are in interval $[\textrm{min}\{\frac{d_i-a_i}{sk_i},U_i\},U_i]$ for EV $i$ meaning that the maximum demand that an EV can submit decreases by increasing slackness parameter.
-A reduction in total demand result in lower charging costs.
-Therefore, the total revenue decreases with higher values of parameter $s$ as in Fig.
-\ref{fig:v-s}.
-			%Also, the percentage of EVs that received all of their requested demand increases based on the same fact.
-The main goal of this simulation is to observe that obtained theoretical result on approximation ratio is confirmed as optimality gap of the SCS algorithm reduces by increasing $s$ in Fig.
-\ref{fig:v-s}.
-\vspace{0.1mm}
-\vspace{-4mm}
-			\section{Conclusion}
-			\label{sec:conclusion}
-This paper proposed offline and online algorithms for the EV charging scheduling problem under fractional and integral revenue models in an adaptive charging network (ACN).
-The problem is different, and more challenging than the existing single station EV charging scheduling problems since it requires respecting the aggregate peak charging demand of the ACN.
-%More importantly, the problem is online in nature in the sense that the EVs arrive in time and the scheduler has no information regarding future arrivals. 
-As the notable contributions, our proposed online algorithm for fractional revenue model achieves constant competitive ratio of $2$.
-Moreover, the offline integral algorithm achieves a theoretical bound on the optimality gap and approximates the optimum by $92\%$, on average in experiments.
-As a future work, we plan to study the problem under posted pricing mechanism where the charging station publishes the unit price of the power (which can be varied over time) and the users can accept or reject the offer.
-\revv{Another interesting future direction is to tackle the EV charging scheduling in market-based scenarios where the prices change over time.}
-%As a future work, we plan to analyze the truthfulness of the algorithms to make sure that it is a dominant strategy for the EV owners to declare their true valuations and availabilities.
-\vspace{-4mm}
-
-%\input{intro.tex}
-%\input{rel.tex}
-%\input{sys.tex}		
-%\input{fraction.sol.tex}		
-%\input{integral.sol.tex}
-%\input{exp.tex}
-%%%\vspace{0.1mm}
-%\input{conc.tex}
-%\newpage
-%ss
-%\newpage
-%\pagestyle{empty}
-\bibliography{ref}{}
-\vspace{-2.8mm}
-\bibliographystyle{ieeetr}
-
-\input{app.tex}
-
-\begin{comment}
-\vspace{-10mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{alinia.jpg}}]{Bahram Alinia} received a B.Sc degree in computer science from University of Tabriz, Tabriz, Iran and a masters degree in Information Technology Engineering from University of Tehran, Tehran, Iran.
-He was a Researcher with the School of Computer Science, Institute for Research in Fundamental Sciences, Iran, from 2009 to 2012.
-He is currently a Ph.D.
-student in service architecture lab, Institute Telecom SudParis, France and participated in several European projects in the domain of smart grids.
-His research area includes wireless communications, energy systems, transportation electrification, algorithm design and approximation.
-\end{IEEEbiography}
-%\vspace{-30mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{hajiesmaili.jpg}}]{Mohammad H.
-Hajiesmaili} received the B.Sc.
-degree from the Department of Computer Engineering, Sharif University of Technology, Iran, in 2007, and the M.Sc.
-and Ph.D.
-degrees from the Electrical and Computer Engineering Department, University of Tehran, Iran, in 2009 and 2014, respectively.
-He was a Post-Doctoral Fellow with the Department of Information Engineering, the Chinese University of Hong Kong, from 2014 to 2016, and with the Department of Electrical and Computer Engineering, Johns Hopkins University, form 2017 to 2018.
-He is currently a Research Assistant Professor with the College of Information and Computer Sciences, University of Massachusetts, Amherst.
-His research interests include optimization, algorithm, and mechanism design in energy systems, electricity market, transportation networks, and multimedia networks.
-\end{IEEEbiography}
-%\vspace{-30mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{crespi.jpg}}]{Prof.
-No\"{e}l Crespi} holds Masters degrees from the Universities of Orsay (Paris 11) and Kent (UK), a diplome d'ing\'{e}nieur from Telecom ParisTech, a Ph.D and an Habilitation from UPMC (Paris-Sorbonne University).
-From 1993 he worked at CLIP, Bouygues Telecom and then at Orange Labs in 1995.
-He took leading roles in the creation of new services with the successful conception and launch of Orange prepaid service, and in standardisation (from rapporteurship of IN standard to coordination of all mobile standards activities for Orange).
-In 1999, he joined Nortel Networks as telephony program manager, architecting core network products for EMEA region.
-He joined Institut Mines-Telecom in 2002 and is currently professor and Program Director, leading the Service Architecture Lab.
-He coordinates the standardisation activities for Institut Mines-Telecom at ITU-T and ETSI.
-He is also an adjunct professor at KAIST (South Korea), an affiliate professor at Concordia University (Canada), and gest researcher at the University of Goettingen (Germany).
-He is the scientific director the French-Korean laboratory ILLUMINE.
-His current research interests are in Data Analytics, Internet of Things and Softwarisation.
-http://noelcrespi.wp.tem-tsp.eu/
-\end{IEEEbiography}	
-\end{comment}
-\end{document}

### 2025-03-09 ev-scheduling-cpp/CS.cpp
organize

@@ -1,0 +1,249 @@
+#include "pch.h"
+#include "CS.h"
+#include <cmath>
+#include <algorithm>
+#include <numeric>
+#include <iostream>
+#include <ctime>
+
+
+
+
+CS::CS(int e, int p, std::list<EV> evList) : n{ static_cast<int>(evList.size()) }, evList{ evList }, evCapacity{ e }, pwCapacity{ p }, Y(evList.size(), std::vector<double>(TL, 0))
+{
+	if (e <= 0 || p <= 0)
+	{
+		throw std::string{ "bad object" };
+	}
+}
+
+CS::CS(int e, int p, int n) : n{ n }, evCapacity { e }, pwCapacity{ p }, Y(n, std::vector<double>(TL, 0))
+{
+	if (e <= 0 || p <= 0)
+	{
+		throw std::string{ "bad object" };
+	}
+
+	evList = evGenerator(n);
+}
+
+std::list<std::list<EV>> CS::convertEvListToMatrix(const std::list<EV>& allEvs)
+{
+	std::list<std::list<EV>> allEvsMatrix_(TL);
+	
+	for (const auto& ev : allEvs)
+	{
+		auto it = allEvsMatrix_.begin();
+		std::advance(it, ev.arrival);
+		(*it).insert((*it).end(), ev);
+	}
+	return allEvsMatrix_;
+}
+
+void CS::WFAIR(slot t)
+{
+	//std::cout << "==============Time slot " << t << std::endl;
+	if (t > TL - 1 || t < 0)
+	{
+		throw std::string{"invalid time slot"};
+	}
+
+	double yTotal = 0;				//remaining power capacity at slot t	
+	std::for_each(evList.begin(), evList.end(), [&yTotal, t](const EV& ev)
+	{
+		yTotal += ev.y[t];
+	});
+	while (yTotal < pwCapacity-0.01)
+	{		
+		std::list<EV*> curEvs;		//list of active EVs at time slot t	
+		for (auto& ev : evList)
+		{
+			if (ev.isActive(t) && ev.y[t] < ev.maxRate)
+			{
+				curEvs.insert(curEvs.end(), &ev);				
+			}
+		}
+		//std::cout << "curEvs: ";
+		//for (const auto& ev : curEvs)
+		//{
+		//	std::cout << ev->csID << " ";
+		//}
+		//std::cout << "\n";
+
+		if (curEvs.size() == 0)
+		{
+			break;
+		}
+		
+		double pTotal = 0;
[…]

### 2025-03-09 ev-scheduling-cpp/CS.h

@@ -1,0 +1,53 @@
+#pragma once
+#include "EV.h"
+#include <vector>
+#include <list>
+#include <random>
+#include <functional>
+
+
+
+//Time horizon {1...24}
+const size_t TL = 6;
+using slot = size_t;
+
+class EV;
+
+//charging station class
+class CS
+{
+	int n;
+	int evCapacity;						//size of charging station	
+	int pwCapacity;						//maximum output power of station at each time slot (kWh)
+	slot curSlot;						//current time slot	
+	std::list<EV> evList;
+	std::vector<std::vector<double>> Y; //n * TL matrix where Y[i][j] indicates allocated resource to EV i at time slot j 
+
+public:
+	CS() = delete;
+	CS(int e, int p, std::list<EV> evList);
+	CS(int e, int p, int n);
+	std::list<std::list<EV>> convertEvListToMatrix(const std::list<EV>& allEvs);
+
+	void WFAIR(slot t);
+	void WFAIR();
+	void WRAND(slot t);
+	void FOCS();
+	void FOCS(slot t);
+	std::list<EV> getEvList()
+	{
+		return evList;
+	}
+
+	friend std::ostream& operator << (std::ostream& os, const CS& cs);
+};
+
+std::list<EV> evGenerator(int n);
+
+std::ostream& operator << (std::ostream& os, const EV& ev);
+std::ostream& operator << (std::ostream& os, const CS& cs);
+
+int randi(int a, int b);		//[a,b]
+int randi(int b);				//[0,b]
+double randf(int a, int b);		//[a,b]
+double randf(int b);			//[0,b]

### 2025-03-09 ev-scheduling-cpp/EV.cpp

@@ -1,0 +1,41 @@
+#include "pch.h"
+#include "EV.h"
+#include <iostream>
+
+
+EV::EV(size_t a, size_t d, double v, double D, double k, double b, size_t id) :
+	arrival{ a }, deadline{ d }, value{ v }, demand{ D }, maxRate{ k }, batteryCapacity{ b }, csID{ id }, isFullyCharged_{ false },
+	remDemand{ D }, p{ value / demand }, parkTime{ d - a + 1 }, y(TL, 0)
+{
+	size_t minWaitingTime{ static_cast<size_t>(ceil(demand / maxRate)) };
+	if (a < 0 || d < 0 || v <= 0 || D <= 0 || k <= 0 || minWaitingTime > parkTime || D > batteryCapacity) //enforce invariant
+	{
+		std::cout << "bad object created:" << std::endl;
+		std::cout << "a:" << a << " d:" << d << " v:" << v << " D:" << D << " k:" << k << " b:" << b << " minWaitingTime:" << minWaitingTime << std::endl;
+		throw std::string{ "bad object" };
+	}
+}
+
+std::ostream& operator << (std::ostream& os, const EV& ev)
+{
+	//os << "constructor arguments: " <<  ev.arrival << "," << ev.deadline << "," 
+	//   << ev.value << "," << ev.demand << ","
+	//   << ev.maxRate << "," << ev.batteryCapacity << "," << ev.csID << "\n";
+
+	os << "a:" << ev.arrival << " ";
+	os << "d:" << ev.deadline << " ";
+	os << "v:" << ev.value << " ";
+	os << "D:" << ev.demand << " ";
+	os << "K:" << ev.maxRate << " ";
+	os << "b" << ev.batteryCapacity << " ";
+	os << "id" << ev.csID << " ";
+
+	os << "p:" << ev.p << " ";
+	os << "rD:" << ev.remDemand << " ";
+	os << "pTime:" << ev.parkTime << "\n";
+
+	os << "y vector: ";
+	for (size_t i = 0; i < TL; ++i)
+		os << ev.y[i] << " ";
+	return os;
+}

### 2025-03-09 ev-scheduling-cpp/EV.h

@@ -1,0 +1,42 @@
+#pragma once
+#include <vector>
+#include "CS.h"
+
+using slot = size_t;
+
+class EV
+{
+	size_t arrival;   //arrival time slot
+	size_t deadline;  //desired departure time slot
+	double value;     //value of demand (could represent price, priority, etc)	
+	double demand;    //electricty demand (kWh)	
+	double maxRate;   //maximum charging rate of EV in kWh
+
+	double batteryCapacity;
+	double remDemand; //remaining demand (dynamically updated)	
+	double p;         //value/demand ratio
+	size_t parkTime;  //number of time slots from arrival to departure
+	std::vector<double> y;  //y[i] is charging rate of the EV at time slot arrival+i
+	size_t csID;
+	bool isFullyCharged_;
+
+public:
+	EV() = delete;
+	EV(size_t a, size_t d, double v, double D, double k, double b, size_t id);
+
+	bool isFullyCharged() const
+	{
+		return isFullyCharged_;
+	}
+	bool isPresent(slot t) const
+	{
+		return (t >= arrival && t <= deadline);
+	}
+	bool isActive(slot t) const
+	{
+		return (!isFullyCharged() && isPresent(t));
+	}
+
+	friend std::ostream& operator << (std::ostream& os, const EV& ev);
+	friend class CS;
+};

### 2025-03-09 ev-scheduling-cpp/main.cpp

@@ -1,0 +1,26 @@
+#include "pch.h"
+#include "CS.h"
+#include <iostream>
+
+int main()
+{		
+	//a sample input
+	std::list<EV> evList;
+    evList.insert(evList.end(), EV(4,4,4.4,8,10,58,0));
+	evList.insert(evList.end(), EV(0,4,12.32,28,7,63,1));
+	evList.insert(evList.end(), EV(0,5,14.256,43.2,9,52,2));
+	evList.insert(evList.end(), EV(4, 5, 5.28, 16, 10, 89, 3));
+	evList.insert(evList.end(), EV(1, 3, 3.96, 12, 5, 46, 4));
+	evList.insert(evList.end(), EV(5, 5, 1.76, 3.2, 4, 25, 5));
+	
+	//std::list<EV> evList = evGenerator(6); //use this method to generate n random EV profiles instead of sample input
+	CS aCS(10, 12, evList); //generate a charging station with capacity for 10 EVs, power capacity of 12 kWh and EVs given in evList	
+	aCS.FOCS();
+	//aCS.WFAIR();			//allocate resources by WFAIR algorithm
+	std::cout << "Allocation finished" << std::endl << "----------Input:" << std::endl;
+	for (const auto& ev : aCS.getEvList())
+		std::cout << ev << std::endl;
+	std::cout << "-----------Output CS status:\n" << aCS << std::endl;
+
+	return 0;
+}
